### 2017-10-06 ARTICLE_STABFEM/ARTICLE_ASME.tex
Adding documentation

%%%%%%%%%%%%%%%%%%%%%%%%%%% asme2ej.tex %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Template for producing ASME-format journal articles using LaTeX    %
% Written by   Harry H. Cheng, Professor and Director                %
%              Integration Engineering Laboratory                    %
%              Department of Mechanical and Aeronautical Engineering %
%              University of California                              %
%              Davis, CA 95616                                       %
%              Tel: (530) 752-5020 (office)                          %
%                   (530) 752-1028 (lab)                             %
%              Fax: (530) 752-4158                                   %
%              Email: hhcheng@ucdavis.edu                            %
%              WWW:   http://iel.ucdavis.edu/people/cheng.html       %
%              May 7, 1994                                           %
% Modified: February 16, 2001 by Harry H. Cheng                      %
% Modified: January  01, 2003 by Geoffrey R. Shiflett                %
% Use at your own risk, send complaints to /dev/null                 %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%% use twocolumn and 10pt options with the asme2ej format
\documentclass[twocolumn,10pt]{asme2ej}

\usepackage{epsfig} %% for loading postscript figures

\graphicspath{{./}{./FIGURES/}}
\usepackage{listings}

\newcommand{\be}[1]{ \begin{equation} \label{#1}}
\newcommand{\ee}{\end{equation}}

\newcommand{\bes}[1]{ \begin{equation} \label{#1}\begin{array}{rl}}
\newcommand{\ees}{\end{array}\end{equation}}

%% The class has several options
%  onecolumn/twocolumn - format for one or two columns per page
%  10pt/11pt/12pt - use 10, 11, or 12 point font
%  oneside/twoside - format for oneside/twosided printing
%  final/draft - format for final/draft copy
%  cleanfoot - take out copyright info in footer leave page number
%  cleanhead - take out the conference banner on the title page
%  titlepage/notitlepage - put in titlepage or leave out titlepage
%  
%% The default is oneside, onecolumn, 10pt, final

\title{Popularizing linear and nonlinear global approaches to hydrodynamic instabilities : 
A review and a simple implementation for the wake of a cylinder}

%%% first author
\author{D. Fabre$^{(a)}$ et al.%, P. Bonnefis$^{(a)}$
    \affiliation{
	IMFT, University of Toulouse
    }	
}

%%% second author
%%% remove the following entry for single author papers
%%% add more entries for additional authors
%\author{V. Citro$^{(b)}$ \& F. Giannetti$^{(b)}$ \\
 %   \affiliation{ University of Salerno
  %  }
%}

\begin{document}
\lstset{numbers=left, numberstyle=\small, numbersep=8pt, frame = single, language=Matlab, framexleftmargin=15pt}

\maketitle

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
{\it This is the abstract.
This article illustrates preparation of ASME paper using 
\LaTeX2\raisebox{-.3ex}{$\epsilon$}.
An abstract for an ASME paper should be less than 150 words and is normally in italics.
%%% 
Please use this template to test how your figures will look on the printed journal page of the Journal of Mechanical Design.  The Journal will no longer publish papers that contain errors in figure resolution.  These usually consist of unreadable or fuzzy text, and pixilation or rasterization of lines.  This template identifies the specifications used by JMD some of which may not be easily duplicated; for example, ASME actually uses Helvetica Condensed Bold, but this is not generally available so for the purpose of this exercise Helvetica is adequate.  However, reproduction of the journal page is not the goal, instead this exercise is to verify the quality of your figures. Notice that this abstract is to be set in 9pt Times Italic, single spaced and right justified.  
}
\end{abstract}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Introduction}

The destabilization of a flow as a parameter is varied, leading from a steady solution to a unsteady one, is an ubiquous situation in fluid dynamics. Specific analytical and numerical methods suited to the description have emerged in the second part of the 19th century and continuously evolved up to the present day. When the flow has no analytical expression, the stability problem requires a numerical resolution, and when there are at least two spatial variables, the class of methods suited to solve such problems are generally called "global stability approaches."\footnote{Sorry Laurette !}

Among all instability problems, one of the most famous and most studied is the flow around a 2D cylinder, which becomes unsteady for $Re \approx 47$ leading to the well-known Bénard-Von Karman vortex alley. This situation has served as a benchmark in the development of this class of methods.  
If one is only interested in predicting the stability or instability of a flow, it is enough to conduct an  {\em linear stability analysis} which is the fundamental brick of global stability approaches. 
Beyond this simple question, in the past two decades, a number of extensions have been developed and popularized.  {\em Adjoint methods} are an important extension (Giannetti \& Luchini ; Marquet et al ) ; they can give insight into the sensitivity of the flow to intrinsic or extrinsic contributions. 
{\em Nonlinear stability approaches} (Sipp \& Lebedev; Mantic-Lugo et al) have also been developed in order to extend the range of applicability of the approach towards large amplitude perturbations.

%Among many others, the most noticable milestones are [?] for basic stability analysis,
%and for adjoint and sensitivity approaches, and for nonlinear approaches.

%Many discretization of spatial derivative operators (finite differences, spectral methods, ...) can be used to build. and is now routinely used by a growing number of teams

The objective of the present work is to contribute to the popularization of such methods 
in two ways:
%for both research and education purposes. 
\begin{itemize}
\item
First, we give a concise but self-contained exposition of the main concepts and 
specific numerical methods pertaining to global stability, including basic linear stability, adjoint-based sensitivity, as well as the most recent nonlinear developments.
\item
Secondly we offer an open-source and user-friendly software called  "StabFem" to perform such calculations. The software combines program written in both FreeFem++ and Matlab languages. 
FreeFem++ is used to generate and adapt the meshes and to solve the various linear problems arising in the analysis. Matlab is used as a driver to monitor the computations, perform the required loops over parameters, and plot the results.
\end{itemize}

In the present paper the concepts are introduced and the software is demonstrated for the reference case of the incompressible, two-dimensional flow around a cylinder, but the software is easily customizable to a variety of other situations (compressible, three-dimensional, etc..).

Although we don't claim to invent any radically new method, our exposition and implementation contains a number of originalities making the computation particularly efficient in terms of computational time and memory (all the figures of the paper can be produced in only a few minutes on a standard laptop). The most notable originalities are the systematic use of mesh adaptation (\S 2 and 3), the use of simple shift-invert instead of Arnoldi (\S 3), and a reformulation and simplification of the nonlinear self-consistent approach of Mantic-Lugo et al in terms of a harmonic balance (\S 4).

%which is based on both FreeFem++ and Matlab.
%The fundamental case of a cylinder is used as a guideline to present the method, but the 
%provide a simple and all-in-one implementation of

\section{Linear stability analysis : equations and methods}
\vspace{.2cm}

\subsection{Computing a base-flow with Newton iteration}
\vspace{.2cm}

\paragraph{Navier-Stokes equations and weak form}

We start from the general problem of a flow field $[{\bf u},p]$ satisfying the incompressible Navier-Stokes equations on a domain $\Omega$,
\be{NSprimitive}
\partial_t {\bf u} = NS ({\bf u};p)
\equiv - {\bf u} \cdot \nabla {\bf u} - \nabla p + \frac{2}{Re}  \nabla \cdot {\bf D}({\bf u})  \quad [\mbox{with} \nabla \cdot {\bf u} = 0].  \\
\ee
with suitable boundary conditions on the frontier $\partial \Omega$ of the domain.
Here $ {\bf D}({\bf u}) $ is the rate-of-strain tensor defined as
$$
 {\bf D}({\bf u}) = 1/2
\left( \nabla {\bf u} +  \nabla^T  {\bf u}\right)
$$ 
In the framework of finite element methods, it is convenient to write the equation in weak form.
Prior to this we define a scalar product as follows, for either scalar or vectorial quantities 
($\phi_1, \phi_2)$:
$$
\left< \phi_1, \phi_2 \right> = \int_\Omega \overline{\phi_1} \cdot \phi_2   \mbox{ d} \Omega
$$
The weak form of the Navier-Stokes equations is readily defined by introducing test functions 
$[{\bf v},q]$ associated with the momentum and continuity equations, and integrating over the domain\footnote{In the simple presentation given here we have omitted the issue of boundary conditions. Details on way boundary conditions can be incorporated in the weak formulation through integration by parts can be found in the appendix.}

\be{NSweak}
\forall [{\bf v},q], \quad \partial_t \left< {\bf v}, {\bf u}\right> = \left< {\bf v} , NS ({\bf u};p) \right> + \left< q, \nabla \cdot {\bf u}\right>.
\ee

%Note that the notation $NS ({\bf u})$ is a shortcut as it is defined as an operator acting on the velocity field ${\bf u}$, not on the full flow field $({\bf u},p)$.

%The incompressible Navier-Stokes equations can also be written into the more compact form :

%\be{NS}
%\partial_t {\bf u} \ee

%\subsection{Equations}
%\paragraph{Base-flow equations}

%$ {\bf D}({\bf u}) $ is the rate-of-strain tensor defined as

\paragraph{Newton iteration}

We look for a steady base-flow $({\bf u}_b;p_b)$ satisfying the steady Navier-Stokes equations, i.e. 
${\cal NS} ({\bf u}_b,p_b) = 0$.
Suppose that we have a 'guess' for the base flow $[{\bf u}_b^g,p_b^g]$  which almost satisfies the equations.  We look for a better approximation under the form
\be{Newton1}
[{\bf u}_b,p_b]  = [{\bf u}_b^g,p_b^g] + [\delta {\bf u}_b, \delta p_b].
\ee
Injecting into the Navier-Stokes equation in weak form (\ref{NSweak}) and developing up to linear terms in terms of the perturbation lead to  
$NS ({\bf u}_b^g,p_b^g) + NSL_{{\bf u}_b^g}(\delta {\bf u}_b,\delta p_b)$, which can also be written in weak form :
%\be
%{\cal C}( {\bf u}_b^g , \delta {\bf u}_b) -\nabla \delta p_b 
%-2 \nu \nabla  {\bf D}(\delta {\bf u}_b)
%+
%\left[{\bf u}_b^g \cdot \nabla {\bf u}_b^g - \nabla p_b^g -2 \nu {\bf D}(\delta {\bf u}_b^g) \right]
% \qquad \mbox{with} \nabla \delta {\bf u} = 0. 
%\ee
%Or equivalently, in weak form :
\bes{Newton2}
&\left< {\bf v}, NS ({\bf u}_b^g)\right> + \left<q, \nabla \cdot {\bf u}_b^g\right>  
\\
+ &\left< { \bf v}, NSL_{{\bf u}_b^g}( \delta {\bf u}_b,\delta p_b) \right> + \left<q, \nabla \cdot \delta{\bf u}_b\right> = 0.
\ees
Where $NSL$ is the linearised Navier-Stokes operator, defined by its action on a flow field $({\bf u} ; p)$ as follows 
\be{defNSL}
 NSL_{{\bf U}}( {\bf u} ;  p) = - {\cal C}( {\bf U} , {\bf u}) -\nabla p
+\frac{2}{Re} \nabla  \cdot {\bf D}({\bf u}), %\quad ( \mbox{ with } \nabla \cdot {\bf u } = 0 \, ).
 \ee
and {\cal C} is the convection operator defined by 
\be{defC}
{\cal C}( {\bf U} , {\bf u}) = \left( {\bf U} \cdot \nabla \right) {\bf u} + \left( {\bf u} \cdot \nabla \right)  {\bf U}.
\ee

This problem can now be discretized by projecting upon a basis of Taylor-Hood (P2-P2-P1) finite elements. Noting $\delta X$ the discretization of ($\delta {\bf u}_b;\delta p_b$) this eventually leads to a matricial problem with the form $A \cdot \delta X = Y$. The procedure of Newton iteration is to solve iteratively this set of equations up to convergence.
In our implementation, the algorithm is written in the Freefem++ solver {\em Newton\_2D.edp} 
which is wrapped by the Matlab driver {\em Freefem\_BaseFlow.m}.

\subsection{Linear stability}
\vspace{.2cm}

\paragraph{Direct eigenvalue problem}
We consider the stability using the classical ansatz 
\be{startmodepropre}
{\bf u} = {\bf u}_b + \epsilon \hat{\bf u} e^{\lambda t} 
\ee
Where $\lambda = \sigma + i \omega$ is the eigenvalue, $\sigma$ the amplification rate,
$\omega$ the oscillation rate, $\hat{{\bf u}}$ the eigenmode, and $\epsilon$ a small parameter.
The eigenmodes is governed by the linear problem 
$\lambda \hat{{\bf u}} = NSL_{{\bf u}_b}( \hat{\bf u},\hat{p})$, or, in weak form : 
\be{eigenvalueproblem}
\lambda \left< {\bf v} , \hat{{\bf u}} \right> = \left< {\bf v}, NSL_{{\bf u}_b} ( \hat{\bf u},\hat{p})\right> + \left< q, \nabla \cdot \hat{\bf u} \right>.
\ee
After discretization we end up with an eigenvalue problem with the matricial form
\be{Eigen_matricial}
\lambda B \hat{X} = A \hat{X}
\ee
Where $A$ is the matrix resulting from the discretization of $NSL_{{\bf u}_b}$, i.e. the very same matrix as appearing in the Newton computation of the base flow, and  $B$ is a 'weight' matrix associated to the scalar product $\left<v,u\right> = \int \overline{\bf v} \cdot {\bf u} \mbox{ d} \Omega$.

\paragraph{Adjoint eigenvalue problem and structural sensitivity}
Developed in the two past decades, the concept adjoint modes has now become an unavoidable complement to the linear global stability approach. We here give a short summary of the definition and usefulness of this concept.
We can first define the {\em adjoint linearised Navier-Stokes operator} $NSL^\dag$ defined by the property:
\bes{NSLAdj}
\forall ( {\bf u}, p ; {\bf v}, q), & \left< NSL^\dag_{\bf U}( {\bf v},q) ,{\bf u}\right> + \left< \nabla \cdot {\bf v},p\right>  \\
=& \left< {\bf v}, NSL_{\bf U} ({\bf u},p)\right> + \left< q, \nabla \cdot {\bf u}\right>.
\ees
We can then define the adjoint eigenmodes as the solutions to the eigenvalue problem 
\be{EigenAdj} 
\forall ( {\bf u}, p), \quad  \lambda^\dag \left< \hat{\bf v}, {\bf u}\right> =
 \left< NSL^\dag_{\bf U}( \hat{\bf v},\hat{q}) ,{\bf u}\right> + \left< \nabla \cdot \hat{\bf v},p\right>  
\ee
It can be shown (Schmid \& Henningson, 2001) that the adjoint eigenvalues $\lambda^\dag$ are the complex conjugates of the direct eigenvalues ($\lambda$).

Although the concept of adjoint operator may sound complicate, the resolution of the adjoint problem using finite elements methods is actually extremely easy. In effect, the scalar product used in the definition of the weak formulation and that appearing in the definition of adjoint being the same, the weak formulations of both problems are thus identical when exchanging the test functions and the unknown functions. Thus the matricial form of the discretized version of (\ref{EigenAdj} is deduced from the one of the direct problem by a simple transpose of the matrix :
\be{Eigen_Adj_matricial}
\overline{\lambda}^\dag B \hat{X}\dag = A^T \hat{X}\dag.
\ee

Adjoint eigenmodes are a powerful tool for investigating problems such as transient growth, control, sensitivity (see the reviews of Chomaz, Schmid, Luchini). The simplest physical interpretation of an adjoint eigenmode is as follows : it corresponds to the initial condition which has maximum projection along the direction of the corresponding eigenmode.
Thus, the adjoint of the most amplified mode corresponds to the optimal perturbation which will maximize the growth of energy in the limit of large time. In effect, one can prove that for $t \rightarrow \infty$  the asymptotic behaviour of a solution with initial condition ${\bf u}_i$  is given as :
$$
{\bf u}(t) \approx 
\frac{ \left< \hat{\bf u}^\dag, {\bf u}_i\right>}{\left<\hat{\bf u}^\dag, \hat{\bf u}\right>} 
e^{\lambda t} \hat{\bf u}  
$$.
The choice ${\bf u}_i = \hat{\bf u}^\dag$ is the initial condition of norm unity which maximizes the first factor in this expression.
%\item

The adjoint eigenmode also allows to deduce a quantity called the {\em structural sensitivity}  and defined as $S(x,y) = || \hat{\bf u}^\dag||  ||\hat{\bf u}||$ which has became popular in the recent years.
%is called the structural sensitivity of the eigenmode. 
This quantity is a direct and practical measure of the effect of perturbations of the linear operator on the eigenvalue. The region of the flow where $S(x,y)$ is thus the region where the instability mechanism originates, and is often referred to as the {\em wavemaker region}

%\end{itemize}

\paragraph{Iterative methods for eigenvalue computations}

When it comes to the numerical resolution of generalized eigenvalue problems such as $A X = \lambda B X$ (or its adjoint version), several methods are possible. Direct methods to compute the whole spectrum are both costly prohibitive and useless. A popular alternative is iterative methods which allow to compute a limited set of eigenvalues located in the vicinity of a 
"shift" value $\lambda_{shift}$. The simplest version of this method is the simple shift-invert iteration, which consists of solving iteratively the system
$$
X^{n} =  (A- \lambda_{shift} B)^{-1} B X^{n-1}
$$ 
It is easy to show that this quickly asymptotes to $X^{n+1} \approx ({\lambda^*}^{-1})^n \hat{X}$
where $\hat{X}$ is the eigenmode with largest ${\lambda^*}^{-1}$ (i.e. the one with eigenvalue $\lambda$ closest to the shift).

When one has a good estimation of the eigenvalue, this method converges very rapidly and is very efficient, but it can only provide a single eigenvalue.
If one wants to compute a larger number of eigenvalues, one can revert to a generalized version of iterative methods, called Arnoldi methods. The shift-invert version of the Arnoldi method is in fact the most commonly  used method of the current time and is at the basis of both the popular matlab solver eigs and the build-in eigenvalue solver of FreeFem. Our implementation in StabFem allows to chose between single eigenvalue computation (power method) and multiple eigenvalue computation (Arnoldi). The selection is made according to the parameter "nev" transmitted to the driver.

\subsection{Mesh adaptation procedure}
\vspace{.2cm}

As for any numerical method, a crucial point in the numerical efficiency is the design of the mesh. The finite element method allows to use unstructured mesh and hence to locally adapt the refinement. %Following Sipp \& Lebedev, 
The most common procedure is to decompose the domain into several parts with different grid densities ; for instance for the wake of a cylinder, we will design a near-wall region with very small  size, a "wake" region with intermediate mesh size, and an outer region with large mesh size. The inconvenient is that the design relies on an a priori expectation of the regions where gradients will be large.

In our implementation, we used an automatic mesh adaptation method. %which provides an optimal mesh adapted to the structure of the flow. 
The implementation relies on the AdaptMesh procedure of the FreeFem++ software. This procedure is detailed in detail in ref. []. In short, 
the classical Delaunay-Voronoi algorithm produces a mesh with gridpoint distribution specified by a {\em Metric } matrix $\cal M$. The AdaptMesh algorithm consists of using as a metric the {\em Hessian} (second-order spatial derivative) of an objective function $u_h$ defined over the domain, i.e. ${\cal M} = \nabla \nabla u_h$. The precision can be controlled by specifying an objective value for the interpolation error of the function on the new mesh.

To build an optimal mesh for the base-flow calculation, the idea is to use as the objective function $u_h$ the solution ${\bf u}_b$ itself, as computed on a previous mesh.%The procedure thus ensures that the mesh will be locally adapted to the gradients of the base flow. 
The base flow is then recomputed on the adapted mesh, providing a better approximation of the solution. The procedure can be repeated a few steps to ensure a right convergence.
In our implementation, the whole process is performed using the Matlab driver
 {\em Freefem\_AdaptMesh.m}.

\begin{figure*}[t]
\small
\begin{lstlisting}
baseflow = SF_Init('Mesh_Cylinder_Large.edp');
baseflow = SF_BaseFlow(baseflow,'Re',1);
baseflow = SF_BaseFlow(baseflow,'Re',10);
baseflow = SF_BaseFlow(baseflow,'Re',60);
baseflow = SF_Adapt(baseflow,'Hmax',10,'InterpError',0.01);
[ev,em] = SF_Stability(baseflow,'shift',0.04+0.74i,'type','S')
baseflow = SF_Adapt(baseflow,em,'Hmax',10,'InterpError',0.01);
plotFF(baseflow,'mesh'); plotFF(baseflow,'ux');

Re_Range = [2 : 2: 50]; Drag_tab = []; Lx_tab = [];
    for Re = Re_Range
        baseflow = SF_BaseFlow(baseflow,'Re',Re);
        Drag_tab = [Drag_tab,baseflow.Drag];
        Lx_tab = [Lx_tab,baseflow.Lx];
    end
plot(Re_Range,2*Drag_tab,'b+-');
plot(Re_Range,Lx_tab,'b+-');

Re_Range = [40 : 2: 100];lambda_branch=[];
baseflow=SF_BaseFlow(baseflow,'Re',40);
[ev,em] = SF_Stability(baseflow,'shift',-.03+.72i,'nev',1,'type','D');
    for Re = Re_Range
        baseflow = SF_BaseFlow(baseflow,'Re',Re);
        [ev,em] = SF_Stability(baseflow,'nev',1,'shift','cont');
        lambda_branch = [lambda_branch ev];
    end
plot(Re_Range,real(lambda_branch),'b+-');
plot(Re_Range,imag(lambda_branch)/(2*pi),'b+-');
\end{lstlisting}
\normalsize
\caption{Illustration of the computation of base-flow properties with StabFem (from script)}
\label{Listing2}
\end{figure*}

\begin{figure}
%\vspace{-.5cm}
\includegraphics[width=.9 \linewidth]{Cylinder_Mesh.png}
%\vspace{-.5cm}
%\vspace{-.5cm}
\includegraphics[width=.9 \linewidth]{Cylinder_BaseFlowReC.png}
%\vspace{-1.cm}
\caption{Adapted mesh $(a)$  and base flow (axial velocity component) ($b$) for the flow over a cylinder at $Re=Re_c = 46.7$.}
\label{fig:Baseflow}
\end{figure}

\begin{figure}
\includegraphics[width=.9 \linewidth]{Cylinder_Lx_baseflow.png}
\includegraphics[width=.9 \linewidth]{Cylinder_Drag_baseflow.png}
\caption{Recirculation length $L_x$ $(a)$  and drag $C_x$ ($b$) of the base flow over a cylinder as function of $Re$.}
\label{fig:LxandDrag}
\end{figure}

\section{Illustration for the wake of a cylinder} 
\vspace{.2cm}

\paragraph{Problem description}

We will now illustrate the applicati

\paragraph{Mesh adaptation procedure}

\paragraph{Base flow}

Having thus produced an convenient mesh, we can now illustrate the properties of the base flow as function of Reynolds number. Figure (\ref{Listing2}) shows how to compute and plot with StabFem the two most commonly studied quantities, namely the drag coefficient $C_x(Re)$  and the recirculation length $Lx(Re)$, namely the location of the stagnation point at the rear of the recirculation region. 
Note that the object \verb|baseflow| is defined as a structure with fields \verb|Drag| and \verb|Lx|. 
The resulting plots are given in figure (\ref{fig:LxandDrag}), and are in good agreement with known results for this classical problem.
In particular, for low Reynolds, the recirculation $L_x(Re)$ is equal to $0.5$ (which is the radius of the cylinder) indicating the absence of a recirculation region. The latter appears for $Re > 4.8$, in accordance with known results.

%\subsection{Implementation}

%\subsection{Application to the cylinder}

%\clearpage

%We now review the main concepts of linear stability approach and explain how such calculations are implemented in our software.

\begin{figure}
%\vspace{-.5cm}
\includegraphics[width=.9 \linewidth]{Cylinder_EigenModeReC.png}
%\vspace{-.5cm}
%\vspace{-.5cm}
\includegraphics[width=.9 \linewidth]{Cylinder_EigenModeAdjReC.png}
%\vspace{-.5cm}\vspace{-.5cm}
\includegraphics[width=.9 \linewidth]{Cylinder_SensitivityReC.png}
%\vspace{-.5cm}
\caption{Eigenmode $(a)$  (axial velocity component),  Adjoint mode $(b)$ and structural sensitivity ($c$) for the cylinder's wake at $Re=Re_c = 46.7$.}
\label{fig:Eigenmode}
\end{figure}

\begin{figure}
\includegraphics[width=.9 \linewidth]{Cylinder_Sigma_Re.png}
\includegraphics[width=.9 \linewidth]{Cylinder_Strouhal_Re.png}
\caption{Growth rate $\sigma$ $(a)$  and Strouhal number $St = (a \omega)/(2\pi U_0)$ ($b$) as function of Reynolds number}
\label{fig:SigmaOmega}
\end{figure}

%\begin{figure*}
%\small
%\begin{lstlisting}
%\end{lstlisting}
%\normalsize
%\caption{Illustration of the procedure to compute stability properties and adapt the mesh using StabFem (from script {\em SCRIPT\_CYLINDER.m}. }
%\label{listing4}
%\end{figure*}

\paragraph{Linear stability results}

%popular class of method are {\em power methods} which allow to compute a limited set

%based on the idea that the repeated application of an operator mostly amplifies the perturbations along the eigenspaces with largest eigenvalues.

%These de Andrea Fani

%\paragraph{Implementation and mesh adaptation for stability calculations}

Matlab driver...

%\paragraph{Sample results}

%\subsection{Illustration of the mesh adaptation for stability calculations}

%See listing....

%\subsection{Sample results for a cylinder}

%\clearpage

\section{Nonlinear global stability approaches}
\vspace{.2cm}
%\section{Computing the limit cycle for $Re>Re_c$ with Harmonic Balance}

\paragraph{Review on nonlinear global stability approaches}
%For $Re\right>Re_c$, the linear stability analysis based on the {\em base flow} does not allow to predict the properties of the limit cycle; in particular the Strouhal number is substantially underestimated. %It has been shown that investigating the stability properties of the {\em mean flow} obtained by averaging time-marching solution gives a better accordance. Attempts to on a rigourous basis  
In the past decade, efforts have been devoted to extend the range of validity of global approaches into the nonlinear régime for $Re>Re_c$, with the double objective to describe the properties of the limit cycle reached after saturation and to derive amplitude equations describing the transitent dynamics towards this cycle.
 The first milestone in that direction is the work of Sipp \& Lebedev who used a weakly nonlinear development in terms of the distance to the threshold $Re-Re_c$. However, although derived on rigorous grounds, the weakly nonlinear development has a very limited range of validity and already fails for $Re\ge47$.
More recently,  Mantic-lugo et al.  proposed an alternative approach termed {\em Self-consistent model} which succeeds in predicting the dynamics up to $Re =120$ and more. 
This model was build as a linear stability approach build on a {\em mean flow} which includes a 
retroaction of the eigenmode. However, if one is interested in the limit cycle and not the transient,
the approach is actually equivalent to a Fourier series decomposition of the flow with respect to time (an approach also known as {\em harmonic balance}) retaining only the two first terms. 
%The approach is based on a generalisation of the eigenmode ansatz \ref{} and

In the next section we thus present this model and propose a direct resolution method. The relation with the initial method of Mantic-Lugo et al. will be discussed afterwards.

\paragraph{Harmonic balance : equations and procedure }

In this section, to simplify the notations, The Navier-Stokes equations will be written symbolically as 
$\partial_t  {\bf u }  = NS(  {\bf u } )$, therefore droping the systematic reference of the incompressibility constraint and associated pressure field.

We thus start with a Fourier decomposition of the limit cycle under the form :
\be{HB}
{\bf u } = {\bf u }_0 + {\bf u }_1 e^{i \omega t} +   {\bf u }_{-1} e^{-i \omega t}
\ee  
Here ${\bf u }_0$ is the mean flow (averaged over time),  ${\bf u }_1$ is the mode
(fourrier component at the fundamental frequency), ${\bf u }_{-1} = \overline{{\bf u }_1}$ is its complex conjugate, and $\omega$ is the (real) oscillation frequency of the limit cycle (which is not known a priori). Injecting this ansartz into the Navier-Stokes equations and taking the mean value and first Fourier component leads to the following coupled equations :
\be{HBEq0}
NS(  {\bf u }_0 ) - {\cal C}( {\bf u }_1, \overline{\bf u }_1) = 0,
\ee
\be{HBEq1}
i \omega {\bf u }_1 =  NSL_{{\bf u }_0}(  {\bf u }_1 ).
\ee

Note that the Fourier description of the limit cycle is invariant with respect to the phase $\phi$ (i.e. the equations are unchanged when replacing $[ {\bf u }_1,  {\bf u }_{-1}] $ by  $[ {\bf u }_1 e^{i\varphi},  {\bf u }_{-1}  e^{-i\varphi}] $. 
To allow resolution we thus need an extra equation to fix this phase. Several choices are possible, but a convenient one is to set the lift associated with the imaginary part of ${\bf u }_1$ to lift. Physically, this means that the instant $t=0$ will correspond to a maximum of lift. This condition reads :
\be{HBphase}
\Im F_y({\bf u}_1) =0
\ee

With $F_y ({\bf u_1}) = 
 \int_{\Gamma_w} \left[-p_1 {\bf n} + \frac{2}{Re} {\bf D}({\bf u_1}) \cdot {\bf n} \right]   \cdot {\bf e_y}  = 0.$

Mathematically, the problem $\ref{HBEq0,HBEq1,HBphase}$ for the unknown $[{\bf u }_0, {\bf u }_{1}, \omega]$ is well posed, and can be solved using a Newton iteration just as explained for the base flow in section 2. To allow resolution, we separate the mode into real and imaginary part, by writing ${\bf u }_1 = {\bf u }_{1,r} +  i {\bf u }_{1,i} $.
We then assume that we know a 'guess' 
$$
[{\bf u }_0, {\bf u }_{1,r}, {\bf u }_{1,i}, \omega] = 
 [{\bf u }_0^g, {\bf u }_{1,r}^g, {\bf u }_{1,i}^g, \omega^g]
+ [\delta {\bf u }_0, \delta {\bf u }_{1,r}, \delta {\bf u }_{1,i}, \delta \omega]
$$.

Injecting and developing up to linear order leads to the following 
\begin{equation}
\begin{array}{ll}
\displaystyle
& NS(  {\bf u }_0^g ) - [ {\cal C}( {\bf u }_{1,r}^g,{\bf u }_{1,r}^g) +  {\cal C}( {\bf u }_{1,i}^g,{\bf u }_{1,i}^g) ]
\\
+& NSL_{{\bf u }_0^g}(\delta {\bf u }_0) - 2 [ {\cal C}( {\bf u }_{1,r}^g,\delta {\bf u }_{1,r}) +  {\cal C}( {\bf u }_{1,i}^g,\delta {\bf u }_{1,i}) ] = 0;
\\
\\
&  NSL_{{\bf u }_0^g}( {\bf u }_{1,r}^g) - \omega^g {\bf u }_{1,i}^g 
 \\
  +& NSL_{{\bf u }_0^g}( \delta {\bf u }_{1,r}^g) 
   -  {\cal C}( \delta {\bf u }_{0}^g, {\bf u }_{1,r})
   - \delta \omega^g \delta {\bf u }_{1,i}^g 
 - \omega^g \delta {\bf u }_{1,r} = 0 ;
 \\
\\
&  NSL_{{\bf u }_0^g}({\bf u }_{1,i}^g) + \omega^g {\bf u }_{1,i}^g
 \\
  +& NSL_{{\bf u }_0^g}( \delta {\bf u }_{1,i}^g) 
  -  {\cal C}( \delta {\bf u }_{0}^g, {\bf u }_{1,i}) 
  + \delta \omega^g \delta {\bf u }_{1,i}^g 
+ \omega^g \delta {\bf u }_{1,r} = 0 ;
\\
\\
& F_y({\bf u }_{1,i}^g) + F_y(\delta {\bf u }_{1,i}) = 0.
 \end{array}
\end{equation}

After discretization, this leads to a linear problem with the form $A X = Y$ where $X$ is the discretized version of the unknowns  $[\delta {\bf u }_0, \delta {\bf u }_{1,r}, \delta {\bf u }_{1,i}, \delta \omega]$, and $A$ is a matrix of dimension $3 N_{dof} +1$.

%\ref{HBEq0,HBEq1,HBphase}

\paragraph{Results for the wake of a cylinder}

\paragraph{Link with the Self-Consistent approach}

We now discuss the link between the harmonic balance approach presented above and the self-consistent approach as introduced by Mantic-Lugo et al.
The starting point of this model is a pseudo-eigenmode expansion of the flow as follows :

\be{SC}
{\bf u } = {\bf u }_m + A \left[ \tilde{{\bf u }}_1 e^{\sigma_{SC} t + i \omega_{SC} t} +   \tilde{\bf u }_{-1} e^{\sigma_{SC} t  -i \omega_{SC} t} \right]
\ee  
Where ${\bf u }_m$ is a {\em mean flow} defined by phase-averaging over the cycle, $\tilde{{\bf u }}_1$ is a pseudo-eigenvector which is normalized by the condition  $||\tilde{{\bf u }}_1|| = 1/\sqrt{2}$, 
 $A$ is an amplitude parameter directly related to the energy of the oscillating flow, and $\lambda = \sigma_{SC} + i \omega_{SC}$ is a pseudo-eigenvalue which depends upon the parameter $A$. The mean flow is then governed by the same equation
(\ref{HBEq0}) written above, while $\tilde{{\bf u }}_1$ is the solution of an eigenvalue problem with the same form as  (\ref{HBEq1}) except that $i \omega$ is replaced by $\sigma_{SC} + i \omega_{SC}$.
The self-consistent model has the following properties :
\begin{itemize}
\item[-] For $A \ll 1$ it is equivalent to the linear eigenvalue problem (\ref{LEP}), and the generalized eigenvalue coincides with the one predicted by linear stability : $\sigma_{SC} + i \omega_{SC} = \sigma_{lin} + i \omega_{lin}$. 
\item[-] For $\sigma_{SC}=0$ (corresponding to a specific choice of the amplitude $A=A_c$),  the expansion (\ref{SC}) is equivalent to the harmonic-balance decomposition (\ref{HB})
\item[-] For $0<A<A_c$, the resolution leads to a relation $\sigma_{SC}(A) ; \omega_{SC}(A)$
such that $0< \sigma_{SC}(A) < \sigma_{lin}$.
 Although in this case the expansion \ref{SC} cannot represent the flow for all $t$, Mantic-Lugo et al. argued that the relation between $\sigma_{SC}$ and $A$ can be used to build an amplitude equation which captures the transient approach to the limit cycle. 
\end{itemize}

%Barkley [] and Leontini [] have

\begin{figure}
\begin{center}
\includegraphics[width=.9 \linewidth]{Cylinder_Lx_Re_HB.png}
\includegraphics[width=.9 \linewidth]{Cylinder_Drag_Re_HB.png}
\end{center}
\caption{Harmonic-balance results : mean-flow characteristics}
\label{fig:HB}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[width=.9 \linewidth]{Cylinder_Strouhal_Re_HB.png}
\includegraphics[width=.9 \linewidth]{Cylinder_Lift_Re_SC.png}
\includegraphics[width=.9 \linewidth]{Cylinder_Energy_Re_SC.png}
\end{center}
\caption{Harmonic-balance results : mode characteristics}
\label{fig:HB}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[width=.9 \linewidth]{Cylinder_SC100_EnergySigma.png}
\includegraphics[width=.9 \linewidth]{Cylinder_SC100_LiftSigma.png}
\end{center}
\caption{SELF CONSISTENT APPROACH FOR THE WAKE OF A CYLINDER, $Re = 60$}
\label{fig:SC60}
\end{figure}

\appendix

\section{Appendix : details on mesh convergence}

\paragraph{Illustration of mesh convergence procedure for a cylinder}

\begin{figure*}
\small
\begin{lstlisting}
> baseflow=SF_Init('Mesh_Cylinder_Large.edp');
      ### INITIAL MESH CREATED WITH np = 2207 points
> baseflow=SF_BaseFlow(baseflow,'Re',1);
      ### FUNCTION SF_BaseFlow : computing base flow for Re = 1
      # Base flow converged in 6 iterations ; Drag = 5.9876; Lx = 0.501
> baseflow=SF_BaseFlow(baseflow,'Re',10);
      ### FUNCTION SF_BaseFlow : computing base flow for Re = 10
      # Base flow f converged in 5 iterations ; Drag = 1.4519; Lx = 0.73191
> baseflow=SF_BaseFlow(baseflow,'Re',60);
      ### FUNCTION SF_BaseFlow : computing base flow for Re = 60
      # Base flow converged in 6 iterations ; Drag = 0.66348; Lx = 3.6989

> baseflow=SF_Adapt(baseflow,'Hmax',10,'InterpError',0.01);
     ### ADAPT mesh to base flow ; InterpError = 0.01  ; Hmax = 10
      #   Number of points np = 1352 ; Ndof = 11862
      #  h_min, h_max : 0.018824 , 10.2895
      #  h_(A,B,C,D) : 0.027467 , 0.28644 , 0.45948 , 0.89245
      ### FUNCTION SF_BaseFlow : computing base flow for Re = 60
      # Base flow converged in 5 iterations ; Drag = 0.65805; Lx = 4.0737

> plotFF(baseflow,'mesh');

\end{lstlisting}
\normalsize

\caption{Illustration of the procedure to compute a base flow and an adapted mesh using StabFem (from script {\em SCRIPT\_CYLINDER.m}. }
\end{figure*}

\begin{figure*}
\small
\begin{lstlisting}
> [ev,em] = SF_Stability(baseflow,'shift',0.04+0.76i,'nev',1,'type','D');
> [baseflow,em]=SF_Adapt(baseflow,em,'Hmax',10,'InterpError',0.005);  
      ### ADAPT mesh to base flow AND MODE   ; InterpError = 0.005  ; Hmax = 10
      #   Number of points np = 13458 ; Ndof = 120030
      #  deltamin, deltapax : 0.0089891 , 13.367
      #  delta_(A,B,C,D) : 0.020536 , 0.082852 , 0.07316 , 0.11914
      ### FUNCTION SF_BaseFlow : computing base flow for Re = 60
      # Base flow converged in 4 iterations ; Drag = 0.64695; Lx = 4.0715
      ### FUNCTION SF_Stability : computation of 1 eigenvalues/modes (DIRECT) with FF solver
      # Stability calculation converged in 4 iterations, lambda = 0.047152+0.74808i.

> [ev,em] = SF_Stability(baseflow,'shift',0.04+0.76i,'nev',1,'type','S');
> [baseflow,em]=SF_Adapt(baseflow,em,'Hmax',10,'InterpError',0.005);
      ### ADAPT mesh to base flow AND SENSITIVITY ; InterpError = 0.005  ; Hmax = 10
      #   Number of points np = 4355 ; Ndof = 38559
      #  deltamin, deltapax : 0.0058536 , 13.1164
      #  delta_(A,B,C,D) : 0.01049 , 0.091861 , 0.13319 , 0.89372
      ### FUNCTION SF_BaseFlow : computing base flow for Re = 60
      # Base flow converged in 3 iterations ; Drag = 0.64758; Lx = 4.0725
      ### FUNCTION SF_Stability : computation of 1 eigenvalues/modes (DIRECT) with FF solver
      # Stability calculation converged in 3 iterations (D+A+S), lambda = 0.047165+0.74823i.

\end{lstlisting}
\normalsize

\caption{Illustration of the procedure to adapt the mesh for stability calculations with StabFem (from script {\em SCRIPT\_CYLINDER.m}. }
\end{figure*}

We illustrate the procedure in the case of a cylinder.  Figure 1 gives a retranscription of the sequence of commands (from {\em SCRIPT\_CYLINDER\_ADAPTMESH\_BASEFLOW}) 
and the output produced.
First we build an initial mesh (line 1), and compute base flow solutions for increasing values of the Reynolds number up to $Re = 60$ (lines 3-9).

Then we perform the mesh adaptation (line 13). The produced outputs (lines 14-17) gives information about the resulting mesh. 
Note the values $h_{min}$ and $h_{max}$ of the smaller and larger edges, as well as the local grid size at four points A,B,C,D defined as $(x_A,y_A) = (0.5,0)$ (at the surface of the cylinder at the position of maximum shear), $(x_B,y_B) = (0.5,2.5)$ (at the location of the peak of structural sensitivity, see next section), $(x_C,y_C) = (0.,4)$ (in the near wake), and $(x_D,y_D) = (0.,10)$ (in the the far wake). Finally, the base flow is automatically recomputed on the resulting mesh (line 18-19). Finally, lines 21-22 plot the mesh and base flow structure, producing the result displayed in figure (\ref{fig:Baseflow}).

\begin{figure*}
\small
\begin{lstlisting}
\end{lstlisting}
\normalsize

\caption{Illustration of the procedure to adapt the mesh for stability calculations with StabFem (from script {\em SCRIPT\_CYLINDER.m}. }
\label{listing3}
\end{figure*}

\section{Detail of the weak formulation}
%The problem can be set into weak form by multiplying by multiplying Eq. \ref{Newton2} by a test function ${\bf v}$ and the associated divergence constraint by a test function $q$. After a few integration by parts we are led to :
\begin{eqnarray}
\label{NewtonWeak}
&\forall ({\bf v};q), \\
\displaystyle &\int \left[ {\bf v} \cdot {\cal C}( {\bf u}_b^g , \delta {\bf u}_b) +  \nabla  \cdot \delta {\bf u}_b q -\nabla  \cdot {\bf v} \delta p_b
+ \frac{2}{Re} {\bf D}(\delta {\bf u}_b) : {\bf D}({\bf v}) \right]
\nonumber
\\
\nonumber
\displaystyle & + \int \left[ {\bf v} \cdot ( {\bf u}_b^g \cdot \nabla {\bf u}_b^g) 
+ \nabla \cdot {\bf u}_b^g  q 
- \nabla \cdot {\bf v} p_b^g
+ \frac{2}{Re} {\bf D}({\bf u}_b^g) : {\bf D}({\bf v}) \right] = 0 
\end{eqnarray}

\end{document}

### 2017-10-09 ARTICLE_STABFEM/ARTICLE_ASME.tex
minor fix

@@
 
-\subsection{Mesh adaptation procedure}
-\vspace{.2cm}
-
-As for any numerical method, a crucial point in the numerical efficiency is the design of the mesh.
-The finite element method allows to use unstructured mesh and hence to locally adapt the refinement.
-%Following Sipp \& Lebedev,
-The most common procedure is to decompose the domain into several parts with different grid densities ; for instance for the wake of a cylinder, we will design a near-wall region with very small  size, a "wake" region with intermediate mesh size, and an outer region with large mesh size.
-The inconvenient is that the design relies on an a priori expectation of the regions where gradients will be large.
-
-In our implementation, we used an automatic mesh adaptation method. %which provides an optimal mesh adapted to the structure of the flow. 
-The implementation relies on the AdaptMesh procedure of the FreeFem++ software. This procedure is detailed in detail in ref. []. In short, 
-the classical Delaunay-Voronoi algorithm produces a mesh with gridpoint distribution specified by a {\em Metric } matrix $\cal M$.
-The AdaptMesh algorithm consists of using as a metric the {\em Hessian} (second-order spatial derivative) of an objective function $u_h$ defined over the domain, i.e.
-${\cal M} = \nabla \nabla u_h$.
-The precision can be controlled by specifying an objective value for the interpolation error of the function on the new mesh.
-
-To build an optimal mesh for the base-flow calculation, the idea is to use as the objective function $u_h$ the solution ${\bf u}_b$ itself, as computed on a previous mesh.%The procedure thus ensures that the mesh will be locally adapted to the gradients of the base flow.
-The base flow is then recomputed on the adapted mesh, providing a better approximation of the solution. The procedure can be repeated a few steps to ensure a right convergence.
-In our implementation, the whole process is performed using the Matlab driver
- {\em Freefem\_AdaptMesh.m}.
-
 \begin{figure*}[t]
@@
 
+\subsection{Mesh adaptation procedure}
+\vspace{.2cm}
+
+As for any numerical method, a crucial point in the numerical efficiency is the design of the mesh.
+The finite element method allows to use unstructured mesh and hence to locally adapt the refinement.
+%Following Sipp \& Lebedev,
+The most common procedure is to decompose the domain into several parts with different grid densities ; for instance for the wake of a cylinder, we will design a near-wall region with very small  size, a "wake" region with intermediate mesh size, and an outer region with large mesh size.
+The inconvenient is that the design relies on an a priori expectation of the regions where gradients will be large.
+
+In our implementation, we used an automatic mesh adaptation method. %which provides an optimal mesh adapted to the structure of the flow. 
+The implementation relies on the AdaptMesh procedure of the FreeFem++ software. This procedure is detailed in detail in ref. []. In short, 
+the classical Delaunay-Voronoi algorithm produces a mesh with gridpoint distribution specified by a {\em Metric } matrix $\cal M$.
+The AdaptMesh algorithm consists of using as a metric the {\em Hessian} (second-order spatial derivative) of an objective function $u_h$ defined over the domain, i.e.
+${\cal M} = \nabla \nabla u_h$.
+The precision can be controlled by specifying an objective value for the interpolation error of the function on the new mesh.
+
+To build an optimal mesh for the base-flow calculation, the idea is to use as the objective function $u_h$ the solution ${\bf u}_b$ itself, as computed on a previous mesh.%The procedure thus ensures that the mesh will be locally adapted to the gradients of the base flow.
+The base flow is then recomputed on the adapted mesh, providing a better approximation of the solution. The procedure can be repeated a few steps to ensure a right convergence.
+
+The mesh generated in the previous way may not be optimal for the stability calculations as the structure of the eigenmode may be more complex than that of the base flow.
+To remedy with this, the idea is to subsequently adapt the mesh to both the mesh flow and the results of the stability calculation.
+This is easily done with FreeFem, as the  AdaptMesh procedure can be used with several objective functions.
+We have experimented two different ideas.
+The first is to adapt the mesh to the base flow and the structure of the leading eigenmode.
+A second and smarter idea is to adapt the mesh to the base flow and the structural sensitivity.
+Since this quantity is directly linked to the sensitivity of the eigenvalues to perturbations of any kind (including spatial discretization errors), this procedure yields a lighter mesh while ensuring that the eigenvalue is effectively converged with respect to discretization errors.
+On the other hand, if one is interested to know the structure of the eigenmode (which may extend far away from the wavemaker region), it is more recommended to use mesh adaptation on the structure of the eigenmode.
+
+In our implementation, the whole process is performed using the Matlab driver {\em Freefem\_AdaptMesh.m} ; the kind of adaptation (to base flow only, to eigenmode, or to sensitivity) is decided by the choice of parameters transmitted to this function.
+
 \section{Illustration for the wake of a cylinder} 
@@
 
+SECTION TO BE COMPLETED.
+
 \paragraph{Problem description}
 
-We will now illustrate the applicati
+Cylinder of unit diameter (radius $r=1/2$), velocity $U = 1$ at inlet.
+
+Domain dimension $[-40,80]x[0,40]$. No-stress conditions at outlet AND LATERAL BOUNDARY.
 
 \paragraph{Mesh adaptation procedure}
+
+Lines 1-7 of the script.
 
@@
 
-%popular class of method are {\em power methods} which allow to compute a limited set
+Figure \ref{fig:Eigenmode} : description of eigenmode.
 
-%based on the idea that the repeated application of an operator mostly amplifies the perturbations along the eigenspaces with largest eigenvalues.
-
-%These de Andrea Fani
-
-%\paragraph{Implementation and mesh adaptation for stability calculations}
-
-Matlab driver...
-
-%\paragraph{Sample results}
-
-%\subsection{Illustration of the mesh adaptation for stability calculations}
-
-%See listing....
-
-%\subsection{Sample results for a cylinder}
-
-%\clearpage
+Figure \ref{fig:SigmaOmega} : growth rates/Strouhal.
 
@@
 
+SECTION TO BE COMPLETED
+
 \paragraph{Link with the Self-Consistent approach}
@@
 \section{Appendix : details on mesh convergence}
+
+SECTION TO BE COMPLETED
 
@@
 After a few integration by parts we are led to :
+
+SECTION TO BE COMPLETED.
+
+We have to explain the integration by parts of the viscous term.
+
 \begin{eqnarray}

### 2017-10-09 CYLINDER/SCRIPT_CYLINDER_DEMO.m

@@ -1,19 +1,25 @@
-% Matlab interface for GlobalFem
+%  Instability of the wake of a cylinder with STABFEM  
 %
-%   (set of programs in Freefem to perform global stability calculations in hydrodynamic stability)
-%  
-%  THIS SCRIPT DEMONSTRATES THE SOFTWARE FOR THE WAKE OF A CYLINDER
+%  this scripts performs the following calculations :
+%  1/ Generation of an adapted mesh
+%  2/ Base-flow properties for Re = [2-40]
+%  3/ Stability curves St(Re) and sigma(Re) for Re = [40-100]
+%  4/ Determination of the instability threshold
+%  5/ Harmonic-Balance for Re = REc-100
+%  6/ Self-consistent model for Re=100
+
+% CHAPTER 0 : set the global variables needed by the drivers
 
 global ff ffdir ffdatadir sfdir verbosity
-ff = '/PRODCOM/FREEFEM/Ubuntu12.04/3.29/bin/FreeFem++-nw'; %% Freefem command with full path 
+%ff = '/PRODCOM/FREEFEM/Ubuntu12.04/3.29/bin/FreeFem++-nw'; % on IMFT network
+ff = '/usr/local/ff++/openmpi-2.1/3.55/bin/FreeFem++-nw'; % on DF's macbookpro 
 ffdatadir = './WORK/';
 sfdir = '../SOURCES_MATLAB/'; % where to find the matlab drivers
 ffdir = '../SOURCES_FREEFEM/'; % where to find the freefem scripts
 verbosity = 1;
 addpath(sfdir);
 system(['mkdir ' ffdatadir]);
-%figureformat= 'epsc'; % to generate eps figure files
-figureformat='png';
+figureformat='png'; AspectRatio = 0.56; % for figure
 
 %##### CHAPTER 1 : COMPUTING THE MESH WITH ADAPTMESH PROCEDURE
 
@@ -33,75 +39,63 @@ baseflow=SF_BaseFlow(baseflow,10);
 baseflow=SF_BaseFlow(baseflow,60);
 baseflow=SF_Adapt(baseflow,'Hmax',5);
 baseflow=SF_Adapt(baseflow,'Hmax',5);
+disp(' ');
+disp('mesh adaptation to SENSITIVITY : ')
[…]

### 2017-10-09 CYLINDER/SCRIPT_CYLINDER_MESHTESTS.m

@@ -1,26 +1,28 @@
-% Matlab interface for GlobalFem
+%  Instability of the wake of a cylinder with STABFEM  
 %
-%   (set of programs in Freefem to perform global stability calculations in hydrodynamic stability)
-%  
-%  THIS SCRIPT DEMONSTRATES THE SOFTWARE FOR THE WAKE OF A CYLINDER
+%  THIS SCRIPT COMPARES THE RESULTS OBTAINED WITH 7 DIFFERENT MESHES
+
+% CHAPTER 0 : set the global variables needed by the drivers
 
 global ff ffdir ffdatadir sfdir verbosity
-ff = '/usr/local/ff++/openmpi-2.1/3.55/bin/FreeFem++-nw -v 0'; %% Freefem command with full path 
+%ff = '/PRODCOM/FREEFEM/Ubuntu12.04/3.29/bin/FreeFem++-nw -v 0'; % on IMFT network
+ff = '/usr/local/ff++/openmpi-2.1/3.55/bin/FreeFem++-nw -v 0'; % on DF's macbookpro 
 ffdatadir = './WORK/';
 sfdir = '../SOURCES_MATLAB/'; % where to find the matlab drivers
 ffdir = '../SOURCES_FREEFEM/'; % where to find the freefem scripts
 verbosity = 1;
 addpath(sfdir);
 system(['mkdir ' ffdatadir]);
-%figureformat= 'epsc'; % to generate eps figure files
-figureformat='png';
+figureformat='png'; AspectRatio = 0.56; % for figure
 
-%##### CHAPTER 1 : COMPUTING THE MESH WITH ADAPTMESH PROCEDURE
 
-disp(' MESH based on base flow : ');     
-disp(' ');
-disp(' LARGE MESH : [-40:80]x[0:40] ');
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 disp(' ');    
+disp('### 1 : MESH based on base flow : ');     
+disp(' ');
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+
 baseflow=SF_Init('Mesh_Cylinder_Large.edp');
 baseflow=SF_BaseFlow(baseflow,1);
 baseflow=SF_BaseFlow(baseflow,10);
[…]

### 2017-10-09 EXAMPLES/SCRIPT_DiskInTube.m

@@ -1,191 +1,0 @@
-% Matlab interface for GlobalFem
-%
-%   (set of programs in Freefem to perform global stability calculations in hydrodynamic stability)
-%  
-%  Demonstration script for the test-case of a cylindrical object in a tube
-%
-% Version 2.0 by D. Fabre , june 2017
-
-
-%close all;
-global ff ffdir ffdatadir sfdir verbosity
-ff = '/usr/local/ff++/openmpi-2.1/3.55/bin/FreeFem++-nw -v 0'; %% Freefem command with full path 
-ffdatadir = './DATA_FREEFEM_DISKINTUBE';
-sfdir = '../SOURCES_MATLAB'; % where to find the matlab drivers
-ffdir = '../SOURCES_FREEFEM/'; % where to find the freefem scripts
-verbosity=1; % use 1 to display FreeFem outputs, 0 to hide them (use 0 for demo mode, otherwise 1 is recommended)
-
-addpath(sfdir);
-
-% 
-Re = 200;
-if(exist([ ffdatadir '/CHBASE/chbase_Re' num2str(Re) '.txt'])==2)
-     disp(['base flow and adapted mesh for Re = ' num2str(Re) ' already computed']);
-    if (exist('baseflow')==0); % if the data are present but the variables were cleared
-    mesh=importFFmesh('mesh.msh');
-    baseflow =importFFdata(mesh,[ ffdatadir '/CHBASE/chbase_Re' num2str(Re) '.ff2m']);
-    end
-else
-    disp('computing base flow and adapting mesh')
-   
-    baseflow = FreeFem_Init('meshInit_DiskInTube.edp'); 
-    Re_start = [10 , 100 , 200]; % values of Re for progressive increasing up to end
-    for Rei = Re_start
-        baseflow=FreeFem_BaseFlow(baseflow,Rei); 
-        baseflow=FreeFem_Adapt(baseflow);
-    end
-    
- % optional : adapting mesh on eigenmode structure as well      
- [ev,eigenmode] = FreeFem_Stability(baseflow,'m',1,'shift',0.021+1.771i,'nev',1);
- [baseflow,eigenmode]=FreeFem_Adapt(baseflow,eigenmode);  
- [baseflow,eigenmode]=FreeFem_Adapt(baseflow,eigenmode); 
- [baseflow,eigenmode]=FreeFem_Adapt(baseflow,eigenmode); 
-
-
[…]

### 2017-10-09 SOURCES_MATLAB/FreeFem_Init.m

@@ -1,45 +1,0 @@
-function baseflow = FreeFem_MeshInit(meshfile,problemtype)
-% Matlab/FreeFem driver for generating initial mesh and base flow
-%
-% usage : [baseflow,eigenmode] = FreeFem_Adapt(baseflow,eigenmode)
-%
-% with only one input argument the adaptation will be done only on base
-% flow.
-%
-% with two input arguments the adaptation will be done on base flow and
-% eigenmode structure.
-%
-%
-% Version 2.0 by D. Fabre ,  june 2017
-
-global ff ffdir ffdatadir sfdir verbosity
-
-[status,result]=system(['mkdir ' ffdatadir ]); 
-[status,result]=system(['mkdir ' ffdatadir '/CHBASE']); 
-[status,result]=system(['rm ' ffdatadir '/CHBASE/*']); 
-
-
-%[status,result]= system([ff,' ',ffdir,meshfile]);
-command = [ff,' ',meshfile];
-error = 'ERROR : Freefem not working (path may be wrong, change variable ff in script)';
-mysystem(command,error);
-
-%    if(status~=0) 
- %       result
- %       error('ERROR : Freefem not working (path may be wrong, change variable ff in script)');
- %       
- %   else
-  %      disp('FreeFem : initial mesh successfully created');
-  %  end
-   
-if(nargout==1)
-mesh = importFFmesh('mesh.msh');
-[status,result]=system(['cp mesh.msh ' ffdatadir '/CHBASE/mesh_init.msh']); 
-[status,result]=system(['cp chbase_guess.txt ' ffdatadir '/CHBASE/chbase_init.txt']); 
-mesh.namefile=[ ffdatadir '/CHBASE/mesh_init.msh'];
-baseflow=importFFdata(mesh,'chbase.ff2m');
-baseflow.namefile = [ ffdatadir '/CHBASE/chbase_init.txt'];
-disp(['      ### INITIAL MESH CREATED WITH np = ',num2str(mesh.np),' points']);
-
-end
-    

### 2017-10-09 SOURCES_MATLAB/SF_HarmonicBalance.m

@@ -24,7 +24,7 @@ elseif(meanflow.datatype=='MeanFlow')
     system(['cp ',ffdatadir, 'SelfConsistentMode.txt ',ffdatadir, 'SelfConsistentMode_guess.txt']);  
 
 else
-    error('ERROR to be fixed on next monday (hihihi... DAvid)'); 
+    error('wrong type of field for Harmonic balance'); 
 end
 
  if(p.Results.Lguess~=-1) 
@@ -48,6 +48,9 @@ disp(['#### SELF CONSISTENT CALCULATION COMPLETED with Re = ' num2str(p.Results.
 meanflow=importFFdata(meanflow.mesh,'MeanFlow.ff2m');
 mode=importFFdata(meanflow.mesh,'SelfConsistentMode.ff2m');
 
+if(meanflow.iter<0)
+    error('ERROR in SF_HarmonicBalance : Newton iteration did not converge')
+end
 
 disp(['#### omega =  ' num2str(imag(mode.lambda)) ]);
 %disp(['#### A =  ' num2str(mode.A) ]);

### 2017-10-09 SOURCES_MATLAB/SF_Spectrum_Exploration.m

@@ -88,7 +88,7 @@ for ind=1:length(EVr);
   xlabel('\sigma_i');ylabel('\sigma_r');
   title('Computed eigenvalues (click to see eigenmodes)')
   %%%%  plotting command for eigenmodes and callback function 
-  tt=['eigenmodeP= importFFdata(baseflow.mesh, ''' ffdatadir '/RUN' num2str(iRUN) '/Eigenmode' num2str(ind) '.ff2m''); ' ... 
+  tt=['eigenmodeP= importFFdata(baseflow.mesh, ''' ffdatadir 'RUN' num2str(iRUN) '/Eigenmode' num2str(ind) '.ff2m''); ' ... 
       'eigenmodeP.xlim = [-1 , 3]; eigenmodeP.plottitle =''Eigenmode for Re = ',num2str(Re),' , m = ',num2str(m), ...
       ', sigma = ', num2str(EVr(ind)) ' + 1i * ' num2str(EVi(ind)) ' '' ; '... 
       'plotFF(eigenmodeP,''ux1'',1); '  ];

### 2017-10-09 CYLINDER/SCRIPT_CYLINDER_DEMO.m
minor fix

@@ -166,7 +166,7 @@ plot(Re_Range,imag(lambda_branch)/(2*pi),'b+-');
 xlabel('Re');ylabel('St');
 box on; pos = get(gcf,'Position'); pos(4)=pos(3)*AspectRatio;set(gcf,'Position',pos); % resize aspect ratio
 set(gca,'FontSize', 18);
-%saveas(gca,'Cylinder_Strouhal_Re',figureformat);
+saveas(gca,'Cylinder_Strouhal_Re',figureformat);
 pause(0.1);
     
 figure(22);hold off;

### 2017-10-09 ARTICLE_STABFEM/ARTICLE_ASME.tex
minor fix

@@
 
+\usepackage{cprotect}
+
 \begin{document}
@@
 Specific analytical and numerical methods suited to the description have emerged in the second part of the 19th century and continuously evolved up to the present day.
-When the flow has no analytical expression, the stability problem requires a numerical resolution, and when there are at least two spatial variables, the class of methods suited to solve such problems are generally called "global stability approaches."\footnote{Sorry Laurette !}
+When the flow has no analytical expression, the stability problem requires a numerical resolution, and when there are at least two spatial variables, the class of methods suited to solve such problems are generally called "global stability approaches."%\footnote{Sorry Laurette !}
 
@@
 \item
-Secondly we offer an open-source and user-friendly software called  "StabFem" to perform such calculations. The software combines program written in both FreeFem++ and Matlab languages. 
+Secondly we offer an open-source and user-friendly software called  "StabFem"
+\cprotect\footnote{The StabFem software may be obtained at the following url : 
+\verb| https://github.com/erbafdavid/StabFem |} 
+to perform such calculations. The software combines program written in both FreeFem++ and Matlab languages. 
 FreeFem++ is used to generate and adapt the meshes and to solve the various linear problems arising in the analysis.
@@
 \normalsize
-\caption{Illustration of the computation of base-flow properties with StabFem (from script)}
+\caption{Illustration of the usage of the StabFem software to produce an adapted mesh and study the base flow and the linear stability properties of a cylinder
+(from script {\em SCRIPT\_CYLINDER\_DEMO.m})}
 \label{Listing2}
@@
 %\vspace{-.5cm}
-\includegraphics[width=.9 \linewidth]{Cylinder_BaseFlowReC.png}
+\includegraphics[width=.9 \linewidth]{Cylinder_BaseFlowRe60.png}
 %\vspace{-1.cm}
@@
 A second and smarter idea is to adapt the mesh to the base flow and the structural sensitivity.
-Since this quantity is directly linked to the sensitivity of the eigenvalues to perturbations of any kind (including spatial discretization errors), this procedure yields a lighter mesh while ensuring that the eigenvalue is effectively converged with respect to discretization errors.
-On the other hand, if one is interested to know the structure of the eigenmode (which may extend far away from the wavemaker region), it is more recommended to use mesh adaptation on the structure of the eigenmode.
+Results show that the two procedures yield the same values for the eigenvalues with less than $1\%$ error, but that the second method gives a mesh with about 3 times less grid points, leading to much faster computations (see appendix A).
+So, if one is interested only in the eigenvalues, for instance to plot growth rates as function of Reynolds or to identify the critical Reynolds number, mesh adaptation to the sensitivity gives the best option.
+On the other hand, if one is interested in the detailed structure of the eigenmode, which may extend far away from the wavemaker region, it is advised to use mesh adaptation on the eigenmode.
 
@@
 
+Definition of lift and drag operators :
+
+\be{drag}
+F_x ({\bf u},p) = 
+ \int_{\Gamma_w} \left[-p {\bf n} + \frac{2}{Re} {\bf D}({\bf u}) \cdot {\bf n} \right]   \cdot {\bf e_x} 
+\ee
+
+\be{lift}
+F_y ({\bf u},p) = 
+ \int_{\Gamma_w} \left[-p {\bf n} + \frac{2}{Re} {\bf D}({\bf u}) \cdot {\bf n} \right]   \cdot {\bf e_y} 
+\ee
+
 \paragraph{Mesh adaptation procedure}
 
-Lines 1-7 of the script.
+First we build an initial mesh (line 1), and compute base flow solutions for increasing values of the Reynolds number up to $Re = 60$ (lines 3-9).
+Then we perform the mesh adaptation with the structural sensitivity, as explained in a previously (line 13). 
+The resulting mesh is used for the rest of the computation presented in this paper (except for displaying the eigenmode in figure 4$a$). 
+Appendix A presents additional test regarding mesh convergence, and demonstrate that results obtained with the resulting mesh are trustable within $1\%$ accuracy for the eigenvalue, while requiring a very reasonable number of grid points compared to previous studies of this problem.
+
+%It is shown that as well as doing mesh adaptation with the eigenmode structure instead of the sensitivity, as discussed above, gives comparable results within $1\%$ as for the eigenvalue of the most amplified mode.
+
+%The produced outputs (lines 14-17) gives information about the resulting mesh. 
+%Note the values $h_{min}$ and $h_{max}$ of the smaller and larger edges, as well as the local grid size at four points A,B,C,D defined as $(x_A,y_A) = (0.5,0)$ (at the surface of the cylinder at the position of maximum shear), $(x_B,y_B) = (0.5,2.5)$ (at the location of the peak of structural sensitivity, see next section), $(x_C,y_C) = (0.,4)$ (in the near wake), and $(x_D,y_D) = (0.,10)$ (in the the far wake).
+Finally, the base flow is automatically recomputed on the resulting mesh (line 18-19).
+Finally, lines 21-22 plot the mesh and base flow structure, producing the result displayed in figure (\ref{fig:Baseflow}).
 
@@
 %\vspace{-.5cm}
-\includegraphics[width=.9 \linewidth]{Cylinder_EigenModeReC.png}
+\includegraphics[width=.9 \linewidth]{Cylinder_EigenModeRe60.png}
 %\vspace{-.5cm}
 %\vspace{-.5cm}
-\includegraphics[width=.9 \linewidth]{Cylinder_EigenModeAdjReC.png}
+\includegraphics[width=.9 \linewidth]{Cylinder_EigenModeAdjRe60.png}
 %\vspace{-.5cm}\vspace{-.5cm}
-\includegraphics[width=.9 \linewidth]{Cylinder_SensitivityReC.png}
+\includegraphics[width=.9 \linewidth]{Cylinder_SensitivityRe60.png}
 %\vspace{-.5cm}
@@
 \ee
-
-With $F_y ({\bf u_1}) = 
- \int_{\Gamma_w} \left[-p_1 {\bf n} + \frac{2}{Re} {\bf D}({\bf u_1}) \cdot {\bf n} \right]   \cdot {\bf e_y}  = 0.$
 
@@
 \end{center}
-\caption{Harmonic-balance results : mode characteristics}
+\caption{Harmonic-balance results : characteristics of the limit cycle.
+NOTE THAT THE AMPLITUDE IS NOTABLY LOWER THAN IN MANTIC-LUGO. TO BE EXPLAINED.
+}
 \label{fig:HB}
@@
 \end{center}
-\caption{SELF CONSISTENT APPROACH FOR THE WAKE OF A CYLINDER, $Re = 60$}
-\label{fig:SC60}
+\caption{SELF CONSISTENT APPROACH FOR THE WAKE OF A CYLINDER, $Re = 100$. NOTE THAT THE AMPLITUDE IS NOTABLY LOWER THAN IN MANTIC-LUGO. TO BE EXPLAINED.}
+\label{fig:SC100}
 \end{figure}
@@
 \paragraph{Illustration of mesh convergence procedure for a cylinder}
+
+\begin{figure}
+\includegraphics[width=.9 \linewidth]{Cylinder_Sigma_Re_TESTMESHES.png}
+\includegraphics[width=.9 \linewidth]{Cylinder_Strouhal_Re_TESTMESHES.png}
+\caption{Growth rate $\sigma$ $(a)$  and Strouhal number $St = (a \omega)/(2\pi U_0)$ ($b$) as function of Reynolds number FOR 8 DIFFERENT MESHES}
+\label{fig:MeshConvergence}
+\end{figure}
 
@@
 
-We illustrate the procedure in the case of a cylinder.  Figure 1 gives a retranscription of the sequence of commands (from {\em SCRIPT\_CYLINDER\_ADAPTMESH\_BASEFLOW}) 
-and the output produced.
-First we build an initial mesh (line 1), and compute base flow solutions for increasing values of the Reynolds number up to $Re = 60$ (lines 3-9).
+In this appendix we compare the results obtained with 8 different meshes, to demonstrate the efficency of the mesh adaptation process.
+The whole results can be obtained using the script {\em SCRIPT\_CYLINDER\_MESHCONVERGENCE.m} available in the StabFem repository.
 
-Then we perform the mesh adaptation (line 13). The produced outputs (lines 14-17) gives information about the resulting mesh. 
-Note the values $h_{min}$ and $h_{max}$ of the smaller and larger edges, as well as the local grid size at four points A,B,C,D defined as $(x_A,y_A) = (0.5,0)$ (at the surface of the cylinder at the position of maximum shear), $(x_B,y_B) = (0.5,2.5)$ (at the location of the peak of structural sensitivity, see next section), $(x_C,y_C) = (0.,4)$ (in the near wake), and $(x_D,y_D) = (0.,10)$ (in the the far wake).
-Finally, the base flow is automatically recomputed on the resulting mesh (line 18-19).
-Finally, lines 21-22 plot the mesh and base flow structure, producing the result displayed in figure (\ref{fig:Baseflow}).
+The Reference mesh is adapted to the Structural sensitivity, for $Re= 60$, with interpolation error 0.01, mesh dimensions $[-40,120]\times[0,40]$, and no-stress boundary conditions at the outlet and lateral boundaries.
 
-\begin{figure*}
-\small
-\begin{lstlisting}
-\end{lstlisting}
-\normalsize
+Figure \ref{fig:MeshConvergence} displays the results.
 
-\caption{Illustration of the procedure to adapt the mesh for stability calculations with StabFem (from script {\em SCRIPT\_CYLINDER.m}. }
-\label{listing3}
-\end{figure*}
+\begin{table}
+$$
+\begin{array}{c|c|c|c|c|c|c|}
+\mbox{ Mesh } & N_p & N_{d.o.f} & \mbox{ Dimensions } & h_{min} & h_{wall} & h_{wake} \\ 
+\mbox{ BaseFlow } & 1468 & 12856 \\
+\mbox{ Ref.} & 2055 & 18105\\
+\mbox{ Mode} &12308 & 109788 \\
+\mbox{ Err= }0.005 & 4355 & 38559 \\
+\mbox{Slip B.C.} & \\ 
+\mbox{Larger} & \\
+\mbox{Smaller} &  
+\end{array}
+$$
+\caption{Description of the 8 different meshes used in the convergence study}
+\end{table}
+
+%Figure 1 gives a retranscription of the sequence of commands (from {\em SCRIPT\_CYLINDER\_ADAPTMESH\_BASEFLOW}) 
+%and the output produced.
 

### 2017-10-09 ARTICLE_STABFEM/OLD/ARTICLE_ASME---copie---copie.tex
minor fix

--- 2017-10-06 ARTICLE_STABFEM/ARTICLE_ASME.tex
@@
 The base flow is then recomputed on the adapted mesh, providing a better approximation of the solution. The procedure can be repeated a few steps to ensure a right convergence.
-In our implementation, the whole process is performed using the Matlab driver
- {\em Freefem\_AdaptMesh.m}.
+
+The mesh generated in the previous way may not be optimal for the stability calculations as the structure of the eigenmode may be more complex than that of the base flow.
+To remedy with this, the idea is to subsequently adapt the mesh to both the mesh flow and the results of the stability calculation.
+This is easily done with FreeFem, as the  AdaptMesh procedure can be used with several objective functions.
+We have experimented two different ideas.
+The first is to adapt the mesh to the base flow and the structure of the leading eigenmode.
+A second and smarter idea is to adapt the mesh to the base flow and the structural sensitivity.
+Results show that the two procedures yield the same values for the eigenvalues with less than $1\percent$ error, but that the second method gives a mesh with about 3 times less grid points, leading to much faster computations (see appendix A).
+So, if one is interested only in the eigenvalues, for instance to plot growth rates as function of Reynolds or to identify the critical Reynolds number, mesh adaptation to the sensitivity gives the best option.
+On the other hand, if one is interested in the detailed structure of the eigenmode, which may extend far away from the wavemaker region, it is advied to use mesh adaptation on the eigenmode.
+
+In our implementation, the whole process is performed using the Matlab driver {\em Freefem\_AdaptMesh.m} ; the kind of adaptation 
+(to base flow only, to eigenmode, or to sensitivity) is decided by the choice of parameters transmitted to this function.
 
@@
 \begin{lstlisting}
-baseflow = SF_Init('Mesh_Cylinder_Large.edp');
-baseflow = SF_BaseFlow(baseflow,'Re',1);
-baseflow = SF_BaseFlow(baseflow,'Re',10);
-baseflow = SF_BaseFlow(baseflow,'Re',60);
-baseflow = SF_Adapt(baseflow,'Hmax',10,'InterpError',0.01);
-[ev,em] = SF_Stability(baseflow,'shift',0.04+0.74i,'type','S')
-baseflow = SF_Adapt(baseflow,em,'Hmax',10,'InterpError',0.01);
-plotFF(baseflow,'mesh'); plotFF(baseflow,'ux');
-
 Re_Range = [2 : 2: 50]; Drag_tab = []; Lx_tab = [];
@@
 
-\begin{figure}
-\includegraphics[width=.9 \linewidth]{Cylinder_Lx_baseflow.png}
-\includegraphics[width=.9 \linewidth]{Cylinder_Drag_baseflow.png}
-\caption{Recirculation length $L_x$ $(a)$  and drag $C_x$ ($b$) of the base flow over a cylinder as function of $Re$.}
-\label{fig:LxandDrag}
-\end{figure}
-
 \section{Illustration for the wake of a cylinder} 
 \vspace{.2cm}
-
-\paragraph{Problem description}
-
-We will now illustrate the applicati
-
-\paragraph{Mesh adaptation procedure}
 
@@
 
+\begin{figure}
+\includegraphics[width=.9 \linewidth]{Cylinder_Lx_baseflow.png}
+\includegraphics[width=.9 \linewidth]{Cylinder_Drag_baseflow.png}
+\caption{Recirculation length $L_x$ $(a)$  and drag $C_x$ ($b$) of the base flow over a cylinder as function of $Re$.}
+\label{fig:LxandDrag}
+\end{figure}
+
 %\clearpage
+
+\paragraph{Linear stability results}
 
@@
 
-\paragraph{Linear stability results}
-
 %popular class of method are {\em power methods} which allow to compute a limited set
@@
 
-%\clearpage
+\clearpage
 
@@
 
-\begin{figure*}
-\small
-\begin{lstlisting}
-> [ev,em] = SF_Stability(baseflow,'shift',0.04+0.76i,'nev',1,'type','D');
-> [baseflow,em]=SF_Adapt(baseflow,em,'Hmax',10,'InterpError',0.005);  
-      ### ADAPT mesh to base flow AND MODE   ; InterpError = 0.005  ; Hmax = 10
-      #   Number of points np = 13458 ; Ndof = 120030
-      #  deltamin, deltapax : 0.0089891 , 13.367
-      #  delta_(A,B,C,D) : 0.020536 , 0.082852 , 0.07316 , 0.11914
-      ### FUNCTION SF_BaseFlow : computing base flow for Re = 60
-      # Base flow converged in 4 iterations ; Drag = 0.64695; Lx = 4.0715
-      ### FUNCTION SF_Stability : computation of 1 eigenvalues/modes (DIRECT) with FF solver
-      # Stability calculation converged in 4 iterations, lambda = 0.047152+0.74808i.
-
-> [ev,em] = SF_Stability(baseflow,'shift',0.04+0.76i,'nev',1,'type','S');
-> [baseflow,em]=SF_Adapt(baseflow,em,'Hmax',10,'InterpError',0.005);
-      ### ADAPT mesh to base flow AND SENSITIVITY ; InterpError = 0.005  ; Hmax = 10
-      #   Number of points np = 4355 ; Ndof = 38559
-      #  deltamin, deltapax : 0.0058536 , 13.1164
-      #  delta_(A,B,C,D) : 0.01049 , 0.091861 , 0.13319 , 0.89372
-      ### FUNCTION SF_BaseFlow : computing base flow for Re = 60
-      # Base flow converged in 3 iterations ; Drag = 0.64758; Lx = 4.0725
-      ### FUNCTION SF_Stability : computation of 1 eigenvalues/modes (DIRECT) with FF solver
-      # Stability calculation converged in 3 iterations (D+A+S), lambda = 0.047165+0.74823i.
-
-\end{lstlisting}
-\normalsize
-
-\caption{Illustration of the procedure to adapt the mesh for stability calculations with StabFem (from script {\em SCRIPT\_CYLINDER.m}. }
-\end{figure*}
-
 We illustrate the procedure in the case of a cylinder.  Figure 1 gives a retranscription of the sequence of commands (from {\em SCRIPT\_CYLINDER\_ADAPTMESH\_BASEFLOW}) 
@@
 \section{Detail of the weak formulation}
-%The problem can be set into weak form by multiplying by multiplying Eq.
+The problem can be set into weak form by multiplying by multiplying Eq.
 \ref{Newton2} by a test function ${\bf v}$ and the associated divergence constraint by a test function $q$.

### 2017-10-09 ARTICLE_STABFEM/OLD/ARTICLE_ASME_5oct.tex
minor fix

--- 2017-10-09 ARTICLE_STABFEM/OLD/ARTICLE_ASME---copie---copie.tex
@@
 The base flow is then recomputed on the adapted mesh, providing a better approximation of the solution. The procedure can be repeated a few steps to ensure a right convergence.
-
-The mesh generated in the previous way may not be optimal for the stability calculations as the structure of the eigenmode may be more complex than that of the base flow.
-To remedy with this, the idea is to subsequently adapt the mesh to both the mesh flow and the results of the stability calculation.
-This is easily done with FreeFem, as the  AdaptMesh procedure can be used with several objective functions.
-We have experimented two different ideas.
-The first is to adapt the mesh to the base flow and the structure of the leading eigenmode.
-A second and smarter idea is to adapt the mesh to the base flow and the structural sensitivity.
-Results show that the two procedures yield the same values for the eigenvalues with less than $1\percent$ error, but that the second method gives a mesh with about 3 times less grid points, leading to much faster computations (see appendix A).
-So, if one is interested only in the eigenvalues, for instance to plot growth rates as function of Reynolds or to identify the critical Reynolds number, mesh adaptation to the sensitivity gives the best option.
-On the other hand, if one is interested in the detailed structure of the eigenmode, which may extend far away from the wavemaker region, it is advied to use mesh adaptation on the eigenmode.
-
-In our implementation, the whole process is performed using the Matlab driver {\em Freefem\_AdaptMesh.m} ; the kind of adaptation 
-(to base flow only, to eigenmode, or to sensitivity) is decided by the choice of parameters transmitted to this function.
+In our implementation, the whole process is performed using the Matlab driver
+ {\em Freefem\_AdaptMesh.m}.
 
@@
 \vspace{.2cm}
+
+\paragraph{Problem description}
+
+We will now illustrate the
+
+\paragraph{Mesh adaptation procedure}
 
@@
 \section{Detail of the weak formulation}
-The problem can be set into weak form by multiplying by multiplying Eq.
+%The problem can be set into weak form by multiplying by multiplying Eq.
 \ref{Newton2} by a test function ${\bf v}$ and the associated divergence constraint by a test function $q$.

### 2017-10-09 ARTICLE_STABFEM/OLD/ARTICLE_STABFEM.tex
minor fix

--- 2017-10-09 ARTICLE_STABFEM/OLD/ARTICLE_ASME---copie---copie.tex
@@
-%%%%%%%%%%%%%%%%%%%%%%%%%%% asme2ej.tex %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Template for producing ASME-format journal articles using LaTeX    %
-% Written by   Harry H. Cheng, Professor and Director                %
-%              Integration Engineering Laboratory                    %
-%              Department of Mechanical and Aeronautical Engineering %
-%              University of California                              %
-%              Davis, CA 95616                                       %
-%              Tel: (530) 752-5020 (office)                          %
-%                   (530) 752-1028 (lab)                             %
-%              Fax: (530) 752-4158                                   %
-%              Email: hhcheng@ucdavis.edu                            %
-%              WWW:   http://iel.ucdavis.edu/people/cheng.html       %
-%              May 7, 1994                                           %
-% Modified: February 16, 2001 by Harry H. Cheng                      %
-% Modified: January  01, 2003 by Geoffrey R. Shiflett                %
-% Use at your own risk, send complaints to /dev/null                 %
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\documentclass[review]{elsarticle}
+\documentclass{elsarticle}
 
-%%% use twocolumn and 10pt options with the asme2ej format
-\documentclass[twocolumn,10pt]{asme2ej}
+\usepackage{lineno,hyperref}
+\modulolinenumbers[5]
 
-\usepackage{epsfig} %% for loading postscript figures
+\journal{Computers \& Fluids}
+
+%%%%%%%%%%%%%%%%%%%%%%%
+%% Elsevier bibliography styles
+%%%%%%%%%%%%%%%%%%%%%%%
+%% To change the style, put a % in front of the second line of the current style and
+%% remove the % from the second line of the style you would like to use.
+%%%%%%%%%%%%%%%%%%%%%%%
+
+%% Numbered
+%\bibliographystyle{model1-num-names}
+
+%% Numbered without titles
+%\bibliographystyle{model1a-num-names}
+
+%% Harvard
+%\bibliographystyle{model2-names.bst}\biboptions{authoryear}
+
+%% Vancouver numbered
+%\usepackage{numcompress}\bibliographystyle{model3-num-names}
+
+%% Vancouver name/year
+%\usepackage{numcompress}\bibliographystyle{model4-names}\biboptions{authoryear}
+
+%% APA style
+%\bibliographystyle{model5-names}\biboptions{authoryear}
+
+%% AMA style
+%\usepackage{numcompress}\bibliographystyle{model6-num-names}
+
+%% `Elsevier LaTeX' style
+\bibliographystyle{elsarticle-num}
+%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-\newcommand{\bes}[1]{ \begin{equation} \label{#1}\begin{array}{rl}}
-\newcommand{\ees}{\end{array}\end{equation}}
+\begin{document}
 
-%% The class has several options
-%  onecolumn/twocolumn - format for one or two columns per page
-%  10pt/11pt/12pt - use 10, 11, or 12 point font
-%  oneside/twoside - format for oneside/twosided printing
-%  final/draft - format for final/draft copy
-%  cleanfoot - take out copyright info in footer leave page number
-%  cleanhead - take out the conference banner on the title page
-%  titlepage/notitlepage - put in titlepage or leave out titlepage
-%  
-%% The default is oneside, onecolumn, 10pt, final
+\begin{frontmatter}
 
-\title{Popularizing linear and nonlinear global approaches to hydrodynamic instabilities : 
-A review and a simple implementation for the wake of a cylinder}
+\title{Popularizing linear and nonlinear approaches to global flow instabilities : 
+A review and a simple implementation for the wake of a cylinder (and of a sphere ?)}%\tnoteref{mytitlenote}}
 
-%%% first author
-\author{D. Fabre$^{(a)}$ et al.%, P. Bonnefis$^{(a)}$
-    \affiliation{
-	IMFT, University of Toulouse
-    }	
-}
+%\tnotetext[mytitlenote]{Fully documented templates are available in the elsarticle package on \href{http://www.ctan.org/tex-archive/macros/latex/contrib/elsarticle}{CTAN}.}
 
-%%% second author
-%%% remove the following entry for single author papers
-%%% add more entries for additional authors
-%\author{V. Citro$^{(b)}$ \& F. Giannetti$^{(b)}$ \\
- %   \affiliation{ University of Salerno
-  %  }
-%}
+%% Group authors per affiliation:
+\author{D. Fabre$^{(a)}$, P. Bonnefis$^{(a)}$}
+\address[IMFT]{IMFT, University of Toulouse}
+\author{ V. Citro$^{(b)}$ \& F. Giannetti$^{(b)}$}
+\address[Salerno]{University of Salerno}
+%\fntext[myfootnote]{Since 1880.}
 
-\begin{document}
-\lstset{numbers=left, numberstyle=\small, numbersep=8pt, frame = single, language=Matlab, framexleftmargin=15pt}
+%% or include affiliations in footnotes:
+%\author[mymainaddress,mysecondaryaddress]{Elsevier Inc}
+%\ead[url]{www.elsevier.com}
 
-\maketitle
+%\author[mysecondaryaddress]{Global Customer Service\corref{mycorrespondingauthor}}
+%\cortext[mycorrespondingauthor]{Corresponding author}
+%\ead{support@elsevier.com}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\address[mymainaddress]{1600 John F Kennedy Boulevard, Philadelphia}
+%\address[mysecondaryaddress]{360 Park Avenue South, New York}
+
 \begin{abstract}
-{\it This is the abstract.
-This article illustrates preparation of ASME paper using 
-\LaTeX2\raisebox{-.3ex}{$\epsilon$}.
-An abstract for an ASME paper should be less than 150 words and is normally in italics.
-%%% 
-Please use this template to test how your figures will look on the printed journal page of the Journal of Mechanical Design.
-The Journal will no longer publish papers that contain errors in figure resolution.
-These usually consist of unreadable or fuzzy text, and pixilation or rasterization of lines.
-This template identifies the specifications used by JMD some of which may not be easily duplicated; for example, ASME actually uses Helvetica Condensed Bold, but this is not generally available so for the purpose of this exercise Helvetica is adequate.
-However, reproduction of the journal page is not the goal, instead this exercise is to verify the quality of your figures.
-Notice that this abstract is to be set in 9pt Times Italic, single spaced and right justified.
-}
+This template helps you to create a properly formatted \LaTeX\ manuscript.
 \end{abstract}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{keyword}
+Global instabilities, wake instabilities, finite elements
+%\texttt{elsarticle.cls}\sep \LaTeX\sep Elsevier \sep template
+%\MSC[2010] 00-01\sep  99-00
+\end{keyword}
+
+\end{frontmatter}
+
+\linenumbers
 
@@
 The objective of the present work is to contribute to the popularization of such methods 
-in two ways:
+in two ways.
 %for both research and education purposes.
-\begin{itemize}
-\item
+
 First, we give a concise but self-contained exposition of the main concepts and 
 specific numerical methods pertaining to global stability, including basic linear stability, adjoint-based sensitivity, as well as the most recent nonlinear developments.
-\item
+
 Secondly we offer an open-source and user-friendly software called  "StabFem" to perform such calculations. The software combines program written in both FreeFem++ and Matlab languages. 
@@
 Matlab is used as a driver to monitor the computations, perform the required loops over parameters, and plot the results.
-\end{itemize}
 
@@
 
-\section{Linear stability analysis : equations and methods}
-\vspace{.2cm}
+\section{Computing a base-flow with Newton iteration}
 
-\subsection{Computing a base-flow with Newton iteration}
-\vspace{.2cm}
+\paragraph{Governing equations}
 
-\paragraph{Navier-Stokes equations and weak form}
+Navier-Stokes equations :
 
-We start from the general problem of a flow field $[{\bf u},p]$ satisfying the incompressible Navier-Stokes equations on a domain $\Omega$,
 \be{NSprimitive}
-\partial_t {\bf u} = NS ({\bf u};p)
-\equiv - {\bf u} \cdot \nabla {\bf u} - \nabla p + \frac{2}{Re}  \nabla \cdot {\bf D}({\bf u})  \quad [\mbox{with} \nabla \cdot {\bf u} = 0].  \\
+\partial_t {\bf u} = {\cal NS} ({\bf u})
+\equiv {\bf u} \cdot \nabla {\bf u} - \nabla p + 2 \mu \nabla \cdot {\bf D}({\bf u}) 
+ \qquad \mbox{with the constraint } \nabla \cdot {\bf u} = 0.
 \ee
-with suitable boundary conditions on the frontier $\partial \Omega$ of the domain.
-Here $ {\bf D}({\bf u}) $ is the rate-of-strain tensor defined as
+
+$ {\bf D}({\bf u}) $ is the rate-of-strain tensor defined as
+
 $$
@@
 $$
-In the framework of finite element methods, it is convenient to write the equation in weak form.
-Prior to this we define a scalar product as follows, for either scalar or vectorial quantities 
-($\phi_1, \phi_2)$:
-$$
-\left< \phi_1, \phi_2 \right> = \int_\Omega \overline{\phi_1} \cdot \phi_2   \mbox{ d} \Omega
-$$
-The weak form of the Navier-Stokes equations is readily defined by introducing test functions 
-$[{\bf v},q]$ associated with the momentum and continuity equations, and integrating over the domain\footnote{In the simple presentation given here we have omitted the issue of boundary conditions.
-Details on way boundary conditions can be incorporated in the weak formulation through integration by parts can be found in the appendix.}
 
-\be{NSweak}
-\forall [{\bf v},q], \quad \partial_t \left< {\bf v}, {\bf u}\right> = \left< {\bf v} , NS ({\bf u};p) \right> + \left< q, \nabla \cdot {\bf u}\right>.
-\ee
-
-%Note that the notation $NS ({\bf u})$ is a shortcut as it is defined as an operator acting on the velocity field ${\bf u}$, not on the full flow field $({\bf u},p)$.
+Note that the notation ${\cal NS} ({\bf u})$ is a shortcut as it is defined as an operator acting on the velocity field ${\bf u}$, not on the full flow field $({\bf u},p)$.
 
@@
 %\subsection{Equations}
-%\paragraph{Base-flow equations}
+\paragraph{Base-flow equations}
+We look for a steady base-flow $({\bf u}_b;p_b)$ satisfying the Navier-Stokes equations :
+\be{NSb}
+{\cal NS} ({\bf u}_b) = 0
+\ee
 
@@
 
-We look for a steady base-flow $({\bf u}_b;p_b)$ satisfying the steady Navier-Stokes equations, i.e. 
-${\cal NS} ({\bf u}_b,p_b) = 0$.
-Suppose that we have a 'guess' for the base flow $[{\bf u}_b^g,p_b^g]$  which almost satisfies the equations.  We look for a better approximation under the form
+Suppose that we have a 'guess' for the base flow ${\bf u}_b^g$ which almost satisfies the equations.  We look for a better approximation under the form
 \be{Newton1}
-[{\bf u}_b,p_b]  = [{\bf u}_b^g,p_b^g] + [\delta {\bf u}_b, \delta p_b].
+{\bf u}_b = {\bf u}_b^g + \delta {\bf u}_b
 \ee
-Injecting into the Navier-Stokes equation in weak form (\ref{NSweak}) and developing up to linear terms in terms of the perturbation lead to  
-$NS ({\bf u}_b^g,p_b^g) + NSL_{{\bf u}_b^g}(\delta {\bf u}_b,\delta p_b)$, which can also be written in weak form :
-%\be
+
+Injecting into the equation and developing up to linear order in the perturbations leads to :
+%$$
 %{\cal C}( {\bf u}_b^g , \delta {\bf u}_b) -\nabla \delta p_b 
@@
 % \qquad \mbox{with} \nabla \delta {\bf u} = 0. 
-%\ee
-%Or equivalently, in weak form :
-\bes{Newton2}
-&\left< {\bf v}, NS ({\bf u}_b^g)\right> + \left<q, \nabla \cdot {\bf u}_b^g\right>  
+%$$
+
+\be{Newton2}
+{\cal NS} ({\bf u}_b^g) + {\cal NSL}_{{\bf u}_b^g}( \delta {\bf u}_b)  = 0
+\ee
+
+Where ${\cal NSL}$ is the linearised Navier-Stokes operator, defined by its action on a flow field $({\bf u} ; p)$ as follows :
+\be{defNSL}
+ {\cal NSL}_{{\bf U}}( {\bf u} ;  p) = {\cal C}( {\bf U} , {\bf u}) -\nabla p
++2 \nu \nabla  \cdot {\bf D}({\bf u}) \quad ( \mbox{ with } \nabla \cdot {\bf u } = 0 \, ).
+ \ee
+
+{\cal C} is the convection operator defined by 
+\be{defC}
+{\cal C}( {\bf U} , {\bf u}) = {\bf U} \cdot \nabla {\bf u} + {\bf u} \cdot \nabla {\bf U}
+\ee
+
+The problem can be set into weak form by multiplying by multiplying Eq.
+\ref{Newton2} by a test function ${\bf v}$ and the associated divergence constraint by a test function $q$.
+After a few integration by parts we are led to :
+\begin{eqnarray}
+\label{NewtonWeak}
+\forall ({\bf v};q), \quad
+\displaystyle &\int \left[ {\bf v} \cdot {\cal C}( {\bf u}_b^g , \delta {\bf u}_b) + \delta {\bf u}_b \cdot \nabla q - {\bf v} \cdot \nabla \delta p_b
++ 2 \mu {\bf D}(\delta {\bf u}_b) : {\bf D}(\delta {\bf v}) \right]
 \\
-+ &\left< { \bf v}, NSL_{{\bf u}_b^g}( \delta {\bf u}_b,\delta p_b) \right> + \left<q, \nabla \cdot \delta{\bf u}_b\right> = 0.
-\ees
-Where $NSL$ is the linearised Navier-Stokes operator, defined by its action on a flow field $({\bf u} ; p)$ as follows 
-\be{defNSL}
- NSL_{{\bf U}}( {\bf u} ;  p) = - {\cal C}( {\bf U} , {\bf u}) -\nabla p
-+\frac{2}{Re} \nabla  \cdot {\bf D}({\bf u}), %\quad ( \mbox{ with } \nabla \cdot {\bf u } = 0 \, ).
- \ee
-and {\cal C} is the convection operator defined by 
-\be{defC}
-{\cal C}( {\bf U} , {\bf u}) = \left( {\bf U} \cdot \nabla \right) {\bf u} + \left( {\bf u} \cdot \nabla \right)  {\bf U}.
-\ee
+\nonumber
+\displaystyle & + \int \left[ {\bf v} \cdot ( {\bf u}_b^g \cdot \nabla {\bf u}_b^g) 
++ {\bf u}_b^g \cdot \nabla q 
+- {\bf v} \cdot \nabla p_b^g
++ 2 \mu {\bf D}({\bf u}_b^g) : {\bf D}(\delta {\bf v}) \right] = 0 
+\end{eqnarray}
 
@@
 The procedure of Newton iteration is to solve iteratively this set of equations up to convergence.
+
 In our implementation, the algorithm is written in the Freefem++ solver {\em Newton\_2D.edp} 
@@
 
-\subsection{Linear stability}
-\vspace{.2cm}
-
-\paragraph{Direct eigenvalue problem}
-We consider the stability using the classical ansatz 
-\be{startmodepropre}
-{\bf u} = {\bf u}_b + \epsilon \hat{\bf u} e^{\lambda t} 
-\ee
-Where $\lambda = \sigma + i \omega$ is the eigenvalue, $\sigma$ the amplification rate,
-$\omega$ the oscillation rate, $\hat{{\bf u}}$ the eigenmode, and $\epsilon$ a small parameter.
-The eigenmodes is governed by the linear problem 
-$\lambda \hat{{\bf u}} = NSL_{{\bf u}_b}( \hat{\bf u},\hat{p})$, or, in weak form : 
-\be{eigenvalueproblem}
-\lambda \left< {\bf v} , \hat{{\bf u}} \right> = \left< {\bf v}, NSL_{{\bf u}_b} ( \hat{\bf u},\hat{p})\right> + \left< q, \nabla \cdot \hat{\bf u} \right>.
-\ee
-After discretization we end up with an eigenvalue problem with the matricial form
-\be{Eigen_matricial}
-\lambda B \hat{X} = A \hat{X}
-\ee
-Where $A$ is the matrix resulting from the discretization of $NSL_{{\bf u}_b}$, i.e.
-the very same matrix as appearing in the Newton computation of the base flow, and  $B$ is a 'weight' matrix associated to the scalar product $\left<v,u\right> = \int \overline{\bf v} \cdot {\bf u} \mbox{ d} \Omega$.
-
-\paragraph{Adjoint eigenvalue problem and structural sensitivity}
-Developed in the two past decades, the concept adjoint modes has now become an unavoidable complement to the linear global stability approach.
-We here give a short summary of the definition and usefulness of this concept.
-We can first define the {\em adjoint linearised Navier-Stokes operator} $NSL^\dag$ defined by the property:
-\bes{NSLAdj}
-\forall ( {\bf u}, p ; {\bf v}, q), & \left< NSL^\dag_{\bf U}( {\bf v},q) ,{\bf u}\right> + \left< \nabla \cdot {\bf v},p\right>  \\
-=& \left< {\bf v}, NSL_{\bf U} ({\bf u},p)\right> + \left< q, \nabla \cdot {\bf u}\right>.
-\ees
-We can then define the adjoint eigenmodes as the solutions to the eigenvalue problem 
-\be{EigenAdj} 
-\forall ( {\bf u}, p), \quad  \lambda^\dag \left< \hat{\bf v}, {\bf u}\right> =
- \left< NSL^\dag_{\bf U}( \hat{\bf v},\hat{q}) ,{\bf u}\right> + \left< \nabla \cdot \hat{\bf v},p\right>  
-\ee
-It can be shown (Schmid \& Henningson, 2001) that the adjoint eigenvalues $\lambda^\dag$ are the complex conjugates of the direct eigenvalues ($\lambda$).
-
-Although the concept of adjoint operator may sound complicate, the resolution of the adjoint problem using finite elements methods is actually extremely easy.
-In effect, the scalar product used in the definition of the weak formulation and that appearing in the definition of adjoint being the same, the weak formulations of both problems are thus identical when exchanging the test functions and the unknown functions.
-Thus the matricial form of the discretized version of (\ref{EigenAdj} is deduced from the one of the direct problem by a simple transpose of the matrix :
-\be{Eigen_Adj_matricial}
-\overline{\lambda}^\dag B \hat{X}\dag = A^T \hat{X}\dag.
-\ee
-
-Adjoint eigenmodes are a powerful tool for investigating problems such as transient growth, control, sensitivity (see the reviews of Chomaz, Schmid, Luchini).
-The simplest physical interpretation of an adjoint eigenmode is as follows : it corresponds to the initial condition which has maximum projection along the direction of the corresponding eigenmode.
-Thus, the adjoint of the most amplified mode corresponds to the optimal perturbation which will maximize the growth of energy in the limit of large time.
-In effect, one can prove that for $t \rightarrow \infty$  the asymptotic behaviour of a solution with initial condition ${\bf u}_i$  is given as :
-$$
-{\bf u}(t) \approx 
-\frac{ \left< \hat{\bf u}^\dag, {\bf u}_i\right>}{\left<\hat{\bf u}^\dag, \hat{\bf u}\right>} 
-e^{\lambda t} \hat{\bf u}  
-$$.
-The choice ${\bf u}_i = \hat{\bf u}^\dag$ is the initial condition of norm unity which maximizes the first factor in this expression.
-%\item
-
-The adjoint eigenmode also allows to deduce a quantity called the {\em structural sensitivity}  and defined as $S(x,y) = || \hat{\bf u}^\dag||  ||\hat{\bf u}||$ which has became popular in the recent years.
-%is called the structural sensitivity of the eigenmode. 
-This quantity is a direct and practical measure of the effect of perturbations of the linear operator on the eigenvalue.
-The region of the flow where $S(x,y)$ is thus the region where the instability mechanism originates, and is often referred to as the {\em wavemaker region}
-
-%\end{itemize}
-
-\paragraph{Iterative methods for eigenvalue computations}
-
-When it comes to the numerical resolution of generalized eigenvalue problems such as $A X = \lambda B X$ (or its adjoint version), several methods are possible.
-Direct methods to compute the whole spectrum are both costly prohibitive and useless.
-A popular alternative is iterative methods which allow to compute a limited set of eigenvalues located in the vicinity of a
-"shift" value $\lambda_{shift}$. The simplest version of this method is the simple shift-invert iteration, which consists of solving iteratively the system
-$$
-X^{n} =  (A- \lambda_{shift} B)^{-1} B X^{n-1}
-$$ 
-It is easy to show that this quickly asymptotes to $X^{n+1} \approx ({\lambda^*}^{-1})^n \hat{X}$
-where $\hat{X}$ is the eigenmode with largest ${\lambda^*}^{-1}$ (i.e. the one with eigenvalue $\lambda$ closest to the shift).
-
-When one has a good estimation of the eigenvalue, this method converges very rapidly and is very efficient, but it can only provide a single eigenvalue.
-If one wants to compute a larger number of eigenvalues, one can revert to a generalized version of iterative methods, called Arnoldi methods.
-The shift-invert version of the Arnoldi method is in fact the most commonly  used method of the current time and is at the basis of both the popular matlab solver eigs and the build-in eigenvalue solver of FreeFem.
-Our implementation in StabFem allows to chose between single eigenvalue computation (power method) and multiple eigenvalue computation (Arnoldi).
-The selection is made according to the parameter "nev" transmitted to the driver.
-
-\subsection{Mesh adaptation procedure}
-\vspace{.2cm}
+\paragraph{Mesh adaptation procedure}
 
@@
 The finite element method allows to use unstructured mesh and hence to locally adapt the refinement.
-%Following Sipp \& Lebedev,
-The most common procedure is to decompose the domain into several parts with different grid densities ; for instance for the wake of a cylinder, we will design a near-wall region with very small  size, a "wake" region with intermediate mesh size, and an outer region with large mesh size.
+Following Sipp & Lebedev, the usual procedure is to decompose the domain into several parts with different grid densities ; for instance for the wake of a cylinder, we will design a near-wall region with very small  size, a "wake" region with intermediate mesh size, and an outer region with large mesh size.
 The inconvenient is that the design relies on an a priori expectation of the regions where gradients will be large.
 
-In our implementation, we used an automatic mesh adaptation method. %which provides an optimal mesh adapted to the structure of the flow. 
-The implementation relies on the AdaptMesh procedure of the FreeFem++ software. This procedure is detailed in detail in ref. []. In short, 
+In our implementation, we used an automatic mesh adaptation procedure which provides an optimal mesh adapted to the structure of the flow.
+The implementation relies on the AdaptMesh procedure of the FreeFem++ software.
+This procedure is detailed in detail in ref.
+[].
+In short,
 the classical Delaunay-Voronoi algorithm produces a mesh with gridpoint distribution specified by a {\em Metric } matrix $\cal M$.
@@
 The base flow is then recomputed on the adapted mesh, providing a better approximation of the solution. The procedure can be repeated a few steps to ensure a right convergence.
+In our implementation, the whole process is performed using the Matlab driver
+ {\em Freefem\_AdaptMesh.m}.
 
-The mesh generated in the previous way may not be optimal for the stability calculations as the structure of the eigenmode may be more complex than that of the base flow.
-To remedy with this, the idea is to subsequently adapt the mesh to both the mesh flow and the results of the stability calculation.
-This is easily done with FreeFem, as the  AdaptMesh procedure can be used with several objective functions.
-We have experimented two different ideas.
-The first is to adapt the mesh to the base flow and the structure of the leading eigenmode.
-A second and smarter idea is to adapt the mesh to the base flow and the structural sensitivity.
-Results show that the two procedures yield the same values for the eigenvalues with less than $1\percent$ error, but that the second method gives a mesh with about 3 times less grid points, leading to much faster computations (see appendix A).
-So, if one is interested only in the eigenvalues, for instance to plot growth rates as function of Reynolds or to identify the critical Reynolds number, mesh adaptation to the sensitivity gives the best option.
-On the other hand, if one is interested in the detailed structure of the eigenmode, which may extend far away from the wavemaker region, it is advied to use mesh adaptation on the eigenmode.
+\paragraph{Example for the cylinder}
 
-In our implementation, the whole process is performed using the Matlab driver {\em Freefem\_AdaptMesh.m} ; the kind of adaptation 
-(to base flow only, to eigenmode, or to sensitivity) is decided by the choice of parameters transmitted to this function.
+We illustrate the procedure in the case of a cylinder (see program {\em SCRIPT\_CYLINDER\_ADAPTMESH\_BASEFLOW})
 
-\begin{figure*}[t]
+First we build an initial mesh, and compute base flow solutions for increasing values of the Reynolds number up to $Re = 60$ :
+
 \small
 \begin{lstlisting}
-Re_Range = [2 : 2: 50]; Drag_tab = []; Lx_tab = [];
-    for Re = Re_Range
-        baseflow = SF_BaseFlow(baseflow,'Re',Re);
-        Drag_tab = [Drag_tab,baseflow.Drag];
-        Lx_tab = [Lx_tab,baseflow.Lx];
-    end
-plot(Re_Range,2*Drag_tab,'b+-');
-plot(Re_Range,Lx_tab,'b+-');
+> baseflow=FreeFem_Init('Mesh_Cylinder_Large.edp');
+      ### INITIAL MESH CREATED WITH np = 2207 points
+> baseflow=FreeFem_BaseFlow(baseflow,'Re',1);
+      ### FUNCTION FreeFem_BaseFlow : computing base flow for Re = 1
+      # Base flow converged in 6 iterations ; Drag = 5.9876; Lx = 0.501
+> baseflow=FreeFem_BaseFlow(baseflow,'Re',10);
+      ### FUNCTION FreeFem_BaseFlow : computing base flow for Re = 10
+      # Base flow f converged in 5 iterations ; Drag = 1.4519; Lx = 0.73191
+> baseflow=FreeFem_BaseFlow(baseflow,'Re',60);
+      ### FUNCTION FreeFem_BaseFlow : computing base flow for Re = 60
+      # Base flow converged in 6 iterations ; Drag = 0.66348; Lx = 3.6989
+\end{lstlisting}
+\normal
 
-Re_Range = [40 : 2: 100];lambda_branch=[];
-baseflow=SF_BaseFlow(baseflow,'Re',40);
-[ev,em] = SF_Stability(baseflow,'shift',-.03+.72i,'nev',1,'type','D');
-    for Re = Re_Range
-        baseflow = SF_BaseFlow(baseflow,'Re',Re);
-        [ev,em] = SF_Stability(baseflow,'nev',1,'shift','cont');
-        lambda_branch = [lambda_branch ev];
-    end
-plot(Re_Range,real(lambda_branch),'b+-');
-plot(Re_Range,imag(lambda_branch)/(2*pi),'b+-');
+Then we perform the mesh adaptation.
+The following listing shows the output of the software.
+Note the values $h_{min}$ and $h_{max}$ of the smaller and larger edges, as well as the local grid size at four points A,B,C,D defined as $(x_A,y_A) = (0.5,0)$ (at the surface of the cylinder at the position of maximum shear), $(x_B,y_B) = (0.5,2.5)$ (at the location of the peak of structural sensitivity, see next section), $(x_C,y_C) = (0.,4)$ (in the near wake), and $(x_D,y_D) = (0.,10)$ (in the the far wake).
+
+\small
+\begin{lstlisting}
+> baseflow=FreeFem_Adapt(baseflow,'Hmax',10,'InterpError',0.005);
+
+     ### ADAPT mesh to base flow ; InterpError = 0.01  ; Hmax = 10
+      #   Number of points np = 1352 ; Ndof = 11862
+      #  h_min, h_max : 0.018824 , 10.2895
+      #  h_(A,B,C,D) : 0.027467 , 0.28644 , 0.45948 , 0.89245
+      ### FUNCTION FreeFem_BaseFlow : computing base flow for Re = 60
+      # Base flow converged in 5 iterations ; Drag = 0.65805; Lx = 4.0737
 \end{lstlisting}
 \normalsize
-\caption{Illustration of the computation of base-flow properties with StabFem (from script)}
-\label{Listing2}
-\end{figure*}
+
+The resulting mesh and base flow are plotted on figure 1.
 
 \begin{figure}
-%\vspace{-.5cm}
-\includegraphics[width=.9 \linewidth]{Cylinder_Mesh.png}
-%\vspace{-.5cm}
-%\vspace{-.5cm}
-\includegraphics[width=.9 \linewidth]{Cylinder_BaseFlowReC.png}
-%\vspace{-1.cm}
+\includegraphics[width=.48 \linewidth]{Cylinder_Mesh.pdf}
+\includegraphics[width=.48 \linewidth]{Cylinder_BaseFlowReC.pdf}
 \caption{Adapted mesh $(a)$  and base flow (axial velocity component) ($b$) for the flow over a cylinder at $Re=Re_c = 46.7$.}
@@
 
-\section{Illustration for the wake of a cylinder} 
-\vspace{.2cm}
-
-\paragraph{Base flow}
-
-Having thus produced an convenient mesh, we can now illustrate the properties of the base flow as function of Reynolds number.
-Figure (\ref{Listing2}) shows how to compute and plot with StabFem the two most commonly studied quantities, namely the drag coefficient $C_x(Re)$  and the recirculation length $Lx(Re)$, namely the location of the stagnation point at the rear of the recirculation region.
-Note that the object \verb|baseflow| is defined as a structure with fields \verb|Drag| and \verb|Lx|. 
-The resulting plots are given in figure (\ref{fig:LxandDrag}), and are in good agreement with known results for this classical problem.
-In particular, for low Reynolds, the recirculation $L_x(Re)$ is equal to $0.5$ (which is the radius of the cylinder) indicating the absence of a recirculation region.
-The latter appears for $Re > 4.8$, in accordance with known results.
+\paragraph{Base flow characteristics}
 
@@
 \begin{figure}
-\includegraphics[width=.9 \linewidth]{Cylinder_Lx_baseflow.png}
-\includegraphics[width=.9 \linewidth]{Cylinder_Drag_baseflow.png}
-\caption{Recirculation length $L_x$ $(a)$  and drag $C_x$ ($b$) of the base flow over a cylinder as function of $Re$.}
+\includegraphics[width=.48 \linewidth]{Cylinder_Lx_baseflow.pdf}
+\includegraphics[width=.48 \linewidth]{Cylinder_Drag_baseflow.pdf}
+\caption{Recirculation length $L_x$ $(a)$  and drag $C_x$ ($b$) of the base flow over a cylinder at $Re=Re_c = 46.7$.}
 \label{fig:LxandDrag}
@@
 
-%\clearpage
+\clearpage
 
-\paragraph{Linear stability results}
+\section{Computing an eigenmode with a shift-invert method}
 
-%We now review the main concepts of linear stability approach and explain how such calculations are implemented in our software.
+We consider the stability using the classical ansatz
+
+${\bf u} = {\bf u}_b + \hat{{\bf u}} e^{\lambda t}$
+
+Where $\lambda = \sigma + i \omega$ is the eigenvalue, $\sigma$ the amplification rate,
+$\omega$ the oscillation rate, $\hat{{\bf u}}$ the eigenmode.
+
+The eigenmode is governed by the linear problem
+
+After discretization we end up
+
+\paragraph{Stability equations}
+
+Eigenvalue problem
+
+Adjoint eigenvalue problem
+
+Sensitivity
+
+\paragraph{Iterative methods}
+
+These de Andrea Fani
+
+\paragraph{Implementation}
+
+Matlab driver...
+
+\subsection{Results}
 
 \begin{figure}
-%\vspace{-.5cm}
-\includegraphics[width=.9 \linewidth]{Cylinder_EigenModeReC.png}
-%\vspace{-.5cm}
-%\vspace{-.5cm}
-\includegraphics[width=.9 \linewidth]{Cylinder_EigenModeAdjReC.png}
-%\vspace{-.5cm}\vspace{-.5cm}
-\includegraphics[width=.9 \linewidth]{Cylinder_SensitivityReC.png}
-%\vspace{-.5cm}
-\caption{Eigenmode $(a)$  (axial velocity component),  Adjoint mode $(b)$ and structural sensitivity ($c$) for the cylinder's wake at $Re=Re_c = 46.7$.}
+\includegraphics[width=.48 \linewidth]{Cylinder_EigenModeReC.pdf}
+\includegraphics[width=.48 \linewidth]{Cylinder_EigenModeAdjReC.pdf}
+\includegraphics[width=.48 \linewidth]{Cylinder_SensitivityReC.pdf}
+\caption{Eigenmode $(a)$  (axial velocity component),  Adjoint eigenmode $(b)$ and structural sensitivity ($c$) for the cylinder's wake at $Re=Re_c = 46.7$.}
 \label{fig:Eigenmode}
@@
 \begin{figure}
-\includegraphics[width=.9 \linewidth]{Cylinder_Sigma_Re.png}
-\includegraphics[width=.9 \linewidth]{Cylinder_Strouhal_Re.png}
+\includegraphics[width=.48 \linewidth]{Cylinder_Sigma_Re.pdf}
+\includegraphics[width=.48 \linewidth]{Cylinder_Omega_Re.pdf}
 \caption{Growth rate $\sigma$ $(a)$  and Strouhal number $St = (a \omega)/(2\pi U_0)$ ($b$) as function of Reynolds number}
@@
 
-%\begin{figure*}
-%\small
-%\begin{lstlisting}
-%\end{lstlisting}
-%\normalsize
-%\caption{Illustration of the procedure to compute stability properties and adapt the mesh using StabFem (from script {\em SCRIPT\_CYLINDER.m}. }
-%\label{listing4}
-%\end{figure*}
+\subsection{Application}
 
-%popular class of method are {\em power methods} which allow to compute a limited set
-
-%based on the idea that the repeated application of an operator mostly amplifies the perturbations along the eigenspaces with largest eigenvalues.
-
-%These de Andrea Fani
-
-%\paragraph{Implementation and mesh adaptation for stability calculations}
-
-Matlab driver...
-
-%\paragraph{Sample results}
-
-%\subsection{Illustration of the mesh adaptation for stability calculations}
-
-%See listing....
-
-%\subsection{Sample results for a cylinder}
-
-\clearpage
-
-\section{Nonlinear global stability approaches}
-\vspace{.2cm}
-%\section{Computing the limit cycle for $Re>Re_c$ with Harmonic Balance}
-
-\paragraph{Review on nonlinear global stability approaches}
-%For $Re\right>Re_c$, the linear stability analysis based on the {\em base flow} does not allow to predict the properties of the limit cycle; in particular the Strouhal number is substantially underestimated.
-%It has been shown that investigating the stability properties of the {\em mean flow} obtained by averaging time-marching solution gives a better accordance.
-Attempts to on a rigourous basis
-In the past decade, efforts have been devoted to extend the range of validity of global approaches into the nonlinear régime for $Re>Re_c$, with the double objective to describe the properties of the limit cycle reached after saturation and to derive amplitude equations describing the transitent dynamics towards this cycle.
- The first milestone in that direction is the work of Sipp \& Lebedev who used a weakly nonlinear development in terms of the distance to the threshold $Re-Re_c$.
-However, although derived on rigorous grounds, the weakly nonlinear development has a very limited range of validity and already fails for $Re\ge47$.
-More recently,  Mantic-lugo et al.  proposed an alternative approach termed {\em Self-consistent model} which succeeds in predicting the dynamics up to $Re =120$ and more. 
-This model was build as a linear stability approach build on a {\em mean flow} which includes a 
-retroaction of the eigenmode. However, if one is interested in the limit cycle and not the transient,
-the approach is actually equivalent to a Fourier series decomposition of the flow with respect to time (an approach also known as {\em harmonic balance}) retaining only the two first terms. 
-%The approach is based on a generalisation of the eigenmode ansatz \ref{} and
-
-In the next section we thus present this model and propose a direct resolution method. The relation with the initial method of Mantic-Lugo et al. will be discussed afterwards.
-
-\paragraph{Harmonic balance : equations and procedure }
-
-In this section, to simplify the notations, The Navier-Stokes equations will be written symbolically as 
-$\partial_t  {\bf u }  = NS(  {\bf u } )$, therefore droping the systematic reference of the incompressibility constraint and associated pressure field.
-
-We thus start with a Fourier decomposition of the limit cycle under the form :
-\be{HB}
-{\bf u } = {\bf u }_0 + {\bf u }_1 e^{i \omega t} +   {\bf u }_{-1} e^{-i \omega t}
-\ee  
-Here ${\bf u }_0$ is the mean flow (averaged over time),  ${\bf u }_1$ is the mode
-(fourrier component at the fundamental frequency), ${\bf u }_{-1} = \overline{{\bf u }_1}$ is its complex conjugate, and $\omega$ is the (real) oscillation frequency of the limit cycle (which is not known a priori).
-Injecting this ansartz into the Navier-Stokes equations and taking the mean value and first Fourier component leads to the following coupled equations :
-\be{HBEq0}
-NS(  {\bf u }_0 ) - {\cal C}( {\bf u }_1, \overline{\bf u }_1) = 0,
-\ee
-\be{HBEq1}
-i \omega {\bf u }_1 =  NSL_{{\bf u }_0}(  {\bf u }_1 ).
-\ee
-
-Note that the Fourier description of the limit cycle is invariant with respect to the phase $\phi$ (i.e.
-the equations are unchanged when replacing $[ {\bf u }_1,  {\bf u }_{-1}] $ by  $[ {\bf u }_1 e^{i\varphi},  {\bf u }_{-1}  e^{-i\varphi}] $.
-To allow resolution we thus need an extra equation to fix this phase.
-Several choices are possible, but a convenient one is to set the lift associated with the imaginary part of ${\bf u }_1$ to lift.
-Physically, this means that the instant $t=0$ will correspond to a maximum of lift.
-This condition reads :
-\be{HBphase}
-\Im F_y({\bf u}_1) =0
-\ee
-
-With $F_y ({\bf u_1}) = 
- \int_{\Gamma_w} \left[-p_1 {\bf n} + \frac{2}{Re} {\bf D}({\bf u_1}) \cdot {\bf n} \right]   \cdot {\bf e_y}  = 0.$
-
-Mathematically, the problem $\ref{HBEq0,HBEq1,HBphase}$ for the unknown $[{\bf u }_0, {\bf u }_{1}, \omega]$ is well posed, and can be solved using a Newton iteration just as explained for the base flow in section 2.
-To allow resolution, we separate the mode into real and imaginary part, by writing ${\bf u }_1 = {\bf u }_{1,r} +  i {\bf u }_{1,i} $.
-We then assume that we know a 'guess' 
-$$
-[{\bf u }_0, {\bf u }_{1,r}, {\bf u }_{1,i}, \omega] = 
- [{\bf u }_0^g, {\bf u }_{1,r}^g, {\bf u }_{1,i}^g, \omega^g]
-+ [\delta {\bf u }_0, \delta {\bf u }_{1,r}, \delta {\bf u }_{1,i}, \delta \omega]
-$$.
-
-Injecting and developing up to linear order leads to the following 
-\begin{equation}
-\begin{array}{ll}
-\displaystyle
-& NS(  {\bf u }_0^g ) - [ {\cal C}( {\bf u }_{1,r}^g,{\bf u }_{1,r}^g) +  {\cal C}( {\bf u }_{1,i}^g,{\bf u }_{1,i}^g) ]
-\\
-+& NSL_{{\bf u }_0^g}(\delta {\bf u }_0) - 2 [ {\cal C}( {\bf u }_{1,r}^g,\delta {\bf u }_{1,r}) +  {\cal C}( {\bf u }_{1,i}^g,\delta {\bf u }_{1,i}) ] = 0;
-\\
-\\
-&  NSL_{{\bf u }_0^g}( {\bf u }_{1,r}^g) - \omega^g {\bf u }_{1,i}^g 
- \\
-  +& NSL_{{\bf u }_0^g}( \delta {\bf u }_{1,r}^g) 
-   -  {\cal C}( \delta {\bf u }_{0}^g, {\bf u }_{1,r})
-   - \delta \omega^g \delta {\bf u }_{1,i}^g 
- - \omega^g \delta {\bf u }_{1,r} = 0 ;
- \\
-\\
-&  NSL_{{\bf u }_0^g}({\bf u }_{1,i}^g) + \omega^g {\bf u }_{1,i}^g
- \\
-  +& NSL_{{\bf u }_0^g}( \delta {\bf u }_{1,i}^g) 
-  -  {\cal C}( \delta {\bf u }_{0}^g, {\bf u }_{1,i}) 
-  + \delta \omega^g \delta {\bf u }_{1,i}^g 
-+ \omega^g \delta {\bf u }_{1,r} = 0 ;
-\\
-\\
-& F_y({\bf u }_{1,i}^g) + F_y(\delta {\bf u }_{1,i}) = 0.
- \end{array}
-\end{equation}
-
-After discretization, this leads to a linear problem with the form $A X = Y$ where $X$ is the discretized version of the unknowns  $[\delta {\bf u }_0, \delta {\bf u }_{1,r}, \delta {\bf u }_{1,i}, \delta \omega]$, and $A$ is a matrix of dimension $3 N_{dof} +1$.
-
-%\ref{HBEq0,HBEq1,HBphase}
-
-\paragraph{Results for the wake of a cylinder}
-
-\paragraph{Link with the Self-Consistent approach}
-
-We now discuss the link between the harmonic balance approach presented above and the self-consistent approach as introduced by Mantic-Lugo et al.
-The starting point of this model is a pseudo-eigenmode expansion of the flow as follows :
-
-\be{SC}
-{\bf u } = {\bf u }_m + A \left[ \tilde{{\bf u }}_1 e^{\sigma_{SC} t + i \omega_{SC} t} +   \tilde{\bf u }_{-1} e^{\sigma_{SC} t  -i \omega_{SC} t} \right]
-\ee  
-Where ${\bf u }_m$ is a {\em mean flow} defined by phase-averaging over the cycle, $\tilde{{\bf u }}_1$ is a pseudo-eigenvector which is normalized by the condition  $||\tilde{{\bf u }}_1|| = 1/\sqrt{2}$,
- $A$ is an amplitude parameter directly related to the energy of the oscillating flow, and $\lambda = \sigma_{SC} + i \omega_{SC}$ is a pseudo-eigenvalue which depends upon the parameter $A$.
-The mean flow is then governed by the same equation
-(\ref{HBEq0}) written above, while $\tilde{{\bf u }}_1$ is the solution of an eigenvalue problem with the same form as  (\ref{HBEq1}) except that $i \omega$ is replaced by $\sigma_{SC} + i \omega_{SC}$.
-The self-consistent model has the following properties :
-\begin{itemize}
-\item[-] For $A \ll 1$ it is equivalent to the linear eigenvalue problem (\ref{LEP}), and the generalized eigenvalue coincides with the one predicted by linear stability : $\sigma_{SC} + i \omega_{SC} = \sigma_{lin} + i \omega_{lin}$.
-\item[-] For $\sigma_{SC}=0$ (corresponding to a specific choice of the amplitude $A=A_c$),  the expansion (\ref{SC}) is equivalent to the harmonic-balance decomposition (\ref{HB})
-\item[-] For $0<A<A_c$, the resolution leads to a relation $\sigma_{SC}(A) ; \omega_{SC}(A)$
-such that $0< \sigma_{SC}(A) < \sigma_{lin}$.
- Although in this case the expansion \ref{SC} cannot represent the flow for all $t$, Mantic-Lugo et al.
-argued that the relation between $\sigma_{SC}$ and $A$ can be used to build an amplitude equation which captures the transient approach to the limit cycle.
-\end{itemize}
-
-%Barkley [] and Leontini [] have
+\section{Computing the limit cycle for $Re>Re_c$ with Harmonic Balance}
 
@@
 \begin{center}
-\includegraphics[width=.9 \linewidth]{Cylinder_Lx_Re_HB.png}
-\includegraphics[width=.9 \linewidth]{Cylinder_Drag_Re_HB.png}
+\includegraphics[width=.48 \linewidth]{Cylinder_Lx_Re_SC.pdf}
+\includegraphics[width=.48 \linewidth]{Cylinder_Drag_Re_SC.pdf}
+\includegraphics[width=.48 \linewidth]{Cylinder_Omega_Re_SC.pdf}
+\includegraphics[width=.48 \linewidth]{Cylinder_Lift_Re_SC.pdf}
+\includegraphics[width=.48 \linewidth]{Cylinder_Energy_Re_SC.pdf}
 \end{center}
-\caption{Harmonic-balance results : mean-flow characteristics}
+\caption{HARMONIC BALANCE APPROACH FOR THE WAKE OF A CYLINDER}
 \label{fig:HB}
@@
 \begin{center}
-\includegraphics[width=.9 \linewidth]{Cylinder_Strouhal_Re_HB.png}
-\includegraphics[width=.9 \linewidth]{Cylinder_Lift_Re_SC.png}
-\includegraphics[width=.9 \linewidth]{Cylinder_Energy_Re_SC.png}
-\end{center}
-\caption{Harmonic-balance results : mode characteristics}
-\label{fig:HB}
-\end{figure}
-
-\begin{figure}
-\begin{center}
-\includegraphics[width=.9 \linewidth]{Cylinder_SC100_EnergySigma.png}
-\includegraphics[width=.9 \linewidth]{Cylinder_SC100_LiftSigma.png}
+\includegraphics[width=.48 \linewidth]{Cylinder_SC60_EnergySigma.pdf}
+\includegraphics[width=.48 \linewidth]{Cylinder_SC60_LiftSigma.pdf}
 \end{center}
@@
 
-\paragraph{Illustration of mesh convergence procedure for a cylinder}
+\end{document}
 
-\begin{figure*}
-\small
-\begin{lstlisting}
-> baseflow=SF_Init('Mesh_Cylinder_Large.edp');
-      ### INITIAL MESH CREATED WITH np = 2207 points
-> baseflow=SF_BaseFlow(baseflow,'Re',1);
-      ### FUNCTION SF_BaseFlow : computing base flow for Re = 1
-      # Base flow converged in 6 iterations ; Drag = 5.9876; Lx = 0.501
-> baseflow=SF_BaseFlow(baseflow,'Re',10);
-      ### FUNCTION SF_BaseFlow : computing base flow for Re = 10
-      # Base flow f converged in 5 iterations ; Drag = 1.4519; Lx = 0.73191
-> baseflow=SF_BaseFlow(baseflow,'Re',60);
-      ### FUNCTION SF_BaseFlow : computing base flow for Re = 60
-      # Base flow converged in 6 iterations ; Drag = 0.66348; Lx = 3.6989
+\paragraph{Installation} If the document class \emph{elsarticle} is not available on your computer, you can download and install the system package \emph{texlive-publishers} (Linux) or install the \LaTeX\ package \emph{elsarticle} using the package manager of your \TeX\ installation, which is typically \TeX\ Live or Mik\TeX.
 
-> baseflow=SF_Adapt(baseflow,'Hmax',10,'InterpError',0.01);
-     ### ADAPT mesh to base flow ; InterpError = 0.01  ; Hmax = 10
-      #   Number of points np = 1352 ; Ndof = 11862
-      #  h_min, h_max : 0.018824 , 10.2895
-      #  h_(A,B,C,D) : 0.027467 , 0.28644 , 0.45948 , 0.89245
-      ### FUNCTION SF_BaseFlow : computing base flow for Re = 60
-      # Base flow converged in 5 iterations ; Drag = 0.65805; Lx = 4.0737
+\paragraph{Usage} Once the package is properly installed, you can use the document class \emph{elsarticle} to create a manuscript.
+Please make sure that your manuscript follows the guidelines in the Guide for Authors of the relevant journal.
+It is not necessary to typeset your manuscript in exactly the same way as an article, unless you are submitting to a camera-ready copy (CRC) journal.
 
-> plotFF(baseflow,'mesh');
+\paragraph{Functionality} The Elsevier article class is based on the standard article class and supports almost all of the functionality of that class.
+In addition, it features commands and options to format the
+\begin{itemize}
+\item document style
+\item baselineskip
+\item front matter
+\item keywords and MSC codes
+\item theorems, definitions and proofs
+\item lables of enumerations
+\item citation style and labeling.
+\end{itemize}
 
-\end{lstlisting}
-\normalsize
+\section{Front matter}
 
-\caption{Illustration of the procedure to compute a base flow and an adapted mesh using StabFem (from script {\em SCRIPT\_CYLINDER.m}. }
-\end{figure*}
+The author names and affiliations could be formatted in two ways:
+\begin{enumerate}[(1)]
+\item Group the authors per affiliation.
+\item Use footnotes to indicate the affiliations.
+\end{enumerate}
+See the front matter of this document for examples. You are recommended to conform your choice to the journal you are submitting to.
 
-We illustrate the procedure in the case of a cylinder.  Figure 1 gives a retranscription of the sequence of commands (from {\em SCRIPT\_CYLINDER\_ADAPTMESH\_BASEFLOW}) 
-and the output produced.
-First we build an initial mesh (line 1), and compute base flow solutions for increasing values of the Reynolds number up to $Re = 60$ (lines 3-9).
+\section{Bibliography styles}
 
-Then we perform the mesh adaptation (line 13). The produced outputs (lines 14-17) gives information about the resulting mesh. 
-Note the values $h_{min}$ and $h_{max}$ of the smaller and larger edges, as well as the local grid size at four points A,B,C,D defined as $(x_A,y_A) = (0.5,0)$ (at the surface of the cylinder at the position of maximum shear), $(x_B,y_B) = (0.5,2.5)$ (at the location of the peak of structural sensitivity, see next section), $(x_C,y_C) = (0.,4)$ (in the near wake), and $(x_D,y_D) = (0.,10)$ (in the the far wake).
-Finally, the base flow is automatically recomputed on the resulting mesh (line 18-19).
-Finally, lines 21-22 plot the mesh and base flow structure, producing the result displayed in figure (\ref{fig:Baseflow}).
+There are various bibliography styles available.
+You can select the style of your choice in the preamble of this document.
+These styles are Elsevier styles based on standard styles like Harvard and Vancouver.
+Please use Bib\TeX\ to generate your bibliography and include DOIs whenever available.
 
-\begin{figure*}
-\small
-\begin{lstlisting}
-\end{lstlisting}
-\normalsize
+Here are two sample references: \cite{Feynman1963118,Dirac1953888}.
 
-\caption{Illustration of the procedure to adapt the mesh for stability calculations with StabFem (from script {\em SCRIPT\_CYLINDER.m}. }
-\label{listing3}
-\end{figure*}
+\section*{References}
 
-\section{Detail of the weak formulation}
-The problem can be set into weak form by multiplying by multiplying Eq.
-\ref{Newton2} by a test function ${\bf v}$ and the associated divergence constraint by a test function $q$.
-After a few integration by parts we are led to :
-\begin{eqnarray}
-\label{NewtonWeak}
-&\forall ({\bf v};q), \\
-\displaystyle &\int \left[ {\bf v} \cdot {\cal C}( {\bf u}_b^g , \delta {\bf u}_b) +  \nabla  \cdot \delta {\bf u}_b q -\nabla  \cdot {\bf v} \delta p_b
-+ \frac{2}{Re} {\bf D}(\delta {\bf u}_b) : {\bf D}({\bf v}) \right]
-\nonumber
-\\
-\nonumber
-\displaystyle & + \int \left[ {\bf v} \cdot ( {\bf u}_b^g \cdot \nabla {\bf u}_b^g) 
-+ \nabla \cdot {\bf u}_b^g  q 
-- \nabla \cdot {\bf v} p_b^g
-+ \frac{2}{Re} {\bf D}({\bf u}_b^g) : {\bf D}({\bf v}) \right] = 0 
-\end{eqnarray}
+\bibliography{mybibfile}
 

### 2017-10-10 ARTICLE_STABFEM/ARTICLE_ASME.tex
adding WNL a la Sipp & Lebedev

@@
 
-In the next section we thus present this model and propose a direct resolution method. The relation with the initial method of Mantic-Lugo et al. will be discussed afterwards.
+In the next sections we thus successively present the weakly nonlinear model, the self-consistent model and eventually the harmonic-balance model, and propose a direct resolution method. 
+%The relation with the initial method of Mantic-Lugo et al. will be discussed afterwards.
+
+In this section, to simplify the notations, The Navier-Stokes equations will be written symbolically as 
+$\partial_t  {\bf u }  = NS(  {\bf u } )$, therefore dropping the systematic reference of the incompressibility constraint and associated pressure field.
+
+\paragraph{Weakly nonlinear model}
+
+We give here a brief account of the Weakly nonlinear model of Sipp \& Lebedev, also discussed by
+Gallaire et al.
+(FDR 2016).
+The derivation is based on a multiple scale decomposition based on the parameter $\epsilon = 1/Re - 1/Re_c$, and the slow time scale $\tau = \epsilon t$.
+The starting point is an expansion of the flow under the following form :
+
+\begin{eqnarray}
+{\bf u} &=& {\bf u}_{bc} + \epsilon \left[ A(\tau) \hat{\bf u}_c e^{i \omega_c t} + c.c. \right] \label{WNL1}\\
+&+& \epsilon^2 \left[ {\bf u}_\epsilon + |A|^2  {\bf u}_{2,0} + \left(  A^2 {\bf u}_{2,2} e^{2 i \omega_c t} + c.c. \right) \right] + {\cal O}( \epsilon ^3)
+\nonumber
+\end{eqnarray}
+where ${\bf u}_{bc}$ is the base flow at the threshold $Re_c$, $\hat{\bf u}$ the neutral eigenmode at $Re_c$, $A(\tau)$ a slowly varying amplitude.
+The order $\epsilon^2$ contains three terms respectively computed as the solutions of the following linear problems :
+\begin{eqnarray}
+NSL_{{\bf u}_bc} ({\bf u}_\epsilon) + 2 \nabla \cdot {\bf D}( \hat{\bf u}) &=&0,\\
+NSL_{{\bf u}_bc} ({\bf u}_{2,0}) &=& {\cal C}(\hat{\bf u}, ,\overline{\hat{\bf u}}),\\
+NSL_{{\bf u}_bc} ({\bf u}_{2,2}) - 2 i \omega_c {\bf u}_{2,2}  &=& \frac{1}{2} {\cal C}(\hat{\bf u},\hat{\bf u}).
+ \end{eqnarray}
+
+Finally compatibility conditions are imposed at order 3 leading to an amplitude equation with the following
+form :
+\be{WNL3}
+\frac{\partial A }{\partial \tau} = \Lambda A - (\nu_0+\nu_2)  |A|^2 A
+\ee
+With 
+\begin{eqnarray}
+\Lambda &=& \frac{ \left< {\hat{\bf u}}^\dag, 
+\left( {\cal C}({\bf u}_\epsilon, \hat{\bf u}) - 2 \nabla \cdot  {\bf D}( \hat{\bf u}) \right) \right>}
+{  \left<  \hat{\bf u}^\dag,\hat{\bf u} \right> },\\
+\nu_0 &=& -\frac{ \left< {\hat{\bf u}}^\dag,  {\cal C}({\bf u}_{20}, \hat{\bf u} ) \right>}
+{  \left<  \hat{\bf u}^\dag,\hat{\bf u} \right> },\\
+\nu_2 &=& -\frac{ \left< {\hat{\bf u}}^\dag,  {\cal C}({\bf u}_{22}, \overline{\hat{\bf u}})  \right>}
+{  \left<  \hat{\bf u}^\dag,\hat{\bf u} \right> }.
+ \end{eqnarray}
+
+If one is interested in the amplitude of the limit cycle, we have 
+$|\tilde{A}| = \sqrt{\Lambda_r/(\nu{0,r}+\nu{2,r})}$ and eventually, reintroducing the scaling :
+\be 
+|A| =  \frac{\Lambda_r}{\nu{0,r}+\nu{2,r} } \sqrt{\frac{1}{Re_c}-\frac{1}{Re}}
+\ee
+
+The approach gives good prediction in the imediate vicinity of $Re_c$, but deviation appears very 
+rapidly and disagreement is already large at $Re=48$ (although, as discussed by Galaire et al. 
+and also observed by Tchoufag et al. (PRL), a convenient definition of the $\epsilon$ improves the results).
 
 \paragraph{Harmonic balance : equations and procedure }
-
-In this section, to simplify the notations, The Navier-Stokes equations will be written symbolically as 
-$\partial_t  {\bf u }  = NS(  {\bf u } )$, therefore droping the systematic reference of the incompressibility constraint and associated pressure field.
 

### 2017-10-10 CYLINDER/SCRIPT_CYLINDER_WNL.m

@@ -1,0 +1,80 @@
+%  Instability of the wake of a cylinder with STABFEM  
+%
+%  this scripts performs the following calculations :
+%  1/ Generation of an adapted mesh
+%  2/ Base-flow properties for Re = [2-40]
+%  3/ Stability curves St(Re) and sigma(Re) for Re = [40-100]
+%  4/ Determination of the instability threshold
+%  5/ Harmonic-Balance for Re = REc-100
+%  6/ Self-consistent model for Re=100
+
+% CHAPTER 0 : set the global variables needed by the drivers
+
+global ff ffdir ffdatadir sfdir verbosity
+%ff = '/PRODCOM/FREEFEM/Ubuntu12.04/3.29/bin/FreeFem++-nw'; % on IMFT network
+ff = '/usr/local/ff++/openmpi-2.1/3.55/bin/FreeFem++-nw'; % on DF's macbookpro 
+ffdatadir = './WORK/';
+sfdir = '../SOURCES_MATLAB/'; % where to find the matlab drivers
+ffdir = '../SOURCES_FREEFEM/'; % where to find the freefem scripts
+verbosity = 1;
+addpath(sfdir);
+system(['mkdir ' ffdatadir]);
+figureformat='png'; AspectRatio = 0.56; % for figure
+
+%##### CHAPTER 1 : COMPUTING THE MESH WITH ADAPTMESH PROCEDURE
+
+if(exist('baseflow')==1)
+disp(' ADAPTMESH PROCEDURE WAS PREVIOUSLY DONE, START WITH EXISTING MESH : '); 
+baseflow=SF_BaseFlow(baseflow,60);
+[ev,em] = SF_Stability(baseflow,'shift',0.04+0.76i,'nev',1,'type','S');
+else
+   
+disp(' STARTING ADAPTMESH PROCEDURE : ');    
+disp(' ');
+disp(' LARGE MESH : [-40:80]x[0:40] ');
+disp(' ');    
+baseflow=SF_Init('Mesh_Cylinder_Large.edp');
+baseflow=SF_BaseFlow(baseflow,1);
+baseflow=SF_BaseFlow(baseflow,10);
+baseflow=SF_BaseFlow(baseflow,60);
+baseflow=SF_Adapt(baseflow,'Hmax',5);
[…]

### 2017-10-12 ARTICLE_STABFEM/ARTICLE_ASME.tex
adding wnl analysis for cylinder

@@
 \includegraphics[width=.9 \linewidth]{Cylinder_Lx_baseflow.png}
-\includegraphics[width=.9 \linewidth]{Cylinder_Drag_baseflow.png}
+\includegraphics[width=.9 \linewidth]{Cylinder_Cx_baseflow.png}
 \caption{Recirculation length $L_x$ $(a)$  and drag $C_x$ ($b$) of the base flow over a cylinder as function of $Re$.}
@@
 
+In this section, to simplify the notations, The Navier-Stokes equations will be written symbolically as 
+$\partial_t  {\bf u }  = NS(  {\bf u } )$, therefore dropping the systematic reference of the incompressibility constraint and associated pressure field.
+
 \paragraph{Review on nonlinear global stability approaches}
@@
 
-In this section, to simplify the notations, The Navier-Stokes equations will be written symbolically as 
-$\partial_t  {\bf u }  = NS(  {\bf u } )$, therefore dropping the systematic reference of the incompressibility constraint and associated pressure field.
-
 \paragraph{Weakly nonlinear model}
@@
 (FDR 2016).
-The derivation is based on a multiple scale decomposition based on the parameter $\epsilon = 1/Re - 1/Re_c$, and the slow time scale $\tau = \epsilon t$.
+The derivation is based on a multiple scale decomposition based on the parameter $\epsilon^2 = 1/Re - 1/Re_c$, and the slow time scale $\tau = \epsilon t$.
 The starting point is an expansion of the flow under the following form :
@@
 \begin{eqnarray}
-{\bf u} &=& {\bf u}_{bc} + \epsilon \left[ A(\tau) \hat{\bf u}_c e^{i \omega_c t} + c.c. \right] \label{WNL1}\\
-&+& \epsilon^2 \left[ {\bf u}_\epsilon + |A|^2  {\bf u}_{2,0} + \left(  A^2 {\bf u}_{2,2} e^{2 i \omega_c t} + c.c. \right) \right] + {\cal O}( \epsilon ^3)
+{\bf u} &=& {\bf u}_{bc} + \epsilon \left[ A_{wnl} (\tau) \hat{\bf u} e^{i \omega_c t} + c.c. \right] \label{WNL1}\\
+&+& \epsilon^2 \left[ {\bf u}_\epsilon + |A_{wnl}|^2  {\bf u}_{2,0} + \left(  A_{wnl}^2 {\bf u}_{2,2} e^{2 i \omega_c t} + c.c. \right) \right] + {\cal O}( \epsilon ^3)
 \nonumber
 \end{eqnarray}
-where ${\bf u}_{bc}$ is the base flow at the threshold $Re_c$, $\hat{\bf u}$ the neutral eigenmode at $Re_c$, $A(\tau)$ a slowly varying amplitude.
+where ${\bf u}_{bc}$ is the base flow at the threshold $Re_c$, $\hat{\bf u}$ the neutral eigenmode at $Re_c$, $A_{wnl}(\tau)$ a slowly varying amplitude.
 The order $\epsilon^2$ contains three terms respectively computed as the solutions of the following linear problems :
@@
 \be{WNL3}
-\frac{\partial A }{\partial \tau} = \Lambda A - (\nu_0+\nu_2)  |A|^2 A
+\frac{\partial A_{wnl} }{\partial \tau} = \Lambda A_{wnl} - (\nu_0+\nu_2)  |A_{wnl}|^2 A_{wnl}
 \ee
@@
 If one is interested in the amplitude of the limit cycle, we have 
-$|\tilde{A}| = \sqrt{\Lambda_r/(\nu{0,r}+\nu{2,r})}$ and eventually, reintroducing the scaling :
-\be 
-|A| =  \frac{\Lambda_r}{\nu{0,r}+\nu{2,r} } \sqrt{\frac{1}{Re_c}-\frac{1}{Re}}
+$|A_{wnl}| = \sqrt{\Lambda_r/(\nu_{0,r}+\nu_{2,r})}$ and eventually, reintroducing the scaling :
+\be{ANL} 
+|A| =  \epsilon |A_{wnl}| = \frac{\Lambda_r}{\nu_{0,r}+\nu_{2,r} } \sqrt{\frac{1}{Re_c}-\frac{1}{Re}}
+\ee
+The frequency of the limit cycle is given by
+\be{omegaWNL} 
+\omega = \omega_c + 
+\left( \Lambda_r - \Lambda_i \frac{\nu_{0,i}+\nu_{2,i} }{\nu_{0,r}+\nu_{2,r} } \right) 
+\left(\frac{1}{Re_c}-\frac{1}{Re}\right)
 \ee
 
-The approach gives good prediction in the imediate vicinity of $Re_c$, but deviation appears very 
-rapidly and disagreement is already large at $Re=48$ (although, as discussed by Galaire et al. 
-and also observed by Tchoufag et al. (PRL), a convenient definition of the $\epsilon$ improves the results).
+As can be seen on figures 6 and 7,  the approach gives good prediction in the immediate vicinity of $Re_c$, but deviation appears very rapidly and disagreement is already large at $Re=48$ (although, as discussed by Gallaire et al.
+and also observed by Tchoufag et al.
+(PRL), a convenient definition of the $\epsilon$ improves the results).
+
+\paragraph{Self-Consistent approach}
+
+We now discuss the self-consistent approach as introduced by Mantic-Lugo et al.
+The starting point of this model is a pseudo-eigenmode expansion of the flow as follows :
+
+\be{SC}
+{\bf u } = {\bf u }_m + A \left[ \tilde{{\bf u }}_1 e^{\sigma_{sc} t + i \omega_{sc} t} +   \tilde{\bf u }_{-1} e^{\sigma_{sc} t  -i \omega_{sc} t} \right]
+\ee
+
+Where ${\bf u }_m$ is a {\em mean flow} defined by phase-averaging over the cycle, $\tilde{{\bf u }}_1$ is a pseudo-eigenvector which is normalized by the condition  $||\tilde{{\bf u }}_1|| = 1/\sqrt{2}$,
+ $A$ is an amplitude parameter directly related to the energy of the oscillating flow, and $\lambda = \sigma_{SC} + i \omega_{SC}$ is a pseudo-eigenvalue which depends upon the parameter $A$.
+
+\be{HBEq0}
+NS(  {\bf u }_m ) - A_{sc}^2 {\cal C}( \tilde{{\bf u }}, \overline{\tilde{\bf u }}) = 0,
+\ee
+\be{HBEq1}
+(\sigma_{sc} + i \omega_{sc}) \tilde{{\bf u }} =  NSL_{{\bf u }_m}(  \tilde{{\bf u }} ),
+\ee
+\be{BBEqnorm}
+|| \tilde{{\bf u }}|| = \frac{1}{\sqrt{2}}.
+\ee
+
+% The mean flow is then governed by the same equation
+%\ref{HBEq0}) written above, while $\tilde{{\bf u }}_1$ is the solution of an eigenvalue problem with the same form as  (\ref{HBEq1}) except that $i \omega$ is replaced by $\sigma_{SC} + i \omega_{SC}$.
+The self-consistent model has the following properties :
+\begin{itemize}
+\item[-] For $A \ll 1$ it is equivalent to the linear eigenvalue problem (\ref{LEP}), and the generalized eigenvalue coincides with the one predicted by linear stability : $\sigma_{SC} + i \omega_{SC} = \sigma_{lin} + i \omega_{lin}$.
+\item[-] For $\sigma_{SC}=0$ (corresponding to a specific choice of the amplitude $A=A_c$),  the expansion (\ref{SC}) is equivalent to a Fourier decomposition of the limit cycle with only two term retained.
+\item[-] For $0<A<A_c$, the resolution leads to a relation $\sigma_{SC}(A) ; \omega_{SC}(A)$
+such that $0< \sigma_{SC}(A) < \sigma_{lin}$.
+ Although in this case the expansion \ref{SC} cannot represent the flow for all $t$, Mantic-Lugo et al.
+argued that the relation between $\sigma_{SC}$ and $A$ can be used to build an amplitude equation which captures the transient approach to the limit cycle.
+\end{itemize}
 
@@
 
+As discussed above, the Self-Consistent model was initially presented as the authors as a rational way to explain the dynamics in terms of a stability analysis of the {\em mean flow}.
+Furthermore, the resolution method presented by the authors, which involves a double iteration loop, is not easy to implement and not particularly efficient.
+
+If one is only interested by the properties of the limit cycle and not the transient, the model is actually equivalent to a Fourier series, and amenable to a more direct resolution method. 
 We thus start with a Fourier decomposition of the limit cycle under the form :
@@
 
-Note that the Fourier description of the limit cycle is invariant with respect to the phase $\phi$ (i.e.
-the equations are unchanged when replacing $[ {\bf u }_1,  {\bf u }_{-1}] $ by  $[ {\bf u }_1 e^{i\varphi},  {\bf u }_{-1}  e^{-i\varphi}] $.
+Note that contrary to the SC model, the ${\bf u }_1$ component is not normalized.
+The amplitude $A$ can easily be computed a posteriori as $A = \sqrt{2 ||{\bf u }_1||}$.
+On the other hand, the Fourier description of the limit cycle is invariant with respect to the phase $\phi$ (i.e.
+the equations are unchanged when replacing $[ {\bf u }_1,  {\bf u }_{-1}] $ by  $[ {\bf u }_1 e^{i\varphi},  {\bf u }_{-1}  e^{-i\varphi}] $).
 To allow resolution we thus need an extra equation to fix this phase.
@@
 
-\paragraph{Results for the wake of a cylinder}
+\paragraph{Implementation and results for cylinder}
 
-SECTION TO BE COMPLETED
+\begin{figure*}
+\small
+\begin{lstlisting}
+[baseflow,em]=SF_FindThreshold(baseflow,em);
+wnl = SF_WNL(baseflow);
 
-\paragraph{Link with the Self-Consistent approach}
+Re_HB = [Rec 47.5 48 49 50 55 60 65 70 75 80 85 90 95 100];
+omega_HB = [Omegac]; Aenergy_HB = [0];
 
-We now discuss the link between the harmonic balance approach presented above and the self-consistent approach as introduced by Mantic-Lugo et al.
-The starting point of this model is a pseudo-eigenmode expansion of the flow as follows :
+baseflow=SF_BaseFlow(baseflow,47.5);
+[ev,em] = SF_Stability(baseflow,'shift',Omegac*i);
+Astart = sqrt(wnl.Lambda/(wnl.Nu0+wnl.Nu2)*(1/Rec-1/47.5));
+[meanflow,mode] = SF_HarmonicBalance(baseflow,em,'sigma',0.,'Re',47.5,'Aguess',Astart);
 
-\be{SC}
-{\bf u } = {\bf u }_m + A \left[ \tilde{{\bf u }}_1 e^{\sigma_{SC} t + i \omega_{SC} t} +   \tilde{\bf u }_{-1} e^{\sigma_{SC} t  -i \omega_{SC} t} \right]
-\ee  
-Where ${\bf u }_m$ is a {\em mean flow} defined by phase-averaging over the cycle, $\tilde{{\bf u }}_1$ is a pseudo-eigenvector which is normalized by the condition  $||\tilde{{\bf u }}_1|| = 1/\sqrt{2}$,
- $A$ is an amplitude parameter directly related to the energy of the oscillating flow, and $\lambda = \sigma_{SC} + i \omega_{SC}$ is a pseudo-eigenvalue which depends upon the parameter $A$.
-The mean flow is then governed by the same equation
-(\ref{HBEq0}) written above, while $\tilde{{\bf u }}_1$ is the solution of an eigenvalue problem with the same form as  (\ref{HBEq1}) except that $i \omega$ is replaced by $\sigma_{SC} + i \omega_{SC}$.
-The self-consistent model has the following properties :
-\begin{itemize}
-\item[-] For $A \ll 1$ it is equivalent to the linear eigenvalue problem (\ref{LEP}), and the generalized eigenvalue coincides with the one predicted by linear stability : $\sigma_{SC} + i \omega_{SC} = \sigma_{lin} + i \omega_{lin}$.
-\item[-] For $\sigma_{SC}=0$ (corresponding to a specific choice of the amplitude $A=A_c$),  the expansion (\ref{SC}) is equivalent to the harmonic-balance decomposition (\ref{HB})
-\item[-] For $0<A<A_c$, the resolution leads to a relation $\sigma_{SC}(A) ; \omega_{SC}(A)$
-such that $0< \sigma_{SC}(A) < \sigma_{lin}$.
- Although in this case the expansion \ref{SC} cannot represent the flow for all $t$, Mantic-Lugo et al.
-argued that the relation between $\sigma_{SC}$ and $A$ can be used to build an amplitude equation which captures the transient approach to the limit cycle.
-\end{itemize}
+for Re = Re_HB(2:end)
+    [meanflow,mode] = SF_HarmonicBalance(meanflow,mode,'Re',Re);
+    omega_HB = [omega_HB imag(mode.lambda)];
+    Aenergy_HB  = [Aenergy_HB mode.Energy];
+end
+\end{lstlisting}
+\normalsize
 
-%Barkley [] and Leontini [] have
+\caption{Illustration of the procedure for nonlinear calculations using StabFem (from script {\em SCRIPT\_CYLINDER.m}. }
+\label{fig:listingNL}
+\end{figure*}
+
+Figure \ref{fig:listingNL}, which is again extracted from the script 
+\verb|SCRIPT\_CYLINDER\_DEMO.m|, illustrate the sequence of commands to perform both the weakly nonlinear and the harmonic balance studies for the case of a cylinder.
+On line 1, we first determine the instability threshold, and the corresponding base flow and eigenmode\footnote{This routine uses Newton iteration to directly compute the base flow, the eigenmode, the frequency and the critical Reynolds.
+The algorithm is very similar to the one presented for the HB, with an additional unknown (Re) and an additional constraint (normalization of the mode).
+The interested reader should reconstruct easily the whole procedure from the code provided.}
+On line 2 we then compute all the terms and coefficients of the wnl model.
+Then we construct  vectors to store the frequency and the amplitude of the limit cycle in the range $Re = [47.5-100]$.
+Note that for the computation at $Re=47.5$ we need a guess for the amplitude, which is deduced from the weakly nonlinear approach on line 9.
+In the sequel of the loop no guess value is prescribed, hence the solver uses continuation.
 
@@
 \includegraphics[width=.9 \linewidth]{Cylinder_Lx_Re_HB.png}
-\includegraphics[width=.9 \linewidth]{Cylinder_Drag_Re_HB.png}
+\includegraphics[width=.9 \linewidth]{Cylinder_Cx_Re_HB.png}
 \end{center}
@@
 \includegraphics[width=.9 \linewidth]{Cylinder_Strouhal_Re_HB.png}
-\includegraphics[width=.9 \linewidth]{Cylinder_Lift_Re_SC.png}
+\includegraphics[width=.9 \linewidth]{Cylinder_Cy_Re_SC.png}
 \includegraphics[width=.9 \linewidth]{Cylinder_Energy_Re_SC.png}
@@
 
+The whole results are presented in figures 8 (mean-flow properties) and 9 (oscillating mode properties).
+
+%Barkley [] and Leontini [] have
+
 \begin{figure}
@@
 \includegraphics[width=.9 \linewidth]{Cylinder_SC100_EnergySigma.png}
-\includegraphics[width=.9 \linewidth]{Cylinder_SC100_LiftSigma.png}
+\includegraphics[width=.9 \linewidth]{Cylinder_SC100_CySigma.png}
 \end{center}
-\caption{SELF CONSISTENT APPROACH FOR THE WAKE OF A CYLINDER, $Re = 100$. NOTE THAT THE AMPLITUDE IS NOTABLY LOWER THAN IN MANTIC-LUGO. TO BE EXPLAINED.}
+\caption{SELF CONSISTENT APPROACH FOR THE WAKE OF A CYLINDER, $Re = 100$.}
 \label{fig:SC100}
@@
 
-\appendix
+\clearpage
+
+\section{Conclusion}
 

### 2017-10-12 CYLINDER/SCRIPT_CYLINDER_DEMO.m

@@ -4,7 +4,8 @@
 %  1/ Generation of an adapted mesh
 %  2/ Base-flow properties for Re = [2-40]
 %  3/ Stability curves St(Re) and sigma(Re) for Re = [40-100]
-%  4/ Determination of the instability threshold
+%  4/ Determination of the instability threshold and Weakly-Nonlinear
+%  analysis
 %  5/ Harmonic-Balance for Re = REc-100
 %  6/ Self-consistent model for Re=100
 
@@ -97,14 +98,14 @@ saveas(gca,'Cylinder_SensitivityRe60',figureformat);
 
 %%%% CHAPTER 2 : DESCRIPTION OF BASE FLOW PROPERTIES (range 2-50)
 
-if(exist('Re_RangeB')==0)
+if(exist('Cx_BF')==0)
 
-Re_RangeB = [2 : 2: 50];
-Drag_tabB = []; Lx_tabB = [];
-    for Re = Re_RangeB
+Re_BF = [2 : 2: 50];
+Cx_BF = []; Lx_BF = [];
+    for Re = Re_BF
         baseflow = SF_BaseFlow(baseflow,'Re',Re);
-        Drag_tabB = [Drag_tabB,baseflow.Drag];
-        Lx_tabB = [Lx_tabB,baseflow.Lx];
+        Cx_BF = [Cx_BF,baseflow.Cx];
+        Lx_BF = [Lx_BF,baseflow.Lx];
     end
     
 end
@@ -112,14 +113,14 @@ end
 %%% chapter 2B : figures
  
 figure(22);hold off;
-plot(Re_RangeB,Drag_tabB,'b+-');
-xlabel('Re');ylabel('Drag');
+plot(Re_BF,Cx_BF,'b+-');
+xlabel('Re');ylabel('Cx');
 box on; pos = get(gcf,'Position'); pos(4)=pos(3)*AspectRatio;set(gcf,'Position',pos); % resize aspect ratio
 set(gca,'FontSize', 18);
-saveas(gca,'Cylinder_Drag_baseflow',figureformat);
+saveas(gca,'Cylinder_Cx_baseflow',figureformat);
 
 figure(23);hold off;
-plot(Re_RangeB,Lx_tabB,'b+-');
+plot(Re_BF,Lx_BF,'b+-');
 xlabel('Re');ylabel('Lx');
[…]

### 2018-03-06 ARTICLE_STABFEM/ARTICLE_ASME.tex
Adding Acoustic cases (TP M1, UPS, 2018)

@@
 \usepackage{epsfig} %% for loading postscript figures
+\usepackage{amsmath}
 
@@
 \usepackage{listings}
+\usepackage[colorlinks, linkcolor=blue, citecolor=blue, filecolor=black,urlcolor=blue]{hyperref}
 
@@
 
-\title{Popularizing linear and nonlinear global approaches to hydrodynamic instabilities : 
-A review and a simple implementation for the wake of a cylinder}
+%\title{Popularizing linear and nonlinear global approaches to hydrodynamic instabilities : 
+%A review and a simple implementation for the wake of a cylinder}
+
+\title{A {practical} review on linear and nonlinear global approaches to stability analysis}
 
@@
 \begin{abstract}
-{\it This is the abstract.
-This article illustrates preparation of ASME paper using 
-\LaTeX2\raisebox{-.3ex}{$\epsilon$}.
-An abstract for an ASME paper should be less than 150 words and is normally in italics.
-%%% 
-Please use this template to test how your figures will look on the printed journal page of the Journal of Mechanical Design.
-The Journal will no longer publish papers that contain errors in figure resolution.
-These usually consist of unreadable or fuzzy text, and pixilation or rasterization of lines.
-This template identifies the specifications used by JMD some of which may not be easily duplicated; for example, ASME actually uses Helvetica Condensed Bold, but this is not generally available so for the purpose of this exercise Helvetica is adequate.
-However, reproduction of the journal page is not the goal, instead this exercise is to verify the quality of your figures.
-Notice that this abstract is to be set in 9pt Times Italic, single spaced and right justified.
+{\it 
+This paper is aimed to review the linear and nonlinear approaches to study the stability of fluid flows. 
+We provide a concise but self-contained exposition of the main concepts and specific numerical methods 
+designed for global stability studies, including the classical linear stability analysis, the adjoint-based sensitivity and  
+the most recent nonlinear developments.
+A simple computer code, that implements all the concepts discussed in the present paper, is provided. 
+In particular, we discuss the mesh adaptation, the use of simple shift-invert strategy instead of the classical Arnoldi algorithm and a reformulation and simplification of the recent nonlinear self-consistent approach proposed by Manti\v{c}-Lugo et al \cite{MLugo2014} in terms of a harmonic balance.
+The code is demonstrated for the reference case of the incompressible, two-dimensional flow around a circular cylinder, but the software is easily customisable to a variety of other
+flow configurations or flow equations.
+%An abstract for an ASME paper should be less than 150 words and is normally in italics.
 }
@@
 
-The destabilization of a flow as a parameter is varied, leading from a steady solution to a unsteady one, is an ubiquous situation in fluid dynamics.
-Specific analytical and numerical methods suited to the description have emerged in the second part of the 19th century and continuously evolved up to the present day.
-When the flow has no analytical expression, the stability problem requires a numerical resolution, and when there are at least two spatial variables, the class of methods suited to solve such problems are generally called "global stability approaches."%\footnote{Sorry Laurette !}
+The concept of stability bears on the reaction of a system to a small perturbation of its state.
+If the generic disturbance grows in time, the system is unstable.
+The concept of stability can be simply formulated for a system of Ordinary Differential Equations (ODE).
+Such systems can be at equilibrium, where the state does not depend on time, or can present a periodic state, with all components returning to the same values, after every period.
 
-Among all instability problems, one of the most famous and most studied is the flow around a 2D cylinder, which becomes unsteady for $Re \approx 47$ leading to the well-known Bénard-Von Karman vortex alley.
-This situation has served as a benchmark in the development of this class of methods.
-If one is only interested in predicting the stability or instability of a flow, it is enough to conduct an  {\em linear stability analysis} which is the fundamental brick of global stability approaches.
+The stability of fluid flows usually depends on the value of a given parameter.
+A bifurcation occurs when a critical value is reached and the original solution becomes linearly unstable, with the system tending towards a new steady or unsteady state.
+%The destabilization of a flow as a parameter is varied, leading from a steady solution to a unsteady one, is an ubiquous situation in fluid dynamics. 
+In the second part of the 19th century, specific analytical and numerical methods able to study these bifurcations have emerged and are continuously evolving up to the present days. 
+A crucial point, that drove the development in this field, is the availability of larger and larger computing resources. 
+Initially, the linear stability theory focused on fluid flows that are homogeneous in two spatial directions, e.g.
+plane Poiseuille flow \cite{Dreid2004}.
+This implies that the streamwise and the spanwise base-flow gradients vanish and, as a consequence, it is possible to consider only one (streamwise) velocity component.
+Thus, the stability problem requires a \textit{local} numerical resolution, i.e.
+a one-dimensional problem.
+On the other hand,  when there are at least two spatial variables, the class of methods suited to solve such problems are generally called "global stability approaches".
+%When the flow has no analytical expression, the stability problem requires a numerical resolution, and when there are at least two spatial variables, the class of methods suited to solve such problems are generally called "global stability approaches."%\footnote{Sorry Laurette !}
+A classical example of such behavior in fluid dynamics is the instability occurring in the wake of a circular cylinder.
+At low Reynolds number (precisely for $Re < 46.7$) the flow is steady and symmetric, but for larger values of Re a global instability arises in the flow field leading to the well-known von K\'arm\'an vortex alley.
+%Among all instability problems, one of the most famous and most studied is the flow around a 2D cylinder, which becomes unsteady for $Re \approx 47$ leading to the well-known Bénard-Von Karman vortex alley.
+This flow configuration has served as a benchmark in the development of this class of methods.  
+If one is only interested in predicting the stability or instability of a flow, it is enough to conduct a {\em linear stability analysis} which is the fundamental brick of global stability approaches.
 Beyond this simple question, in the past two decades, a number of extensions have been developed and popularized.
-{\em Adjoint methods} are an important extension (Giannetti \& Luchini ; Marquet et al ) ; they can give insight into the sensitivity of the flow to intrinsic or extrinsic contributions.
-{\em Nonlinear stability approaches} (Sipp \& Lebedev; Mantic-Lugo et al) have also been developed in order to extend the range of applicability of the approach towards large amplitude perturbations.
+{\em Adjoint methods} are an important extension \cite{GiannettiLuchini},\cite{Marquet} ; they can give insight into the sensitivity of the flow to intrinsic or extrinsic contributions.
+{\em Nonlinear stability approaches} \cite{MLugo2014}, \cite{SippLebedev} have also been developed in order to extend the range of applicability of the approach towards large amplitude perturbations.
 
@@
 \cprotect\footnote{The StabFem software may be obtained at the following url : 
-\verb| https://github.com/erbafdavid/StabFem |} 
+\url{https://github.com/erbafdavid/StabFem}} 
 to perform such calculations. The software combines program written in both FreeFem++ and Matlab languages. 
@@
 We start from the general problem of a flow field $[{\bf u},p]$ satisfying the incompressible Navier-Stokes equations on a domain $\Omega$,
-\be{NSprimitive}
-\partial_t {\bf u} = NS ({\bf u};p)
-\equiv - {\bf u} \cdot \nabla {\bf u} - \nabla p + \frac{2}{Re}  \nabla \cdot {\bf D}({\bf u})  \quad [\mbox{with} \nabla \cdot {\bf u} = 0].  \\
-\ee
+\begin{eqnarray} \label{NSprimitive}
+\partial_t {\bf u} = {\cal NS} ({\bf u};p)
+\equiv - {\bf u} \cdot \nabla {\bf u} - \nabla p + \frac{2}{Re}  \nabla \cdot {\mathsf{D}}({\bf u})  \\
+\nabla \cdot {\bf u} = 0,
+\end{eqnarray}
+
 with suitable boundary conditions on the frontier $\partial \Omega$ of the domain.
-Here $ {\bf D}({\bf u}) $ is the rate-of-strain tensor defined as
+Here $ {\mathsf{D}}({\bf u}) $ is the rate-of-strain tensor defined as
 $$
- {\bf D}({\bf u}) = 1/2
+ {\mathsf{D}}({\bf u}) = 1/2
 \left( \nabla {\bf u} +  \nabla^T  {\bf u}\right)
 $$ 
-In the framework of finite element methods, it is convenient to write the equation in weak form.
+In the framework of finite element methods, we need to write the equation in weak form.
 Prior to this we define a scalar product as follows, for either scalar or vectorial quantities 
-($\phi_1, \phi_2)$:
+$\left< \phi_1, \phi_2 \right> $:
 $$
-\left< \phi_1, \phi_2 \right> = \int_\Omega \overline{\phi_1} \cdot \phi_2   \mbox{ d} \Omega
+\left< \phi_1, \phi_2 \right> = \int_\Omega \overline{\phi}_1 \cdot \phi_2   \mbox{ d} \Omega
 $$
@@
 \be{NSweak}
-\forall [{\bf v},q], \quad \partial_t \left< {\bf v}, {\bf u}\right> = \left< {\bf v} , NS ({\bf u};p) \right> + \left< q, \nabla \cdot {\bf u}\right>.
+\forall [{\bf v},q], \quad \partial_t \left< {\bf v}, {\bf u}\right> = \left< {\bf v} , {\cal NS} ({\bf u};p) \right> + \left< q, \nabla \cdot {\bf u}\right>.
 \ee
@@
 \ee
-Injecting into the Navier-Stokes equation in weak form (\ref{NSweak}) and developing up to linear terms in terms of the perturbation lead to  
-$NS ({\bf u}_b^g,p_b^g) + NSL_{{\bf u}_b^g}(\delta {\bf u}_b,\delta p_b)$, which can also be written in weak form :
+Injecting (\ref{Newton1}) into the weak form (\ref{NSweak}) of the Navier-Stokes equations and developing up to linear terms in terms of the perturbation lead to  
+${\cal NS}  ({\bf u}_b^g,p_b^g) + {\cal L} _{{\bf u}_b^g}(\delta {\bf u}_b,\delta p_b;{\bf u}_b^g)$, which can also be written in weak form as :
 %\be
@@
 \bes{Newton2}
-&\left< {\bf v}, NS ({\bf u}_b^g)\right> + \left<q, \nabla \cdot {\bf u}_b^g\right>  
+&\left< {\bf v}, {\cal NS} ({\bf u}_b^g)\right> + \left<q, \nabla \cdot {\bf u}_b^g\right>  
 \\
-+ &\left< { \bf v}, NSL_{{\bf u}_b^g}( \delta {\bf u}_b,\delta p_b) \right> + \left<q, \nabla \cdot \delta{\bf u}_b\right> = 0.
++ &\left< { \bf v}, {\cal L} _{{\bf u}_b^g}( \delta {\bf u}_b,\delta p_b; {\bf u}_b^g) \right> + \left<q, \nabla \cdot \delta{\bf u}_b\right> = 0,
 \ees
-Where $NSL$ is the linearised Navier-Stokes operator, defined by its action on a flow field $({\bf u} ; p)$ as follows 
+where ${\cal L}$ is the linearised Navier-Stokes operator, defined by its action on a flow field $({\bf u} ; p)$ as follows 
 \be{defNSL}
- NSL_{{\bf U}}( {\bf u} ;  p) = - {\cal C}( {\bf U} , {\bf u}) -\nabla p
-+\frac{2}{Re} \nabla  \cdot {\bf D}({\bf u}), %\quad ( \mbox{ with } \nabla \cdot {\bf u } = 0 \, ).
+ {\cal L}_{{\bf U}}( {\bf u}, p; {\bf U}) = - {\cal C}( {\bf U} , {\bf u}) -\nabla p
++\frac{2}{Re} \nabla  \cdot {\mathsf{D}}({\bf u}), %\quad ( \mbox{ with } \nabla \cdot {\bf u } = 0 \, ).
  \ee
-and {\cal C} is the convection operator defined by 
+and ${\cal C}$ is the convection operator defined by 
 \be{defC}
@@
 
-This problem can now be discretized by projecting upon a basis of Taylor-Hood (P2-P2-P1) finite elements.
-Noting $\delta X$ the discretization of ($\delta {\bf u}_b;\delta p_b$) this eventually leads to a matricial problem with the form $A \cdot \delta X = Y$.
+This problem can now be discretized by projecting upon a basis of Taylor-Hood $(u,v,p) \rightarrow (P2,P2,P1)$ finite elements.
+Noting $\delta X$ the discretization of ($\delta {\bf u}_b;\delta p_b$) this eventually leads to a matricial problem of the form $A \cdot \delta X = Y$.
 The procedure of Newton iteration is to solve iteratively this set of equations up to convergence.
@@
 \paragraph{Direct eigenvalue problem}
-We consider the stability using the classical ansatz 
+We study the onset of the instability within the linear theory by using a normal-mode analysis:
+
 \be{startmodepropre}
-{\bf u} = {\bf u}_b + \epsilon \hat{\bf u} e^{\lambda t} 
+{\bf u} ({\bf{x}},t) = {\bf u}_b({\bf{x}}) + \epsilon \hat{\bf u}({\bf{x}}) e^{\lambda t}, \,\,\,\, {p}({\bf{x}},t) = {p}_b({\bf{x}}) + \epsilon \hat{p}({\bf{x}}) e^{\lambda t}
 \ee
-Where $\lambda = \sigma + i \omega$ is the eigenvalue, $\sigma$ the amplification rate,
-$\omega$ the oscillation rate, $\hat{{\bf u}}$ the eigenmode, and $\epsilon$ a small parameter.
-The eigenmodes is governed by the linear problem 
-$\lambda \hat{{\bf u}} = NSL_{{\bf u}_b}( \hat{\bf u},\hat{p})$, or, in weak form : 
+where $\lambda = \sigma + i \omega$ is the eigenvalue, $\sigma$ the amplification rate,
+$\omega$ the oscillation rate, $\hat{{\bf u}},\hat{p}$ the eigenmodes, and $\epsilon$ a small parameter.
+The eigenmodes and the eigenvalues are the solution of the following eigenproblem:
+
+\be{LEP}
+\lambda \hat{{\bf u}} = {\cal L}_{{\bf u}_b}( \hat{\bf u},\hat{p}),
+\ee
+or, in weak form : 
 \be{eigenvalueproblem}
-\lambda \left< {\bf v} , \hat{{\bf u}} \right> = \left< {\bf v}, NSL_{{\bf u}_b} ( \hat{\bf u},\hat{p})\right> + \left< q, \nabla \cdot \hat{\bf u} \right>.
+\lambda \left< {\bf v} , \hat{{\bf u}} \right> = \left< {\bf v}, {\cal L}_{{\bf u}_b} ( \hat{\bf u},\hat{p})\right> + \left< q, \nabla \cdot \hat{\bf u} \right>.
 \ee
-After discretization we end up with an eigenvalue problem with the matricial form
+After discretization, we end up with an eigenvalue problem with the matricial form
 \be{Eigen_matricial}
-\lambda B \hat{X} = A \hat{X}
+\lambda {\mathsf{B}} \hat{X} = {\mathsf{A}} \hat{X}
 \ee
-Where $A$ is the matrix resulting from the discretization of $NSL_{{\bf u}_b}$, i.e.
-the very same matrix as appearing in the Newton computation of the base flow, and  $B$ is a 'weight' matrix associated to the scalar product $\left<v,u\right> = \int \overline{\bf v} \cdot {\bf u} \mbox{ d} \Omega$.
+Where ${\mathsf{A}}$ is the matrix resulting from the discretization of ${\cal L}_{{\bf u}_b}$, i.e.
+the same matrix  appearing in the Newton computation of the base flow, and  $B$ is a 'weight' matrix associated to the scalar product $\left<v,u\right> = \int \overline{\bf v} \cdot {\bf u} \mbox{ d} \Omega$.
 
@@
 Developed in the two past decades, the concept adjoint modes has now become an unavoidable complement to the linear global stability approach.
-We here give a short summary of the definition and usefulness of this concept.
-We can first define the {\em adjoint linearised Navier-Stokes operator} $NSL^\dag$ defined by the property:
+We here give a short summary of the definition and usefulness of this concept,
+we refer to Luchini \& Bottaro\cite{LucBott2014} for further details.
+First of all, the {\em adjoint linearised Navier-Stokes operator} ${\cal L}^\dag$ is defined thanks to the following 
+property:
 \bes{NSLAdj}
-\forall ( {\bf u}, p ; {\bf v}, q), & \left< NSL^\dag_{\bf U}( {\bf v},q) ,{\bf u}\right> + \left< \nabla \cdot {\bf v},p\right>  \\
-=& \left< {\bf v}, NSL_{\bf U} ({\bf u},p)\right> + \left< q, \nabla \cdot {\bf u}\right>.
+\forall ( {\bf u}, p ; {\bf v}, q), & \left< {\cal L}^\dag_{\bf U}( {\bf v},q) ,{\bf u}\right> + \left< \nabla \cdot {\bf v},p\right>  \\
+=& \left< {\bf v}, {\cal L}_{\bf U} ({\bf u},p)\right> + \left< q, \nabla \cdot {\bf u}\right>.
 \ees
-We can then define the adjoint eigenmodes as the solutions to the eigenvalue problem 
+We can then define the adjoint eigenvalues and eigenmodes as the solutions of the eigenvalue problem 
 \be{EigenAdj} 
 \forall ( {\bf u}, p), \quad  \lambda^\dag \left< \hat{\bf v}, {\bf u}\right> =
- \left< NSL^\dag_{\bf U}( \hat{\bf v},\hat{q}) ,{\bf u}\right> + \left< \nabla \cdot \hat{\bf v},p\right>  
+ \left< {\cal L}^\dag_{\bf U}( \hat{\bf v},\hat{q}) ,{\bf u}\right> + \left< \nabla \cdot \hat{\bf v},p\right> . 
 \ee
-It can be shown (Schmid \& Henningson, 2001) that the adjoint eigenvalues $\lambda^\dag$ are the complex conjugates of the direct eigenvalues ($\lambda$).
+It can be shown \cite{SchmidHenningson2001} that the adjoint eigenvalues $\lambda^\dag_k$ are the complex conjugates of the direct eigenvalues $\lambda_k$.
 
@@
 In effect, the scalar product used in the definition of the weak formulation and that appearing in the definition of adjoint being the same, the weak formulations of both problems are thus identical when exchanging the test functions and the unknown functions.
-Thus the matricial form of the discretized version of (\ref{EigenAdj} is deduced from the one of the direct problem by a simple transpose of the matrix :
+Thus the matricial form of the discretized version of (\ref{EigenAdj}) is deduced from the one of the direct problem by a simple (Hermitian) transpose of the matrix :
 \be{Eigen_Adj_matricial}
-\overline{\lambda}^\dag B \hat{X}\dag = A^T \hat{X}\dag.
+\overline{\lambda}^\dag B \hat{X}^\dag = A^T \hat{X}^\dag.
 \ee
 
-Adjoint eigenmodes are a powerful tool for investigating problems such as transient growth, control, sensitivity (see the reviews of Chomaz, Schmid, Luchini).
+Adjoint eigenmodes are a powerful tool for investigating problems such as receptivity, transient growth, control and sensitivity (see the reviews of \cite{Jmc2005}, \cite{Ps2007}, \cite{LucBott2014}).
 The simplest physical interpretation of an adjoint eigenmode is as follows : it corresponds to the initial condition which has maximum projection along the direction of the corresponding eigenmode.
@@
 \frac{ \left< \hat{\bf u}^\dag, {\bf u}_i\right>}{\left<\hat{\bf u}^\dag, \hat{\bf u}\right>} 
-e^{\lambda t} \hat{\bf u}  
-$$.
+e^{\lambda t} \hat{\bf u}.
+$$
 The choice ${\bf u}_i = \hat{\bf u}^\dag$ is the initial condition of norm unity which maximizes the first factor in this expression.
@@
 
-The adjoint eigenmode also allows to deduce a quantity called the {\em structural sensitivity}  and defined as $S(x,y) = || \hat{\bf u}^\dag||  ||\hat{\bf u}||$ which has became popular in the recent years.
+The adjoint eigenmode also allows us to introduce the so-called {\em structural sensitivity tensor } that is defined as 
+\be{Structursens} 
+{\bf{S}}({\bf{x}}) = \frac{|| \hat{\bf u}^\dag|| \,\, ||\hat{\bf u}|| }{{\left<\hat{\bf u}^\dag, \hat{\bf u}\right>}},
+\ee 
+which has became popular in the recent years.
 %is called the structural sensitivity of the eigenmode. 
 This quantity is a direct and practical measure of the effect of perturbations of the linear operator on the eigenvalue.
-The region of the flow where $S(x,y)$ is thus the region where the instability mechanism originates, and is often referred to as the {\em wavemaker region}
+The region of the flow where ${\bf{S}}({\bf{x}})$ reaches its maximum values is, thus, the region where the instability mechanism originates, and is often referred to as the {\em wavemaker region}.
 
@@
 
-When it comes to the numerical resolution of generalized eigenvalue problems such as $A X = \lambda B X$ (or its adjoint version), several methods are possible.
+When it comes to the numerical resolution of generalized eigenvalue problems such as $A X = \lambda B X$ (or its adjoint version (\ref{Eigen_Adj_matricial}) ), several methods are possible.
 Direct methods to compute the whole spectrum are both costly prohibitive and useless.
-A popular alternative is iterative methods which allow to compute a limited set of eigenvalues located in the vicinity of a
+A popular alternative is the use of iterative methods which allow us to compute a limited set of eigenvalues located in the vicinity of a
 "shift" value $\lambda_{shift}$. The simplest version of this method is the simple shift-invert iteration, which consists of solving iteratively the system
 $$
-X^{n} =  (A- \lambda_{shift} B)^{-1} B X^{n-1}
+X^{n} =  (A- \lambda_{shift} B)^{-1} B X^{n-1}.
 $$ 
-It is easy to show that this quickly asymptotes to $X^{n+1} \approx ({\lambda^*}^{-1})^n \hat{X}$
+It is easy to show that this iterative procedure quickly asymptotes to $X^{n+1} \approx ({\lambda^*}^{-1})^n \hat{X}$
 where $\hat{X}$ is the eigenmode with largest ${\lambda^*}^{-1}$ (i.e. the one with eigenvalue $\lambda$ closest to the shift).
 
-When one has a good estimation of the eigenvalue, this method converges very rapidly and is very efficient, but it can only provide a single eigenvalue.
-If one wants to compute a larger number of eigenvalues, one can revert to a generalized version of iterative methods, called Arnoldi methods.
-The shift-invert version of the Arnoldi method is in fact the most commonly  used method of the current time and is at the basis of both the popular matlab solver eigs and the build-in eigenvalue solver of FreeFem.
+When a good estimation of the eigenvalue is available, this method converges very rapidly and is very efficient, but it can only provide a single eigenvalue.
+If we want to compute a larger number of eigenvalues, we can revert to a generalized version of iterative methods, called Arnoldi methods\cite{Arnoldi51}.
+The shift-invert version of the Arnoldi method is in fact the most commonly used method of the current time and is at the basis of both the popular matlab function {\tt{eigs}} and the eigenvalue solver of FreeFem (i.e.
+ARPACK++).
 Our implementation in StabFem allows to chose between single eigenvalue computation (power method) and multiple eigenvalue computation (Arnoldi).
@@
 %\vspace{-1.cm}
-\caption{Adapted mesh $(a)$  and base flow (axial velocity component) ($b$) for the flow over a cylinder at $Re=Re_c = 46.7$.}
+\caption{Adapted mesh $(top)$  and base flow (axial velocity component) ($bottom$) for the flow over a cylinder at $Re=Re_c = 46.7$.}
 \label{fig:Baseflow}
@@
 \includegraphics[width=.9 \linewidth]{Cylinder_Lx_baseflow.png}
-\includegraphics[width=.9 \linewidth]{Cylinder_Cx_baseflow.png}
+\includegraphics[width=.9 \linewidth]{Cylinder_Drag_baseflow.png}
 \caption{Recirculation length $L_x$ $(a)$  and drag $C_x$ ($b$) of the base flow over a cylinder as function of $Re$.}
@@
 %Following Sipp \& Lebedev,
-The most common procedure is to decompose the domain into several parts with different grid densities ; for instance for the wake of a cylinder, we will design a near-wall region with very small  size, a "wake" region with intermediate mesh size, and an outer region with large mesh size.
+The most common procedure is to decompose the domain into several parts with different grid densities; for instance for the wake of a cylinder, we will design a near-wall region with very small  size, a "wake" region with intermediate mesh size, and an outer region with large mesh size.
 The inconvenient is that the design relies on an a priori expectation of the regions where gradients will be large.
@@
 In our implementation, we used an automatic mesh adaptation method. %which provides an optimal mesh adapted to the structure of the flow. 
-The implementation relies on the AdaptMesh procedure of the FreeFem++ software. This procedure is detailed in detail in ref. []. In short, 
-the classical Delaunay-Voronoi algorithm produces a mesh with gridpoint distribution specified by a {\em Metric } matrix $\cal M$.
-The AdaptMesh algorithm consists of using as a metric the {\em Hessian} (second-order spatial derivative) of an objective function $u_h$ defined over the domain, i.e.
+The implementation relies on the AdaptMesh procedure of the FreeFem++ software. This procedure is detailed in detail in ref. \cite{adapt}. 
+In short, the classical Delaunay-Voronoi algorithm produces a mesh with gridpoint distribution specified by a {\em Metric } matrix $\cal M$.
+The AdaptMesh algorithm consists of using as a metric the {\em Hessian} (second-order spatial derivatives) of an objective function $u_h$ defined over the domain, i.e.
 ${\cal M} = \nabla \nabla u_h$.
@@
 
-SECTION TO BE COMPLETED.
+\paragraph{Problem description}
+Here, we consider the two-dimensional flow past a circular cylinder. All flow quantities are normalized using 
+the uniform incoming velocity $U_{\infty}$ and the cylinder diameter $D$, which are the characteristic velocity and 
+length scales used for the definition of Reynolds number $Re= U_{\infty} D / \nu$.
+The origin of the cartesian frame of reference is considered located on the cylinder axis, the x-axis is chosen to be parallel to the incoming free-stream velocity while the y-axis with the cross-stream velocity.
+The dimensions of the computational domain are the following: $-40 \le x/D \le 80$ and $-40 \le y/D \le 40$.
+We impose a no-slip condition $(u=0,v=0)$ on the cylinder surface (${\Gamma_{cil}}$), a uniform velocity $(u=1,v=0)$ at the inflow 
+$x/D=-40$ and a no-stress condition at the outlet $x/D=80$ and on the lateral boundaries of the computational domain $y/D=\pm 40$.
 
-\paragraph{Problem description}
-
-Cylinder of unit diameter (radius $r=1/2$), velocity $U = 1$ at inlet.
-
-Domain dimension $[-40,80]x[0,40]$. No-stress conditions at outlet AND LATERAL BOUNDARY.
-
-Definition of lift and drag operators :
+%Domain dimension $[-40,80]x[0,40]$. No-stress conditions at outlet AND LATERAL BOUNDARY.
+The hydrodynamic loads can be obtained by integrating the stress tensor over the cylinder surface.
+In particular, the hydrodynamic lift and drag forces read
 
 \be{drag}
-F_x ({\bf u},p) = 
- \int_{\Gamma_w} \left[-p {\bf n} + \frac{2}{Re} {\bf D}({\bf u}) \cdot {\bf n} \right]   \cdot {\bf e_x} 
+D = F_x ({\bf u},p) = 
+ \int_{\Gamma_{cil}} \left[-p {\bf n} + \frac{2}{Re} {\bf D}({\bf u}) \cdot {\bf n} \right]   \cdot {\bf e_x} d\ell
 \ee
@@
 \be{lift}
-F_y ({\bf u},p) = 
- \int_{\Gamma_w} \left[-p {\bf n} + \frac{2}{Re} {\bf D}({\bf u}) \cdot {\bf n} \right]   \cdot {\bf e_y} 
+L = F_y ({\bf u},p) = 
+ \int_{\Gamma_{cil}} \left[-p {\bf n} + \frac{2}{Re} {\bf D}({\bf u}) \cdot {\bf n} \right]   \cdot {\bf e_y} d\ell. 
 \ee
@@
 
+Let's consider now the matlab code reported in figure \ref{Listing2}.
 First we build an initial mesh (line 1), and compute base flow solutions for increasing values of the Reynolds number up to $Re = 60$ (lines 3-9).
 Then we perform the mesh adaptation with the structural sensitivity, as explained in a previously (line 13). 
-The resulting mesh is used for the rest of the computation presented in this paper (except for displaying the eigenmode in figure 4$a$). 
+The resulting mesh, depicted in figure \ref{fig:Baseflow}, is used for the rest of the computations presented in this paper (except for displaying the eigenmode in figure 4$a$). 
 Appendix A presents additional test regarding mesh convergence, and demonstrate that results obtained with the resulting mesh are trustable within $1\%$ accuracy for the eigenvalue, while requiring a very reasonable number of grid points compared to previous studies of this problem.
@@
 
-Having thus produced an convenient mesh, we can now illustrate the properties of the base flow as function of Reynolds number.
-Figure (\ref{Listing2}) shows how to compute and plot with StabFem the two most commonly studied quantities, namely the drag coefficient $C_x(Re)$  and the recirculation length $Lx(Re)$, namely the location of the stagnation point at the rear of the recirculation region.
+Having thus produced a convenient mesh, we can now illustrate the properties of the base flow as function of Reynolds number.
+Figure \ref{Listing2} shows how to compute and plot with StabFem the two most commonly studied quantities, namely the recirculation length $Lx(Re)$, i.e.
+the location of the stagnation point at the rear of the recirculation region, and the drag coefficient $C_x(Re)$.
 Note that the object \verb|baseflow| is defined as a structure with fields \verb|Drag| and \verb|Lx|. 
-The resulting plots are given in figure (\ref{fig:LxandDrag}), and are in good agreement with known results for this classical problem.
+The resulting plots are given in figure \ref{fig:LxandDrag}, and are in good agreement with known results for this classical problem.
 In particular, for low Reynolds, the recirculation $L_x(Re)$ is equal to $0.5$ (which is the radius of the cylinder) indicating the absence of a recirculation region.
@@
 \begin{figure}
+\includegraphics[width=.9 \linewidth]{Cylinder_Sigma_Re.png}
+\includegraphics[width=.9 \linewidth]{Cylinder_Strouhal_Re.png}
+\caption{Growth rate $\sigma$ $(a)$  and Strouhal number $St = (a \omega)/(2\pi U_{\infty})$ ($b$) as function of Reynolds number}
+\label{fig:SigmaOmega}
+\end{figure}
+
+\begin{figure}
 %\vspace{-.5cm}
@@
 %\vspace{-.5cm}
-\caption{Eigenmode $(a)$  (axial velocity component),  Adjoint mode $(b)$ and structural sensitivity ($c$) for the cylinder's wake at $Re=Re_c = 46.7$.}
+\caption{Contour plot of the streamwise velocity component: $(a)$ (Direct) Eigenmode; $(b)$ Adjoint mode and ($c$) Structural sensitivity field for the cylinder's wake at $Re=Re_c = 46.7$.}
 \label{fig:Eigenmode}
-\end{figure}
-
-\begin{figure}
-\includegraphics[width=.9 \linewidth]{Cylinder_Sigma_Re.png}
-\includegraphics[width=.9 \linewidth]{Cylinder_Strouhal_Re.png}
-\caption{Growth rate $\sigma$ $(a)$  and Strouhal number $St = (a \omega)/(2\pi U_0)$ ($b$) as function of Reynolds number}
-\label{fig:SigmaOmega}
 \end{figure}
@@
 
-Figure \ref{fig:Eigenmode} : description of eigenmode.
+We investigate the stability of the base flow fields by performing a parametric study of the eigenproblem 
+(\ref{Eigen_matricial}). In this way, we determine the critical Reynolds number $Re_c$ at with the steady base flow
+first becomes unstable: to this end it is useful to remember that a flow state is 
+linearly unstable when the real part of 
+the leading eigenvalue, i.e. the growth rate, is positive. 
+Figure \ref{fig:SigmaOmega} shows growth rate and the Strouhal number 
+$St=a\omega/2 \pi U_{\infty}$ as a function of the 
+Reynolds number. It is easy to check that the critical Reynolds number is about 47 
+for the first mode. 
+The associated direct eigenmode is depicted in figure \ref{fig:Eigenmode}. The 
+spatial structure of this mode 
+extends downstream of the bluff body and is characterized by streamwise 
+extended spatial disturbances. 
+On the other hand, the adjoint mode is highly localized near the cylinder 
+on the upper (and lower) side of the body surface. 
+We recall that the adjoint field provides useful information about the mechanism to
+flow receptivity to momentum forcing and mass injection.
+We note also that this receptivity decays rapidly both upstream and downstream 
+of the bluff body.
 
-Figure \ref{fig:SigmaOmega} : growth rates/Strouhal.
+The structural sensitivity field displayed in figure \ref{fig:Eigenmode}c)
+is obtained by evaluating eq. \ref{Structursens}.
+In particular, we plot the spectral norm of the sensitivity tensor, it 
+gives the maximum possible coupling among the velocity components. 
+This spatial map can be used to identify the flow region where the 
+instability mechanism acts.
 
@@
 
-In this section, to simplify the notations, The Navier-Stokes equations will be written symbolically as 
-$\partial_t  {\bf u }  = NS(  {\bf u } )$, therefore dropping the systematic reference of the incompressibility constraint and associated pressure field.
+We turn now to analyze how nonlinear effects can be considered in the framework 
+of global stability analysis. 
+Here, we symbolically write the Navier-Stokes system as $\partial_t {\bf u} = {\cal 
+NS} ({\bf u};p)$, therefore dropping the systematic reference of the 
+incompressibility constraint and associated pressure field.
 
@@
 Attempts to on a rigourous basis
-In the past decade, efforts have been devoted to extend the range of validity of global approaches into the nonlinear régime for $Re>Re_c$, with the double objective to describe the properties of the limit cycle reached after saturation and to derive amplitude equations describing the transitent dynamics towards this cycle.
- The first milestone in that direction is the work of Sipp \& Lebedev who used a weakly nonlinear development in terms of the distance to the threshold $Re-Re_c$.
+In the past decade, efforts have been devoted to extend the range of validity of global approaches into the nonlinear regime for $Re>Re_c$, with the double objective to describe the properties of the limit cycle reached after saturation and to derive amplitude equations describing the transitent dynamics towards this cycle.
+ The first milestone in this direction is the work of Sipp \& Lebedev \cite{SippLebedev} who used a weakly nonlinear development in terms of the distance to the threshold $Re-Re_c$.
 However, although derived on rigorous grounds, the weakly nonlinear development has a very limited range of validity and already fails for $Re\ge47$.
-More recently,  Mantic-lugo et al.  proposed an alternative approach termed {\em Self-consistent model} which succeeds in predicting the dynamics up to $Re =120$ and more. 
+More recently,  Manti\v{c}-Lugo et al \cite{MLugo2014} proposed an alternative approach termed {\em Self-consistent model} which succeeds in predicting the dynamics up to $Re =120$ and more. 
 This model was build as a linear stability approach build on a {\em mean flow} which includes a 
@@
 
-In the next sections we thus successively present the weakly nonlinear model, the self-consistent model and eventually the harmonic-balance model, and propose a direct resolution method. 
+In the next sections, we thus successively present the weakly nonlinear model, the self-consistent model and eventually the harmonic-balance model, and propose a direct resolution method. 
 %The relation with the initial method of Mantic-Lugo et al. will be discussed afterwards.
@@
 \paragraph{Weakly nonlinear model}
-
-We give here a brief account of the Weakly nonlinear model of Sipp \& Lebedev, also discussed by
-Gallaire et al.
-(FDR 2016).
-The derivation is based on a multiple scale decomposition based on the parameter $\epsilon^2 = 1/Re - 1/Re_c$, and the slow time scale $\tau = \epsilon t$.
-The starting point is an expansion of the flow under the following form :
-
-\begin{eqnarray}
-{\bf u} &=& {\bf u}_{bc} + \epsilon \left[ A_{wnl} (\tau) \hat{\bf u} e^{i \omega_c t} + c.c. \right] \label{WNL1}\\
-&+& \epsilon^2 \left[ {\bf u}_\epsilon + |A_{wnl}|^2  {\bf u}_{2,0} + \left(  A_{wnl}^2 {\bf u}_{2,2} e^{2 i \omega_c t} + c.c. \right) \right] + {\cal O}( \epsilon ^3)
-\nonumber
-\end{eqnarray}
-where ${\bf u}_{bc}$ is the base flow at the threshold $Re_c$, $\hat{\bf u}$ the neutral eigenmode at $Re_c$, $A_{wnl}(\tau)$ a slowly varying amplitude.
-The order $\epsilon^2$ contains three terms respectively computed as the solutions of the following linear problems :
-\begin{eqnarray}
-NSL_{{\bf u}_bc} ({\bf u}_\epsilon) + 2 \nabla \cdot {\bf D}( \hat{\bf u}) &=&0,\\
-NSL_{{\bf u}_bc} ({\bf u}_{2,0}) &=& {\cal C}(\hat{\bf u}, ,\overline{\hat{\bf u}}),\\
-NSL_{{\bf u}_bc} ({\bf u}_{2,2}) - 2 i \omega_c {\bf u}_{2,2}  &=& \frac{1}{2} {\cal C}(\hat{\bf u},\hat{\bf u}).
- \end{eqnarray}
-
-Finally compatibility conditions are imposed at order 3 leading to an amplitude equation with the following
-form :
-\be{WNL3}
-\frac{\partial A_{wnl} }{\partial \tau} = \Lambda A_{wnl} - (\nu_0+\nu_2)  |A_{wnl}|^2 A_{wnl}
-\ee
-With 
-\begin{eqnarray}
-\Lambda &=& \frac{ \left< {\hat{\bf u}}^\dag, 
-\left( {\cal C}({\bf u}_\epsilon, \hat{\bf u}) - 2 \nabla \cdot  {\bf D}( \hat{\bf u}) \right) \right>}
-{  \left<  \hat{\bf u}^\dag,\hat{\bf u} \right> },\\
-\nu_0 &=& -\frac{ \left< {\hat{\bf u}}^\dag,  {\cal C}({\bf u}_{20}, \hat{\bf u} ) \right>}
-{  \left<  \hat{\bf u}^\dag,\hat{\bf u} \right> },\\
-\nu_2 &=& -\frac{ \left< {\hat{\bf u}}^\dag,  {\cal C}({\bf u}_{22}, \overline{\hat{\bf u}})  \right>}
-{  \left<  \hat{\bf u}^\dag,\hat{\bf u} \right> }.
- \end{eqnarray}
-
-If one is interested in the amplitude of the limit cycle, we have 
-$|A_{wnl}| = \sqrt{\Lambda_r/(\nu_{0,r}+\nu_{2,r})}$ and eventually, reintroducing the scaling :
-\be{ANL} 
-|A| =  \epsilon |A_{wnl}| = \frac{\Lambda_r}{\nu_{0,r}+\nu_{2,r} } \sqrt{\frac{1}{Re_c}-\frac{1}{Re}}
-\ee
-The frequency of the limit cycle is given by
-\be{omegaWNL} 
-\omega = \omega_c + 
-\left( \Lambda_r - \Lambda_i \frac{\nu_{0,i}+\nu_{2,i} }{\nu_{0,r}+\nu_{2,r} } \right) 
-\left(\frac{1}{Re_c}-\frac{1}{Re}\right)
-\ee
-
-As can be seen on figures 6 and 7,  the approach gives good prediction in the immediate vicinity of $Re_c$, but deviation appears very rapidly and disagreement is already large at $Re=48$ (although, as discussed by Gallaire et al.
-and also observed by Tchoufag et al.
-(PRL), a convenient definition of the $\epsilon$ improves the results).
-
-\paragraph{Self-Consistent approach}
-
-We now discuss the self-consistent approach as introduced by Mantic-Lugo et al.
-The starting point of this model is a pseudo-eigenmode expansion of the flow as follows :
-
-\be{SC}
-{\bf u } = {\bf u }_m + A \left[ \tilde{{\bf u }}_1 e^{\sigma_{sc} t + i \omega_{sc} t} +   \tilde{\bf u }_{-1} e^{\sigma_{sc} t  -i \omega_{sc} t} \right]
-\ee
-
-Where ${\bf u }_m$ is a {\em mean flow} defined by phase-averaging over the cycle, $\tilde{{\bf u }}_1$ is a pseudo-eigenvector which is normalized by the condition  $||\tilde{{\bf u }}_1|| = 1/\sqrt{2}$,
- $A$ is an amplitude parameter directly related to the energy of the oscillating flow, and $\lambda = \sigma_{SC} + i \omega_{SC}$ is a pseudo-eigenvalue which depends upon the parameter $A$.
-
-\be{HBEq0}
-NS(  {\bf u }_m ) - A_{sc}^2 {\cal C}( \tilde{{\bf u }}, \overline{\tilde{\bf u }}) = 0,
-\ee
-\be{HBEq1}
-(\sigma_{sc} + i \omega_{sc}) \tilde{{\bf u }} =  NSL_{{\bf u }_m}(  \tilde{{\bf u }} ),
-\ee
-\be{BBEqnorm}
-|| \tilde{{\bf u }}|| = \frac{1}{\sqrt{2}}.
-\ee
-
-% The mean flow is then governed by the same equation
-%\ref{HBEq0}) written above, while $\tilde{{\bf u }}_1$ is the solution of an eigenvalue problem with the same form as  (\ref{HBEq1}) except that $i \omega$ is replaced by $\sigma_{SC} + i \omega_{SC}$.
-The self-consistent model has the following properties :
-\begin{itemize}
-\item[-] For $A \ll 1$ it is equivalent to the linear eigenvalue problem (\ref{LEP}), and the generalized eigenvalue coincides with the one predicted by linear stability : $\sigma_{SC} + i \omega_{SC} = \sigma_{lin} + i \omega_{lin}$.
-\item[-] For $\sigma_{SC}=0$ (corresponding to a specific choice of the amplitude $A=A_c$),  the expansion (\ref{SC}) is equivalent to a Fourier decomposition of the limit cycle with only two term retained.
-\item[-] For $0<A<A_c$, the resolution leads to a relation $\sigma_{SC}(A) ; \omega_{SC}(A)$
-such that $0< \sigma_{SC}(A) < \sigma_{lin}$.
- Although in this case the expansion \ref{SC} cannot represent the flow for all $t$, Mantic-Lugo et al.
-argued that the relation between $\sigma_{SC}$ and $A$ can be used to build an amplitude equation which captures the transient approach to the limit cycle.
-\end{itemize}
-
-\paragraph{Harmonic balance : equations and procedure }
-
-As discussed above, the Self-Consistent model was initially presented as the authors as a rational way to explain the dynamics in terms of a stability analysis of the {\em mean flow}.
-Furthermore, the resolution method presented by the authors, which involves a double iteration loop, is not easy to implement and not particularly efficient.
-
-If one is only interested by the properties of the limit cycle and not the transient, the model is actually equivalent to a Fourier series, and amenable to a more direct resolution method. 
-We thus start with a Fourier decomposition of the limit cycle under the form :
-\be{HB}
-{\bf u } = {\bf u }_0 + {\bf u }_1 e^{i \omega t} +   {\bf u }_{-1} e^{-i \omega t}
-\ee  
-Here ${\bf u }_0$ is the mean flow (averaged over time),  ${\bf u }_1$ is the mode
-(fourrier component at the fundamental frequency), ${\bf u }_{-1} = \overline{{\bf u }_1}$ is its complex conjugate, and $\omega$ is the (real) oscillation frequency of the limit cycle (which is not known a priori).
-Injecting this ansartz into the Navier-Stokes equations and taking the mean value and first Fourier component leads to the following coupled equations :
-\be{HBEq0}
-NS(  {\bf u }_0 ) - {\cal C}( {\bf u }_1, \overline{\bf u }_1) = 0,
-\ee
-\be{HBEq1}
-i \omega {\bf u }_1 =  NSL_{{\bf u }_0}(  {\bf u }_1 ).
-\ee
-
-Note that contrary to the SC model, the ${\bf u }_1$ component is not normalized.
-The amplitude $A$ can easily be computed a posteriori as $A = \sqrt{2 ||{\bf u }_1||}$.
-On the other hand, the Fourier description of the limit cycle is invariant with respect to the phase $\phi$ (i.e.
-the equations are unchanged when replacing $[ {\bf u }_1,  {\bf u }_{-1}] $ by  $[ {\bf u }_1 e^{i\varphi},  {\bf u }_{-1}  e^{-i\varphi}] $).
-To allow resolution we thus need an extra equation to fix this phase.
-Several choices are possible, but a convenient one is to set the lift associated with the imaginary part of ${\bf u }_1$ to lift.
-Physically, this means that the instant $t=0$ will correspond to a maximum of lift.
-This condition reads :
-\be{HBphase}
-\Im F_y({\bf u}_1) =0
-\ee
-
-Mathematically, the problem $\ref{HBEq0,HBEq1,HBphase}$ for the unknown $[{\bf u }_0, {\bf u }_{1}, \omega]$ is well posed, and can be solved using a Newton iteration just as explained for the base flow in section 2.
-To allow resolution, we separate the mode into real and imaginary part, by writing ${\bf u }_1 = {\bf u }_{1,r} +  i {\bf u }_{1,i} $.
-We then assume that we know a 'guess' 
-$$
-[{\bf u }_0, {\bf u }_{1,r}, {\bf u }_{1,i}, \omega] = 
- [{\bf u }_0^g, {\bf u }_{1,r}^g, {\bf u }_{1,i}^g, \omega^g]
-+ [\delta {\bf u }_0, \delta {\bf u }_{1,r}, \delta {\bf u }_{1,i}, \delta \omega]
-$$.
-
-Injecting and developing up to linear order leads to the following 
-\begin{equation}
-\begin{array}{ll}
-\displaystyle
-& NS(  {\bf u }_0^g ) - [ {\cal C}( {\bf u }_{1,r}^g,{\bf u }_{1,r}^g) +  {\cal C}( {\bf u }_{1,i}^g,{\bf u }_{1,i}^g) ]
-\\
-+& NSL_{{\bf u }_0^g}(\delta {\bf u }_0) - 2 [ {\cal C}( {\bf u }_{1,r}^g,\delta {\bf u }_{1,r}) +  {\cal C}( {\bf u }_{1,i}^g,\delta {\bf u }_{1,i}) ] = 0;
-\\
-\\
-&  NSL_{{\bf u }_0^g}( {\bf u }_{1,r}^g) - \omega^g {\bf u }_{1,i}^g 
- \\
-  +& NSL_{{\bf u }_0^g}( \delta {\bf u }_{1,r}^g) 
-   -  {\cal C}( \delta {\bf u }_{0}^g, {\bf u }_{1,r})
-   - \delta \omega^g \delta {\bf u }_{1,i}^g 
- - \omega^g \delta {\bf u }_{1,r} = 0 ;
- \\
-\\
-&  NSL_{{\bf u }_0^g}({\bf u }_{1,i}^g) + \omega^g {\bf u }_{1,i}^g
- \\
-  +& NSL_{{\bf u }_0^g}( \delta {\bf u }_{1,i}^g) 
-  -  {\cal C}( \delta {\bf u }_{0}^g, {\bf u }_{1,i}) 
-  + \delta \omega^g \delta {\bf u }_{1,i}^g 
-+ \omega^g \delta {\bf u }_{1,r} = 0 ;
-\\
-\\
-& F_y({\bf u }_{1,i}^g) + F_y(\delta {\bf u }_{1,i}) = 0.
- \end{array}
-\end{equation}
-
-After discretization, this leads to a linear problem with the form $A X = Y$ where $X$ is the discretized version of the unknowns  $[\delta {\bf u }_0, \delta {\bf u }_{1,r}, \delta {\bf u }_{1,i}, \delta \omega]$, and $A$ is a matrix of dimension $3 N_{dof} +1$.
-
-%\ref{HBEq0,HBEq1,HBphase}
-
-\paragraph{Implementation and results for cylinder}
 
@@
 end
+
 \end{lstlisting}
 \normalsize
-
 \caption{Illustration of the procedure for nonlinear calculations using StabFem (from script {\em SCRIPT\_CYLINDER.m}. }
@@
 
-Figure \ref{fig:listingNL}, which is again extracted from the script 
-\verb|SCRIPT\_CYLINDER\_DEMO.m|, illustrate the sequence of commands to perform both the weakly nonlinear and the harmonic balance studies for the case of a cylinder.
-On line 1, we first determine the instability threshold, and the corresponding base flow and eigenmode\footnote{This routine uses Newton iteration to directly compute the base flow, the eigenmode, the frequency and the critical Reynolds.
-The algorithm is very similar to the one presented for the HB, with an additional unknown (Re) and an additional constraint (normalization of the mode).
-The interested reader should reconstruct easily the whole procedure from the code provided.}
-On line 2 we then compute all the terms and coefficients of the wnl model.
-Then we construct  vectors to store the frequency and the amplitude of the limit cycle in the range $Re = [47.5-100]$.
-Note that for the computation at $Re=47.5$ we need a guess for the amplitude, which is deduced from the weakly nonlinear approach on line 9.
-In the sequel of the loop no guess value is prescribed, hence the solver uses continuation.
+We give here a brief account of the weakly nonlinear model of Sipp \& 
+Lebedev\cite{SippLebedev}, also discussed by
+Gallaire et al. \cite{FDR2016}. The derivation is based on a multiple scale 
+decomposition based on the parameter $\epsilon^2 = 1/Re - 1/Re_c$, and the slow 
+time scale $\tau = \epsilon t$. They started by considering the following asymptotic expansion of the flow state ${\bf{q}}=({\bf{u}},p)$ :
+\begin{eqnarray}
+{\bf q} &=& {\bf q}_{bc} + \epsilon \left[ A_{wnl} (\tau) \hat{\bf q} e^{i \omega_c t} + c.c. \right] \label{WNL1}\\
+&+& \epsilon^2 \left[ {\bf q}_\epsilon + |A_{wnl}|^2  {\bf q}_{2,0} + \left(  A_{wnl}^2 {\bf q}_{2,2} e^{2 i \omega_c t} + c.c. \right) \right] + {\cal O}( \epsilon ^3)
+\nonumber
+\end{eqnarray}
+where ${\bf q}_{bc}$ is the base flow at the threshold $Re_c$, $\hat{\bf q}$ the neutral 
+eigenmode at $Re_c$, $A_{wnl}(\tau)$ a slowly varying amplitude.
+Substituting the above expansion (\ref{WNL1}) into the Navier-Stokes equations and grouping terms 
+multiplied by the same power of $\epsilon$, a hierarchy of equations is obtained.
+The order $\epsilon^2$ contains three terms respectively computed as the solutions of the following linear problems :
+\begin{eqnarray}
+{\cal L}_{{\bf u}_{bc}} ({\bf u}_\epsilon) + 2 \nabla \cdot {\bf D}( \hat{\bf u}) &=&0,\\
+{\cal L}_{{\bf u}_{bc}} ({\bf u}_{2,0}) &=& {\cal C}(\hat{\bf u},\overline{\hat{\bf u}}),\\
+{\cal L}_{{\bf u}_{bc}} ({\bf u}_{2,2}) - 2 i \omega_c {\bf u}_{2,2}  &=& \frac{1}{2} {\cal C}(\hat{\bf u},\hat{\bf u}).
+ \end{eqnarray}
 
-\begin{figure}
-\begin{center}
-\includegraphics[width=.9 \linewidth]{Cylinder_Lx_Re_HB.png}
-\includegraphics[width=.9 \linewidth]{Cylinder_Cx_Re_HB.png}
-\end{center}
-\caption{Harmonic-balance results : mean-flow characteristics}
-\label{fig:HB}
-\end{figure}
+Finally, compatibility conditions are imposed at order $\epsilon^3$ leading to an amplitude equation with the following
+form :
+\be{WNL3}
+\frac{\partial A_{wnl} }{\partial \tau} = \Lambda A_{wnl} - (\nu_0+\nu_2)  |A_{wnl}|^2 A_{wnl},
+\ee
+where 
+\begin{eqnarray}
+\Lambda &=& \frac{ \left< {\hat{\bf u}}^\dag, 
+\left( {\cal C}({\bf u}_\epsilon, \hat{\bf u}) - 2 \nabla \cdot  {\bf D}( \hat{\bf u}) \right) \right>}
+{  \left<  \hat{\bf u}^\dag,\hat{\bf u} \right> },\\
+\nu_0 &=& -\frac{ \left< {\hat{\bf u}}^\dag,  {\cal C}({\bf u}_{20}, \hat{\bf u} ) \right>}
+{  \left<  \hat{\bf u}^\dag,\hat{\bf u} \right> },\\
+\nu_2 &=& -\frac{ \left< {\hat{\bf u}}^\dag,  {\cal C}({\bf u}_{22}, \overline{\hat{\bf u}})  \right>}
+{  \left<  \hat{\bf u}^\dag,\hat{\bf u} \right> }.
+ \end{eqnarray}
+
+If one is interested in the amplitude of the limit cycle, we have 
+$|A_{wnl}| = \sqrt{\Lambda_r/(\nu_{0,r}+\nu_{2,r})}$ and eventually, reintroducing the scaling :
+\be{ANL} 
+|A| =  \epsilon |A_{wnl}| = \frac{\Lambda_r}{\nu_{0,r}+\nu_{2,r} } \sqrt{\frac{1}{Re_c}-\frac{1}{Re}}.
+\ee
+The frequency of the limit cycle is given by
+\be{omegaWNL} 
+\omega = \omega_c + 
+\left( \Lambda_r - \Lambda_i \frac{\nu_{0,i}+\nu_{2,i} }{\nu_{0,r}+\nu_{2,r} } \right) 
+\left(\frac{1}{Re_c}-\frac{1}{Re}\right).
+\ee
+
+Figure \ref{fig:listingNL}, which is extracted from the script 
+\verb|SCRIPT_CYLINDER_DEMO.m|, illustrate the sequence of commands to 
+perform the weakly nonlinear study for the cylinder wake.
+On line 1, we first determine the instability threshold, and the corresponding base flow 
+and eigenmode\footnote{This routine uses Newton iteration to directly compute the 
+base flow, the eigenmode, the frequency and the critical Reynolds. The algorithm is 
+very similar to the one presented for the HB, with an additional unknown (Re) and an 
+additional constraint (normalization of the mode). The interested reader should 
+reconstruct easily the whole procedure from the code provided.}.
+On line 2, we then compute all the terms and coefficients of the WNL model. 
+%After that, 
+%we construct  vectors to store the frequency and the amplitude of the limit cycle in the 
+%range $Re = [47.5-100]$. Note that for the computation at $Re=47.5$, we need a guess 
+%for the amplitude, which is deduced from the weakly nonlinear approach on line 9. In 
+%the sequel of the loop no guess value is prescribed, hence the solver uses 
+%continuation.
+
+As can be seen on figure \ref{fig:Comp2},  the approach gives good prediction in the immediate vicinity of $Re_c$, but deviation appears very rapidly and disagreement is already large at $Re=48$ (although, as discussed by Gallaire et al.?
+and also observed by Tchoufag et al.
+\cite{Tchoufag2015}, a convenient definition of the $\epsilon$ improves the results).
 
@@
 \includegraphics[width=.9 \linewidth]{Cylinder_Strouhal_Re_HB.png}
+\includegraphics[width=.9 \linewidth]{Cylinder_Cx_Re_HB.png}
 \includegraphics[width=.9 \linewidth]{Cylinder_Cy_Re_SC.png}
@@
 \end{center}
-\caption{Harmonic-balance results : characteristics of the limit cycle.
-NOTE THAT THE AMPLITUDE IS NOTABLY LOWER THAN IN MANTIC-LUGO. TO BE EXPLAINED.
+\caption{Comparison between the weakly nonlinear results (WNL) and the harmonic 
+balance data (HB). We report also the Strouhal number computed by using the 
+classical linear stability theory (Linear) and the base flow (BF) $C_x$.
+%c_x should be consistent with the drag definition given at beginning
 }
-\label{fig:HB}
+\label{fig:Comp2}
 \end{figure}
 
-The whole results are presented in figures 8 (mean-flow properties) and 9 (oscillating mode properties).
-
-%Barkley [] and Leontini [] have
-
+\paragraph{Self-Consistent approach}
 \begin{figure}
@@
 \end{center}
-\caption{SELF CONSISTENT APPROACH FOR THE WAKE OF A CYLINDER, $Re = 100$.}
+\caption{Self-consistent approach for the wake of a cyrcular cilinder: results at $Re = 
+100$.}
 \label{fig:SC100}
 \end{figure}
+We now briefly review the self-consistent approach as introduced by Manti\v{c}-Lugo et 
+al \cite{MLugo2014}. The authors adopted a pseudo-eigenmode expansion of the flow 
+as follows: 
+\be{SC}
+{\bf u } = {\bf u }_m + A_{sc} \left[ \tilde{{\bf u }}_1 e^{\sigma_{sc} t + i \omega_{sc} t} +   \tilde{\bf u }_{-1} e^{\sigma_{sc} t  -i \omega_{sc} t} \right],
+\ee  
+where ${\bf u }_m$ is the {\em mean flow} defined by phase-averaging over the cycle, $\tilde{{\bf u }}_1$ is a pseudo-eigenvector which is normalized by the condition  $||\tilde{{\bf u }}_1|| = 1/\sqrt{2}$,
+$A_{sc}$ is an amplitude parameter directly related to the energy of the oscillating flow, and $\lambda_{sc} = \sigma_{sc} + i \omega_{sc}$ is a pseudo-eigenvalue which depends upon the parameter $A_{sc}$.
+Introducing the decomposition (\ref{SC}) into the Navier-Stokes equations we are left 
+with the following problem:
 
-\clearpage
+\begin{subequations}\label{sc12}
+\begin{eqnarray}
+{\cal NS}(  {\bf u }_m ) - A_{sc}^2 {\cal C}( \tilde{{\bf u }}, \overline{\tilde{\bf u }}) = 0, 
+\label{sis1}
+\\
+(\sigma_{sc} + i \omega_{sc}) \tilde{{\bf u }} =  {\cal L}_{{\bf u }_m}(  \tilde{{\bf u }} ).
+\label{sis2}
+\end{eqnarray}
+\end{subequations}
+
+Equation (\ref{sis1}) provides the mean flow field ${\bf u }_m$ while the 
+pseudo-eigenpairs $(\lambda_{sc}, \tilde{{\bf u }})$ can be computed by solving the eigenvalue problem (\ref{sis2}).
+%The computed mode is normalized as $ || \tilde{{\bf u }}|| = 1/{\sqrt{2}}$
+%is of the same form as  (\ref{HBEq1}) except that $i \omega$ is 
+%replaced by $\sigma_{SC} + i \omega_{SC}$. 
+% The mean flow is then governed by the same equation
+%\ref{HBEq0}) written above, while $\tilde{{\bf u }}_1$ is the solution of an eigenvalue problem with the same form as  (\ref{HBEq1}) except that $i \omega$ is replaced by $\sigma_{SC} + i \omega_{SC}$.
+
+The self-consistent model has the following properties :
+\begin{itemize}
+\item[-] For $A \ll 1$ it is equivalent to the linear eigenvalue problem (\ref{LEP}), and the generalized eigenvalue coincides with the one predicted by linear stability : $\sigma_{SC} + i \omega_{SC} = \sigma_{lin} + i \omega_{lin}$.
+\item[-] For $\sigma_{SC}=0$ (corresponding to a specific choice of the amplitude $A=A_c$),  the expansion (\ref{SC}) is equivalent to a Fourier decomposition of the limit cycle with only two term retained.
+\item[-] For $0<A<A_c$, the resolution leads to a relation $\sigma_{SC}(A) ; \omega_{SC}(A)$
+such that $0< \sigma_{SC}(A) < \sigma_{lin}$.
+ Although in this case the expansion ({\ref{SC}}) cannot represent the flow for all $t$, Manti\v{c}-Lugo et al \cite{MLugo2014} argued that the relation between $\sigma_{SC}$ and $A$ can be used to build an amplitude equation which captures the transient approach to the limit cycle.
+\end{itemize}
+
+Figure \ref{fig:SC100} shows the results of the self-consistent model at Re=100.
+
+\paragraph{Harmonic balance : equations and procedure }
+\begin{figure}
+\begin{center}
+\includegraphics[width=.9 \linewidth]{Cylinder_Lx_Re_HB.png}
+\end{center}
+\caption{Flow past a circular cylinder: length of the wake bubble (measured from the 
+rear stagnation point) for different Reynolds number. Comparison between the base flow bubble and the mean flow bubble computed by using the harmonic balance.}
+\label{fig:Comp1}
+\end{figure}
+As discussed above, the Self-Consistent model was initially presented by the authors as a rational way to explain the dynamics in terms of a stability analysis of the {\em mean flow}.
+Furthermore, the resolution method presented by the authors, which involves a double iteration loop, is not easy to implement and not particularly efficient.
+
+If one is only interested by the properties of the limit cycle and not the transient, the model is actually equivalent to a Fourier series, and amenable to a more direct resolution method. 
+We thus start with a Fourier decomposition of the limit cycle under the form :
+\be{HB}
+{\bf u } = {\bf u }_0 + {\bf u }_1 e^{i \omega t} +   {\bf u }_{-1} e^{-i \omega t}.
+\ee  
+Here ${\bf u }_0$ is the mean flow (averaged over time),  ${\bf u }_1$ is the mode
+(Fourier component at the fundamental frequency), ${\bf u }_{-1} = \overline{{\bf u }_1}$ is its complex conjugate, and $\omega$ is the (real) oscillation frequency of the limit cycle (which is not known a priori).
+Injecting this ansartz into the Navier-Stokes equations and taking the mean value and the first Fourier component leads to the following coupled equations :
+\be{HBEq0}
+{\cal NS}(  {\bf u }_0 ) - {\cal C}( {\bf u }_1, \overline{\bf u }_1) = 0,
+\ee
+\be{HBEq1}
+i \omega {\bf u }_1 =  {\cal L}_{{\bf u }_0}(  {\bf u }_1 ).
+\ee
+
+Note that contrary to the SC model, the ${\bf u }_1$ component is not normalized.
+The amplitude $A$ can easily be computed a posteriori as $A = \sqrt{2 ||{\bf u }_1||}$.
+On the other hand, the Fourier description of the limit cycle is invariant with respect to the phase $\phi$ (i.e.
+the equations are unchanged when replacing $[ {\bf u }_1,  {\bf u }_{-1}] $ by  $[ {\bf u }_1 e^{i\varphi},  {\bf u }_{-1}  e^{-i\varphi}] $).
+To allow resolution we thus need an extra equation to fix this phase.
+Several choices are possible, but a convenient one is to set the lift associated with the imaginary part of ${\bf u }_1$ to lift.
+Physically, this means that the instant $t=0$ will correspond to a maximum of lift.
+This condition reads :
+\be{HBphase}
+\Im \{F_y({\bf u}_1) \} =0.
+\ee
+
+Mathematically, the system (\ref{HBEq0},\ref{HBEq1},\ref{HBphase}) for the unknown $[{\bf u }_0, {\bf u }_{1}, \omega]$ is well posed, and can be solved using a Newton iteration just as explained for the base flow in section 2.
+To allow resolution, we separate the mode into real and imaginary part, by writing ${\bf u }_1 = {\bf u }_{1,r} +  i {\bf u }_{1,i} $.
+We then assume that we know a 'guess' 
+$$
+[{\bf u }_0, {\bf u }_{1,r}, {\bf u }_{1,i}, \omega] = 
+ [{\bf u }_0^g, {\bf u }_{1,r}^g, {\bf u }_{1,i}^g, \omega^g]
++ [\delta {\bf u }_0, \delta {\bf u }_{1,r}, \delta {\bf u }_{1,i}, \delta \omega].
+$$
+
+Injecting and developing up to linear order leads to the following 
+\begin{equation}
+\begin{array}{ll}
+\displaystyle
+& {\cal NS}(  {\bf u }_0^g ) - [ {\cal C}( {\bf u }_{1,r}^g,{\bf u }_{1,r}^g) +  {\cal C}( {\bf u }_{1,i}^g,{\bf u }_{1,i}^g) ]
+\\
++& {\cal L}_{{\bf u }_0^g}(\delta {\bf u }_0) - 2 [ {\cal C}( {\bf u }_{1,r}^g,\delta {\bf u }_{1,r}) +  {\cal C}( {\bf u }_{1,i}^g,\delta {\bf u }_{1,i}) ] = 0;
+\\
+\\
+&  {\cal L}_{{\bf u }_0^g}( {\bf u }_{1,r}^g) - \omega^g {\bf u }_{1,i}^g 
+ \\
+  +& {\cal L}_{{\bf u }_0^g}( \delta {\bf u }_{1,r}^g) 
+   -  {\cal C}( \delta {\bf u }_{0}^g, {\bf u }_{1,r})
+   - \delta \omega^g \delta {\bf u }_{1,i}^g 
+ - \omega^g \delta {\bf u }_{1,r} = 0 ;
+ \\
+\\
+&  {\cal L}_{{\bf u }_0^g}({\bf u }_{1,i}^g) + \omega^g {\bf u }_{1,i}^g
+ \\
+  +& {\cal L}_{{\bf u }_0^g}( \delta {\bf u }_{1,i}^g) 
+  -  {\cal C}( \delta {\bf u }_{0}^g, {\bf u }_{1,i}) 
+  + \delta \omega^g \delta {\bf u }_{1,i}^g 
++ \omega^g \delta {\bf u }_{1,r} = 0 ;
+\\
+\\
+& F_y({\bf u }_{1,i}^g) + F_y(\delta {\bf u }_{1,i}) = 0.
+ \end{array}
+\end{equation}
+
+After discretization, this leads to a linear problem of the form $A X = Y$ where $X$ is the discretized version of the unknowns  $[\delta {\bf u }_0, \delta {\bf u }_{1,r}, \delta {\bf u }_{1,i}, \delta \omega]$, and $A$ is a matrix of dimension $3 N_{dof} +1$.
+
+%\ref{HBEq0,HBEq1,HBphase}
+
+As mentioned before, figure \ref{fig:Comp2} shows the comparison between the 
+weakly non linear approach and the harmonic balance data.  
+Figure \ref{fig:Comp1} compares the length of the cylinder bubble computed by using 
+the harmonic balance with the base flow length.
+
+%Barkley [] and Leontini [] have
+
+%\clearpage
 
 \section{Conclusion}
+The aim of the present review is to introduce advanced stability approaches 
+from a {\tt practical} point of view. The reader can reproduce all the figures presented 
+in this paper by just running the Matlab code available in the StabFem repository.
 
-\section{Appendix : details on mesh convergence}
+\section*{Acknowledgements}
+bla bla
 
-SECTION TO BE COMPLETED
-
-\paragraph{Illustration of mesh convergence procedure for a cylinder}
-
+\section*{Appendix A : details on mesh convergence}
 \begin{figure}
@@
 > plotFF(baseflow,'mesh');
-
 \end{lstlisting}
 \normalsize
-
 \caption{Illustration of the procedure to compute a base flow and an adapted mesh using StabFem (from script {\em SCRIPT\_CYLINDER.m}. }
+\label{ill_bsflow}
 \end{figure*}
@@
 \caption{Illustration of the procedure to adapt the mesh for stability calculations with StabFem (from script {\em SCRIPT\_CYLINDER.m}. }
+\label{stabmesh}
 \end{figure*}
@@
 
-The Reference mesh is adapted to the Structural sensitivity, for $Re= 60$, with interpolation error 0.01, mesh dimensions $[-40,120]\times[0,40]$, and no-stress boundary conditions at the outlet and lateral boundaries.
+Giannetti \& Luchini\cite{GiannettiLuchini} showed that the accuracy of the stability 
+results for the flow past a circular cylinder is strictly related to the mesh characteristics 
+in the wavemaker region, i.e. the region where the structural sensitivity reaches its 
+maximum values. Following this idea, we chose as reference solution the field
+computed on an adapted mesh obtained by using the structural sensitivity field.
+We set the interpolation error equal to 0.01 and the size of the computational domain 
+is $[-40,120]\times[0,40]$. The base flow is computed by using classical no-slip 
+boundary conditions on the body surface, a uniform velocity profile at the inlet
+and no-stress boundary conditions at the outlet and lateral boundaries.
+The conditions for the stability computations are simply derived from the ones of the base flow.
 
-Figure \ref{fig:MeshConvergence} displays the results.
+Figure \ref{fig:MeshConvergence} displays global stability results. We note that there is 
+a very weak variation in the growth rate and we found an error up to 1\% on the 
+Strouhal number. Figure \ref{ill_bsflow} illustrate the procedure adopted to compute the 
+base flow and the adapted mesh. Figure \ref{stabmesh} reports the Matlab code 
+adopted to adapt the mesh by using the information provided by both the base flow and the sensitivity field.
 
@@
 
+\bibliographystyle{asmems4}
+
+\bibliography{ARTICLE_ASME}
+
 \end{document}

### 2018-03-06 ACOUSTICS_PIPES/SF_Acoustic.m

@@ -1,0 +1,28 @@
+function AC = SF_Impedance(baseflow,varargin)
+global ff ffdir ffdatadir sfdir verbosity
+%%% management of optionnal parameters
+    p = inputParser;
+    addParameter(p,'k',0.1);
+    addParameter(p,'plotPhi','no');
+    addParameter(p,'plotaxis','no');
+    parse(p,varargin{:});
+    
+    solvercommand = ['echo ' num2str(p.Results.k) ' | ' ff  ' Impedance_plot.edp'];
+        status = mysystem(solvercommand);
+              
+        
+    AC=importFFdata(baseflow.mesh,'AcousticField.ff2m');
+    
+   if ( strcmp(p.Results.plotPhi,'yes')  ==1)
+           plotFF(AC,'Phi');
+   end
+   
+    if ( strcmp(p.Results.plotaxis,'yes')  ==1)
+           plot(AC.Xaxis,real(AC.Paxis),'r-',AC.Xaxis,imag(AC.Paxis),'r--',...
+               AC.Xaxis,real(AC.Uaxis),'b-',AC.Xaxis,imag(AC.Uaxis),'b--');
+           title('Pressure and velocity along the axis ')
+           legend('Re(P)', 'Im(P)','Re(U)','Im(U)'); 
+   end
+   
+   
+   

### 2018-03-06 CYLINDER/SCRIPT_CYLINDER_WNL.m

@@ -1,50 +1,5 @@
-%  Instability of the wake of a cylinder with STABFEM  
-%
-%  this scripts performs the following calculations :
-%  1/ Generation of an adapted mesh
-%  2/ Base-flow properties for Re = [2-40]
-%  3/ Stability curves St(Re) and sigma(Re) for Re = [40-100]
-%  4/ Determination of the instability threshold
-%  5/ Harmonic-Balance for Re = REc-100
-%  6/ Self-consistent model for Re=100
 
-% CHAPTER 0 : set the global variables needed by the drivers
-
-global ff ffdir ffdatadir sfdir verbosity
-%ff = '/PRODCOM/FREEFEM/Ubuntu12.04/3.29/bin/FreeFem++-nw'; % on IMFT network
-ff = '/usr/local/ff++/openmpi-2.1/3.55/bin/FreeFem++-nw'; % on DF's macbookpro 
-ffdatadir = './WORK/';
-sfdir = '../SOURCES_MATLAB/'; % where to find the matlab drivers
-ffdir = '../SOURCES_FREEFEM/'; % where to find the freefem scripts
-verbosity = 1;
-addpath(sfdir);
-system(['mkdir ' ffdatadir]);
-figureformat='png'; AspectRatio = 0.56; % for figure
-
-%##### CHAPTER 1 : COMPUTING THE MESH WITH ADAPTMESH PROCEDURE
-
-if(exist('baseflow')==1)
-disp(' ADAPTMESH PROCEDURE WAS PREVIOUSLY DONE, START WITH EXISTING MESH : '); 
-baseflow=SF_BaseFlow(baseflow,60);
-[ev,em] = SF_Stability(baseflow,'shift',0.04+0.76i,'nev',1,'type','S');
-else
-   
-disp(' STARTING ADAPTMESH PROCEDURE : ');    
-disp(' ');
-disp(' LARGE MESH : [-40:80]x[0:40] ');
-disp(' ');    
-baseflow=SF_Init('Mesh_Cylinder_Large.edp');
-baseflow=SF_BaseFlow(baseflow,1);
-baseflow=SF_BaseFlow(baseflow,10);
[…]

### 2018-03-07 ACOUSTICS_PIPES/TP_Freefem.tex
fix

\documentclass[11pt,a4paper]{article}

\usepackage[francais]{babel}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
%\usepackage{fancyhdr}
\usepackage{graphicx, amsmath, amssymb, latexsym}
%\usepackage{natbib}

\setlength{\textheight}{26cm} % 24
\setlength{\topmargin}{-2cm}
\setlength{\textwidth}{17cm}  % 15
%\setlength{\oddsidemargin}{20mm} % marge gauche (im)paire = 1in. + x1mm
%\setlength{\evensidemargin}{0mm} % book : marge gauche paire = 1in. + x2mm
\setlength{\oddsidemargin}{-5mm} % marge gauche (im)paire = 1in. + x1mm
\setlength{\evensidemargin}{-5mm} % book : marge gauche paire = 1in. + x2mm
\setlength{\fboxsep}{5mm}

\newcommand{\e}  {\mathrm{e}}   
\newcommand{\dd}  {\textrm d}      
\newcommand{\im}  {\mathrm{i}} %\newcommand{\im}  {\textrm i}
\newcommand{\dpa}[2]  {\frac {\partial #1} {\partial #2}}   
\newcommand{\ddpa}[2] {\frac {\partial^{2} #1} {\partial #2 ^{2}}}   
\newcommand{\dto}[2]  {\frac {{\textrm d} #1} {{\textrm d} #2}}   
\newcommand{\ddto}[2] {\frac {{\textrm d}^{2} #1} {{\textrm d} #2 ^{2}}}
%\newcommand{\tensor}[1]{\stackrel{\Rightarrow}{#1}}

%\graphicspath{{../Figures/}{../FiguresPierre/}}
\graphicspath{Figures/}

%\makeindex

%------------------------------------------------------------------------------
\begin{document}

%\begin{titlepage}

\noindent
\textsc{Universit\'e Paul Sabatier \hfill Ann\'ee 2017/2018} \\
\textsc{M1 Mécanique \hfill majeure Ondes et Turbulence / Ondes}
%\vspace{1cm}

%\begin{center}

\vspace{.3cm}
%\section*{TP numérique : ondes sur une corde} 
\begin{center}
{\Huge \bf TP numérique}

\vspace{.3cm}

{\Huge \bf Flûtes et pots d'échappements}
\end{center}

\vspace{.6cm}
\large

%\section{TP numérique : Tuyaux et pots d'échappement}

Dans ce TP on va résoudre à l'aide du logiciel FreeFem++ l'équation des ondes en régime harmonique, dans un domaine dont l'entrée est un tuyau de section 
$S_{in}$.

\vspace{.4cm}

\section{Partie théorique}

%Pour l'année prochaine :

% - densité 6 au lieu de 12

 %- tout encapsuler

% - faire les impedances avant les plots

% - travailler sur Azteca (verifier instal)

 %- cas pot d'echappement : log-log

 %- appeler les cas 1,2,3,4

 %- mettre Z0 = 1

%- virer l'option [1-2] pour le plot

%- verifier les options du plot (fill et isovalues)

\subsection{Rappel : impédance d'entrée d'un circuit acoustique}

On étudie un circuit acoustique (tuyau, pot d'échappement, silencieux ou autre) de section d'entrée $S_{in}$. Le circuit est forçé en régime harmonique à la pulsation $\omega$, c'est-à-dire qu'en 
entrée le flux acoustique (débit massique) $q$ et la pression acoustique $p'$ 
sont de la forme $q = U_{in}e^{-i \omega t}$ et $p' = p_{in} e^{-i \omega t}$. On définit alors l'impédance d'entrée du circuit par 
$$
Z_{in} = \frac{p_{in} }{U_{in}} . 
$$

Cette quantité (complexe) a les propriétés suivantes :

\begin{itemize}

\item Les minimums de $|Z_{in}|$ correspondent aux fréquences de résonance du circuit forcé en pression,

\item Les maximums de $|Z_{in}|$ correspondent aux fréquences de résonance 
du circuit forcé en vitesse,

\item La partie réelle (en général positive) est reliée au flux d'énergie injecté dans le circuit par le forçage en entrée, et la partie imaginaire est reliée au déphasage entre la pression et le débit.

\item L'impédance est directement reliée au coefficients de réflexion et de transmission (en intensité acoustique) par :
$$
R_i = \left|  \frac{ Z_{in} - Z_0}{Z_{in} + Z_0}  \right|^2 ; \qquad 
T_i = 1- R_i.
$$

où $Z_0 = \rho c/S_{IN}$ est l'impédance caractéristique d'un tuyau de section égale à la section d'entrée $S_{IN}$ du circuit.

\end{itemize}

\subsection{Résolution numérique par éléments finis}

Si le circuit étudié admet une symétrie de révolution, on peut travailler en coordonnées axisymétriques et introduire un potentiel des vitesses de la forme  
$$
\Phi(r,z,t) = \phi(r,z) e^{-i \omega t}
$$

Le problème consiste alors à résoudre l'équation des ondes sous la forme 
\begin{equation}
\Delta \phi + k^2 \phi = 0  \qquad \mbox{ pour } (r,z) \in \Omega \mbox{ avec } k = \omega/c
\label{eq:Ondes}
\end{equation}
Couplé à des conditions limites adaptées sur les frontières du domaine (cf. TD).

Le problème est résolu par une méthode d'éléments finis.

L'impédance du circuit est ensuite déduite du potentiel des vitesses par :
$$
Z_{in} = \frac{p_{in} }{U_{in}} =  \frac{ 1/S_{in} \int_{\Gamma_i} (i \rho \phi)  2 \pi r dr  } 
{ \int_{\Gamma_i} (\partial \phi / \partial z) 2 \pi r dr } 
$$

\subsection{Installation des programmes}

Pour ce TP on fournit deux types de programmes :

- Un ensemble de programmes écrit avec le logiciel d'éléments finis FreeFem++ (fichiers de la forme \verb| ###.edp |).

%Ces programmes sont à utiliser dans la fenêtre terminal par la commande suivante :

%\verb| > FreeFem++ ####.edp |

- Des 'drivers' matlab (fichiers de la forme \verb| SF_###.m |)  issus du projet collaboratif StabFem, permettant d'utiliser ces programmes dans l'environnement Matlab.

Outre Matlab, vous devrez donc installer et/ou télécharger les logiciels suivants :

- FreeFem++ (installé sur Azteca,  a télécharger gratuitement si vous souhaitez utiliser votre ordinateur personnel)

- La suite "StabFem" qui se télécharge en tapant dans une fenêtre terminal la commande suivante : 
\verb| git clone https://github.com/erbafdavid/StabFem |

{\small 
(  Cette commande devrait suffire sur un ordinateur linux ou mac, ou windows si vous disposez de l'utilitaire {\em git } ;  dans le cas contraire vous pouvez télécharger le fichier compacté disponible à l'adresse suivante : 
\verb| https://github.com/erbafdavid/StabFem/tree/master/ACOUSTICS_PIPES.tgz  |
)
}

Vous travaillerez par la suite dans le sous-répertoire \verb| ACOUSTICS_PIPES |.

Si vous n'arrivez pas à installer les drivers StabFem, vous pouvez toutefois utiliser les programmes FreeFem directement  en mode terminal (voir ci-dessous).

\subsection{Description et utilisation des programmes}

\begin{enumerate}

\item Les quatre premiers programmes, nommés 
\verb| Mesh_#.edp|
%Pipe_Flanged.edp |, 
%\verb| Mesh_Tube_58cm_Trou.edp |, 
 %\verb| Mesh_TailPipe.edp | et \verb|Mesh_ExpansionChamber.edp |
 servent à construire un maillage du domaine, dans les 4 cas étudiés.

\begin{itemize}
\item En mode terminal,  tapez la commande

\verb| > FreeFem++ ####.edp |.

\item En mode Matlab/StabFem, le driver correspondant est le programme \verb| SF_Init |, a utiliser de la manière suivante :

\verb| >>  bf = SF_Init('Mesh_#.edp') |

Pour visualisez le maillage, vous pourrez utiliser la commande \verb| plotFF(bf,'mesh') |.
\end{itemize}

 \item Le programme \verb| FF_Acoustic.edp | calcule le potentiel des vitesses pour une valeur de $k$ donnée, en déduit la valeur de l'impédance $Z_{in}(k)$.

\begin{itemize}
\item En mode terminal,  tapez la commande \verb| > FreeFem++ FF_Acoustic.edp |, puis entrez au clavier la valeur du nombre d'onde  $k$. Le programme affiche le potentiel des vitesses dans le domaine (appuyez sur entrée pour afficher le potentiel à des instants successifs). Le programme génère aussi un fichier de données \verb|Champs_P_U_Axe.txt|
contenant les valeurs de P et U sur l'axe de symétrie, ainsi qu'un fichier graphique 
\verb|Champ_Acoustique.eps| que vous pouvez utiliser par exemple pour illustrer un rapport...

\item En mode matlab/StabFem, le driver correspondant s'utilise de la manière suivante (par exemple pour $k=1$) :

\verb| >>  AC = SF_Acoustic(bf,'k',1) |

le résultat AC est une "structure matlab" dont les champs peuvent être exploités et tracés avec plotFF et plot (voir examples dans le script).

\end{itemize}

 \item Le programme \verb| FF_Acoustic_Impedance.edp | Calcule successivement les valeur de l'impédance $Z_{in}(k)$ dans un intervalle de $k$ compris entre $k_{min}$ et $k_{max}$, par pas $dk$.

\begin{itemize}
\item En mode terminal,  tapez \verb| > FreeFem++ FF_Acoustic_Impedance.edp | puis entrez successivement au clavier $k_min$, $k_max$, $dk$. Les résultats sont écrits dans un fichier \verb| Impedances.txt | qui peut ensuite être utilisé par un autre programme pour tracer les courbes (Matlab ou autre).

\item En mode matlab/StabFem, le driver correspondant s'utilise de la manière suivante (par exemple pour l'intervalle $k \in [0,1]$) :

\verb| >>  IMP = SF_Acoustic_Impedance(bf,'k',[0:.02:1]) |

le résultat IMP est une "structure matlab" dont les champs IMP.k et IMP.Z sont des vecteurs de même dimension que l'on peut tracer l'un un fonction de l'autre (voir examples dans le script).

\end{itemize}

\end{enumerate}

%  \vspace{.3cm}
%Les programmes se lancent avec la commande suivante (a taper dans un terminal unix) :
%
%\verb| > FreeFem++ | {\em(nom du programme)}
%
%\vspace{.3cm}
%Les programmes peuvent également être lancés dans une fenêtre de commande ou un programme Matlab de la manière suivante :
%
%\verb| >> system('/usr/local/bin/FreeFem++| {\em(nom du programme)} \verb| ')|
%
%\vspace{.3cm}
%
% Outre ces programmes on fournit des scripts Matlab qui "encapsulent" les programmes FreeFem+ Afin de pouvoir les utiliser comme s'il s'agissait de programmes Matlab :
% 
%\begin{itemize}
%
%\item Les quatre scripts nommés \verb| Script_|{\em (nom du cas)}\verb|.m|
%utilisent le programme 
%
%\verb| Impedance_loop.edp | et permettent de tracer l'impédance $|Z(k)|$ et/ou le coefficient de transmission $T_i(k)$ pour chacun des cas.
% 
% \item Le script \verb| Plot_P_U_Axe.m | est basé sur le programme \verb| Impedance_plot.edp |
%et permet de tracer les courbes donnant la pression $P(0,z)$ et la vitesse $U(0,z)$ sur l'axe de symétrie du domaine (à partir des données lues dans le fichier \verb|Champs_P_U_Axe.txt|).
% 
% 
%\end{itemize} 
%  \clearpage
\section{  Cas étudiés }

\subsection{Tuyau cylindrique débouchant dans un demi-espace}

On considère tout d'abord un tuyau cylindrique de longueur $L=10$ et rayon $a = 1$, 
débouchant dans un demi-espace. Le problème est adimensionné en posant $\rho = c =1$ 
(on a alors directement $\omega = k$).

Si vous travaillez en mode matlab/StabFem, il vous suffira de faire tourner le programme suivant pour étudier ce cas :

\verb| SCRIPT_DEMO_ACOUSTIQUE.m |

{\small
(si vous préferez travailler en mode terminal, vous devrez taper sucessivement les commandes équivalentes dans la fenêtre terminal.)
}

\begin{enumerate}

\item A partir de la courbe de l'impédance calculée, identifiez les valeurs de $k$ correspondant aux deux premiers minimums de $Z_{in}$. Comparez aux prédictions théoriques de l'exercice 2.4.1.

\item A l'aide du programme \verb| FF_Acoustic.edp | et/ou du driver \verb| SF_Acoustic.m |,
étudiez la structure du champ acoustique pour les valeurs de $k$ précédemment identifiées. Que constate-t-on ?

\item Pour ces  valeurs de $k$, observez la courbe donnant la pression $P(x)$ sur l'axe de symétrie. Ou se trouvent les noeuds de pression ? Estimez la valeur de la "correction de longueur" $\Delta$ (exercice 2.2).

\item Mêmes questions pour les deux premiers maximums de $Z_{in}$.

\item Tracez, sur la même figure, la valeur de $Z_{in}$ calculée par le logiciel FreeFem++ et celle prédite par la théorie (exercice 2.2).

\end{enumerate}

\subsection{Tuyau avec trou latéral}

Dans ce second cas on considère un tuyau de longueur $L = 58cm$ et de rayon $a =1cm$. 
On prend les caractéristiques de l'air : $\rho = 1.225 kg/m^3$ et $c = 34000 cm/s$. 
Le maillage correspondant est généré par le programme \verb| Mesh_2.edp |.

\begin{enumerate}
%\item
%Générez le maillage avec le programme \verb| Mesh_Tube_58cm_Trou.edp |.
\item
Observez la structure du champ acoustique pour différentes valeurs de $k$ à l'aide du programme \verb| FF_Acoustic.edp | et/ou du driver \verb| SF_Acoustic.m |.

\item 
Tracez $Z_{in}$ en fonction de la fréquence $f = \omega/2\pi$ à l'aide du programme 
\verb| FF_Acoustic_Impedance.edp | et/ou du driver \verb| SF_Acoustic_Impedance.m |.

\item Comparez avec la théorie (exercice 2.3). Quelles valeurs faut-il prendre pour les corrections de longueur $\Delta$ et $\Delta'$ ?

\item Quelle est la fréquence fondamentale de ce tuyau dans le cas d'un forçage en pression (flûte) et d'un forçage en vitesse (clarinette) ? A quelles notes ces fréquences correspondent-elles ?

\end{enumerate}

\subsection{Pot d'échappement}

On considère maintenant le cas d'un pot d'échappement (exercice 2.3.3).
Celui-ci est modélisé par un tuyau de rayon $a$, relié au travers d'une
ouverture d'aire $A$ à un résonateur de Helmholtz de volume $V$.

Le maillage fourni correspond aux valeurs $a=1,A=6.28,V=388.8$.

(le programme ne permettant de traiter que des géométrie axisymétriques, l'ouverture est supposée de forme annulaire et de longueur $h$, l'aire vaut donc $A = 2\pi a h$)

Le maillage est généré avec le programme \verb| Mesh_3.edp |.

\begin{enumerate}
%\item
%Générez 
%\item
%Observez la structure du potentiel des vitesses pour différentes valeurs de $k$ à l'aide du programme \verb| Impedance_plot.edp |.
\item 
Tracez $Z_{in}$ (figure 1) ainsi que $T_i$ (figure 4 (échelle linéaire) et 5 (échelle logarithmique))  à l'aide du driver Mablab 
\verb| SF_Acoustic_Impedance.m |., pour $k$ dans l'intervalle $[0-0.02]$.

\item Une modélisation simplifiée (exercice 2.3.3) prédit que le coefficient de transmission vaut 
$$
T_i  = \frac{1}{1+(k/k_c)^2}, \mbox{ avec } k_c = \frac{2 A}{V}.
$$
Comparez cette prédiction avec le résultat du programme.

\item Pour des valeurs de $k$ plus grandes, on observe des maximums et minimums de $|Z|$ pour des valeurs précises. Illustrez la structure du champ acoustique dans ces cas (dans le domaine et sur l'axe). Peut-on prédire les valeurs de $k$ correspondantes (cf. exercice 3.1...)

%Ce modèle est également tracé par le script sur les figures 4 et 5. Que constate-t-on ?

%\item 
%Modifiez le script \verb| Script_TailPipe.m |, pour tracer le coefficient de transmission pour $k$ dans l'intervalle $[0-1]$. Que constate-t-on ? Expliquez.

%On pourra utiliser le programme \verb| Impedance_plot.edp | et/ou le script

%\verb| Plot_P_U_Axe.m | pour observer la structure du champ acoustique pour certaines valeurs de $k$.

\end{enumerate}

\subsection{Chambre d'expansion}

On considère finalement le cas d'une chambre d'expansion (exercice 2.3.2).

Le maillage correspondant est généré avec le programme \verb| Mesh_4.edp |.

\begin{enumerate}
%\item
%Générez le maillage avec le programme \verb| Mesh_ExpansionChamber.edp |.
\item
Observez la structure du champ acoustique pour différentes valeurs de $k$ à l'aide du programme \verb| FF_Acoustic.edp | et/ou du driver \verb| SF_Acoustic.m |.

\item 
Tracez $Z_{in}$ en fonction de $k$ ainsi que $T$ en fonction de $k$ à l'aide du script Mablab 
\verb| SF_Acoustic_Impedance.m |.

\item 
Comparez avec les prédictions théoriques (exercices 2.1.2 et 2.3.2).

\end{enumerate}

\subsection{Autres cas (bonus...)}

En explorant les programmes fournis vous trouverez 5 autres programmes construisant des maillages pour des géométries différentes. N'hésitez pas à jouer avec !

\section{Travail demandé}

Parmi les cas proposés, vous choisirez deux cas d'étude.

Pour chacun des cas choisis :
\begin{itemize}
\item Illustrez à l'aide des résultats du programme le comportement acoustique du circuit au travers d'un choix judicieux de courbes générées par les programmes, qui seront commentés de manière physique en lien avec l'application considérée (instrument de musique ou atténuateur de bruit).

\item Comparez avec les éléments de théorie vus en cours et/ou en TD.

\item Commentez et expliquez les ressemblances et éventuelles différences.
\end{itemize}

On précise que seules les figures disposant d'une légende et commentées dans le rapport seront prises en compte dans l'évaluation.

\end{document}

\subsection{Application 1 : instruments de musique}

Dans ce cas on s'intéresse aux maximums et minimums de l'impédance $|Z|$.

\subsubsection{Tuyau cylindrique}

Théorie :

$$
Z_{IN} = Z_0 \frac{Z_L \cos k L + j Z_0 \sin k L}{j Z_L \sin k L + Z_0 \cos k L}
$$

avec

$$
Z_L = Z_0 \left( \frac{k^2 a^2}{4} + j k \Delta \right) 
$$

\subsubsection{Tube cylindrique avec trou latéral}

Théorie : formule précédente en remplaçant $L$ par $L-D$ et $\Delta$ par $\Delta'$.

\subsubsection{Tube conique}

Cone tronqué.

Théorie :

$$
Z_{IN} =...
$$

(Rossing, page 211).

\subsubsection{Pavillon exponentiel}

\subsection{Silencieux et pot d'échappement}

Dans ce cas on s'intéresse au coefficient de transmission.

\subsubsection{Silencieux simple constitué d'une chambre d'expansion}

Théorie :

\subsubsection{Pot d'échappement}

Théorie :

\end{document}

### 2018-03-07 ACOUSTICS_PIPES/SF_Acoustic.m

@@ -7,7 +7,7 @@ global ff ffdir ffdatadir sfdir verbosity
     addParameter(p,'plotaxis','no');
     parse(p,varargin{:});
     
-    solvercommand = ['echo ' num2str(p.Results.k) ' | ' ff  ' Impedance_plot.edp'];
+    solvercommand = ['echo ' num2str(p.Results.k) ' | ' ff  ' FF_Acoustic.edp'];
         status = mysystem(solvercommand);
               
         

### 2018-03-07 ACOUSTICS_PIPES/SF_Acoustic_Impedance.m

@@ -11,7 +11,7 @@ global ff ffdir ffdatadir sfdir verbosity
    dk = p.Results.k(2)-p.Results.k(1)
    
     
-    solvercommand = ['echo ' num2str(kmin) ' ' num2str(dk) ' ' num2str(kmax)  ' | ' ff  ' Impedance_loop.edp'];
+    solvercommand = ['echo ' num2str(kmin) ' ' num2str(dk) ' ' num2str(kmax)  ' | ' ff  ' FF_Acoustic_Impedance.edp'];
         status = mysystem(solvercommand);
               
         

### 2018-05-17 CYLINDER/SCRIPT_CYLINDER_DEMO.m
FIRST BIG STEP TOWARDS INCORPORATION OF COMPRESSSIBLE SOLVER !

@@ -1,351 +1,0 @@
-%  Instability of the wake of a cylinder with STABFEM  
-%
-%  this scripts performs the following calculations :
-%  1/ Generation of an adapted mesh
-%  2/ Base-flow properties for Re = [2-40]
-%  3/ Stability curves St(Re) and sigma(Re) for Re = [40-100]
-%  4/ Determination of the instability threshold and Weakly-Nonlinear
-%  analysis
-%  5/ Harmonic-Balance for Re = REc-100
-%  6/ Self-consistent model for Re=100
-
-% CHAPTER 0 : set the global variables needed by the drivers
-
-run('../SOURCES_MATLAB/SF_Start.m');
-figureformat='png'; AspectRatio = 0.56; % for figures
-
-%##### CHAPTER 1 : COMPUTING THE MESH WITH ADAPTMESH PROCEDURE
-
-if(exist('baseflow')==1)
-disp(' ADAPTMESH PROCEDURE WAS PREVIOUSLY DONE, START WITH EXISTING MESH : '); 
-baseflow=SF_BaseFlow(baseflow,'Re',60);
-[ev,em] = SF_Stability(baseflow,'shift',0.04+0.76i,'nev',1,'type','S');
-else
-   
-disp(' STARTING ADAPTMESH PROCEDURE : ');    
-disp(' ');
-disp(' LARGE MESH : [-40:80]x[0:40] ');
-disp(' ');    
-baseflow=SF_Init('Mesh_Cylinder.edp',[-40 80 40]);
-baseflow=SF_BaseFlow(baseflow,'Re',1);
-baseflow=SF_BaseFlow(baseflow,'Re',10);
-baseflow=SF_BaseFlow(baseflow,'Re',60);
-baseflow=SF_Adapt(baseflow,'Hmax',5);
-baseflow=SF_Adapt(baseflow,'Hmax',5);
-disp(' ');
-disp('mesh adaptation to SENSITIVITY : ')
-[ev,em] = SF_Stability(baseflow,'shift',0.04+0.76i,'nev',1,'type','S');
-[baseflow,em]=SF_Adapt(baseflow,em,'Hmax',10);
-
-end
-
-%%% CHAPTER 1b : DRAW FIGURES
-
-% plot the mesh (full size)
-plotFF(baseflow,'mesh');
[…]

### 2018-05-17 CompressibleCylinder/SCRIPT_TEST.m

@@ -1,0 +1,33 @@
+clear all; clc;
+
+run('../SOURCES_MATLAB/SF_Start.m');
+verbosity = 20;
+
+close all;
+
+% generating initial mesh
+bf = SF_Init('Mesh.edp',[]);
+
+% plot
+bf.mesh.xlim=[-5,10];bf.mesh.ylim=[-8,8];
+plotFF(bf,'ux');
+
+
+
+system('ff-mpirun -np 2 Newton_2D_Comp.edp'); 
+bf = importFFdata(bf.mesh,'BaseFlow.ff2m');
+plotFF(bf,'ux');
+% This first basic integration works, FANTASTICO !
+
+
+%% to be incorporated in the general SF_Baseflow driver
+% remain to find the way to pass the parameters in paralel mpi operation
+% and then to do the stability 
+
+% 17 may 2018 has been an extremely productive day !
+
+% GRANDE FLAVIO !
+ 
+
+
+

### 2018-05-17 IMPACTINGJET/SCRIPT_ImpactingJet.m

@@ -19,12 +19,12 @@ bf.mesh.xlim=[-3,H];bf.mesh.ylim=[0,4]; % these ranges will be used for all plot
 % computation of base flow with increasing Re
 for Re = [10 30 60 80 100 150 200 250 300]
     bf = SF_BaseFlow(bf,'Re',Re);
-    bf = SF_Adapt(bf);
+  %  bf = SF_Adapt(bf);
 end
 
 % Adaptation to the structure of an eigenmode 
-[ev,em] = SF_Stability(bf,'nev',1,'shift',0.005+0.i,'k',2,'type','S')
- bf = SF_Adapt(bf,em);
+[ev,em] = SF_Stability(bf,'nev',1,'shift',0.005+0.i,'k',2,'type','D')
+% bf = SF_Adapt(bf,em);
   
 end
 % a few plots

### 2018-05-24 ARTICLE_STABFEM/ARTICLE_ASME_V2.tex
adding V2 of the ASME paper

--- 2018-03-06 ARTICLE_STABFEM/ARTICLE_ASME.tex
@@
 %%% first author
-\author{D. Fabre$^{(a)}$ et al.%, P. Bonnefis$^{(a)}$
+\author{D. Fabre$^{(a)}$, D. Ferreira Sabino$^{(a)}$, P. Bonnefis$^{(a)}$,  V. Citro \& F. Giannetti
     \affiliation{
@@
 \begin{lstlisting}
-baseflow = SF_Init('Mesh_Cylinder_Large.edp');
-baseflow = SF_BaseFlow(baseflow,'Re',1);
-baseflow = SF_BaseFlow(baseflow,'Re',10);
-baseflow = SF_BaseFlow(baseflow,'Re',60);
-baseflow = SF_Adapt(baseflow,'Hmax',10,'InterpError',0.01);
-[ev,em] = SF_Stability(baseflow,'shift',0.04+0.74i,'type','S')
-baseflow = SF_Adapt(baseflow,em,'Hmax',10,'InterpError',0.01);
-plotFF(baseflow,'mesh'); plotFF(baseflow,'ux');
+bf = SF_Init('Mesh_Cylinder_Large.edp');
+bf = SF_BaseFlow(bf,'Re',1);
+bf = SF_BaseFlow(bf,'Re',10);
+bf = SF_BaseFlow(bf,'Re',60);
+bf = SF_Adapt(bf,'Hmax',10,'InterpError',0.01);
+[ev,em] = SF_Stability(bf,'shift',0.04+0.74i,'type','S')
+bf = SF_Adapt(bf,em,'Hmax',10,'InterpError',0.01);
+plotFF(bf,'mesh'); plotFF(bf,'ux');
 
@@
     for Re = Re_Range
-        baseflow = SF_BaseFlow(baseflow,'Re',Re);
-        Drag_tab = [Drag_tab,baseflow.Drag];
-        Lx_tab = [Lx_tab,baseflow.Lx];
+        bf = SF_BaseFlow(bf,'Re',Re);
+        Drag_tab = [Drag_tab,bf.Drag];
+        Lx_tab = [Lx_tab,bf.Lx];
     end
@@
 Re_Range = [40 : 2: 100];lambda_branch=[];
-baseflow=SF_BaseFlow(baseflow,'Re',40);
-[ev,em] = SF_Stability(baseflow,'shift',-.03+.72i,'nev',1,'type','D');
+bf=SF_BaseFlow(bf,'Re',40);
+[ev,em] = SF_Stability(bf,'shift',-.03+.72i,'nev',1,'type','D');
     for Re = Re_Range
-        baseflow = SF_BaseFlow(baseflow,'Re',Re);
-        [ev,em] = SF_Stability(baseflow,'nev',1,'shift','cont');
+        bf = SF_BaseFlow(bf,'Re',Re);
+        [ev,em] = SF_Stability(bf,'nev',1,'shift','cont');
         lambda_branch = [lambda_branch ev];
@@
 \caption{Illustration of the usage of the StabFem software to produce an adapted mesh and study the base flow and the linear stability properties of a cylinder
-(from script {\em SCRIPT\_CYLINDER\_DEMO.m})}
+(from script {\em SCRIPT\_CYLINDER\_ALLFIGURES.m})}
 \label{Listing2}
@@
 the location of the stagnation point at the rear of the recirculation region, and the drag coefficient $C_x(Re)$.
-Note that the object \verb|baseflow| is defined as a structure with fields \verb|Drag| and \verb|Lx|. 
+Note that the object \verb|bf| is defined as a structure with fields \verb|Drag| and \verb|Lx|. 
 The resulting plots are given in figure \ref{fig:LxandDrag}, and are in good agreement with known results for this classical problem.
@@
 
-We turn now to analyze how nonlinear effects can be considered in the framework 
-of global stability analysis. 
-Here, we symbolically write the Navier-Stokes system as $\partial_t {\bf u} = {\cal 
-NS} ({\bf u};p)$, therefore dropping the systematic reference of the 
-incompressibility constraint and associated pressure field.
-
-\paragraph{Review on nonlinear global stability approaches}
 %For $Re\right>Re_c$, the linear stability analysis based on the {\em base flow} does not allow to predict the properties of the limit cycle; in particular the Strouhal number is substantially underestimated.
@@
 In the past decade, efforts have been devoted to extend the range of validity of global approaches into the nonlinear regime for $Re>Re_c$, with the double objective to describe the properties of the limit cycle reached after saturation and to derive amplitude equations describing the transitent dynamics towards this cycle.
- The first milestone in this direction is the work of Sipp \& Lebedev \cite{SippLebedev} who used a weakly nonlinear development in terms of the distance to the threshold $Re-Re_c$.
-However, although derived on rigorous grounds, the weakly nonlinear development has a very limited range of validity and already fails for $Re\ge47$.
-More recently,  Manti\v{c}-Lugo et al \cite{MLugo2014} proposed an alternative approach termed {\em Self-consistent model} which succeeds in predicting the dynamics up to $Re =120$ and more. 
-This model was build as a linear stability approach build on a {\em mean flow} which includes a 
-retroaction of the eigenmode. However, if one is interested in the limit cycle and not the transient,
-the approach is actually equivalent to a Fourier series decomposition of the flow with respect to time (an approach also known as {\em harmonic balance}) retaining only the two first terms. 
+The two main milestones in this direction is the {\em weakly nonlinear model}  (WNL) of Sipp \& Lebedev \cite{SippLebedev} and the {\em self-consistent model} (SC) of Manti\v{c}-Lugo et al \cite{MLugo2014}.
+ {\color{blue} In this review, we will address only the first of the two questions, namely description of the saturated cycle, and leave aside the question of transient dynamics.
+We will successively review the two aforementioned models, in a simplified formulation devoted to describe only the saturated cycle.
+We also provide a simple implementation of these two models.
+Finally, in line with the previous section, we will again illustrate with results obtained for the wake of a cylinder.
+ }
+
+\paragraph{General definitions in the nonlinear régime}
+
+In this part, to simplify the notations, we symbolically write the Navier-Stokes equations, as $\partial_t {\bf u} = {\cal 
+NS} ({\bf u};p)$, therefore dropping the systematic reference to the 
+incompressibility constraint and associated pressure field.
+
+In the nonlinear régime, the {\em base flow} introduced in the linear theory is not directly accessible and no longer relevant, especially when the oscillation amplitudes become large. 
+Instead, we will define a {\em mean flow}  as the time-average  of the flow :
+\be{defumean}
+{\bf u}_m({\bf x})  = \frac{1}{T} \int_0^{T}  {\bf u}({\bf x},t)  dt
+\ee
+where $T = 2\pi/\omega$ is the period of the oscillation cycle.
+
+A convenient measure of the unsteady part of the flow, which has been adopted in both the WNL and SC models, is the energy-amplitude, defined as the square-root of the total energy associated to the fluctuating part of the velocity field :
+
+\be{defAnergy}
+A_E = \sqrt{\frac{1}{T} \int_0^{T} \left( \int_\Omega | {\bf u} - {\bf u}_m |^2 \, dS \right) dt}
+\ee
+
+Another quantity which has been particularly addressed in previous studies is the mean recirculation length $L_x$
+already discussed introduced and documented in figure ??.
+In the nonlinear regime, the recirculation bubble becomes unsteady so it is difficult to define properly an instantaneous recirculation length.
+It is still possible to define a mean recirculation length associated to the mean flow.
+
+In the next sections we will document the predictions of the WNL and SC models regarding the quantities $A_E$ and $L_x$ adopted in past studies.
+In addition, we will document two other quantities of practical interest : the drag and Lift forces $F_x$ and $F_y$ exerted on the cylinder.
+Both are periodic functions of time, and owing to symmetry consideration, the drag contains only even harmonics and the lift only odd harmonics :
+$$
+F_x  = F_{x,0}  + \Sigma \left(  F_{x,2n,c} \cos 2 n \omega t + F_{x,2n,s} \sin 2 n  \omega t \right)
+$$
+$$
+F_y  =  \Sigma \left(  F_{y,{2n+1},c} \cos (2n+1) \omega t + F_{y,(2n+1),s} \sin (2n+1) \omega t \right)
+$$
+
+In the sequel we will focus on the {\em mean drag}
+ $F_{x,0}$ and the part of the fundamental frequency part of the lift  given by $F_{y,1,c}$ and $F_{y,1,s}$.
+
+%MThe mean drag is given by
+
+%$$F_{x,m} = D(u_m)$$
+%with "Drag" operator defined in equation ().
+
+%The oscillating lift $F_y(t)$  is a	 periodic function of period $T$, and we will 
+%$$F_y = F_y,c
+
+%The first milestone in this direction is the work of Sipp \& Lebedev \cite{SippLebedev} who used a weakly nonlinear development in terms of the distance to the threshold $Re-Re_c$.
+However, although derived on rigorous grounds, the weakly nonlinear development has a very limited range of validity and already fails for $(Re-Re_c) \approx 1$.
+%More recently,  Manti\v{c}-Lugo et al \cite{MLugo2014} proposed an alternative approach termed {\em Self-consistent model} which succeeds in predicting the dynamics up to $Re =120$ and more. 
+%This model was build as a linear stability approach build on a {\em mean flow} which includes a retroaction of the eigenmode. However, if one is interested in the limit cycle and not the transient,
+%the approach is actually equivalent to a Fourier series decomposition of the flow with respect to time (an approach also known as {\em harmonic balance}) retaining only the two first terms. 
 %The approach is based on a generalisation of the eigenmode ansatz \ref{} and
 
-In the next sections, we thus successively present the weakly nonlinear model, the self-consistent model and eventually the harmonic-balance model, and propose a direct resolution method. 
+%In the next sections, we thus successively present the weakly nonlinear model, the self-consistent model, and propose a direct resolution method for this latter model.
+
 %The relation with the initial method of Mantic-Lugo et al. will be discussed afterwards.
@@
 \begin{lstlisting}
-[baseflow,em]=SF_FindThreshold(baseflow,em);
-wnl = SF_WNL(baseflow);
+[bf,em]=SF_FindThreshold(bf,em);
+wnl = SF_WNL(bf,em);
 
@@
 
-baseflow=SF_BaseFlow(baseflow,47.5);
-[ev,em] = SF_Stability(baseflow,'shift',Omegac*i);
+bf=SF_BaseFlow(bf,47.5);
+[ev,em] = SF_Stability(bf,'shift',Omegac*i);
 Astart = sqrt(wnl.Lambda/(wnl.Nu0+wnl.Nu2)*(1/Rec-1/47.5));
-[meanflow,mode] = SF_HarmonicBalance(baseflow,em,'sigma',0.,'Re',47.5,'Aguess',Astart);
+[meanflow,mode] = SF_HarmonicBalance(bf,em,'sigma',0.,'Re',47.5,'Aguess',Astart);
 
@@
 We give here a brief account of the weakly nonlinear model of Sipp \& 
-Lebedev\cite{SippLebedev}, also discussed by
-Gallaire et al. \cite{FDR2016}. The derivation is based on a multiple scale 
-decomposition based on the parameter $\epsilon^2 = 1/Re - 1/Re_c$, and the slow 
-time scale $\tau = \epsilon t$. They started by considering the following asymptotic expansion of the flow state ${\bf{q}}=({\bf{u}},p)$ :
+Lebedev\cite{SippLebedev}, also discussed by Gallaire et al. \cite{FDR2016}. 
+The derivation is based on a multiple scale  decomposition based on the parameter $\epsilon^2 = 1/Re - 1/Re_c$. 
+In the case where we are interested only in the desciption of the saturation cycle, the starting point can be taken as the following expansion of the state-vector ${\bf{q}}=({\bf{u}},p)$ defining the flow :
+
 \begin{eqnarray}
-{\bf q} &=& {\bf q}_{bc} + \epsilon \left[ A_{wnl} (\tau) \hat{\bf q} e^{i \omega_c t} + c.c. \right] \label{WNL1}\\
-&+& \epsilon^2 \left[ {\bf q}_\epsilon + |A_{wnl}|^2  {\bf q}_{2,0} + \left(  A_{wnl}^2 {\bf q}_{2,2} e^{2 i \omega_c t} + c.c. \right) \right] + {\cal O}( \epsilon ^3)
+{\bf q} &=& {\bf q}_{bc} + \epsilon \left[ A_{wnl}  \hat{\bf q} e^{i (\omega_c+\epsilon \omega_\epsilon)  t} + c.c. \right] \label{WNL1}\\
+&+& \epsilon^2 \left[ {\bf q}_\epsilon + |A_{wnl}|^2  {\bf q}_{2,0} + \left(  A_{wnl}^2 {\bf q}_{2,2} e^{2 i(\omega_c+\epsilon \omega_\epsilon)  t} + c.c. \right) \right] + {\cal O}( \epsilon ^3)
 \nonumber
+\label{eq:WNLdevelopment}
 \end{eqnarray}
 where ${\bf q}_{bc}$ is the base flow at the threshold $Re_c$, $\hat{\bf q}$ the neutral 
-eigenmode at $Re_c$, $A_{wnl}(\tau)$ a slowly varying amplitude.
-Substituting the above expansion (\ref{WNL1}) into the Navier-Stokes equations and grouping terms 
-multiplied by the same power of $\epsilon$, a hierarchy of equations is obtained.
-The order $\epsilon^2$ contains three terms respectively computed as the solutions of the following linear problems :
-\begin{eqnarray}
-{\cal L}_{{\bf u}_{bc}} ({\bf u}_\epsilon) + 2 \nabla \cdot {\bf D}( \hat{\bf u}) &=&0,\\
-{\cal L}_{{\bf u}_{bc}} ({\bf u}_{2,0}) &=& {\cal C}(\hat{\bf u},\overline{\hat{\bf u}}),\\
-{\cal L}_{{\bf u}_{bc}} ({\bf u}_{2,2}) - 2 i \omega_c {\bf u}_{2,2}  &=& \frac{1}{2} {\cal C}(\hat{\bf u},\hat{\bf u}).
- \end{eqnarray}
-
-Finally, compatibility conditions are imposed at order $\epsilon^3$ leading to an amplitude equation with the following
-form :
+eigenmode at $Re_c$, $A_{wnl}$, an amplitude, $\omega_c$ the frequency predicted by the linear approach at $Re=Re_c$ and $\omega_\epsilon$ a small deviation of the frequency.
+
+Note that this starting point is slightly different from the original approach of \cite{SippLebedev} who used a multiple scale method and assumed a dependence of the amplitude $A_{wnl}$ as function of a slow time-scale $\tau = \epsilon t$.
+This latter starting point is the righth way to parametrize the problem if one wants to obtain an amplitude equation, but as specified above our goal here is to provide a simpler formulation descibing only the saturated cycle.
+
+Details of the approach are given in the appendix. The outcome is a relationship with the form
+
 \be{WNL3}
-\frac{\partial A_{wnl} }{\partial \tau} = \Lambda A_{wnl} - (\nu_0+\nu_2)  |A_{wnl}|^2 A_{wnl},
-\ee
-where 
-\begin{eqnarray}
-\Lambda &=& \frac{ \left< {\hat{\bf u}}^\dag, 
-\left( {\cal C}({\bf u}_\epsilon, \hat{\bf u}) - 2 \nabla \cdot  {\bf D}( \hat{\bf u}) \right) \right>}
-{  \left<  \hat{\bf u}^\dag,\hat{\bf u} \right> },\\
-\nu_0 &=& -\frac{ \left< {\hat{\bf u}}^\dag,  {\cal C}({\bf u}_{20}, \hat{\bf u} ) \right>}
-{  \left<  \hat{\bf u}^\dag,\hat{\bf u} \right> },\\
-\nu_2 &=& -\frac{ \left< {\hat{\bf u}}^\dag,  {\cal C}({\bf u}_{22}, \overline{\hat{\bf u}})  \right>}
-{  \left<  \hat{\bf u}^\dag,\hat{\bf u} \right> }.
- \end{eqnarray}
+i \omega_\epsilon A_{wnl} = \Lambda A_{wnl} - (\nu_0+\nu_2)  |A_{wnl}|^2 A_{wnl},
+\ee
+
+Where coefficients $\Lambda$, $\nu_0$ and $\nu_2$ are given by eqs. (???)
 
 If one is interested in the amplitude of the limit cycle, we have 
-$|A_{wnl}| = \sqrt{\Lambda_r/(\nu_{0,r}+\nu_{2,r})}$ and eventually, reintroducing the scaling :
-\be{ANL} 
-|A| =  \epsilon |A_{wnl}| = \frac{\Lambda_r}{\nu_{0,r}+\nu_{2,r} } \sqrt{\frac{1}{Re_c}-\frac{1}{Re}}.
-\ee
+$|A_{wnl}| = \sqrt{\Lambda_r/(\nu_{0,r}+\nu_{2,r})}$.
+
+% and eventually, reintroducing the scaling :
+%\be{ANL} 
+%|A| =  \epsilon |A_{wnl}| = \frac{\Lambda_r}{\nu_{0,r}+\nu_{2,r} } \sqrt{\frac{1}{Re_c}-\frac{1}{Re}}.
+%\ee
+
 The frequency of the limit cycle is given by
 \be{omegaWNL} 
-\omega = \omega_c + 
-\left( \Lambda_r - \Lambda_i \frac{\nu_{0,i}+\nu_{2,i} }{\nu_{0,r}+\nu_{2,r} } \right) 
-\left(\frac{1}{Re_c}-\frac{1}{Re}\right).
-\ee
+\omega_\epsilon =  - \Lambda_i \frac{\nu_{0,i}+\nu_{2,i} }{\nu_{0,r}+\nu_{2,r} } 
+\ee
+
+THE MEAN FLOW IS GIVEN BY :
+
+AND THE ASSOCIATED DRAG FORCE IS GIVEN BY :
+
+{\color{blue}
+A key issue in the weakly nonlinear expansion is that the definition of the amplitude depends upon a normalization choice 
+of the eigenmodes. Several choices are possible. In the litterature three possibilities have been used :
+\begin{itemize}
+\item First, \cite{SippLebedev} normalized the eigenmode by assuming a specified value to the $y$-component of the velocity at one point, namely :
+\be{normsipp}
+\hat{u_y}(1,0) = 0.4612
+\ee
+The advantage of this choice is that the amplitude is then a measure of the energy of the perturbation: 
+$\epsilon A_{wnl} \approx A_E$.
+
+\item Secondly, \cite{FDR2016} proposed the following normalisation choice :
+\be{normFDR}
+\int_\Omega |\hat{\bf u}|^2 d {\bf x}  = \frac{1}{2}
+\ee
+This directly leads to $\epsilon A_{wnl} = A_E$.
+
+\item Thirdly, following \cite{Fabre2012}, another convenient choice is to normalize the eigenmode with its lift 
+force : 
+\be{normfabre}
+L(\hat{\bf u};\hat{p}) = 1/2
+\ee
+The advantage of this choice is that the amplitude $\epsilon A_{wnl}$ is directly related to the fundamental lift :
+$
+F_{y,1,c} 
+%= \epsilon A \left( 1/2 e^{i \omega t} + c.c. \right)
+=   \epsilon A \cos (\omega t) ; \quad F_{y,1,c} = 0. 
+$
+
+\end{itemize}
+}
+
+In our implementation of the WNL approach, we allowed to choose the normalization convention. 
+In table (??) we give the predictions of the WNL approach using the three normalization choices.
+We can note that the coefficients $\nu_0$ and $\nu_2$ strongly depend on the normalization choice.
+on the other hand, the frequency deviation as well as the drag and lift coefficients are independent of it.
+
+\begin{table}
+$$\begin{array}{cc}
+a&b
+\end{array}$$
+\caption{Coefficients of the weakly nonlinear coefficients : }
+\end{table}
 
@@
 \paragraph{Self-Consistent approach}
+
+TO BE SHORTENED
+
 \begin{figure}
@@
 \paragraph{Harmonic balance : equations and procedure }
+
+TO BE SIMPLIFIED...
+
 \begin{figure}
@@
 \be{HB}
-{\bf u } = {\bf u }_0 + {\bf u }_1 e^{i \omega t} +   {\bf u }_{-1} e^{-i \omega t}.
-\ee  
+{\bf u } = {\bf u }_m + {\bf u }_{1,c} \cos( \omega t ) +   {\bf u }_{1,s} \sin( \omega t )
+\ee
+
+The connection with the definition of Mantic-Lugo is as follows :
+\be{HBtoSC}
+\left( {\bf u }_{1,c} - i {\bf u }_{1,s} \right) = 2 A_{sc} \tilde{{\bf u }}_1
+\ee
+
 Here ${\bf u }_0$ is the mean flow (averaged over time),  ${\bf u }_1$ is the mode
@@
 Injecting this ansartz into the Navier-Stokes equations and taking the mean value and the first Fourier component leads to the following coupled equations :
+
+CHECK !!!
+
 \be{HBEq0}
-{\cal NS}(  {\bf u }_0 ) - {\cal C}( {\bf u }_1, \overline{\bf u }_1) = 0,
+{\cal NS}(  {\bf u }_0 ) - \frac{{\cal C}( {\bf u }_{1,c}, {\bf u }_{1,c}) +{\cal C}( {\bf u }_{1,s}, {\bf u }_{1,s})}{2}  = 0,
 \ee
 \be{HBEq1}
-i \omega {\bf u }_1 =  {\cal L}_{{\bf u }_0}(  {\bf u }_1 ).
+ \omega {\bf u }_{1,s} =  {\cal L}_{{\bf u }_0}(  {\bf u }_{1,c} ).
+\ee
+
+\be{HBEq1b}
+ -\omega {\bf u }_{1,c} =  {\cal L}_{{\bf u }_0}(  {\bf u }_{1,s} ).
 \ee
@@
 
+\begin{table*}
+$$
+\begin{array}{|c||c|c|c|c|c|c|c|c|c|}
+\hline
+\mbox{Mesh} & N_v & N_{ddl} & \delta_{min} & \delta_{max} & \delta_A  & \delta_B  & \delta_C  & \delta_D  \\
+\hline
+\mathbf{M}_0 \mbox{(Adapt on base flow) } & 1429 & 		& 0.0131 & 14.33 		& 0.0259 	& 0.514 	& 0.819 	& 1.067 \\   
+\mathbf{M}_1 \mbox{(Adapt on sensitivity) } & 2038 & 		& 0.0155 & 14.17 		& 0.02826 & 0.2046 	& 0.3909 	& 1.2014 	\\
+\mathbf{M}_2 \mbox{(Adapt on sensitivity, split) } & 7974 &		& 0.0077 & 7.1  		& 0.014 	& 0.1 	&   0.2 	& 0.6   \\
+\mathbf{M}_3 \mbox{(Adapt on mode) } 	& 12080  &			&0.00825	& 124.61		& 0.0229	& 0.143	& 0.0993	& 0.0934 \\
+\mathbf{M}_4 \mbox{(Adapt on adjoint) } 	& 11564 	&		& 0.0091	& 14.14		& 0.0228	& 0.130	& 0.109	& 0.0796  \\
+\hline
+\end{array}
+$$
+\caption{Description of meshes used for validation of mesh adaptation strategy}
+\end{table*}
+
+\begin{table*}
+$$
+\begin{array}{|c||c|c||c||c|c||c|c|c|}
+\hline
+\mbox{Mesh} & L_x & F_x & \lambda & L_{x,SC} & F_{x,SC} & \omega_{SC}  & F_{Y,SC} & A_{E,SC} \\
+\hline
+\mathbf{M}_0 & 4.0733 & 0.6431 	& 0.047056 + 0.74416i 		& 2.6073  &0.69277 		&  0.84334 & 0.1298 & 1.8301  \\
+\mathbf{M}_1 & 4.075 &.  0.64348  	& 0.046719 + 0.74489i 		& 2.          & 0.69246 	& 0.84351 & 0.12789 & 1.7134 \\  
+\mathbf{M}_2 & 4.0772 & 0.64391 	& 0.04684. +  0.74511i 		& 2.6141  & 0.69338 	& 0.84383 & 0.12799 & 2.048   \\ 
+\mathbf{M}_3 & 4.0748 & 0.64402 	& 0.04676  + 0.74502i 		& 2.613 	& 0.690338 	& 0.84371 & 0.12809 & 2.5905 \\
+\mathbf{M}_4 & 4.0772 & 0.64384	& 0.046857+0.74511i 		& 2.6146 	& 0.6932		& 0.84333 & 0.1276	 & 2.5971 \\
+\hline
+\end{array}
+$$
+\caption{Results for mesh adaptation strategy ($Re = 60$)}
+\end{table*}
+
+\begin{table*}
+$$
+\begin{array}{|c|c||c|c||c||c|c||c|c|c|}
+\hline
+\mbox{Mesh} & N & L_x & F_x & \lambda & L_{x,SC} & F_{x,SC} & \omega_{SC}  & F_{Y,SC} & A_{E,SC} \\
+\hline
+\mathbf{M}_2 \mbox{(ref)} 	& 7974  	& 4.0772 & 0.64391 	& 0.04684. +  0.74511i 	& 2.6141  & 0.69338 	& 0.84383 & 0.12799 & 2.048   \\
+
+\mathbf{M}_5 [-20,40]x[0,20] 	& 7437	&  4.108 & 0.64987 	& 0.048368. +  0.74952i 	& 2  & 0.69957 	& 0.85015 & 0.13125 & 2.3638   \\ 
+\mathbf{M}_6 [-80,160]x[0,80] 	& 7480	& 4.0641 & 0.64129		& 0.046271 + 0.74341i 	& 2 	& 0.69069 	& 0.84159 & 0.12653 & 2.4453 \\
+\mathbf{M}_7 \mbox{(slip conditions)}	 & 7056	& 4.0467 &0.66295		& 0.049216+0.76553i 	& 2 	& 0.69241		& 0.8438  & 0.12716	 & 2.3202 \\
+\hline
+\end{array}
+$$
+\caption{Results for mesh adaptation strategy ($Re = 60$)}
+\end{table*}
+
+\section{detail of WNL approach}
+
+Substituting the above expansion (\ref{WNL1}) into the Navier-Stokes equations and grouping terms 
+multiplied by the same power of $\epsilon$, a hierarchy of equations is obtained.
+The order $\epsilon^2$ contains three terms respectively computed as the solutions of the following linear problems :
+\begin{eqnarray}
+{\cal L}_{{\bf u}_{bc}} ({\bf u}_\epsilon) + 2 \nabla \cdot {\bf D}( \hat{\bf u}) &=&0,\\
+{\cal L}_{{\bf u}_{bc}} ({\bf u}_{2,0}) &=& {\cal C}(\hat{\bf u},\overline{\hat{\bf u}}),\\
+{\cal L}_{{\bf u}_{bc}} ({\bf u}_{2,2}) - 2 i \omega_c {\bf u}_{2,2}  &=& \frac{1}{2} {\cal C}(\hat{\bf u},\hat{\bf u}).
+ \end{eqnarray}
+
+Finally, compatibility conditions are imposed at order $\epsilon^3$ lead to
+
+\be{WNL3}
+i \omega_\epsilon A_{wnl} = \Lambda A_{wnl} - (\nu_0+\nu_2)  |A_{wnl}|^2 A_{wnl},
+\ee
+
+\begin{eqnarray}
+\Lambda &=& \frac{ \left< {\hat{\bf u}}^\dag, 
+\left( {\cal C}({\bf u}_\epsilon, \hat{\bf u}) - 2 \nabla \cdot  {\bf D}( \hat{\bf u}) \right) \right>}
+{  \left<  \hat{\bf u}^\dag,\hat{\bf u} \right> },\\
+\nu_0 &=& -\frac{ \left< {\hat{\bf u}}^\dag,  {\cal C}({\bf u}_{20}, \hat{\bf u} ) \right>}
+{  \left<  \hat{\bf u}^\dag,\hat{\bf u} \right> },\\
+\nu_2 &=& -\frac{ \left< {\hat{\bf u}}^\dag,  {\cal C}({\bf u}_{22}, \overline{\hat{\bf u}})  \right>}
+{  \left<  \hat{\bf u}^\dag,\hat{\bf u} \right> }.
+ \end{eqnarray}
+
 \section{Detail of the weak formulation}

### 2018-05-24 ARTICLE_STABFEM/ARTICLE_ASME_V2.tex
version 2 of the paper

@@
 
+%\begin{figure}
+%\begin{center}
+%\includegraphics[width=.9 \linewidth]{Cylinder_SC100_EnergySigma.png}
+%\includegraphics[width=.9 \linewidth]{Cylinder_SC100_CySigma.png}
+%\end{center}
+%\caption{Self-consistent approach for the wake of a cyrcular cilinder: results at $Re =  100$.}
+%\label{fig:SC100}
+%\end{figure}
+
 \begin{figure}
 \begin{center}
-\includegraphics[width=.9 \linewidth]{Cylinder_SC100_EnergySigma.png}
-\includegraphics[width=.9 \linewidth]{Cylinder_SC100_CySigma.png}
+\includegraphics[width=.9 \linewidth]{toto.png}
 \end{center}
-\caption{Self-consistent approach for the wake of a cyrcular cilinder: results at $Re = 
+\caption{Self-consistent approach for the wake of a circular cilinder:  description of the MEAN FLOW for  $Re = 
 100$.}
-\label{fig:SC100}
+\label{fig:MF60}
 \end{figure}
+
 We now briefly review the self-consistent approach as introduced by Manti\v{c}-Lugo et 
@@
 Injecting and developing up to linear order leads to the following
+
+TO BE CORRECTED !
+
 \begin{equation}
@@
 \section*{Appendix A : details on mesh convergence}
-\begin{figure}
-\includegraphics[width=.9 \linewidth]{Cylinder_Sigma_Re_TESTMESHES.png}
-\includegraphics[width=.9 \linewidth]{Cylinder_Strouhal_Re_TESTMESHES.png}
-\caption{Growth rate $\sigma$ $(a)$  and Strouhal number $St = (a \omega)/(2\pi U_0)$ ($b$) as function of Reynolds number FOR 8 DIFFERENT MESHES}
-\label{fig:MeshConvergence}
-\end{figure}
-
-\begin{figure*}
-\small
-\begin{lstlisting}
-> baseflow=SF_Init('Mesh_Cylinder_Large.edp');
-      ### INITIAL MESH CREATED WITH np = 2207 points
-> baseflow=SF_BaseFlow(baseflow,'Re',1);
-      ### FUNCTION SF_BaseFlow : computing base flow for Re = 1
-      # Base flow converged in 6 iterations ; Drag = 5.9876; Lx = 0.501
-> baseflow=SF_BaseFlow(baseflow,'Re',10);
-      ### FUNCTION SF_BaseFlow : computing base flow for Re = 10
-      # Base flow f converged in 5 iterations ; Drag = 1.4519; Lx = 0.73191
-> baseflow=SF_BaseFlow(baseflow,'Re',60);
-      ### FUNCTION SF_BaseFlow : computing base flow for Re = 60
-      # Base flow converged in 6 iterations ; Drag = 0.66348; Lx = 3.6989
-
-> baseflow=SF_Adapt(baseflow,'Hmax',10,'InterpError',0.01);
-     ### ADAPT mesh to base flow ; InterpError = 0.01  ; Hmax = 10
-      #   Number of points np = 1352 ; Ndof = 11862
-      #  h_min, h_max : 0.018824 , 10.2895
-      #  h_(A,B,C,D) : 0.027467 , 0.28644 , 0.45948 , 0.89245
-      ### FUNCTION SF_BaseFlow : computing base flow for Re = 60
-      # Base flow converged in 5 iterations ; Drag = 0.65805; Lx = 4.0737
-
-> plotFF(baseflow,'mesh');
-\end{lstlisting}
-\normalsize
-\caption{Illustration of the procedure to compute a base flow and an adapted mesh using StabFem (from script {\em SCRIPT\_CYLINDER.m}. }
-\label{ill_bsflow}
-\end{figure*}
-
-\begin{figure*}
-\small
-\begin{lstlisting}
-> [ev,em] = SF_Stability(baseflow,'shift',0.04+0.76i,'nev',1,'type','D');
-> [baseflow,em]=SF_Adapt(baseflow,em,'Hmax',10,'InterpError',0.005);  
-      ### ADAPT mesh to base flow AND MODE   ; InterpError = 0.005  ; Hmax = 10
-      #   Number of points np = 13458 ; Ndof = 120030
-      #  deltamin, deltapax : 0.0089891 , 13.367
-      #  delta_(A,B,C,D) : 0.020536 , 0.082852 , 0.07316 , 0.11914
-      ### FUNCTION SF_BaseFlow : computing base flow for Re = 60
-      # Base flow converged in 4 iterations ; Drag = 0.64695; Lx = 4.0715
-      ### FUNCTION SF_Stability : computation of 1 eigenvalues/modes (DIRECT) with FF solver
-      # Stability calculation converged in 4 iterations, lambda = 0.047152+0.74808i.
-
-> [ev,em] = SF_Stability(baseflow,'shift',0.04+0.76i,'nev',1,'type','S');
-> [baseflow,em]=SF_Adapt(baseflow,em,'Hmax',10,'InterpError',0.005);
-      ### ADAPT mesh to base flow AND SENSITIVITY ; InterpError = 0.005  ; Hmax = 10
-      #   Number of points np = 4355 ; Ndof = 38559
-      #  deltamin, deltapax : 0.0058536 , 13.1164
-      #  delta_(A,B,C,D) : 0.01049 , 0.091861 , 0.13319 , 0.89372
-      ### FUNCTION SF_BaseFlow : computing base flow for Re = 60
-      # Base flow converged in 3 iterations ; Drag = 0.64758; Lx = 4.0725
-      ### FUNCTION SF_Stability : computation of 1 eigenvalues/modes (DIRECT) with FF solver
-      # Stability calculation converged in 3 iterations (D+A+S), lambda = 0.047165+0.74823i.
-
-\end{lstlisting}
-\normalsize
-
-\caption{Illustration of the procedure to adapt the mesh for stability calculations with StabFem (from script {\em SCRIPT\_CYLINDER.m}. }
-\label{stabmesh}
-\end{figure*}
+
+TO BE FINISHED
 

### 2018-06-12 99_Documentation/diogo_perso.tex
New version of Paper : V4 (plus little fixes at various places)

\begin{tikzpicture}
\tikzset{every node/.style={on chain,draw,thick,rounded corners,
minimum height=3em, text width=10em, align=center}}
\begin{scope}[start chain=going below]
\node (prepare-group) {Prepare group list (\texttt{.csv})};
\node (import-group) {Import group list for new score file (\texttt{.xml})};
\node (enter-rating) {Enter peer ratings given by each student};
\node (compute-score) {Compute autorated weights and scores};
\node (export-csv) {Export data for Excel (\texttt{.csv})};
\end{scope}
\node[right=of enter-rating] (open-score) {Open previously saved score file (\texttt{.xml})};

\path[draw,line width=0.4ex, ->,>= angle 60]
(prepare-group) edge (import-group) 
(import-group) edge (enter-rating)
(open-score) edge (enter-rating)
(enter-rating) edge (compute-score) 
(compute-score) edge (export-csv);
\end{tikzpicture}

### 2018-06-12 ARTICLE_STABFEM/ARTICLE_ASME_V4.tex
New version of Paper : V4 (plus little fixes at various places)

%%%%%%%%%%%%%%%%%%%%%%%%%%% asme2ej.tex %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Template for producing ASME-format journal articles using LaTeX    %
% Written by   Harry H. Cheng, Professor and Director                %
%              Integration Engineering Laboratory                    %
%              Department of Mechanical and Aeronautical Engineering %
%              University of California                              %
%              Davis, CA 95616                                       %
%              Tel: (530) 752-5020 (office)                          %
%                   (530) 752-1028 (lab)                             %
%              Fax: (530) 752-4158                                   %
%              Email: hhcheng@ucdavis.edu                            %
%              WWW:   http://iel.ucdavis.edu/people/cheng.html       %
%              May 7, 1994                                           %
% Modified: February 16, 2001 by Harry H. Cheng                      %
% Modified: January  01, 2003 by Geoffrey R. Shiflett                %
% Use at your own risk, send complaints to /dev/null                 %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%% use twocolumn and 10pt options with the asme2ej format

\documentclass[twocolumn,10pt]{asme2ej}

\usepackage[none]{hyphenat}
\usepackage{epsfig} %% for loading postscript figures
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{breqn}

% color code for matlab (thanks to SOUAD !)
\usepackage{listings} 
\lstset{language=Matlab}
\usepackage{color} %red, green, blue, yellow, cyan, magenta, black, white
\definecolor{mygreen}{RGB}{28,172,0} % color values Red, Green, Blue
\definecolor{mylilas}{RGB}{170,55,241}

\lstset{language=Matlab,%
   %basicstyle=\color{red},
   breaklines=true,%
   morekeywords={matlab2tikz},
   keywordstyle=\color{blue},%
   morekeywords=[2]{1}, keywordstyle=[2]{\color{black}},
   identifierstyle=\color{black},%
   stringstyle=\color{mylilas},
   commentstyle=\color{mygreen},%
   showstringspaces=false,%without this there will be a symbol in the places where there is a space
   numbers=left,%
   frame=trBL,
   numberstyle={\tiny \color{black}},% size of the numbers
   numbersep=9pt, % this defines how far the numbers are from the text
   emph=[1]{for,end,break},emphstyle=[1]\color{red}, %some words to emphasise
   %emph=[2]{word1,word2}, emphstyle=[2]{style},   
   }

\graphicspath{{./}{./FIGURES/}}

% previous way
%\usepackage{listings}
\usepackage[colorlinks, linkcolor=blue, citecolor=blue,filecolor=black,urlcolor=blue]{hyperref}

\newcommand{\be}[1]{ \begin{equation} \label{#1}}
\newcommand{\ee}{\end{equation}}

\newcommand{\bes}[1]{ \begin{equation} \label{#1}\begin{array}{rl}}
\newcommand{\ees}{\end{array}\end{equation}}

%% The class has several options
%  onecolumn/twocolumn - format for one or two columns per page
%  10pt/11pt/12pt - use 10, 11, or 12 point font
%  oneside/twoside - format for oneside/twosided printing
%  final/draft - format for final/draft copy
%  cleanfoot - take out copyright info in footer leave page number
%  cleanhead - take out the conference banner on the title page
%  titlepage/notitlepage - put in titlepage or leave out titlepage
%  
%% The default is oneside, onecolumn, 10pt, final

%\title{Popularizing linear and nonlinear global approaches to hydrodynamic instabilities : 
%A review and a simple implementation for the wake of a cylinder}

\title{A {practical} review on linear and nonlinear global approaches to stability analysis}

%%% first author
\author{D. Fabre$^{(a)}$,  V. Citro$^{(b)}$,  D. Ferreira Sabino$^{(a)}$, P. Bonnefis$^{(a)}$,  \& F. Giannetti$^{(b)}$
    \affiliation{
	$^{(a)}$ Institut de Mécanique des fluides de Toulouse (IMFT), University of Toulouse \\
	$^{(b)}$ Dipartimento do Ingegneria (DIIN), Università di Salerno.
    }

}

%%% second author
%%% remove the following entry for single author papers
%%% add more entries for additional authors
%\author{V. Citro$^{(b)}$ \& F. Giannetti$^{(b)}$ \\
 %   \affiliation{ University of Salerno
  %  }
%}

\usepackage{cprotect}

\begin{document}
\lstset{numbers=left, numberstyle=\small, numbersep=8pt, frame = single, language=Matlab, framexleftmargin=15pt}

\maketitle

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
{\it 
This paper is aimed to review the linear and nonlinear approaches to study the stability of fluid flows. 
We provide a concise but self-contained exposition of the main concepts and specific numerical methods 
designed for global stability studies, including the classical linear stability analysis, the adjoint-based sensitivity and  
the most recent nonlinear developments. 
Regarding numerical implementation, a number of ideas making resolution particularly efficient are discussed, 
including mesh adaptation, simple shift-invert strategy instead of the classical Arnoldi algorithm, 
and a simplification of the recent nonlinear self-consistent approach proposed by Manti\v{c}-Lugo et al \cite{MLugo2014}. 
An open-source software implementing all the concepts discussed in the present paper is provided. 
The software is demonstrated for the reference case of the incompressible, two-dimensional flow around a circular cylinder, but is easily customisable to a variety of other flow configurations or flow equations.
%An abstract for an ASME paper should be less than 150 words and is normally in italics.
}
\end{abstract}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Introduction}

The concept of stability bears on the reaction of a system to a small perturbation of its state. If the generic disturbance grows in time, the system is unstable. The concept of stability can be simply formulated for a system of Ordinary Differential Equations (ODE). 
Such systems can be at equilibrium, where the state does not depend on time, or can present a periodic state, with all components returning to the same values, after every period.

The stability of fluid flows usually depends on the value of a given parameter. A bifurcation occurs when a critical value is reached and the original solution becomes linearly unstable, with the system tending towards a new steady or unsteady state. 
%The destabilization of a flow as a parameter is varied, leading from a steady solution to a unsteady one, is an ubiquous situation in fluid dynamics. 
In the second part of the 19th century, specific analytical and numerical methods able to study these bifurcations have emerged and are continuously evolving up to the present days. 
A crucial point, that drove the development in this field, is the availability of larger and larger computing resources. 
Initially, the linear stability theory focused on fluid flows that are homogeneous in two spatial directions, e.g. plane Poiseuille flow \cite{Dreid2004}. This implies that the streamwise and the spanwise base-flow gradients vanish and, as a consequence, it is possible to consider only one (streamwise) velocity component. Thus, the stability problem requires a \textit{local} numerical resolution, i.e. a one-dimensional problem.
On the other hand,  when there are at least two spatial variables, the class of methods suited to solve such problems are generally called "global stability approaches".
%When the flow has no analytical expression, the stability problem requires a numerical resolution, and when there are at least two spatial variables, the class of methods suited to solve such problems are generally called "global stability approaches."%\footnote{Sorry Laurette !}
A classical example of such behavior in fluid dynamics is the instability occurring in the wake of a circular cylinder. At low Reynolds number (precisely for $Re < 46.7$) the flow is steady and symmetric, but for larger values of Re a global instability arises in the flow field leading to the well-known von K\'arm\'an vortex alley. 
%Among all instability problems, one of the most famous and most studied is the flow around a 2D cylinder, which becomes unsteady for $Re \approx 47$ leading to the well-known Bénard-Von Karman vortex alley. 
This flow configuration has served as a benchmark in the development of this class of methods.  
If one is only interested in predicting the stability or instability of a flow, it is enough to conduct a {\em linear stability analysis} which is the fundamental brick of global stability approaches. 
Beyond this simple question, in the past two decades, a number of extensions have been developed and popularized.  {\em Adjoint methods} are an important extension \cite{GiannettiLuchini},\cite{Marquet} ; they can give insight into the sensitivity of the flow to intrinsic or extrinsic contributions. 
{\em Nonlinear stability approaches} \cite{MLugo2014}, \cite{SippLebedev} have also been developed in order to extend the range of applicability of the approach towards large amplitude perturbations.

%Among many others, the most noticable milestones are [?] for basic stability analysis,
%and for adjoint and sensitivity approaches, and for nonlinear approaches.

%Many discretization of spatial derivative operators (finite differences, spectral methods, ...) can be used to build. and is now routinely used by a growing number of teams

The objective of the present work is to contribute to the popularization of such methods 
in two ways:
%for both research and education purposes. 
\begin{itemize}
\item
First, we give a concise but self-contained exposition of the main concepts and 
specific numerical methods pertaining to global stability, including basic linear stability, adjoint-based sensitivity, as well as the most recent nonlinear developments.
\item
Secondly we offer an open-source and user-friendly software called  "StabFem"
\cprotect\footnote{The StabFem software may be obtained at the following url : 
\url{https://github.com/erbafdavid/StabFem}} 
to perform such calculations. The software combines program written in both FreeFem++ and Matlab languages. 
FreeFem++ is used to generate and adapt the meshes and to solve the various linear problems arising in the analysis. Matlab is used as a driver to monitor the computations, perform the required loops over parameters, and plot the results.
\end{itemize}

In the present paper the concepts are introduced and the software is demonstrated for the reference case of the incompressible, two-dimensional flow around a cylinder, but the software is easily customizable to a variety of other situations (compressible, three-dimensional, etc..).

Although we don't claim to invent any radically new method, our exposition and implementation contains a number of originalities making the computation particularly efficient in terms of computational time and memory (all the figures of the paper can be produced in only a few minutes on a standard laptop)
\footnote{All the figures contained in the present paper can be processed by launching a single Matlab script SCRIPT\_CYLINDER\_ALLFIGURES.m . On a MacbookPro (2018,  2.5Ghz, 16Go Ram),  the execution time is 19.76 seconds for the results of the linear analysis (section 3) and 15. seconds for the results of the nonlinear analysis (section 4).
}. 
The most notable originalities are the systematic use of mesh adaptation (\S 2 and 3), the use of simple shift-invert instead of Arnoldi (\S 3), and a reformulation and simplification of the nonlinear self-consistent approach of Mantic-Lugo et al  (\S 4).

%which is based on both FreeFem++ and Matlab.
%The fundamental case of a cylinder is used as a guideline to present the method, but the 
%provide a simple and all-in-one implementation of

\section{Linear stability analysis : equations and methods}
\vspace{.2cm}

\subsection{Computing a base-flow with Newton iteration}
\vspace{.2cm}

\paragraph{Navier-Stokes equations and weak form}

We start from the general problem of a flow field $[{\bf u},p]$ satisfying the incompressible Navier-Stokes equations on a domain $\Omega$,
\begin{eqnarray} \label{NSprimitive}
\partial_t {\bf u} = {\color{red}{\cal NS} ({\bf u},p)}
\equiv - {\bf u} \cdot \nabla {\bf u} - \nabla p + \frac{2}{Re}  \nabla \cdot {\mathsf{D}}({\bf u}),  \\
\nabla \cdot {\bf u} = 0,
\end{eqnarray}
with suitable boundary conditions on the frontier $\partial \Omega$ of the domain.
Here $ {\mathsf{D}}({\bf u}) $ is the rate-of-strain tensor defined as
$$
 {\mathsf{D}}({\bf u}) = 1/2
\left( \nabla {\bf u} +  \nabla^T  {\bf u}\right),
$$ 
In the framework of finite element methods, we need to write the equation in weak form.
Prior to this we define a scalar product as follows, for either scalar or vectorial quantities 
$\left< \phi_1, \phi_2 \right> $:
$$
\left< \phi_1, \phi_2 \right> = \int_\Omega \overline{\phi}_1 \cdot \phi_2   \mbox{ d} \Omega,
$$
The weak form of the Navier-Stokes equations is readily defined by introducing test functions 
$[{\bf v},q]$ associated with the momentum and continuity equations, and integrating over the domain\footnote{In the simple presentation given here we have omitted the issue of boundary conditions. Details on way boundary conditions can be incorporated in the weak formulation through integration by parts can be found in appendix A.}
\be{NSweak}
\forall [{\bf v},q], \quad \partial_t \left< {\bf v}, {\bf u}\right> = \left< {\bf v} , {\color{red}{\cal NS} ({\bf u},p)} \right> + \left< q, \nabla \cdot {\bf u}\right>.
\ee

\paragraph{Newton iteration}

We look for a steady base-flow {\color{red}$[{\bf u}_b,p_b]$} satisfying the steady Navier-Stokes equations, i.e. 
%${\cal NS} ({\bf u}_b,p_b) = 0$.
{\color{red}${\cal NS} ({\bf u}_b,p_b) = 0$.}
Suppose that we have a {\color{red}``guess''}  for the base flow $[{\bf u}_b^g,p_b^g]$  which almost satisfies the equations.  We look for a better approximation under the form
\be{Newton1}
[{\bf u}_b,p_b]  = [{\bf u}_b^g,p_b^g] + [\delta {\bf u}_b, \delta p_b].
\ee
Injecting (\ref{Newton1}) into the weak form (\ref{NSweak}) of the Navier-Stokes equations and developing up to linear terms in terms of the perturbation lead to  
${\cal NS}  ({\bf u}_b^g,p_b^g) + {\color{red} {\cal LNS} _{{\bf u}_b^g}(\delta {\bf u}_b,\delta p_b)}$, which can also be written in weak form as :
\bes{Newton2}
&\left< {\bf v}, {\color{red}{\cal NS} ({\bf u}_b^g,p_b^g)}\right> + \left<q, \nabla \cdot {\bf u}_b^g\right>  
\\
+ &\left< { \bf v}, {\color{red}{\cal LNS} _{{\bf u}_b^g}( \delta {\bf u}_b,\delta p_b) }\right> + \left<q, \nabla \cdot \delta{\bf u}_b\right> = 0,
\ees
where ${\cal LNS}$ is the linearised Navier-Stokes operator, defined by its action on a flow field {\color{red}$[{\bf u} , p]$} as follows 
\be{defNSL}
{\color{red} {\cal LNS}_{{\bf U}}( {\bf u}, p)} = - {\cal C}( {\bf U} , {\bf u}) -\nabla p
+\frac{2}{Re} \nabla  \cdot {\mathsf{D}}({\bf u}), %\quad ( \mbox{ with } \nabla \cdot {\bf u } = 0 \, ).
 \ee
and ${\cal C}$ is the convection operator defined by 
\be{defC}
{\cal C}( {\bf U} , {\bf u}) = \left( {\bf U} \cdot \nabla \right) {\bf u} + \left( {\bf u} \cdot \nabla \right)  {\bf U}.
\ee
This problem can now be discretized by projecting upon a basis of Taylor-Hood $(u,v,p) \rightarrow (P2,P2,P1)$ finite elements. Noting $\delta X$ the discretization of {\color{red}$[\delta {\bf u}_b,\delta p_b]$} this eventually leads to a matricial problem of the form $A \cdot \delta X = Y$. The procedure of Newton iteration is to solve iteratively this set of equations up to convergence.
In our implementation, the algorithm is written in the Freefem++ solver {\em Newton\_2D.edp} 
which is wrapped by the Matlab driver {\em Freefem\_BaseFlow.m}.

\subsection{Linear stability}
\vspace{.2cm}

\paragraph{Direct eigenvalue problem}
We study the onset of the instability within the linear theory by using a normal-mode analysis:
\be{startmodepropre}
{\bf u} ({\bf{x}},t) = {\bf u}_b({\bf{x}}) + \epsilon \hat{\bf u}({\bf{x}}) e^{\lambda t}, \,\,\,\, {p}({\bf{x}},t) = {p}_b({\bf{x}}) + \epsilon \hat{p}({\bf{x}}) e^{\lambda t},
\ee
where $\lambda = \sigma + i \omega$ is the eigenvalue, $\sigma$ the amplification rate,
$\omega$ the oscillation rate, $\hat{{\bf u}},\hat{p}$ the eigenmodes, and $\epsilon$ a small parameter.
The eigenmodes and the eigenvalues are the solution of the following eigenproblem:
 \be{LEP}
\lambda \hat{{\bf u}} = {\cal LNS}_{{\bf u}_b}( \hat{\bf u},\hat{p}),
\ee
or, in weak form : 
\be{eigenvalueproblem}
\lambda \left< {\bf v} , \hat{{\bf u}} \right> = \left< {\bf v}, {\cal LNS}_{{\bf u}_b} ( \hat{\bf u},\hat{p})\right> + \left< q, \nabla \cdot \hat{\bf u} \right>.
\ee
After discretization, we end up with an eigenvalue problem with the matricial form
\be{Eigen_matricial}
\lambda {\mathsf{B}} \hat{X} = {\mathsf{A}} \hat{X},
\ee
{\color{red} where} ${\mathsf{A}}$ is the matrix resulting from the discretization of ${\cal LNS}_{{\bf u}_b}$, i.e. the same matrix  appearing in the Newton computation of the base flow, and  $B$ is a 'weight' matrix associated to the scalar product $\left<v,u\right> = \int \overline{\bf v} \cdot {\bf u} \mbox{ d} \Omega$.

\paragraph{Adjoint eigenvalue problem and structural sensitivity}
Developed in the two past decades, the concept adjoint modes has now become an unavoidable complement to the linear global stability approach. We here give a short summary of the definition and usefulness of this concept, 
we refer to Luchini \& Bottaro\cite{LucBott2014} for further details.
First of all, the {\em adjoint linearised Navier-Stokes operator} ${\cal LNS}^\dag$ is defined thanks to the following 
property:
\bes{NSLAdj}
\forall ( {\bf u}, p ; {\bf v}, q), & \left< {\cal LNS}^\dag_{\bf U}( {\bf v},q) ,{\bf u}\right> + \left< \nabla \cdot {\bf v},p\right>  \\
=& \left< {\bf v}, {\cal LNS}_{\bf U} ({\bf u},p)\right> + \left< q, \nabla \cdot {\bf u}\right>.
\ees
We can then define the adjoint eigenvalues and eigenmodes as the solutions of the eigenvalue problem 
\be{EigenAdj} 
\forall ( {\bf u}, p), \quad  \lambda^\dag \left< \hat{\bf v}, {\bf u}\right> =
 \left< {\cal LNS}^\dag_{\bf U}( \hat{\bf v},\hat{q}) ,{\bf u}\right> + \left< \nabla \cdot \hat{\bf v},p\right> . 
\ee
It can be shown \cite{SchmidHenningson2001} that the adjoint eigenvalues $\lambda^\dag_k$ are the complex conjugates of the direct eigenvalues $\lambda_k$.

Although the concept of adjoint operator may sound complicate, the resolution of the adjoint problem using finite elements methods is actually extremely easy. In effect, the scalar product used in the definition of the weak formulation and that appearing in the definition of adjoint being the same, the weak formulations of both problems are thus identical when exchanging the test functions and the unknown functions. Thus the matricial form of the discretized version of (\ref{EigenAdj}) is deduced from the one of the direct problem by a simple (Hermitian) transpose of the matrix :
\be{Eigen_Adj_matricial}
\overline{\lambda}^\dag B \hat{X}^\dag = A^T \hat{X}^\dag.
\ee
Adjoint eigenmodes are a powerful tool for investigating problems such as receptivity, transient growth, control and sensitivity (see the reviews of \cite{Jmc2005}, \cite{Ps2007}, \cite{LucBott2014}). The simplest physical interpretation of an adjoint eigenmode is as follows : it corresponds to the initial condition which has maximum projection along the direction of the corresponding eigenmode.
Thus, the adjoint of the most amplified mode corresponds to the optimal perturbation which will maximize the growth of energy in the limit of large time. In effect, one can prove that for $t \rightarrow \infty$  the asymptotic behaviour of a solution with initial condition ${\bf u}_i$  is given as :
$$
{\bf u}(t) \approx 
\frac{ \left< \hat{\bf u}^\dag, {\bf u}_i\right>}{\left<\hat{\bf u}^\dag, \hat{\bf u}\right>} 
e^{\lambda t} \hat{\bf u}.
$$
The choice ${\bf u}_i = \hat{\bf u}^\dag$ is the initial condition of norm unity which maximizes the first factor in this expression.

The adjoint eigenmode also allows us to introduce the so-called {\em structural sensitivity tensor } that is defined as 
\be{Structursens} 
{\bf{S}}({\bf{x}}) = \frac{|| \hat{\bf u}^\dag|| \,\, ||\hat{\bf u}|| }{{\left<\hat{\bf u}^\dag, \hat{\bf u}\right>}},
\ee 
which has became popular in the recent years.
%is called the structural sensitivity of the eigenmode. 
This quantity is a direct and practical measure of the effect of perturbations of the linear operator on the eigenvalue. The region of the flow where ${\bf{S}}({\bf{x}})$ reaches its maximum values is, thus, the region where the instability mechanism originates, and is often referred to as the {\em wavemaker region}.

%\end{itemize}

\paragraph{Iterative methods for eigenvalue computations}

When it comes to the numerical resolution of generalized eigenvalue problems such as $A X = \lambda B X$ (or its adjoint version (\ref{Eigen_Adj_matricial}) ), several methods are possible. Direct methods to compute the whole spectrum are both costly prohibitive and useless. A popular alternative is the use of iterative methods which allow us to compute a limited set of eigenvalues located in the vicinity of a 
"shift" value $\lambda_{shift}$. The simplest version of this method is the simple shift-invert iteration, which consists of solving iteratively the system
$$
X^{n} =  (A- \lambda_{shift} B)^{-1} B X^{n-1}.
$$ 
It is easy to show that this iterative procedure quickly asymptotes to $X^{n+1} \approx ({\lambda^*}^{-1})^n \hat{X}$
where $\hat{X}$ is the eigenmode with largest ${\lambda^*}^{-1}$ (i.e. the one with eigenvalue $\lambda$ closest to the shift).

When a good estimation of the eigenvalue is available, this method converges very rapidly and is very efficient, but it can only provide a single eigenvalue.
If we want to compute a larger number of eigenvalues, we can revert to a generalized version of iterative methods, called Arnoldi methods\cite{Arnoldi51}. The shift-invert version of the Arnoldi method is in fact the most commonly used method of the current time and is at the basis of both the popular matlab function {\tt{eigs}} and the eigenvalue solver of FreeFem (i.e. ARPACK++). Our implementation in StabFem allows to chose between single eigenvalue computation (power method) and multiple eigenvalue computation (Arnoldi). The selection is made according to the parameter "nev" transmitted to the driver.

\begin{figure*}[t]
\small
\lstinputlisting{Script_Cylinder_Part1.m}
 \normalsize
\caption{Illustration of the usage of the StabFem software to produce an adapted mesh and study the base flow and the linear stability properties of the wake flow around a cylinder 
(extract from script {\em SCRIPT\_CYLINDER\_ALLFIGURES.m})}
\label{Listing2}
\end{figure*}

\begin{figure}
%\vspace{-.5cm}
%\includegraphics[width=.9 \linewidth]{Cylinder_Mesh.png}
%\vspace{-.5cm}
%\vspace{-.5cm}
\includegraphics[width=.9 \linewidth]{Cylinder_BaseFlowRe60.png}
%\vspace{-1.cm}
\caption{Base flow (axial velocity component) for the flow over a cylinder at $Re=60$.}
\label{fig:Baseflow}
\end{figure}

\begin{figure}
\includegraphics[width=.9 \linewidth]{Cylinder_Lx_baseflow.png}
\includegraphics[width=.9 \linewidth]{Cylinder_Drag_baseflow.png}
\caption{Recirculation length $L_x$ $(a)$  and nondimensional drag $F_x$ ($b$) of the base flow over a cylinder as function of $Re$.}
\label{fig:LxandDrag}
\end{figure}

\subsection{Mesh adaptation procedure}
\vspace{.2cm}

As for any numerical method, a crucial point in the numerical efficiency is the design of the mesh. The finite element method allows to use unstructured mesh and hence to locally adapt the refinement. %Following Sipp \& Lebedev, 
The most common procedure is to decompose the domain into several parts with different grid densities; for instance for the wake of a cylinder, we will design a near-wall region with very small  size, a "wake" region with intermediate mesh size, and an outer region with large mesh size. The inconvenient is that the design relies on an a priori expectation of the regions where gradients will be large.

In our implementation, we used an automatic mesh adaptation method. %which provides an optimal mesh adapted to the structure of the flow. 
The implementation relies on the AdaptMesh procedure of the FreeFem++ software. This procedure is detailed in detail in ref. \cite{adapt}. 
In short, the classical Delaunay-Voronoi algorithm produces a mesh with gridpoint distribution specified by a {\em Metric } matrix $\cal M$. The AdaptMesh algorithm consists of using as a metric the {\em Hessian} (second-order spatial derivatives) of an objective function $u_h$ defined over the domain, i.e. ${\cal M} = \nabla \nabla u_h$. The precision can be controlled by specifying an objective value for the interpolation error of the function on the new mesh.

To build an optimal mesh for the base-flow calculation, the idea is to use as the objective function $u_h$ the solution ${\bf u}_b$ itself, as computed on a previous mesh.%The procedure thus ensures that the mesh will be locally adapted to the gradients of the base flow. 
The base flow is then recomputed on the adapted mesh, providing a better approximation of the solution. The procedure can be repeated a few steps to ensure a right convergence.

The mesh generated in the previous way may not be optimal for the stability calculations as the structure of the eigenmode may be more complex than that of the base flow. To remedy with this, the idea is to subsequently adapt the mesh to both the mesh flow and the results of the stability calculation. This is easily done with FreeFem, as the  AdaptMesh procedure can be used with several objective functions. We have experimented two different ideas. The first is to adapt the mesh to the base flow and the structure of the leading eigenmode. A second and smarter idea is to adapt the mesh to the base flow and the structural sensitivity. This idea is supported by Giannetti \& Luchini\cite{GiannettiLuchini} who showed that the accuracy of the stability results for the flow past a circular cylinder is strictly related to the mesh characteristics in the wavemaker region, i.e. the region where the structural sensitivity reaches its maximum values. 
Results show that the two procedures yield the same values for the eigenvalues with less than $1\%$ error, but that the second method gives a mesh with about 3 times less grid points, leading to much faster computations (see appendix D). So, if one is interested only in the eigenvalues, for instance to plot growth rates as function of Reynolds or to identify the critical Reynolds number, mesh adaptation to the sensitivity gives the best option. On the other hand, if one is interested in the detailed structure of the eigenmode, which may extend far away from the wavemaker region, it is advised to use mesh adaptation on the eigenmode.

In our implementation, the whole process is performed using the Matlab driver {\em Freefem\_AdaptMesh.m} ; the kind of adaptation  (to base flow only, to eigenmode, or to sensitivity) is decided by the choice of parameters transmitted to this function.

\section{Illustration for the wake of a cylinder} 
\vspace{.2cm}

\paragraph{Problem description}
Here, we consider the two-dimensional flow of an incompressible fluid of density $\rho$ past a circular cylinder. 
All flow quantities are normalized using the uniform incoming velocity $U_{\infty}$ and the cylinder diameter $D$, 
which are the characteristic velocity and length scales used for the definition of Reynolds number $Re= U_{\infty} D / \nu$.
The origin of the cartesian frame of reference is considered located on the cylinder axis, the x-axis is chosen to be parallel to the incoming free-stream velocity while the y-axis with the cross-stream velocity.
The dimensions of the computational domain are the following: $-40 \le x/D \le 80$ and $-40 \le y/D \le 40$.
We impose a no-slip condition $(u=0,v=0)$ on the cylinder surface (${\Gamma_{cil}}$), a uniform velocity $(u=1,v=0)$ at the inflow 
$x/D=-40$ and a no-stress condition at the outlet $x/D=80$ and on the lateral boundaries of the computational domain $y/D=\pm 40$.

%Domain dimension $[-40,80]x[0,40]$. No-stress conditions at outlet AND LATERAL BOUNDARY.
The hydrodynamic loads can be obtained by integrating the stress tensor over the cylinder surface.
In particular, the hydrodynamic lift and drag forces read
\footnote{ Remark that $F_x$ and $F_y$ are actually nondimensional forces per unit length. 
For a cylinder of diameter $D$ and length $L$ (assuming $L\gg D$ so that the assumption of 2D flow makes sense), 
the corresponding dimensional forces are $F_x^* = \rho U_\infty^2 D L F_x $ and $F_y^* = \rho U_\infty^2 D L F_y$. 
Alternatively, one may characterize the forces through the drag and lift coefficients $C_x$ and $C_y$. With the usual convention, 
The connection between the nondimensional forces and the force coefficients is $C_x = 2 F_x$ ; $Cy = 2 F_y$.
}
\be{drag}
F_x = {\cal D}_{Re} ({\bf u},p) \equiv 
 2 \int_{\Gamma_{cyl}} \left[-p {\bf n} + \frac{2}{Re} {\bf D}({\bf u}) \cdot {\bf n} \right]   \cdot {\bf e_x} d\ell,
\ee
\be{lift}
F_y = {\cal L}_{Re} ({\bf u},p) \equiv
 2 \int_{\Gamma_{cyl}} \left[-p {\bf n} + \frac{2}{Re} {\bf D}({\bf u}) \cdot {\bf n} \right]   \cdot {\bf e_y} d\ell. 
\ee
where $\Gamma_{cyl}$ is the boundary of the cylinder. The factor 2 stands for the fact that our numerical domain is half the physical domain.

\paragraph{Mesh adaptation procedure}

Let's consider now the matlab code reported in figure \ref{Listing2}. First we build an initial mesh (line 1), and compute base flow solutions for increasing values of the Reynolds number up to $Re = 60$ (lines 3-9).
Then we perform the mesh adaptation with the structural sensitivity, as explained in a previously (line 13). 
The resulting mesh, depicted in figure \ref{meshM2}, is used for the rest of the computations presented in this paper (except for displaying the eigenmode in figure 4$a$). 
Appendix D presents additional test regarding mesh convergence, and demonstrate that results obtained with the resulting mesh are trustable within $0.1\%$ accuracy for the eigenvalue, while requiring a very reasonable number of grid points compared to previous studies of this problem.

%It is shown that as well as doing mesh adaptation with the eigenmode structure instead of the sensitivity, as discussed above, gives comparable results within $1\%$ as for the eigenvalue of the most amplified mode.

%The produced outputs (lines 14-17) gives information about the resulting mesh. 
%Note the values $h_{min}$ and $h_{max}$ of the smaller and larger edges, as well as the local grid size at four points A,B,C,D defined as $(x_A,y_A) = (0.5,0)$ (at the surface of the cylinder at the position of maximum shear), $(x_B,y_B) = (0.5,2.5)$ (at the location of the peak of structural sensitivity, see next section), $(x_C,y_C) = (0.,4)$ (in the near wake), and $(x_D,y_D) = (0.,10)$ (in the the far wake). Finally, the base flow is automatically recomputed on the resulting mesh (line 18-19). Finally, lines 21-22 plot the mesh and base flow structure, producing the result displayed in figure (\ref{fig:Baseflow}).

\paragraph{Base flow}

Having thus produced a convenient mesh, we can now illustrate the properties of the base flow as function of Reynolds number. Figure \ref{Listing2} shows how to compute and plot with StabFem the two most commonly studied quantities, namely the recirculation length $Lx(Re)$, i.e. the location of the stagnation point at the rear of the recirculation region, and the drag coefficient $C_x(Re)$.
Note that the object \verb|bf| is defined as a structure with fields \verb|Drag| and \verb|Lx|. 
The resulting plots are given in figure \ref{fig:LxandDrag}, and are in good agreement with known results for this classical problem.
In particular, for low Reynolds, the recirculation $L_x(Re)$ is equal to $0.5$ (which is the radius of the cylinder) indicating the absence of a recirculation region. The latter appears for $Re > 4.8$, in accordance with known results.

An illustration of the structure of the base flow is given in figure \ref{fig:Baseflow},  for the case $Re = 60$. The contour line on this plot corresponds to the iso-level $u_x = 0$, and allows to visualize the recirculation region associated to this base flow. In accordance with figure \ref{fig:LxandDrag}$(b)$, for $Re = 60$ the recirculation length is $L_x = \approx 4.07$.

%\subsection{Implementation}

%\subsection{Application to the cylinder}

%\clearpage

%We now review the main concepts of linear stability approach and explain how such calculations are implemented in our software.

\begin{figure}
\includegraphics[width=.9 \linewidth]{Cylinder_Sigma_Re.png}
\includegraphics[width=.9 \linewidth]{Cylinder_Strouhal_Re.png}
\caption{Growth rate $\sigma$ $(a)$  and Strouhal number $St = \omega/2\pi$ ($b$) as function of Reynolds number}
\label{fig:SigmaOmega}
\end{figure}

\begin{figure}
%\vspace{-.5cm}
\includegraphics[width=.9 \linewidth]{Cylinder_EigenModeRe60_AdaptD.png}
%\vspace{-.5cm}
%\vspace{-.5cm}
\includegraphics[width=.9 \linewidth]{Cylinder_EigenModeAdjRe60.png}
%\vspace{-.5cm}\vspace{-.5cm}
\includegraphics[width=.9 \linewidth]{Cylinder_SensitivityRe60.png}
%\vspace{-.5cm}
\caption{Contour plot of the streamwise velocity component: $(a)$ (Direct) Eigenmode; $(b)$ Adjoint mode and ($c$) Structural sensitivity field for the cylinder's wake at $Re=Re_c = 46.7$.}
\label{fig:Eigenmode}
\end{figure}

%\begin{figure*}
%\small
%\begin{lstlisting}
%\end{lstlisting}
%\normalsize
%\caption{Illustration of the procedure to compute stability properties and adapt the mesh using StabFem (from script {\em SCRIPT\_CYLINDER.m}. }
%\label{listing4}
%\end{figure*}

\paragraph{Linear stability results}

We investigate the stability of the base flow fields by performing a parametric study of the eigenproblem 
(\ref{Eigen_matricial}). In this way, we determine the critical Reynolds number $Re_c$ at with the steady base flow
first becomes unstable: to this end it is useful to remember that a flow state is 
linearly unstable when the real part of 
the leading eigenvalue, i.e. the growth rate, is positive. 
Figure \ref{fig:SigmaOmega} shows growth rate and the Strouhal number 
$St=a\omega/2 \pi U_{\infty}$ as a function of the 
Reynolds number. It is easy to check that the critical Reynolds number is about 47 
for the first mode. 
The associated direct eigenmode is depicted in figure \ref{fig:Eigenmode}. The 
spatial structure of this mode 
extends downstream of the bluff body and is characterized by streamwise 
extended spatial disturbances. 
On the other hand, the adjoint mode is highly localized near the cylinder 
on the upper (and lower) side of the body surface. 
We recall that the adjoint field provides useful information about the mechanism to
flow receptivity to momentum forcing and mass injection.
We note also that this receptivity decays rapidly both upstream and downstream 
of the bluff body.

The structural sensitivity field displayed in figure \ref{fig:Eigenmode}c)
is obtained by evaluating eq. \ref{Structursens}.
In particular, we plot the spectral norm of the sensitivity tensor, it 
gives the maximum possible coupling among the velocity components. 
This spatial map can be used to identify the flow region where the 
instability mechanism acts.

\section{Nonlinear global stability approaches}
\vspace{.2cm}
%\section{Computing the limit cycle for $Re>Re_c$ with Harmonic Balance}

%For $Re\right>Re_c$, the linear stability analysis based on the {\em base flow} does not allow to predict the properties of the limit cycle; in particular the Strouhal number is substantially underestimated. %It has been shown that investigating the stability properties of the {\em mean flow} obtained by averaging time-marching solution gives a better accordance. Attempts to on a rigourous basis

In the past decade, efforts have been devoted to extend the range of validity of global approaches into the nonlinear regime for $Re>Re_c$, with the double objective to describe the properties of the limit cycle reached after saturation and to derive amplitude equations describing the transitent dynamics towards this cycle. The two main milestones in this direction {\color{red} are} the {\em weakly nonlinear model}  (WNL) of Sipp \& Lebedev \cite{SippLebedev} and the {\em self-consistent model} (SC) of Manti\v{c}-Lugo et al \cite{MLugo2014}.
 {\color{blue} In this review, we will address only the first of the two questions, namely {\color{red} the} description of the saturated cycle, and leave aside the question of transient dynamics. We will successively review the two aforementioned models, in a simplified formulation devoted to describe only the saturated cycle. We also provide a simple implementation of these two models. Finally, in line with the previous section, we will again illustrate with results obtained for the wake of a cylinder.
 }

\subsection{General definitions in the nonlinear regime}

In the nonlinear regime, the {\em base flow} introduced in the linear theory is not directly accessible and no longer relevant, especially when the oscillation amplitudes become large. 
Instead, one may define a {\em mean flow} by time-averaging : 
%{\color{red} we taken the Reynolds decomposition ${\bf u}={\bf u}_m({\bf x})+{\bf u}'({\bf x},t)$, with ${\bf u}'$ the nonlinear perturbation and ${\bf u}_m$ the {\em mean flow} defined as the time-average  of the flow:}

\be{defumean}
{\bf u}_m({\bf x})  = \frac{1}{T} \int_0^{T}  {\bf u}({\bf x},t)  dt,
\ee
where $T = 2\pi/\omega$  is the period of the oscillation cycle. The difference between the instantaneous solution and the mean flow is then called the {\em nonlinear perturbation}, defined as

\be{defuprime}
{\bf u}'({\bf x},t) =   {\bf u}({\bf x},t)-  {\bf u}_m({\bf x}).
\ee

A convenient measure of the unsteady part of the flow, which has been adopted in both the WNL and SC models, is the energy-amplitude, defined as the square-root of the total energy associated to the nonlinear perturbation:
\be{defAnergy}
A_E = \sqrt{\frac{1}{T} \int_0^{T} \left( \int_\Omega | {\bf u}' |^2 \, dS \right) dt}.
\ee

In the next sections we will document the predictions of the WNL and SC models regarding the quantities $A_E$ and $L_x$ adopted in past studies. In addition, we will document two other quantities of practical interest : the Drag and Lift forces $F_x$ and $F_y$ exerted on the cylinder. 
Both are periodic functions of time and; owing to symmetry consideration, the drag contains only even harmonics and the lift only odd harmonics:

%\be{drag_lift_def}
%\begin{cases}
%F_x=F_{x,0} + \sum_{n=1}^\infty \big( F_{x,2n,c} \cos ( 2 n \omega t) + F_{x,2n,s} \sin( 2 n  \omega t ) \big) \\
%\begin{split}
%F_y  =  \sum_{n=1}^\infty \big(  F_{y,{2n-1},c} \cos ((2n-1) \omega t ) +\\
% F_{y,(2n-1),s} \sin ((2n-1) \omega t) \big)
%\end{split}
%\end{cases}.
%\ee
\begin{align}
F_x &=F_{x,0} + \sum_{n=1}^\infty \big( F_{x,2n,c} \cos ( 2 n \omega t) + F_{x,2n,s} \sin( 2 n  \omega t ) \big),
\\
\begin{split}
F_y  & =\sum_{n=1}^\infty \big( F_{y,{2n-1},c} \cos ((2n-1) \omega t )\\
             &\qquad + F_{y,(2n-1),s}  \sin ((2n-1) \omega t) \big).
\end{split}
\label{drag_lift_def}
\end{align}

In the sequel we will focus on the {\em mean drag}  $F_{x,0}$ and on the fundamental components of the lift  
$F_{y,1,c}$ and $F_{y,1,s}$. These quantities are easily extractible from a numerical simulation or an experiment, and we will
show how they can be predicted from the nonlinear global approaches.

 In this part, to simplify the notations, we symbolically write the Navier-Stokes equations, as {\color{red}$\partial_t {\bf u} = {\cal NS} ({\bf u})$}, therefore dropping the systematic reference to the incompressibility constraint and associated pressure field. {\color{red} The same is done with the linearized operator ${\cal LNS}_{{\bf U}}( {\bf u})$.}

%MThe mean drag is given by

%$$F_{x,m} = D(u_m)$$
%with "Drag" operator defined in equation ().

%The oscillating lift $F_y(t)$  is a	 periodic function of period $T$, and we will 
%$$F_y = F_y,c

%The first milestone in this direction is the work of Sipp \& Lebedev \cite{SippLebedev} who used a weakly nonlinear development in terms of the distance to the threshold $Re-Re_c$. However, although derived on rigorous grounds, the weakly nonlinear development has a very limited range of validity and already fails for $(Re-Re_c) \approx 1$.
%More recently,  Manti\v{c}-Lugo et al \cite{MLugo2014} proposed an alternative approach termed {\em Self-consistent model} which succeeds in predicting the dynamics up to $Re =120$ and more. 
%This model was build as a linear stability approach build on a {\em mean flow} which includes a retroaction of the eigenmode. However, if one is interested in the limit cycle and not the transient,
%the approach is actually equivalent to a Fourier series decomposition of the flow with respect to time (an approach also known as {\em harmonic balance}) retaining only the two first terms. 
%The approach is based on a generalisation of the eigenmode ansatz \ref{} and

%In the next sections, we thus successively present the weakly nonlinear model, the self-consistent model, and propose a direct resolution method for this latter model.

%The relation with the initial method of Mantic-Lugo et al. will be discussed afterwards.

\subsection{The weakly nonlinear model}

\paragraph{WNL model : analysis}

\begin{figure*}
\small
\lstinputlisting{Script_Cylinder_Part2.m}
 \normalsize
\caption{Illustration of the procedure for nonlinear calculations using StabFem (extract from script {{\em SCRIPT\_CYLINDER\_ALLFIGURES.m})}. }
\label{fig:listingNL}
\end{figure*}

We first review the weakly nonlinear model of Sipp \& 
Lebedev\cite{SippLebedev}, also discussed by Gallaire et al. \cite{FDR2016}.  
The initial derivation of \cite{SippLebedev} makes use of a multiple scale method in order to obtained an amplitude equation.
This complete analysis is reproduced in appendix B. In the present paragraph, we give a simplified derivation of this model restricted to the description of the periodic saturated cycle.
The starting point can be taken as the following expansion of the velocity flow field:
 {\color{red}
\be{WNL1}
\begin{aligned}
&{\bf u} = {}  {\bf u}_{bc} + \epsilon \left[ A_{wnl}  \hat{\bf u} e^{i (\omega_c+\epsilon^{\color{red}2} \omega_\epsilon)  t} + c.c. \right]\\
&+ \epsilon^2 \left[ {\bf u}_\epsilon + |A_{wnl}|^2  {\bf u}_{2,0} + \left(  A_{wnl}^2 {\bf u}_{2,2} e^{2 i(\omega_c+\epsilon^{\color{red}2} \omega_\epsilon)  t} + c.c. \right) \right]\\
& + {\cal O}( \epsilon ^3),
\end{aligned}
\ee
}

This expansion is built as an asymptotic expansion in terms of the small parameter $\epsilon = \sqrt{1/Re_c - 1/Re}$ corresponding to the distance to the critical Reynolds. 
The zero-order term {\color{red}${\bf u}_{bc}$} is the base flow at the threshold $Re_c$.

In the first-order term, $\hat{\bf u}$ is the neutral eigenmode at $Re_c$ conveniently normalized (see discussion in appendix B), 
$A_{wnl}$ an amplitude, $\omega_c$ the frequency predicted by the linear approach at $Re=Re_c$ and $\omega_\epsilon$ a small deviation of the frequency.

The second-order term contains three contributions: ${\bf u}_{\epsilon}$ is the modification to the base flow related to the 
increase of $Re$, ${\bf u}_{2,0}$  represents the nonlinear interaction of $\hat{\bf u}$ with its conjugate, ${\bf u}_{2,2}$ the nonlinear 
interaction of $\hat{\bf u}$ with itself. These three terms are computed as solutions of nonsingular linear systems 
(see eqs. \ref{eq:LL1},\ref{eq:LL2},\ref{eq:LL3} in appendix B).

At ${\cal O}( \epsilon ^3)$, compatibility conditions have to be imposed to ensure that the problem is correcty posed. These conditions lead to an "amplitude equation" which relates the amplitude $ A_{wnl}$ to three parameters $\Lambda, \nu_{0}$ and $\nu_{2}$ which depend
uniquely on ${\bf u}_\epsilon$, ${\bf u}_{2,0}$ and ${\bf u}_{2,2}$, respectively (see equations \ref{LAMBDA}, \ref{NU0} and \ref{NU2} in appendix B). Restricting to the description of the limit cycle, the "amplitude equation" takes the form :

\be{WNL3}
i \omega_\epsilon A_{wnl} = \Lambda A_{wnl} - (\nu_0+\nu_2)  |A_{wnl}|^2 A_{wnl}.
\ee

%where the coefficients $\Lambda$, $\nu_0$ and $\nu_2$ are given by We note that $\Lambda$ does not depend on the normalization choice of the eigenmode, discussed later, while $\nu_0$ and $\nu_2$ depend. 
The amplitude $A_{wnl}$ and the correction to the frequency are then determined by considering the real and imaginary parts of this equation, leading to
%\be{AWNL}
$
|A_{wnl}|= \sqrt{ \frac{\Lambda_r}{\nu_{0,r}+\nu_{2,r}}}
$ and
%\ee
%\be{omegaeps}
$
\omega_\epsilon = \Lambda_i- \Lambda_r \frac{\nu_{0,i}+\nu_{2,i}}{\nu_{0,r}+\nu_{2,r}} 
$
%\ee
where the subscripts $r$ and $i$ represent the real and imaginary parts.
Reintroducing the scaling, the  amplitude $|A| =  \epsilon |A_{wnl}| $ and the frequency $\omega$ of the limit cycle are thus predicted as
\be{ANL} 
|A| =  \epsilon |A_{wnl}| =\sqrt{ \frac{\Lambda_r}{\nu_{0,r}+\nu_{2,r} }} \sqrt{\frac{1}{Re_c}-\frac{1}{Re}},
\ee
\be{omegaWNL} 
\omega \equiv \omega^{(wnl)} =\omega_c+ \left( \Lambda_i- \Lambda_r \frac{\nu_{0,i}+\nu_{2,i}}{\nu_{0,r}+\nu_{2,r}} \right) \left(\frac{1}{Re_c}-\frac{1}{Re}\right)
\ee

Finally, as specified above, we explain how the mean drag $F_{x,0}$ and fundamental components $(F_{y,1,c},F_{y,1,s})$ of the oscillating lift can be predicted from the WNL approach.
The mean drag  can be obtained by $F_{x,0} = {\cal D}_{Re}({\bf u}_m,p_m)$, where ${\cal D}$ is the drag operator defined in \ref{drag} and 
$[{\bf u}_m,p_m]$ is the {\em mean flow}  
which corresponds to the time-average of expansion  \ref{WNL1}, namely :
$
[{\bf u}_m,p_m] = [{\bf u}_{bc},p_{bc}] +\epsilon^2 \left( [{\bf u}_\epsilon,p_\epsilon] + A_{wnl}^2 [{\bf u}_{2,0}, p_{2,0} ] \right).
$
Developing the terms as an asymptotic expansion leads to :

\be{drag_cos}
 F_{x,0}(Re) \approx F_{x,0,{Re_c}} +  F_{x,0,\epsilon} \left(\frac{1}{Re_c}-\frac{1}{Re}\right)
\ee 
\begin{equation*}
\begin{aligned}
& \mbox{with} \quad F_{x0,{Re_c}}  = {\cal D}_{Re_c} ({\bf u}_{bc},p_{bc}), \quad \mbox{and}  
\\ 
& F_{x0,\epsilon} = {\cal D}_{Re_c} ({\bf u}_\epsilon, p_\epsilon ) - {\cal D}_{1} ({\bf u}_{bc},0) 
+ | A_{wnl} |^2 {\cal D}_{Re_c} ({\bf u}_{2,0},p_{2,0}) 
\end{aligned}
\end{equation*}

%_{\epsilon},p_\epsilon)
%D({\bf u}_{\epsilon})- 2\int_{\Gamma_{cyl}}} \mathbf{D} ({\bf u}_{bc}) \cdot {\bf n}  \cdot {\bf e}_x d \ell \right) 
%\\
%&+|A|^2 D({\bf u}_{2,0})\\
%&+2|A|^2\big(F_{x,r}({\bf u}_{2,2})\cos(2\omega t)
%-F_{x,i}({\bf u}_{2,2})\sin(2\omega t) \big),

Similarly the required components of the lift force are obtained by applying the lift operator ${\cal L}$ defined in \ref{lift} 
to the order-one component of the expansion, leading to :
\be{lift_cos}
F_{y,1,c} - i F_{y,1,s} = 2 |A_{wnl}| {\cal{L}}_{Re_c}( {\bf \hat{u}},\hat{p} ) \sqrt{\frac{1}{Re_c}-\frac{1}{Re}}.
%|A|_i F_{x,i}({\bf \hat{u}})\sin(\omega t) \big),\\
%\end{aligned}
\ee

%\be{lift_cos}
%\begin{aligned}
%F_{y,WNL} =2\big(|A|_r F_{x,r}({\bf \hat{u}})\cos(\omega t)-
%|A|_i F_{x,i}({\bf \hat{u}})\sin(\omega t) \big),\\
%\end{aligned}
%\ee

%where $F_{x}$ and $F_{y}$ are given by and \ref{lift} (with the associated pressure field implicit), respectively . All terms in these equations can be matched with the interesting ones in \ref{drag_lift_def}: $F_{x,0}$ is the first 4 terms of \ref{drag_cos}; $F_{x,2,c}$, $F_{x,2,s}$ are the fifth and sixth terms of \ref{drag_cos}; $F_{y,1,c}$, $F_{y,1,s}$ are the first and second terms of \ref{lift_cos}. We note that the \textit{sin} term is associated to the phase of the forces in a physical way. }

%\iffalse
%\begin{eqnarray}
%\begin{aligned}
%F_{x,WNL} = F_{x}({\bf q}_{bc})&+\epsilon^2 \big( 
%F_{x}({\bf q}_{\epsilon})- 2\mathsf{D}({\bf u}_{bc}) \big)\\
%&+F_{x}({\bf q}_{2,0})|A|^2\\
%&+2F_{x,r}({\bf q}_{2,2}\cos(2\omega t)+
%2F_{x,i}({\bf q}_{2,2}\sin(2\omega t)
%),\\
%\end{aligned}\\
%F_{y,WNL} = |A|^2 \big[ F_{y}({\bf \hat{q}})e^{i\omega_{LC} t} +c.c. \big],
%\end{eqnarray}
%\fi

\paragraph{WNL model : implementation and results for the cylinder}

Lines 1-8 of the script shown in igure \ref{fig:listingNL}, which is extracted from the script {\color{red}
\verb|SCRIPT_CYLINDER_ALLFIGURES.m|}, illustrate the sequence of commands to 
perform the weakly nonlinear study for the cylinder wake.
On line 2, we first determine the instability threshold, and the corresponding base flow and eigenmode
\footnote{This routine uses Newton iteration to directly compute the base flow, the eigenmode, the frequency and the critical Reynolds. The algorithm is very similar to the one presented for the HB, with an additional unknown (Re) and an additional constraint (normalization of the mode). The interested reader should reconstruct easily the whole procedure from the code provided.}. 
On line 3 we solve the adjoint problem required for some terms in the WNL formulation.
On line 4, we then compute all the terms and coefficients of the WNL model.
Lines 6-8 then processes the results in a way they can be plotted.
%{\color{red}The other lines are explained latter.}
%After that, 
%we construct  vectors to store the frequency and the amplitude of the limit cycle in the 
%range $Re = [47.5-100]$. Note that for the computation at $Re=47.5$, we need a guess 
%for the amplitude, which is deduced from the weakly nonlinear approach on line 9. In 
%the sequel of the loop no guess value is prescribed, hence the solver uses 
%continuation.

%{\color{red} 
%The forces coefficients given by $F_x({\bf u})$ and $F_y({\bf u})$ are then converted in a more traditional form, $C_x=2F_x({\bf u})$ and $C_y=2F_y({\bf u})$.
%}

Figure \ref{fig:HB_SC_DATA_COMP} represent the predictions of the WNL approach regarding the frequency (expressed as a Strouhal number through $St = \omega/2\pi$), mean drag, amplitude of the oscillating lift, and energy-amplitude.
As discussed in \cite{SippLebedev} and \cite{FDR2016},  when compared to DNS results the approach gives good prediction in the immediate vicinity of $Re_c$, but deviation appears very rapidly and disagreement is already large at $Re=48$ (although, as discussed by \cite{FDR2016} and also observed  \cite{Tchoufag2015}, a convenient definition of the $\epsilon$ improves the results). 
{\color{red} These aspects are justified by the perturbative nature of the WNL approach. The description of the limit cycle can be extended to larger $Re$ with the approach presented next.  }

\begin{figure}
\begin{center}
\includegraphics[width=.9 \linewidth]{Cylinder_Strouhal_Re_HB.png}
\includegraphics[width=.9 \linewidth]{Cylinder_Cx_Re_HB.png}
\includegraphics[width=.9 \linewidth]{Cylinder_Cy_Re_SC.png}
\includegraphics[width=.9 \linewidth]{Cylinder_Energy_Re_SC.png}
\includegraphics[width=.9 \linewidth]{Cylinder_Lx_Re_HB.png}
\end{center}
\caption{Comparison between the weakly nonlinear results (WNL) the harmonic balance data (HB), and baseflow/linear results : Strouhal number $(a)$, Mean drag $(b)$, amplitude of oscillating lift $(c)$, Energy-amplitude of the nonlinear perturbation $(d)$ and recirculation lenght of mean/base flows ($e)$. 
%c_x should be consistent with the drag definition given at beginning
}
\label{fig:HB_SC_DATA_COMP}
\end{figure}

\subsection{The Self-Consistent model  }
\paragraph{SC model : analysis }

%\begin{figure}
%\begin{center}
%\includegraphics[width=.9 \linewidth]{Cylinder_SC100_EnergySigma.png}
%\includegraphics[width=.9 \linewidth]{Cylinder_SC100_CySigma.png}
%\end{center}
%\caption{Self-consistent approach for the wake of a cyrcular cilinder: results at $Re =  100$.}
%\label{fig:SC100}
%\end{figure}

We now briefly review the self-consistent {\color{red} model} as introduced by Manti\v{c}-Lugo et 
al \cite{MLugo2014}. In its original exposition, the authors adopted a pseudo-eigenmode expansion of the flow 
as follows: 
\be{SC}
{\bf u } = {\bf u }_m + A_{sc} \left[ \tilde{{\bf u }}_1 e^{\sigma_{sc} t + i \omega_{sc} t} +   {\color{red} \overline{\tilde{\bf u }_1}} e^{\sigma_{sc} t  -i \omega_{sc} t} \right],
\ee  
where ${\bf u }_m$ is the {\em mean flow} defined by phase-averaging over the cycle, $\tilde{{\bf u }}_1$ is a pseudo-eigenvector which is normalized by the condition  $||\tilde{{\bf u }}_1|| = 1/\sqrt{2}$, {\color{red}$\overline{\tilde{{\bf u }}_1}$ is its complex conjugate,}
$A_{sc}$ is an amplitude parameter directly related to the energy of the oscillating flow, and $\lambda_{sc} = \sigma_{sc} + i \omega_{sc}$ is a pseudo-eigenvalue which depends upon the parameter $A_{sc}$.

The original version of the model (discussed with some more details in appendix C) allowed to obtain an amplitude equation relating the instantaneous growth rate $\sigma$ as function of the amplitude $A_{sc}$. However, if we are simply interested in the properties of the limit cycle, not the transient, we may recast the self-consistent model in a simpler way.

%Figure \ref{fig:SC100} shows the results of the self-consistent model at Re=100.

%\paragraph{{\color{red}First Order Harmonic balance: equations and procedure} }

%\begin{figure}
%\begin{center}
%\includegraphics[width=.9 \linewidth]{Cylinder_Lx_Re_HB.png}
%\end{center}
%\caption{Flow past a circular cylinder: length of the wake bubble (measured from the 
%rear stagnation point) for different Reynolds number. Comparison between the base flow bubble and the mean flow bubble computed by using the harmonic balance.}
%\label{fig:recirculation_lengh}
%\end{figure}

%As discussed above, the Self-Consistent model was initially presented by the authors as a rational way to explain the dynamics in terms of a stability analysis of the {\em mean flow}. Furthermore, the resolution method presented by the authors, which involves a double iteration loop, is not easy to implement and not particularly efficient.

%If one is only interested by the properties of the limit cycle and not the transient, the model is actually equivalent to a Fourier series, and amenable to a more direct resolution method. 
We thus start with a truncated Fourier decomposition of the limit cycle under the form:
\be{HB}
{\bf u } = {\bf u }_m + {\bf u }_{1,c} \cos( \omega t ) +   {\bf u }_{1,s} \sin( \omega t ),
\ee
where ${\bf u }_{1,c}$ and ${\bf u }_{1,s}$ are two {\em real} fields describing the cycle at two instants separated by a quater-period of oscillation, and $\omega$ is the (real) oscillation frequency of the limit cycle (which is not known a priori).  
The connection with the definition of Manti\v{c}-Lugo is as follows :
\be{HBtoSC}
\left( {\bf u }_{1,c} - i {\bf u }_{1,s} \right) = 2 A_{sc} \tilde{{\bf u }}_1.
\ee

Injecting this ansartz into the Navier-Stokes equations and taking the mean value and the first Fourier component leads to the following coupled equations:
\begin{subequations}\label{eq_principal}
\begin{eqnarray}
{\cal NS}(  {\color{red}{\bf u }_m }) = \frac{{\cal C}( {\bf u }_{1,c}, {\bf u }_{1,c}) +{\cal C}( {\bf u }_{1,s}, {\bf u }_{1,s})}{{\color{red}4}}, 
\label{HBEq0}
\\
 \omega {\bf u }_{1,s} =  {\cal LNS}_{{\bf u }_m}(  {\bf u }_{1,c} ),
\label{HBEq1}
\\
 -\omega {\bf u }_{1,c} =  {\cal LNS}_{{\bf u }_m}(  {\bf u }_{1,s} ).
\label{HBEq1b}
\end{eqnarray}
\end{subequations}

%Note {\color{red} that,} contrary to the SC model, the amplitude $A_{HB}$ of the oscillation} can easily be computed a posteriori as ${\color{red}A_{HB}} = \sqrt{2 ||{\bf u }_1||}$. 
%On the other hand, the Fourier description of the limit cycle is invariant with respect to the phase $\phi$ (i.e. the equations are unchanged when replacing ${\color{red} {\bf u }_1 }$ by  ${\color{red} {\bf u }_1 e^{i\phi}}$).

To allow resolution we need an extra equation to fix the {\em phase} of the cycle. Several choices are possible, but a convenient one is to decide that the instant $t=0$ corresponds to a maximum of the lift force.
This condition reads:
\be{HBphase}
{\cal L}_{Re}({\bf u}_{1s}) =0.
\ee

Note that the amplitude $A_{sc}$, which was considered as a key parameter in the original model of \cite{MLugo2014}, 
does not appear in the simplified version discussed here. This parameter can easily be computed a posteriori as 
$A_{sc} = \sqrt{2 \int_\Omega ( |{\bf u }_{1,c}|^2+ |{\bf u }_{1,s}|^2) d S} $.

\paragraph{SC model: implementation and results for a cylinder}

Mathematically, the system (\ref{HBEq0},\ref{HBEq1},\ref{HBEq1b},\ref{HBphase}) for the unknown {\color{red}$[{\bf u }_m, {\bf u }_{1,c}, {\bf u }_{1,s}, \omega]$} is well posed. Instead of the double-loop resolution procedure of \cite{MLugo2014}, we propose a direct resolution using a Newton iteration just as explained for the base flow in section 2. 
%To allow resolution, we separate the mode into real and imaginary part, by writing ${\bf u }_1 = {\bf u }_{1,r} +  i {\bf u }_{1,i} $.
We then assume that we know a {\color{red}``guess'':
$$
[{\bf u }_m, {\bf u }_{1,c}, {\bf u }_{1,s}, \omega] = 
 [{\bf u }_m^g, {\bf u }_{1,c}^g, {\bf u }_{1,s}^g, \omega^g]
+ [\delta {\bf u }_m, \delta {\bf u }_{1,c}, \delta {\bf u }_{1,s}, \delta \omega].
$$
} Injecting and developing up to linear order leads to the following equations:{\color{red}
\begin{subequations}\label{eq:harmonic_total}
\begin{eqnarray}
\begin{split}
&{\cal NS}(  {\bf u }_m^g ) - \frac{1}{4} \big[ {\cal C}( {\bf u }_{1,c}^g,{\bf u }_{1,c}^g) +  {\cal C}( {\bf u }_{1,s}^g,{\bf u }_{1,s}^g) \big]+ {\cal LNS}_{{\bf u }_m^g}(\delta {\bf u }_m)
\\
&-\frac{1}{2} \big[ {\cal C}( {\bf u }_{1,c}^g,\delta {\bf u }_{1,c}) +  {\cal C}( {\bf u }_{1,s}^g,\delta {\bf u }_{1,s}) \big] = 0,
\end{split}
\label{HB_1}
\\
\begin{split}
{\cal LNS}_{{\bf u }_m^g}( {\bf u }_{1,c}^g) - \omega^g {\bf u }_{1,s}^g& -  {\cal C}( \delta {\bf u }_{m}, {\bf u }_{1,c}^g)
\\
&+{\cal LNS}_{{\bf u }_m^g}( \delta {\bf u }_{1,c})  - \omega^g \delta {\bf u }_{1,s}  
 - \delta \omega {\bf u }_{1,s}^g = 0 ,
 \end{split}
\label{HB_2}
\\
\begin{split}
{\cal LNS}_{{\bf u }_m^g}({\bf u }_{1,s}^g) + \omega^g {\bf u }_{1,c}^g& -  {\cal C}( \delta {\bf u }_{m}, {\bf u }_{1,s}^g)
\\
&+{\cal LNS}_{{\bf u }_m^g}( \delta {\bf u }_{1,s}) + \omega^g \delta {\bf u }_{1,c} +  \delta \omega {\bf u }_{1,c}^g= 0 ,
\end{split}
\label{HB_3}
\\
\begin{split}
 F_y({\bf u }_{1,s}^g) + F_y(\delta {\bf u }_{1,s}) = 0. \qquad \qquad \qquad \qquad \qquad \qquad \quad
\end{split}
\end{eqnarray}
\end{subequations}
}
After discretization, this leads to a linear problem of the form $A X = Y$ where $X$ is the discretized version of the unknowns  $[\delta {\bf u }_m, \delta {\bf u }_{1,c}, \delta {\bf u }_{1,s}, \delta \omega]$, and $A$ is a matrix of dimension $3 N_{dof} +1$, where $N_{dof}$ is the dimension of the Taylor-Hood basis of finite elements describing each of the three $[{\bf u},p]$ fields.    This system is solved iteratively in the same way as explained in section 2.1 for determination of the base flow. Using the adapted mesh described in figure 2, the dimension of the system 
is $3 N_{dof} +1 \approx 58 000$ and the resolution remains possible at very reasonable computational costs.

Lines 10-17 of the script shown in figure \label{fig:listingNL}  explain how to solve SC model using the StabFem software, 
for the wake of a cylinder in the range $Re \in [47-100] $. Note that a "guess" for the mean flow and the self-consistent mode for $Re = 47$, i.e. just above the threshold, has already been generated from the weakly nonlinear model at line 4 of the same script. This guess is used for the first step of the loop over Reynolds in lines 14-17. For next steps of the loop, continuation is done using the previous calculation as a guess.

\begin{figure}
\begin{center}
\includegraphics[width=.9 \linewidth]{Cylinder_MeanFlowRe60.png}
\end{center}
\caption{Self-consistent approach for the wake of a circular cylinder:  description of the MEAN FLOW for  $Re = 
100$.}
\label{fig:MF60}
\end{figure}

Fgure \ref{fig:MF60} illustrates the structure of the mean flow for $Re=60$. As already identified by  \cite{MLugo2014}, the recirculation region associated with this mean flow is notably shorter than the one associated with the base flow (figure 2).

%Line 19 shows how to plot the results along with the

%\ref{HBEq0,HBEq1,HBphase}

Figure \ref{fig:HB_SC_DATA_COMP} shows the comparison between the WNL (green) and SC (red) models for the quantities of interest identified in this paper, namely the Strouhal number, the mean drag, the maximum lift, the energy-ampligude, and the recirculation length associated to the mean flow. When relevant, results concerning the base flow and the linear approach are also displayed (blue)
\footnote{Figure   \ref{fig:HB_SC_DATA_COMP} is obtained by line 19 of the script displayed in figure \ref{fig:listingNL}. The other figures are processed in a similar way. The entire set of commands to obtain all figures is provided in the script {\em SCRIPT\_CYLINDER\_ALLFIGURES.m} .}.
Concerning the quantities $St$, $A_E$ and $L_x$, differences between SC, WNL models have already been commented in  \cite{MLugo2014} and \cite{FDR2016}. The predictions of the SC models were also compared to numerical simulations results showing excellent agreement in the range $Re \in [Re_c,100]$. Regarding the forces exerted on the body, we can remark that the predictions of the WNL and SC models rapidly depart from each other as soon as $Re-Re_c \gtrsim 1$. Comparison of these results with DNS simulations is not provided here (consistently with the objectives of the present paper) but the reader may verify that the SC model correctly predicts these quantities in the range of Reynolds number considered here.

%\clearpage

\section{Conclusion}
%The aim of the present review is to introduce advanced stability approaches 
%from a {\tt practical} point of view. The reader can reproduce all the figures presented 
%in this paper by just running the Matlab code available in the StabFem repository.

The objective of this paper was twofold. First, we aimed at giving an up-to-date and comprehensive review on global stability approaches, both linear and nonlinear, including the most recent developments of the field. 
Secondly, we intended to provide an easy to use software performing all these computations from a single program. In accordance with this objective, all the figures presented in the paper can be produced by launching a single Matlab program available on the website of the project.

Although the focus here was on the reference case of 2D, incompressible flow around a cylinder, the  {\em StabFem } software is designed to be easily customisable to a variety of other situations. The project is currently in constant development, and incorporates a growing number of other configurations. In the present status, the project incorporates test-cases for the following classes of problems:
\begin{itemize}
\item Incompressible flows around 2D objects, either fixed or in movement such as the case of a spring-mounted cylinder \cite{Navrose},
\item Incompressible flows in axisymmetric geometries such as the wake of spheres and disks \cite{Tchoufag16} and the flow through apertures \cite{FabreASME}, 
\item Compressible flow around 2D objects  \cite{Fani18}, 
\item Oscillations of hanging drops and liquid bridges \cite{Chireux}
\end{itemize}
The project is intended as collaborative, so anyone who wants to contribute is welcome !

%\section*{Acknowledgements}

%J. Tchoufag, J. Mougel, O. Marquet, D. Sipp,

\appendix

\section{Details of the weak formulation}

In the presentation of the numerical methods in sections 2.1 and 2.2, and introduction of the {\em weak form}, we have omitted an important point,; namely the issue of boundary conditions. In this appendix we explain more rigorously how the weak formulation is obtained. We consider here the full time-dependent nonlinear Navier-Stokes equations, but the treatment of the base-flow equations and the linearised equations is essentially the same.

Noting $\Gamma$ the boundary of the numerical domain, the latter can be decomposed in five parts : 
$\Gamma = \Gamma_{in} \cup \Gamma_{cyl} \cup \Gamma_{axis} \cup \Gamma_{out} \cup \Gamma_{lat}$. 
Noting $\sigma = 2 Re^{-1} {\bf D}({\bf u}) - p {\bf 1}$ the stress tensor, the relevant boundary conditions are as follows:
\begin{itemize}
\item On $\Gamma_{in}$ (inlet): ${\bf u} = {\bf e}_x$ (Dirichlet).
\item On $\Gamma_{cyl}$ (surface of the cylinder): ${\bf u} = {\bf 0}$ (Dirichlet).
\item On $\Gamma_{out}$ (outlet): $\sigma \cdot {\bf n} = {\bf 0}$ (Neumann). 
\item On $\Gamma_{axis}$ (symmetry plane): $u_y = 0$ and $\sigma_{xy} = 0$ (Mixed). 
\item On $\Gamma_{lat}$ (lateral boundary): $u_y = 0$ and $\sigma_{xy} = 0$ (Mixed). 
\end{itemize}
We will introduce the following notation for integrals along any portion of the boundary $\Gamma_i$ of the product of two quantities $\phi_1, \phi_2$ (either scalar or vectorial) :
%$\left< \phi_1, \phi_2 \right>_{\Gamma_i} $:
$$
\left< \phi_1, \phi_2 \right>_{\Gamma_i} = \int_{\Gamma_i}  \overline{\phi}_1 \cdot \phi_2   \mbox{ d} \ell,
$$
Instead of the simplified version \ref{NSweak}, the more precise form of the weak formulation can be first written as follows:
\begin{eqnarray}
\label{NSweakFull}
\forall [{\bf v},q], &&\quad \partial_t \left< {\bf v}, {\bf u}\right> = \left< {\bf v} , {\color{red}{\cal NS} ({\bf u},p)} \right> + \left< q, \nabla \cdot {\bf u}\right>\\
+ &&\frac{1}{\epsilon} \left(  \left< {\bf v}, \bf{u} \right>_{\Gamma_{cyl}} + \left< {\bf v}, ({\bf u}- {\bf e}_x ) \right>_{\Gamma_{in}} 
+ \left< v_y, u_y\right>_{\Gamma_{axis}\cup \Gamma_{lat}} \right) \nonumber \\
+ && \left< {\bf v}, \sigma \cdot {\bf n} \right>_{\Gamma_{out} \cup  \Gamma_{lat} \cup \Gamma_{axis} }  \nonumber 
\end{eqnarray}
where $\epsilon=10^{-30}$ is a small parameter used to impose the Dirichlet boundary conditions by penalization.
An integration by parts of the pressure gradient and viscous stress terms of the Navier-Stokes equation eventually 
leads to the weak form effectively used in the programs {\em Newton2D.edp} and {\em Stab2D.edp}:
\begin{eqnarray}
\forall [{\bf v},q], &&\, \partial_t \left< {\bf v}, {\bf u}\right> = - \left< {\bf v} , {\cal C}({\bf u},{\bf u})/2 \right>
- 2 Re^{-1} \left< {\bf D}({\bf v}) : {\bf D}({\bf u})  \right>  \nonumber \\
+ &&\left< \nabla \cdot {\bf v}, p \right> + \left< q, \nabla \cdot {\bf u} \right> \label{NSweakFullN} \\
+ &&\frac{1}{\epsilon} \left(  \left< {\bf v}, \bf{u} \right>_{\Gamma_{cyl}} + \left< {\bf v}, ({\bf u}- {\bf e}_x ) \right>_{\Gamma_{in}} 
+ \left< v_y, u_y\right>_{\Gamma_{axis}\cup \Gamma_{lat}} \right) \nonumber 
\end{eqnarray}
Note that the Neumann boundary conditions do not appear any more thanks to the integration by parts.

%The problem can be set into weak form by multiplying by multiplying Eq. \ref{Newton2} by a test function ${\bf v}$ and the associated divergence constraint by a test function $q$. After a few integration by parts we are led to :

%SECTION TO BE COMPLETED.

%We have to explain the integration by parts of the viscous term.

%\begin{eqnarray}
%\label{NewtonWeak}
%&\forall ({\bf v};q), \\
%\displaystyle &\int \left[ {\bf v} \cdot {\cal C}( {\bf u}_b^g , \delta {\bf u}_b) +  \nabla  \cdot \delta {\bf u}_b q -\nabla  \cdot {\bf v} \delta p_b
%+ \frac{2}{Re} {\bf D}(\delta {\bf u}_b) : {\bf D}({\bf v}) \right]
%\nonumber
%\\
%\nonumber
%\displaystyle & + \int \left[ {\bf v} \cdot ( {\bf u}_b^g \cdot \nabla {\bf u}_b^g) 
%+ \nabla \cdot {\bf u}_b^g  q 
%- \nabla \cdot {\bf v} p_b^g
%+ \frac{2}{Re} {\bf D}({\bf u}_b^g) : {\bf D}({\bf v}) \right] = 0 
%\end{eqnarray}

\section{Additional details of the weakly nonlinear approach}

\subsection{Derivation of the amplitude equation using multiple-scale approach}

The initial derivation of \cite{SippLebedev} makes use of a multiple scale method in order to obtained an amplitude equation.
The starting point can be taken as the following expansion of the velocity flow field:
 {\color{red}
\be{WNL2}
\begin{aligned}
&{\bf u} = {}  {\bf u}_{bc} + \epsilon \left[ A_{wnl}(\tau)  \hat{\bf u} e^{i \omega_c t} + c.c. \right]\\
&+ \epsilon^2 \left[ {\bf u}_\epsilon + |A_{wnl}(\tau) |^2  {\bf u}_{2,0} + \left(  A_{wnl}(\tau) ^2 {\bf u}_{2,2} e^{2 i \omega_c t} + c.c. \right) \right]\\
& + {\cal O}( \epsilon ^3),
\end{aligned}
\ee
}
Note that compared to the simplified version given in the main text by eq. \ref{WNL1}, the amplitude $A_{wnl}$ depends upon a slow time scale 
$\tau = \epsilon^2 t$.

Substituting the expansion \ref{WNL2} into the Navier-Stokes equations \ref{NSprimitive} and grouping terms multiplied by the same power of $\epsilon$, a hierarchy of equations is obtained. The order $\epsilon^0$ gives directly the base flow at $Re_c$. The order $\epsilon^1$
corresponds to the linear neutral eigenmode as computed in the first part of this article.
The order $\epsilon^2$ contains three terms respectively computed as the solutions of the following linear problems:
\begin{eqnarray}
{\color{red} {\cal LNS}_{{\bf u}_{bc}} ({\bf u}_\epsilon) - 2 \nabla \cdot {\bf D}({\bf u}_{bc})} &=&0,
\label{eq:LL1} \\
{\cal LNS}_{{\bf u}_{bc}} ({\bf u}_{2,0}) &=& {\cal C}(\hat{\bf u},\overline{\hat{\bf u}}), \label{eq:LL2} \\
{\cal LNS}_{{\bf u}_{bc}} ({\bf u}_{2,2}) - 2 i \omega_c {\bf u}_{2,2}  &=& \frac{1}{2} {\cal C}(\hat{\bf u},\hat{\bf u}). \label{eq:LL3}
 \end{eqnarray}

Finally, compatibility conditions, {\color{red}given by the Fredholm's alternative, are imposed at order $\epsilon^3$ to remove the secular terms, leading to an amplitude equation, known as Stuart-Landau equation:
\be{WNL3_2}
\frac{\partial A_{wnl}}{\partial \tau} = \Lambda A_{wnl} - (\nu_0+\nu_2)  |A_{wnl}|^2 A_{wnl},
\ee
}
where coefficients $\Lambda$, $\nu_0$ and $\nu_2$ are given by
{\color{red}
\begin{eqnarray}
\Lambda &=& -\frac{ \left< {\hat{\bf u}}^\dag, 
\left( {\cal C}({\bf u}_\epsilon, \hat{\bf u}) + 2 \nabla \cdot  {\bf D}( \hat{\bf u}) \right) \right>}
{  \left<  \hat{\bf u}^\dag,\hat{\bf u} \right> },\label{LAMBDA}\\
\nu_0 &=& \frac{ \left< {\hat{\bf u}}^\dag,  {\cal C}({\bf u}_{20}, \hat{\bf u} ) \right>}
{  \left<  \hat{\bf u}^\dag,\hat{\bf u} \right> },\label{NU0}\\
\nu_2 &=& \frac{ \left< {\hat{\bf u}}^\dag,  {\cal C}({\bf u}_{22}, \overline{\hat{\bf u}})  \right>}
{  \left<  \hat{\bf u}^\dag,\hat{\bf u} \right> }.,\label{NU2}
 \end{eqnarray}
}

\subsection{Normalisation of the eigenmode}

A key issue in the weakly nonlinear expansion is that the definition of the amplitude depends upon a normalization choice of the eigenmodes. Several choices are possible. In the literature three possibilities have been used:
%\begin{itemize}
%\item

First, \cite{SippLebedev} normalized the eigenmode by assuming a specified value to the $y$-component of the velocity at one point, namely:
\be{normsipp}
{\color{red}\hat{u}}_y(1,0) = 0.4612.
\ee
The advantage of this choice is that the amplitude ${\color{red}|A|}$ is then an approximate measure of the energy of the perturbation: 
${\color{red}|A|} \approx A_E$. %{\color{red}However the lift phase its not fixed.}

%\item 
Secondly, \cite{FDR2016} proposed the following {\color{red}normalization} choice:
\be{normFDR}
\int_\Omega |\hat{\bf u}|^2 d {\bf x}  = \frac{1}{2}.
\ee
This directly leads to ${\color{red}|A|} = A_E$, so this normalisation seems equivalent to the previous one.
%{\color{red} The lift phase is not specified in \cite{FDR2016} and can be set to nil before the normalization.}

%\item 
Thirdly, following \cite{Fabre2012}, another convenient choice is to normalize the eigenmode with its lift 
force: 
\be{normfabre}
{{\cal D}_{Re_c}(\hat{\bf u},\hat{p}) }=\frac{1}{2}.
\ee
The advantage of this choice is that the amplitude $|A|$ is then an direct measure of the fundamental lift.
In effect, eq. \ref{lift_cos} directlty leads to $F_{y,1,c} = |A|$, $F_{y,1,s} = 0$.

In our implementation of the WNL approach, we allowed to choose the normalization convention, as seen in line 3 of figure \ref{fig:listingNL}.
%%ATTENTION, si figure est actualisé, il faut actualiser la ligne
In table \ref{tab:WNL_coefs} we give the predictions of the WNL approach using the three normalization choices.
We can note that the coefficients $\nu_0$ and $\nu_2$ strongly depend on the normalization choice. On the other hand, the frequency deviation $\omega_\epsilon$ and the $\lambda$ coefficient, and the term $F_{x,0,\epsilon}$ related to the dependency of mean drag with deviation from the threshold are independent upon the normalization.

Considering the lift force, columns 7 and 8 of the table show that the different choices of normalization give different values for the coefficients $F_{1,y,c}$ and $F_{1,y,s}$. %This explains that the normalization choice fixes differently the phase of the cycle. 
However,  the sin-cos expansion of the lift force can be recast as 
$F_y =  (F_{y,1,c} \cos \omega t + F_{y,1,s} \sin \omega t ) =  |F_{y,1}|  \cos (\omega t + \varphi)$ 
with $ |F_{y,1}| =  \sqrt{F_{y,1,c}^2 + F_{y,1,s}^2}$. The last column of the table confirms that the three possible normalization choices effectively lead to the same values of $|F_{y,1}|$.

\begin{table*}[!h]
\centering
$$
{\small
\begin{array}{|c||c|c|c|c|c|c|c|c|}
\hline
\mbox{Norm.} & \lambda & \nu_{0} & \nu_{2} &\omega_{\epsilon}& F_{x,0,\epsilon} & F_{y,1,c}/\epsilon & F_{y,1,s}/\epsilon &  |F_{y,1}| /\epsilon \\
\hline
\mbox{\cite{SippLebedev}} & 9.10988+3.28004i & 9.3996-32.0289i & -0.305116-0.866118i & 36.2307 
& 5.2848 & - & - & 0.537254
\\
\mbox{\cite{FDR2016}} &  9.10988+3.28004i  & (4.88701 -1.66524 i) \times 10^{-3} & (-1.58635 - 4.50309i )\times 10^{-5} &36.2307
& 5.2848 & - & - & 0.537254
\\
\mbox{\cite{Fabre2012}} & 9.10988+3.28004i & 32.62-111.152i & -1.05886-3.00574i & 36.2307
& 5.2848 & 0.537254 & 0 & 0.537254
\\
\hline
\end{array}
}
$$
\caption{Results of the WNL approach for three different choices of eigenmode normalization.}
\label{tab:WNL_coefs}
\end{table*}

%\be{lift_explanation}

%= {\color{red}|A|} \left( {\color{red}\frac{1}{2}} e^{i \omega t} + c.c. \right)
%=   {\color{red}|A|} \cos (\omega t) ; \quad F_{y,1,{\color{red}s}} = 0. 
%\ee

%\end{itemize}

\begin{figure}
\vspace{-.5cm}\vspace{-.5cm}
\includegraphics[width = .9\linewidth]{Cylinder_Mesh2_Full.png}
\vspace{-.5cm}\vspace{-.5cm}
\includegraphics[width = .9\linewidth]{Cylinder_Mesh2.png}
\caption{Illustration of the stucture of mesh  $\mathbf{M}_2$ (adapted to both the base flow and structural sensitivity).}
\label{fig:mesh2}
\end{figure}

\begin{figure}
\vspace{-.5cm}\vspace{-.5cm}
\includegraphics[width = .9\linewidth]{Cylinder_Mesh4_Full.png}
\vspace{-.5cm}\vspace{-.5cm}
\includegraphics[width = .9\linewidth]{Cylinder_Mesh4.png}
\caption{Illustration of the stucture of mesh  $\mathbf{M}_4$ (adapted to both the base flow and direct eigenmode).}
\label{fig:mesh4}
\end{figure}

\section{Additional details about the self-consistent method}

{\em NOT SURE IF THIS PART SHOULD BE KEPT OR NOT...}

The original form of the SC model given by \cite{ManticLugo14} was obtained by introducing the decomposition (\ref{SC}) into the Navier-Stokes equations, leading to :
\begin{subequations}\label{sc12}
\begin{eqnarray}
{\cal NS}(  {\bf u }_m ) - A^2 {\cal C}{\color{red}( \tilde{{\bf u }}_1, \overline{\tilde{\bf u }_1})} = 0, 
\label{sis1}
\\
(\sigma_{sc} + i \omega_{sc}) {\color{red}\tilde{{\bf u }}_1} =  {\cal LNS}_{{\bf u }_m}( {\color{red} \tilde{{\bf u }}_1} ).
\label{sis2}
\end{eqnarray}
\end{subequations}

Equation (\ref{sis1}) provides the mean flow field ${\bf u }_m$ while the 
pseudo-eigenpairs $(\lambda_{sc},{\color{red}  \tilde{{\bf u }}_1})$ can be computed by solving the eigenvalue problem (\ref{sis2}).
\cite{ManticLugo14} Initially proposed a resolution method involving two imbricated loops, which is advantageaously replaced by
the direct Newton resolution of section 4.3.

%The computed mode is normalized as $ || \tilde{{\bf u }}|| = 1/{\sqrt{2}}$
%is of the same form as  (\ref{HBEq1}) except that $i \omega$ is 
%replaced by $\sigma_{SC} + i \omega_{SC}$. 
% The mean flow is then governed by the same equation
%\ref{HBEq0}) written above, while $\tilde{{\bf u }}_1$ is the solution of an eigenvalue problem with the same form as  (\ref{HBEq1}) except that $i \omega$ is replaced by $\sigma_{SC} + i \omega_{SC}$.

The self-consistent model has the following properties:
\begin{itemize}
\item[-] For $ \ll 1$ it is equivalent to the linear eigenvalue problem (\ref{LEP}), and the generalized eigenvalue coincides with the one predicted by linear stability : $\sigma_{SC} + i \omega_{SC} = \sigma_{lin} + i \omega_{lin}$.
\item[-] For $\sigma_{SC}=0$ (corresponding to a specific choice of the amplitude $A=A_c$),  the expansion (\ref{SC}) is equivalent to 
the Fourier expansion \ref{eq:sc1} taken as the starting point in the present paper. 
\item[-] For $0<A<A^c$, the resolution leads to a relation $\sigma_{SC}(A) ; \omega_{SC}(A)$
such that $0< \sigma_{SC}(A) < \sigma_{lin}$.
 Although in this case the expansion ({\ref{SC}}) cannot represent the flow for all $t$, Manti\v{c}-Lugo et al \cite{MLugo2014} argued that the relation between $\sigma_{SC}$ and $A$ can be used to build an amplitude equation which captures the transient approach to the limit cycle. 
\end{itemize}

\section{Mesh convergence : efficiency of mesh adaptation and effect of domain size}

\begin{table*}
$$
\begin{array}{|c||c|c|c|c|c|c|c|c|c|}
\hline
\mbox{Mesh} & N_p & N_{dof} & \delta_{min} & \delta_{max} & \delta_A  & \delta_B  & \delta_C  & \delta_D  \\
\hline
\mathbf{M}_1 \mbox{(Adapt on base flow) } & 1429 & 12545	& 0.0131 & 14.33 		& 0.0259 	& 0.514 	& 0.819 	& 1.067 \\   
\mathbf{M}_2 \mbox{(Adapt on sensitivity) } & 2038 & 		& 0.0155 & 14.17 		& 0.02826 & 0.2046 	& 0.3909 	& 1.2014 	\\
\mathbf{M}_3 \mbox{(Adapt on sensitivity, split) } & 7974 &		& 0.0077 & 7.1  		& 0.014 	& 0.1 	&   0.2 	& 0.6   \\
\mathbf{M}_4 \mbox{(Adapt on mode) } 	& 12080  &			&0.00825	& 124.61		& 0.0229	& 0.143	& 0.0993	& 0.0934 \\
\mathbf{M}_5 \mbox{(Adapt on adjoint) } 	& 3813 	& 33715		& 0.0081	& 14.4		& 0.0123 	& 0.156	& 0.166	& 1.44  \\
\hline
\end{array}
$$
\caption{Description of meshes used for validation of mesh adaptation strategy : number of vertices $N_p$ ; number of degrees of freedom of the P2-P2-P1 Taylor-hood basis $N_{dof}$ ; cell size (minimum and value, and value at four characteristic point A,B,C,D as defined in the text). 
 }
\label{tab:conv1}
\end{table*}

\begin{table*}
$$
\begin{array}{|c||c|c||c||c|c||c|c|c|}
\hline
\mbox{Mesh} & L_x & F_x & \lambda & L_{x,SC} & F_{x,SC} & \omega_{SC}  & F_{y,1,c} & A_{E} \\
\hline
\mathbf{M}_1 & 4.0733 & 0.6431 	& 0.047056 + 0.74416i 		& 2.6073  &0.69277 		&  0.84334 & 0.1298 & 1.8301  \\
\mathbf{M}_2 & 4.075 &.  0.64348  	& 0.046719 + 0.74489i 		& 2.          & 0.69246 	& 0.84351 & 0.12789 & 1.7134 \\  
\mathbf{M}_3 & 4.0772 & 0.64391 	& 0.04684. +  0.74511i 		& 2.6141  & 0.69338 	& 0.84383 & 0.12799 & 2.048   \\ 
\mathbf{M}_4 & 4.0748 & 0.64402 	& 0.04676  + 0.74502i 		& 2.613 	& 0.690338 	& 0.84371 & 0.12809 & 2.5905 \\
\mathbf{M}_5 & 4.0772 & 0.64384	& 0.04665 + 0.74530i		& 2.6146 	& 0.6932		& 0.84333 & 0.1276	 & 2.5971 \\
\hline
\end{array}
$$
\caption{Results for mesh adaptation strategy ($Re = 60$) : Base-flow characteristics $L_x$ and $F_x$, linear eigenvalue $\lambda$, 
Nonlinear self-consistent model characteristics  $\omega_{SC}$, $F_{y,1,c}$ and $A_E$. All the results can be optained using the matlab program
{\em SCRIPT\_CYLINDER\_MESHCONVERGENCE.m}. }
\label{tab:conv2}
\end{table*}

\begin{table*}
$$
\begin{array}{|c|c||c|c||c||c|c||c|c|c|}
\hline
\mbox{Mesh} & N & L_x & F_x & \lambda & L_{x,SC} & F_{x,SC} & \omega_{SC}  & F_{Y,SC} & A_{E,SC} \\
\hline
\mathbf{M}_2 \mbox{(ref)} 	& 7974  	& 4.0772 & 0.64391 	& 0.04684. +  0.74511i 	& 2.6141  & 0.69338 	& 0.84383 & 0.12799 & 2.048   \\ 
\mathbf{M}_6 [-20,40]x[0,20] 	& 7437	&  4.108 & 0.64987 	& 0.048368. +  0.74952i 	& 2  & 0.69957 	& 0.85015 & 0.13125 & 2.3638   \\ 
\mathbf{M}_7 [-80,160]x[0,80] 	& 7480	& 4.0641 & 0.64129		& 0.046271 + 0.74341i 	& 2 	& 0.69069 	& 0.84159 & 0.12653 & 2.4453 \\
\mathbf{M}_8 \mbox{(slip conditions)}	 & 7056	& 4.0467 &0.66295		& 0.049216+0.76553i 	& 2 	& 0.69241		& 0.8438  & 0.12716	 & 2.3202 \\
\hline
\end{array}
$$
\caption{Comparison of the performances of several meshes with variable dimensions and different boundary conditions}
\label{tab:conv3}
\end{table*}

This appendix presents complementary results obtained using various mesh designs. 
All the results can be obtained using the following program available on the StabFem website : 
{\em SCRIPT\_CYLINDER\_MESHCONVERGENCE.m}.

\subsection{Efficiency of the mesh adaptation process}

As discussed in section 3, the mesh adaptation proves to be an extremely efficient way to obtain significant results 
with very reasonable meshes. The objective of this paragraph is to demonstrate this point by comparing the efficiency of several ways to perform mesh adaptation.

For this purpose, 5 meshes were generated. 
Mesh $\mathbf{M}_1$ was adapted on the {\em base flow} obtained for $Re=60$.
Mesh $\mathbf{M}_2$ was adapted to both the base flow and structural sensitivity.
Mesh $\mathbf{M}_3$ was obtained by a subsequent refinement of mesh $\mathbf{M}_2$, splitting all triangles in four subtriangles, therefore doubling the effective density of the mesh.
Meshes $\mathbf{M}_4$ and $\mathbf{M}_5$ were obtained by adapting to the structure of the direct eigenmode and of the adjoint eigenmode.
In each case, the adaptmesh process was repeated twice in order to ensure a correct convergence.

Figures \ref{fig:mesh2} and \ref{fig:mesh4} illustrate the structure of meshes $\mathbf{M}_2$ and $\mathbf{M}_4$. As can be observed, these two mesh adaptation strategies lead to meshes with comparable densities in the region close to the cylinder. On the other hand, when moving downwards in the wake, mesh $\mathbf{M}_2$ quickly gets rather coarse, while mesh $\mathbf{M}_4$ maintains a significant density

Table \ref{tab:conv1} gives additional details about the geometry of these meshes. In particular, we document the minimum and maximum cell size, as well as the cell size at four point A,B,C,D defined with by their coordinates as follows : $(x_A,y_A) = (0,0.5)$ (within the boundary layer at the cylinder wall); $(x_B,y_B) = (2.5,0.5)$ (in the region of maximum structural sensitivity); $(x_C,y_C) = (4,0)$ (in the near wake); $(x_D,y_D) = (10,0)$ (in the far wake). Results confirm that mesh all meshes have similar densities in the near wake (cell size at points A,B,C are comparable) 
while $\mathbf{M}_4$ has maximum resolution in the far wake (in the vicinity of point D).

Table  \ref{tab:conv2} compares the results obtained with the five meshes. For base-flow characteristics $L_x$ and $F_x$, all values agree with a relative dispersion of less than $0.15\%$, confiming that all adaptation stategies are successful to correctly compute the base flow. 
The performances of meshes for linear stability calculations can then be evaluated by comparing the eigenvalues. Meshes $\mathbf{M}_2$ to $\mathbf{M}_5$ all give values within less than $0.1\%$ dispersion. The value obtained with mesh  $\mathbf{M}_1$, which is not adapted to the eigenmode, is a bit farther from the others but still rather good. The table also displays results allowing to compare the performances of meshes for nonlinear self-consistent calculations. As for the frequency and the maximum lift, meshes $\mathbf{M}_2$ to $\mathbf{M}_5$ again give almost identical values within less than $0.1\%$ dispersion. The dispersion is much larger concerning the energy-amplitude of the perturbation $A_E$ displayed in the last column. Only the mesh $\mathbf{M}_4$ is able to correctly compute this quantities, while all other meshes significantly underestimate it. This is not surprising since this quantity is an integral one which depends upon the structure of the nonlinear perturbation in the whole wake, not only the near-wake region.

From this study we can conclude that if we are only interested in predicting the frequency of the mode and the forces exerted on the cylinder (in both linear and nonlinear regimes), the strategy of mesh adaptation to both base flow and structural sensitivity (mesh $\mathbf{M}_2$) is the most efficient and leads to a very light mesh (here only 2048 points). On the other hand, if we are interested in describing the structure of the perturbation in the whole domain (and being able to correctly evaluate its energy), mesh adaptation to the eigenmode structure is preferable. However this second strategy produces a much heavier mesh (here 12080 point).

\subsection{Effect of domain size and boundary conditions}

As already identified in several previous studies, the size of the domain and the type of boundary conditions applied at the boundaries have a notable impact on the results. To illustrate this, we designed three additional meshes. All were obtained through adaptation to base flow and sensitivity, just as mesh $\mathbf{M}_2$.
Meshes $\mathbf{M}_6$ and $\mathbf{M}_7$ are respectively twice smaller and twice larger than the reference one. 
 $\mathbf{M}_8$ has the same dimension as the reference case but the boundary condition at the lateral boundary $\Gamma_{lat}$ is replaced by a less restrictive slip condition.

Even though the domain size of the reference case (namely $[-40,80]\times[0,40]$) may appear large, the table shows that confinement effects are still present. The quantity which appears the most sensible to domain size and/or boundary conditions is the imaginary part of the linear eigenvalue. Interestingly, the nonlinear SC results appears to be more robust with respect to confinement effects than linear ones. 
In effect, values for nonlinear frequency $\omega_{SC}$ and the maximum lift $F_{y,1,c}$ obtained with meshes  $\mathbf{M}_2$, $\mathbf{M}_7$
and  $\mathbf{M}_8$ agree with less than $0.3\%$ dispersion.

%In this appendix we compare the results obtained with 8 different meshes, to demonstrate the efficency of the mesh adaptation process. The whole results can be obtained using the script {\em SCRIPT\_CYLINDER\_MESHCONVERGENCE.m} available in the StabFem repository.

%Giannetti \& Luchini\cite{GiannettiLuchini} showed that the accuracy of the stability results for the flow past a circular cylinder is strictly related to the mesh characteristics  in the wavemaker region, i.e. the region where the structural sensitivity reaches its maximum values. Following this idea, we chose as reference solution the field, computed on an adapted mesh obtained by using the structural sensitivity field.We set the interpolation  error equal to 0.01 and the size of the computational domain is $[-40,120]\times[0,40]$. The base flow is computed by using classical no-slip boundary conditions on the body surface, a uniform velocity profile at the inlet and no-stress boundary conditions at the outlet and lateral boundaries. The conditions for the stability computations are simply derived from the ones of the base flow.

%Figure \ref{fig:MeshConvergence} displays global stability results. We note that there is a very weak variation in the growth rate and we found an error up to 1\% on the  Strouhal number. Figure \ref{ill_bsflow} illustrate the procedure adopted to compute the 
%base flow and the adapted mesh. Figure \ref{stabmesh} reports the Matlab code 
%adopted to adapt the mesh by using the information provided by both the base flow and the sensitivity field.

%Figure 1 gives a retranscription of the sequence of commands (from {\em SCRIPT\_CYLINDER\_ADAPTMESH\_BASEFLOW}) 
%and the output produced.

\bibliographystyle{asmems4}

\bibliography{ARTICLE_ASME}

\end{document}

### 2018-06-12 CYLINDER/SCRIPT_CYLINDER_MESHTESTS.m

@@ -5,50 +5,54 @@
 % CHAPTER 0 : set the global variables needed by the drivers
 
 run('../SOURCES_MATLAB/SF_Start.m');
-verbosity=2;
+verbosity=0;
 figureformat='png'; AspectRatio = 0.56; % for figure
 
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-disp(' ');    
-disp('### 1 : MESH based on base flow : ');     
+ 
+ %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+ disp(' ');    
+ disp('### 1 : MESH based on base flow : ');     
+ disp(' ');
+ %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+ 
+ 
+ bf=SF_Init('Mesh_Cylinder.edp',[-40 80 40]);
+ bf=SF_BaseFlow(bf,'Re',1);
+ bf=SF_BaseFlow(bf,'Re',10);
+ bf=SF_BaseFlow(bf,'Re',60);
+ bf=SF_Adapt(bf,'Hmax',10);
+ bf=SF_Adapt(bf,'Hmax',10);
+ 
 disp(' ');
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-
-baseflow=SF_Init('Mesh_Cylinder.edp',[-40 80 40]);
-baseflow=SF_BaseFlow(baseflow,'Re',1);
-baseflow=SF_BaseFlow(baseflow,'Re',10);
-baseflow=SF_BaseFlow(baseflow,'Re',60);
-baseflow=SF_Adapt(baseflow,'Hmax',10);
-baseflow=SF_Adapt(baseflow,'Hmax',10);
-
-disp(' ');
+disp(['number of vertices : ' num2str(bf.mesh.np)]);
+disp(['number of DOF : ' num2str(bf.mesh.Ndof)]);
 disp('### Mesh grid size at point A,B,C,D : ');
-disp(['A : ' num2str(baseflow.mesh.deltaA)]);
-disp(['B : ' num2str(baseflow.mesh.deltaB)]);
-disp(['C : ' num2str(baseflow.mesh.deltaC)]);
[…]

### 2018-06-12 EXAMPLE_Lshape/SCRIPT_Lshape.m

@@ -1,3 +1,8 @@
+
+% This script is a basic example which illustrates the main functionalities
+% of the StabFem Software
+
+
 clear all;
 close all;
 run('../SOURCES_MATLAB/SF_Start.m');

### 2018-06-12 SOURCES_MATLAB/SF_Stability.m

@@ -2,10 +2,10 @@ function [eigenvalues,eigenvectors] = SF_Stability(baseflow,varargin)
 
 % Matlab/FreeFem driver for Base flow calculation (Newton iteration)
 %
-% usage : [eigenvectors] = SF_Stability(bf, [,param1,value1] [,param2,value2] [...])
+% usage : [eigenvectors] = SF_Stability(field, [,param1,value1] [,param2,value2] [...])
 %
-% baseflow is either a "baseflow" structure (with mesh as a field) or a
-% mesh structure.
+% field is either a "baseflow" structure (with "mesh" structure as a subfield) 
+% or directly a "mesh" structure (for instance in problems such as sloshing where baseflow is not relevant).
 %
 % Parameters include :
 % Re : Reynolds number (specify only if it differs from the base flow, which is not usual)

### 2018-06-15 99_Documentation/11_StabFem_BasicFunctionalities.tex
Documentation !

% !TEX root = main.tex

\chapter{The basics of StabFem }

In this chapter we explain the basic functionalities of StabFem. We recommend that you study the basic example \texttt{EXAMPLE\_Lshape.m}.

This directory contains three freefem programs and a demo matlab script doing solving tghe following problem :

\section{Simple problem : solution of heat equation in a L-shaped domain}

1. Solve the steady heat conduction equations on a L-shaped domain with constant volumic source term $P$ and homogeneous Dirichlet boiundary conditions :

$$ \nabla^2 T = P  \mbox {  for } {\bf x} \in \Omega ; \quad T = 0   \mbox {  for } {\bf x} \in \Gamma$$

2.  Solve the unsteady heat conduction equations on a L-shaped domain with zero source term $P$ and time-periodic Dirichlet boundary conditions :

$$ 
 \partial T_1/\partial t= \nabla^2 T_1  \mbox {  for } {\bf x} \in \Omega ; \quad T_1 = T_w e^{i \omega t}   \mbox {  for } {\bf x} \in \Gamma
$$

\section{Matlab script and results}

The programs are sufficiently short to be fully given in these pages. See figures \ref{SCRIPT_Lshape.m}, etc...

The reader already familiar with FreeFm++ should not have any provblem in undersanding the programs. If not, we recommand that you study the FreeFem++ Manual (chapter "Learning by examples").

The results are given

\begin{figure*}[t]
\small
\lstinputlisting{../EXAMPLE_Lshape/SCRIPT_Lshape.m}
 \normalsize
\caption{
Matlab program {\texttt SCRIPT\_Lshape.m})}
\label{SCRIPT_Lshape.m}
\end{figure*}

\begin{figure*}[t]
\small
\lstinputlisting{../EXAMPLE_Lshape/Lshape_Mesh.edp}
 \normalsize
\caption{
FreeFem++ program {\texttt Lshape\_Mesh.edp})}
\label{Lshape_Mesh.edp}
\end{figure*}

\begin{figure*}[t]
\small
\lstinputlisting{../EXAMPLE_Lshape/Lshape_Steady.edp}
\normalsize
\caption{
FreeFem++ program {\texttt Lshape\_Steady.edf})}
\label{Lshape_Mesh.edp}
\end{figure*}

\begin{figure*}[t]
\includegraphics[width = .45 \linewidth]{../EXAMPLE_Lshape/FIGURES/Lshape_T0.png}
\includegraphics[width = .45 \linewidth]{../EXAMPLE_Lshape/FIGURES/Lshape_T0_Cut.png}
\caption{Solution for the steady hrat equation in a L-shape domain : $(a)$ Temperature field $T(x,y)$. 
$(b)$ Temperature $T(x,0.25)$ along a horizontal line. }
\label{Lshape_Mesh.edp}
\end{figure*}

\section{How does it work ?}

\subsection{Explanation of the \texttt{.ff2m} exchange format}.

### 2018-06-15 ARTICLE_STABFEM/ARTICLE_ASME_Submitted.tex
Documentation !

--- 2018-06-12 ARTICLE_STABFEM/ARTICLE_ASME_V4.tex
@@
 a one-dimensional problem.
-On the other hand,  when there are at least two spatial variables, the class of methods suited to solve such problems are generally called "global stability approaches".
+On the other hand,  when there are at least two spatial variables, the class of methods suited to solve such problems are generally called ``global stability approaches".
 %When the flow has no analytical expression, the stability problem requires a numerical resolution, and when there are at least two spatial variables, the class of methods suited to solve such problems are generally called "global stability approaches."%\footnote{Sorry Laurette !}
@@
 Beyond this simple question, in the past two decades, a number of extensions have been developed and popularized.
-{\em Adjoint methods} are an important extension \cite{GiannettiLuchini},\cite{Marquet} ; they can give insight into the sensitivity of the flow to intrinsic or extrinsic contributions.
+{\em Adjoint methods} are an important extension \cite{GiannettiLuchini},\cite{Marquet}; they can give insight into the sensitivity of the flow to intrinsic or extrinsic contributions.
 {\em Nonlinear stability approaches} \cite{MLugo2014}, \cite{SippLebedev} have also been developed in order to extend the range of applicability of the approach towards large amplitude perturbations.
@@
 \item
-Secondly we offer an open-source and user-friendly software called  "StabFem"
-\cprotect\footnote{The StabFem software may be obtained at the following url : 
+Secondly we offer an open-source and user-friendly software called  ``StabFem"\cprotect\footnote{The StabFem software may be obtained at the following url : 
 \url{https://github.com/erbafdavid/StabFem}} 
@@
 
-Although we don't claim to invent any radically new method, our exposition and implementation contains a number of originalities making the computation particularly efficient in terms of computational time and memory (all the figures of the paper can be produced in only a few minutes on a standard laptop)
-\footnote{All the figures contained in the present paper can be processed by launching a single Matlab script SCRIPT\_CYLINDER\_ALLFIGURES.m .
+Although we don't claim to invent any radically new method, our exposition and implementation contains a number of originalities making the computation particularly efficient in terms of computational time and memory (all the figures of the paper can be produced in only a few minutes on a standard laptop)\footnote{All the figures contained in the present paper can be processed by launching a single Matlab script SCRIPT\_CYLINDER\_ALLFIGURES.m .
 On a MacbookPro (2018,  2.5Ghz, 16Go Ram),  the execution time is 19.76 seconds for the results of the linear analysis (section 3) and 15.
@@
 \begin{eqnarray} \label{NSprimitive}
-\partial_t {\bf u} = {\color{red}{\cal NS} ({\bf u},p)}
+\partial_t {\bf u} = {\cal NS} ({\bf u},p)
 \equiv - {\bf u} \cdot \nabla {\bf u} - \nabla p + \frac{2}{Re}  \nabla \cdot {\mathsf{D}}({\bf u}),  \\
@@
 \be{NSweak}
-\forall [{\bf v},q], \quad \partial_t \left< {\bf v}, {\bf u}\right> = \left< {\bf v} , {\color{red}{\cal NS} ({\bf u},p)} \right> + \left< q, \nabla \cdot {\bf u}\right>.
+\forall [{\bf v},q], \quad \partial_t \left< {\bf v}, {\bf u}\right> = \left< {\bf v} , {\cal NS} ({\bf u},p) \right> + \left< q, \nabla \cdot {\bf u}\right>.
 \ee
@@
 
-We look for a steady base-flow {\color{red}$[{\bf u}_b,p_b]$} satisfying the steady Navier-Stokes equations, i.e. 
+We look for a steady base-flow $[{\bf u}_b,p_b]$ satisfying the steady Navier-Stokes equations, i.e. 
 %${\cal NS} ({\bf u}_b,p_b) = 0$.
-{\color{red}${\cal NS} ({\bf u}_b,p_b) = 0$.}
-Suppose that we have a {\color{red}``guess''}  for the base flow $[{\bf u}_b^g,p_b^g]$  which almost satisfies the equations.  We look for a better approximation under the form
+${\cal NS} ({\bf u}_b,p_b) = 0$.
+Suppose that we have a ``guess''  for the base flow $[{\bf u}_b^g,p_b^g]$  which almost satisfies the equations.  We look for a better approximation under the form
 \be{Newton1}
@@
 Injecting (\ref{Newton1}) into the weak form (\ref{NSweak}) of the Navier-Stokes equations and developing up to linear terms in terms of the perturbation lead to  
-${\cal NS}  ({\bf u}_b^g,p_b^g) + {\color{red} {\cal LNS} _{{\bf u}_b^g}(\delta {\bf u}_b,\delta p_b)}$, which can also be written in weak form as :
+${\cal NS}  ({\bf u}_b^g,p_b^g) +  {\cal LNS} _{{\bf u}_b^g}(\delta {\bf u}_b,\delta p_b)$, which can also be written in weak form as :
 \bes{Newton2}
-&\left< {\bf v}, {\color{red}{\cal NS} ({\bf u}_b^g,p_b^g)}\right> + \left<q, \nabla \cdot {\bf u}_b^g\right>  
-\\
-+ &\left< { \bf v}, {\color{red}{\cal LNS} _{{\bf u}_b^g}( \delta {\bf u}_b,\delta p_b) }\right> + \left<q, \nabla \cdot \delta{\bf u}_b\right> = 0,
+&\left< {\bf v}, {\cal NS} ({\bf u}_b^g,p_b^g)\right> + \left<q, \nabla \cdot {\bf u}_b^g\right>  
+\\
++ &\left< { \bf v}, {\cal LNS} _{{\bf u}_b^g}( \delta {\bf u}_b,\delta p_b) \right> + \left<q, \nabla \cdot \delta{\bf u}_b\right> = 0,
 \ees
-where ${\cal LNS}$ is the linearised Navier-Stokes operator, defined by its action on a flow field {\color{red}$[{\bf u} , p]$} as follows 
+where ${\cal LNS}$ is the linearised Navier-Stokes operator, defined by its action on a flow field $[{\bf u} , p]$ as follows 
 \be{defNSL}
-{\color{red} {\cal LNS}_{{\bf U}}( {\bf u}, p)} = - {\cal C}( {\bf U} , {\bf u}) -\nabla p
+ {\cal LNS}_{{\bf U}}( {\bf u}, p) = - {\cal C}( {\bf U} , {\bf u}) -\nabla p
 +\frac{2}{Re} \nabla  \cdot {\mathsf{D}}({\bf u}), %\quad ( \mbox{ with } \nabla \cdot {\bf u } = 0 \, ).
@@
 This problem can now be discretized by projecting upon a basis of Taylor-Hood $(u,v,p) \rightarrow (P2,P2,P1)$ finite elements.
-Noting $\delta X$ the discretization of {\color{red}$[\delta {\bf u}_b,\delta p_b]$} this eventually leads to a matricial problem of the form $A \cdot \delta X = Y$.
+Noting $\delta X$ the discretization of $[\delta {\bf u}_b,\delta p_b]$ this eventually leads to a matricial problem of the form $A \cdot \delta X = Y$.
 The procedure of Newton iteration is to solve iteratively this set of equations up to convergence.
@@
 \ee
-{\color{red} where} ${\mathsf{A}}$ is the matrix resulting from the discretization of ${\cal LNS}_{{\bf u}_b}$, i.e.
-the same matrix  appearing in the Newton computation of the base flow, and  $B$ is a 'weight' matrix associated to the scalar product $\left<v,u\right> = \int \overline{\bf v} \cdot {\bf u} \mbox{ d} \Omega$.
+where ${\mathsf{A}}$ is the matrix resulting from the discretization of ${\cal LNS}_{{\bf u}_b}$, i.e.
+the same matrix  appearing in the Newton computation of the base flow, and  $B$ is a ``weight" matrix associated to the scalar product $\left<v,u\right> = \int \overline{\bf v} \cdot {\bf u} \mbox{ d} \Omega$.
 
@@
 A popular alternative is the use of iterative methods which allow us to compute a limited set of eigenvalues located in the vicinity of a
-"shift" value $\lambda_{shift}$. The simplest version of this method is the simple shift-invert iteration, which consists of solving iteratively the system
+``shift" value $\lambda_{shift}$. The simplest version of this method is the simple shift-invert iteration, which consists of solving iteratively the system
 $$
@@
 Our implementation in StabFem allows to chose between single eigenvalue computation (power method) and multiple eigenvalue computation (Arnoldi).
-The selection is made according to the parameter "nev" transmitted to the driver.
+The selection is made according to the parameter ``nev" transmitted to the driver.
 
@@
 %Following Sipp \& Lebedev,
-The most common procedure is to decompose the domain into several parts with different grid densities; for instance for the wake of a cylinder, we will design a near-wall region with very small  size, a "wake" region with intermediate mesh size, and an outer region with large mesh size.
+The most common procedure is to decompose the domain into several parts with different grid densities; for instance for the wake of a cylinder, we will design a near-wall region with very small  size, a ``wake" region with intermediate mesh size, and an outer region with large mesh size.
 The inconvenient is that the design relies on an a priori expectation of the regions where gradients will be large.
@@
 Then we perform the mesh adaptation with the structural sensitivity, as explained in a previously (line 13). 
-The resulting mesh, depicted in figure \ref{meshM2}, is used for the rest of the computations presented in this paper (except for displaying the eigenmode in figure 4$a$). 
+The resulting mesh, depicted in figure \ref{fig:mesh2}, is used for the rest of the computations presented in this paper (except for displaying the eigenmode in figure 4$a$). 
 Appendix D presents additional test regarding mesh convergence, and demonstrate that results obtained with the resulting mesh are trustable within $0.1\%$ accuracy for the eigenvalue, while requiring a very reasonable number of grid points compared to previous studies of this problem.
@@
 In the past decade, efforts have been devoted to extend the range of validity of global approaches into the nonlinear regime for $Re>Re_c$, with the double objective to describe the properties of the limit cycle reached after saturation and to derive amplitude equations describing the transitent dynamics towards this cycle.
-The two main milestones in this direction {\color{red} are} the {\em weakly nonlinear model}  (WNL) of Sipp \& Lebedev \cite{SippLebedev} and the {\em self-consistent model} (SC) of Manti\v{c}-Lugo et al \cite{MLugo2014}.
- {\color{blue} In this review, we will address only the first of the two questions, namely {\color{red} the} description of the saturated cycle, and leave aside the question of transient dynamics.
+The two main milestones in this direction  are the {\em weakly nonlinear model}  (WNL) of Sipp \& Lebedev \cite{SippLebedev} and the {\em self-consistent model} (SC) of Manti\v{c}-Lugo et al \cite{MLugo2014}.
+ In this review, we will address only the first of the two questions, namely  the description of the saturated cycle, and leave aside the question of transient dynamics.
 We will successively review the two aforementioned models, in a simplified formulation devoted to describe only the saturated cycle.
@@
 Finally, in line with the previous section, we will again illustrate with results obtained for the wake of a cylinder.
- }
 
@@
 
- In this part, to simplify the notations, we symbolically write the Navier-Stokes equations, as {\color{red}$\partial_t {\bf u} = {\cal NS} ({\bf u})$}, therefore dropping the systematic reference to the incompressibility constraint and associated pressure field.
-{\color{red} The same is done with the linearized operator ${\cal LNS}_{{\bf U}}( {\bf u})$.}
+ In this part, to simplify the notations, we symbolically write the Navier-Stokes equations, as $\partial_t {\bf u} = {\cal NS} ({\bf u})$, therefore dropping the systematic reference to the incompressibility constraint and associated pressure field.
+The same is done with the linearized operator ${\cal LNS}_{{\bf U}}( {\bf u})$.
 
@@
 
-\paragraph{WNL model : analysis}
+\paragraph{WNL model: analysis}
 
@@
 The starting point can be taken as the following expansion of the velocity flow field:
- {\color{red}
 \be{WNL1}
 \begin{aligned}
-&{\bf u} = {}  {\bf u}_{bc} + \epsilon \left[ A_{wnl}  \hat{\bf u} e^{i (\omega_c+\epsilon^{\color{red}2} \omega_\epsilon)  t} + c.c. \right]\\
-&+ \epsilon^2 \left[ {\bf u}_\epsilon + |A_{wnl}|^2  {\bf u}_{2,0} + \left(  A_{wnl}^2 {\bf u}_{2,2} e^{2 i(\omega_c+\epsilon^{\color{red}2} \omega_\epsilon)  t} + c.c. \right) \right]\\
+&{\bf u} = {}  {\bf u}_{bc} + \epsilon \left[ A_{wnl}  \hat{\bf u} e^{i (\omega_c+\epsilon^2 \omega_\epsilon)  t} + c.c. \right]\\
+&+ \epsilon^2 \left[ {\bf u}_\epsilon + |A_{wnl}|^2  {\bf u}_{2,0} + \left(  A_{wnl}^2 {\bf u}_{2,2} e^{2 i(\omega_c+\epsilon^2 \omega_\epsilon)  t} + c.c. \right) \right]\\
 & + {\cal O}( \epsilon ^3),
@@
 \ee
-}
 
 This expansion is built as an asymptotic expansion in terms of the small parameter $\epsilon = \sqrt{1/Re_c - 1/Re}$ corresponding to the distance to the critical Reynolds. 
-The zero-order term {\color{red}${\bf u}_{bc}$} is the base flow at the threshold $Re_c$.
+The zero-order term ${\bf u}_{bc}$ is the base flow at the threshold $Re_c$.
 
@@
 interaction of $\hat{\bf u}$ with itself. These three terms are computed as solutions of nonsingular linear systems 
-(see eqs. \ref{eq:LL1},\ref{eq:LL2},\ref{eq:LL3} in appendix B).
-
-At ${\cal O}( \epsilon ^3)$, compatibility conditions have to be imposed to ensure that the problem is correcty posed.
-These conditions lead to an "amplitude equation" which relates the amplitude $ A_{wnl}$ to three parameters $\Lambda, \nu_{0}$ and $\nu_{2}$ which depend
+(see eqs. \ref{eq:LL1}, \ref{eq:LL2}, \ref{eq:LL3} in appendix B).
+
+At ${\cal O}( \epsilon ^3)$, compatibility conditions have to be imposed to ensure that the problem is correctly posed.
+These conditions lead to an ``amplitude equation" which relates the amplitude $ A_{wnl}$ to three parameters $\Lambda, \nu_{0}$ and $\nu_{2}$ which depend
 uniquely on ${\bf u}_\epsilon$, ${\bf u}_{2,0}$ and ${\bf u}_{2,2}$, respectively (see equations \ref{LAMBDA}, \ref{NU0} and \ref{NU2} in appendix B).
-Restricting to the description of the limit cycle, the "amplitude equation" takes the form :
+Restricting to the description of the limit cycle, the ``amplitude equation" takes the form :
 
@@
 Developing the terms as an asymptotic expansion leads to :
-
 \be{drag_cos}
@@
 & F_{x0,\epsilon} = {\cal D}_{Re_c} ({\bf u}_\epsilon, p_\epsilon ) - {\cal D}_{1} ({\bf u}_{bc},0) 
-+ | A_{wnl} |^2 {\cal D}_{Re_c} ({\bf u}_{2,0},p_{2,0}) 
++ | A_{wnl} |^2 {\cal D}_{Re_c} ({\bf u}_{2,0},p_{2,0}). 
 \end{aligned}
 \end{equation*}
-
 %_{\epsilon},p_\epsilon)
@@
 
-Lines 1-8 of the script shown in igure \ref{fig:listingNL}, which is extracted from the script {\color{red}
-\verb|SCRIPT_CYLINDER_ALLFIGURES.m|}, illustrate the sequence of commands to 
+Lines 1-8 of the script shown in figure \ref{fig:listingNL}, which is extracted from the script 
+\verb|SCRIPT_CYLINDER_ALLFIGURES.m|, illustrate the sequence of commands to 
 perform the weakly nonlinear study for the cylinder wake.
-On line 2, we first determine the instability threshold, and the corresponding base flow and eigenmode
-\footnote{This routine uses Newton iteration to directly compute the base flow, the eigenmode, the frequency and the critical Reynolds.
+On line 2, we first determine the instability threshold, and the corresponding base flow and eigenmode\footnote{This routine uses Newton iteration to directly compute the base flow, the eigenmode, the frequency and the critical Reynolds.
 The algorithm is very similar to the one presented for the HB, with an additional unknown (Re) and an additional constraint (normalization of the mode).
@@
 As discussed in \cite{SippLebedev} and \cite{FDR2016},  when compared to DNS results the approach gives good prediction in the immediate vicinity of $Re_c$, but deviation appears very rapidly and disagreement is already large at $Re=48$ (although, as discussed by \cite{FDR2016} and also observed  \cite{Tchoufag2015}, a convenient definition of the $\epsilon$ improves the results).
-{\color{red} These aspects are justified by the perturbative nature of the WNL approach. The description of the limit cycle can be extended to larger $Re$ with the approach presented next.  }
+ These aspects are justified by the perturbative nature of the WNL approach. The description of the limit cycle can be extended to larger $Re$ with the approach presented next.
 
@@
 
-We now briefly review the self-consistent {\color{red} model} as introduced by Manti\v{c}-Lugo et 
+We now briefly review the self-consistent model as introduced by Manti\v{c}-Lugo et 
 al \cite{MLugo2014}. In its original exposition, the authors adopted a pseudo-eigenmode expansion of the flow 
@@
 \be{SC}
-{\bf u } = {\bf u }_m + A_{sc} \left[ \tilde{{\bf u }}_1 e^{\sigma_{sc} t + i \omega_{sc} t} +   {\color{red} \overline{\tilde{\bf u }_1}} e^{\sigma_{sc} t  -i \omega_{sc} t} \right],
-\ee  
-where ${\bf u }_m$ is the {\em mean flow} defined by phase-averaging over the cycle, $\tilde{{\bf u }}_1$ is a pseudo-eigenvector which is normalized by the condition  $||\tilde{{\bf u }}_1|| = 1/\sqrt{2}$, {\color{red}$\overline{\tilde{{\bf u }}_1}$ is its complex conjugate,}
+{\bf u } = {\bf u }_m + A_{sc} \left[ \tilde{{\bf u }}_1 e^{\sigma_{sc} t + i \omega_{sc} t} +   \overline{\tilde{\bf u }_1} e^{\sigma_{sc} t  -i \omega_{sc} t} \right],
+\ee  
+where ${\bf u }_m$ is the {\em mean flow} defined by phase-averaging over the cycle, $\tilde{{\bf u }}_1$ is a pseudo-eigenvector which is normalized by the condition  $||\tilde{{\bf u }}_1|| = 1/\sqrt{2}$, $\overline{\tilde{{\bf u }}_1}$ is its complex conjugate,
 $A_{sc}$ is an amplitude parameter directly related to the energy of the oscillating flow, and $\lambda_{sc} = \sigma_{sc} + i \omega_{sc}$ is a pseudo-eigenvalue which depends upon the parameter $A_{sc}$.
@@
 \begin{eqnarray}
-{\cal NS}(  {\color{red}{\bf u }_m }) = \frac{{\cal C}( {\bf u }_{1,c}, {\bf u }_{1,c}) +{\cal C}( {\bf u }_{1,s}, {\bf u }_{1,s})}{{\color{red}4}}, 
+{\cal NS}(  {\bf u }_m ) = \frac{{\cal C}( {\bf u }_{1,c}, {\bf u }_{1,c}) +{\cal C}( {\bf u }_{1,s}, {\bf u }_{1,s})}{4}, 
 \label{HBEq0}
@@
 
-Mathematically, the system (\ref{HBEq0},\ref{HBEq1},\ref{HBEq1b},\ref{HBphase}) for the unknown {\color{red}$[{\bf u }_m, {\bf u }_{1,c}, {\bf u }_{1,s}, \omega]$} is well posed.
+Mathematically, the system (\ref{HBEq0}, \ref{HBEq1}, \ref{HBEq1b}, \ref{HBphase}) for the unknown $[{\bf u }_m, {\bf u }_{1,c}, {\bf u }_{1,s}, \omega]$ is well posed.
 Instead of the double-loop resolution procedure of \cite{MLugo2014}, we propose a direct resolution using a Newton iteration just as explained for the base flow in section 2.
 %To allow resolution, we separate the mode into real and imaginary part, by writing ${\bf u }_1 = {\bf u }_{1,r} +  i {\bf u }_{1,i} $.
-We then assume that we know a {\color{red}``guess'':
+We then assume that we know a ``guess'':
 $$
@@
 $$
-} Injecting and developing up to linear order leads to the following equations:{\color{red}
+Injecting and developing up to linear order leads to the following equations:
+\iffalse
 \begin{subequations}\label{eq:harmonic_total}
@@
 \end{subequations}
-}
+\fi
+
+\begin{subequations}
+
+\begin{align}
+{\cal NS}(  {\bf u }_m^g ) - \frac{1}{4} &\big[ {\cal C}( {\bf u }_{1,c}^g,{\bf u }_{1,c}^g) +  {\cal C}( {\bf u }_{1,s}^g,{\bf u }_{1,s}^g) \big]+ {\cal LNS}_{{\bf u }_m^g}(\delta {\bf u }_m) \nonumber \\
+-\frac{1}{2}& \big[ {\cal C}( {\bf u }_{1,c}^g,\delta {\bf u }_{1,c}) +  {\cal C}( {\bf u }_{1,s}^g,\delta {\bf u }_{1,s}) \big] = 0, \label{HB_1} \\
+{\cal LNS}_{{\bf u }_m^g}( {\bf u }_{1,c}^g)& - \omega^g {\bf u }_{1,s}^g -  {\cal C}( \delta {\bf u }_{m}, {\bf u }_{1,c}^g) \nonumber \\
+&\hspace{-0.9cm}+{\cal LNS}_{{\bf u }_m^g}( \delta {\bf u }_{1,c})  - \omega^g \delta {\bf u }_{1,s}  
+ - \delta \omega {\bf u }_{1,s}^g = 0 , \label{HB_2}\\
+{\cal LNS}_{{\bf u }_m^g}({\bf u }_{1,s}^g)& + \omega^g {\bf u }_{1,c}^g -  {\cal C}( \delta {\bf u }_{m}, {\bf u }_{1,s}^g) \nonumber \\
+&\hspace{-0.9cm}+{\cal LNS}_{{\bf u }_m^g}( \delta {\bf u }_{1,s}) + \omega^g \delta {\bf u }_{1,c} +  \delta \omega {\bf u }_{1,c}^g= 0 , \label{HB_3} \\
+&\hspace{1.65cm} F_y({\bf u }_{1,s}^g) + F_y(\delta {\bf u }_{1,s}) = 0. 
+\end{align}
+\end{subequations}
+
 After discretization, this leads to a linear problem of the form $A X = Y$ where $X$ is the discretized version of the unknowns  $[\delta {\bf u }_m, \delta {\bf u }_{1,c}, \delta {\bf u }_{1,s}, \delta \omega]$, and $A$ is a matrix of dimension $3 N_{dof} +1$, where $N_{dof}$ is the dimension of the Taylor-Hood basis of finite elements describing each of the three $[{\bf u},p]$ fields.
@@
 for the wake of a cylinder in the range $Re \in [47-100] $.
-Note that a "guess" for the mean flow and the self-consistent mode for $Re = 47$, i.e.
+Note that a ``guess" for the mean flow and the self-consistent mode for $Re = 47$, i.e.
 just above the threshold, has already been generated from the weakly nonlinear model at line 4 of the same script.
@@
 
-In the presentation of the numerical methods in sections 2.1 and 2.2, and introduction of the {\em weak form}, we have omitted an important point,; namely the issue of boundary conditions.
+In the presentation of the numerical methods in sections 2.1 and 2.2, and introduction of the {\em weak form}, we have omitted an important point, namely the issue of boundary conditions.
 In this appendix we explain more rigorously how the weak formulation is obtained.
@@
 \label{NSweakFull}
-\forall [{\bf v},q], &&\quad \partial_t \left< {\bf v}, {\bf u}\right> = \left< {\bf v} , {\color{red}{\cal NS} ({\bf u},p)} \right> + \left< q, \nabla \cdot {\bf u}\right>\\
+\forall [{\bf v},q], &&\quad \partial_t \left< {\bf v}, {\bf u}\right> = \left< {\bf v} , {\cal NS} ({\bf u},p) \right> + \left< q, \nabla \cdot {\bf u}\right>\\
 + &&\frac{1}{\epsilon} \left(  \left< {\bf v}, \bf{u} \right>_{\Gamma_{cyl}} + \left< {\bf v}, ({\bf u}- {\bf e}_x ) \right>_{\Gamma_{in}} 
@@
 \forall [{\bf v},q], &&\, \partial_t \left< {\bf v}, {\bf u}\right> = - \left< {\bf v} , {\cal C}({\bf u},{\bf u})/2 \right>
-- 2 Re^{-1} \left< {\bf D}({\bf v}) : {\bf D}({\bf u})  \right>  \nonumber \\
+- 2 Re^{-1} \left< {\mathsf D}({\bf v}) : {\mathsf D}({\bf u})  \right>  \nonumber \\
 + &&\left< \nabla \cdot {\bf v}, p \right> + \left< q, \nabla \cdot {\bf u} \right> \label{NSweakFullN} \\
@@
 The starting point can be taken as the following expansion of the velocity flow field:
- {\color{red}
 \be{WNL2}
@@
 \ee
-}
 Note that compared to the simplified version given in the main text by eq. \ref{WNL1}, the amplitude $A_{wnl}$ depends upon a slow time scale 
@@
 \begin{eqnarray}
-{\color{red} {\cal LNS}_{{\bf u}_{bc}} ({\bf u}_\epsilon) - 2 \nabla \cdot {\bf D}({\bf u}_{bc})} &=&0,
+ {\cal LNS}_{{\bf u}_{bc}} ({\bf u}_\epsilon) - 2 \nabla \cdot {\mathsf D}({\bf u}_{bc}) &=&0,
 \label{eq:LL1} \\
@@
 
-Finally, compatibility conditions, {\color{red}given by the Fredholm's alternative, are imposed at order $\epsilon^3$ to remove the secular terms, leading to an amplitude equation, known as Stuart-Landau equation:
+Finally, compatibility conditions, given by the Fredholm's alternative, are imposed at order $\epsilon^3$ to remove the secular terms, leading to an amplitude equation, known as Stuart-Landau equation:
 \be{WNL3_2}
@@
 \ee
-}
 where coefficients $\Lambda$, $\nu_0$ and $\nu_2$ are given by
-{\color{red}
 \begin{eqnarray}
 \Lambda &=& -\frac{ \left< {\hat{\bf u}}^\dag, 
-\left( {\cal C}({\bf u}_\epsilon, \hat{\bf u}) + 2 \nabla \cdot  {\bf D}( \hat{\bf u}) \right) \right>}
+\left( {\cal C}({\bf u}_\epsilon, \hat{\bf u}) + 2 \nabla \cdot  {\mathsf D}( \hat{\bf u}) \right) \right>}
 {  \left<  \hat{\bf u}^\dag,\hat{\bf u} \right> },\label{LAMBDA}\\
@@
  \end{eqnarray}
-}
 
@@
 \be{normsipp}
-{\color{red}\hat{u}}_y(1,0) = 0.4612.
-\ee
-The advantage of this choice is that the amplitude ${\color{red}|A|}$ is then an approximate measure of the energy of the perturbation: 
-${\color{red}|A|} \approx A_E$. %{\color{red}However the lift phase its not fixed.}
+\hat{u}_y(1,0) = 0.4612.
+\ee
+The advantage of this choice is that the amplitude $|A|$ is then an approximate measure of the energy of the perturbation: 
+$|A| \approx A_E$. %{\color{red}However the lift phase its not fixed.}
 
 %\item 
-Secondly, \cite{FDR2016} proposed the following {\color{red}normalization} choice:
+Secondly, \cite{FDR2016} proposed the following normalization choice:
 \be{normFDR}
@@
 \ee
-This directly leads to ${\color{red}|A|} = A_E$, so this normalisation seems equivalent to the previous one.
+This directly leads to $|A| = A_E$, so this normalisation seems equivalent to the previous one.
 %{\color{red} The lift phase is not specified in \cite{FDR2016} and can be set to nil before the normalization.}
@@
 \mbox{\cite{SippLebedev}} & 9.10988+3.28004i & 9.3996-32.0289i & -0.305116-0.866118i & 36.2307 
-& 5.2848 & - & - & 0.537254
-\\
-\mbox{\cite{FDR2016}} &  9.10988+3.28004i  & (4.88701 -1.66524 i) \times 10^{-3} & (-1.58635 - 4.50309i )\times 10^{-5} &36.2307
-& 5.2848 & - & - & 0.537254
+& 5.2848 & 0.0349973 & -0.536113 & 0.537254
+\\
+\mbox{\cite{FDR2016}} &  9.10988+3.28004i  & (0.488701 -1.66524 i) \times 10^{-3} & (-1.58635 - 4.50309i )\times 10^{-5} &36.2307
+& 5.2848 & 0.537254 & 0 & 0.537254
 \\
@@
 \begin{eqnarray}
-{\cal NS}(  {\bf u }_m ) - A^2 {\cal C}{\color{red}( \tilde{{\bf u }}_1, \overline{\tilde{\bf u }_1})} = 0, 
+{\cal NS}(  {\bf u }_m ) - A^2 {\cal C}( \tilde{{\bf u }}_1, \overline{\tilde{\bf u }_1}) = 0, 
 \label{sis1}
 \\
-(\sigma_{sc} + i \omega_{sc}) {\color{red}\tilde{{\bf u }}_1} =  {\cal LNS}_{{\bf u }_m}( {\color{red} \tilde{{\bf u }}_1} ).
+(\sigma_{sc} + i \omega_{sc}) \tilde{{\bf u }}_1 =  {\cal LNS}_{{\bf u }_m}(\tilde{{\bf u }}_1 ).
 \label{sis2}
@@
 Equation (\ref{sis1}) provides the mean flow field ${\bf u }_m$ while the 
-pseudo-eigenpairs $(\lambda_{sc},{\color{red}  \tilde{{\bf u }}_1})$ can be computed by solving the eigenvalue problem (\ref{sis2}).
+pseudo-eigenpairs $(\lambda_{sc},  \tilde{{\bf u }}_1)$ can be computed by solving the eigenvalue problem (\ref{sis2}).
 \cite{ManticLugo14} Initially proposed a resolution method involving two imbricated loops, which is advantageaously replaced by

### 2018-06-15 99_Documentation/11_StabFem_BasicFunctionalities.tex
Documentation is progressing :)

@@
 
-In this chapter we explain the basic functionalities of StabFem. We recommend that you study the basic example \texttt{EXAMPLE\_Lshape.m}.
+In this chapter we explain the basic functionalities of StabFem. We recommend that you study the basic example \keys{EXAMPLE\_Lshape.m}.
 
-This directory contains three freefem programs and a demo matlab script doing solving tghe following problem :
+This directory contains three freefem programs and a demo matlab script doing solving the following problem :
 
@@
 
-The programs are sufficiently short to be fully given in these pages. See figures \ref{SCRIPT_Lshape.m}, etc...
+The programs are sufficiently short to be fully given in these pages. See figures \ref{SCRIPT_Lshape.m},  \ref{Lshape_Mesh.edp}, \ref{Lshape_Steady.edp}.
 
@@
 
-The results are given
+The results are given in figure \ref{Lshape_Figures}.
 
@@
 \caption{
-Matlab program {\texttt SCRIPT\_Lshape.m})}
+Matlab program \keys{SCRIPT\_Lshape.m})}
 \label{SCRIPT_Lshape.m}
+\end{figure*}
+
+\begin{figure*}[t]
+\includegraphics[width = .45 \linewidth]{../EXAMPLE_Lshape/FIGURES/Lshape_T0.png}
+\includegraphics[width = .45 \linewidth]{../EXAMPLE_Lshape/FIGURES/Lshape_T0_Cut.png}
+\caption{Solution for the steady hrat equation in a L-shape domain : $(a)$ Temperature field $T(x,y)$. 
+$(b)$ Temperature $T(x,0.25)$ along a horizontal line. }
+\label{Lshape_Figures}
 \end{figure*}
@@
 \caption{
-FreeFem++ program {\texttt Lshape\_Mesh.edp})}
+FreeFem++ program \keys{Lshape\_Mesh.edp})}
 \label{Lshape_Mesh.edp}
@@
 \caption{
-FreeFem++ program {\texttt Lshape\_Steady.edf})}
+FreeFem++ program \keys{Lshape\_Steady.edp})}
 \label{Lshape_Mesh.edp}
@@
 
-\begin{figure*}[t]
-\includegraphics[width = .45 \linewidth]{../EXAMPLE_Lshape/FIGURES/Lshape_T0.png}
-\includegraphics[width = .45 \linewidth]{../EXAMPLE_Lshape/FIGURES/Lshape_T0_Cut.png}
-\caption{Solution for the steady hrat equation in a L-shape domain : $(a)$ Temperature field $T(x,y)$. 
-$(b)$ Temperature $T(x,0.25)$ along a horizontal line. }
-\label{Lshape_Mesh.edp}
-\end{figure*}
+\clearpage
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{How does it work ?}
 
-\subsection{Explanation of the \texttt{.ff2m} exchange format}.
+\subsection{Analysis of the example}
+
+Let us observe and explain the most important steps of the example matlab script \keys{SCRIPT\_Lshape.m}.
+
+\begin{itemize}
+\item  The first step is {\bf creating and importing a mesh}. This is done by the function \keys{SF\_Mesh.m} invoked at line 7 of the script. 
+Basically this function does the following operations :
+\begin{enumerate}
+\item Launch the FreeFem++ program \keys{Lshape\_Mesh.edp} with the {\em entry parameter} \footnote{Here and in the sequel, 
+{\em entry parameter} means a value you will be invited to type on the keyboard if using directly FreeFem++ in the way you are used to. Just try !}
+$Ndensity = 40$ (here corresponding to the mesh density).
+\item Import the data produced by the FreeFem++ Macro {\sf SFWriteMesh} (more explanations in paragraph 3.3) 
+\item Return the data as a Matlab {\em structure} object called {\sf ffmesh}
+\end{enumerate}
+
+Execution of this step leads to the following :
+\lstinputlisting[linerange={1-15}]{Lshape_ExecutionExample.txt}
+
+This structure objects has several fields which will serve for plotting data obtained on this mesh. See more in section 2.3.
+
+\item The second step is {\bf launching a FreeFem program using this mesh and importing results}. 
+This is done by the generic driver function \keys{SF\_Launch.m} invoked at line 12 of the script. 
+Basically this function does the following operations :
+\begin{enumerate}
+\item Launch the FreeFem++ program \keys{Lshape\_Steady.edp}  (here with no {\em entry parameter}).
+\item Import the data produced by the FreeFem++. By default the driver will look for a file called \keys{Data.ff2m}. 
+This file is the one created by the FreeFem program in lines 14-22 of the Freefem program \ref{Lshape_Steady.edp}.
+
+Looking inside the file \keys{Data.ff2m}, the header (i.e.  first four lines) is as follows :
+\lstinputlisting[linerange={1-5}]{../EXAMPLE_Lshape/Data.ff2m}, 
+meaning that this files contains a P1 mesh-organised field called 'T'.
+
+\item Return the data as a matlab {\em structure} object called {\sf heatS}.
+\end{enumerate}
+
+Execution of this step leads to the following :
+\lstinputlisting[linerange={17-24}]{Lshape_ExecutionExample.txt}
+
+Where we can see that the structure has field called 'T' (containing the imported data)
+ and a field called 'mesh'  which is actually the mesh object previously constructed and passed to the driver as a parameter as a field.
+
+\item The third step which is important to explain ist {\bf importation of results previously generated by Freefem}. 
+This is done by the generic driver function \keys{importFFdata.m} invoked at line 12 of the script.
+
+Here, besides the file Data.edp previously imported, our program has generated a second data file called \keys{Heat\_1Dcut.ff2m}.
+%This file is the one created by the FreeFem program in lines 14-22 of the Freefem program \ref{Lshape_Steady.edp}.
+The header of this file is as follows :
+\lstinputlisting[linerange={1-5}]{../EXAMPLE_Lshape/Heat_1Dcut.ff2m}, 
+meaning that this files contains two vectors of dimension 101 called X and T.
+
+Execution of this step leads to the following :
+\lstinputlisting[linerange={26-32}]{Lshape_ExecutionExample.txt}
+
+Where we can see that the data is imported as a structure with two fields corresponding to the required data.
+
+\end{itemize}
+
+The \keys{importFFdata.m} functions is the core of the interface, and is actually internally called by the higher-levels drivers \keys{SF\_Mesh.m}  and \keys{SF\_Launch.m}.
+
+%\caption{
+%File \keys{Data.ff2m})}
+%\label{Lshape_Data.ff2m}
+%\end{figure*}
+
+%File \keys{Heat\_1Dcut.ff2m}
+
+%\lstinputlisting[linerange={1-5}]{../EXAMPLE_Lshape/Heat_1Dcut.ff2m}
+
+%\lstinputlisting{../EXAMPLE_Lshape/ExecutionExample}
+
+\subsection{Explanations of the \texttt{.ff2m} exchange format}
+
+As can be seen in the previous short examples, the basis of the FreeFem/Matlab interface relies in the file exchange format \keys{.ff2m}
+and the importation "wizard"  \keys{importFFdata.m} which reads these files.
+
+Let us explain how such files are constituted. As we have observed, the header of a \keys{.ff2m} file has the following structure :
+
+\lstinputlisting{Lshape_FormatExplanation.ff2m}.
+
+The line 4 explains the nature of the data which is contained in the file.
+There can be as many data objects as you want organised in the order of your choice. The recognized types are currently as follows :
+\begin{description}
+\item{ \bf P1}  for mesh-structured data stored as P1 finite-elements
+\footnote{P2 data is not yet supported, the solution is to convert everything to P1 before exportation.}  
+\item{\bf P1c}  for mesh-structured {\em complex} data stored as P1 finite-elements
+\item{\bf real} for real scalars,
+\item{\bf complex} for complex scalars,
+\item{\bf real.N} for real vectors of dimension N not associated to a mesh,
+\item{\bf complex.N} for complex vectors of dimension N not associated to a mesh,
+\item{\bf P1s} for real data defined along a frontier of the mesh,
+\item{\bf P1sc} for complex data defined along a frontier of the mesh.
+\end{description}
+
+\subsection{Explanations about the mesh }
+
+to be continued...

### 2018-06-25 99_Documentation/02_FrontPage.tex

%\title{Documentation \ti{StabFem}}
%\author{Toulouse, IMFT}
%\date{ April 16, 2018}
%\begin{document}
%\maketitle

\newcommand*{\titleGM}{
\thispagestyle{empty}\begingroup % Create the command for including the title page in the document
\hbox{ % Horizontal box
\hspace*{0.2\textwidth} % Whitespace to the left of the title page
\rule{1pt}{\textheight} % Vertical line
\hspace*{0.05\textwidth} % Whitespace between the vertical line and title page text
\parbox[b]{0.75\textwidth}{ % Paragraph box which restricts text to less than the width of the page
\includegraphics[scale=0.5]{imft.jpg}

\vspace{0.5cm} 
{\noindent\Huge\bfseries  \ti{StabFem} Documentation\\}\\[2\baselineskip] % Title
{\large \textit{Manual}}\\[4\baselineskip] % Tagline or further description
{\large \textsc{  }} % Author name
\begin{center}
\includegraphics[scale=0.5]{zoom_finner_mesh_final.png}
\end{center}

\vspace{0.35\textheight} % Whitespace between the title block and the publisher
{\noindent IMFT, v0.2 May 2018  }\\[\baselineskip] 
}}
\endgroup}

 % Sets margins and page size
\pagestyle{empty} % Removes page numbers
\makeatletter % Need for anything that contains an @ command 
\renewcommand{\maketitle} % Redefine maketitle to conserve space
{ \begingroup \vskip 10pt \begin{center} \Huge {\bf \@title}
	\vskip 10pt \large \@author \hskip 20pt \@date \end{center}
  \vskip 10pt \endgroup \setcounter{footnote}{0} }
\makeatother % End of region containing @ commands

%\let\vaccent=\v % rename builtin command \v{} to \vaccent{}

\usepackage{cancel}

 %\pagestyle{myheadings}

 \begin{document}
 \let\cleardoublepage\clearpage
\titleGM

\tableofcontents

\setcounter{page}{1}

### 2018-06-25 99_Documentation/14_StabFem_plotting.tex

% !TEX root = main.tex

\chapter{Plotting data with StabFem}

\section{Plotting with StabFem : \texttt{plotFF.m}}

\section{Native FreeFem plots (ffglut)}

this is enabled/disabled with the MACRO FREEFEMPLOTS

\section{Interfacing with Tecplot}

\texttt{exportFF\_Tecplot.m}

\section{Interfacing with Paraview}

Javier did that ???

\section{Alternative idea}

The problem with plotFF is that is is built upon pdeplot and requires the pdetools toolbox.

An alternative solution would be to adapt the solution of chloros based on patch, which has the advantage of operating under OCTAVE.

See more there :  \verb| https://github.com/samplemaker/freefem_matlab_octave_plot  |

### 2018-06-25 99_Documentation/99_Chapterexample.tex

\section{Chapterexample}

\begin{enumerate}
\item a exmaple item:

  \begin{itemize}[noitemsep]
  \item Record the \emph{ID} and \emph{name} of a student on each line.
  \item Use a comma (\texttt{,}) to separate the ID and name on each line.
  \item Leave an \emph{empty line} between groups.
  \end{itemize}

\item Save file using \texttt{.txt} or \texttt{.csv} extension, e.g.\\\texttt{DIT1234-Apr2013-groups.txt}.

\medskip

\begin{leftbar}
You may also do this You may also do this You may also do this You may also do thisYou may also do thisYou may also do thisYou may also do thisYou may also do this.
\end{leftbar}

\item Launch the Stabfem tool by double-clicking on its icon.
\item From the menu bar, select \menu{File>Import...} or press \keys{Ctrl+I}.
\item Select a \emph{group list file} (\texttt{*.txt, *.csv}) to import from, e.g.\\\texttt{DIT1234-Apr2013-groups.txt}.
\item Stabfem will then ask you for a \emph{new} file name to save the new score list as (\texttt{*.xml}), e.g.~\texttt{DIT1234-Apr2013-Assgn1.xml}.

\medskip

\begin{leftbar}
Make sure the \texttt{.xml} score filename selected does not already exist. Otherwise the existing score file \textbf{may be overwritten without warning}!
\end{leftbar}

\medskip

\item Stabfem imports the group lists and displays the student IDs and names in the main panel (Figure~\ref{fig:grouplist}).

\end{enumerate}

### 2018-06-25 ARTICLE_STABFEM/ARTICLE_ASME_Submitted.tex

@@
 
-\graphicspath{{./}{./FIGURES/}}
+\graphicspath{{./}{../CYLINDER/FIGURES/}}
 
@@
 
-\title{A {practical} review on linear and nonlinear global approaches to stability analysis}
+\title{A practical review on linear and nonlinear global approaches to flow instabilities}
 
@@
 	$^{(a)}$ Institut de Mécanique des fluides de Toulouse (IMFT), University of Toulouse \\
-	$^{(b)}$ Dipartimento do Ingegneria (DIIN), Università di Salerno.
-    }
-
+	$^{(b)}$ Dipartimento do Ingegneria (DIIN), Universit\`a} di Salerno. 
 }
@@
 {\it 
-This paper is aimed to review the linear and nonlinear approaches to study the stability of fluid flows. 
+This paper aims at reviewing the linear and nonlinear approaches to study the stability of fluid flows. 
 We provide a concise but self-contained exposition of the main concepts and specific numerical methods 
@@
 including mesh adaptation, simple shift-invert strategy instead of the classical Arnoldi algorithm, 
-and a simplification of the recent nonlinear self-consistent approach proposed by Manti\v{c}-Lugo et al \cite{MLugo2014}. 
+and a simplification of the recent nonlinear self-consistent approach proposed by Manti\v{c}-Lugo et al (2014). 
 An open-source software implementing all the concepts discussed in the present paper is provided. 
@@
 A bifurcation occurs when a critical value is reached and the original solution becomes linearly unstable, with the system tending towards a new steady or unsteady state.
-%The destabilization of a flow as a parameter is varied, leading from a steady solution to a unsteady one, is an ubiquous situation in fluid dynamics. 
 In the second part of the 19th century, specific analytical and numerical methods able to study these bifurcations have emerged and are continuously evolving up to the present days. 
@@
 a one-dimensional problem.
-On the other hand,  when there are at least two spatial variables, the class of methods suited to solve such problems are generally called ``global stability approaches".
-%When the flow has no analytical expression, the stability problem requires a numerical resolution, and when there are at least two spatial variables, the class of methods suited to solve such problems are generally called "global stability approaches."%\footnote{Sorry Laurette !}
+On the other hand,  when there are at least two spatial variables, the class of methods suited to solve such problems are generally called {\em global stability approaches}.
 A classical example of such behavior in fluid dynamics is the instability occurring in the wake of a circular cylinder.
 At low Reynolds number (precisely for $Re < 46.7$) the flow is steady and symmetric, but for larger values of Re a global instability arises in the flow field leading to the well-known von K\'arm\'an vortex alley.
-%Among all instability problems, one of the most famous and most studied is the flow around a 2D cylinder, which becomes unsteady for $Re \approx 47$ leading to the well-known Bénard-Von Karman vortex alley.
 This flow configuration has served as a benchmark in the development of this class of methods.  
@@
 
-%Among many others, the most noticable milestones are [?] for basic stability analysis,
-%and for adjoint and sensitivity approaches, and for nonlinear approaches.
-
-%Many discretization of spatial derivative operators (finite differences, spectral methods, ...) can be used to build. and is now routinely used by a growing number of teams
-
 The objective of the present work is to contribute to the popularization of such methods 
 in two ways:
-%for both research and education purposes. 
 \begin{itemize}
@@
 \item
-Secondly we offer an open-source and user-friendly software called  ``StabFem"\cprotect\footnote{The StabFem software may be obtained at the following url : 
-\url{https://github.com/erbafdavid/StabFem}} 
+Secondly we offer an open-source and user-friendly software called  {\em StabFem} %\cprotect 
+\footnote{The StabFem software may be obtained at the following url : \\
+\url{https://github.com/erbafdavid/StabFem}
+%{\sf \color{blue} https://github.com/erbafdavid/StabFem}
+} 
 to perform such calculations. The software combines program written in both FreeFem++ and Matlab languages. 
@@
 
-Although we don't claim to invent any radically new method, our exposition and implementation contains a number of originalities making the computation particularly efficient in terms of computational time and memory (all the figures of the paper can be produced in only a few minutes on a standard laptop)\footnote{All the figures contained in the present paper can be processed by launching a single Matlab script SCRIPT\_CYLINDER\_ALLFIGURES.m .
-On a MacbookPro (2018,  2.5Ghz, 16Go Ram),  the execution time is 19.76 seconds for the results of the linear analysis (section 3) and 15.
-seconds for the results of the nonlinear analysis (section 4).
-}. 
+Although we don't claim to invent any radically new method, our exposition and implementation contains a number of originalities making the computation particularly efficient in terms of computational time and memory\footnote{All the figures contained in the present paper can be processed by launching a single Matlab script {\sf SCRIPT\_CYLINDER\_ALLFIGURES.m} .
+On a MacbookPro (2018,  2.5Ghz, 16Go Ram) in single-core sequential execution,  and using mesh ${\mathbf M}_2$ as described in appendix B, the execution time is 203 seconds for the linear analysis (section 3), and 413 seconds for the nonlinear analysis.}.
+% 1868 seconds using mesh M4
 The most notable originalities are the systematic use of mesh adaptation (\S 2 and 3), the use of simple shift-invert instead of Arnoldi (\S 3), and a reformulation and simplification of the nonlinear self-consistent approach of Mantic-Lugo et al  (\S 4).
@@
 $[{\bf v},q]$ associated with the momentum and continuity equations, and integrating over the domain\footnote{In the simple presentation given here we have omitted the issue of boundary conditions.
-Details on way boundary conditions can be incorporated in the weak formulation through integration by parts can be found in appendix A.}
+Details on way boundary conditions can be incorporated in the weak formulation through integration by parts can be found in appendix D.}
 \be{NSweak}
@@
 ${\cal NS} ({\bf u}_b,p_b) = 0$.
-Suppose that we have a ``guess''  for the base flow $[{\bf u}_b^g,p_b^g]$  which almost satisfies the equations.  We look for a better approximation under the form
+Suppose that we have a {\em guess}  for the base flow $[{\bf u}_b^g,p_b^g]$  which almost satisfies the equations.  We look for a better approximation under the form
 \be{Newton1}
@@
 \ee
-Injecting (\ref{Newton1}) into the weak form (\ref{NSweak}) of the Navier-Stokes equations and developing up to linear terms in terms of the perturbation lead to  
+Injecting (\ref{Newton1}) into the weak form (\ref{NSweak}) of the Navier-Stokes equations and linearizing leads to  
 ${\cal NS}  ({\bf u}_b^g,p_b^g) +  {\cal LNS} _{{\bf u}_b^g}(\delta {\bf u}_b,\delta p_b)$, which can also be written in weak form as :
@@
 In our implementation, the algorithm is written in the Freefem++ solver {\em Newton\_2D.edp} 
-which is wrapped by the Matlab driver {\em Freefem\_BaseFlow.m}.
+which is wrapped by the Matlab driver {\sf SF\_BaseFlow.m}.
 
@@
 where ${\mathsf{A}}$ is the matrix resulting from the discretization of ${\cal LNS}_{{\bf u}_b}$, i.e.
-the same matrix  appearing in the Newton computation of the base flow, and  $B$ is a ``weight" matrix associated to the scalar product $\left<v,u\right> = \int \overline{\bf v} \cdot {\bf u} \mbox{ d} \Omega$.
+the same matrix  appearing in the Newton computation of the base flow, and  $B$ is a weight matrix associated to the scalar product $\left<v,u\right> = \int \overline{\bf v} \cdot {\bf u} \mbox{ d} \Omega$.
 
@@
 
-When it comes to the numerical resolution of generalized eigenvalue problems such as $A X = \lambda B X$ (or its adjoint version (\ref{Eigen_Adj_matricial}) ), several methods are possible.
+The numerical resolution of generalized eigenvalue problems such as $A X = \lambda B X$ (or its adjoint version (\ref{Eigen_Adj_matricial}) ), 
+can be performed using several methods.
 Direct methods to compute the whole spectrum are both costly prohibitive and useless.
-A popular alternative is the use of iterative methods which allow us to compute a limited set of eigenvalues located in the vicinity of a
-``shift" value $\lambda_{shift}$. The simplest version of this method is the simple shift-invert iteration, which consists of solving iteratively the system
+A popular alternative is the use of iterative methods to compute a limited set of eigenvalues located in the vicinity of a
+{\em shift} value $\lambda_{shift}$. The simplest version of this method is the simple shift-invert iteration, which consists of solving iteratively the system
 $$
@@
 Our implementation in StabFem allows to chose between single eigenvalue computation (power method) and multiple eigenvalue computation (Arnoldi).
-The selection is made according to the parameter ``nev" transmitted to the driver.
+The selection is made according to the parameter \verb|nev|  (i.e.
+number of requested eigenvalues) transmitted to the driver.
 
@@
 %\vspace{-1.cm}
-\caption{Base flow (axial velocity component) for the flow over a cylinder at $Re=60$.}
+\caption{Base flow (streamwise velocity component) for the flow over a cylinder at $Re=60$.}
 \label{fig:Baseflow}
@@
 \includegraphics[width=.9 \linewidth]{Cylinder_Lx_baseflow.png}
-\includegraphics[width=.9 \linewidth]{Cylinder_Drag_baseflow.png}
+\includegraphics[width=.9 \linewidth]{Cylinder_Fx_baseflow}
 \caption{Recirculation length $L_x$ $(a)$  and nondimensional drag $F_x$ ($b$) of the base flow over a cylinder as function of $Re$.}
@@
 %Following Sipp \& Lebedev,
-The most common procedure is to decompose the domain into several parts with different grid densities; for instance for the wake of a cylinder, we will design a near-wall region with very small  size, a ``wake" region with intermediate mesh size, and an outer region with large mesh size.
+The most common procedure is to decompose the domain into several parts with different grid densities; for instance for the wake of a cylinder, we will design a near-wall region with very small  size, a wake region with intermediate mesh size, and an outer region with large mesh size.
 The inconvenient is that the design relies on an a priori expectation of the regions where gradients will be large.
@@
 This is easily done with FreeFem, as the  AdaptMesh procedure can be used with several objective functions.
-We have experimented two different ideas.
+We have experimented three different ideas.
 The first is to adapt the mesh to the base flow and the structure of the leading eigenmode.
-A second and smarter idea is to adapt the mesh to the base flow and the structural sensitivity.
+The second idea is to use the adjoint mode instead of the direct mode for mesh adaptation.
+The third idea is to adapt the mesh to the base flow and the structural sensitivity.
 This idea is supported by Giannetti \& Luchini\cite{GiannettiLuchini} who showed that the accuracy of the stability results for the flow past a circular cylinder is strictly related to the mesh characteristics in the wavemaker region, i.e.
 the region where the structural sensitivity reaches its maximum values.
-Results show that the two procedures yield the same values for the eigenvalues with less than $1\%$ error, but that the second method gives a mesh with about 3 times less grid points, leading to much faster computations (see appendix D).
+Results show that the three procedures yield the same values for base flow characteristics and eigenvalues with less than $0,3\%$ deviation, but that compared to the two previous ideas mesh adaptation to structural sensitivity result in a mesh with much less grid vertices, leading to much faster computations (see appendix A).
 So, if one is interested only in the eigenvalues, for instance to plot growth rates as function of Reynolds or to identify the critical Reynolds number, mesh adaptation to the sensitivity gives the best option.
@@
 
-In our implementation, the whole process is performed using the Matlab driver {\em Freefem\_AdaptMesh.m} ; the kind of adaptation  (to base flow only, to eigenmode, or to sensitivity) is decided by the choice of parameters transmitted to this function.
+In our implementation, the whole process is performed using the Matlab driver {\em SF\_AdaptMesh.m} ; the kind of adaptation  (to base flow only, to eigenmode, or to sensitivity) is decided by the the nature of the eigenmode object transmitted to this function.
 
@@
 which are the characteristic velocity and length scales used for the definition of Reynolds number $Re= U_{\infty} D / \nu$.
-The origin of the cartesian frame of reference is considered located on the cylinder axis, the x-axis is chosen to be parallel to the incoming free-stream velocity while the y-axis with the cross-stream velocity.
-The dimensions of the computational domain are the following: $-40 \le x/D \le 80$ and $-40 \le y/D \le 40$.
-We impose a no-slip condition $(u=0,v=0)$ on the cylinder surface (${\Gamma_{cil}}$), a uniform velocity $(u=1,v=0)$ at the inflow 
-$x/D=-40$ and a no-stress condition at the outlet $x/D=80$ and on the lateral boundaries of the computational domain $y/D=\pm 40$.
+The origin of the cartesian frame of reference is considered located on the cylinder axis, the x-axis is chosen to be parallel to 
+the incoming free-stream velocity while the y-axis with the cross-stream velocity. 
+The dimensions of the computational domain are the following: $-40 \le x/D \le 80$ and $0 \le y/D \le 40$ (boundary conditions and their implementation are detailed in appendix D).
+Note that we take advantage of the symmetry properties of the problem to use a half-domain for resolution. 
+%We impose a no-slip condition $(u=0,v=0)$ on the cylinder surface (${\Gamma_{cil}}$), a uniform velocity $(u=1,v=0)$ at the inflow 
+%$x/D=-40$ and a no-stress condition at the outlet $x/D=80$ and on the lateral boundaries of the computational domain $y/D=\pm 40$.
 
@@
 F_x = {\cal D}_{Re} ({\bf u},p) \equiv 
- 2 \int_{\Gamma_{cyl}} \left[-p {\bf n} + \frac{2}{Re} {\bf D}({\bf u}) \cdot {\bf n} \right]   \cdot {\bf e_x} d\ell,
+  \int_{\Gamma_{cyl}} \left[-p {\bf n} + \frac{2}{Re} {\mathsf{D}}({\bf u}) \cdot {\bf n} \right]   \cdot {\bf e_x} d\ell,
 \ee
@@
 F_y = {\cal L}_{Re} ({\bf u},p) \equiv
- 2 \int_{\Gamma_{cyl}} \left[-p {\bf n} + \frac{2}{Re} {\bf D}({\bf u}) \cdot {\bf n} \right]   \cdot {\bf e_y} d\ell. 
-\ee
-where $\Gamma_{cyl}$ is the boundary of the cylinder. The factor 2 stands for the fact that our numerical domain is half the physical domain.
+  \int_{\Gamma_{cyl}} \left[-p {\bf n} + \frac{2}{Re} {\mathsf{D}}({\bf u}) \cdot {\bf n} \right]   \cdot {\bf e_y} d\ell. 
+\ee
+where $\Gamma_{cyl}$ is the boundary of the cylinder. %The factor 2 stands for the fact that our numerical domain is half the physical domain.
 
@@
 
-Let's consider now the matlab code reported in figure \ref{Listing2}.
+Let us consider now the matlab code reported in figure \ref{Listing2}.
 First we build an initial mesh (line 1), and compute base flow solutions for increasing values of the Reynolds number up to $Re = 60$ (lines 3-9).
-Then we perform the mesh adaptation with the structural sensitivity, as explained in a previously (line 13). 
-The resulting mesh, depicted in figure \ref{fig:mesh2}, is used for the rest of the computations presented in this paper (except for displaying the eigenmode in figure 4$a$). 
-Appendix D presents additional test regarding mesh convergence, and demonstrate that results obtained with the resulting mesh are trustable within $0.1\%$ accuracy for the eigenvalue, while requiring a very reasonable number of grid points compared to previous studies of this problem.
+Then we perform the mesh adaptation with the structural sensitivity, as explained previously (line 13). 
+The resulting mesh, depicted in figure \ref{fig:mesh2}, is used for the rest of the computations presented in this paper (except for computing
+the energy of the nonlinear perturbation displayed in figure \ref{fig:HB_SC_DATA_COMP}$(d)$ which requires a heavier mesh). 
+Appendix A presents additional test regarding mesh convergence, and demonstrate that results obtained with the resulting mesh are trustable within $0.3\%$ accuracy for the eigenvalue.
+It must be emphasized  that the mesh generated through this adaptation process is very light, with only 2048 vertices, which is significantly less than reported in previous work (for instance, in their mesh convergence studies, \cite{SippLebedev} and \cite{MLugo2014} used respectively 190868  and 6731 vertices).
 
@@
 Figure \ref{Listing2} shows how to compute and plot with StabFem the two most commonly studied quantities, namely the recirculation length $Lx(Re)$, i.e.
-the location of the stagnation point at the rear of the recirculation region, and the drag coefficient $C_x(Re)$.
-Note that the object \verb|bf| is defined as a structure with fields \verb|Drag| and \verb|Lx|. 
+the location of the stagnation point at the rear of the recirculation region, and the drag force $F_x(Re)$.
+Note that the object \verb|bf| is defined as a structure with fields \verb|Fx| and \verb|Lx|. 
 The resulting plots are given in figure \ref{fig:LxandDrag}, and are in good agreement with known results for this classical problem.
@@
 
+ In this part, to simplify the notations, we symbolically write the Navier-Stokes equations as $\partial_t {\bf u} = {\cal NS} ({\bf u})$, therefore dropping the systematic reference to the incompressibility constraint and associated pressure field.
+The same is done with the linearized operator ${\cal LNS}_{{\bf U}}( {\bf u})$.
+
 \subsection{General definitions in the nonlinear regime}
 
-In the nonlinear regime, the {\em base flow} introduced in the linear theory is not directly accessible and no longer relevant, especially when the oscillation amplitudes become large. 
+In the nonlinear regime, the {\em base flow} introduced in the linear theory is no longer relevant, especially when the oscillation amplitudes become large. 
 Instead, one may define a {\em mean flow} by time-averaging : 
@@
 
- In this part, to simplify the notations, we symbolically write the Navier-Stokes equations, as $\partial_t {\bf u} = {\cal NS} ({\bf u})$, therefore dropping the systematic reference to the incompressibility constraint and associated pressure field.
-The same is done with the linearized operator ${\cal LNS}_{{\bf U}}( {\bf u})$.
-
 %MThe mean drag is given by
@@
 
-\paragraph{WNL model: analysis}
+%\paragraph{Analysis}
 
@@
 In the first-order term, $\hat{\bf u}$ is the neutral eigenmode at $Re_c$ conveniently normalized (see discussion in appendix B), 
-$A_{wnl}$ an amplitude, $\omega_c$ the frequency predicted by the linear approach at $Re=Re_c$ and $\omega_\epsilon$ a small deviation of the frequency.
+$A_{wnl}$ an amplitude which can be assumed as real, $\omega_c$ the frequency predicted by the linear approach at $Re=Re_c$ and $\omega_\epsilon$ a small deviation of the frequency.
 
@@
 At ${\cal O}( \epsilon ^3)$, compatibility conditions have to be imposed to ensure that the problem is correctly posed.
-These conditions lead to an ``amplitude equation" which relates the amplitude $ A_{wnl}$ to three parameters $\Lambda, \nu_{0}$ and $\nu_{2}$ which depend
+These conditions lead to an {\em amplitude equation} which relates the amplitude $ A_{wnl}$ to three parameters $\Lambda, \nu_{0}$ and $\nu_{2}$ which depend
 uniquely on ${\bf u}_\epsilon$, ${\bf u}_{2,0}$ and ${\bf u}_{2,2}$, respectively (see equations \ref{LAMBDA}, \ref{NU0} and \ref{NU2} in appendix B).
-Restricting to the description of the limit cycle, the ``amplitude equation" takes the form :
+Restricting to the description of the limit cycle, the {\em amplitude equation} takes the form :
 
@@
 $
-|A_{wnl}|= \sqrt{ \frac{\Lambda_r}{\nu_{0,r}+\nu_{2,r}}}
+A_{wnl}= \sqrt{ \frac{\Lambda_r}{\nu_{0,r}+\nu_{2,r}}}
 $ and
@@
 where the subscripts $r$ and $i$ represent the real and imaginary parts.
-Reintroducing the scaling, the  amplitude $|A| =  \epsilon |A_{wnl}| $ and the frequency $\omega$ of the limit cycle are thus predicted as
+Reintroducing the scaling, the  amplitude $A =  \epsilon A_{wnl} $ and the frequency $\omega$ of the limit cycle are thus predicted as
 \be{ANL} 
-|A| =  \epsilon |A_{wnl}| =\sqrt{ \frac{\Lambda_r}{\nu_{0,r}+\nu_{2,r} }} \sqrt{\frac{1}{Re_c}-\frac{1}{Re}},
+A =  \epsilon A_{wnl} =\sqrt{ \frac{\Lambda_r}{\nu_{0,r}+\nu_{2,r} }} \sqrt{\frac{1}{Re_c}-\frac{1}{Re}},
 \ee
@@
 & F_{x0,\epsilon} = {\cal D}_{Re_c} ({\bf u}_\epsilon, p_\epsilon ) - {\cal D}_{1} ({\bf u}_{bc},0) 
-+ | A_{wnl} |^2 {\cal D}_{Re_c} ({\bf u}_{2,0},p_{2,0}). 
++ A_{wnl}^2 {\cal D}_{Re_c} ({\bf u}_{2,0},p_{2,0}). 
 \end{aligned}
@@
 \be{lift_cos}
-F_{y,1,c} - i F_{y,1,s} = 2 |A_{wnl}| {\cal{L}}_{Re_c}( {\bf \hat{u}},\hat{p} ) \sqrt{\frac{1}{Re_c}-\frac{1}{Re}}.
+F_{y,1,c} - i F_{y,1,s} = 2 A_{wnl} {\cal{L}}_{Re_c}( {\bf \hat{u}},\hat{p} ) \sqrt{\frac{1}{Re_c}-\frac{1}{Re}}.
 %|A|_i F_{x,i}({\bf \hat{u}})\sin(\omega t) \big),\\
@@
 
-\paragraph{WNL model : implementation and results for the cylinder}
+\paragraph{Implementation and results for the cylinder}
 
 Lines 1-8 of the script shown in figure \ref{fig:listingNL}, which is extracted from the script 
-\verb|SCRIPT_CYLINDER_ALLFIGURES.m|, illustrate the sequence of commands to 
+{\sf SCRIPT\_CYLINDER\_ALLFIGURES.m}, illustrate the sequence of commands to 
 perform the weakly nonlinear study for the cylinder wake.
@@
 \includegraphics[width=.9 \linewidth]{Cylinder_Cy_Re_SC.png}
-\includegraphics[width=.9 \linewidth]{Cylinder_Energy_Re_SC.png}
+\includegraphics[width=.9 \linewidth]{Cylinder_Energy_Re_SC_AdaptD.png}
 \includegraphics[width=.9 \linewidth]{Cylinder_Lx_Re_HB.png}
@@
 \ee  
-where ${\bf u }_m$ is the {\em mean flow} defined by phase-averaging over the cycle, $\tilde{{\bf u }}_1$ is a pseudo-eigenvector which is normalized by the condition  $||\tilde{{\bf u }}_1|| = 1/\sqrt{2}$, $\overline{\tilde{{\bf u }}_1}$ is its complex conjugate,
+where ${\bf u }_m$ is the {\em mean flow} as previously defined,  $\tilde{{\bf u }}_1$ is a pseudo-eigenvector which is normalized by the condition  $||\tilde{{\bf u }}_1|| = 1/\sqrt{2}$, $\overline{\tilde{{\bf u }}_1}$ is its complex conjugate,
 $A_{sc}$ is an amplitude parameter directly related to the energy of the oscillating flow, and $\lambda_{sc} = \sigma_{sc} + i \omega_{sc}$ is a pseudo-eigenvalue which depends upon the parameter $A_{sc}$.
 
-The original version of the model (discussed with some more details in appendix C) allowed to obtain an amplitude equation relating the instantaneous growth rate $\sigma$ as function of the amplitude $A_{sc}$.
+The original version of the model (discussed with some more details in appendix C) allowed to obtain an amplitude equation predicting the instantaneous growth rate $\sigma$ as function of the amplitude $A_{sc}$.
 However, if we are simply interested in the properties of the limit cycle, not the transient, we may recast the self-consistent model in a simpler way.
@@
 \ee
-where ${\bf u }_{1,c}$ and ${\bf u }_{1,s}$ are two {\em real} fields describing the cycle at two instants separated by a quater-period of oscillation, and $\omega$ is the (real) oscillation frequency of the limit cycle (which is not known a priori).
+where ${\bf u }_{1,c}$ and ${\bf u }_{1,s}$ are two {\em real} fields describing the nonlinear perturbation at two instants separated by a quarter-period of oscillation, and $\omega$ is the (real) oscillation frequency of the limit cycle (which is not known a priori).
 The connection with the definition of Manti\v{c}-Lugo is as follows :
@@
 
-To allow resolution we need an extra equation to fix the {\em phase} of the cycle.
+Note that this system of equations contains three unknown fields (discretized on the Taylor-Hood basis) plus an extra scalar unknown, 
+namely the frequency $\omega$. 
+In order to solve this coupled problem, we thus need an extra scalar equation.
+The latter is provided by fixing {\em phase} of the cycle.
 Several choices are possible, but a convenient one is to decide that the instant $t=0$ corresponds to a maximum of the lift force.
@@
 \be{HBphase}
-{\cal L}_{Re}({\bf u}_{1s}) =0.
+{\cal L}_{Re}({\bf u}_{1s},p_{1s}) =0, 
+\ee
+so that the Fourier decomposition of the lift force \ref{drag_lift_def} will contain only a cosine term, namely 
+\be{FySC}
+F_y \approx F_{y,1,c} \cos \omega t, \quad \mbox{ with } \quad F_{y,1,c} = {\cal L}_{Re}({\bf u}_{1c},p_{1c}).
 \ee
@@
 %To allow resolution, we separate the mode into real and imaginary part, by writing ${\bf u }_1 = {\bf u }_{1,r} +  i {\bf u }_{1,i} $.
-We then assume that we know a ``guess'':
+We then assume that we know a {\em guess}:
 $$
@@
 This system is solved iteratively in the same way as explained in section 2.1 for determination of the base flow.
-Using the adapted mesh described in figure 2, the dimension of the system
-is $3 N_{dof} +1 \approx 58 000$ and the resolution remains possible at very reasonable computational costs.
-
-Lines 10-17 of the script shown in figure \label{fig:listingNL}  explain how to solve SC model using the StabFem software, 
+%Using the adapted mesh described in figure 2, the dimension of the system is $3 N_{dof} +1 \approx 58 000$ and the resolution remains possible at very reasonable computational costs.
+Mesh convergence issues for the nonlinear calculations are discussed in appendix A.
+It is shown that the mesh $\mathbf{M}_2$ adapted to {\em structural sensitivity} is sufficient to yield converged results within $0.3\%$ accuracy for all quantities considered here, with the exception of the energy-amplitude $A_E$ which requires the more refined mesh $\mathbf{M}_4$ obtained by adaptation to the structure of direct eigenmode.\footnote{In terms of computational cost, on a standard laptop the program  \ref{fig:listingNL} requires approximatively 413 seconds using  mesh $\mathbf{M}_2$ and 31 minutes using mesh $\mathbf{M}_4$.}
+
+Lines 10-17 of the script shown in figure \ref{fig:listingNL}  explain how to solve SC model using the StabFem software, 
 for the wake of a cylinder in the range $Re \in [47-100] $.
-Note that a ``guess" for the mean flow and the self-consistent mode for $Re = 47$, i.e.
+Note that a {\em guess} for the mean flow and the self-consistent mode for $Re = 47$, i.e.
 just above the threshold, has already been generated from the weakly nonlinear model at line 4 of the same script.
@@
 \end{center}
-\caption{Self-consistent approach for the wake of a circular cylinder:  description of the MEAN FLOW for  $Re = 
-100$.}
+\caption{Structure of the {\em mean flow} over a cylinder for $Re = 
+60$, as computed by the Self-Consistent model (streamwise velocity component).}
 \label{fig:MF60}
@@
 
-Fgure \ref{fig:MF60} illustrates the structure of the mean flow for $Re=60$.
+Figure \ref{fig:MF60} illustrates the structure of the mean flow for $Re=60$.
 As already identified by  \cite{MLugo2014}, the recirculation region associated with this mean flow is notably shorter than the one associated with the base flow (figure 2).
@@
 The other figures are processed in a similar way.
-The entire set of commands to obtain all figures is provided in the script {\em SCRIPT\_CYLINDER\_ALLFIGURES.m} .}.
+The entire set of commands to obtain all figures is provided in the script {\sf SCRIPT\_CYLINDER\_ALLFIGURES.m} .}.
 Concerning the quantities $St$, $A_E$ and $L_x$, differences between SC, WNL models have already been commented in  \cite{MLugo2014} and \cite{FDR2016}.
@@
 \item Incompressible flows around 2D objects, either fixed or in movement such as the case of a spring-mounted cylinder \cite{Navrose},
-\item Incompressible flows in axisymmetric geometries such as the wake of spheres and disks \cite{Tchoufag16} and the flow through apertures \cite{FabreASME}, 
-\item Compressible flow around 2D objects  \cite{Fani18}, 
-\item Oscillations of hanging drops and liquid bridges \cite{Chireux}
+\item Incompressible flows in axisymmetric geometries such as the wake of spheres and disks \cite{Tchoufag2015} and the flow through apertures \cite{FabreISMA}, 
+\item Compressible flow around 2D objects  \cite{Fani2018}, 
+\item Oscillations of hanging drops and liquid bridges \cite{Chireux2015}
 \end{itemize}
@@
 \appendix
-
-\section{Details of the weak formulation}
-
-In the presentation of the numerical methods in sections 2.1 and 2.2, and introduction of the {\em weak form}, we have omitted an important point, namely the issue of boundary conditions.
-In this appendix we explain more rigorously how the weak formulation is obtained.
-We consider here the full time-dependent nonlinear Navier-Stokes equations, but the treatment of the base-flow equations and the linearised equations is essentially the same.
-
-Noting $\Gamma$ the boundary of the numerical domain, the latter can be decomposed in five parts : 
-$\Gamma = \Gamma_{in} \cup \Gamma_{cyl} \cup \Gamma_{axis} \cup \Gamma_{out} \cup \Gamma_{lat}$. 
-Noting $\sigma = 2 Re^{-1} {\bf D}({\bf u}) - p {\bf 1}$ the stress tensor, the relevant boundary conditions are as follows:
-\begin{itemize}
-\item On $\Gamma_{in}$ (inlet): ${\bf u} = {\bf e}_x$ (Dirichlet).
-\item On $\Gamma_{cyl}$ (surface of the cylinder): ${\bf u} = {\bf 0}$ (Dirichlet).
-\item On $\Gamma_{out}$ (outlet): $\sigma \cdot {\bf n} = {\bf 0}$ (Neumann). 
-\item On $\Gamma_{axis}$ (symmetry plane): $u_y = 0$ and $\sigma_{xy} = 0$ (Mixed). 
-\item On $\Gamma_{lat}$ (lateral boundary): $u_y = 0$ and $\sigma_{xy} = 0$ (Mixed). 
-\end{itemize}
-We will introduce the following notation for integrals along any portion of the boundary $\Gamma_i$ of the product of two quantities $\phi_1, \phi_2$ (either scalar or vectorial) :
-%$\left< \phi_1, \phi_2 \right>_{\Gamma_i} $:
-$$
-\left< \phi_1, \phi_2 \right>_{\Gamma_i} = \int_{\Gamma_i}  \overline{\phi}_1 \cdot \phi_2   \mbox{ d} \ell,
-$$
-Instead of the simplified version \ref{NSweak}, the more precise form of the weak formulation can be first written as follows:
-\begin{eqnarray}
-\label{NSweakFull}
-\forall [{\bf v},q], &&\quad \partial_t \left< {\bf v}, {\bf u}\right> = \left< {\bf v} , {\cal NS} ({\bf u},p) \right> + \left< q, \nabla \cdot {\bf u}\right>\\
-+ &&\frac{1}{\epsilon} \left(  \left< {\bf v}, \bf{u} \right>_{\Gamma_{cyl}} + \left< {\bf v}, ({\bf u}- {\bf e}_x ) \right>_{\Gamma_{in}} 
-+ \left< v_y, u_y\right>_{\Gamma_{axis}\cup \Gamma_{lat}} \right) \nonumber \\
-+ && \left< {\bf v}, \sigma \cdot {\bf n} \right>_{\Gamma_{out} \cup  \Gamma_{lat} \cup \Gamma_{axis} }  \nonumber 
-\end{eqnarray}
-where $\epsilon=10^{-30}$ is a small parameter used to impose the Dirichlet boundary conditions by penalization.
-An integration by parts of the pressure gradient and viscous stress terms of the Navier-Stokes equation eventually 
-leads to the weak form effectively used in the programs {\em Newton2D.edp} and {\em Stab2D.edp}:
-\begin{eqnarray}
-\forall [{\bf v},q], &&\, \partial_t \left< {\bf v}, {\bf u}\right> = - \left< {\bf v} , {\cal C}({\bf u},{\bf u})/2 \right>
-- 2 Re^{-1} \left< {\mathsf D}({\bf v}) : {\mathsf D}({\bf u})  \right>  \nonumber \\
-+ &&\left< \nabla \cdot {\bf v}, p \right> + \left< q, \nabla \cdot {\bf u} \right> \label{NSweakFullN} \\
-+ &&\frac{1}{\epsilon} \left(  \left< {\bf v}, \bf{u} \right>_{\Gamma_{cyl}} + \left< {\bf v}, ({\bf u}- {\bf e}_x ) \right>_{\Gamma_{in}} 
-+ \left< v_y, u_y\right>_{\Gamma_{axis}\cup \Gamma_{lat}} \right) \nonumber 
-\end{eqnarray}
-Note that the Neumann boundary conditions do not appear any more thanks to the integration by parts.
 
@@
 
+\section{Mesh convergence : efficiency of mesh adaptation and effect of domain size}
+\begin{figure}
+%\vspace{-.5cm}\vspace{-.5cm}
+\includegraphics[width = .9\linewidth]{Cylinder_Mesh2_Full.png}
+%\vspace{-.5cm}\vspace{-.5cm}
+\includegraphics[width = .9\linewidth]{Cylinder_Mesh2.png}
+\caption{Illustration of the stucture of mesh  $\mathbf{M}_2$ (adapted to both the base flow and structural sensitivity).}
+\label{fig:mesh2}
+\end{figure}
+
+\begin{figure}
+%\vspace{-.5cm}\vspace{-.5cm}
+\includegraphics[width = .9\linewidth]{Cylinder_Mesh4_Full.png}
+%\vspace{-.5cm}\vspace{-.5cm}
+\includegraphics[width = .9\linewidth]{Cylinder_Mesh4.png}
+\caption{Illustration of the stucture of mesh  $\mathbf{M}_4$ (adapted to both the base flow and direct eigenmode).}
+\label{fig:mesh4}
+\end{figure}
+
+\begin{table*}
+$$
+\begin{array}{|c||c|c|c|c|c|c|c|c|c|}
+\hline
+\mbox{Mesh} & N_p & N_{dof} & \delta_{min} & \delta_{max} & \delta_A  & \delta_B  & \delta_C  & \delta_D  \\
+\hline
+\mathbf{M}_1 \mbox{(Adapt on base flow) } & 1429 & 12545	& 0.0131 & 14.33 		& 0.0259 	& 0.514 	& 0.819 	& 1.067 \\   
+\mathbf{M}_2 \mbox{(Adapt on sensitivity) } & 2038 & 17885	& 0.0155 & 14.17 		& 0.02826 & 0.2046 	& 0.3909 	& 1.2014 	\\
+\mathbf{M}_3 \mbox{(Adapt on sensitivity, split) } & 7974 & 70651	& 0.00786 & 7.131  		& 0.0104 	& 0.0744 	&   0.0975 & 0.614   \\
+\mathbf{M}_4 \mbox{(Adapt on mode) } 	& 12080  & 103564		&0.00825	& 124.61		& 0.0229	& 0.143	& 0.0993	& 0.0934 \\
+\mathbf{M}_5 \mbox{(Adapt on adjoint) } 	& 3813 	& 33715		& 0.0108	& 13.95		& 0.0176 	& 0.114	& 0.127	& 1.177  \\
+\hline
+\end{array}
+$$
+\caption{Description of meshes used for validation of mesh adaptation strategy : number of vertices $N_p$ ; number of degrees of freedom of the P2-P2-P1 Taylor-hood basis $N_{dof}$ ; cell size (minimum and maximum value, and value at four characteristic point A,B,C,D as defined in the text).
+ }
+\label{tab:conv1}
+\end{table*}
+
+Fx = 0.6447; Lx = 4.0736
+\begin{table*}
+$$
+\begin{array}{|c||c|c||c||c|c||c|c|c|}
+\hline
+\mbox{Mesh} & L_x & F_x & \lambda & L_{x,SC} & F_{x,SC} & \omega_{SC}  & F_{y,1,c} & A_{E} \\
+\hline
+\mathbf{M}_1 & 4.0733 & 0.64310	& 0.047056 + 0.74416i 		& 2.6073  & 0.69277 	&  0.84334 & 0.1298 & 1.8301  \\
+\mathbf{M}_2 & 4.075 &.  0.64348  	& 0.046719 + 0.74489i 		& 2.6153  & 0.69246 	& 0.84351 & 0.12789 & 1.7134 \\  
+\mathbf{M}_3 & 4.0772 & 0.64391 	& 0.04684. +  0.74511i 		& 2.6141  & 0.69338 	& 0.84383 & 0.12799 & 2.048   \\ 
+\mathbf{M}_4 & 4.0748 & 0.64402 	& 0.04676  + 0.74502i 		& 2.6130 	& 0.69034 	& 0.84371 & 0.12809 & 2.5905 \\
+\mathbf{M}_5 & 4.0736 & 0.64470	& 0.046782+0.74534i		& 2.6142 	& 0.69399		& 0.84390 & 0.12800 & 1.8234 \\
+\hline
+\end{array}
+$$
+\caption{Results for mesh adaptation strategy ($Re = 60$) : Base-flow characteristics $L_x$ and $F_x$, linear eigenvalue $\lambda$, 
+Nonlinear self-consistent model characteristics  $\omega_{SC}$, $F_{y,1,c}$ and $A_E$. All the results can be optained using the matlab program
+{\sf SCRIPT\_CYLINDER\_MESHCONVERGENCE.m}. }
+\label{tab:conv2}
+\end{table*}
+
+This appendix presents complementary results obtained using various mesh designs. 
+All the results can be obtained using the following program available on the StabFem website : 
+{\sf SCRIPT\_CYLINDER\_MESHCONVERGENCE.m}.
+
+\subsection{Efficiency of the mesh adaptation process}
+
+As discussed in section 3, the mesh adaptation proves to be an extremely efficient way to obtain significant results 
+with very reasonable meshes. The objective of this paragraph is to demonstrate this point by comparing the efficiency of several ways to perform mesh adaptation.
+
+For this purpose, 5 meshes were generated. 
+Mesh $\mathbf{M}_1$ was adapted on the {\em base flow} obtained for $Re=60$.
+Mesh $\mathbf{M}_2$ was adapted to both the base flow and structural sensitivity.
+Mesh $\mathbf{M}_3$ was obtained by a subsequent refinement of mesh $\mathbf{M}_2$, splitting all triangles in four subtriangles, therefore doubling the effective density of the mesh.
+Meshes $\mathbf{M}_4$ and $\mathbf{M}_5$ were obtained by adapting to the structure of the direct eigenmode and of the adjoint eigenmode.
+In each case, the adaptmesh process was repeated twice in order to ensure a correct convergence.
+
+Figures \ref{fig:mesh2} and \ref{fig:mesh4} illustrate the structure of meshes $\mathbf{M}_2$ and $\mathbf{M}_4$.
+As can be observed, these two mesh adaptation strategies lead to meshes with comparable densities in the region close to the cylinder.
+On the other hand, when moving downwards in the wake, mesh $\mathbf{M}_2$ quickly gets rather coarse, while mesh $\mathbf{M}_4$ maintains a significant density
+
+Table \ref{tab:conv1} gives numerical informations about the geometry of these meshes.
+In particular, we document the minimum and maximum cell size, as well as the cell size at four point A,B,C,D defined with by their coordinates as follows : $(x_A,y_A) = (0,0.5)$ (within the boundary layer at the cylinder wall); $(x_B,y_B) = (2.5,0.5)$ (in the region of maximum structural sensitivity); $(x_C,y_C) = (4,0)$ (in the near wake); $(x_D,y_D) = (10,0)$ (in the far wake).
+Results confirm that mesh all meshes have similar densities in the near wake (cell size at points A,B,C are comparable)
+while $\mathbf{M}_4$ has maximum resolution in the far wake (in the vicinity of point D).
+
+Table  \ref{tab:conv2} compares the results obtained with the five meshes.
+For base-flow characteristics $L_x$ and $F_x$, all values agree with a relative dispersion of less than $0.15\%$, confiming that all adaptation stategies are successful to correctly compute the base flow.
+The performances of meshes for linear stability calculations can then be evaluated by comparing the eigenvalues.
+Meshes $\mathbf{M}_2$ to $\mathbf{M}_5$ all give values within less than $0.1\%$ dispersion.
+The value obtained with mesh  $\mathbf{M}_1$, which is not adapted to the eigenmode, is a bit farther from the others but still rather good.
+The table also displays results allowing to compare the performances of meshes for nonlinear self-consistent calculations.
+As for the frequency and the maximum lift, meshes $\mathbf{M}_2$ to $\mathbf{M}_5$ again give almost identical values within less than $0.1\%$ dispersion.
+The dispersion is much larger concerning the energy-amplitude of the perturbation $A_E$ displayed in the last column.
+Only the mesh $\mathbf{M}_4$ is able to correctly compute this quantities, while all other meshes significantly underestimate it.
+This is not surprising since this quantity is an integral one which depends upon the structure of the nonlinear perturbation in the whole wake, not only the near-wake region.
+
+From this study we can conclude that if we are only interested in predicting the frequency of the mode and the forces exerted on the cylinder (in both linear and nonlinear regimes), the strategy of mesh adaptation to both base flow and structural sensitivity (mesh $\mathbf{M}_2$) is the most efficient and leads to a very light mesh (here only 2048 vertices).
+On the other hand, if we are interested in describing the structure of the perturbation in the whole domain (and being able to correctly evaluate its energy), mesh adaptation to the eigenmode structure is preferable.
+However this second strategy produces a much heavier mesh (here 12080 point).
+
+ \begin{table*}
+$$
+\begin{array}{|c|c||c|c||c||c|c||c|c|}
+\hline
+\mbox{Mesh} & N & L_x & F_x & \lambda & L_{x,SC} & F_{x,SC} & \omega_{SC}  & F_{Y,SC} \\%& A_{E,SC} \\
+\hline
+%\mathbf{M}_2 \mbox{(ref)} 	& 7974  	& 4.0772 & 0.64391 	& 0.04684. +  0.74511i 	& 2.6141  & 0.69338 	& 0.84383 & 0.12799 & 2.048   \\ 
+\mathbf{M}_6 [-20,40]x[0,20] 			& 1954	&  4.1097 & 0.65048 	& 0.048335+0.74989i 	& 2.6014  & 0.69988 & 0.85032 & 0.13219 \\%& 1.7019   \\ 
+\mathbf{M}_7 [-80,160]x[0,80] 			& 2292	& 4.0618 & 0.64046		& 0.046081+0.74286i 	& 2.6188 	& 0.68924 	& 0.84042 & 0.12631 \\%& 1.6892 \\
+\mathbf{M}_8 \mbox{("slip" conditions)}	 & 2026	& 4.0701 &0.64590		& 0.047017+0.74790i	& 2.6127 	& 0.69492		& 0.84613 & 0.12836 \\%& 1.7154 \\
+\mathbf{M}_9 \mbox{("inlet" conditions)}	 & 2043	& 4.0677 &0.64	557	& 0.047077+0.74781i	& 2.6152 	& 0.69429		& 0.84562  & 0.12771 \\%1.7004 \\
+\hline
+\end{array}
+$$
+\caption{Comparison of the performances of several meshes with variable dimensions and different boundary conditions}
+\label{tab:conv3}
+\end{table*}
+
+\subsection{Effect of domain size and boundary conditions}
+
+As already identified in several previous studies, the size of the domain and the type of boundary conditions applied at the boundaries have a notable impact on the results.
+To illustrate this, we designed four additional meshes.
+All were obtained through adaptation to base flow and sensitivity, just as mesh $\mathbf{M}_2$.
+Meshes $\mathbf{M}_6$ and $\mathbf{M}_7$ are respectively twice smaller and twice larger than the reference one. 
+Meshes $\mathbf{M}_8$ and $\mathbf{M}_9$ have the same dimension but the boundary condition at the lateral boundary
+ $\Gamma_{lat}$ differs.
+Unlike the reference case $\mathbf{M}_2$ which uses a no-stress boundary condition (identical to that applied at the outlet), mesh $\mathbf{M}_8$ uses a "slip" condition $u_y = 0 ; \partial u_x/\partial y = 0$ while mesh $\mathbf{M}_9$ uses an even more restrictive constant-flow condition (the condition at the lateral boundary is $u_x = 1, u_y = 0$, just as for the inlet).
+
+Even though the domain size of the reference case (namely $[-40,80]\times[0,40]$) may appear large, the table shows that confinement effects are still present.
+The quantity which appears the most sensible to domain size and/or boundary conditions is the imaginary part of the linear eigenvalue.
+Interestingly, the nonlinear SC results appears to be more robust with respect to confinement effects than linear ones.
+In effect, values for nonlinear frequency $\omega_{SC}$ and the maximum lift $F_{y,1,c}$ obtained with meshes  $\mathbf{M}_2$, $\mathbf{M}_7$ $\mathbf{M}_8$ and $\mathbf{M}_9$ agree with less than $0.3\%$ dispersion.
+
 \section{Additional details of the weakly nonlinear approach}
@@
 
-A key issue in the weakly nonlinear expansion is that the definition of the amplitude depends upon a normalization choice of the eigenmodes.
-Several choices are possible.
-In the literature three possibilities have been used:
-%\begin{itemize}
-%\item
-
-First, \cite{SippLebedev} normalized the eigenmode by assuming a specified value to the $y$-component of the velocity at one point, namely:
-\be{normsipp}
-\hat{u}_y(1,0) = 0.4612.
-\ee
-The advantage of this choice is that the amplitude $|A|$ is then an approximate measure of the energy of the perturbation: 
-$|A| \approx A_E$. %{\color{red}However the lift phase its not fixed.}
-
-%\item 
-Secondly, \cite{FDR2016} proposed the following normalization choice:
-\be{normFDR}
-\int_\Omega |\hat{\bf u}|^2 d {\bf x}  = \frac{1}{2}.
-\ee
-This directly leads to $|A| = A_E$, so this normalisation seems equivalent to the previous one.
-%{\color{red} The lift phase is not specified in \cite{FDR2016} and can be set to nil before the normalization.}
-
-%\item 
-Thirdly, following \cite{Fabre2012}, another convenient choice is to normalize the eigenmode with its lift 
-force: 
-\be{normfabre}
-{{\cal D}_{Re_c}(\hat{\bf u},\hat{p}) }=\frac{1}{2}.
-\ee
-The advantage of this choice is that the amplitude $|A|$ is then an direct measure of the fundamental lift.
-In effect, eq. \ref{lift_cos} directlty leads to $F_{y,1,c} = |A|$, $F_{y,1,s} = 0$.
-
-In our implementation of the WNL approach, we allowed to choose the normalization convention, as seen in line 3 of figure \ref{fig:listingNL}.
-%%ATTENTION, si figure est actualisé, il faut actualiser la ligne
-In table \ref{tab:WNL_coefs} we give the predictions of the WNL approach using the three normalization choices.
-We can note that the coefficients $\nu_0$ and $\nu_2$ strongly depend on the normalization choice.
-On the other hand, the frequency deviation $\omega_\epsilon$ and the $\lambda$ coefficient, and the term $F_{x,0,\epsilon}$ related to the dependency of mean drag with deviation from the threshold are independent upon the normalization.
-
-Considering the lift force, columns 7 and 8 of the table show that the different choices of normalization give different values for the coefficients $F_{1,y,c}$ and $F_{1,y,s}$.
-%This explains that the normalization choice fixes differently the phase of the cycle.
-However,  the sin-cos expansion of the lift force can be recast as 
-$F_y =  (F_{y,1,c} \cos \omega t + F_{y,1,s} \sin \omega t ) =  |F_{y,1}|  \cos (\omega t + \varphi)$ 
-with $ |F_{y,1}| =  \sqrt{F_{y,1,c}^2 + F_{y,1,s}^2}$. The last column of the table confirms that the three possible normalization choices effectively lead to the same values of $|F_{y,1}|$.
-
 \begin{table*}[!h]
@@
 \\
-\mbox{\cite{Fabre2012}} & 9.10988+3.28004i & 32.62-111.152i & -1.05886-3.00574i & 36.2307
+\mbox{\cite{Fabre2008}} & 9.10988+3.28004i & 32.62-111.152i & -1.05886-3.00574i & 36.2307
 & 5.2848 & 0.537254 & 0 & 0.537254
@@
 
+A key issue in the weakly nonlinear expansion is that the definition of the amplitude depends upon a normalization choice of the eigenmodes.
+Several choices are possible.
+In the literature three possibilities have been used:
+%\begin{itemize}
+%\item
+
+First, \cite{SippLebedev} normalized the eigenmode by assuming a specified value to the $y$-component of the velocity at one point, namely:
+\be{normsipp}
+\hat{u}_y(1,0) = 0.4612.
+\ee
+The advantage of this choice is that the coefficients $\nu_0$ and $\nu_2$ have the same order of magnitude as the coefficient $\Lambda$.
+
+%\item 
+Secondly, \cite{FDR2016} proposed the following normalization choice:
+\be{normFDR}
+\int_\Omega |\hat{\bf u}|^2 d {\bf x}  = \frac{1}{2}.
+\ee
+This directly leads to $|A| = A_E$, so this normalisation seems equivalent to the previous one.
+%{\color{red} The lift phase is not specified in \cite{FDR2016} and can be set to nil before the normalization.}
+
+%\item 
+Thirdly, following \cite{Fabre2008}, another convenient choice is to normalize the eigenmode with its lift 
+force: 
+\be{normfabre}
+{{\cal D}_{Re_c}(\hat{\bf u},\hat{p}) }=\frac{1}{2}.
+\ee
+The advantage of this choice is that the amplitude $|A|$ is then an direct measure of the fundamental lift.
+In effect, eq. \ref{lift_cos} directlty leads to $F_{y,1,c} = |A|$, $F_{y,1,s} = 0$.
+
+In our implementation of the WNL approach, we allowed to choose the normalization convention, as seen in line 3 of figure \ref{fig:listingNL}.
+%%ATTENTION, si figure est actualisé, il faut actualiser la ligne
+In table \ref{tab:WNL_coefs} we give the predictions of the WNL approach using the three normalization choices.
+We can note that the coefficients $\nu_0$ and $\nu_2$ strongly depend on the normalization choice.
+On the other hand, the frequency deviation $\omega_\epsilon$ and the $\lambda$ coefficient, and the term $F_{x,0,\epsilon}$ related to the dependency of mean drag with deviation from the threshold are independent upon the normalization.
+
+Considering the lift force, columns 7 and 8 of the table show that the different choices of normalization give different values for the coefficients $F_{1,y,c}$ and $F_{1,y,s}$.
+%This explains that the normalization choice fixes differently the phase of the cycle.
+However,  the sin-cos expansion of the lift force can be recast as 
+$F_y =  (F_{y,1,c} \cos \omega t + F_{y,1,s} \sin \omega t ) =  |F_{y,1}|  \cos (\omega t + \varphi)$ 
+with $ |F_{y,1}| =  \sqrt{F_{y,1,c}^2 + F_{y,1,s}^2}$. The last column of the table confirms that the three possible normalization choices effectively lead to the same values of $|F_{y,1}|$.
+
 %\be{lift_explanation}
@@
 
-\begin{figure}
-\vspace{-.5cm}\vspace{-.5cm}
-\includegraphics[width = .9\linewidth]{Cylinder_Mesh2_Full.png}
-\vspace{-.5cm}\vspace{-.5cm}
-\includegraphics[width = .9\linewidth]{Cylinder_Mesh2.png}
-\caption{Illustration of the stucture of mesh  $\mathbf{M}_2$ (adapted to both the base flow and structural sensitivity).}
-\label{fig:mesh2}
-\end{figure}
-
-\begin{figure}
-\vspace{-.5cm}\vspace{-.5cm}
-\includegraphics[width = .9\linewidth]{Cylinder_Mesh4_Full.png}
-\vspace{-.5cm}\vspace{-.5cm}
-\includegraphics[width = .9\linewidth]{Cylinder_Mesh4.png}
-\caption{Illustration of the stucture of mesh  $\mathbf{M}_4$ (adapted to both the base flow and direct eigenmode).}
-\label{fig:mesh4}
-\end{figure}
-
 \section{Additional details about the self-consistent method}
 
-{\em NOT SURE IF THIS PART SHOULD BE KEPT OR NOT...}
-
-The original form of the SC model given by \cite{ManticLugo14} was obtained by introducing the decomposition (\ref{SC}) into the Navier-Stokes equations, leading to :
+The objective of this appendix is to provide additional details about the  SC model in its original form as given by \cite{MLugo2014}, and to explain the connection with the simpler version discussed in section 4.2.
+The full model is obtained by introducing the decomposition (\ref{SC}) into the Navier-Stokes equations, leading to :
 \begin{subequations}\label{sc12}
@@
 pseudo-eigenpairs $(\lambda_{sc},  \tilde{{\bf u }}_1)$ can be computed by solving the eigenvalue problem (\ref{sis2}).
-\cite{ManticLugo14} Initially proposed a resolution method involving two imbricated loops, which is advantageaously replaced by
+\cite{MLugo2014} Initially proposed a resolution method involving two imbricated loops, which is advantageaously replaced by
 the direct Newton resolution of section 4.3.
@@
 \begin{itemize}
-\item[-] For $ \ll 1$ it is equivalent to the linear eigenvalue problem (\ref{LEP}), and the generalized eigenvalue coincides with the one predicted by linear stability : $\sigma_{SC} + i \omega_{SC} = \sigma_{lin} + i \omega_{lin}$.
-\item[-] For $\sigma_{SC}=0$ (corresponding to a specific choice of the amplitude $A=A_c$),  the expansion (\ref{SC}) is equivalent to 
+\item[-] For $ A \ll 1$ it is equivalent to the linear eigenvalue problem (\ref{LEP}), and the generalized eigenvalue coincides with the one predicted by linear stability : $\sigma_{SC} + i \omega_{SC} = \sigma_{lin} + i \omega_{lin}$.
+\item[-] For $\sigma_{SC}=0$ (corresponding to a specific choice of the amplitude $A=A_{sc}$),  the expansion (\ref{SC}) is equivalent to 
 the Fourier expansion \ref{eq:sc1} taken as the starting point in the present paper. 
-\item[-] For $0<A<A^c$, the resolution leads to a relation $\sigma_{SC}(A) ; \omega_{SC}(A)$
+\item[-] For $0<A<A_{sc}$, the resolution leads to a relation $\sigma_{SC}(A) ; \omega_{SC}(A)$
 such that $0< \sigma_{SC}(A) < \sigma_{lin}$.
@@
 
-\section{Mesh convergence : efficiency of mesh adaptation and effect of domain size}
-
-\begin{table*}
-$$
-\begin{array}{|c||c|c|c|c|c|c|c|c|c|}
-\hline
-\mbox{Mesh} & N_p & N_{dof} & \delta_{min} & \delta_{max} & \delta_A  & \delta_B  & \delta_C  & \delta_D  \\
-\hline
-\mathbf{M}_1 \mbox{(Adapt on base flow) } & 1429 & 12545	& 0.0131 & 14.33 		& 0.0259 	& 0.514 	& 0.819 	& 1.067 \\   
-\mathbf{M}_2 \mbox{(Adapt on sensitivity) } & 2038 & 		& 0.0155 & 14.17 		& 0.02826 & 0.2046 	& 0.3909 	& 1.2014 	\\
-\mathbf{M}_3 \mbox{(Adapt on sensitivity, split) } & 7974 &		& 0.0077 & 7.1  		& 0.014 	& 0.1 	&   0.2 	& 0.6   \\
-\mathbf{M}_4 \mbox{(Adapt on mode) } 	& 12080  &			&0.00825	& 124.61		& 0.0229	& 0.143	& 0.0993	& 0.0934 \\
-\mathbf{M}_5 \mbox{(Adapt on adjoint) } 	& 3813 	& 33715		& 0.0081	& 14.4		& 0.0123 	& 0.156	& 0.166	& 1.44  \\
-\hline
-\end{array}
-$$
-\caption{Description of meshes used for validation of mesh adaptation strategy : number of vertices $N_p$ ; number of degrees of freedom of the P2-P2-P1 Taylor-hood basis $N_{dof}$ ; cell size (minimum and value, and value at four characteristic point A,B,C,D as defined in the text).
- }
-\label{tab:conv1}
-\end{table*}
-
-\begin{table*}
-$$
-\begin{array}{|c||c|c||c||c|c||c|c|c|}
-\hline
-\mbox{Mesh} & L_x & F_x & \lambda & L_{x,SC} & F_{x,SC} & \omega_{SC}  & F_{y,1,c} & A_{E} \\
-\hline
-\mathbf{M}_1 & 4.0733 & 0.6431 	& 0.047056 + 0.74416i 		& 2.6073  &0.69277 		&  0.84334 & 0.1298 & 1.8301  \\
-\mathbf{M}_2 & 4.075 &.  0.64348  	& 0.046719 + 0.74489i 		& 2.          & 0.69246 	& 0.84351 & 0.12789 & 1.7134 \\  
-\mathbf{M}_3 & 4.0772 & 0.64391 	& 0.04684. +  0.74511i 		& 2.6141  & 0.69338 	& 0.84383 & 0.12799 & 2.048   \\ 
-\mathbf{M}_4 & 4.0748 & 0.64402 	& 0.04676  + 0.74502i 		& 2.613 	& 0.690338 	& 0.84371 & 0.12809 & 2.5905 \\
-\mathbf{M}_5 & 4.0772 & 0.64384	& 0.04665 + 0.74530i		& 2.6146 	& 0.6932		& 0.84333 & 0.1276	 & 2.5971 \\
-\hline
-\end{array}
-$$
-\caption{Results for mesh adaptation strategy ($Re = 60$) : Base-flow characteristics $L_x$ and $F_x$, linear eigenvalue $\lambda$, 
-Nonlinear self-consistent model characteristics  $\omega_{SC}$, $F_{y,1,c}$ and $A_E$. All the results can be optained using the matlab program
-{\em SCRIPT\_CYLINDER\_MESHCONVERGENCE.m}. }
-\label{tab:conv2}
-\end{table*}
-
-\begin{table*}
-$$
-\begin{array}{|c|c||c|c||c||c|c||c|c|c|}
-\hline
-\mbox{Mesh} & N & L_x & F_x & \lambda & L_{x,SC} & F_{x,SC} & \omega_{SC}  & F_{Y,SC} & A_{E,SC} \\
-\hline
-\mathbf{M}_2 \mbox{(ref)} 	& 7974  	& 4.0772 & 0.64391 	& 0.04684. +  0.74511i 	& 2.6141  & 0.69338 	& 0.84383 & 0.12799 & 2.048   \\ 
-\mathbf{M}_6 [-20,40]x[0,20] 	& 7437	&  4.108 & 0.64987 	& 0.048368. +  0.74952i 	& 2  & 0.69957 	& 0.85015 & 0.13125 & 2.3638   \\ 
-\mathbf{M}_7 [-80,160]x[0,80] 	& 7480	& 4.0641 & 0.64129		& 0.046271 + 0.74341i 	& 2 	& 0.69069 	& 0.84159 & 0.12653 & 2.4453 \\
-\mathbf{M}_8 \mbox{(slip conditions)}	 & 7056	& 4.0467 &0.66295		& 0.049216+0.76553i 	& 2 	& 0.69241		& 0.8438  & 0.12716	 & 2.3202 \\
-\hline
-\end{array}
-$$
-\caption{Comparison of the performances of several meshes with variable dimensions and different boundary conditions}
-\label{tab:conv3}
-\end{table*}
-
-This appendix presents complementary results obtained using various mesh designs. 
-All the results can be obtained using the following program available on the StabFem website : 
-{\em SCRIPT\_CYLINDER\_MESHCONVERGENCE.m}.
-
-\subsection{Efficiency of the mesh adaptation process}
-
-As discussed in section 3, the mesh adaptation proves to be an extremely efficient way to obtain significant results 
-with very reasonable meshes. The objective of this paragraph is to demonstrate this point by comparing the efficiency of several ways to perform mesh adaptation.
-
-For this purpose, 5 meshes were generated. 
-Mesh $\mathbf{M}_1$ was adapted on the {\em base flow} obtained for $Re=60$.
-Mesh $\mathbf{M}_2$ was adapted to both the base flow and structural sensitivity.
-Mesh $\mathbf{M}_3$ was obtained by a subsequent refinement of mesh $\mathbf{M}_2$, splitting all triangles in four subtriangles, therefore doubling the effective density of the mesh.
-Meshes $\mathbf{M}_4$ and $\mathbf{M}_5$ were obtained by adapting to the structure of the direct eigenmode and of the adjoint eigenmode.
-In each case, the adaptmesh process was repeated twice in order to ensure a correct convergence.
-
-Figures \ref{fig:mesh2} and \ref{fig:mesh4} illustrate the structure of meshes $\mathbf{M}_2$ and $\mathbf{M}_4$.
-As can be observed, these two mesh adaptation strategies lead to meshes with comparable densities in the region close to the cylinder.
-On the other hand, when moving downwards in the wake, mesh $\mathbf{M}_2$ quickly gets rather coarse, while mesh $\mathbf{M}_4$ maintains a significant density
-
-Table \ref{tab:conv1} gives additional details about the geometry of these meshes.
-In particular, we document the minimum and maximum cell size, as well as the cell size at four point A,B,C,D defined with by their coordinates as follows : $(x_A,y_A) = (0,0.5)$ (within the boundary layer at the cylinder wall); $(x_B,y_B) = (2.5,0.5)$ (in the region of maximum structural sensitivity); $(x_C,y_C) = (4,0)$ (in the near wake); $(x_D,y_D) = (10,0)$ (in the far wake).
-Results confirm that mesh all meshes have similar densities in the near wake (cell size at points A,B,C are comparable)
-while $\mathbf{M}_4$ has maximum resolution in the far wake (in the vicinity of point D).
-
-Table  \ref{tab:conv2} compares the results obtained with the five meshes.
-For base-flow characteristics $L_x$ and $F_x$, all values agree with a relative dispersion of less than $0.15\%$, confiming that all adaptation stategies are successful to correctly compute the base flow.
-The performances of meshes for linear stability calculations can then be evaluated by comparing the eigenvalues.
-Meshes $\mathbf{M}_2$ to $\mathbf{M}_5$ all give values within less than $0.1\%$ dispersion.
-The value obtained with mesh  $\mathbf{M}_1$, which is not adapted to the eigenmode, is a bit farther from the others but still rather good.
-The table also displays results allowing to compare the performances of meshes for nonlinear self-consistent calculations.
-As for the frequency and the maximum lift, meshes $\mathbf{M}_2$ to $\mathbf{M}_5$ again give almost identical values within less than $0.1\%$ dispersion.
-The dispersion is much larger concerning the energy-amplitude of the perturbation $A_E$ displayed in the last column.
-Only the mesh $\mathbf{M}_4$ is able to correctly compute this quantities, while all other meshes significantly underestimate it.
-This is not surprising since this quantity is an integral one which depends upon the structure of the nonlinear perturbation in the whole wake, not only the near-wake region.
-
-From this study we can conclude that if we are only interested in predicting the frequency of the mode and the forces exerted on the cylinder (in both linear and nonlinear regimes), the strategy of mesh adaptation to both base flow and structural sensitivity (mesh $\mathbf{M}_2$) is the most efficient and leads to a very light mesh (here only 2048 points).
-On the other hand, if we are interested in describing the structure of the perturbation in the whole domain (and being able to correctly evaluate its energy), mesh adaptation to the eigenmode structure is preferable.
-However this second strategy produces a much heavier mesh (here 12080 point).
-
-\subsection{Effect of domain size and boundary conditions}
-
-As already identified in several previous studies, the size of the domain and the type of boundary conditions applied at the boundaries have a notable impact on the results.
-To illustrate this, we designed three additional meshes.
-All were obtained through adaptation to base flow and sensitivity, just as mesh $\mathbf{M}_2$.
-Meshes $\mathbf{M}_6$ and $\mathbf{M}_7$ are respectively twice smaller and twice larger than the reference one. 
- $\mathbf{M}_8$ has the same dimension as the reference case but the boundary condition at the lateral boundary $\Gamma_{lat}$ is replaced by a less restrictive slip condition.
-
-Even though the domain size of the reference case (namely $[-40,80]\times[0,40]$) may appear large, the table shows that confinement effects are still present.
-The quantity which appears the most sensible to domain size and/or boundary conditions is the imaginary part of the linear eigenvalue.
-Interestingly, the nonlinear SC results appears to be more robust with respect to confinement effects than linear ones.
-In effect, values for nonlinear frequency $\omega_{SC}$ and the maximum lift $F_{y,1,c}$ obtained with meshes  $\mathbf{M}_2$, $\mathbf{M}_7$
-and  $\mathbf{M}_8$ agree with less than $0.3\%$ dispersion.
+Note that in our numerical implementation, the programs can actually be used to solve the SC model in the general case (with $\sigma\ne0$). 
+This can be controlled by assigning a nonzero value to the optional parameter \verb|sigma| of the  {\sf SF\_SelfConsistent.m} Matlab function.
+The interested reader will find on the website of the {\em StabFem} project a program {\sf SCRIPT\_CYLINDER\_NONLINEAR.m} which computes $A$ as function of $\sigma$ for $Re=100$, yielding identical results as displayed in figure 3 of \cite{MLugo2014}.
+
+\section{Details of the weak formulation}
+
+In the presentation of the numerical methods in sections 2.1 and 2.2, and introduction of the {\em weak form}, we have omitted an important point, namely the issue of boundary conditions.
+In this appendix we explain more rigorously how the weak formulation is obtained.
+We consider here the full time-dependent nonlinear Navier-Stokes equations, but the treatment of the base-flow equations and the linearised equations is essentially the same.
+
+Noting $\Gamma$ the boundary of the numerical domain, the latter can be decomposed in five parts : 
+$\Gamma = \Gamma_{in} \cup \Gamma_{cyl} \cup \Gamma_{axis} \cup \Gamma_{out} \cup \Gamma_{lat}$. 
+Noting $\sigma = 2 Re^{-1} {\bf D}({\bf u}) - p {\bf 1}$ the stress tensor, the relevant boundary conditions are as follows:
+\begin{itemize}
+\item On $\Gamma_{in}$ (inlet): ${\bf u} = {\bf e}_x$ (Dirichlet).
+\item On $\Gamma_{cyl}$ (surface of the cylinder): ${\bf u} = {\bf 0}$ (Dirichlet).
+\item On $\Gamma_{out}$ (outlet): $\sigma \cdot {\bf n} = {\bf 0}$ (Neumann). 
+\item On $\Gamma_{lat}$ (lateral boundary):  $\sigma \cdot {\bf n} = {\bf 0}$ (Neumann). 
+\item On $\Gamma_{axis}$ (symmetry plane): $u_y = 0$ and $\sigma_{xy} = 0$ (Mixed). 
+\end{itemize}
+We will introduce the following notation for integrals along any portion of the boundary $\Gamma_i$ of the product of two quantities $\phi_1, \phi_2$ (either scalar or vectorial) :
+%$\left< \phi_1, \phi_2 \right>_{\Gamma_i} $:
+$$
+\left< \phi_1, \phi_2 \right>_{\Gamma_i} = \int_{\Gamma_i}  \overline{\phi}_1 \cdot \phi_2   \mbox{ d} \ell,
+$$
+Instead of the simplified version \ref{NSweak}, the more precise form of the weak formulation can be first written as follows:
+\begin{eqnarray}
+\label{NSweakFull}
+\forall [{\bf v},q], &&\quad \partial_t \left< {\bf v}, {\bf u}\right> = \left< {\bf v} , {\cal NS} ({\bf u},p) \right> + \left< q, \nabla \cdot {\bf u}\right>\\
++ &&\frac{1}{\epsilon} \left(  \left< {\bf v}, \bf{u} \right>_{\Gamma_{cyl}} + \left< {\bf v}, ({\bf u}- {\bf e}_x ) \right>_{\Gamma_{in}} 
++ \left< v_y, u_y\right>_{\Gamma_{axis}} \right) \nonumber \\
++ && \left< {\bf v}, \sigma \cdot {\bf n} \right>_{\Gamma_{out} \cup  \Gamma_{lat} \cup \Gamma_{axis} }  \nonumber 
+\end{eqnarray}
+where $\epsilon=10^{-30}$ is a small parameter used to impose the Dirichlet boundary conditions by penalization.
+An integration by parts of the pressure gradient and viscous stress terms of the Navier-Stokes equation eventually 
+leads to the weak form effectively used in the programs {\sf Newton2D.edp} and {\sf Stab2D.edp}:
+\begin{eqnarray}
+\forall [{\bf v},q], &&\, \partial_t \left< {\bf v}, {\bf u}\right> = - \left< {\bf v} , {\cal C}({\bf u},{\bf u})/2 \right>
+- 2 Re^{-1} \left< {\mathsf D}({\bf v}) : {\mathsf D}({\bf u})  \right>  \nonumber \\
++ &&\left< \nabla \cdot {\bf v}, p \right> + \left< q, \nabla \cdot {\bf u} \right> \label{NSweakFullN} \\
++ &&\frac{1}{\epsilon} \left(  \left< {\bf v}, \bf{u} \right>_{\Gamma_{cyl}} + \left< {\bf v}, ({\bf u}- {\bf e}_x ) \right>_{\Gamma_{in}} 
++ \left< v_y, u_y\right>_{\Gamma_{axis}} \right) \nonumber 
+\end{eqnarray}
+Note that the Neumann boundary conditions do not appear any more thanks to the integration by parts.
 

### 2018-06-25 ARTICLE_STABFEM/ARTICLE_ASME_V4.tex
Recovering plotFF

@@
 \footnote{All the figures contained in the present paper can be processed by launching a single Matlab script SCRIPT\_CYLINDER\_ALLFIGURES.m .
-On a MacbookPro (2018,  2.5Ghz, 16Go Ram),  the execution time is 19.76 seconds for the results of the linear analysis (section 3) and 15.
-seconds for the results of the nonlinear analysis (section 4).
+On a MacbookPro (2018,  2.5Ghz, 16Go Ram),  the execution time is 203 seconds for the results of the linear analysis (section 3).
+The results of the nonlinear analysis requires 1868 seconds using mesh ${\mathbf M}_4$, a time which can be
+reduced to only 413 seconds using mesh ${\mathbf M}_2$ if one is not interested in a precise description of the perturbation in the far-wake region.
 }. 

### 2018-06-25 EXAMPLE_Lshape/SCRIPT_Lshape_BASE_6716.m

@@ -1,40 +1,0 @@
-clear all;
-close all;
-run('../SOURCES_MATLAB/SF_Start.m');
-
-% importation of a mesh and data field 'base flow' 
-Ndensity =40;
-% here Ndensity is the only parameter, but we can pass several 
-ffmesh=SF_Mesh('Lshape_Mesh.edp','Params',Ndensity);
-
-
-% plot the mesh and the associated data
-ffmesh.plottitle = 'Mesh for L-shape body';
-hand = plotFF(ffmesh);
-
-% importation and plotting of a real P1 field : temperature
-heatS=SF_Launch('Lshape_Steady.edp','Mesh',ffmesh)
-heatS.plottitle = 'Solution of the steady heat equation on a L-shaped domain';
-plotFF(heatS,'T');
-
-% importation and plotting of data not associated to mesh : temperature along a line
-heatCut = importFFdata('Heat_1Dcut.ff2m');
-figure(3);
-plot(heatCut.Xcut,heatCut.Tcut);
-title('Temperature along a line : T(x,y=0.25)') 
-
-% importation and plotting of a complex P1 field : temperature for unsteady problem
-heatU=SF_Launch('Lshape_Unsteady.edp','Params',10,'Mesh',ffmesh,'DataFile','Heat_Unsteady.ff2m')
-
-heatU.plottitle = ['Solution of the unsteady heat equation for omega = ' num2str(heatU.omega) ' : Re(Uc) ' ];
-heatU.xlim = [-.5,1.5]; % note the way to specify plot ranges xlim, ylim 
-heatU.ylim = [-.5,1.5];
-hand = plotFF(heatU,'Tc.re');%plot the real part of a complex
-
-heatU.plottitle = ['Solution of the unsteady heat equation for omega = ' num2str(heatU.omega) ' : Im(Uc) ' ];
-hand = plotFF(heatU,'Tc.im');%plot the imag part of a complex
-    
-heatU.plottitle = ['Solution of the unsteady heat equation for omega = ' num2str(heatU.omega) ' : |grad(Uc)| ' ];
-hand = plotFF(heatU,'normTc');
-    
-

### 2018-06-25 EXAMPLE_Lshape/SCRIPT_Lshape_REMOTE_6716.m

@@ -1,26 +1,0 @@
-% This script is a basic example which illustrates the main functionalities of the StabFem Software
-clear all; close all;
-run('../SOURCES_MATLAB/SF_Start.m');ffdatadir = './';
-
-% Generation of the mesh
-Ndensity =40;
-ffmesh=SF_Mesh('Lshape_Mesh.edp','Params',Ndensity)
-plotFF(ffmesh,'title','Mesh for L-shape body');
-set(gca,'FontSize', 18); saveas(gca,'FIGURES/Lshape_Mesh','png');
-
-% importation and plotting of a real P1 field : temperature
-heatS=SF_Launch('Lshape_Steady.edp','Mesh',ffmesh)
-plotFF(heatS,'T','title', 'Solution of the steady heat equation on a L-shaped domain');
-set(gca,'FontSize', 18); saveas(gca,'FIGURES/Lshape_T0','png');
-
-% importation and plotting of data not associated to a mesh : temperature along a line
-heatCut = importFFdata('Heat_1Dcut.ff2m')
-figure();plot(heatCut.Xcut,heatCut.Tcut);
-title('Temperature along a line : T(x,y=0.25)') 
-set(gca,'FontSize', 18); saveas(gca,'FIGURES/Lshape_T0_Cut','png');
-
-% importation and plotting of a complex P1 field : temperature for unsteady problem
-heatU=SF_Launch('Lshape_Unsteady.edp','Params',100,'Mesh',ffmesh,'DataFile','Heat_Unsteady.ff2m')
-plotFF(heatU,'Tc.re','contour','Tc.im','title',['Ti: ' char(13) 'real(colors) and imaginary(levels) parts'])
-set(gca,'FontSize', 18); saveas(gca,'FIGURES/Lshape_Tc','png');
-

### 2018-06-25 SOURCES_MATLAB/SF_Start.m

@@ -7,25 +7,27 @@ global ff ffdir ffdatadir sfdir verbosity
 % ffdatadir -> path where to store the results (recommended is ./WORK) 
 
 if(isunix)
-ff = '/PRODCOM/FREEFEM/Ubuntu12.04/3.29/bin/FreeFem++-nw'; % on IMFT network
+ff = '/PRODCOM/FREEFEM/Ubuntu12.04/3.29/bin/FreeFem++ -v 0'; % on IMFT network
 end
 if(ismac)
-ff = '/usr/local/bin/FreeFem++ -nw';
+ff = '/usr/local/bin/FreeFem++ -v 0';
 % NB normally this is where the FreeFem++ executable should be on a mac.
 % If not the case, either do a symbolic link (recommended) or replace with
 % the right one. option "-nw" is better to discard the ff++ graphical output. 
 % below are possible choices for various contributors :
 %ff = '/usr/local/ff++/openmpi-2.1/3.60/bin/FreeFem++'; % old syntax for David
-%ff = '/usr/local/ff++/bin/FreeFem++ -nw'; for Flavio
+%ff = '/usr/local/ff++/bin/FreeFem++'; for Flavio
 end
 if(ispc)
     ff = 'FreeFem++ -nw -v 0'; % for windows systems
+    ff = 'launchff++'; % for older windows systems (?)
 end
 
 sfdir = '../SOURCES_MATLAB/'; 
 ffdir = '../SOURCES_FREEFEM/';
 
-addpath(sfdir);
+
+
 
 % This is the recommended implementation on most systems. 
 % In case StabFem is not in your root directory you may adapt. Bellow a few
@@ -37,7 +39,11 @@ addpath(sfdir);
 %sfdir = '/Users/fabred/StabFem/SOURCES_MATLAB/'; % where to find the matlab drivers
 %ffdir = '/Users/fabred/StabFem/SOURCES_FREEFEM/'; % where to find the freefem scripts
 
-ffdatadir = '.\WORK\';
+
+addpath(sfdir);
+
+
+ffdatadir = './WORK/';
 
 verbosity = 1;
 

### 2018-06-25 SOURCES_MATLAB/importFFmesh.m

@@ -26,6 +26,7 @@ fileToRead3 = [filepath,'/SF_Init.ff2m'];
 
 mydisp(2,['FUNCTION  importFFmesh.m : reading complementary files']);
     
+
 meshstruct = importFFdata(fileToRead2,fileToRead3);
 
 % change the field "datatype" to "problemtype"

### 2018-06-28 99_Documentation/211_StabFem_RotatingPolygons.tex

% !TEX root = main.tex

\chapter{Instabilities of a potential free-surface vortex flow}

\begin{description}
\item{Directory in the StabFem project :}  \texttt{ROTATINGPOLYGONS}
\item{Main contributors :} J. Mougel, D. Fabre
\item{Reference :} Mougel et al., JFM 2018 
\end{description}

\begin{figure}
\includegraphics[width=.8\linewidth]{../ROTATING_POLYGONS/FIGURES/POLYGONS_modes.png}
\caption{Oscillation modes of a potential vortex for  $a=H/R=0.3$ and $m=3$ (figure 5, 6 of Mougel et al.).}
\label{Bridges_NV_Eigenmodes_phi_cyl_L3_5}
\end{figure}

\begin{figure}
\includegraphics[width=.45\linewidth]{../ROTATING_POLYGONS/FIGURES/POLYGONS_omega.png}
\includegraphics[width=.45\linewidth]{../ROTATING_POLYGONS/FIGURES/POLYGONS_sigma.png}
\caption{Oscillation frequencies and amplification rates for f a potential vortex for $m=3$ (figure 4 of Mougel et al.).}
\label{Bridges_NV_Eigenmodes_phi_cyl_L3_5}
\end{figure}

### 2018-07-09 99_Documentation/11_StabFem_BasicFunctionalities.tex
birdcall data

@@
 Looking inside the file \keys{Data.ff2m}, the header (i.e.  first four lines) is as follows :
-\lstinputlisting[linerange={1-5}]{../EXAMPLE_Lshape/Data.ff2m}, 
+\lstinputlisting[linerange={1-6,199}]{../EXAMPLE_Lshape/Data.ff2m}, 
 meaning that this files contains a P1 mesh-organised field called 'T'.
@@
 \item{\bf complex.N} for complex vectors of dimension N not associated to a mesh,
-\item{\bf P1s} for real data defined along a frontier of the mesh,
-\item{\bf P1sc} for complex data defined along a frontier of the mesh.
+\item{\bf P1surf} for real data defined along a frontier of the mesh,
+\item{\bf P1surfc} for complex data defined along a frontier of the mesh.
 \end{description}

### 2018-07-09 BIRDCALL_Ercoftac/SCRIPT_BirdCall_Linear.m

@@ -69,6 +69,7 @@ guess4 = 0.178 + 10.256i;
 
 
 Re_Range1=[1000:-50:150];Re_Range2=Re_Range1;Re_Range3=Re_Range1;Re_Range4=Re_Range1;
+Re_Range4=[1000:-50:600];
 EV1 = []; EV2 = []; EV3 = []; EV4 = [];
 
 bf = SF_BaseFlow(bf,'Re',1000);

### 2018-07-09 BIRDCALL_Ercoftac/SCRIPT_BirdCall_WNL_Branch2.m

@@ -1,43 +1,33 @@
 
 
-% guess found for Re=400
-% first one  
-%guess1 = -0.0741+2.476i;
-guess1 = 0.02352+3.2924i; % for 1st hole normalisation
-%second one : 
-%guess2 =  -0.289+4.039i; % for 2nd hole normalisation
 guess2 = -0.0229848+5.39569i
-% third one :
-%guess3 = -0.930+8.006i;
 
-%%%%% BRANCH NUMBER 2:
 
-%%%%% CALCULATION OF A PART OF THE BRANCH CLOSE TO THE THRESHOLD
 
 Re_Range = [400 408 409 410 420 430 440 450];
-    
- if(exist('DP0_Branch')==0)% to save time if already computed
-    DP0_Branch = [];
+  
+ %if(exist('DP0_Branch')==0)% to save time if already computed
+     DP0_Branch = [];
+     EVW = [];  
+    [ev,em] = SF_Stability(bf,'m',0,'shift',guess2,'nev',1);
     for Re = Re_Range
-        bf=FreeFem_BaseFlow(bf,Re);
-        DP0_Branch = [DP0_Branch,bf.deltaP0]
+        bf=SF_BaseFlow(bf,'Re',Re);
+        DP0_Branch = [DP0_Branch,bf.Pup]
+        if(Re==Re_Range(1)) shift = guess2; else shift = 'cont'; end;
+        [ev,em] = SF_Stability(bf,'m',0,'shift',shift,'nev',1);
+        if(em.iter~=-1) EVW = [EVW ev]; else break; end;
     end
- end
+ %end
  
  figure(3);
     plot(Re_Range,DP0_Branch);
     title('Pressure drop across the whistle as function of Re');
     
 
-   % if(exist('EV1')==0)
-   %     EV1 = FreeFem_Stability_LoopRe(bf,Re_Range,0,guess1,1,'Branch1.dat');
-   % end
-    if(exist('EV2')==0)
-        EV2 = FreeFem_Stability_LoopRe(bf,Re_Range,0,guess2,1,'Branch2.dat');
-    end
-%    if(exist('EV3')==0)
-%        EV3 = FreeFem_Stability_LoopRe(bf,Re_Range,0,guess3,1);
+%    if(exist('EV2')==0)
[…]

### 2018-07-09 EXAMPLE_Lshape/SCRIPT_Lshape.m

@@ -4,23 +4,29 @@ run('../SOURCES_MATLAB/SF_Start.m');ffdatadir = './';
 
 % Generation of the mesh
 Ndensity =40;
-ffmesh=SF_Mesh('Lshape_Mesh.edp','Params',Ndensity);
+ffmesh=SF_Mesh('Lshape_Mesh.edp','Params',Ndensity)
 figure();plotFF(ffmesh,'title','Mesh for L-shape body');
 set(gca,'FontSize', 18); saveas(gca,'FIGURES/Lshape_Mesh','png');
 
+pause
+
 % importation and plotting of a real P1 field : temperature
-heatS=SF_Launch('Lshape_Steady.edp','Mesh',ffmesh);
+heatS=SF_Launch('Lshape_Steady.edp','Mesh',ffmesh)
 figure();plotFF(heatS,'T','title', 'Solution of the steady heat equation on a L-shaped domain');
 set(gca,'FontSize', 18); saveas(gca,'FIGURES/Lshape_T0','png');
 
+pause
+
 % importation and plotting of data not associated to a mesh : temperature along a line
-heatCut = importFFdata('Heat_1Dcut.ff2m');
+heatCut = importFFdata('Heat_1Dcut.ff2m')
 figure();plot(heatCut.Xcut,heatCut.Tcut);
 title('Temperature along a line : T(x,y=0.25)') 
 set(gca,'FontSize', 18); saveas(gca,'FIGURES/Lshape_T0_Cut','png');
 
+pause
+
 % importation and plotting of a complex P1 field : temperature for unsteady problem
-heatU=SF_Launch('Lshape_Unsteady.edp','Params',100,'Mesh',ffmesh,'DataFile','Heat_Unsteady.ff2m');
+heatU=SF_Launch('Lshape_Unsteady.edp','Params',100,'Mesh',ffmesh,'DataFile','Heat_Unsteady.ff2m')
 figure();plotFF(heatU,'Tc.re','title',['Ti: real(colors) part'])
 %figure();plotFF(heatU,'Tc.re','contour','Tc.im','title',['Ti: ' char(13) 'real(colors) and imaginary(levels) parts'])
 set(gca,'FontSize', 18); saveas(gca,'FIGURES/Lshape_Tc','png');

### 2018-07-09 SOURCES_MATLAB/SF_Stability.m

@@ -293,8 +293,8 @@ eigenvalues = EVr+1i*EVi;
 
 % updating two previous iterations
 if(strcmp(p.Results.shift,'cont')==1)
-sigmaPrevPrev = sigmaPrev;
-sigmaPrev = eigenvalues(1);
+sigmaPrevPrev = sigmaPrev
+sigmaPrev = eigenvalues(1)
 mycp([ffdatadir 'Eigenmode.txt'],[ffdatadir 'Eigenmode_guess.txt']);  
 else
 sigmaPrevPrev = eigenvalues(1);

### 2018-07-09 SOURCES_MATLAB/mysystem.m

@@ -43,6 +43,7 @@ else % verbose mode
  disp('$$ LEAVING FREEFEM++ :')
  disp('$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$');
     if(status~=0)&&(status~=141)&&(status~=13)&&(strcmp(errormessage,'skip')==0)
+        status
         error(errormessage);
     end   
 end

### 2018-07-16 99_Documentation/11_StabFem_BasicFunctionalities.tex

@@
 Looking inside the file \keys{Data.ff2m}, the header (i.e.  first four lines) is as follows :
-\lstinputlisting[linerange={1-6,199}]{../EXAMPLE_Lshape/Data.ff2m}, 
+\lstinputlisting[linerange={1-4}]{../EXAMPLE_Lshape/Data.ff2m}, 
 meaning that this files contains a P1 mesh-organised field called 'T'.
@@
 Execution of this step leads to the following :
-\lstinputlisting[linerange={17-24}]{Lshape_ExecutionExample.txt}
+\lstinputlisting[linerange={21-28}]{Lshape_ExecutionExample.txt}
 
@@
 Execution of this step leads to the following :
-\lstinputlisting[linerange={26-32}]{Lshape_ExecutionExample.txt}
+\lstinputlisting[linerange={30-37}]{Lshape_ExecutionExample.txt}
 
@@
 
-The line 4 explains the nature of the data which is contained in the file.
+Line 2 contains a description string which is imported as field 'datadescription'.
+
+Line 3 contains a series of property names and alphanumeric (string) values.
+
+Line 4 explains the nature of the data which is contained in the file.
 There can be as many data objects as you want organised in the order of your choice. The recognized types are currently as follows :
@@
 
-to be continued...
+Examination of the simple example here shows that the mesh generation produces four files (here all generated by the macro SF\_writemesh defined
+in file Macros\_StabFem.edp)
+
+\begin{itemize}
+\item file \keys{mesh.txt} contains the mesh in the native FreeFem format.
+Namely, information about the vertices, the boundaries and the triangles.
+This mesh is imported in stabfem using importFFmesm.m , and it is also needed for subsequent Freefem++ programs.
+
+\item file \keys{mesh.ff2m} contains informations about the mesh structure, to be imported by StabFem (it is read by importFFmesm.m)
+
+\item file  \keys{SF\_Init.ff2m} contains informations about the mesh geometry, to be imported by StabFem as well  (it is also read by importFFmesm.m)
+
+\item file \keys{SF\_geom.edp} contains definitions of case-dependent geometrical parameters which may be used by the FreeFem++ solvers.
+This file is designed to be {\em included } in the header of the FreeFem++ solvers.
+\end{itemize}
+
+Note that files \keys{mesh.ff2m} and  \keys{SF\_Init.ff2m} may seem redundant... the difference is that  \keys{SF\_Init.ff2m} is created only once 
+while  \keys{mesh.ff2m} is recreated each time the mesh is modified (adapted, splitted, etc...) .

### 2018-07-17 99_Documentation/ARTICLE_STABFEM/Beamer_12oct2017_IMFT.tex
Reorganization of the base

\documentclass{beamer}

\usepackage[frenchb]{babel}

\usepackage[T1]{fontenc}
%\usepackage[latin1]{inputenc}
\usepackage[utf8]{inputenc}

\usepackage{marvosym}

\newcommand{\be}[1]{ \begin{equation} \label{#1}}
\newcommand{\ee}{\end{equation}}

\newcommand{\bes}[1]{ \begin{equation} \label{#1}\begin{array}{rl}}
\newcommand{\ees}{\end{array}\end{equation}}

% \usetheme{default} -> A utiliser dans un premier temps

% \usetheme{Warsaw} -> A utiliser dans un second temps

\newcommand{\ssp}{\vspace{.2cm} }

\title{Approches globales, linéaires et non-linéaires, des instabilités hydrodynamiques.
}

\subtitle{"La stabilité globale pour les neuneus"}

\author{D. Fabre}

\institute{IMFT, groupe Interface}

\date{12 octobre 2017}

\begin{document}

\begin{frame}

\titlepage

\end{frame}

\section{Introduction}

\begin{frame}{Qu'es aquò ?? }

Les problèmes d'instabilités sont omniprésents en mécanique des fluides.

\ssp

Leur résolution fait appel à une classe de méthodes numériques spécifiques, 
complémentaires aux approches de simulation directe, qui sont actuellement en plein développement.

\ssp

On parle {\em stabilité globale} quand la géométrie du problème necésssite une résolution en 2D (ou en 3D).

\ssp

(par opposition à {\em stabilité locale} quand des directions d'invariance (écoulement parallèle par ex.) permettent de rammener le problème à une résolution en 1D).

\end{frame}

\begin{frame}{Outils de résolution numérique}

Les méthodes d'éléments finis sont bien adaptés à ces problèmes.

Le logiciel {\em FreeFem++} est un outil très populaire dans la communauté de la stabilité hydrodynamique.

\ssp

%{\color{green} \Smiley{} \quad }  (solides, fluides, thermique, etc...)

{\color{green} \Smiley{} \quad } Syntaxe intuitive basée directement sur la formulation faible.

{\color{green} \Smiley{} \quad } Mailleur puissant et adaptatif (movemesh, adaptmesh, etc...)

{\color{red} \Frowny{} \quad } Interface graphique limitée (ffglut).

{\color{red} \Frowny{} \quad } Language interprété : pas adapté à la programmation fonctionnelle (mais des macros puissantes).

 \ssp

Necessité d'une surcouche "driver"  pour piloter les calculs et tracer les résultats en mode terminal ou par l'intermédiaire de sripts.
\ssp 
Choix : solveurs FreeFem / drivers Matlab.

\ssp -> Logiciel "Stabfem", développé à des fins d'enseignement et de recherche.

\ssp
{\color{orange}
\verb! https://github.com/erbafdavid/StabFem !
}

\end{frame}

\section{Linear stability }

\subsection{Step 0 : computation of a base flow}

\begin{frame}{Base flow}

We look for a steady base-flow $({\bf u}_b;p_b)$ satisfying the steady Navier-Stokes equations, i.e. 
$NS ({\bf u}_b,p_b) = 0$.

Suppose that we have a 'guess' for the base flow $[{\bf u}_b^g,p_b^g]$  which almost satisfies the equations.  We look for a better approximation under the form
\be{Newton1}
[{\bf u}_b,p_b]  = [{\bf u}_b^g,p_b^g] + [\delta {\bf u}_b, \delta p_b] = 0.
\ee

Injecting into the Navier-Stokes equation lead to $$
NS ({\bf u}_b^g,p_b^g) + NSL_{{\bf u}_b^g}(\delta {\bf u}_b,\delta p_b)$$

Where $NSL$ is the linearised Navier-Stokes operator. 
%defined by its action on a flow field $({\bf u} ; p)$ as follows

=>  matricial problem with the form $A \cdot \delta X = Y$. The procedure of Newton iteration is to solve iteratively this set of equations up to convergence.

\end{frame}

\subsection{Eigenvalue computation}

\begin{frame}{Linear stability}

\be{startmodepropre}
{\bf u} = {\bf u}_b + \epsilon \hat{\bf u} e^{\lambda t} 
\ee

The eigenmodes is governed by the linear problem 
$$\lambda \hat{{\bf u}} = NSL_{{\bf u}_b}( \hat{\bf u},\hat{p})$$,

After discretization we end up with an eigenvalue problem with the matricial form
\be{Eigen_matricial}
\lambda B \hat{X} = A \hat{X}
\ee

\ssp
Iterative method : single-mode shift-invert iteration
$$
X^{n} =  (A- \lambda_{shift} B)^{-1} B X^{n-1}
$$

Generalization : Arnoldi

\end{frame}

\subsection{Adjoint problem}

\begin{frame}{Adjoint problem}

\small

Define a scalar product :
$$
\left< \phi_1, \phi_2 \right> = \int_\Omega \overline{\phi_1} \cdot \phi_2   \mbox{ d} \Omega
$$

We can first define the {\em adjoint linearised Navier-Stokes operator} $NSL^\dag$ defined by the property:
\bes{NSLAdj}
\forall ( {\bf u}, p ; {\bf v}, q), & \left< NSL^\dag_{\bf U}( {\bf v},q) ,{\bf u}\right> + \left< \nabla \cdot {\bf v},p\right>  \\
=& \left< {\bf v}, NSL_{\bf U} ({\bf u},p)\right> + \left< q, \nabla \cdot {\bf u}\right>.
\ees
We can then define the adjoint eigenmodes as the solutions to the eigenvalue problem 
\be{EigenAdj} 
\forall ( {\bf u}, p), \quad  \lambda^\dag \left< \hat{\bf v}, {\bf u}\right> =
 \left< NSL^\dag_{\bf U}( \hat{\bf v},\hat{q}) ,{\bf u}\right> + \left< \nabla \cdot \hat{\bf v},p\right>  
\ee

Matricial form :

\be{Eigen_Adj_matricial}
\overline{\lambda}^\dag B \hat{X}\dag = A^T \hat{X}\dag.
\ee

\end{frame}

\begin{frame}{Adjoint mode and structural sensitivity}

Significance of the adjoint mode :

(optimal perturbation)

\end{frame}

\section{Nonlinear global approaches to hydrodynamic instabilities}

\begin{frame}{Nonlinear global stability approaches : review}

%The linear stability approach approach is the right tool to predict instability threshold ($Re_c$) and the %shedding frequency at threshold ($St_c = \omega_c/2\pi$).

%\ssp
% But for $Re>Re_c$ it badly predicts the frequency of the limit cycle.

$$
\includegraphics[width=8cm]{FIGURES/Barkley_figure.png}
$$

 \ssp It has been remarked that stability analysis of the {\em mean flow} obtained by time-averaging the limit cycle gives better predictions (Barkley, Leontini,...).

\ssp

  => Objective of nonlinear stability approaches : Give a rigourous ground to study the stability of mean flow.

\end{frame}

\begin{frame}{Weakly nonlinear approach {\small (Sipp \& Lebedev, 2007)}}

Starting point : weakly non-linear expansion, with multiple scale method.

$$
\epsilon : \frac{1}{Re_c} - \frac{1}{Re} ; \quad \tau = \epsilon^2 t
$$

\begin{eqnarray}
{\bf u} &=& {\bf u}_{bc} + \epsilon \left[ A_{wnl} (\tau) \hat{\bf u} e^{i \omega_c t} + c.c. \right] \label{WNL1}\\
&+& \epsilon^2 \left[ {\bf u}_\epsilon + |A_{wnl}|^2  {\bf u}_{2,0} + \left(  A_{wnl}^2 {\bf u}_{2,2} e^{2 i \omega_c t} + c.c. \right) \right] + {\cal O}( \epsilon ^3)
\nonumber
\end{eqnarray}

\end{frame}

\begin{frame}{Self-Consistent approach {\small (Mantic-Lugo, Arratia \& Gallaire, 2014)}}

Starting point : Pseudo-eigenmode decomposition

\end{frame}

\begin{frame}{Harmonic-Balance}

\end{frame}

\end{document}

### 2018-07-17 99_Documentation/MANUAL/03_Previous_Note.tex
Reorganization of the base

\section*{Previous Note}

\ti{StabFem} is a software to perform Global Stability calculations in Fluid Mechanics, which is developed for both research and education purposes. It can be downloaded at \url{https://github.com/erbafdavid/StabFem}. Additionally, one will previously need to install \ti{Matlab} and \ti{FreeFem++} on the running system. For now, \ti{StabFem} works perfectly in \ti{Ubuntu16.06}. On other Operating Systems, it's not sure that it will work.

This document is a collaboration of different people and is intended to explain, the best way possible, the different parts of \textit{StabFem}. Perhaps as the reader will read it, some chapters are uncompleted or complicated to understand. The reader is invited to contribute in order to render the documentation more understandable.

### 2018-07-17 ACOUSTICS_PIPES/SCRIPT_DEMO_ACOUSTIQUE.m

@@ -1,79 +1,0 @@
-% initialisation
-clear all
-close all
-
-SF_Start
-%####
-disp('Etape 1 : construction d''un maillage');
-%####
-
-% construction d'un maillage
-bf = SF_Init('Mesh_1.edp');
-
-% pour tracer le maillage : (peut prendre du temps...)
-%plotFF(bf,'mesh');
-
-%disp('Appuyez sur entree pour la suite...')
-%pause; 
- 
-%####
-disp('Etape 2 : resolution d''un pb force pour une valeur de k');
-%#### 
- 
-% calcul d'un champ acoustique pour une valeur de k
-AC = SF_Acoustic(bf,'k',0.1)
-
-% trac? de la structure du champ acoustique
-plotFF(AC,'Phi');
-
-
-% pour tracer Phi*r on peut faire : 
-% AC.R = sqrt(AC.mesh.X.^2+AC.mesh.Y.^2);
-% AC.PhiR = AC.Phi*AC.R;
-% plotFF(AC,'PhiR')
-
-% Pour tracer u et p sur l'axe :
-  figure(2);
-  plot(AC.Xaxis,real(AC.Paxis),'r-',AC.Xaxis,imag(AC.Paxis),'r--',...
-               AC.Xaxis,real(AC.Uaxis),'b-',AC.Xaxis,imag(AC.Uaxis),'b--');
-           title('Pressure and velocity along the axis ')
-           legend('Re(P)', 'Im(P)','Re(U)','Im(U)'); 
-  
-
-% Remarque : on peut directement faire le calcul et les trac?s avec 
-% la commande suivante :
-% AC = SF_Acoustic(bf,'k',0.1,'plotPhi','yes','plotaxis','yes')
-
-% Calcul de l'impedance pour plusieurs valeurs de k
-
-disp('Appuyez sur entree pour la suite...')
-pause; 
-
-%###
-disp('Etape 3 : boucle sur k pour trace de l''impedance');
-%### 
- 
-IMP = SF_Acoustic_Impedance(bf,'k',[0:.01:2])
-
-% trace de Z(k) parties reelles et imaginaires
-figure(3);
-plot(IMP.k,real(IMP.Z),'b',IMP.k,imag(IMP.Z),'b--');
-title('Impedance : real and imaginary parts')
-xlabel('k'); ylabel('Z_r,Z_i')
-pause(0.1);
-
-% trace de |Z(k)| en semilog
[…]

### 2018-07-17 ACOUSTICS_PIPES/SF_Acoustic.m

@@ -1,28 +1,0 @@
-function AC = SF_Impedance(baseflow,varargin)
-global ff ffdir ffdatadir sfdir verbosity
-%%% management of optionnal parameters
-    p = inputParser;
-    addParameter(p,'k',0.1);
-    addParameter(p,'plotPhi','no');
-    addParameter(p,'plotaxis','no');
-    parse(p,varargin{:});
-    
-    solvercommand = ['echo ' num2str(p.Results.k) ' | ' ff  ' FF_Acoustic.edp'];
-        status = mysystem(solvercommand);
-              
-        
-    AC=importFFdata(baseflow.mesh,'AcousticField.ff2m');
-    
-   if ( strcmp(p.Results.plotPhi,'yes')  ==1)
-           plotFF(AC,'Phi');
-   end
-   
-    if ( strcmp(p.Results.plotaxis,'yes')  ==1)
-           plot(AC.Xaxis,real(AC.Paxis),'r-',AC.Xaxis,imag(AC.Paxis),'r--',...
-               AC.Xaxis,real(AC.Uaxis),'b-',AC.Xaxis,imag(AC.Uaxis),'b--');
-           title('Pressure and velocity along the axis ')
-           legend('Re(P)', 'Im(P)','Re(U)','Im(U)'); 
-   end
-   
-   
-   

### 2018-07-17 ACOUSTICS_PIPES/SF_Start.m

@@ -1,31 +1,0 @@
-global ff ffdir ffdatadir sfdir verbosity
-
-
-
-if(isunix)
-    ff =  '/usr/local/bin/FreeFem++';   % on most systems, including the server AZTECA (UPS)
-    %ff = '/PRODCOM/FREEFEM/Ubuntu12.04/3.29/bin/FreeFem++-nw'; % on IMFT network
-end
-
-if(ismac)
-    ff =  '/usr/local/bin/FreeFem++'; % on most mac instalations
-    %ff = '/usr/local/ff++/openmpi-2.1/3.55/bin/FreeFem++-nw'; % on DF's macbookpro 
-end
-   
-
-if(ispc)
-    ff = 'launchff++'; % for windows systems
-end
-
-
-ffdatadir = './';
-%sfdir = '/Users/dfabre/StabFem/SOURCES_MATLAB/'; % where to find the matlab drivers
-sfdir = './';
-ffdir = './'; % where to find the freefem scripts
-verbosity = 5;
-%addpath(sfdir);
-%if(exist(ffdatadir)~=7)
-%    mysystem(['mkdir ' ffdatadir]);
-%end
-mysystem(['echo "// File automatically created by StabFem" > SF_Geom.edp']); 
-% a file SF_Geom should be present, even if blank 

### 2018-07-17 ACOUSTICS_PIPES/mysystem.m

@@ -1,34 +1,0 @@
-
-function status=mysystem(command,errormessage);
-global ff ffdir ffdatadir sfdir verbosity
-
-%%% system command managements of StabFem.
-%
-% usage : 
-% status=mysystem(command,errormessage);
-%   -> execute the command ; displays the errormessage if fails
-%   special cases : 
-%    mysystem(command) -> will generate errormessage automatically 
-%    mysystem(command,'skip') -> will ignore the error and continue
-%                       (useful for cp/mv/rm file manipulations)
-%
-%global parameter verbosity will manage the verbosity
-
-
-if(nargin==1)
-    errormessage=['mysystem Error while calling ',command];
-end
-    
-
-if(verbosity<10) % quiet mode
-[status,result]=system(command);
-    if(status~=0)&&(strcmp(errormessage,'skip')==0)  
-        result
-        error(errormessage);
-    end
-else % verbose mode
- [status]=system(command)
-    if(status~=0)&&(strcmp(errormessage,'skip')==0)
-        error(errormessage);
-    end   
-end

### 2018-07-17 ACOUSTICS_PIPES/plotFF.m

@@ -1,102 +1,0 @@
-function handle = plotFF(FFdata,field1,varargin);
-%  function plotFF
-%  plots a data field imported from freefem using pdeplot command from
-%  toolbox pdetools
-%  Usage : 
-%  1/ handle=plotFF(mesh); (if mesh is a mesh object)
-%  2/ handle=plotFF(ffdata,'field'); to plot isocontours of a P1 field
-%  3/ handle=plotFF(ffdata,'field.re'); to plot isocontours of a P1 complex
-%  field (specify '.re' or '.im')
-%  4/ handle=plotFF(ffdata,'field',[PARAM,VALUE,..])
-%      where [PARAM,VALUE] is any couple of parameters accepted by pdeplot.
-%       (help pdeplot for a list of possibilities)
-%
-%  FFdata is the structure containing the data to plot
-%  field is the field to plot (the data may comprise multiple fields)
-%  normalisation (optional) is used to plot real(field/normalisation)
-%  (may be useful, for instance, to plot re/im parts of a complex field)
-
-
-global ff ffdir ffdatadir sfdir verbosity
-
-handle = figure();
-%handle = gcf;
-
-% single-input mode (to plot mesh)
-if(nargin==1)
-    field1 = 'mesh';
-end
-
-% two-input mode (to plot a field, real or complex)
-if(strcmp(field1,'mesh')==0)
-   [dumb,field,suffix] = fileparts(field1); % to extract the suffix
-   mesh=FFdata.mesh;
-   if(strcmp(suffix,'.im')==1)
-        data = imag(getfield(FFdata,field));
-   else
-        data = real(getfield(FFdata,field));
-   end
-end
-
-if(strcmp(field1,'mesh')~=1)
- 
-axes1 = axes('Parent',handle);
-box(axes1,'on');
-hold(axes1,'all');
-if(any(strcmp('plottitle',fieldnames(FFdata)))) 
-    title(FFdata.plottitle) 
-end
-%pdemesh(mesh.points,mesh.seg,mesh.tri) ;
-
-
-if(any(cellfun(@(x) isequal(x, 'Contour'), varargin))&&(length(FFdata.mesh.seg)==1))
-mydisp(2,'PlotFF : Reconstructing seg array for contour plots');
[…]

### 2018-07-17 ARTICLE_STABFEM/SCRIPT_CYLINDER_Part1.m

@@ -1,29 +1,0 @@
-bf = SF_Init('Mesh_Cylinder_Large.edp');
-bf = SF_BaseFlow(bf,'Re',1);
-bf = SF_BaseFlow(bf,'Re',10);
-bf = SF_BaseFlow(bf,'Re',60);
-bf = SF_Adapt(bf,'Hmax',10,'InterpError',0.01);
-[ev,em] = SF_Stability(bf,'shift',0.04+0.74i,'type','S')
-bf = SF_Adapt(bf,em,'Hmax',10,'InterpError',0.01);
-plotFF(bf,'mesh');  % Figure 2a
-plotFF(bf,'ux','Contour','on','Levels', [0,0] ); % Figure 2b
-
-Re_Range = [2 : 2: 50]; Drag_tab = []; Lx_tab = [];
-    for Re = Re_Range
-        bf = SF_BaseFlow(bf,'Re',Re);
-        Drag_tab = [Drag_tab,bf.Drag];
-        Lx_tab = [Lx_tab,bf.Lx];
-    end
-plot(Re_Range,Drag_tab,'b+-'); %Figure 3a 
-plot(Re_Range,Lx_tab,'b+-'); % Figure 3b
-
-Re_Range = [40 : 2: 100];lambda_branch=[];
-bf=SF_BaseFlow(bf,'Re',40);
-[ev,em] = SF_Stability(bf,'shift',-.03+.72i,'nev',1,'type','D');
-    for Re = Re_Range
-        bf = SF_BaseFlow(bf,'Re',Re);
-        [ev,em] = SF_Stability(bf,'nev',1,'shift','cont');
-        lambda_branch = [lambda_branch ev];
-    end
-plot(Re_Range,real(lambda_branch),'b+-'); %Figure 4a
-plot(Re_Range,imag(lambda_branch)/(2*pi),'b+-'); % Figure 4b

### 2018-07-17 BIRDCALL_Ercoftac/SCRIPT_BirdCall_Linear.m

@@ -1,143 +1,0 @@
-
-%% CHAPTER O : initialisations
-
-run('../SOURCES_MATLAB/SF_Start.m');
-verbosity=10;
-ffdatadir = './DATA_SF_BIRDCALL_ERCOFTAC/';
-
-%% Chapter 1 : generation of a mesh
-
-Re = 1000; % Reference value for the robust mesh generation
-
-    disp('computing base flow and adapting mesh')
-
-disp('generating base flow and mesh')
-bf = SF_Init('Mesh_BirdCall.edp'); %% this is the mesh from Benjamin/Raffaele
-%figure();plotFF(bf,'mesh','xlim',[-1 5],'ylim',[0 4]);
-ReTab = [10 100 200 300 400 600 700 800 900 1000]
-for Re = ReTab
-    bf = SF_BaseFlow(bf,'Re',Re);
-    if(Re>100) 
-        bf = SF_Adapt(bf,'Hmax',.5);
-    end
-end
-
- 
-[ev,em] = SF_Stability(bf,'m',0,'shift',0.9 + 5.76i,'nev',1,'type','D');
-bf=SF_Adapt(bf,em,'Hmax',.5); 
-[ev,em] = SF_Stability(bf,'m',0,'shift',0.9 + 5.76i,'nev',1,'type','D');
-bf=SF_Adapt(bf,em,'Hmax',.5); 
-
-
-%% Chapter 1b : figures
-
-figure();plotFF(bf,'mesh','xlim',[-1 5],'ylim',[0 4]);
-figure();plotFF(bf,'ux','xlim',[-1 5],'ylim',[0 4]); 
-
-%% 1C : spectrum exploration
-ev = SF_Stability(bf,'m',0,'shift',2 + 5i,'nev',20,'type','D');
-figure();plot(real(ev),imag(ev),'xr');title('spectrum for Re=1000');hold on;
-ev = SF_Stability(bf,'m',0,'shift',2 + 9i,'nev',20,'type','D');
-plot(real(ev),imag(ev),'xr');title('spectrum for Re=1000');hold on;
-
-%% CHAPTER 2 : stability branches
-
-% first one  
-% Benjamin :    0.4837 + 3.5115i (St = 0.55) 
-%   Ercoftac:
-%guess1 = 0.480839 + 3.51013i;
-% now :
-guess1 = 0.4512 + 3.5440i;
-
-
-%second one : 
[…]

### 2018-07-17 BIRDCALL_Ercoftac/SCRIPT_BirdCall_WNL_Branch2.m

@@ -1,93 +1,0 @@
-
-
-guess2 = -0.0229848+5.39569i
-
-
-
-Re_Range = [400 408 409 410 420 430 440 450];
-  
- %if(exist('DP0_Branch')==0)% to save time if already computed
-     DP0_Branch = [];
-     EVW = [];  
-    [ev,em] = SF_Stability(bf,'m',0,'shift',guess2,'nev',1);
-    for Re = Re_Range
-        bf=SF_BaseFlow(bf,'Re',Re);
-        DP0_Branch = [DP0_Branch,bf.Pup]
-        if(Re==Re_Range(1)) shift = guess2; else shift = 'cont'; end;
-        [ev,em] = SF_Stability(bf,'m',0,'shift',shift,'nev',1);
-        if(em.iter~=-1) EVW = [EVW ev]; else break; end;
-    end
- %end
- 
- figure(3);
-    plot(Re_Range,DP0_Branch);
-    title('Pressure drop across the whistle as function of Re');
-    
-
-%    if(exist('EV2')==0)
-%        EV2 = SF_Stability_LoopRe(bf,Re_Range,0,guess2,1,'Branch2.dat');
-%    end
-
-    
-    figure(4);
-    subplot(2,1,1);
-    plot(Re_Range,real(EV2),'-*b');%,Re_Range,real(EV1),'-*g')
-    title('growth rate Re(sigma) vs. Reynolds ; mode 1 (red) and mode 2 (blue)')
-    subplot(2,1,2);
-    plot(Re_Range,imag(EV2)/(2*pi),'-*b');%,Re_Range,imag(EV3)/(2*pi),'-*g')%,Re_Range,imag(EVI),'-*r')
-    title('Strouhal vs. Reynolds');
-    
-    
-
-pause(0.1);
-
-%%% WEAKLY NONLINEAR ANALYSIS AT THE THRESHOLD
-
-
-Rec = 408.56;
-bf = SF_BaseFlow(bf,'Re',Rec)
-
-%if(exist('emA')==0)
-    bf = SF_BaseFlow(bf,'Re',Rec)
-    [ev,em] = SF_Stability(bf,'Re',Rec,'m',0,'shift',5.39374i,'nev',1,'type','S');
-    %bf.sensitivity = abs(em.ux1).*abs(emA.ux1)+abs(em.ur1).*abs(emA.ur1);
-    plotFF(bf,'sensitivity');
-%end
-%if(exist('wnl')==0)
[…]

### 2018-07-17 CASES_DEVELOPMENT/BIRDCALL_Ercoftac/SCRIPT_BirdCall_WNL_Branch2.m

@@ -1,0 +1,93 @@
+
+
+guess2 = -0.0229848+5.39569i
+
+
+
+Re_Range = [400 408 409 410 420 430 440 450];
+  
+ %if(exist('DP0_Branch')==0)% to save time if already computed
+     DP0_Branch = [];
+     EVW = [];  
+    [ev,em] = SF_Stability(bf,'m',0,'shift',guess2,'nev',1);
+    for Re = Re_Range
+        bf=SF_BaseFlow(bf,'Re',Re);
+        DP0_Branch = [DP0_Branch,bf.Pup]
+        if(Re==Re_Range(1)) shift = guess2; else shift = 'cont'; end;
+        [ev,em] = SF_Stability(bf,'m',0,'shift',shift,'nev',1);
+        if(em.iter~=-1) EVW = [EVW ev]; else break; end;
+    end
+ %end
+ 
+ figure(3);
+    plot(Re_Range,DP0_Branch);
+    title('Pressure drop across the whistle as function of Re');
+    
+
+%    if(exist('EV2')==0)
+%        EV2 = SF_Stability_LoopRe(bf,Re_Range,0,guess2,1,'Branch2.dat');
+%    end
+
+    
+    figure(4);
+    subplot(2,1,1);
+    plot(Re_Range,real(EV2),'-*b');%,Re_Range,real(EV1),'-*g')
+    title('growth rate Re(sigma) vs. Reynolds ; mode 1 (red) and mode 2 (blue)')
+    subplot(2,1,2);
+    plot(Re_Range,imag(EV2)/(2*pi),'-*b');%,Re_Range,imag(EV3)/(2*pi),'-*g')%,Re_Range,imag(EVI),'-*r')
+    title('Strouhal vs. Reynolds');
+    
+    
+
+pause(0.1);
+
+%%% WEAKLY NONLINEAR ANALYSIS AT THE THRESHOLD
+
+
+Rec = 408.56;
+bf = SF_BaseFlow(bf,'Re',Rec)
+
+%if(exist('emA')==0)
+    bf = SF_BaseFlow(bf,'Re',Rec)
+    [ev,em] = SF_Stability(bf,'Re',Rec,'m',0,'shift',5.39374i,'nev',1,'type','S');
+    %bf.sensitivity = abs(em.ux1).*abs(emA.ux1)+abs(em.ur1).*abs(emA.ur1);
+    plotFF(bf,'sensitivity');
+%end
+%if(exist('wnl')==0)
[…]

### 2018-07-17 CASES_DEVELOPMENT/BLUNTBODY_IN_PIPE/SCRIPT_BLUNTBODY.m

@@ -1,0 +1,73 @@
+
+run('../SOURCES_MATLAB/SF_Start.m');
+close all;
+%ffdatadir = './WORK/'; %% to be fixed : this should be "./WORK" but some of the solvers are not yet operational
+
+Rbody = 1; Lel = 2; Lcyl = 5;Rpipe = 1.5; xmin = -10; xmax = 30;
+bctype = 1;
+
+
+    disp('computing base flow and adapting mesh');
+    bf = SF_Init('meshInit_BluntBodyInTube.edp',[Rbody Lel Lcyl Rpipe xmin xmax bctype]); 
+    Re_start = [10 , 30, 60, 100 , 200]; % values of Re for progressive increasing up to end
+    for Rei = Re_start
+        bf=SF_BaseFlow(bf,'Re',Rei); 
+        bf=SF_Adapt(bf,'Hmax',0.5);
+    end
+ 
+ shift =    0.15+1.098i; % shift for steady mode
+% compute a spectrum   
+ [ev,eigenmode] = SF_Stability(bf,'m',1,'shift',shift,'nev',10,'type','D','plotspectrum','yes');   
+pause(0.1);
+ shift = ev(1);
+ 
+ 
+ % optional : adapting mesh on eigenmode structure as well      
+ [ev,eigenmode] = SF_Stability(bf,'m',1,'shift',shift,'nev',1,'type','S');
+ [bf,eigenmode]= SF_Adapt(bf,eigenmode);  
+ 
+% range for figures
+bf.mesh.xlim=[-2*Rbody,Lbody+5*Rbody]; %x-range for plots
+bf.mesh.ylim=[0,Rpipe];
+
+plotFF(bf,'mesh'); % to plot the mesh
+bf.mesh.xlim=[-2*Rbody,Lbody+5*Rbody]; %x-range for plots
+bf.mesh.ylim=[0,Rpipe];
+plotFF(bf,'ux');  % to plot the bf
+pause(0.1);
+
+%% COMPUTING THE UNSTEADY BRANCH (going backwards)
+    Re_RangeI = [200:-10:100];EVI = [];
+        guessI = 1.09i+0.157;
+        bf=SF_BaseFlow(bf,'Re',200);
+        [ev,em] = SF_Stability(bf,'m',1,'shift',guessI,'nev',1,'type','D');
+        for Re = Re_RangeI
+        bf = SF_BaseFlow(bf,'Re',Re);
[…]

### 2018-07-17 CASES_DEVELOPMENT/CYLINDER_BIS/SCRIPT_CYLINDER_DEMO.m

@@ -1,0 +1,234 @@
+%  Instability of the wake of a cylinder with STABFEM  
+%
+%  this script demonstrates the main fonctionalities of StabFem for the
+%  reference case of the wake of a cylinder.
+%  1/ Generation of an adapted mesh 
+
+%  3/ Stability curves St(Re) and sigma(Re) for Re = [40-100]
+%  4/ Determination of the instability threshold and Weakly-Nonlinear
+%  analysis
+%  5/ Harmonic-Balance for Re = REc-100
+%  6/ Self-consistent model for Re=100
+
+% CHAPTER 0 : set the global variables needed by the drivers
+
+
+run('../SOURCES_MATLAB/SF_Start.m');
+figureformat='png'; AspectRatio = 0.56; % for figures
+verbosity = 10; % to follow what's going on...
+
+%##### CHAPTER 1 : COMPUTING THE MESH WITH ADAPTMESH PROCEDURE
+
+
+if(exist('mesh_completed')==0)
+disp('generation of a mesh : ')    
+bf=SF_Init('Mesh_Cylinder.edp',[-40 80 40]);
+bf=SF_BaseFlow(bf,'Re',1);
+bf=SF_BaseFlow(bf,'Re',10);
+bf=SF_BaseFlow(bf,'Re',60);
+bf=SF_Adapt(bf,'Hmax',5);
+bf=SF_Adapt(bf,'Hmax',5);
+disp(' ');
+
+disp('mesh adaptation to MODE : ')
+[ev,em] = SF_Stability(bf,'shift',0.04+0.76i,'nev',1,'type','D');
+[bf,em]=SF_Adapt(bf,em,'Hmax',10);
+mesh_completed = 1;
+end
+
+
+
+
+%%% CHAPTER 2 : determining instability threshold
+
+if(exist('Rec')==1)
+    disp('INSTABILITY THRESHOLD ALREADY COMPUTED');
+    bf=SF_BaseFlow(bf,'Re',Rec);
+    [ev,em] = SF_Stability(bf,'shift',em.lambda,'type','S','nev',1);
+else 
+%%% DETERMINATION OF THE INSTABILITY THRESHOLD
+disp('COMPUTING INSTABILITY THRESHOLD');
+bf=SF_BaseFlow(bf,'Re',50);
[…]

### 2018-07-17 CASES_DEVELOPMENT/CYLINDER_BIS/SCRIPT_CYLINDER_WNL.m

@@ -1,0 +1,44 @@
+
+verbosity = 11;
+
+%%% CHAPTER 4 : determination of critical reynolds number
+
+if(exist('Rec')==1)
+    disp('INSTABILITY THRESHOLD ALREADY COMPUTED');
+else 
+%%% DETERMINATION OF THE INSTABILITY THRESHOLD
+disp('COMPUTING INSTABILITY THRESHOLD');
+bf=SF_BaseFlow(bf,'Re',50);
+[ev,em] = SF_Stability(bf,'shift',+.75i,'nev',1,'type','S');
+[bf,em]=SF_FindThreshold(bf,em);
+Rec = bf.Re;  Cxc = bf.Cx; 
+Lxc=bf.Lx;    Omegac=imag(em.lambda);
+
+end
+
+bf=SF_BaseFlow(bf,Rec);
+[ev,em] = SF_Stability(bf,'shift',em.lambda,'type','S','nev',1);
+wnl = SF_WNL(bf);
+
+epsilon2_WNL = -0.003:.0001:.005; % will trace results for Re = 40-55 approx.
+Re_WNL = 1./(1/Rec-epsilon2_WNL);
+A_WNL = sqrt(real(wnl.Lambda)/real(wnl.nu0+wnl.nu2))*real(sqrt(epsilon2_WNL));
+Cy_WNL = abs(em.Cy)/sqrt(em.Energy)*A_WNL; 
+omega_WNL =Omegac+epsilon2_WNL*imag(wnl.Lambda)-imag(wnl.nu0+wnl.nu2)*A_WNL.^2;
+%omega_WNLno2 =Omegac+epsilonRANGE.*(imag(wnl.Lambda)-real(wnl.Lambda)*imag(wnl.nu0)/real(wnl.nu0));
+Cx_WNL = wnl.Cx0+wnl.Cxeps*epsilon2_WNL+wnl.Cx20*A_WNL.^2;
+
+figure(20);hold on;
+plot(Re_WNL,real(wnl.Lambda)*epsilon2_WNL,'g--');hold on;
+
+figure(21);hold on;
+plot(Re_WNL,omega_WNL/(2*pi),'g--');hold on;
+
+figure(22);hold on;
+plot(Re_WNL,Cx_WNL,'g--');hold on;
+
+figure(24); hold on;
+plot(Re_WNL,Cy_WNL,'g--');
+
+figure(25);hold on;
+plot(Re_WNL,A_WNL,'g--');

### 2018-07-17 CASES_DEVELOPMENT/CYLINDER_VIV/FreeFem_HarmonicForcing.m

@@ -1,0 +1,27 @@
+function [Omegatab,Ltab,Mtab] = FreeFem_HarmonicForcing(baseflow);
+
+%% 
+%NB THIS IS VERY UGLY PROGRAMMING, TO BE REWRITTEN SOMEDAY
+%
+%%
+
+
+global ff ffdir ffdatadir sfdir verbosity
+
+
+file = ['HARMONIC_2D_LateralOscillations_Re', num2str(baseflow.Re),'.txt']
+if(exist(file)==2)
+    disp('already computed')
+else
+    disp('computing')
+    system([ ff ' Harmonic_2D_LateralOscillations.edp'])
+end
+
+
+rawData1 = importdata(file)
+Omegatab= rawData1(:,1);
+Ltab = rawData1(:,3)+1i*rawData1(:,4);
+Mtab = rawData1(:,5)+1i*rawData1(:,6);
+end
+
+

### 2018-07-17 CASES_DEVELOPMENT/POROUS_ROTATING_DISK/SCRIPT_POROUS_ROTATING_DISK.m

@@ -1,0 +1,169 @@
+%%####################################################################
+%  STAGE IMFT                                        Adrien Rouviere
+%               -- ANALYSE DE STABILITÉ GLOBALE --
+%           -- ÉCOULEMENT AUTOUR D'UN DISQUE POREUX --
+%                                                   
+%#####################################################################
+
+clear all;
+close all;
+clc
+
+%% 0 - Préchauffage
+
+run('../SOURCES_MATLAB/SF_Start.m');
+
+ffdatadir = 'WORK/'; %% to be fixed : this should be "./WORK" but some of the solvers are not yet operational
+figureformat = 'png';
+
+verbosity = 100;
+
+%% 1 - Génération MAILLAGE et BASEFLOW
+
+Rx = 3;
+
+% Géométrie
+Rayon = 1;
+    DIAMETER = num2str(2*Rayon);
+Epaisseur = 1/(2*Rx);
+    THICKNESS = num2str(Epaisseur);
+Xmin = -20*Rayon;
+    XMIN = num2str(Xmin);
+Xmax = 50*Rayon;
+    XMAX = num2str(Xmax);
+Ymax = 20*Rayon;
+    YMAX = num2str(Ymax);
+
+boxx = [-Epaisseur/2, Epaisseur/2, Epaisseur/2, -Epaisseur/2, -Epaisseur/2];
+boxy = [0, 0, Rayon, Rayon, 0];
+
+it=0;
+baseflow=SF_Init('mesh_Disk.edp',[DIAMETER ' ' THICKNESS ' ' XMIN ' ' XMAX ' ' YMAX]);
+
+% Plot mesh initial
+% baseflow.xlim = [Xmin Xmax]; baseflow.ylim=[0,Ymax];
+baseflow.xlabel=('x');baseflow.ylabel=('r');
+baseflow.plottitle = ['Maillage initial du domaine de calcul'];
+plotFF(baseflow,'mesh');
+hold on;fill(boxx,boxy,'y','FaceAlpha', 0.3);hold off;
+
+%% 2 - Génération du BASEFLOW pour un certain Re
+
+% Paramètres de calcul
+Re_start = [10:50:1000];
+Omega = [0.];
+Darcy = [1e-1];
+Porosite = [1];
+
+    it=1;
+    for Re = Re_start
+        tic;
[…]

### 2018-07-17 CASES_STABLE/ACOUSTICS_PIPES/importFFmesh.m

@@ -1,0 +1,158 @@
+function meshstruct = importFFmesh(fileToRead1,opt)
+global ff ffdir ffdatadir sfdir verbosity
+
+%  function importFFmesh
+%  Imports mesh generated by freefem 
+%  Usage : 
+% 1/ mesh=importFFmesh(fileToRead1) -> imports information for points & triangles
+% 2/ mesh=importFFmesh(fileToRead1,'seg') -> imports information for points, triangles & SEGMENTS (VERY INEFFICIENT, SHOULD BE IMPROVED)
+%
+% FileToRead1 is typically of the form "mesh.msh".
+% The program will also need files "mesh.ff2m" and "SF_Init.ff2m"
+%
+%  This program is adapted from FreeFem_to_matlab, copyright Julien Dambrine 2010 ; 
+%  modified by D. Fabre (2017)
+
+
+% Check for the mesh file which should be in the ffdatadir directory
+if(exist([ffdatadir,fileToRead1])==2) 
+    fileToRead1 = [ffdatadir,fileToRead1]; % normally the file should be in "ffdatadir" directory
+end
+
+
+%First, read auxiliary files "mesh.ff2m" and "SF_Init.ff2m"
+[filepath,name,ext] = fileparts(fileToRead1);
+fileToRead2 = [filepath,'/',name,'.ff2m'];
+fileToRead3 = [filepath,'/SF_Init.ff2m'];
+
+mydisp(2,['FUNCTION  importFFmesh.m : reading complementary files']);
+    
+meshstruct = importFFdata(fileToRead2,fileToRead3);
+
+% change the field "datatype" to "problemtype"
+meshstruct.problemtype = meshstruct.datatype;
+meshstruct = rmfield(meshstruct,'datatype');
+
+%
+meshstruct.meshgeneration=0;
+
+%Secondly, reading mesh file
+
+rawData1 = importdata(fileToRead1);
+mydisp(2,['FUNCTION  importFFmesh.m : reading file ' fileToRead1 ]);
+
+% For some simple files (such as a CSV or JPEG files), IMPORTDATA might
+% return a simple array.  If so, generate a structure so that the output
+% matches that from the Import Wizard.
+[unused,name] = fileparts(fileToRead1);
[…]

### 2018-07-17 CASES_STABLE/CYLINDER/SCRIPT_CYLINDER_WNL.m

@@ -1,0 +1,44 @@
+
+verbosity = 11;
+
+%%% CHAPTER 4 : determination of critical reynolds number
+
+if(exist('Rec')==1)
+    disp('INSTABILITY THRESHOLD ALREADY COMPUTED');
+else 
+%%% DETERMINATION OF THE INSTABILITY THRESHOLD
+disp('COMPUTING INSTABILITY THRESHOLD');
+bf=SF_BaseFlow(bf,'Re',50);
+[ev,em] = SF_Stability(bf,'shift',+.75i,'nev',1,'type','S');
+[bf,em]=SF_FindThreshold(bf,em);
+Rec = bf.Re;  Cxc = bf.Cx; 
+Lxc=bf.Lx;    Omegac=imag(em.lambda);
+
+end
+
+bf=SF_BaseFlow(bf,Rec);
+[ev,em] = SF_Stability(bf,'shift',em.lambda,'type','S','nev',1);
+wnl = SF_WNL(bf,em);
+
+epsilon2_WNL = -0.003:.0001:.005; % will trace results for Re = 40-55 approx.
+Re_WNL = 1./(1/Rec-epsilon2_WNL);
+A_WNL = sqrt(real(wnl.Lambda)/real(wnl.nu0+wnl.nu2))*real(sqrt(epsilon2_WNL));
+Cy_WNL = abs(em.Cy)/sqrt(em.Energy)*A_WNL; 
+omega_WNL =Omegac+epsilon2_WNL*imag(wnl.Lambda)-imag(wnl.nu0+wnl.nu2)*A_WNL.^2;
+%omega_WNLno2 =Omegac+epsilonRANGE.*(imag(wnl.Lambda)-real(wnl.Lambda)*imag(wnl.nu0)/real(wnl.nu0));
+Cx_WNL = wnl.Cx0+wnl.Cxeps*epsilon2_WNL+wnl.Cx20*A_WNL.^2;
+
+figure(20);hold on;
+plot(Re_WNL,real(wnl.Lambda)*epsilon2_WNL,'g--');hold on;
+
+figure(21);hold on;
+plot(Re_WNL,omega_WNL/(2*pi),'g--');hold on;
+
+figure(22);hold on;
+plot(Re_WNL,Cx_WNL,'g--');hold on;
+
+figure(24); hold on;
+plot(Re_WNL,Cy_WNL,'g--');
+
+figure(25);hold on;
+plot(Re_WNL,A_WNL,'g--');

### 2018-07-17 CASES_STABLE/CYLINDER/untitled.m

@@ -1,0 +1,52 @@
+
+Mesh 6
+
+0.65048; Lx = 4.1097
+Eigenvalue : 0.048335+0.74989i
+
+mean Fx : 0.69988
+mean Lx : 2.6014
+Mode Fy : 0.066093+1.7347e-18i
+Mode AE : 1.7019
+Mode omega : 0.85032
+
+Mesh 7
+
+2292
+
+Fx = 0.64046; Lx = 4.0618
+
+0.046081+0.74286i
+
+mean Fx : 0.68924
+mean Lx : 2.6188
+Mode Fy : 0.063154+6.0715e-18i
+Mode AE : 1.6892
+Mode omega : 0.84042
+
+
+Mesh 8
+
+ Fx = 0.6459; Lx = 4.0701
+ 
+number of vertices : 2026
+
+0.047017+0.7479i
+
+mean Fx : 0.69492
+mean Lx : 2.6127
+Mode Fy : 0.06418+8.6736e-19i
+Mode AE : 1.7154
+Mode omega : 0.84613
+
+mesh 9
+
+Fx = 0.64557; Lx = 4.0677
+ 
+number of vertices : 2043
+
+mean Fx : 0.69429
+mean Lx : 2.6152
+Mode Fy : 0.063854-3.4694e-18i
+Mode AE : 1.7004
+Mode omega : 0.84562

### 2018-07-17 CASES_STABLE/ELLIPT_BLUNTBODY_IN_PIPE/C5_E2_Rp10.m

@@ -1,0 +1,74 @@
+clear all
+
+%Mes données%
+
+C6=load('DATA_THRESHOLDS/dataC5_E2_Rp1000LD600.txt');
+C4=load('DATA_THRESHOLDS/dataC5_E2_Rp1000LD400.txt');
+C3=load('DATA_THRESHOLDS/dataC5_E2_Rp1000LD300.txt');
+C2=load('DATA_THRESHOLDS/dataC5_E2_Rp1000LD200.txt');
+C1=load('DATA_THRESHOLDS/dataC5_E2_Rp1000LD104.txt');
+
+MM=[C1;C2;C3;C4;C6];
+
+
+plot(MM(find(MM(:,1)==2),4),MM(find(MM(:,1)==2),5),'ro')
+
+
+hold on
+
+plot(MM(find(MM(:,1)==1),4),MM(find(MM(:,1)==1),5),'bv')
+
+
+%Jimenez 3D%
+
+JIMENEZ_X=[1 2];
+JIMENEZ_RECS=[215 319];
+JIMENEZ_RECI=[254 413];
+
+plot(JIMENEZ_X,JIMENEZ_RECI,'k+')
+plot(JIMENEZ_X,JIMENEZ_RECS,'ks')
+
+
+
+%Jimenez 2D
+
+
+J_CI=load('DATA_THRESHOLDS/Jimenez_Globalstability_CI.txt');
+
+x = J_CI(:,1);
+y = J_CI(:,2);
+xx = 1:0.1:9;
+yy = spline(x,y,xx);
+plot(xx,yy,'k:')
+
+J_CS=load('DATA_THRESHOLDS/Jimenez_Globalstability_CS.txt');
+
+x = J_CS(:,1);
+y = J_CS(:,2);
+xx = 1:0.1:9;
+yy = spline(x,y,xx);
+plot(xx,yy,'k--')
+
+
+x = MM(find(MM(:,1)==2),4);
+y = MM(find(MM(:,1)==2),5);
+xx = 1:0.1:6;
+yy = spline(x,y,xx);
+plot(xx,yy,'r')
+
+
+x = MM(find(MM(:,1)==1),4);
+y = MM(find(MM(:,1)==1),5);
+xx = 1:0.1:6;
+yy = spline(x,y,xx);
+plot(xx,yy,'b')
+
+%Titre et légende%
+title('Dependance of the critical Reynolds numbers on L/D')
+xlabel('L/D')
+ylabel('Re')
+axis([0 11 0 1500])
[…]

### 2018-07-17 CASES_STABLE/ELLIPT_BLUNTBODY_IN_PIPE/SCRIPTS/C1_E2_Rp0-70_LD6.m

@@ -1,0 +1,209 @@
+clear all
+format shortG
+
+
+run('/Users/theomouyen/Documents/GitHub/StabFem/SOURCES_MATLAB/SF_Start.m');
+close all;
+
+%ffdatadir = './WORK/'; %% to be fixed : this should be "./WORK" but some of the solvers are not yet operational
+
+%%% PARAMETRES
+
+Rbody = 0.5; Lel = 1; Lcyl = 5;Rpipe = 0.70; xmin = -10; xmax = 100;
+
+
+Lbody=Lcyl+Lel;
+bctype = 1;
+
+Hmax = 0.25; %taille max des mailles
+n=2; %densité du méillage: voir meshInit_BluntbodyInTube.edp
+clear all
+format shortG
+
+
+run('/Users/theomouyen/Documents/GitHub/StabFem/SOURCES_MATLAB/SF_Start.m');
+close all;
+
+%ffdatadir = './WORK/'; %% to be fixed : this should be "./WORK" but some of the solvers are not yet operational
+
+%%% PARAMETRES
+
+Rbody = 0.5; Lel = 1; Lcyl = 5;Rpipe = 0.70; xmin = -10; xmax = 100;
+
+
+Lbody=Lcyl+Lel;
+bctype = 1;
+
+Hmax = 0.25; %taille max des mailles
+n=2; %densité du méillage: voir meshInit_BluntbodyInTube.edp
+
+%%% FIN PARAMETERS
+
+    disp('computing base flow and adapting mesh');
+    
+    Re_start = [10,30,60,100,200,300,400]; 
+    bf = SF_Init('meshInit_BluntBodyInTube.edp',[Rbody Lel Lcyl Rpipe xmin xmax bctype]); 
+    for Rei = Re_start
+        bf=SF_BaseFlow(bf,'Re',Rei);
+        bf=SF_Adapt(bf,'Hmax',Hmax);
+        disp(['delta min : ',num2str(bf.mesh.deltamin)]);
+        disp(['delta max : ',num2str(bf.mesh.deltamax)]);
+    end
+   
+% compute a spectrum  
+
+        bf=SF_BaseFlow(bf,'Re',500);
+        bf=SF_Adapt(bf,'Hmax',Hmax);
+
[…]

### 2018-07-17 CASES_STABLE/ELLIPT_BLUNTBODY_IN_PIPE/SCRIPTS/C1_E2_Rp0-85_LD6.m

@@ -1,0 +1,160 @@
+clear all
+format shortG
+
+
+run('/Users/theomouyen/Documents/GitHub/StabFem/SOURCES_MATLAB/SF_Start.m');
+close all;
+
+%ffdatadir = './WORK/'; %% to be fixed : this should be "./WORK" but some of the solvers are not yet operational
+
+%%% PARAMETRES
+
+Rbody = 0.5; Lel = 1; Lcyl = 5;Rpipe = 0.85; xmin = -10; xmax = 100;
+
+
+Lbody=Lcyl+Lel;
+bctype = 1;
+
+Hmax = 0.25; %taille max des mailles
+n=2; %densité du méillage: voir meshInit_BluntbodyInTube.edp
+
+%%% FIN PARAMETERS
+
+    disp('computing base flow and adapting mesh');
+    
+    Re_start = [10,30,60,100,200,300,400]; 
+    bf = SF_Init('meshInit_BluntBodyInTube.edp',[Rbody Lel Lcyl Rpipe xmin xmax bctype]); 
+    for Rei = Re_start
+        bf=SF_BaseFlow(bf,'Re',Rei);
+        bf=SF_Adapt(bf,'Hmax',Hmax);
+        disp(['delta min : ',num2str(bf.mesh.deltamin)]);
+        disp(['delta max : ',num2str(bf.mesh.deltamax)]);
+    end
+   
+% compute a spectrum  
+% 
+% %         bf=SF_BaseFlow(bf,'Re',700);
+% %          bf=SF_Adapt(bf,'Hmax',Hmax);
+%  [ev1,eigenmode1] = SF_Stability(bf,'m',1,'shift',0,'nev',10,'plotspectrum','yes');   
+%  [ev2,eigenmode2] = SF_Stability(bf,'m',1,'shift',0.4i,'nev',10,'plotspectrum','yes');   
+%  [ev3,eigenmode3] = SF_Stability(bf,'m',1,'shift',0.8i,'nev',10,'plotspectrum','yes');   
+%  [ev4,eigenmode4] = SF_Stability(bf,'m',1,'shift',1.2i,'nev',10,'plotspectrum','yes');   
+%  [ev5,eigenmode5] = SF_Stability(bf,'m',1,'shift',1.6i,'nev',10,'plotspectrum','yes');   
[…]

### 2018-07-17 CASES_STABLE/ELLIPT_BLUNTBODY_IN_PIPE/SCRIPTS/C1_E2_Rp1-05_LD6.m

@@ -1,0 +1,220 @@
+clear all
+format shortG
+
+
+run('/Users/theomouyen/Documents/GitHub/StabFem/SOURCES_MATLAB/SF_Start.m');
+close all;
+
+%ffdatadir = './WORK/'; %% to be fixed : this should be "./WORK" but some of the solvers are not yet operational
+
+%%% PARAMETRES
+
+Rbody = 0.5; Lel = 1; Lcyl = 5;Rpipe = 1.05; xmin = -10; xmax = 100;
+
+
+Lbody=Lcyl+Lel;
+bctype = 1;
+
+Hmax = 0.25; %taille max des mailles
+n=2; %densité du méillage: voir meshInit_BluntbodyInTube.edp
+
+%%% FIN PARAMETERS
+
+    disp('computing base flow and adapting mesh');
+    
+    Re_start = [10,30,60,100,200,300,400]; 
+    bf = SF_Init('meshInit_BluntBodyInTube.edp',[Rbody Lel Lcyl Rpipe xmin xmax bctype]); 
+    for Rei = Re_start
+        bf=SF_BaseFlow(bf,'Re',Rei);
+        bf=SF_Adapt(bf,'Hmax',Hmax);
+        disp(['delta min : ',num2str(bf.mesh.deltamin)]);
+        disp(['delta max : ',num2str(bf.mesh.deltamax)]);
+    end
+   
+% compute a spectrum  
+
+
+%  [ev1,eigenmode1] = SF_Stability(bf,'m',1,'shift',0,'nev',10,'plotspectrum','yes');   
+%  [ev2,eigenmode2] = SF_Stability(bf,'m',1,'shift',0.4i,'nev',10,'plotspectrum','yes');   
+%  [ev3,eigenmode3] = SF_Stability(bf,'m',1,'shift',0.8i,'nev',10,'plotspectrum','yes');   
+%  [ev4,eigenmode4] = SF_Stability(bf,'m',1,'shift',1.2i,'nev',10,'plotspectrum','yes');   
+%  [ev5,eigenmode5] = SF_Stability(bf,'m',1,'shift',1.6i,'nev',10,'plotspectrum','yes');   
[…]

### 2018-07-17 CASES_STABLE/ELLIPT_BLUNTBODY_IN_PIPE/SCRIPTS/C1_E2_Rp1-15_LD6.m

@@ -1,0 +1,221 @@
+clear all
+format shortG
+
+
+run('/Users/theomouyen/Documents/GitHub/StabFem/SOURCES_MATLAB/SF_Start.m');
+close all;
+
+%ffdatadir = './WORK/'; %% to be fixed : this should be "./WORK" but some of the solvers are not yet operational
+
+%%% PARAMETRES
+
+Rbody = 0.5; Lel = 1; Lcyl = 5;Rpipe = 1.15; xmin = -10; xmax = 100;
+
+
+Lbody=Lcyl+Lel;
+bctype = 1;
+
+Hmax = 0.25; %taille max des mailles
+n=2; %densité du méillage: voir meshInit_BluntbodyInTube.edp
+
+%%% FIN PARAMETERS
+
+    disp('computing base flow and adapting mesh');
+    
+    Re_start = [10,30,60,100,200,300,400,500,600,700,800,900]; 
+    bf = SF_Init('meshInit_BluntBodyInTube.edp',[Rbody Lel Lcyl Rpipe xmin xmax bctype]); 
+    for Rei = Re_start
+        bf=SF_BaseFlow(bf,'Re',Rei);
+        bf=SF_Adapt(bf,'Hmax',Hmax);
+        disp(['delta min : ',num2str(bf.mesh.deltamin)]);
+        disp(['delta max : ',num2str(bf.mesh.deltamax)]);
+    end
+   
+% compute a spectrum  
+%         bf=SF_BaseFlow(bf,'Re',1200);
+%         bf=SF_Adapt(bf,'Hmax',Hmax);     
+ [ev1,eigenmode1] = SF_Stability(bf,'m',1,'shift',0,'nev',10,'plotspectrum','yes');   
+ [ev2,eigenmode2] = SF_Stability(bf,'m',1,'shift',0.4i,'nev',10,'plotspectrum','yes');   
+ [ev3,eigenmode3] = SF_Stability(bf,'m',1,'shift',0.8i,'nev',10,'plotspectrum','yes');   
+ [ev4,eigenmode4] = SF_Stability(bf,'m',1,'shift',1.2i,'nev',10,'plotspectrum','yes');   
[…]

### 2018-07-17 CASES_STABLE/ELLIPT_BLUNTBODY_IN_PIPE/SCRIPTS/C1_E2_Rp10_LD6.m

@@ -1,0 +1,104 @@
+clear all
+format shortG
+
+
+run('/Users/theomouyen/Documents/GitHub/StabFem/SOURCES_MATLAB/SF_Start.m');
+close all;
+
+%ffdatadir = './WORK/'; %% to be fixed : this should be "./WORK" but some of the solvers are not yet operational
+
+%%% PARAMETRES
+
+Rbody = 0.5; Lel = 1; Lcyl = 5;Rpipe = 10; xmin = -10; xmax = 60;
+
+
+Lbody=Lcyl+Lel;
+bctype = 1;
+
+Hmax = 1; %taille max des mailles
+n=2; %densité du méillage: voir meshInit_BluntbodyInTube.edp
+
+%%% FIN PARAMETERS
+
+    disp('computing base flow and adapting mesh');
+    
+    Re_start = [10 , 30, 60, 100, 200]; 
+    bf = SF_Init('meshInit_BluntBodyInTube.edp',[Rbody Lel Lcyl Rpipe xmin xmax bctype]); 
+    for Rei = Re_start
+        bf=SF_BaseFlow(bf,'Re',Rei); 
+        bf=SF_Adapt(bf,'Hmax',Hmax);
+        disp(['delta min : ',num2str(bf.mesh.deltamin)]);
+        disp(['delta max : ',num2str(bf.mesh.deltamax)]);
+    end
+   
+% compute a spectrum  
+
+ [ev1,eigenmode1] = SF_Stability(bf,'m',1,'shift',0,'nev',10,'plotspectrum','yes');   
+
+ [ev2,eigenmode2] = SF_Stability(bf,'m',1,'shift',1i,'nev',10,'plotspectrum','yes');   
+
+ [ev3,eigenmode3] = SF_Stability(bf,'m',1,'shift',0.2+0.5i,'nev',10,'plotspectrum','yes');   
+
+ [ev4,eigenmode4] = SF_Stability(bf,'m',1,'shift',0.5,'nev',10,'plotspectrum','yes');   
+
+ [ev5,eigenmode5] = SF_Stability(bf,'m',1,'shift',0.5+0.5i,'nev',10,'plotspectrum','yes');   
+
+ [ev6,eigenmode6] = SF_Stability(bf,'m',1,'shift',0.5+2i,'nev',10,'plotspectrum','yes');   
+
[…]

### 2018-07-17 CASES_STABLE/ELLIPT_BLUNTBODY_IN_PIPE/SCRIPTS/C1_E2_Rp2.m

@@ -1,0 +1,79 @@
+clear all
+
+%Mes données%
+
+
+M1_600=load('dataC1_E2_Rp200LD600(1).txt');
+M1_400=load('dataC1_E2_Rp200LD400(1).txt');
+M1_300=load('dataC1_E2_Rp200LD300(1).txt');
+M1_200=load('dataC1_E2_Rp200LD200(1).txt');
+M1_104=load('dataC1_E2_Rp200LD104(1).txt');
+
+
+M2_600=load('dataC1_E2_Rp200LD600(2).txt');
+M2_400=load('dataC1_E2_Rp200LD400(2).txt');
+M2_300=load('dataC1_E2_Rp200LD300(2).txt');
+M2_200=load('dataC1_E2_Rp200LD200(2).txt');
+M2_104=load('dataC1_E2_Rp200LD104(2).txt');
+
+
+MM=[M1_600;M1_400;M1_300;M1_200;M1_104];
+MM2=[M2_600;M2_400;M2_300;M2_200;M2_104];
+
+%% Premier couple
+
+plot(MM(find(MM(:,1)==2),4),MM(find(MM(:,1)==2),5),'ro')
+hold on
+plot(MM(find(MM(:,1)==1),4),MM(find(MM(:,1)==1),5),'bv')
+
+
+%% Deuxième couple
+
+plot(MM2(find(MM2(:,1)==4),4),MM2(find(MM2(:,1)==4),5),'r+')
+hold on
+plot(MM2(find(MM2(:,1)==3),4),MM2(find(MM2(:,1)==3),5),'bx')
+
+
+%% Titre et légende%
+
+title('Dependance of the critical Reynolds numbers on Rp')
+xlabel('Rp')
+ylabel('Re')
+axis([0 11 0 1500])
+
+
+%% Interpolation
+
+x = MM(find(MM(:,1)==2),4);
+y = MM(find(MM(:,1)==2),5);
+xx = 1:0.1:7;
+yy = spline(x,y,xx);
+plot(xx,yy,'r')
+
+x = MM(find(MM(:,1)==1),4);
+y = MM(find(MM(:,1)==1),5);
+xx = 1:0.1:7;
+yy = spline(x,y,xx);
+plot(xx,yy,'b')
+
+
+x = MM2(find(MM2(:,1)==4),4);
+y = MM2(find(MM2(:,1)==4),5);
+xx = 1:0.1:7;
+yy = spline(x,y,xx);
+plot(xx,yy,'r')
+
+
[…]

### 2018-07-17 CASES_STABLE/ELLIPT_BLUNTBODY_IN_PIPE/SCRIPTS/C1_E2_Rp2_LD1.m

@@ -1,0 +1,120 @@
+clear all
+format shortG
+
+
+run('/Users/theomouyen/Documents/GitHub/StabFem/SOURCES_MATLAB/SF_Start.m');
+close all;
+
+%ffdatadir = './WORK/'; %% to be fixed : this should be "./WORK" but some of the solvers are not yet operational
+
+%%% PARAMETRES
+
+Rbody = 0.5; Lel = 1; Lcyl = 0.04;Rpipe = 2; xmin = -10; xmax = 60;
+
+
+Lbody=Lcyl+Lel;
+bctype = 1;
+
+Hmax = 1; %taille max des mailles
+n=2; %densité du méillage: voir meshInit_BluntbodyInTube.edp
+
+%%% FIN PARAMETERS
+
+    disp('computing base flow and adapting mesh');
+    
+    Re_start = [10 , 30, 60, 100, 200,300,400,500,600]; 
+    bf = SF_Init('meshInit_BluntBodyInTube.edp',[Rbody Lel Lcyl Rpipe xmin xmax bctype]); 
+    for Rei = Re_start
+        bf=SF_BaseFlow(bf,'Re',Rei); 
+        bf=SF_Adapt(bf,'Hmax',Hmax);
+        disp(['delta min : ',num2str(bf.mesh.deltamin)]);
+        disp(['delta max : ',num2str(bf.mesh.deltamax)]);
+    end
+% compute a spectrum  
+
+ [ev1,eigenmode1] = SF_Stability(bf,'m',1,'shift',0,'nev',10,'plotspectrum','yes');   
+
+ [ev2,eigenmode2] = SF_Stability(bf,'m',1,'shift',1.2i,'nev',10,'plotspectrum','yes');   
+
+ [ev3,eigenmode3] = SF_Stability(bf,'m',1,'shift',0.7i,'nev',10,'plotspectrum','yes');   
+
+ pause(0.1);
+
+evtot=[ev1 ev2 ev3]
+
+
+% % range for figures
+% bf.mesh.xlim=[-2*Rbody,Lbody+5*Rbody]; %x-range for plots
+% bf.mesh.ylim=[0,Rpipe];
+% plotFF(bf,'mesh'); % to plot the mesh
+% 
+% pause(0.1);
+
+%% Guess des nombres de Reynolds
+
+% guessReS=0i;
+% guessReI=0.8i;
+% 
[…]

### 2018-07-17 CASES_STABLE/ELLIPT_BLUNTBODY_IN_PIPE/SCRIPTS/C5_E2_Rp20_LD6.m

@@ -1,0 +1,100 @@
+clear all
+format shortG
+
+
+run('/Users/theomouyen/Documents/GitHub/StabFem/SOURCES_MATLAB/SF_Start.m');
+close all;
+
+%ffdatadir = './WORK/'; %% to be fixed : this should be "./WORK" but some of the solvers are not yet operational
+
+%%% PARAMETRES
+
+Rbody = 0.5; Lel = 1; Lcyl = 5;Rpipe = 20; xmin = -10; xmax = 60;
+
+
+Lbody=Lcyl+Lel;
+bctype = 5;
+
+Hmax = 1; %taille max des mailles
+n=2; %densité du méillage: voir meshInit_BluntbodyInTube.edp
+
+%%% FIN PARAMETRES
+
+    disp('computing base flow and adapting mesh');
+    
+    Re_start = [10 , 30, 60, 100, 200]; 
+    bf = SF_Init('meshInit_BluntBodyInTube.edp',[Rbody Lel Lcyl Rpipe xmin xmax bctype]); 
+    for Rei = Re_start
+        bf=SF_BaseFlow(bf,'Re',Rei); 
+        bf=SF_Adapt(bf,'Hmax',Hmax);
+        
+        disp(['delta min : ',num2str(bf.mesh.deltamin)]);
+        disp(['delta max : ',num2str(bf.mesh.deltamax)]);
+    end
+   
+% compute a spectrum  
+
+ [ev1,eigenmode1] = SF_Stability(bf,'m',1,'shift',0,'nev',10,'plotspectrum','yes');   
+
+ [ev2,eigenmode2] = SF_Stability(bf,'m',1,'shift',1i,'nev',10,'plotspectrum','yes');   
+
+ [ev3,eigenmode3] = SF_Stability(bf,'m',1,'shift',0.2+0.5i,'nev',10,'plotspectrum','yes');   
+
+ pause(0.1);
+
+
+
+evtot=[ev1 ev2 ev3]
+
+% range for figures
+bf.mesh.xlim=[-2*Rbody,Lbody+5*Rbody]; %x-range for plots
+bf.mesh.ylim=[0,Rpipe];
+plotFF(bf,'mesh'); % to plot the mesh
+
+pause(0.1);
+
+%% COMPUTING THE UNSTEADY BRANCH (going backwards)
+ReIi=800;
+ReIf=750;
[…]

### 2018-07-17 CASES_STABLE/ELLIPT_BLUNTBODY_IN_PIPE/SCRIPTS/Readjust2.m

@@ -1,0 +1,32 @@
+%Pour la deuxième paire de modes qui apparaissent en confinement
+%Pour avoir les valeurs propres à un nouveau Reynolds et les visualiser
+%Entrée : guessS et guessI
+
+
+% 1er mode
+
+
+bf=SF_BaseFlow(bf,'Re',ReIi); 
+bf=SF_Adapt(bf,'Hmax',Hmax); 
+
+[ev01,eigenmode01] = SF_Stability(bf,'m',1,'shift',guessReI,'nev',1,'plotspectrum','yes');   
+
+ev01
+
+
+% Calcul du base flow intermédiaire
+
+ReInt=(ReIi+ReSi)/2;
+
+        bf=SF_BaseFlow(bf,'Re',ReInt); 
+        bf=SF_Adapt(bf,'Hmax',Hmax);
+
+        
+% 2eme mode
+
+bf=SF_BaseFlow(bf,'Re',ReSi); 
+bf=SF_Adapt(bf,'Hmax',Hmax); 
+
+[ev00,eigenmode00] = SF_Stability(bf,'m',1,'shift',guessReS,'nev',1,'plotspectrum','yes');   
+
+ev00

### 2018-07-17 CASES_STABLE/ELLIPT_BLUNTBODY_IN_PIPE/SCRIPTS/Recritique2.m

@@ -1,0 +1,92 @@
+function [ReCI1,ReCI2,ImCI1,ImCI2] = Recritique2(guessReI1,guessReI2,EVI1,EVI2,Re_RangeI1,Re_RangeI2,bf,Hmax)
+
+%%Calcule les Reynolds critiques par interpolation polynomiale puis donne
+%%leur coordonnées dans le plan complexe
+
+
+
+%Calcul de Rec
+
+
+xx= real(EVI1);
+kk=find(xx(2:end).*xx(1:end-1)<0);
+i=kk;
+j=kk+1;
+
+XS=[Re_RangeI1(i) Re_RangeI1(j)];
+YS=[real(EVI1(i)) real(EVI1(j))];
+
+pS=polyfit(XS,YS,1);
+
+ReCI1=-pS(2)/pS(1);
+
+
+
+xx= real(EVI2);
+kk=find(xx(2:end).*xx(1:end-1)<0);
+k=kk;
+l=kk+1;
+
+XI=[Re_RangeI2(k) Re_RangeI2(l)];
+YI=[real(EVI2(k)) real(EVI2(l))];
+
+pI=polyfit(XI,YI,1);
+
+ReCI2=-pI(2)/pI(1);
+
+%Calcul des coordonnées des modes au Reynolds critique%
+
+bf=SF_BaseFlow(bf,'Re',ReCI1); 
+bf=SF_Adapt(bf,'Hmax',Hmax); 
+
+[ev00,eigenmode00] = SF_Stability(bf,'m',1,'shift',guessReI1,'nev',1);   
+bf = SF_Adapt(bf,eigenmode00,'Hmax',Hmax);
+[ev00,eigenmode00] = SF_Stability(bf,'m',1,'shift',ev00,'nev',1);   
+bf = SF_Adapt(bf,eigenmode00,'Hmax',Hmax);
+[ev00,eigenmode00] = SF_Stability(bf,'m',1,'shift',ev00,'nev',1,'plotspectrum','yes');
+
+figure;
+plotFF(eigenmode00,'ux1');
+title('Profil de vitesse M1')
+figure;
+plotFF(eigenmode00,'vort1');
+title('Ligne de vorticité M1')
+figure;
+plotFF(eigenmode00,'p1');
+title('Lignes de pression M1')
+
+
+
+bf=SF_BaseFlow(bf,'Re',ReCI2); 
[…]

### 2018-07-17 CASES_STABLE/ELLIPT_BLUNTBODY_IN_PIPE/TRASH/E2_Rp10.m

@@ -1,0 +1,71 @@
+clear all
+
+%Mes données%
+
+dataE2_Rp10LD6=load('dataE2_Rp10LD6.txt');
+dataE2_Rp10LD4=load('dataE2_Rp10LD4.txt');
+dataE2_Rp10LD3=load('dataE2_Rp10LD3.txt');
+dataE2_Rp10LD2=load('dataE2_Rp10LD2.txt');
+dataE2_Rp10LD1=load('dataE2_Rp10LD1.txt');
+
+
+MM=[dataE2_Rp10LD1;dataE2_Rp10LD2;dataE2_Rp10LD3;dataE2_Rp10LD4;dataE2_Rp10LD6];
+
+plot([0 1 2 3 4 5 6 7 8 9 10],MM(find(MM(:,1)==2),4),'ro')
+
+hold on
+
+plot(MM(find(MM(:,1)==1),3),MM(find(MM(:,1)==1),4),'bv')
+
+
+%Jimenez 3D%
+
+JIMENEZ_X=[1 2];
+JIMENEZ_RECS=[215 319];
+JIMENEZ_RECI=[254 413];
+
+plot(JIMENEZ_X,JIMENEZ_RECI,'k+')
+plot(JIMENEZ_X,JIMENEZ_RECS,'ks')
+
+
+
+%Jimenez 2D
+
+J_CS=load('Jimenez_Globalstability_CS.txt');
+
+x = J_CS(:,1);
+y = J_CS(:,2);
+xx = 1:0.1:9;
+yy = spline(x,y,xx);
+plot(xx,yy,'k')
+
+J_CI=load('Jimenez_Globalstability_CI.txt');
+
+x = J_CI(:,1);
+y = J_CI(:,2);
+xx = 1:0.1:9;
+yy = spline(x,y,xx);
+plot(xx,yy,'k')
+
+x = MM(find(MM(:,1)==2),3);
+y = MM(find(MM(:,1)==2),4);
+xx = 1:0.1:6;
+yy = spline(x,y,xx);
+plot(xx,yy,'r')
+
+
+x = MM(find(MM(:,1)==1),3);
+y = MM(find(MM(:,1)==1),4);
+xx = 1:0.1:6;
+yy = spline(x,y,xx);
+plot(xx,yy,'b')
+
+
+%Titre et légende%
+title('Dependance of the critical Reynolds numbers on L/D')
+xlabel('L/D')
+ylabel('Re')
+axis([0 11 0 1500])
[…]

### 2018-07-17 CASES_STABLE/ELLIPT_BLUNTBODY_IN_PIPE/TRASH/E2_Rp10LD1.m

@@ -1,0 +1,94 @@
+clear all
+
+run('/Users/theomouyen/Documents/GitHub/StabFem/SOURCES_MATLAB/SF_Start.m');
+close all;
+
+
+%ffdatadir = './WORK/'; %% to be fixed : this should be "./WORK" but some of the solvers are not yet operational
+
+Rbody = 0.5; Lel = 1; Lcyl = 0.04;Rpipe = 10; xmin = -10; xmax = 30;
+Lbody=Lcyl+Lel;
+bctype = 1;
+
+    disp('computing base flow and adapting mesh');
+    bf = SF_Init('meshInit_BluntBodyInTube.edp',[Rbody Lel Lcyl Rpipe xmin xmax bctype]); 
+    Re_start = [10 , 30, 60, 100 , 200]; % values of Re for progressive increasing up to end
+    for Rei = Re_start
+        bf=SF_BaseFlow(bf,'Re',Rei); 
+        bf=SF_Adapt(bf,'Hmax',0.5);
+    end
+   
+% compute a spectrum  
+
+[ev1,eigenmode1] = SF_Stability(bf,'m',1,'shift',0,'nev',10,'type','D','plotspectrum','yes');   
+pause(0.1); 
+
+ [ev2,eigenmode2] = SF_Stability(bf,'m',1,'shift',1i,'nev',10,'type','D','plotspectrum','yes');   
+pause(0.1);
+
+ [ev3,eigenmode3] = SF_Stability(bf,'m',1,'shift',0.2+0.5i,'nev',10,'type','D','plotspectrum','yes');   
+pause(0.1);
+
+ [ev4,eigenmode4] = SF_Stability(bf,'m',1,'shift',0.5,'nev',10,'type','D','plotspectrum','yes');   
+pause(0.1);
+
+ [ev5,eigenmode5] = SF_Stability(bf,'m',1,'shift',0.5+0.5i,'nev',10,'type','D','plotspectrum','yes');   
+pause(0.1);
+
+ [ev6,eigenmode6] = SF_Stability(bf,'m',1,'shift',0.5+2i,'nev',10,'type','D','plotspectrum','yes');   
+pause(0.1);
+
+ [ev7,eigenmode7] = SF_Stability(bf,'m',1,'shift',-0.25+2i,'nev',10,'type','D','plotspectrum','yes');   
+pause(0.1);
[…]

### 2018-07-17 CASES_STABLE/ELLIPT_BLUNTBODY_IN_PIPE/TRASH/E2_Rp10LD4.m

@@ -1,0 +1,93 @@
+clear all
+
+run('/Users/theomouyen/Documents/GitHub/StabFem/SOURCES_MATLAB/SF_Start.m');
+close all;
+
+
+%ffdatadir = './WORK/'; %% to be fixed : this should be "./WORK" but some of the solvers are not yet operational
+
+Rbody = 0.5; Lel = 1; Lcyl = 3;Rpipe = 10; xmin = -10; xmax = 30;
+Lbody=Lcyl+Lel;
+bctype = 1;
+
+    disp('computing base flow and adapting mesh');
+    bf = SF_Init('meshInit_BluntBodyInTube.edp',[Rbody Lel Lcyl Rpipe xmin xmax bctype]); 
+    Re_start = [10 , 30, 60, 100 , 200]; % values of Re for progressive increasing up to end
+    for Rei = Re_start
+        bf=SF_BaseFlow(bf,'Re',Rei); 
+        bf=SF_Adapt(bf,'Hmax',0.5);
+    end
+   
+% compute a spectrum  
+
+ [ev1,eigenmode1] = SF_Stability(bf,'m',1,'shift',0,'nev',10,'type','D','plotspectrum','yes');   
+
+ [ev2,eigenmode2] = SF_Stability(bf,'m',1,'shift',1i,'nev',10,'type','D','plotspectrum','yes');   
+
+ [ev3,eigenmode3] = SF_Stability(bf,'m',1,'shift',0.2+0.5i,'nev',10,'type','D','plotspectrum','yes');   
+
+
+ [ev4,eigenmode4] = SF_Stability(bf,'m',1,'shift',0.5,'nev',10,'type','D','plotspectrum','yes');   
+
+ [ev5,eigenmode5] = SF_Stability(bf,'m',1,'shift',0.5+0.5i,'nev',10,'type','D','plotspectrum','yes');   
+
+ [ev6,eigenmode6] = SF_Stability(bf,'m',1,'shift',0.5+2i,'nev',10,'type','D','plotspectrum','yes');   
+
+ [ev7,eigenmode7] = SF_Stability(bf,'m',1,'shift',-0.25+2i,'nev',10,'type','D','plotspectrum','yes');   
+pause(0.1);
+
+evtot=[ev1 ev2 ev3 ev4 ev5 ev6 ev7]
+
+% range for figures
[…]

### 2018-07-17 CASES_STABLE/ELLIPT_BLUNTBODY_IN_PIPE/TRASH/E2_Rp10LD6.m

@@ -1,0 +1,91 @@
+clear all
+
+run('/Users/theomouyen/Documents/GitHub/StabFem/SOURCES_MATLAB/SF_Start.m');
+close all;
+
+
+%ffdatadir = './WORK/'; %% to be fixed : this should be "./WORK" but some of the solvers are not yet operational
+
+Rbody = 0.5; Lel = 1; Lcyl = 5;Rpipe = 10; xmin = -10; xmax = 30;
+Lbody=Lcyl+Lel;
+bctype = 5;
+
+    disp('computing base flow and adapting mesh');
+    bf = SF_Init('meshInit_BluntBodyInTube.edp',[Rbody Lel Lcyl Rpipe xmin xmax bctype]); 
+    Re_start = [10 , 30, 60, 100 , 200]; % values of Re for progressive increasing up to end
+    for Rei = Re_start
+        bf=SF_BaseFlow(bf,'Re',Rei); 
+        bf=SF_Adapt(bf,'Hmax',0.5);
+    end
+   
+% compute a spectrum  
+
+ [ev1,eigenmode1] = SF_Stability(bf,'m',1,'shift',0,'nev',10,'type','D','plotspectrum','yes');   
+
+ [ev2,eigenmode2] = SF_Stability(bf,'m',1,'shift',1i,'nev',10,'type','D','plotspectrum','yes');   
+
+ [ev3,eigenmode3] = SF_Stability(bf,'m',1,'shift',0.2+0.5i,'nev',10,'type','D','plotspectrum','yes');   
+
+
+ [ev4,eigenmode4] = SF_Stability(bf,'m',1,'shift',0.5,'nev',10,'type','D','plotspectrum','yes');   
+
+ [ev5,eigenmode5] = SF_Stability(bf,'m',1,'shift',0.5+0.5i,'nev',10,'type','D','plotspectrum','yes');   
+
+ [ev6,eigenmode6] = SF_Stability(bf,'m',1,'shift',0.5+2i,'nev',10,'type','D','plotspectrum','yes');   
+
+ [ev7,eigenmode7] = SF_Stability(bf,'m',1,'shift',-0.25+2i,'nev',10,'type','D','plotspectrum','yes');   
+pause(0.1);
+
+evtot=[ev1 ev2 ev3 ev4 ev5 ev6 ev7]
+
+% range for figures
[…]

### 2018-07-17 CASES_STABLE/ELLIPT_BLUNTBODY_IN_PIPE/TRASH/E2_Rp3LD6.m

@@ -1,0 +1,86 @@
+clear all
+
+run('/Users/theomouyen/Documents/GitHub/StabFem/SOURCES_MATLAB/SF_Start.m');
+close all;
+
+
+%ffdatadir = './WORK/'; %% to be fixed : this should be "./WORK" but some of the solvers are not yet operational
+
+Rbody = 0.5; Lel = 1; Lcyl = 5;Rpipe = 3; xmin = -10; xmax = 30;
+Lbody=Lcyl+Lel;
+bctype = 1;
+
+    disp('computing base flow and adapting mesh');
+    bf = SF_Init('meshInit_BluntBodyInTube.edp',[Rbody Lel Lcyl Rpipe xmin xmax bctype]); 
+    Re_start = [10 , 30, 60, 100 , 200]; % values of Re for progressive increasing up to end
+    for Rei = Re_start
+        bf=SF_BaseFlow(bf,'Re',Rei); 
+        bf=SF_Adapt(bf,'Hmax',0.5);
+    end
+   
+% compute a spectrum  
+
+ [ev1,eigenmode1] = SF_Stability(bf,'m',1,'shift',0,'nev',10,'type','D','plotspectrum','yes');   
+
+ [ev2,eigenmode2] = SF_Stability(bf,'m',1,'shift',1i,'nev',10,'type','D','plotspectrum','yes');   
+
+ [ev3,eigenmode3] = SF_Stability(bf,'m',1,'shift',0.2+0.5i,'nev',10,'type','D','plotspectrum','yes');   
+
+
+ [ev4,eigenmode4] = SF_Stability(bf,'m',1,'shift',0.5,'nev',10,'type','D','plotspectrum','yes');   
+
+ [ev5,eigenmode5] = SF_Stability(bf,'m',1,'shift',0.5+0.5i,'nev',10,'type','D','plotspectrum','yes');   
+
+ [ev6,eigenmode6] = SF_Stability(bf,'m',1,'shift',0.5+2i,'nev',10,'type','D','plotspectrum','yes');   
+
+ [ev7,eigenmode7] = SF_Stability(bf,'m',1,'shift',-0.25+2i,'nev',10,'type','D','plotspectrum','yes');   
+pause(0.1);
+
+evtot=[ev1 ev2 ev3 ev4 ev5 ev6 ev7]
+
+% range for figures
[…]

### 2018-07-17 CASES_STABLE/ELLIPT_BLUNTBODY_IN_PIPE/TRASH/E2_Rp5LD6.m

@@ -1,0 +1,93 @@
+clear all
+
+run('/Users/theomouyen/Documents/GitHub/StabFem/SOURCES_MATLAB/SF_Start.m');
+close all;
+
+
+%ffdatadir = './WORK/'; %% to be fixed : this should be "./WORK" but some of the solvers are not yet operational
+
+Rbody = 0.5; Lel = 1; Lcyl = 5;Rpipe = 5; xmin = -10; xmax = 30;
+Lbody=Lcyl+Lel;
+bctype = 1;
+
+    disp('computing base flow and adapting mesh');
+    bf = SF_Init('meshInit_BluntBodyInTube.edp',[Rbody Lel Lcyl Rpipe xmin xmax bctype]); 
+    Re_start = [10 , 30, 60, 100 , 200]; % values of Re for progressive increasing up to end
+    for Rei = Re_start
+        bf=SF_BaseFlow(bf,'Re',Rei); 
+        bf=SF_Adapt(bf,'Hmax',0.5);
+    end
+   
+% compute a spectrum  
+
+ [ev1,eigenmode1] = SF_Stability(bf,'m',1,'shift',0,'nev',10,'type','D','plotspectrum','yes');   
+
+ [ev2,eigenmode2] = SF_Stability(bf,'m',1,'shift',1i,'nev',10,'type','D','plotspectrum','yes');   
+
+ [ev3,eigenmode3] = SF_Stability(bf,'m',1,'shift',0.2+0.5i,'nev',10,'type','D','plotspectrum','yes');   
+
+
+ [ev4,eigenmode4] = SF_Stability(bf,'m',1,'shift',0.5,'nev',10,'type','D','plotspectrum','yes');   
+
+ [ev5,eigenmode5] = SF_Stability(bf,'m',1,'shift',0.5+0.5i,'nev',10,'type','D','plotspectrum','yes');   
+
+ [ev6,eigenmode6] = SF_Stability(bf,'m',1,'shift',0.5+2i,'nev',10,'type','D','plotspectrum','yes');   
+
+ [ev7,eigenmode7] = SF_Stability(bf,'m',1,'shift',-0.25+2i,'nev',10,'type','D','plotspectrum','yes');   
+pause(0.1);
+
+evtot=[ev1 ev2 ev3 ev4 ev5 ev6 ev7]
+
+% range for figures
[…]

### 2018-07-17 CASES_STABLE/EXAMPLE_Lshape/autorun.m

@@ -1,0 +1,54 @@
+function value = autorun(isfigures);
+
+% This script is a basic example which illustrates the main functionalities of the StabFem Software
+
+run('../SOURCES_MATLAB/SF_Start.m');ffdatadir = './';verbosity=0;
+
+% Generation of the mesh
+Ndensity =40;
+ffmesh=SF_Mesh('Lshape_Mesh.edp','Params',Ndensity)
+
+if(isfigures) 
+    figure();plotFF(ffmesh,'title','Mesh for L-shape body'); 
+    set(gca,'FontSize', 18); saveas(gca,'FIGURES/Lshape_Mesh','png');
+    pause(1);
+end;
+
+% importation and plotting of a real P1 field : temperature
+heatS=SF_Launch('Lshape_Steady.edp','Mesh',ffmesh)
+if(isfigures) 
+    figure();plotFF(heatS,'T','title', 'Solution of the steady heat equation on a L-shaped domain'); 
+    set(gca,'FontSize', 18); saveas(gca,'FIGURES/Lshape_T0','png');
+    pause(1);
+end;
+
+% importation and plotting of data not associated to a mesh : temperature along a line
+heatCut = importFFdata('Heat_1Dcut.ff2m')
+if(isfigures) figure();plot(heatCut.Xcut,heatCut.Tcut);
+    title('Temperature along a line : T(x,y=0.25)') 
+    set(gca,'FontSize', 18); saveas(gca,'FIGURES/Lshape_T0_Cut','png');
+    pause(1);
+end;
+
+critere1 = heatCut.Tcut(50);
+critere1REF = 0.034019400000000;
+
+% importation and plotting of a complex P1 field : temperature for unsteady problem
+heatU=SF_Launch('Lshape_Unsteady.edp','Params',100,'Mesh',ffmesh,'DataFile','Heat_Unsteady.ff2m')
+if(isfigures) 
+    figure();plotFF(heatU,'Tc.re','title',['Ti: real(colors) part']) 
+    set(gca,'FontSize', 18); saveas(gca,'FIGURES/Lshape_Tc','png');
+end
+
+critere2 = max(imag(heatU.Tc));
+critere2REF = 0.506614000000000;
+
+ERROR = abs(critere2-critere2REF)+abs(critere1-critere1REF);
+
+if(ERROR<1e-3)
+    value = 0;
+else 
+    value = 1;
+end
+
+end

### 2018-07-17 CYLINDER/SCRIPT_CYLINDER_SC.m

@@ -1,73 +1,0 @@
-%  Instability of the wake of a cylinder with STABFEM  
-%
-%  this script reproduces the results of the Self-Consistent model
-%  of Mantic-Lugo et al. 
-
-
-%% ##### CHAPTER 1 : COMPUTING THE MESH WITH ADAPTMESH PROCEDURE
-run('../SOURCES_MATLAB/SF_Start.m');verbosity = 10;
-figureformat='png'; AspectRatio = 0.56; % for figures
-
-type = 'S';
-bf = CYLINDER_MESHGENERATION(type); 
-    % here use 'S' for mesh M2 (converged results for all quantities except for A_E , but much faster
-    % or 'D' for mesh M4 (converged results for all quantities, but much
-    % slower)
-
-
-%%  CHAPTER 2 : determining instability threshold
-
-disp('COMPUTING INSTABILITY THRESHOLD');
-bf=SF_BaseFlow(bf,'Re',50);
-[ev,em] = SF_Stability(bf,'shift',+.75i,'nev',1,'type','D');
-[bf,em]=SF_FindThreshold(bf,em);
-Rec = bf.Re;  Fxc = bf.Fx; 
-Lxc=bf.Lx;    Omegac=imag(em.lambda);
-
-disp(' ');disp(['   ===> THRESHOLD FOUND FOR Re = ',num2str(Rec)]);disp(' ');
-
-
-%% CHAPTER 6 : SELFCONSISTENT APPROACH WITH RE = 100
-
-%%% (Reproducing the figure of Mantic-Lugo)
-%%%
-%%% HERE the initial guess is for sigma = 0.12 (slightly less than the
-%%% linear growth rate, the initialisation is done with the linear eigmode
-%%% with a "small" amplitude (measured by lift force), namely Fy=0.00734 .
-
-
-% determination of meanflow/selfconsistentmode for Re = 100
-Fyguess = 0.00734;
-bf=SF_BaseFlow(bf,'Re',100);
-[ev,em] = SF_Stability(bf,'shift',0.12+0.72i,'nev',1,'type','D');
-
-sigma_SC = [real(em.lambda),0.12 0.115 0.11 0.1:-.02:0];
-Fy_SC = [0]; AEnergy_SC = [0];
-
-    [meanflow,mode] = SF_HB1(bf,em,'sigma',0.12,'Fyguess',Fyguess) 
-    Fy_SC = [Fy_SC mode.Fy];
[…]

### 2018-07-17 CYLINDER_VIV/SCRIPT_VIV_TEST.m

@@ -1,109 +1,0 @@
-% Matlab interface for GlobalFem
-%
-%   (set of programs in Freefem to perform global stability calculations in hydrodynamic stability)
-%  
-%  THIS SCRIPT DEMONSTRATES THE MESH CONVERGENCE USING ADAPTMESH 
-%   TO BASEFLOW AND EIGENMODE.
-
-
-global ff ffdir ffdatadir sfdir verbosity
-ff = '/usr/local/ff++/openmpi-2.1/3.55/bin/FreeFem++-nw -v 0'; %% Freefem command with full path 
-ffdatadir = './DATA_FREEFEM_CYLINDER';
-sfdir = '../SOURCES_MATLAB'; % where to find the matlab drivers
-ffdir = '../SOURCES_FREEFEM/'; % where to find the freefem scripts
-verbosity=1;
-
-
-addpath(sfdir);
-system(['mkdir ' ffdatadir]);
-
-if(exist('em')==1)
-    disp('Mesh / base flow previously computed');
-else
-
-disp(' ');
-disp(' GENERATING  MESH : [-40:120]x[0:40] ');
-disp(' ');
-
-baseflow=FreeFem_Init('Mesh_Cylinder_Large.edp');
-baseflow=FreeFem_BaseFlow(baseflow,'Re',1);
-baseflow=FreeFem_BaseFlow(baseflow,'Re',10);
-baseflow=FreeFem_BaseFlow(baseflow,'Re',60);
-plotFF(baseflow,'mesh');pause;
-
-baseflow=FreeFem_Adapt(baseflow,'Hmax',10,'InterpError',0.005);
-plotFF(baseflow,'mesh');pause(0.1);
-
-end
-
-disp(' ');
-disp('ADAPTING MESH FOR RE=60 ')
-disp(' ');
-%baseflow=FreeFem_BaseFlow(baseflow,'Re',60);
-
-[ev,em] = FreeFem_Stability(baseflow,'shift',0.04+0.76i,'nev',1,'type','S');
-[baseflow,em]=FreeFem_Adapt(baseflow,em,'Hmax',10,'InterpError',0.005);
-plotFF(baseflow,'mesh');pause(0.1);
-
-%disp(' ');
-%disp(' THRESHOLD : ')
-%[baseflowC,emC]=FreeFem_FindThreshold(baseflow,em);
-
-
-close all;
-
-disp(' ');
[…]

### 2018-07-17 POROUS_ROTATING_DISK/SCRIPT_POROUS_ROTATING_DISK.m

@@ -1,169 +1,0 @@
-%%####################################################################
-%  STAGE IMFT                                        Adrien Rouviere
-%               -- ANALYSE DE STABILITÉ GLOBALE --
-%           -- ÉCOULEMENT AUTOUR D'UN DISQUE POREUX --
-%                                                   
-%#####################################################################
-
-clear all;
-close all;
-clc
-
-%% 0 - Préchauffage
-
-run('../SOURCES_MATLAB/SF_Start.m');
-
-ffdatadir = 'WORK/'; %% to be fixed : this should be "./WORK" but some of the solvers are not yet operational
-figureformat = 'png';
-
-verbosity = 100;
-
-%% 1 - Génération MAILLAGE et BASEFLOW
-
-Rx = 3;
-
-% Géométrie
-Rayon = 1;
-    DIAMETER = num2str(2*Rayon);
-Epaisseur = 1/(2*Rx);
-    THICKNESS = num2str(Epaisseur);
-Xmin = -20*Rayon;
-    XMIN = num2str(Xmin);
-Xmax = 50*Rayon;
-    XMAX = num2str(Xmax);
-Ymax = 20*Rayon;
-    YMAX = num2str(Ymax);
-
-boxx = [-Epaisseur/2, Epaisseur/2, Epaisseur/2, -Epaisseur/2, -Epaisseur/2];
-boxy = [0, 0, Rayon, Rayon, 0];
-
-it=0;
-baseflow=SF_Init('mesh_Disk.edp',[DIAMETER ' ' THICKNESS ' ' XMIN ' ' XMAX ' ' YMAX]);
-
-% Plot mesh initial
-% baseflow.xlim = [Xmin Xmax]; baseflow.ylim=[0,Ymax];
-baseflow.xlabel=('x');baseflow.ylabel=('r');
-baseflow.plottitle = ['Maillage initial du domaine de calcul'];
-plotFF(baseflow,'mesh');
-hold on;fill(boxx,boxy,'y','FaceAlpha', 0.3);hold off;
-
-%% 2 - Génération du BASEFLOW pour un certain Re
-
-% Paramètres de calcul
-Re_start = [10:50:1000];
-Omega = [0.];
-Darcy = [1e-1];
-Porosite = [1];
-
-    it=1;
-    for Re = Re_start
-        tic;
[…]

### 2018-07-17 99_Documentation/ARTICLE_STABFEM/Beamer_10juillet2018.tex
Reorganization of the arborescence (redone with « git mv » to keep tracking)

\documentclass{beamer}

\usepackage[frenchb]{babel}

\usepackage[T1]{fontenc}
%\usepackage[latin1]{inputenc}
\usepackage[utf8]{inputenc}

\usepackage{marvosym}

\newcommand{\be}[1]{ \begin{equation} \label{#1}}
\newcommand{\ee}{\end{equation}}

\newcommand{\bes}[1]{ \begin{equation} \label{#1}\begin{array}{rl}}
\newcommand{\ees}{\end{array}\end{equation}}

\usepackage[normalem]{ ulem }
\usepackage{soul}

% \usetheme{default} -> A utiliser dans un premier temps

% \usetheme{Warsaw} -> A utiliser dans un second temps

\input{../99_Documentation/01_Preamble.tex}

\newcommand{\ssp}{\vspace{.2cm} }

\title{A (kind of) practical review on global stability approches}

\subtitle{}

\author{D. Fabre}

\institute{IMFT, groupe InterfaceS}

\date{Informal Workshop "D\&D", 10 juillet 2018}

\AtBeginSection{
\frame{\tableofcontents[current]}
}

\begin{document}

\begin{frame}

\titlepage

\end{frame}

\section{Linear global stability  : basic principles, and a few useful tricks}

\subsection{Qu'es aquò ??}

\begin{frame}{Qu'es aquò ?? }

Instability problems are ubiquous in fluid mechanics

\ssp

Numerical resolution of such problems resorts to a specific class of numerical methods, which replace
time-stepping of the full equations by  assumptions about temporal dependance (modal expansion, amplitude equations, etc...)

 \ssp These methods are complementary to direct numerical resolution methods (i.e. time-stepping).

%Leur résolution fait appel à une classe de méthodes numériques spécifiques, 
%complémentaires aux approches de simulation directe, qui sont actuellement en plein développement.

\ssp

We refer to {\em global stability} when the geometry requires resolution in 2 (or 3) spatial dimensions.

%On parle {\em stabilité globale} quand la géométrie du problème necésssite une résolution en 2D (ou en 3D).

\ssp

(as opposed to {\em local stability } which takes advantage of invariance directions (parallel flow, etc...)
to bring the problem to spatially 1D).

%(par opposition à {\em stabilité locale} quand des directions d'invariance (écoulement parallèle par ex.) permettent de rammener le problème à une résolution en 1D).

\end{frame}

%\subsection{Step 0 : computation of a base flow}

\begin{frame}{Base flow}

We look for a steady base-flow $({\bf u}_b;p_b)$ satisfying the steady Navier-Stokes equations, i.e. 
$NS ({\bf u}_b,p_b) = 0$.

Suppose that we have a 'guess' for the base flow $[{\bf u}_b^g,p_b^g]$  which almost satisfies the equations.  We look for a better approximation under the form
\be{Newton1}
[{\bf u}_b,p_b]  = [{\bf u}_b^g,p_b^g] + [\delta {\bf u}_b, \delta p_b] = 0.
\ee

Injecting into the Navier-Stokes equation lead to $$
NS ({\bf u}_b^g,p_b^g) + NSL_{{\bf u}_b^g}(\delta {\bf u}_b,\delta p_b)$$

Where $NSL$ is the linearised Navier-Stokes operator. 
%defined by its action on a flow field $({\bf u} ; p)$ as follows

=>  matricial problem with the form $A \cdot \delta X = Y$. The procedure of Newton iteration is to solve iteratively this set of equations up to convergence.

\end{frame}

%\subsection{Step 1 : Eigenvalue computation}

\begin{frame}{Linear stability}

\be{startmodepropre}
{\bf u} = {\bf u}_b + \epsilon \hat{\bf u} e^{\lambda t} 
\ee

The eigenmodes is governed by the linear problem 
$$\lambda \hat{{\bf u}} = NSL_{{\bf u}_b}( \hat{\bf u},\hat{p})$$,

After discretization we end up with an eigenvalue problem with the matricial form
\be{Eigen_matricial}
\lambda B \hat{X} = A \hat{X}
\ee

\ssp
Iterative method : single-mode shift-invert iteration
$$
X^{n} =  (A- \lambda_{shift} B)^{-1} B X^{n-1}
$$

Generalization : Arnoldi

\end{frame}

%\subsection{Adjoint eigenmodes and structural sensitivity}

\begin{frame}{Adjoint problem}

\small

Define a scalar product :
$$
\left< \phi_1, \phi_2 \right> = \int_\Omega \overline{\phi_1} \cdot \phi_2   \mbox{ d} \Omega
$$

We can first define the {\em adjoint linearised Navier-Stokes operator} $NSL^\dag$ defined by the property:
\bes{NSLAdj}
\forall ( {\bf u}, p ; {\bf u}^\dag, p^\dag), & \left< NSL^\dag_{\bf U}( {\bf u}^\dag,p^\dag) ,{\bf u}\right> + \left< \nabla \cdot {\bf u}^\dag,p\right>  \\
=& \left<{\bf u}^\dag, NSL_{\bf U} ({\bf u},p)\right> + \left< p^\dag, \nabla \cdot {\bf u}\right>.
\ees
We can then define the adjoint eigenmodes as the solutions to the eigenvalue problem 
\be{EigenAdj} 
\forall ( {\bf u}, p), \quad  \lambda^\dag \left< \hat{{\bf u}^\dag}, {\bf u}\right> =
 \left< NSL^\dag_{\bf U}( \hat{\bf v},\hat{p^\dag}) ,{\bf u}\right> + \left< \nabla \cdot \hat{\bf u}^\dag,p\right>  
\ee

Matricial form :

\be{Eigen_Adj_matricial}
\overline{\lambda}^\dag B \hat{X}\dag = A^T \hat{X}\dag.
\ee

\end{frame}

\begin{frame}{Adjoint mode and structural sensitivity}

Significance of the adjoint mode :

(optimal perturbation)

\ssp
%\pause

%Structural sensitivity:

The adjoint eigenmode also allows us to introduce the so-called {\em structural sensitivity tensor } that is defined as 
\be{Structursens} 
{\bf{S}}({\bf{x}}) = \frac{|| \hat{\bf u}^\dag|| \,\, ||\hat{\bf u}|| }{{\left<\hat{\bf u}^\dag, \hat{\bf u}\right>}},
\ee 
which has became popular in the recent years.

\end{frame}

\subsection{Three ideas to really speed up your linear stability computations !}

\begin{frame}{Three ideas to really speed up your stability computations !}

\begin{itemize}[<+->]

\item Use simple shift-invert for computing a single mode !

\item Adapt your mesh !
\begin{itemize}
\item to base flow,
\item to base flow + eigenmode, 
\item to base flow + structural sensitivity !
\end{itemize}

\item Escape the real world : go into complex plane !

\begin{itemize}
\item Incompressible case : to handle strongly convective instabilities

(example : whisling jet, with Vincenzo Citro \& Raffaele Longobardi)

\item Compressible case : to handle non-reflective boundary conditions

(example : cylinder wake ; with Javier Sierra)
\end{itemize}

\end{itemize}

\end{frame}

%%%%%%%%%%%%%%%%%% CHAPTER 2 %%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{StabFem : a software that may save your life !}
\subsection{Qu'es aquò ???}

%\subsection{StabFem : présentation du logiciel}

\begin{frame}{FreeFem++}

Finite element methods are well suited to global stability problerms.

The {\em FreeFem++} software is gaining popularity in the hydrodynamic stabillity community.
 %un outil très populaire dans la communauté de la stabilité hydrodynamique.

\small

\begin{itemize}[<+->]
%{\color{green} \Smiley{} \quad }  (solides, fluides, thermique, etc...)
\item
{\color{green} \Smiley{} \quad } Simple and intuitive syntax directly based on weak formulation.
%Syntaxe intuitive basée directement sur la formulation faible.
\item
{\color{green} \Smiley{} \quad } Powerful and adaptative mesh  (movemesh, adaptmesh, etc...)
% Mailleur puissant et adaptatif (movemesh, adaptmesh, etc...)
\item
{\color{green} \Smiley{} \quad } 2D and 3D.
\item
{\color{green} \Smiley{} \quad } Large choice of sequencial and parallel solvers  (Mumps, Petsc/Slepc, ..)
%Grand choix de solveurs séquentiels ou parallèles (Mumps, Petsc/Slepc, ..)
\item
{\color{red} \Frowny{} \quad } Limited graphical interface (ffglut) %Interface graphique limitée (ffglut).
\item
{\color{red} \Frowny{} \quad } Interpreted language : not suited to functional programming (but powerful macros).
%Language interprété : pas adapté à la programmation fonctionnelle (mais des macros puissantes).
\item
{\color{red} \Frowny{} \quad } Syntax may be touchy and debugging sometimes awkward...
%Syntaxe "chatouilleuse" et débuggage parfois complexe...
\end{itemize}
\end{frame}

\begin{frame}{Why interface FreeFem++ with another software ?}

\small

\begin{itemize}[<+->]

\item %Stratégie avant "StabFem" (2010-2017) :
Previous strategy :

Computation chain : freefem solvers / shell scripts / postprocessing with tecplot/gnuplot...

%Chaine de calcul : Solveurs FreeFem++ / Scripts Shell / Post-traitement Tecplot / Gnuplot....

%=> 50 programmes quasiment identiques + 10 manières d'effectuer le post-traitement,

%on ne s'y retrouve plus...

=> 50 almost identical programs + 10 ways to handle post-processing => getting crazy !

\ssp

\item %Nécessité d'une surcouche "driver"  pour piloter les calculs et tracer les résultats en mode "terminal" ou par l'intermédiaire de scripts.
=> Necessity of a  set of "drivers" in a high-level language to monitor computations and draw the results in "command-line" or "script" mode.

\item 
%Philosophie (à terme) : 1 travail (1 article) = 1 unique script Matlab pour reproduire tous les calculs et générer toutes les figures 
Philosophy (objective) : one work (one paper) = 1 unique program to generate all results and produce all figures.
(cf. Basilisk...)

%\item Choix actuel  : Drivers en Matlab/Octave

\end{itemize}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{StabFem : Cahier des charges }
%Equations : 
%\begin{equation}
%$$\frac{\partial V }{\partial t} = \nu \frac{\partial^2 V}{\partial y^2} $$
%\label{eq:navier}
%\end{equation}
%(on a supposé pour simplifier qu'il n'y avait pas de gradient de pression autre qu'hydrostatique).
%Conditions limites : $\left. v\right|_{y=0} = 0$, $\left. v\right|_{y=h} = U(t)$

\begin{itemize}[<+->]

\item StabFem : an open-source and easy-to-use software allowing a large range of computations in fluid mechanics.

\item Designed for both research  \& education.

\item Initially  oriented towards Global Stability Approches (Linear \& Nonlinear) but actually allowing a larger number of computations
(DNS, linear acoustics, etc...)

\item Multi-platform (Unix, MacOs, Windows) and designed to run on "light" computers (Laptops...)

\item Easy to use/install,

\item Easy to customize to a variety of cases (incompressible, compressible, fixed/free objects, free surfaces,...)

\item Freeware, based on two softwares : FreeFem++ and \sout{Matlab}/{\color{red}Octave }

\item Developed as a collaborative project
(IMFT, Università di Salerno, ONERA, UPFL, ...)

\item Maintained on Github

\ssp
{\color{orange}
\verb! https://github.com/erbafdavid/StabFem !
}

\end{itemize}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Articulation FreeFem / Matlab}

\scriptsize

\begin{itemize}[<+->]

\item 
Etage 1 : Solveurs FreeFem++ "briques de base".

Un solveur par "classe de problèmes" (2D incompressible, 2D compressible, Axisymétrique incompressible...) et par "type de calcul" (calcul d'un champ de base, stabilité linéaire, ...)

\item  Etage 2 : drivers Matlab "génériques"

Un unique driver pour chaque "type de calcul" , le choix du bon solveur est fait en fonction 
des paramètres optionnels fournis au driver.

\item Etage 3 : Les boucles sur les paramètres et la génération des figures sont faites dans un "script principal".

\item Les solveurs et les drivers génériques sont dans des répertoires communs {\bf SOURCES\_MATLAB/} et {\bf SOURCES\_FREEFEM/},

\item Les programmes spécifiques à chaque cas d'étude sont dans un répertoire spécifique.

Exemple : le répertoire "CYLINDRE" contient les programmes suivants :

\begin{enumerate}
\scriptsize
\item Mesh\_Cylinder.edp		\qquad -> Génération du maillage

\item Macros\_StabFem.edp \qquad -> Macros case-dependant (conditions limites et post-traitement)

\item SCRIPT\_CYLINDER.m $\qquad$ -> Script "Maitre".

\end{enumerate}
\end{itemize}
\pause

{\em Remarques : les programmes FreeFem doivent pouvoir être utilisés directement en dehors du driver StabFem, 
notamment pour faciliter le développement/débuggage...)}

\ssp

{\em Les contributeurs "utilisateurs" (ex. étudiant M1/M2) ne travaillent qu'à l'étage 3 et ne devraient travailler que sur ces 3 fichiers.
\ssp

Les contributeurs "développeurs" travaillent aux étages inférieurs...}

\end{frame}

\begin{frame}{Format d'échange des données}

\begin{itemize}[<+->]

\item Format de fichier d'échange ".ff2m", généré par FreeFem++ et relu par Matlab

\item Example d'en-tête d'un fichier .ff2m :

\lstinputlisting[linerange={1-4}]{../EXAMPLE_Lshape/Data.ff2m}

Ligne 4 : "TypeField1 NameField1 TypeField2 NameField2... "

TypeField can be "real" (scalar data), "real.N" (vectorial data), "P1" (data associated to mesh), ...

\item Le fichier est lu et importé sous forme d'une {\em structure matlab}

\item Illustration : cas "EXAMPLE\_Lshape"

\end{itemize}

\end{frame}

%\section{Using StabFem for Linear stability }

\subsection{Demonstration for the wake of a cylinder}

\begin{frame}{First step : Generation of a mesh and "guess" base flow}

\small

%\begin{lstlisting}
%bf=SF_Init('Mesh_Cylinder.edp', [-40 80 40]);
%\end{lstlisting}

\keys{bf=SF\_Init('Mesh\_Cylinder.edp', [-40 80 40]);}

\ssp

What the \keys{SF\_Init} driver does :

\begin{itemize}[<+->]
\item Runs the relevant FreeFem++ program \keys{Mesh\_Cylinder.edp}  with the corresponding parameters (here size of the domain),

{\scriptsize This program generates the following output files : \keys{mesh.msh} (mesh data), \keys{mesh.ff2m} (mesh information), \keys{SF\_Init.ff2m} (auxiliary information), \keys{BaseFlow\_init.txt} and \keys{BaseFlow\_init.ff2} ("guess" base flow).}

\item Reads all the output files,

\item Returns a matlab "structure" object containing all the data needed for post-processing and subsequent usage.

\end{itemize}

\end{frame}

%\subsection{Step 0 : computation of a base flow}

\begin{frame}{Computation of a Base flow : principle}

We look for a steady base-flow $({\bf u}_b;p_b)$ satisfying the steady Navier-Stokes equations, i.e. 
$NS ({\bf u}_b,p_b) = 0$.

Suppose that we have a 'guess' for the base flow $[{\bf u}_b^g,p_b^g]$  which almost satisfies the equations.  We look for a better approximation under the form
\be{Newton1}
[{\bf u}_b,p_b]  = [{\bf u}_b^g,p_b^g] + [\delta {\bf u}_b, \delta p_b] = 0.
\ee

Injecting into the Navier-Stokes equation lead to $$
NS ({\bf u}_b^g,p_b^g) + NSL_{{\bf u}_b^g}(\delta {\bf u}_b,\delta p_b)$$

Where $NSL$ is the linearised Navier-Stokes operator. 
%defined by its action on a flow field $({\bf u} ; p)$ as follows

=>  matricial problem with the form $A \cdot \delta X = Y$. The procedure of Newton iteration is to solve iteratively this set of equations up to convergence.

\end{frame}

\begin{frame}{Computation of a Base flow : implementation}

\small

\keys{bf=SF\_BaseFlow(bf,'Re',10);}

%\begin{lstlisting}
%baseflow=SF_BaseFlow(baseflow,'Re',10);
%\end{lstlisting}

\ssp

What the \keys{SF\_Init} driver does :

\begin{itemize}[<+->]
\item Copies the previous base flow  into file \keys{BaseFlow\_guess.txt} which will be read by Freefem++,

\item Runs the relevant FreeFem++ solver (here \keys{Newton\_2D.edp})  with the corresponding parameters (here the value of $Re$),

%{\scriptsize This program generates the following output files : \keys{mesh.msh} (mesh data), \keys{mesh.ff2m} (mesh information), \keys{SF\_Init.ff2m} (auxiliary information), \keys{BaseFlow\_init.txt} and \keys{BaseFlow\_init.ff2} ("guess" base flow).}

\item Reads all the generated output files (here \keys{BaseFlow.ff2m}),

\item Returns a matlab "structure" object containing all the data needed for post-processing and subsequent usage.

\end{itemize}

\end{frame}

\begin{frame}{Mesh adaptation}

\end{frame}

%\subsection{Eigenvalue computation : principle}

\begin{frame}{Linear stability}

\be{startmodepropre}
{\bf u} = {\bf u}_b + \epsilon \hat{\bf u} e^{\lambda t} 
\ee

The eigenmodes is governed by the linear problem 
$$\lambda \hat{{\bf u}} = NSL_{{\bf u}_b}( \hat{\bf u},\hat{p})$$,

After discretization we end up with an eigenvalue problem with the matricial form
\be{Eigen_matricial}
\lambda B \hat{X} = A \hat{X}
\ee

\ssp
Iterative method : single-mode shift-invert iteration
$$
X^{n} =  (A- \lambda_{shift} B)^{-1} B X^{n-1}
$$

Generalization : Arnoldi

\end{frame}

\begin{frame}{Eigenvalue computation : implementation}

\small

\keys{SF\_Stability(bf,’shift’,0.04+0.74i,’nev’,1,’ type ’ , ’D’ ) ;}

%\begin{lstlisting}
%baseflow=SF_BaseFlow(baseflow,'Re',10);
%\end{lstlisting}

\ssp

What the \keys{SF\_Stability} driver does :

\begin{itemize}[<+->]
\item Copies the base flow into file \keys{BaseFlow.txt} which will be needed by Freefem++,

\item Runs the FreeFem++ solver (here \keys{Stab\_2D.edp})  with the corresponding parameters (shift, number of eigenvalues, direct eigenmode),

%{\scriptsize This program generates the following output files : \keys{mesh.msh} (mesh data), \keys{mesh.ff2m} (mesh information), \keys{SF\_Init.ff2m} (auxiliary information), \keys{BaseFlow\_init.txt} and \keys{BaseFlow\_init.ff2} ("guess" base flow).}

\item Reads all the generated output files (here \keys{Eigenmode.ff2m}),

\item Does a number of post-processing (sort the eigenvalues, update the "shift" in continuation mode...)

\item Returns a matlab "structure" object containing all the data needed for post-processing and subsequent usage.

\end{itemize}

\end{frame}

\subsection{List of test-cases currently available}

\begin{frame}{StabFem : list of test-cases currently available (or under development...)}

\scriptsize

\begin{itemize}
\item CYLINDER  		\qquad -> 2D incompressible, objet fixe

\item CYLINDER\_VIV \qquad 	-> 2D incompressible, objet mobile

(Stage Diogo Ferrera-Sabino)

\item IMPACTINGJET  		\qquad -> 2D incompressible, 3D stability.

(with David LoJacono)

\item CYLINDER\_Compressible  \qquad -> 2D compressible

(Javier Serra, Vincenzo Citro...)

\item BIRDCALL \qquad -> 2D-axisymmetric, incompressible or "augmented incompressible"

(with R. Longobardi, V. Citro....)

\item POROUS\_DISK \qquad -> 2D-axisymmetric, with porous object

(stage Adrien Rouvière)

\item LiquidBridges -> 2D axi, with deformable free surface

(stage Nabil Achour)

\item ROTATING\_POLYGONS

(with Jérôme Mougel...)
\item ....

\end{itemize}

=> Illustration dans le cas CYLINDER

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Whistling jets : axisymmetric flow through a two-hole configuration}
(with Raffaele Longobari, Vincenzo Citro \& others...)

\includegraphics[width=.9\linewidth]{FIGURES/WhistlinJetMode.png}
\end{frame}

\begin{frame}{2D around a spring-mounted cylinder...}
(with Diogo Ferreira Sabino \& Olivier Marquet)
\end{frame}

\begin{frame}{2D flow around a compressible cylinder...}
(in fast progress with Javier Sierra...)
\end{frame}

\begin{frame}{Flow around (and through) a porous (\& rotating) disk...}
(with Adrien Rouvière \& D. Lo Jacono)

\includegraphics[width=.6\linewidth]{FIGURES/Ux_Re200_Da1e-2.png}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{frame}{Liquid bridges...}

\begin{description}
%\item{Directory in the StabFem project :}  \texttt{LiquidBridges}
%\item{Main contributors :} D. Fabre.
\item{Reference :} Chireux et al., Phys. Fluids, 2015.
\end{description}

\begin{figure}
\includegraphics[width=.5\linewidth]{../LiquidBridges/FIGURES/Bridges_NV_Eigenmodes_phi_cyl_L3_5.png}
\caption{Oscillation modes of a liquid bridge of aspect ratio $L/R=4$ and reduced volume $V^ =$...}
\label{Bridges_NV_Eigenmodes_phi_cyl_L3_5}
\end{figure}

\begin{figure}
\includegraphics[width=.45\linewidth]{../LiquidBridges/FIGURES/Bridges_NV_coal_omega.png}
\includegraphics[width=.45\linewidth]{../LiquidBridges/FIGURES/Bridges_NV_coal_omega.png}
\caption{Oscillation frequencies of a liquid bridge resulting from the coalescence of two spherical droplets
as function of $L^* =L/R$
(figures 11,12 of Chireux et al.)
}
\label{Bridges_NV_Eigenmodes_phi_cyl_L3_5}
\end{figure}

\end{frame}

\begin{frame}{rotating polygons...}

\begin{description}
%\item{Directory in the StabFem project :}  \texttt{ROTATINGPOLYGONS}
%\item{Main contributors :} J. Mougel, D. Fabre
\item{Reference :} Mougel et al., JFM 2018 
\end{description}

\begin{figure}
\includegraphics[width=.8\linewidth]{../ROTATING_POLYGONS/FIGURES/POLYGONS_modes.png}
\caption{Oscillation modes of a potential vortex for  $a=H/R=0.3$ and $m=3$ (figure 5, 6 of Mougel et al.).}
\label{Bridges_NV_Eigenmodes_phi_cyl_L3_5}
\end{figure}

\begin{figure}
\includegraphics[width=.45\linewidth]{../ROTATING_POLYGONS/FIGURES/POLYGONS_omega.png}
\includegraphics[width=.45\linewidth]{../ROTATING_POLYGONS/FIGURES/POLYGONS_sigma.png}
\caption{Oscillation frequencies and amplification rates for f a potential vortex for $m=3$ (figure 4 of Mougel et al.).}
\label{Bridges_NV_Eigenmodes_phi_cyl_L3_5}
\end{figure}

\end{frame}

\begin{frame}{Sessile drops...}

With Nabil Achour  ( \& Paul Bonnefis)

\includegraphics[width=.9\linewidth]{FIGURES/SessileDrops_Eigenmodes.png}     % SessileDrops__Eigenmodes_eta.png

- Linear oscillations modes ("pined" or "fixed angle" conditions)

Next steps : investigate contact-line dynamics with WNL methods (cf. Viola, Brun \& Gallaire, 2018)

\end{frame}

%%%%%%%%%%%%%%% PART 3 : NONLINEAR APPROACHES %%%%%%%%%%%%%%%%%%%

\section{Nonlinear global stability approaches : status and future}

%\section{Nonlinear global approaches to hydrodynamic instabilities}

\begin{frame}{Nonlinear global stability approaches : review}
\small

The linear stability approach approach is the right tool to predict instability threshold ($Re_c$) and the shedding frequency at threshold ($St_c = \omega_c/2\pi$).

\ssp
 But for $Re>Re_c$ it badly predicts the frequency of the limit cycle.

$$
\includegraphics[width=8cm]{Barkley_figure.png}
$$

 \ssp It has been remarked that stability analysis of the {\em mean flow} obtained by time-averaging the limit cycle gives better predictions (Barkley, Leontini,...).

\ssp

  => Objective of nonlinear stability approaches : provide rational approach to describe the nonlinear oscillation cycle,
  and provide amplitude equations to describe the transients.

  %Give a rigorous ground to study the stability of {\em mean flow}.

\end{frame}
\subsection{Weakly nonlinear approach}

\begin{frame}{Weakly nonlinear approach {\small (Sipp \& Lebedev, 2007)}}

\footnotesize

Starting point : weakly non-linear expansion, with multiple scale method.

$$
\epsilon = \frac{1}{Re_c} - \frac{1}{Re} ; \quad \tau = \epsilon^2 t
$$

\begin{eqnarray}
{\bf u} &=& {\bf u}_{bc} + \epsilon \left[ A_{wnl} (\tau) \hat{\bf u} e^{i \omega_c t} + c.c. \right] \label{WNL1}\\
&+& \epsilon^2 \left[ {\bf u}_\epsilon + |A_{wnl}|^2  {\bf u}_{2,0} + \left(  A_{wnl}^2 {\bf u}_{2,2} e^{2 i \omega_c t} + c.c. \right) \right] + {\cal O}( \epsilon ^3)
\nonumber
\end{eqnarray}

Resolution at order 2 :
%Substituting the expansion \ref{WNL2} into the Navier-Stokes equations \ref{NSprimitive} and grouping terms multiplied by the same power of $\epsilon$, a hierarchy of equations is obtained. The order $\epsilon^0$ gives directly the base flow at $Re_c$. The order $\epsilon^1$
%corresponds to the linear neutral eigenmode as computed in the first part of this article.
%The order $\epsilon^2$ contains three terms respectively computed as the solutions of the following linear problems:
\begin{eqnarray}
 {\cal LNS}_{{\bf u}_{bc}} ({\bf u}_\epsilon) - 2 \nabla \cdot {\mathsf D}({\bf u}_{bc}) &=&0,
\label{eq:LL1} \\
{\cal LNS}_{{\bf u}_{bc}} ({\bf u}_{2,0}) &=& {\cal C}(\hat{\bf u},\overline{\hat{\bf u}}), \label{eq:LL2} \\
{\cal LNS}_{{\bf u}_{bc}} ({\bf u}_{2,2}) - 2 i \omega_c {\bf u}_{2,2}  &=& \frac{1}{2} {\cal C}(\hat{\bf u},\hat{\bf u}). \label{eq:LL3}
 \end{eqnarray}

Compatibility conditions at order 3 :
\be{WNL3_2}
\frac{\partial A_{wnl}}{\partial \tau} = \Lambda A_{wnl} - (\nu_0+\nu_2)  |A_{wnl}|^2 A_{wnl},
\ee
%where coefficients $\Lambda$, $\nu_0$ and $\nu_2$ are given by
\begin{eqnarray}
\Lambda &=& -\frac{ \left< {\hat{\bf u}}^\dag, 
\left( {\cal C}({\bf u}_\epsilon, \hat{\bf u}) + 2 \nabla \cdot  {\mathsf D}( \hat{\bf u}) \right) \right>}
{  \left<  \hat{\bf u}^\dag,\hat{\bf u} \right> },\label{LAMBDA}\\
\nu_0 &=& \frac{ \left< {\hat{\bf u}}^\dag,  {\cal C}({\bf u}_{20}, \hat{\bf u} ) \right>}
{  \left<  \hat{\bf u}^\dag,\hat{\bf u} \right> },\label{NU0}\quad
\nu_2 = \frac{ \left< {\hat{\bf u}}^\dag,  {\cal C}({\bf u}_{22}, \overline{\hat{\bf u}})  \right>}
{  \left<  \hat{\bf u}^\dag,\hat{\bf u} \right> }.,\label{NU2}
 \end{eqnarray}

%Method : weakly nonlinear expansion

%Order 0 : base-flow

%Order 1 : eigenmode at marginal conditions

%Order 2 : nonresonant linear problems -> direct resolution

%Order 3 : resonant problems : compatibility conditions (Fredholm alternative)

%Resolution thanks to adjoint methods

%=> Amplitude equation

\end{frame}

\subsection{Self-consistent approach}

\begin{frame}{Self-Consistent approach {\small (Mantic-Lugo, Arratia \& Gallaire, 2014)}}

\small
Starting point : Pseudo-eigenmode decomposition

\be{SC}
{\bf u } = {\bf u }_m + A_{sc} \left[ \tilde{{\bf u }}_1 e^{\sigma_{sc} t + i \omega_{sc} t} +   \overline{\tilde{\bf u }_1} e^{\sigma_{sc} t  -i \omega_{sc} t} \right],
\quad
\left( |\tilde{{\bf u }}_1|| = 1/\sqrt{2}\right)
\ee

%where ${\bf u }_m$ is the {\em mean flow} as previously defined,  $\tilde{{\bf u }}_1$ is a pseudo-eigenvector which is normalized by the condition  $||\tilde{{\bf u }}_1|| = 1/\sqrt{2}$, $\overline{\tilde{{\bf u }}_1}$ is its complex conjugate,
where $A_{sc}$ is an amplitude parameter, %directly related to the energy of the oscillating flow, 
and $\lambda_{sc} = \sigma_{sc} + i \omega_{sc}$ is a pseudo-eigenvalue which depends upon the parameter $A_{sc}$.

\pause
=> SC-model equations

\begin{subequations}\label{sc12}
\begin{eqnarray}
{\cal NS}(  {\bf u }_m ) - A_{sc}^2 {\cal C}( \tilde{{\bf u }}_1, \overline{\tilde{\bf u }_1}) = 0, 
\label{sis1}
\\
(\sigma_{sc} + i \omega_{sc}) \tilde{{\bf u }}_1 =  {\cal LNS}_{{\bf u }_m}(\tilde{{\bf u }}_1 ).
\label{sis2}
\end{eqnarray}
\end{subequations}

\pause

=> Amplitude equation :
$$
\frac{\partial A_{sc}}{\partial t} = \sigma_{sc} (A_{sc}) A_{sc}
$$

\pause

%$\sigma(A_E

Resolution method of {\small (Mantic-Lugo 2014)}: double iterative loop

- Inner loop :

$\quad$ Fix $A_{sc}$, iteratively solve (eigenvalue problem + calculation of mean flow) up to convergence for $(\sigma_{sc} + i \omega_{sc})$ as function of $A_{sc}$.

- Outer loop :

$\quad$ iterate over $A_{sc}$ to reach  $\sigma_{sc} = 0$

\end{frame}

\begin{frame}{Self-Consistent approach : a direct resolution method}

\small

Let's forget about transients, and look directly for a description of the saturated cycle:
%We thus start with a truncated Fourier decomposition of the limit cycle under the form:

\be{HB}
{\bf u } = {\bf u }_m + {\bf u }_{1,c} \cos( \omega t ) +   {\bf u }_{1,s} \sin( \omega t ),
\ee
where ${\bf u }_{1,c}$ and ${\bf u }_{1,s}$ are two {\em real} fields %describing the nonlinear perturbation at two instants separated by a quarter-period of oscillation,

and $\omega$ is the (real) oscillation frequency of the limit cycle.
%The connection with the definition of Manti\v{c}-Lugo is as follows :
%\be{HBtoSC}
%\left( {\bf u }_{1,c} - i {\bf u }_{1,s} \right) = 2 A_{sc} \tilde{{\bf u }}_1.
%\ee

\ssp

=> Equations :
%Injecting this ansartz into the Navier-Stokes equations and taking the mean value and the first Fourier component leads to the following coupled equations:
\begin{subequations}\label{eq_principal}
\begin{eqnarray}
{\cal NS}(  {\bf u }_m ) = \frac{{\cal C}( {\bf u }_{1,c}, {\bf u }_{1,c}) +{\cal C}( {\bf u }_{1,s}, {\bf u }_{1,s})}{4}, 
\label{HBEq0}
\\
 \omega {\bf u }_{1,s} =  {\cal LNS}_{{\bf u }_m}(  {\bf u }_{1,c} ),
\label{HBEq1}
\\
 -\omega {\bf u }_{1,c} =  {\cal LNS}_{{\bf u }_m}(  {\bf u }_{1,s} ).
\label{HBEq1b}
\end{eqnarray}
\end{subequations}

We need an extra scalar equation to fix the phase of the cycle, e.g:

\begin{equation}
\Im \{F_y({\bf u}_1) \} =0.
\label{HBphase}
\end{equation}

=> Direct resolution with Newton method !
\ssp

Remarks :

- We need a good guess : use the WNL to produce it !

- Computation can be optimized using preconditioning (Ask Olivier...)

\end{frame}

\subsection{Harmonic-balance approach}

\begin{frame}{Harmonic-Balance}

\small

%The Navier-stokes equations can be posed as

%\begin{eqnarray}
%\partial_t {\bf u} = {\cal NS} ({\bf u},p)
%\equiv - {\bf u} \cdot \nabla {\bf u} - \nabla p + \frac{2}{Re}  \nabla \cdot {\mathsf{D}}({\bf u}), \label{NSprimitive}  \\
%\nabla \cdot {\bf u} = 0. \label{eq:DIV}
%\end{eqnarray}

We start with the following expansion:
\begin{equation}
{\bf u } = {\bf u }_m + {\bf u }_{1,c} \cos( \omega t ) +   {\bf u }_{1,s} \sin( \omega t ) +{\bf u }_{2,c} \cos(2 \omega t ) +   {\bf u }_{2,s} \sin(2 \omega t ),
\end{equation}

arriving to a system of equations:
\begin{subequations}\label{eq_principal}
\begin{eqnarray}
{\cal NS}(  {\bf u }_m) = \frac{{\cal C}( {\bf u }_{1,c}, {\bf u }_{1,c}) +{\cal C}( {\bf u }_{1,s}, {\bf u }_{1,s})+{\cal C}( {\bf u }_{2,c}, {\bf u }_{2,c})+{\cal C}( {\bf u }_{2,s}, {\bf u }_{2,s})}{4}, 
\label{HBEq0}
\\
 \omega {\bf u }_{1,s} =  {\cal L}_{{\bf u }_m}(  {\bf u }_{1,c} )-\frac{1}{2}\Big(
 {\cal C}( {\bf u }_{1,c}, {\bf u }_{2,c})+{\cal C}( {\bf u }_{1,s}, {\bf u }_{2,s})
 \Big),
\label{HBEq1}
\\
 -\omega {\bf u }_{1,c} =  {\cal L}_{{\bf u }_m}(  {\bf u }_{1,s} )-\frac{1}{2}\Big(
 {\cal C}( {\bf u }_{1,c}, {\bf u }_{2,s})-{\cal C}( {\bf u }_{1,s}, {\bf u }_{2,c})
 \Big),
\label{HBEq1b}
\\
 2 \omega {\bf u }_{2,s} =  {\cal L}_{{\bf u }_m}(  {\bf u }_{2,c} )-\frac{1}{4}\Big(
 {\cal C}( {\bf u }_{1,c}, {\bf u }_{1,c})-{\cal C}( {\bf u }_{1,s}, {\bf u }_{1,s})
 \Big),
\label{HBEq2}
\\
 -2\omega {\bf u }_{2,s} =  {\cal L}_{{\bf u }_m}(  {\bf u }_{2,s} )-\frac{1}{2}
 {\cal C}( {\bf u }_{1,s}, {\bf u }_{1,c}),
\label{HBEq2b}
\end{eqnarray}
\end{subequations}
%where ${\cal C}( {\bf U} , {\bf u}) = \left( {\bf U} \cdot \nabla \right) {\bf u} + \left( {\bf u} \cdot \nabla \right)  {\bf U}$.

%To allow resolution we thus need an extra equation to fix this phase, e.g:
\begin{equation}
\Im \{F_y({\bf u}_1) \} =0.
\label{HBphase}
\end{equation}

=> Direct Newton resolution again
\end{frame}

\begin{frame}{Harmonic-Balance : results for the cylinder ! }

%\begin{figure}
\begin{center}
\includegraphics[width=.32 \linewidth]{../CYLINDER/FIGURES/Cylinder_Strouhal_Re_HB2.png}
\includegraphics[width=.32 \linewidth]{../CYLINDER/FIGURES/Cylinder_Energy_Re_HB2.png}
\includegraphics[width=.32 \linewidth]{../CYLINDER/FIGURES/Cylinder_Lx_Re_HB2.png}
\end{center}
\begin{center}
\includegraphics[width=.32\linewidth]{../CYLINDER/FIGURES/Cylinder_Fx_Re_HB2.png}
\includegraphics[width=.32 \linewidth]{../CYLINDER/FIGURES/Cylinder_Fy_Re_HB2.png}
\end{center}
%\caption{Comparison between the weakly nonlinear results (WNL) the harmonic balance data (HB), and baseflow/linear results : Strouhal number $(a)$, Mean drag $(b)$, amplitude of oscillating lift $(c)$, Energy-amplitude of the nonlinear perturbation $(d)$ and recirculation lenght of mean/base flows ($e)$. 
%c_x should be consistent with the drag definition given at beginning
%}
%\label{fig:HB_SC_DATA_COMP}
%\end{figure}

\end{frame}

%
%\subsection{Adjoint problem} 
%
%\begin{frame}{Adjoint problem}
%
%\small
%
%Define a scalar product :
%$$
%\left< \phi_1, \phi_2 \right> = \int_\Omega \overline{\phi_1} \cdot \phi_2   \mbox{ d} \Omega
%$$
%
%
%We can first define the {\em adjoint linearised Navier-Stokes operator} $NSL^\dag$ defined by the property:
%\bes{NSLAdj}
%\forall ( {\bf u}, p ; {\bf v}, q), & \left< NSL^\dag_{\bf U}( {\bf v},q) ,{\bf u}\right> + \left< \nabla \cdot {\bf v},p\right>  \\
%=& \left< {\bf v}, NSL_{\bf U} ({\bf u},p)\right> + \left< q, \nabla \cdot {\bf u}\right>.
%\ees
%We can then define the adjoint eigenmodes as the solutions to the eigenvalue problem 
%\be{EigenAdj} 
%\forall ( {\bf u}, p), \quad  \lambda^\dag \left< \hat{\bf v}, {\bf u}\right> =
% \left< NSL^\dag_{\bf U}( \hat{\bf v},\hat{q}) ,{\bf u}\right> + \left< \nabla \cdot \hat{\bf v},p\right>  
%\ee
%
%Matricial form :
%
%\be{Eigen_Adj_matricial}
%\overline{\lambda}^\dag B \hat{X}\dag = A^T \hat{X}\dag.
%\ee
%
%
%\end{frame}
%
%\begin{frame}{Adjoint mode and structural sensitivity}
%
%
%Significance of the adjoint mode : 
%
%(optimal perturbation)
%
%
%\end{frame}

%\section{Nonlinear global approaches to hydrodynamic instabilities}
%
%\begin{frame}{Nonlinear global stability approaches : review}
%
%%The linear stability approach approach is the right tool to predict instability threshold ($Re_c$) and the %shedding frequency at threshold ($St_c = \omega_c/2\pi$).
%
%%\ssp
%% But for $Re>Re_c$ it badly predicts the frequency of the limit cycle. 
% 
%%$$
%%\includegraphics[width=8cm]{FIGURES/Barkley_figure.png}
%%$$
%
% 
% 
%% \ssp It has been remarked that stability analysis of the {\em mean flow} obtained by time-averaging the limit cycle gives better predictions (Barkley, Leontini,...).
%  
%  
%%\ssp 
%  
% % => Objective of nonlinear stability approaches : Give a rigourous ground to study the stability of mean flow.
%  
%  
%
%\end{frame}
%
%\begin{frame}{Weakly nonlinear approach {\small (Sipp \& Lebedev, 2007)}}
%
%Starting point : weakly non-linear expansion, with multiple scale method.
%
%$$
%\epsilon : \frac{1}{Re_c} - \frac{1}{Re} ; \quad \tau = \epsilon^2 t
%$$
%
%\begin{eqnarray}
%{\bf u} &=& {\bf u}_{bc} + \epsilon \left[ A_{wnl} (\tau) \hat{\bf u} e^{i \omega_c t} + c.c. \right] \label{WNL1}\\
%&+& \epsilon^2 \left[ {\bf u}_\epsilon + |A_{wnl}|^2  {\bf u}_{2,0} + \left(  A_{wnl}^2 {\bf u}_{2,2} e^{2 i \omega_c t} + c.c. \right) \right] + {\cal O}( \epsilon ^3)
%\nonumber
%\end{eqnarray}
%
%
%\end{frame}
%
%
%
%\begin{frame}{Self-Consistent approach {\small (Mantic-Lugo, Arratia \& Gallaire, 2014)}}
%
%Starting point : Pseudo-eigenmode decomposition
%
%
%
%\end{frame}

\begin{frame}{Conclusions}
\end{frame}

\appendix{The future of StabFem }

\begin{frame}{Recent progress}

\begin{itemize}

\item Multi-platform objective : 
MacOs OK ; Unix OK ; Windows 10 currently 50 \% compatible.

{\small main issues with windows : cp = copy,...}%  \verb|\| instead of \verb|/|,...}

\item Plotting options : recent intergration of "pdeplot2dff" from Markus "chloros" in place of pdeplot/pdetools .

{\small other solutions for plotting : tecplot converter, vtk converter, ...}

\item Compatibility with Octave : currently 50 \% compatible.

{\small Main issues with octave : importdata, plotting (now solved), inputParser (now solved)}.

\item Translation in Python  ??

\end{itemize}

\end{frame}

%%%%%%%%%%%%
\begin{frame}{Besoins}

\begin{itemize}

\item Maintaining a fully opensource  (Matlab-Octave or Python ?) and fully multiplatform version (windows).

\item Managing a list of test cases (non-regression tests, etc...)

\item Help simplifying/rationalizing the programation style.

\item Gestion of errors / debugging / "verbosity" ...

\item Upgrading to 3D / parallel computation ? (currently not priority)

\item Support with github  (/ gitlab ?)

\item Documentation

Automatic generation from comments in programs ?  Doxygen ??

\end{itemize}

\end{frame}

\end{document}

### 2018-07-17 99_Documentation/ARTICLE_STABFEM/Beamer_6juillet2018.tex
Reorganization of the arborescence (redone with « git mv » to keep tracking)

--- 2018-07-17 99_Documentation/ARTICLE_STABFEM/Beamer_10juillet2018.tex
@@
 
-\title{A (kind of) practical review on global stability approches}
+\title{Réunion "StabFem"}
 
@@
 
-\institute{IMFT, groupe InterfaceS}
+\institute{IMFT, groupe Interface}
 
-\date{Informal Workshop "D\&D", 10 juillet 2018}
+\date{6 juillet 2018}
 
@@
 
-\section{Linear global stability  : basic principles, and a few useful tricks}
-
-\subsection{Qu'es aquò ??}
-
-\begin{frame}{Qu'es aquò ?? }
-
-Instability problems are ubiquous in fluid mechanics
-
-\ssp
-
-Numerical resolution of such problems resorts to a specific class of numerical methods, which replace
-time-stepping of the full equations by  assumptions about temporal dependance (modal expansion, amplitude equations, etc...)
-
- \ssp These methods are complementary to direct numerical resolution methods (i.e. time-stepping).
-
-%Leur résolution fait appel à une classe de méthodes numériques spécifiques, 
-%complémentaires aux approches de simulation directe, qui sont actuellement en plein développement.
-
-\ssp
-
-We refer to {\em global stability} when the geometry requires resolution in 2 (or 3) spatial dimensions.
-
-%On parle {\em stabilité globale} quand la géométrie du problème necésssite une résolution en 2D (ou en 3D).
-
-\ssp
-
-(as opposed to {\em local stability } which takes advantage of invariance directions (parallel flow, etc...)
-to bring the problem to spatially 1D).
-
-%(par opposition à {\em stabilité locale} quand des directions d'invariance (écoulement parallèle par ex.) permettent de rammener le problème à une résolution en 1D).
-
-\end{frame}
-
-%\subsection{Step 0 : computation of a base flow}
-
-\begin{frame}{Base flow}
-
-We look for a steady base-flow $({\bf u}_b;p_b)$ satisfying the steady Navier-Stokes equations, i.e. 
-$NS ({\bf u}_b,p_b) = 0$.
-
-Suppose that we have a 'guess' for the base flow $[{\bf u}_b^g,p_b^g]$  which almost satisfies the equations.  We look for a better approximation under the form
-\be{Newton1}
-[{\bf u}_b,p_b]  = [{\bf u}_b^g,p_b^g] + [\delta {\bf u}_b, \delta p_b] = 0.
-\ee
-
-Injecting into the Navier-Stokes equation lead to $$
-NS ({\bf u}_b^g,p_b^g) + NSL_{{\bf u}_b^g}(\delta {\bf u}_b,\delta p_b)$$
-
-Where $NSL$ is the linearised Navier-Stokes operator. 
-%defined by its action on a flow field $({\bf u} ; p)$ as follows
-
-=>  matricial problem with the form $A \cdot \delta X = Y$. The procedure of Newton iteration is to solve iteratively this set of equations up to convergence.
-
-\end{frame}
-
-%\subsection{Step 1 : Eigenvalue computation}
-
-\begin{frame}{Linear stability}
-
-\be{startmodepropre}
-{\bf u} = {\bf u}_b + \epsilon \hat{\bf u} e^{\lambda t} 
-\ee
-
-The eigenmodes is governed by the linear problem 
-$$\lambda \hat{{\bf u}} = NSL_{{\bf u}_b}( \hat{\bf u},\hat{p})$$,
-
-After discretization we end up with an eigenvalue problem with the matricial form
-\be{Eigen_matricial}
-\lambda B \hat{X} = A \hat{X}
-\ee
-
-\ssp
-Iterative method : single-mode shift-invert iteration
-$$
-X^{n} =  (A- \lambda_{shift} B)^{-1} B X^{n-1}
-$$
-
-Generalization : Arnoldi
-
-\end{frame}
-
-%\subsection{Adjoint eigenmodes and structural sensitivity}
-
-\begin{frame}{Adjoint problem}
-
-\small
-
-Define a scalar product :
-$$
-\left< \phi_1, \phi_2 \right> = \int_\Omega \overline{\phi_1} \cdot \phi_2   \mbox{ d} \Omega
-$$
-
-We can first define the {\em adjoint linearised Navier-Stokes operator} $NSL^\dag$ defined by the property:
-\bes{NSLAdj}
-\forall ( {\bf u}, p ; {\bf u}^\dag, p^\dag), & \left< NSL^\dag_{\bf U}( {\bf u}^\dag,p^\dag) ,{\bf u}\right> + \left< \nabla \cdot {\bf u}^\dag,p\right>  \\
-=& \left<{\bf u}^\dag, NSL_{\bf U} ({\bf u},p)\right> + \left< p^\dag, \nabla \cdot {\bf u}\right>.
-\ees
-We can then define the adjoint eigenmodes as the solutions to the eigenvalue problem 
-\be{EigenAdj} 
-\forall ( {\bf u}, p), \quad  \lambda^\dag \left< \hat{{\bf u}^\dag}, {\bf u}\right> =
- \left< NSL^\dag_{\bf U}( \hat{\bf v},\hat{p^\dag}) ,{\bf u}\right> + \left< \nabla \cdot \hat{\bf u}^\dag,p\right>  
-\ee
-
-Matricial form :
-
-\be{Eigen_Adj_matricial}
-\overline{\lambda}^\dag B \hat{X}\dag = A^T \hat{X}\dag.
-\ee
-
-\end{frame}
-
-\begin{frame}{Adjoint mode and structural sensitivity}
-
-Significance of the adjoint mode :
-
-(optimal perturbation)
-
-\ssp
-%\pause
-
-%Structural sensitivity:
-
-The adjoint eigenmode also allows us to introduce the so-called {\em structural sensitivity tensor } that is defined as 
-\be{Structursens} 
-{\bf{S}}({\bf{x}}) = \frac{|| \hat{\bf u}^\dag|| \,\, ||\hat{\bf u}|| }{{\left<\hat{\bf u}^\dag, \hat{\bf u}\right>}},
-\ee 
-which has became popular in the recent years.
-
-\end{frame}
-
-\subsection{Three ideas to really speed up your linear stability computations !}
-
-\begin{frame}{Three ideas to really speed up your stability computations !}
-
-\begin{itemize}[<+->]
-
-\item Use simple shift-invert for computing a single mode !
-
-\item Adapt your mesh !
-\begin{itemize}
-\item to base flow,
-\item to base flow + eigenmode, 
-\item to base flow + structural sensitivity !
-\end{itemize}
-
-\item Escape the real world : go into complex plane !
-
-\begin{itemize}
-\item Incompressible case : to handle strongly convective instabilities
-
-(example : whisling jet, with Vincenzo Citro \& Raffaele Longobardi)
-
-\item Compressible case : to handle non-reflective boundary conditions
-
-(example : cylinder wake ; with Javier Sierra)
-\end{itemize}
-
-\end{itemize}
-
-\end{frame}
-
-%%%%%%%%%%%%%%%%%% CHAPTER 2 %%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{StabFem : a software that may save your life !}
-\subsection{Qu'es aquò ???}
-
-%\subsection{StabFem : présentation du logiciel}
-
-\begin{frame}{FreeFem++}
-
-Finite element methods are well suited to global stability problerms.
-
-The {\em FreeFem++} software is gaining popularity in the hydrodynamic stabillity community.
- %un outil très populaire dans la communauté de la stabilité hydrodynamique.
-
-\small
-
-\begin{itemize}[<+->]
-%{\color{green} \Smiley{} \quad }  (solides, fluides, thermique, etc...)
-\item
-{\color{green} \Smiley{} \quad } Simple and intuitive syntax directly based on weak formulation.
-%Syntaxe intuitive basée directement sur la formulation faible.
-\item
-{\color{green} \Smiley{} \quad } Powerful and adaptative mesh  (movemesh, adaptmesh, etc...)
-% Mailleur puissant et adaptatif (movemesh, adaptmesh, etc...)
-\item
-{\color{green} \Smiley{} \quad } 2D and 3D.
-\item
-{\color{green} \Smiley{} \quad } Large choice of sequencial and parallel solvers  (Mumps, Petsc/Slepc, ..)
-%Grand choix de solveurs séquentiels ou parallèles (Mumps, Petsc/Slepc, ..)
-\item
-{\color{red} \Frowny{} \quad } Limited graphical interface (ffglut) %Interface graphique limitée (ffglut).
-\item
-{\color{red} \Frowny{} \quad } Interpreted language : not suited to functional programming (but powerful macros).
-%Language interprété : pas adapté à la programmation fonctionnelle (mais des macros puissantes).
-\item
-{\color{red} \Frowny{} \quad } Syntax may be touchy and debugging sometimes awkward...
-%Syntaxe "chatouilleuse" et débuggage parfois complexe...
-\end{itemize}
-\end{frame}
-
-\begin{frame}{Why interface FreeFem++ with another software ?}
-
-\small
-
-\begin{itemize}[<+->]
-
-\item %Stratégie avant "StabFem" (2010-2017) :
-Previous strategy :
-
-Computation chain : freefem solvers / shell scripts / postprocessing with tecplot/gnuplot...
-
-%Chaine de calcul : Solveurs FreeFem++ / Scripts Shell / Post-traitement Tecplot / Gnuplot....
-
-%=> 50 programmes quasiment identiques + 10 manières d'effectuer le post-traitement,
-
-%on ne s'y retrouve plus...
-
-=> 50 almost identical programs + 10 ways to handle post-processing => getting crazy !
-
-\ssp
-
-\item %Nécessité d'une surcouche "driver"  pour piloter les calculs et tracer les résultats en mode "terminal" ou par l'intermédiaire de scripts.
-=> Necessity of a  set of "drivers" in a high-level language to monitor computations and draw the results in "command-line" or "script" mode.
-
-\item 
-%Philosophie (à terme) : 1 travail (1 article) = 1 unique script Matlab pour reproduire tous les calculs et générer toutes les figures 
-Philosophy (objective) : one work (one paper) = 1 unique program to generate all results and produce all figures.
-(cf. Basilisk...)
-
-%\item Choix actuel  : Drivers en Matlab/Octave
-
-\end{itemize}
-
-\end{frame}
+\section{StabFem : présentation du logiciel}
 
@@
 
-\item Designed for both research  \& education.
-
 \item Initially  oriented towards Global Stability Approches (Linear \& Nonlinear) but actually allowing a larger number of computations
@@
 
-\item Freeware, based on two softwares : FreeFem++ and \sout{Matlab}/{\color{red}Octave }
+\item Freeware, based on two softwares : FreeFem++ and \sout{Matlab} %-> Octave ? Python ?
 
@@
 }
+
+\end{itemize}
+
+\end{frame}
+
+\begin{frame}{FreeFem++}
+
+Les méthodes d'éléments finis sont bien adaptés aux problèmes de stabilité globale.
+
+Le logiciel {\em FreeFem++} est un outil très populaire dans la communauté de la stabilité hydrodynamique.
+
+\small
+
+\begin{itemize}[<+->]
+%{\color{green} \Smiley{} \quad }  (solides, fluides, thermique, etc...)
+\item
+{\color{green} \Smiley{} \quad } Syntaxe intuitive basée directement sur la formulation faible.
+\item
+{\color{green} \Smiley{} \quad } Mailleur puissant et adaptatif (movemesh, adaptmesh, etc...)
+\item
+{\color{green} \Smiley{} \quad } 2D et 3D.
+\item
+{\color{green} \Smiley{} \quad } Grand choix de solveurs séquentiels ou parallèles (Mumps, Petsc/Slepc, ..)
+\item
+{\color{red} \Frowny{} \quad } Interface graphique limitée (ffglut).
+\item
+{\color{red} \Frowny{} \quad } Language interprété : pas adapté à la programmation fonctionnelle (mais des macros puissantes).
+\item
+{\color{red} \Frowny{} \quad } Syntaxe "chatouilleuse" et débuggage parfois complexe...
+\end{itemize}
+\end{frame}
+
+\begin{frame}{Pourquoi interfacer FreeFem++ avec un autre logiciel ?}
+
+\small
+
+\begin{itemize}[<+->]
+
+\item Stratégie avant "StabFem" (2010-2017) :
+
+Chaine de calcul : Solveurs FreeFem++ / Scripts Shell / Post-traitement Tecplot / Gnuplot....
+
+=> 50 programmes quasiment identiques + 10 manières d'effectuer le post-traitement,
+
+on ne s'y retrouve plus...
+
+\ssp
+
+\item Nécessité d'une surcouche "driver"  pour piloter les calculs et tracer les résultats en mode "terminal" ou par l'intermédiaire de scripts.
+
+\item Idée (à terme) : 1 travail (1 article) = 1 unique script Matlab pour reproduire tous les calculs et générer toutes les figures 
+(cf. Basilisk...)
+
+\item Choix actuel  : Drivers en Matlab (solution non satisfaisante a terme, pb. licences...)
 
@@
 
-%\section{Using StabFem for Linear stability }
+\section{Using StabFem for Linear stability }
 
-\subsection{Demonstration for the wake of a cylinder}
+\begin{frame}{Stabilité globale : qu'es aquò ?? }
+
+Les problèmes d'instabilités sont omniprésents en mécanique des fluides.
+
+\ssp
+
+Leur résolution fait appel à une classe de méthodes numériques spécifiques, 
+complémentaires aux approches de simulation directe, qui sont actuellement en plein développement.
+
+\ssp
+
+On parle {\em stabilité globale} quand la géométrie du problème necessite une résolution en 2D (ou en 3D).
+
+\ssp
+
+(par opposition à {\em stabilité locale} quand des directions d'invariance (écoulement parallèle par ex.) permettent de rammener le problème à une résolution en 1D).
+
+\end{frame}
+
+\begin{frame}{Stabilité globale : liste des types de problèmes et cas-tests}
+
+\scriptsize
+
+\begin{itemize}
+\item CYLINDER  		\qquad -> 2D incompressible, objet fixe
+
+\item CYLINDER\_VIV \qquad 	-> 2D incompressible, objet mobile
+
+(Stage Diogo Ferrera-Sabino)
+
+\item IMPACTINGJET  		\qquad -> 2D incompressible, 3D stability.
+
+(with David LoJacono)
+
+\item CYLINDER\_Compressible  \qquad -> 2D compressible
+
+(Javier Serra, Vincenzo Citro...)
+
+\item BIRDCALL \qquad -> 2D-axisymmetric, incompressible or "augmented incompressible"
+
+(with R. Longobardi, V. Citro....)
+
+\item POROUS\_DISK \qquad -> 2D-axisymmetric, with porous object
+
+(stage Adrien Rouvière)
+
+\item LiquidBridges -> 2D axi, with deformable free surface
+
+(stage Nabil Achour)
+
+\item ROTATING\_POLYGONS
+
+(with Jérôme Mougel...)
+\item ....
+
+\end{itemize}
+
+=> Illustration dans le cas CYLINDER
+
+\end{frame}
 
@@
 
-\item Does a number of post-processing (sort the eigenvalues, update the "shift" in continuation mode...)
-
 \item Returns a matlab "structure" object containing all the data needed for post-processing and subsequent usage.
@@
 \end{itemize}
-
-\end{frame}
-
-\subsection{List of test-cases currently available}
-
-\begin{frame}{StabFem : list of test-cases currently available (or under development...)}
-
-\scriptsize
-
-\begin{itemize}
-\item CYLINDER  		\qquad -> 2D incompressible, objet fixe
-
-\item CYLINDER\_VIV \qquad 	-> 2D incompressible, objet mobile
-
-(Stage Diogo Ferrera-Sabino)
-
-\item IMPACTINGJET  		\qquad -> 2D incompressible, 3D stability.
-
-(with David LoJacono)
-
-\item CYLINDER\_Compressible  \qquad -> 2D compressible
-
-(Javier Serra, Vincenzo Citro...)
-
-\item BIRDCALL \qquad -> 2D-axisymmetric, incompressible or "augmented incompressible"
-
-(with R. Longobardi, V. Citro....)
-
-\item POROUS\_DISK \qquad -> 2D-axisymmetric, with porous object
-
-(stage Adrien Rouvière)
-
-\item LiquidBridges -> 2D axi, with deformable free surface
-
-(stage Nabil Achour)
-
-\item ROTATING\_POLYGONS
-
-(with Jérôme Mougel...)
-\item ....
-
-\end{itemize}
-
-=> Illustration dans le cas CYLINDER
-
-\end{frame}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{frame}{Whistling jets : axisymmetric flow through a two-hole configuration}
-(with Raffaele Longobari, Vincenzo Citro \& others...)
-
-\includegraphics[width=.9\linewidth]{FIGURES/WhistlinJetMode.png}
-\end{frame}
-
-\begin{frame}{2D around a spring-mounted cylinder...}
-(with Diogo Ferreira Sabino \& Olivier Marquet)
-\end{frame}
-
-\begin{frame}{2D flow around a compressible cylinder...}
-(in fast progress with Javier Sierra...)
-\end{frame}
-
-\begin{frame}{Flow around (and through) a porous (\& rotating) disk...}
-(with Adrien Rouvière \& D. Lo Jacono)
-
-\includegraphics[width=.6\linewidth]{FIGURES/Ux_Re200_Da1e-2.png}
-
-\end{frame}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{frame}{Liquid bridges...}
-
-\begin{description}
-%\item{Directory in the StabFem project :}  \texttt{LiquidBridges}
-%\item{Main contributors :} D. Fabre.
-\item{Reference :} Chireux et al., Phys. Fluids, 2015.
-\end{description}
-
-\begin{figure}
-\includegraphics[width=.5\linewidth]{../LiquidBridges/FIGURES/Bridges_NV_Eigenmodes_phi_cyl_L3_5.png}
-\caption{Oscillation modes of a liquid bridge of aspect ratio $L/R=4$ and reduced volume $V^ =$...}
-\label{Bridges_NV_Eigenmodes_phi_cyl_L3_5}
-\end{figure}
-
-\begin{figure}
-\includegraphics[width=.45\linewidth]{../LiquidBridges/FIGURES/Bridges_NV_coal_omega.png}
-\includegraphics[width=.45\linewidth]{../LiquidBridges/FIGURES/Bridges_NV_coal_omega.png}
-\caption{Oscillation frequencies of a liquid bridge resulting from the coalescence of two spherical droplets
-as function of $L^* =L/R$
-(figures 11,12 of Chireux et al.)
-}
-\label{Bridges_NV_Eigenmodes_phi_cyl_L3_5}
-\end{figure}
-
-\end{frame}
-
-\begin{frame}{rotating polygons...}
-
-\begin{description}
-%\item{Directory in the StabFem project :}  \texttt{ROTATINGPOLYGONS}
-%\item{Main contributors :} J. Mougel, D. Fabre
-\item{Reference :} Mougel et al., JFM 2018 
-\end{description}
-
-\begin{figure}
-\includegraphics[width=.8\linewidth]{../ROTATING_POLYGONS/FIGURES/POLYGONS_modes.png}
-\caption{Oscillation modes of a potential vortex for  $a=H/R=0.3$ and $m=3$ (figure 5, 6 of Mougel et al.).}
-\label{Bridges_NV_Eigenmodes_phi_cyl_L3_5}
-\end{figure}
-
-\begin{figure}
-\includegraphics[width=.45\linewidth]{../ROTATING_POLYGONS/FIGURES/POLYGONS_omega.png}
-\includegraphics[width=.45\linewidth]{../ROTATING_POLYGONS/FIGURES/POLYGONS_sigma.png}
-\caption{Oscillation frequencies and amplification rates for f a potential vortex for $m=3$ (figure 4 of Mougel et al.).}
-\label{Bridges_NV_Eigenmodes_phi_cyl_L3_5}
-\end{figure}
-
-\end{frame}
-
-\begin{frame}{Sessile drops...}
-
-With Nabil Achour  ( \& Paul Bonnefis)
-
-\includegraphics[width=.9\linewidth]{FIGURES/SessileDrops_Eigenmodes.png}     % SessileDrops__Eigenmodes_eta.png
-
-- Linear oscillations modes ("pined" or "fixed angle" conditions)
-
-Next steps : investigate contact-line dynamics with WNL methods (cf. Viola, Brun \& Gallaire, 2018)
-
-\end{frame}
-
-%%%%%%%%%%%%%%% PART 3 : NONLINEAR APPROACHES %%%%%%%%%%%%%%%%%%%
-
-\section{Nonlinear global stability approaches : status and future}
-
-%\section{Nonlinear global approaches to hydrodynamic instabilities}
-
-\begin{frame}{Nonlinear global stability approaches : review}
-\small
-
-The linear stability approach approach is the right tool to predict instability threshold ($Re_c$) and the shedding frequency at threshold ($St_c = \omega_c/2\pi$).
-
-\ssp
- But for $Re>Re_c$ it badly predicts the frequency of the limit cycle.
-
-$$
-\includegraphics[width=8cm]{Barkley_figure.png}
-$$
-
- \ssp It has been remarked that stability analysis of the {\em mean flow} obtained by time-averaging the limit cycle gives better predictions (Barkley, Leontini,...).
-
-\ssp
-
-  => Objective of nonlinear stability approaches : provide rational approach to describe the nonlinear oscillation cycle,
-  and provide amplitude equations to describe the transients.
-
-  %Give a rigorous ground to study the stability of {\em mean flow}.
-
-\end{frame}
-\subsection{Weakly nonlinear approach}
-
-\begin{frame}{Weakly nonlinear approach {\small (Sipp \& Lebedev, 2007)}}
-
-\footnotesize
-
-Starting point : weakly non-linear expansion, with multiple scale method.
-
-$$
-\epsilon = \frac{1}{Re_c} - \frac{1}{Re} ; \quad \tau = \epsilon^2 t
-$$
-
-\begin{eqnarray}
-{\bf u} &=& {\bf u}_{bc} + \epsilon \left[ A_{wnl} (\tau) \hat{\bf u} e^{i \omega_c t} + c.c. \right] \label{WNL1}\\
-&+& \epsilon^2 \left[ {\bf u}_\epsilon + |A_{wnl}|^2  {\bf u}_{2,0} + \left(  A_{wnl}^2 {\bf u}_{2,2} e^{2 i \omega_c t} + c.c. \right) \right] + {\cal O}( \epsilon ^3)
-\nonumber
-\end{eqnarray}
-
-Resolution at order 2 :
-%Substituting the expansion \ref{WNL2} into the Navier-Stokes equations \ref{NSprimitive} and grouping terms multiplied by the same power of $\epsilon$, a hierarchy of equations is obtained.
-The order $\epsilon^0$ gives directly the base flow at $Re_c$.
-The order $\epsilon^1$
-%corresponds to the linear neutral eigenmode as computed in the first part of this article.
-%The order $\epsilon^2$ contains three terms respectively computed as the solutions of the following linear problems:
-\begin{eqnarray}
- {\cal LNS}_{{\bf u}_{bc}} ({\bf u}_\epsilon) - 2 \nabla \cdot {\mathsf D}({\bf u}_{bc}) &=&0,
-\label{eq:LL1} \\
-{\cal LNS}_{{\bf u}_{bc}} ({\bf u}_{2,0}) &=& {\cal C}(\hat{\bf u},\overline{\hat{\bf u}}), \label{eq:LL2} \\
-{\cal LNS}_{{\bf u}_{bc}} ({\bf u}_{2,2}) - 2 i \omega_c {\bf u}_{2,2}  &=& \frac{1}{2} {\cal C}(\hat{\bf u},\hat{\bf u}). \label{eq:LL3}
- \end{eqnarray}
-
-Compatibility conditions at order 3 :
-\be{WNL3_2}
-\frac{\partial A_{wnl}}{\partial \tau} = \Lambda A_{wnl} - (\nu_0+\nu_2)  |A_{wnl}|^2 A_{wnl},
-\ee
-%where coefficients $\Lambda$, $\nu_0$ and $\nu_2$ are given by
-\begin{eqnarray}
-\Lambda &=& -\frac{ \left< {\hat{\bf u}}^\dag, 
-\left( {\cal C}({\bf u}_\epsilon, \hat{\bf u}) + 2 \nabla \cdot  {\mathsf D}( \hat{\bf u}) \right) \right>}
-{  \left<  \hat{\bf u}^\dag,\hat{\bf u} \right> },\label{LAMBDA}\\
-\nu_0 &=& \frac{ \left< {\hat{\bf u}}^\dag,  {\cal C}({\bf u}_{20}, \hat{\bf u} ) \right>}
-{  \left<  \hat{\bf u}^\dag,\hat{\bf u} \right> },\label{NU0}\quad
-\nu_2 = \frac{ \left< {\hat{\bf u}}^\dag,  {\cal C}({\bf u}_{22}, \overline{\hat{\bf u}})  \right>}
-{  \left<  \hat{\bf u}^\dag,\hat{\bf u} \right> }.,\label{NU2}
- \end{eqnarray}
-
-%Method : weakly nonlinear expansion
-
-%Order 0 : base-flow
-
-%Order 1 : eigenmode at marginal conditions
-
-%Order 2 : nonresonant linear problems -> direct resolution
-
-%Order 3 : resonant problems : compatibility conditions (Fredholm alternative)
-
-%Resolution thanks to adjoint methods
-
-%=> Amplitude equation
-
-\end{frame}
-
-\subsection{Self-consistent approach}
-
-\begin{frame}{Self-Consistent approach {\small (Mantic-Lugo, Arratia \& Gallaire, 2014)}}
-
-\small
-Starting point : Pseudo-eigenmode decomposition
-
-\be{SC}
-{\bf u } = {\bf u }_m + A_{sc} \left[ \tilde{{\bf u }}_1 e^{\sigma_{sc} t + i \omega_{sc} t} +   \overline{\tilde{\bf u }_1} e^{\sigma_{sc} t  -i \omega_{sc} t} \right],
-\quad
-\left( |\tilde{{\bf u }}_1|| = 1/\sqrt{2}\right)
-\ee
-
-%where ${\bf u }_m$ is the {\em mean flow} as previously defined,  $\tilde{{\bf u }}_1$ is a pseudo-eigenvector which is normalized by the condition  $||\tilde{{\bf u }}_1|| = 1/\sqrt{2}$, $\overline{\tilde{{\bf u }}_1}$ is its complex conjugate,
-where $A_{sc}$ is an amplitude parameter, %directly related to the energy of the oscillating flow, 
-and $\lambda_{sc} = \sigma_{sc} + i \omega_{sc}$ is a pseudo-eigenvalue which depends upon the parameter $A_{sc}$.
-
-\pause
-=> SC-model equations
-
-\begin{subequations}\label{sc12}
-\begin{eqnarray}
-{\cal NS}(  {\bf u }_m ) - A_{sc}^2 {\cal C}( \tilde{{\bf u }}_1, \overline{\tilde{\bf u }_1}) = 0, 
-\label{sis1}
-\\
-(\sigma_{sc} + i \omega_{sc}) \tilde{{\bf u }}_1 =  {\cal LNS}_{{\bf u }_m}(\tilde{{\bf u }}_1 ).
-\label{sis2}
-\end{eqnarray}
-\end{subequations}
-
-\pause
-
-=> Amplitude equation :
-$$
-\frac{\partial A_{sc}}{\partial t} = \sigma_{sc} (A_{sc}) A_{sc}
-$$
-
-\pause
-
-%$\sigma(A_E
-
-Resolution method of {\small (Mantic-Lugo 2014)}: double iterative loop
-
-- Inner loop :
-
-$\quad$ Fix $A_{sc}$, iteratively solve (eigenvalue problem + calculation of mean flow) up to convergence for $(\sigma_{sc} + i \omega_{sc})$ as function of $A_{sc}$.
-
-- Outer loop :
-
-$\quad$ iterate over $A_{sc}$ to reach  $\sigma_{sc} = 0$
-
-\end{frame}
-
-\begin{frame}{Self-Consistent approach : a direct resolution method}
-
-\small
-
-Let's forget about transients, and look directly for a description of the saturated cycle:
-%We thus start with a truncated Fourier decomposition of the limit cycle under the form:
-
-\be{HB}
-{\bf u } = {\bf u }_m + {\bf u }_{1,c} \cos( \omega t ) +   {\bf u }_{1,s} \sin( \omega t ),
-\ee
-where ${\bf u }_{1,c}$ and ${\bf u }_{1,s}$ are two {\em real} fields %describing the nonlinear perturbation at two instants separated by a quarter-period of oscillation,
-
-and $\omega$ is the (real) oscillation frequency of the limit cycle.
-%The connection with the definition of Manti\v{c}-Lugo is as follows :
-%\be{HBtoSC}
-%\left( {\bf u }_{1,c} - i {\bf u }_{1,s} \right) = 2 A_{sc} \tilde{{\bf u }}_1.
-%\ee
-
-\ssp
-
-=> Equations :
-%Injecting this ansartz into the Navier-Stokes equations and taking the mean value and the first Fourier component leads to the following coupled equations:
-\begin{subequations}\label{eq_principal}
-\begin{eqnarray}
-{\cal NS}(  {\bf u }_m ) = \frac{{\cal C}( {\bf u }_{1,c}, {\bf u }_{1,c}) +{\cal C}( {\bf u }_{1,s}, {\bf u }_{1,s})}{4}, 
-\label{HBEq0}
-\\
- \omega {\bf u }_{1,s} =  {\cal LNS}_{{\bf u }_m}(  {\bf u }_{1,c} ),
-\label{HBEq1}
-\\
- -\omega {\bf u }_{1,c} =  {\cal LNS}_{{\bf u }_m}(  {\bf u }_{1,s} ).
-\label{HBEq1b}
-\end{eqnarray}
-\end{subequations}
-
-We need an extra scalar equation to fix the phase of the cycle, e.g:
-
-\begin{equation}
-\Im \{F_y({\bf u}_1) \} =0.
-\label{HBphase}
-\end{equation}
-
-=> Direct resolution with Newton method !
-\ssp
-
-Remarks :
-
-- We need a good guess : use the WNL to produce it !
-
-- Computation can be optimized using preconditioning (Ask Olivier...)
-
-\end{frame}
-
-\subsection{Harmonic-balance approach}
-
-\begin{frame}{Harmonic-Balance}
-
-\small
-
-%The Navier-stokes equations can be posed as
-
-%\begin{eqnarray}
-%\partial_t {\bf u} = {\cal NS} ({\bf u},p)
-%\equiv - {\bf u} \cdot \nabla {\bf u} - \nabla p + \frac{2}{Re}  \nabla \cdot {\mathsf{D}}({\bf u}), \label{NSprimitive}  \\
-%\nabla \cdot {\bf u} = 0. \label{eq:DIV}
-%\end{eqnarray}
-
-We start with the following expansion:
-\begin{equation}
-{\bf u } = {\bf u }_m + {\bf u }_{1,c} \cos( \omega t ) +   {\bf u }_{1,s} \sin( \omega t ) +{\bf u }_{2,c} \cos(2 \omega t ) +   {\bf u }_{2,s} \sin(2 \omega t ),
-\end{equation}
-
-arriving to a system of equations:
-\begin{subequations}\label{eq_principal}
-\begin{eqnarray}
-{\cal NS}(  {\bf u }_m) = \frac{{\cal C}( {\bf u }_{1,c}, {\bf u }_{1,c}) +{\cal C}( {\bf u }_{1,s}, {\bf u }_{1,s})+{\cal C}( {\bf u }_{2,c}, {\bf u }_{2,c})+{\cal C}( {\bf u }_{2,s}, {\bf u }_{2,s})}{4},
-\label{HBEq0}
-\\
- \omega {\bf u }_{1,s} =  {\cal L}_{{\bf u }_m}(  {\bf u }_{1,c} )-\frac{1}{2}\Big(
- {\cal C}( {\bf u }_{1,c}, {\bf u }_{2,c})+{\cal C}( {\bf u }_{1,s}, {\bf u }_{2,s})
- \Big),
-\label{HBEq1}
-\\
- -\omega {\bf u }_{1,c} =  {\cal L}_{{\bf u }_m}(  {\bf u }_{1,s} )-\frac{1}{2}\Big(
- {\cal C}( {\bf u }_{1,c}, {\bf u }_{2,s})-{\cal C}( {\bf u }_{1,s}, {\bf u }_{2,c})
- \Big),
-\label{HBEq1b}
-\\
- 2 \omega {\bf u }_{2,s} =  {\cal L}_{{\bf u }_m}(  {\bf u }_{2,c} )-\frac{1}{4}\Big(
- {\cal C}( {\bf u }_{1,c}, {\bf u }_{1,c})-{\cal C}( {\bf u }_{1,s}, {\bf u }_{1,s})
- \Big),
-\label{HBEq2}
-\\
- -2\omega {\bf u }_{2,s} =  {\cal L}_{{\bf u }_m}(  {\bf u }_{2,s} )-\frac{1}{2}
- {\cal C}( {\bf u }_{1,s}, {\bf u }_{1,c}),
-\label{HBEq2b}
-\end{eqnarray}
-\end{subequations}
-%where ${\cal C}( {\bf U} , {\bf u}) = \left( {\bf U} \cdot \nabla \right) {\bf u} + \left( {\bf u} \cdot \nabla \right)  {\bf U}$.
-
-%To allow resolution we thus need an extra equation to fix this phase, e.g:
-\begin{equation}
-\Im \{F_y({\bf u}_1) \} =0.
-\label{HBphase}
-\end{equation}
-
-=> Direct Newton resolution again
-\end{frame}
-
-\begin{frame}{Harmonic-Balance : results for the cylinder ! }
-
-%\begin{figure}
-\begin{center}
-\includegraphics[width=.32 \linewidth]{../CYLINDER/FIGURES/Cylinder_Strouhal_Re_HB2.png}
-\includegraphics[width=.32 \linewidth]{../CYLINDER/FIGURES/Cylinder_Energy_Re_HB2.png}
-\includegraphics[width=.32 \linewidth]{../CYLINDER/FIGURES/Cylinder_Lx_Re_HB2.png}
-\end{center}
-\begin{center}
-\includegraphics[width=.32\linewidth]{../CYLINDER/FIGURES/Cylinder_Fx_Re_HB2.png}
-\includegraphics[width=.32 \linewidth]{../CYLINDER/FIGURES/Cylinder_Fy_Re_HB2.png}
-\end{center}
-%\caption{Comparison between the weakly nonlinear results (WNL) the harmonic balance data (HB), and baseflow/linear results : Strouhal number $(a)$, Mean drag $(b)$, amplitude of oscillating lift $(c)$, Energy-amplitude of the nonlinear perturbation $(d)$ and recirculation lenght of mean/base flows ($e)$.
-%c_x should be consistent with the drag definition given at beginning
-%}
-%\label{fig:HB_SC_DATA_COMP}
-%\end{figure}
 
@@
 
-\begin{frame}{Conclusions}
-\end{frame}
-
-\appendix{The future of StabFem }
+\section{The future of StabFem }
 

### 2018-07-17 99_Documentation/MANUAL/05_NotesAndTips.tex
Reorganization of the arborescence (redone with « git mv » to keep tracking)

% !TEX root = main.tex

\section{Notes and tips for users and developers}

When contributing to the project you can intervene at two levels:

\begin{itemize}

\item Contributring as a {\em User}  means that you will use the available solvers and drivers for a class of problems already integrated 
in the project. For instance, if you wish to study the wake flow around an elliptical 2D body, which uses the same solvers than the case of a circular cylinder already present in the base.

In this case, you will create a directory for your case (for instance {\em ELLIPSE/}) containing : The mesh generator freefem script 
(for instance {\em Mesh\_Ellipse.edp}), the macro file {\em Macros\_Stabfem.edp}  containing the case-dependent boundary condition and postprocessing detail, and a number of Mablab scripts. O,n the other hand, you will suposedly not modify thecommon files in the source directories (with the exception of the file {\em SOURCES\_MATLAB/SF\_Start.m}).

\item Contributing as a {\em Developer } means that you wish to help integrate new Freefem solver into the project 
(for instance, you want to solve a 2D problem in the Bousinesq approximation, you already have a set of Freefem solvers for this case and you wish to integrate them in the project).

\end{itemize}

\subsection{FAQ}

Here is a kind of FAQ of the projecft, regerouping in random order notes, tips and "good practize recomendations" for users and developers.

\begin {itemize}

\item
At installation (git clone) it is recommended that you install the whole StabFem project in your home directory and that you do
not remove or displace the parts of the project that you don't (immediately) need. Otherwise this will perturb the operation of the version manager git. 
In short :  if you there are parts you think you don't need, don't remove them, just ignore them !

\item good usage of the "verbosity"' parameter ...

\end{itemize}

\subsection{Note on the usage of github}

The project is supported by the git subversion manager program. Here are a fexw tips/recommendations :

\paragraph{If you are contributing as a user}

\begin {itemize}

\item After the initial git clone, you may want to get the latest development of the main branch using {\em git pull}. This will only update the sources in the common repositories, not your own files.

If you have modified the {\em SF\_Start.m} file and/or made minor modifications to other files that you wish to keep in your local version but do not want to export to the main branch odf the project, the procedure is to do successively :

git stash

git pulll

git stash apply.

(don't be afraid, any "mistake" with git can be undone !)

\item 
If you want to incorporate your work in the project repository (normally after everything is validated...) you should do the following :

git add "files".  {\em (please add only source files of your case directory, such as freefem mesh generator and macro scripts, an example matlab script producing sample results for your case, and possibly matlab functions you have developed for your own case and are not sure they will work for other cases)}

git commit -a

git push

{\em For this last step you need to be register as a contributor, just ask !}

\item (...)

\end{itemize}

\paragraph{If you are contributing as a developer}

\begin {itemize}

\item The best way is to creat a "fork" or a "branch" (still not sure what is the most efficient)

\item Once you have your own branch/fork, use gut commit / git push as frequently as you wish !

\item If you want to merge with the main branch, create a {\em pull request}.

\item (...)

\end{itemize}

\section{Notes/tips about FreeFem}

All the Freefem tricks which are not in the manual....

### 2018-07-17 99_Documentation/MANUAL/05_StabFem_logic.tex
Reorganization of the arborescence (redone with « git mv » to keep tracking)

\chapter{How a StabFem project works}

A \ti{StabFem} project have a directory, for example \directory{StabFemm>CYLINDER} where it can be found: 
\begin{enumerate}
\item The \texttt{*.m} files corresponding to the \ti{Matlab} scripts. Normally, a main script can be found, e.g. \keys{SCRIPT\_CYLINDER\_DEMO.m} ;
\item A directory \directory{StabFemm>CYLINDER > WORK} (if not, it will be created when \ti{Matlab} script run) where it can be found the output data;
\item All the \texttt{*.edp} specific to the project and to be executed automatically by the \ti{Matlab} interface. E.g.: The \keys{Mesh*.edp}, the \keys{Macros\_StabFem.edp}, \keys{Param\_Adaptmesh.edp}, etc.
\end{enumerate}

\section{Running logic of a \ti{StabFem} project}

When one executes the main script \texttt{*.m}, both local and share scripts are executed. For a commum project, the following steps done:

\begin{enumerate}
\item Launch the share script \keys{SF\_Start.m}:
\begin{lstlisting}
run('../SOURCES_MATLAB/SF_Start.m');
\end{lstlisting}
creating the following directories as global variables and adding the \ti{sfdir} to the \ti{matlab} paths:
\begin{lstlisting}
ff = '/PRODCOM/Ubuntu16.04/freefem/3.51/gcc-5.4-mpich_3.2/bin/FreeFem++'; % on IMFT network
sfdir = '~/StabFem/SOURCES_MATLAB/'; % where to find the matlab drivers
ffdir = '~/StabFem/SOURCES_FREEFEM/'; % where to find the freefem scripts
ffdatadir = './WORK/';
addpath(sfdir);
\end{lstlisting}
It also creates the \keys{SF\_Geom.edp} need for \ti{FreeFemm++}.

\item Then, a mesh and a baseflow are generated for the project with the help of the share script \keys{SF\_Init.edp} located in \directory{StabFemm>SOURCES\_MATLAB},e.g.:

\begin{lstlisting}
baseflow=SF_Init('Mesh_Cylinder.edp', [-40 80 40]);
\end{lstlisting}

The detailed input/output parameters are discussed in next chapter (\textcolor{red}{To do...}). It will execute \keys{Mesh*.edp} and generate in the current path the \keys{mesh.msh}, \keys{mesh.ff2m}, \keys{mesh\_init.msh},\keys{SF\_Init.ff2m}, \keys{BaseFlow\_init.txt} and \keys{BaseFlow\_init.ff2m} files.

The path \directory{StabFemm>CYLINDER > WORK>BASEFLOWS} is created. This is where all the base flow for the different Reynolds numbers will be stored.

\item The baseflows for for different parameters ($Re$, Porosity,...) are generated by the command: 
\begin{lstlisting}
baseflow=SF_BaseFlow(baseflow,'Re',10);
\end{lstlisting}
executing the commom scritpt \keys{SF\_BaseFlow.m}. This script will read the \ti{baseflow.mesh.problemtype} parameter and execute the corresponding Newton routing \texttt{Newton*.edp} located at \directory{StabFemm>SOURCES\_FREEFEM} in order to generate the corresponding baseflows in their path.

\item Then, a adaptation of the mesh is made to refine and converge the results for the correct baseflow, with the following command:
\begin{lstlisting}
baseflow=SF_Adapt(baseflow,'Hmax',10,'InterpError',0.005);
\end{lstlisting}
The refine parameters are written in \keys{Param\_Adaptmesh.edp}\textcolor{red}{(why?)} in the current path. \keys{Adapt\_Mode.edp} is executed from \ti{ffdir} to refine the mesh. \textcolor{red}{(Some files are created...explain...)}

\item A mesh adaptation taking into account the eigenmode can be done: for that, first a solution have to be commuted first giving the eigenmodes. Then the mesh adaptation can be done like it was done in last step. 
\begin{lstlisting}
[ev,em] = SF_Stability(baseflow,'shift',0.04+0.74i,'nev',1,'type','D');
[baseflow,em]=SF_Adapt(baseflow,em,'Hmax',10,'InterpError',0.01);
\end{lstlisting}

Here, the eigenvalue problem has been solved with a shitf-and-invert iteration process, detail in next chapter(\textcolor{red}{(to do)}). \keys{SF\_Stability.m} is once again located at \ti{sfdir}.

\item After the former step, once wisely used, post-processing can be made. At that stage, each project have its particularities and it will be detailed in their dedicated chapters.
\end{enumerate}

\section{Create a \ti{StabFem} project}

In order to create a project in \ti{StabFem} one has to start to code the scripts in \ti{FreeFEM++}.

\medskip

\begin{leftbar}
Attention:  When creating the different \texttt{*.edp} files, one has to pay attention on the compulsory inputs and output of the \ti{Matlab} interface.
\end{leftbar}

Then, the \ti{Mathlab} scripts, with the previously presented style, have to be created.

\medskip

\begin{leftbar}
Attention:  The different \texttt{*.m} files created in the particular directory will be used only in your project, so you can used them as you like; but, once the common files are used, they must not be changed without careful examination of the impact on the other projects.
\end{leftbar}

Commonly, the following files are needed in the current file:

\paragraph{\ti{FreeFEM++} file: SCRIPT\_*.edp}

Here, the problem is defined. See chapter \textcolor{red}{(to do)} for more details. It can be a eigenvalue problem, a forced problem, etc. To define the problem, see the FreeFEM++ documentation \cite{FFdoc}\footnote{http://www.freefem.org/ff++/ftp/freefem++doc.pdf}.

\paragraph{\ti{FreeFEM++} file: Mesh\_*.edp}

File where the mesh of the problem and the convenient files are generated.

\paragraph{\ti{FreeFEM++} file: Macros\_StabFem.edp}

Macros are a powerful tool in \ti{FreeFEM++}. In this file all the Macros specific of the project are created. This macros will be used both by the \texttt{*.edp} scripts of one's problem and by the  common scripts located at \directory{StabFemm>SOURCES\_FREEFEM}.

\paragraph{\ti{Matlab} file: mains\_cript.m}

This script will be organise like in the previously presented style. Then, the a  different treatment is given to each problem, and one can be inspired by the project already created.

### 2018-07-17 99_Documentation/MANUAL/12_StabFem_GlobalStability.tex
Reorganization of the arborescence (redone with « git mv » to keep tracking)

--- 2018-07-17 99_Documentation/MANUAL/05_StabFem_logic.tex
@@
-\chapter{How a StabFem project works}
+% !TEX root = main.tex
+
+\chapter{Using StabFem for globals stability calculations}
+
+The stabfem software was initially designed to perforrm global stability calculations (linear and nonlinear).
+This chapter explains this throufh the example of the wake of a cylinder.
+
+The theory is fully explained in the submitted paper [...]. In this chapter we explain the implementation issues.
+
+{\em 
+Newt of the chapter is initial version of Diogo,n to be recast)
+}
 
@@
 \item A directory \directory{StabFemm>CYLINDER > WORK} (if not, it will be created when \ti{Matlab} script run) where it can be found the output data;
-\item All the \texttt{*.edp} specific to the project and to be executed automatically by the \ti{Matlab} interface.
+\item All the \texttt{*.edp} specific to the project and to be editexecuted automatically by the \ti{Matlab} interface.
 E.g.: The \keys{Mesh*.edp}, the \keys{Macros\_StabFem.edp}, \keys{Param\_Adaptmesh.edp}, etc.

### 2018-07-17 99_Documentation/MANUAL/210_StabFem_LiquidBridges.tex
Reorganization of the arborescence (redone with « git mv » to keep tracking)

--- 2018-07-17 99_Documentation/ARTICLE_STABFEM/Beamer_10juillet2018.tex
@@
-\documentclass{beamer}
+% !TEX root = main.tex
 
-\usepackage[frenchb]{babel}
-
-\usepackage[T1]{fontenc}
-%\usepackage[latin1]{inputenc}
-\usepackage[utf8]{inputenc}
-
-\usepackage{marvosym}
-
-\newcommand{\be}[1]{ \begin{equation} \label{#1}}
-\newcommand{\ee}{\end{equation}}
-
-\newcommand{\bes}[1]{ \begin{equation} \label{#1}\begin{array}{rl}}
-\newcommand{\ees}{\end{array}\end{equation}}
-
-\usepackage[normalem]{ ulem }
-\usepackage{soul}
-
-% \usetheme{default} -> A utiliser dans un premier temps
-
-% \usetheme{Warsaw} -> A utiliser dans un second temps
-
-\input{../99_Documentation/01_Preamble.tex}
-
-\newcommand{\ssp}{\vspace{.2cm} }
-
-\title{A (kind of) practical review on global stability approches}
-
-\subtitle{}
-
-\author{D. Fabre}
-
-\institute{IMFT, groupe InterfaceS}
-
-\date{Informal Workshop "D\&D", 10 juillet 2018}
-
-\AtBeginSection{
-\frame{\tableofcontents[current]}
-}
-
-\begin{document}
-
-\begin{frame}
-
-\titlepage
-
-\end{frame}
-
-\section{Linear global stability  : basic principles, and a few useful tricks}
-
-\subsection{Qu'es aquò ??}
-
-\begin{frame}{Qu'es aquò ?? }
-
-Instability problems are ubiquous in fluid mechanics
-
-\ssp
-
-Numerical resolution of such problems resorts to a specific class of numerical methods, which replace
-time-stepping of the full equations by  assumptions about temporal dependance (modal expansion, amplitude equations, etc...)
-
- \ssp These methods are complementary to direct numerical resolution methods (i.e. time-stepping).
-
-%Leur résolution fait appel à une classe de méthodes numériques spécifiques, 
-%complémentaires aux approches de simulation directe, qui sont actuellement en plein développement.
-
-\ssp
-
-We refer to {\em global stability} when the geometry requires resolution in 2 (or 3) spatial dimensions.
-
-%On parle {\em stabilité globale} quand la géométrie du problème necésssite une résolution en 2D (ou en 3D).
-
-\ssp
-
-(as opposed to {\em local stability } which takes advantage of invariance directions (parallel flow, etc...)
-to bring the problem to spatially 1D).
-
-%(par opposition à {\em stabilité locale} quand des directions d'invariance (écoulement parallèle par ex.) permettent de rammener le problème à une résolution en 1D).
-
-\end{frame}
-
-%\subsection{Step 0 : computation of a base flow}
-
-\begin{frame}{Base flow}
-
-We look for a steady base-flow $({\bf u}_b;p_b)$ satisfying the steady Navier-Stokes equations, i.e. 
-$NS ({\bf u}_b,p_b) = 0$.
-
-Suppose that we have a 'guess' for the base flow $[{\bf u}_b^g,p_b^g]$  which almost satisfies the equations.  We look for a better approximation under the form
-\be{Newton1}
-[{\bf u}_b,p_b]  = [{\bf u}_b^g,p_b^g] + [\delta {\bf u}_b, \delta p_b] = 0.
-\ee
-
-Injecting into the Navier-Stokes equation lead to $$
-NS ({\bf u}_b^g,p_b^g) + NSL_{{\bf u}_b^g}(\delta {\bf u}_b,\delta p_b)$$
-
-Where $NSL$ is the linearised Navier-Stokes operator. 
-%defined by its action on a flow field $({\bf u} ; p)$ as follows
-
-=>  matricial problem with the form $A \cdot \delta X = Y$. The procedure of Newton iteration is to solve iteratively this set of equations up to convergence.
-
-\end{frame}
-
-%\subsection{Step 1 : Eigenvalue computation}
-
-\begin{frame}{Linear stability}
-
-\be{startmodepropre}
-{\bf u} = {\bf u}_b + \epsilon \hat{\bf u} e^{\lambda t} 
-\ee
-
-The eigenmodes is governed by the linear problem 
-$$\lambda \hat{{\bf u}} = NSL_{{\bf u}_b}( \hat{\bf u},\hat{p})$$,
-
-After discretization we end up with an eigenvalue problem with the matricial form
-\be{Eigen_matricial}
-\lambda B \hat{X} = A \hat{X}
-\ee
-
-\ssp
-Iterative method : single-mode shift-invert iteration
-$$
-X^{n} =  (A- \lambda_{shift} B)^{-1} B X^{n-1}
-$$
-
-Generalization : Arnoldi
-
-\end{frame}
-
-%\subsection{Adjoint eigenmodes and structural sensitivity}
-
-\begin{frame}{Adjoint problem}
-
-\small
-
-Define a scalar product :
-$$
-\left< \phi_1, \phi_2 \right> = \int_\Omega \overline{\phi_1} \cdot \phi_2   \mbox{ d} \Omega
-$$
-
-We can first define the {\em adjoint linearised Navier-Stokes operator} $NSL^\dag$ defined by the property:
-\bes{NSLAdj}
-\forall ( {\bf u}, p ; {\bf u}^\dag, p^\dag), & \left< NSL^\dag_{\bf U}( {\bf u}^\dag,p^\dag) ,{\bf u}\right> + \left< \nabla \cdot {\bf u}^\dag,p\right>  \\
-=& \left<{\bf u}^\dag, NSL_{\bf U} ({\bf u},p)\right> + \left< p^\dag, \nabla \cdot {\bf u}\right>.
-\ees
-We can then define the adjoint eigenmodes as the solutions to the eigenvalue problem 
-\be{EigenAdj} 
-\forall ( {\bf u}, p), \quad  \lambda^\dag \left< \hat{{\bf u}^\dag}, {\bf u}\right> =
- \left< NSL^\dag_{\bf U}( \hat{\bf v},\hat{p^\dag}) ,{\bf u}\right> + \left< \nabla \cdot \hat{\bf u}^\dag,p\right>  
-\ee
-
-Matricial form :
-
-\be{Eigen_Adj_matricial}
-\overline{\lambda}^\dag B \hat{X}\dag = A^T \hat{X}\dag.
-\ee
-
-\end{frame}
-
-\begin{frame}{Adjoint mode and structural sensitivity}
-
-Significance of the adjoint mode :
-
-(optimal perturbation)
-
-\ssp
-%\pause
-
-%Structural sensitivity:
-
-The adjoint eigenmode also allows us to introduce the so-called {\em structural sensitivity tensor } that is defined as 
-\be{Structursens} 
-{\bf{S}}({\bf{x}}) = \frac{|| \hat{\bf u}^\dag|| \,\, ||\hat{\bf u}|| }{{\left<\hat{\bf u}^\dag, \hat{\bf u}\right>}},
-\ee 
-which has became popular in the recent years.
-
-\end{frame}
-
-\subsection{Three ideas to really speed up your linear stability computations !}
-
-\begin{frame}{Three ideas to really speed up your stability computations !}
-
-\begin{itemize}[<+->]
-
-\item Use simple shift-invert for computing a single mode !
-
-\item Adapt your mesh !
-\begin{itemize}
-\item to base flow,
-\item to base flow + eigenmode, 
-\item to base flow + structural sensitivity !
-\end{itemize}
-
-\item Escape the real world : go into complex plane !
-
-\begin{itemize}
-\item Incompressible case : to handle strongly convective instabilities
-
-(example : whisling jet, with Vincenzo Citro \& Raffaele Longobardi)
-
-\item Compressible case : to handle non-reflective boundary conditions
-
-(example : cylinder wake ; with Javier Sierra)
-\end{itemize}
-
-\end{itemize}
-
-\end{frame}
-
-%%%%%%%%%%%%%%%%%% CHAPTER 2 %%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{StabFem : a software that may save your life !}
-\subsection{Qu'es aquò ???}
-
-%\subsection{StabFem : présentation du logiciel}
-
-\begin{frame}{FreeFem++}
-
-Finite element methods are well suited to global stability problerms.
-
-The {\em FreeFem++} software is gaining popularity in the hydrodynamic stabillity community.
- %un outil très populaire dans la communauté de la stabilité hydrodynamique.
-
-\small
-
-\begin{itemize}[<+->]
-%{\color{green} \Smiley{} \quad }  (solides, fluides, thermique, etc...)
-\item
-{\color{green} \Smiley{} \quad } Simple and intuitive syntax directly based on weak formulation.
-%Syntaxe intuitive basée directement sur la formulation faible.
-\item
-{\color{green} \Smiley{} \quad } Powerful and adaptative mesh  (movemesh, adaptmesh, etc...)
-% Mailleur puissant et adaptatif (movemesh, adaptmesh, etc...)
-\item
-{\color{green} \Smiley{} \quad } 2D and 3D.
-\item
-{\color{green} \Smiley{} \quad } Large choice of sequencial and parallel solvers  (Mumps, Petsc/Slepc, ..)
-%Grand choix de solveurs séquentiels ou parallèles (Mumps, Petsc/Slepc, ..)
-\item
-{\color{red} \Frowny{} \quad } Limited graphical interface (ffglut) %Interface graphique limitée (ffglut).
-\item
-{\color{red} \Frowny{} \quad } Interpreted language : not suited to functional programming (but powerful macros).
-%Language interprété : pas adapté à la programmation fonctionnelle (mais des macros puissantes).
-\item
-{\color{red} \Frowny{} \quad } Syntax may be touchy and debugging sometimes awkward...
-%Syntaxe "chatouilleuse" et débuggage parfois complexe...
-\end{itemize}
-\end{frame}
-
-\begin{frame}{Why interface FreeFem++ with another software ?}
-
-\small
-
-\begin{itemize}[<+->]
-
-\item %Stratégie avant "StabFem" (2010-2017) :
-Previous strategy :
-
-Computation chain : freefem solvers / shell scripts / postprocessing with tecplot/gnuplot...
-
-%Chaine de calcul : Solveurs FreeFem++ / Scripts Shell / Post-traitement Tecplot / Gnuplot....
-
-%=> 50 programmes quasiment identiques + 10 manières d'effectuer le post-traitement,
-
-%on ne s'y retrouve plus...
-
-=> 50 almost identical programs + 10 ways to handle post-processing => getting crazy !
-
-\ssp
-
-\item %Nécessité d'une surcouche "driver"  pour piloter les calculs et tracer les résultats en mode "terminal" ou par l'intermédiaire de scripts.
-=> Necessity of a  set of "drivers" in a high-level language to monitor computations and draw the results in "command-line" or "script" mode.
-
-\item 
-%Philosophie (à terme) : 1 travail (1 article) = 1 unique script Matlab pour reproduire tous les calculs et générer toutes les figures 
-Philosophy (objective) : one work (one paper) = 1 unique program to generate all results and produce all figures.
-(cf. Basilisk...)
-
-%\item Choix actuel  : Drivers en Matlab/Octave
-
-\end{itemize}
-
-\end{frame}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{frame}{StabFem : Cahier des charges }
-%Equations : 
-%\begin{equation}
-%$$\frac{\partial V }{\partial t} = \nu \frac{\partial^2 V}{\partial y^2} $$
-%\label{eq:navier}
-%\end{equation}
-%(on a supposé pour simplifier qu'il n'y avait pas de gradient de pression autre qu'hydrostatique).
-%Conditions limites : $\left. v\right|_{y=0} = 0$, $\left. v\right|_{y=h} = U(t)$
-
-\begin{itemize}[<+->]
-
-\item StabFem : an open-source and easy-to-use software allowing a large range of computations in fluid mechanics.
-
-\item Designed for both research  \& education.
-
-\item Initially  oriented towards Global Stability Approches (Linear \& Nonlinear) but actually allowing a larger number of computations
-(DNS, linear acoustics, etc...)
-
-\item Multi-platform (Unix, MacOs, Windows) and designed to run on "light" computers (Laptops...)
-
-\item Easy to use/install,
-
-\item Easy to customize to a variety of cases (incompressible, compressible, fixed/free objects, free surfaces,...)
-
-\item Freeware, based on two softwares : FreeFem++ and \sout{Matlab}/{\color{red}Octave }
-
-\item Developed as a collaborative project
-(IMFT, Università di Salerno, ONERA, UPFL, ...)
-
-\item Maintained on Github
-
-\ssp
-{\color{orange}
-\verb! https://github.com/erbafdavid/StabFem !
-}
-
-\end{itemize}
-
-\end{frame}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{frame}{Articulation FreeFem / Matlab}
-
-\scriptsize
-
-\begin{itemize}[<+->]
-
-\item 
-Etage 1 : Solveurs FreeFem++ "briques de base".
-
-Un solveur par "classe de problèmes" (2D incompressible, 2D compressible, Axisymétrique incompressible...) et par "type de calcul" (calcul d'un champ de base, stabilité linéaire, ...)
-
-\item  Etage 2 : drivers Matlab "génériques"
-
-Un unique driver pour chaque "type de calcul" , le choix du bon solveur est fait en fonction 
-des paramètres optionnels fournis au driver.
-
-\item Etage 3 : Les boucles sur les paramètres et la génération des figures sont faites dans un "script principal".
-
-\item Les solveurs et les drivers génériques sont dans des répertoires communs {\bf SOURCES\_MATLAB/} et {\bf SOURCES\_FREEFEM/},
-
-\item Les programmes spécifiques à chaque cas d'étude sont dans un répertoire spécifique.
-
-Exemple : le répertoire "CYLINDRE" contient les programmes suivants :
-
-\begin{enumerate}
-\scriptsize
-\item Mesh\_Cylinder.edp		\qquad -> Génération du maillage
-
-\item Macros\_StabFem.edp \qquad -> Macros case-dependant (conditions limites et post-traitement)
-
-\item SCRIPT\_CYLINDER.m $\qquad$ -> Script "Maitre".
-
-\end{enumerate}
-\end{itemize}
-\pause
-
-{\em Remarques : les programmes FreeFem doivent pouvoir être utilisés directement en dehors du driver StabFem, 
-notamment pour faciliter le développement/débuggage...)}
-
-\ssp
-
-{\em Les contributeurs "utilisateurs" (ex. étudiant M1/M2) ne travaillent qu'à l'étage 3 et ne devraient travailler que sur ces 3 fichiers.
-\ssp
-
-Les contributeurs "développeurs" travaillent aux étages inférieurs...}
-
-\end{frame}
-
-\begin{frame}{Format d'échange des données}
-
-\begin{itemize}[<+->]
-
-\item Format de fichier d'échange ".ff2m", généré par FreeFem++ et relu par Matlab
-
-\item Example d'en-tête d'un fichier .ff2m :
-
-\lstinputlisting[linerange={1-4}]{../EXAMPLE_Lshape/Data.ff2m}
-
-Ligne 4 : "TypeField1 NameField1 TypeField2 NameField2... "
-
-TypeField can be "real" (scalar data), "real.N" (vectorial data), "P1" (data associated to mesh), ...
-
-\item Le fichier est lu et importé sous forme d'une {\em structure matlab}
-
-\item Illustration : cas "EXAMPLE\_Lshape"
-
-\end{itemize}
-
-\end{frame}
-
-%\section{Using StabFem for Linear stability }
-
-\subsection{Demonstration for the wake of a cylinder}
-
-\begin{frame}{First step : Generation of a mesh and "guess" base flow}
-
-\small
-
-%\begin{lstlisting}
-%bf=SF_Init('Mesh_Cylinder.edp', [-40 80 40]);
-%\end{lstlisting}
-
-\keys{bf=SF\_Init('Mesh\_Cylinder.edp', [-40 80 40]);}
-
-\ssp
-
-What the \keys{SF\_Init} driver does :
-
-\begin{itemize}[<+->]
-\item Runs the relevant FreeFem++ program \keys{Mesh\_Cylinder.edp}  with the corresponding parameters (here size of the domain),
-
-{\scriptsize This program generates the following output files : \keys{mesh.msh} (mesh data), \keys{mesh.ff2m} (mesh information), \keys{SF\_Init.ff2m} (auxiliary information), \keys{BaseFlow\_init.txt} and \keys{BaseFlow\_init.ff2} ("guess" base flow).}
-
-\item Reads all the output files,
-
-\item Returns a matlab "structure" object containing all the data needed for post-processing and subsequent usage.
-
-\end{itemize}
-
-\end{frame}
-
-%\subsection{Step 0 : computation of a base flow}
-
-\begin{frame}{Computation of a Base flow : principle}
-
-We look for a steady base-flow $({\bf u}_b;p_b)$ satisfying the steady Navier-Stokes equations, i.e. 
-$NS ({\bf u}_b,p_b) = 0$.
-
-Suppose that we have a 'guess' for the base flow $[{\bf u}_b^g,p_b^g]$  which almost satisfies the equations.  We look for a better approximation under the form
-\be{Newton1}
-[{\bf u}_b,p_b]  = [{\bf u}_b^g,p_b^g] + [\delta {\bf u}_b, \delta p_b] = 0.
-\ee
-
-Injecting into the Navier-Stokes equation lead to $$
-NS ({\bf u}_b^g,p_b^g) + NSL_{{\bf u}_b^g}(\delta {\bf u}_b,\delta p_b)$$
-
-Where $NSL$ is the linearised Navier-Stokes operator. 
-%defined by its action on a flow field $({\bf u} ; p)$ as follows
-
-=>  matricial problem with the form $A \cdot \delta X = Y$. The procedure of Newton iteration is to solve iteratively this set of equations up to convergence.
-
-\end{frame}
-
-\begin{frame}{Computation of a Base flow : implementation}
-
-\small
-
-\keys{bf=SF\_BaseFlow(bf,'Re',10);}
-
-%\begin{lstlisting}
-%baseflow=SF_BaseFlow(baseflow,'Re',10);
-%\end{lstlisting}
-
-\ssp
-
-What the \keys{SF\_Init} driver does :
-
-\begin{itemize}[<+->]
-\item Copies the previous base flow  into file \keys{BaseFlow\_guess.txt} which will be read by Freefem++,
-
-\item Runs the relevant FreeFem++ solver (here \keys{Newton\_2D.edp})  with the corresponding parameters (here the value of $Re$),
-
-%{\scriptsize This program generates the following output files : \keys{mesh.msh} (mesh data), \keys{mesh.ff2m} (mesh information), \keys{SF\_Init.ff2m} (auxiliary information), \keys{BaseFlow\_init.txt} and \keys{BaseFlow\_init.ff2} ("guess" base flow).}
-
-\item Reads all the generated output files (here \keys{BaseFlow.ff2m}),
-
-\item Returns a matlab "structure" object containing all the data needed for post-processing and subsequent usage.
-
-\end{itemize}
-
-\end{frame}
-
-\begin{frame}{Mesh adaptation}
-
-\end{frame}
-
-%\subsection{Eigenvalue computation : principle}
-
-\begin{frame}{Linear stability}
-
-\be{startmodepropre}
-{\bf u} = {\bf u}_b + \epsilon \hat{\bf u} e^{\lambda t} 
-\ee
-
-The eigenmodes is governed by the linear problem 
-$$\lambda \hat{{\bf u}} = NSL_{{\bf u}_b}( \hat{\bf u},\hat{p})$$,
-
-After discretization we end up with an eigenvalue problem with the matricial form
-\be{Eigen_matricial}
-\lambda B \hat{X} = A \hat{X}
-\ee
-
-\ssp
-Iterative method : single-mode shift-invert iteration
-$$
-X^{n} =  (A- \lambda_{shift} B)^{-1} B X^{n-1}
-$$
-
-Generalization : Arnoldi
-
-\end{frame}
-
-\begin{frame}{Eigenvalue computation : implementation}
-
-\small
-
-\keys{SF\_Stability(bf,’shift’,0.04+0.74i,’nev’,1,’ type ’ , ’D’ ) ;}
-
-%\begin{lstlisting}
-%baseflow=SF_BaseFlow(baseflow,'Re',10);
-%\end{lstlisting}
-
-\ssp
-
-What the \keys{SF\_Stability} driver does :
-
-\begin{itemize}[<+->]
-\item Copies the base flow into file \keys{BaseFlow.txt} which will be needed by Freefem++,
-
-\item Runs the FreeFem++ solver (here \keys{Stab\_2D.edp})  with the corresponding parameters (shift, number of eigenvalues, direct eigenmode),
-
-%{\scriptsize This program generates the following output files : \keys{mesh.msh} (mesh data), \keys{mesh.ff2m} (mesh information), \keys{SF\_Init.ff2m} (auxiliary information), \keys{BaseFlow\_init.txt} and \keys{BaseFlow\_init.ff2} ("guess" base flow).}
-
-\item Reads all the generated output files (here \keys{Eigenmode.ff2m}),
-
-\item Does a number of post-processing (sort the eigenvalues, update the "shift" in continuation mode...)
-
-\item Returns a matlab "structure" object containing all the data needed for post-processing and subsequent usage.
-
-\end{itemize}
-
-\end{frame}
-
-\subsection{List of test-cases currently available}
-
-\begin{frame}{StabFem : list of test-cases currently available (or under development...)}
-
-\scriptsize
-
-\begin{itemize}
-\item CYLINDER  		\qquad -> 2D incompressible, objet fixe
-
-\item CYLINDER\_VIV \qquad 	-> 2D incompressible, objet mobile
-
-(Stage Diogo Ferrera-Sabino)
-
-\item IMPACTINGJET  		\qquad -> 2D incompressible, 3D stability.
-
-(with David LoJacono)
-
-\item CYLINDER\_Compressible  \qquad -> 2D compressible
-
-(Javier Serra, Vincenzo Citro...)
-
-\item BIRDCALL \qquad -> 2D-axisymmetric, incompressible or "augmented incompressible"
-
-(with R. Longobardi, V. Citro....)
-
-\item POROUS\_DISK \qquad -> 2D-axisymmetric, with porous object
-
-(stage Adrien Rouvière)
-
-\item LiquidBridges -> 2D axi, with deformable free surface
-
-(stage Nabil Achour)
-
-\item ROTATING\_POLYGONS
-
-(with Jérôme Mougel...)
-\item ....
-
-\end{itemize}
-
-=> Illustration dans le cas CYLINDER
-
-\end{frame}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{frame}{Whistling jets : axisymmetric flow through a two-hole configuration}
-(with Raffaele Longobari, Vincenzo Citro \& others...)
-
-\includegraphics[width=.9\linewidth]{FIGURES/WhistlinJetMode.png}
-\end{frame}
-
-\begin{frame}{2D around a spring-mounted cylinder...}
-(with Diogo Ferreira Sabino \& Olivier Marquet)
-\end{frame}
-
-\begin{frame}{2D flow around a compressible cylinder...}
-(in fast progress with Javier Sierra...)
-\end{frame}
-
-\begin{frame}{Flow around (and through) a porous (\& rotating) disk...}
-(with Adrien Rouvière \& D. Lo Jacono)
-
-\includegraphics[width=.6\linewidth]{FIGURES/Ux_Re200_Da1e-2.png}
-
-\end{frame}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{frame}{Liquid bridges...}
+\chapter{Capillary oscillations of a liquid bridge}
 
 \begin{description}
-%\item{Directory in the StabFem project :}  \texttt{LiquidBridges}
-%\item{Main contributors :} D. Fabre.
+\item{Directory in the StabFem project :}  \texttt{LiquidBridges}
+\item{Main contributors :} D. Fabre.
 \item{Reference :} Chireux et al., Phys. Fluids, 2015.
@@
 \begin{figure}
-\includegraphics[width=.5\linewidth]{../LiquidBridges/FIGURES/Bridges_NV_Eigenmodes_phi_cyl_L3_5.png}
+\includegraphics[width=.8\linewidth]{../../CASES_STABLE/LiquidBridges/FIGURES/Bridges_NV_Eigenmodes_phi_cyl_L3_5.png}
 \caption{Oscillation modes of a liquid bridge of aspect ratio $L/R=4$ and reduced volume $V^ =$...}
@@
 \begin{figure}
-\includegraphics[width=.45\linewidth]{../LiquidBridges/FIGURES/Bridges_NV_coal_omega.png}
-\includegraphics[width=.45\linewidth]{../LiquidBridges/FIGURES/Bridges_NV_coal_omega.png}
+\includegraphics[width=.45\linewidth]{../../CASES_STABLE/LiquidBridges/FIGURES/Bridges_NV_coal_omega.png}
+\includegraphics[width=.45\linewidth]{../../CASES_STABLE/LiquidBridges/FIGURES/Bridges_NV_coal_omega.png}
 \caption{Oscillation frequencies of a liquid bridge resulting from the coalescence of two spherical droplets
@@
 \end{figure}
-
-\end{frame}
-
-\begin{frame}{rotating polygons...}
-
-\begin{description}
-%\item{Directory in the StabFem project :}  \texttt{ROTATINGPOLYGONS}
-%\item{Main contributors :} J. Mougel, D. Fabre
-\item{Reference :} Mougel et al., JFM 2018 
-\end{description}
-
-\begin{figure}
-\includegraphics[width=.8\linewidth]{../ROTATING_POLYGONS/FIGURES/POLYGONS_modes.png}
-\caption{Oscillation modes of a potential vortex for  $a=H/R=0.3$ and $m=3$ (figure 5, 6 of Mougel et al.).}
-\label{Bridges_NV_Eigenmodes_phi_cyl_L3_5}
-\end{figure}
-
-\begin{figure}
-\includegraphics[width=.45\linewidth]{../ROTATING_POLYGONS/FIGURES/POLYGONS_omega.png}
-\includegraphics[width=.45\linewidth]{../ROTATING_POLYGONS/FIGURES/POLYGONS_sigma.png}
-\caption{Oscillation frequencies and amplification rates for f a potential vortex for $m=3$ (figure 4 of Mougel et al.).}
-\label{Bridges_NV_Eigenmodes_phi_cyl_L3_5}
-\end{figure}
-
-\end{frame}
-
-\begin{frame}{Sessile drops...}
-
-With Nabil Achour  ( \& Paul Bonnefis)
-
-\includegraphics[width=.9\linewidth]{FIGURES/SessileDrops_Eigenmodes.png}     % SessileDrops__Eigenmodes_eta.png
-
-- Linear oscillations modes ("pined" or "fixed angle" conditions)
-
-Next steps : investigate contact-line dynamics with WNL methods (cf. Viola, Brun \& Gallaire, 2018)
-
-\end{frame}
-
-%%%%%%%%%%%%%%% PART 3 : NONLINEAR APPROACHES %%%%%%%%%%%%%%%%%%%
-
-\section{Nonlinear global stability approaches : status and future}
-
-%\section{Nonlinear global approaches to hydrodynamic instabilities}
-
-\begin{frame}{Nonlinear global stability approaches : review}
-\small
-
-The linear stability approach approach is the right tool to predict instability threshold ($Re_c$) and the shedding frequency at threshold ($St_c = \omega_c/2\pi$).
-
-\ssp
- But for $Re>Re_c$ it badly predicts the frequency of the limit cycle.
-
-$$
-\includegraphics[width=8cm]{Barkley_figure.png}
-$$
-
- \ssp It has been remarked that stability analysis of the {\em mean flow} obtained by time-averaging the limit cycle gives better predictions (Barkley, Leontini,...).
-
-\ssp
-
-  => Objective of nonlinear stability approaches : provide rational approach to describe the nonlinear oscillation cycle,
-  and provide amplitude equations to describe the transients.
-
-  %Give a rigorous ground to study the stability of {\em mean flow}.
-
-\end{frame}
-\subsection{Weakly nonlinear approach}
-
-\begin{frame}{Weakly nonlinear approach {\small (Sipp \& Lebedev, 2007)}}
-
-\footnotesize
-
-Starting point : weakly non-linear expansion, with multiple scale method.
-
-$$
-\epsilon = \frac{1}{Re_c} - \frac{1}{Re} ; \quad \tau = \epsilon^2 t
-$$
-
-\begin{eqnarray}
-{\bf u} &=& {\bf u}_{bc} + \epsilon \left[ A_{wnl} (\tau) \hat{\bf u} e^{i \omega_c t} + c.c. \right] \label{WNL1}\\
-&+& \epsilon^2 \left[ {\bf u}_\epsilon + |A_{wnl}|^2  {\bf u}_{2,0} + \left(  A_{wnl}^2 {\bf u}_{2,2} e^{2 i \omega_c t} + c.c. \right) \right] + {\cal O}( \epsilon ^3)
-\nonumber
-\end{eqnarray}
-
-Resolution at order 2 :
-%Substituting the expansion \ref{WNL2} into the Navier-Stokes equations \ref{NSprimitive} and grouping terms multiplied by the same power of $\epsilon$, a hierarchy of equations is obtained.
-The order $\epsilon^0$ gives directly the base flow at $Re_c$.
-The order $\epsilon^1$
-%corresponds to the linear neutral eigenmode as computed in the first part of this article.
-%The order $\epsilon^2$ contains three terms respectively computed as the solutions of the following linear problems:
-\begin{eqnarray}
- {\cal LNS}_{{\bf u}_{bc}} ({\bf u}_\epsilon) - 2 \nabla \cdot {\mathsf D}({\bf u}_{bc}) &=&0,
-\label{eq:LL1} \\
-{\cal LNS}_{{\bf u}_{bc}} ({\bf u}_{2,0}) &=& {\cal C}(\hat{\bf u},\overline{\hat{\bf u}}), \label{eq:LL2} \\
-{\cal LNS}_{{\bf u}_{bc}} ({\bf u}_{2,2}) - 2 i \omega_c {\bf u}_{2,2}  &=& \frac{1}{2} {\cal C}(\hat{\bf u},\hat{\bf u}). \label{eq:LL3}
- \end{eqnarray}
-
-Compatibility conditions at order 3 :
-\be{WNL3_2}
-\frac{\partial A_{wnl}}{\partial \tau} = \Lambda A_{wnl} - (\nu_0+\nu_2)  |A_{wnl}|^2 A_{wnl},
-\ee
-%where coefficients $\Lambda$, $\nu_0$ and $\nu_2$ are given by
-\begin{eqnarray}
-\Lambda &=& -\frac{ \left< {\hat{\bf u}}^\dag, 
-\left( {\cal C}({\bf u}_\epsilon, \hat{\bf u}) + 2 \nabla \cdot  {\mathsf D}( \hat{\bf u}) \right) \right>}
-{  \left<  \hat{\bf u}^\dag,\hat{\bf u} \right> },\label{LAMBDA}\\
-\nu_0 &=& \frac{ \left< {\hat{\bf u}}^\dag,  {\cal C}({\bf u}_{20}, \hat{\bf u} ) \right>}
-{  \left<  \hat{\bf u}^\dag,\hat{\bf u} \right> },\label{NU0}\quad
-\nu_2 = \frac{ \left< {\hat{\bf u}}^\dag,  {\cal C}({\bf u}_{22}, \overline{\hat{\bf u}})  \right>}
-{  \left<  \hat{\bf u}^\dag,\hat{\bf u} \right> }.,\label{NU2}
- \end{eqnarray}
-
-%Method : weakly nonlinear expansion
-
-%Order 0 : base-flow
-
-%Order 1 : eigenmode at marginal conditions
-
-%Order 2 : nonresonant linear problems -> direct resolution
-
-%Order 3 : resonant problems : compatibility conditions (Fredholm alternative)
-
-%Resolution thanks to adjoint methods
-
-%=> Amplitude equation
-
-\end{frame}
-
-\subsection{Self-consistent approach}
-
-\begin{frame}{Self-Consistent approach {\small (Mantic-Lugo, Arratia \& Gallaire, 2014)}}
-
-\small
-Starting point : Pseudo-eigenmode decomposition
-
-\be{SC}
-{\bf u } = {\bf u }_m + A_{sc} \left[ \tilde{{\bf u }}_1 e^{\sigma_{sc} t + i \omega_{sc} t} +   \overline{\tilde{\bf u }_1} e^{\sigma_{sc} t  -i \omega_{sc} t} \right],
-\quad
-\left( |\tilde{{\bf u }}_1|| = 1/\sqrt{2}\right)
-\ee
-
-%where ${\bf u }_m$ is the {\em mean flow} as previously defined,  $\tilde{{\bf u }}_1$ is a pseudo-eigenvector which is normalized by the condition  $||\tilde{{\bf u }}_1|| = 1/\sqrt{2}$, $\overline{\tilde{{\bf u }}_1}$ is its complex conjugate,
-where $A_{sc}$ is an amplitude parameter, %directly related to the energy of the oscillating flow, 
-and $\lambda_{sc} = \sigma_{sc} + i \omega_{sc}$ is a pseudo-eigenvalue which depends upon the parameter $A_{sc}$.
-
-\pause
-=> SC-model equations
-
-\begin{subequations}\label{sc12}
-\begin{eqnarray}
-{\cal NS}(  {\bf u }_m ) - A_{sc}^2 {\cal C}( \tilde{{\bf u }}_1, \overline{\tilde{\bf u }_1}) = 0, 
-\label{sis1}
-\\
-(\sigma_{sc} + i \omega_{sc}) \tilde{{\bf u }}_1 =  {\cal LNS}_{{\bf u }_m}(\tilde{{\bf u }}_1 ).
-\label{sis2}
-\end{eqnarray}
-\end{subequations}
-
-\pause
-
-=> Amplitude equation :
-$$
-\frac{\partial A_{sc}}{\partial t} = \sigma_{sc} (A_{sc}) A_{sc}
-$$
-
-\pause
-
-%$\sigma(A_E
-
-Resolution method of {\small (Mantic-Lugo 2014)}: double iterative loop
-
-- Inner loop :
-
-$\quad$ Fix $A_{sc}$, iteratively solve (eigenvalue problem + calculation of mean flow) up to convergence for $(\sigma_{sc} + i \omega_{sc})$ as function of $A_{sc}$.
-
-- Outer loop :
-
-$\quad$ iterate over $A_{sc}$ to reach  $\sigma_{sc} = 0$
-
-\end{frame}
-
-\begin{frame}{Self-Consistent approach : a direct resolution method}
-
-\small
-
-Let's forget about transients, and look directly for a description of the saturated cycle:
-%We thus start with a truncated Fourier decomposition of the limit cycle under the form:
-
-\be{HB}
-{\bf u } = {\bf u }_m + {\bf u }_{1,c} \cos( \omega t ) +   {\bf u }_{1,s} \sin( \omega t ),
-\ee
-where ${\bf u }_{1,c}$ and ${\bf u }_{1,s}$ are two {\em real} fields %describing the nonlinear perturbation at two instants separated by a quarter-period of oscillation,
-
-and $\omega$ is the (real) oscillation frequency of the limit cycle.
-%The connection with the definition of Manti\v{c}-Lugo is as follows :
-%\be{HBtoSC}
-%\left( {\bf u }_{1,c} - i {\bf u }_{1,s} \right) = 2 A_{sc} \tilde{{\bf u }}_1.
-%\ee
-
-\ssp
-
-=> Equations :
-%Injecting this ansartz into the Navier-Stokes equations and taking the mean value and the first Fourier component leads to the following coupled equations:
-\begin{subequations}\label{eq_principal}
-\begin{eqnarray}
-{\cal NS}(  {\bf u }_m ) = \frac{{\cal C}( {\bf u }_{1,c}, {\bf u }_{1,c}) +{\cal C}( {\bf u }_{1,s}, {\bf u }_{1,s})}{4}, 
-\label{HBEq0}
-\\
- \omega {\bf u }_{1,s} =  {\cal LNS}_{{\bf u }_m}(  {\bf u }_{1,c} ),
-\label{HBEq1}
-\\
- -\omega {\bf u }_{1,c} =  {\cal LNS}_{{\bf u }_m}(  {\bf u }_{1,s} ).
-\label{HBEq1b}
-\end{eqnarray}
-\end{subequations}
-
-We need an extra scalar equation to fix the phase of the cycle, e.g:
-
-\begin{equation}
-\Im \{F_y({\bf u}_1) \} =0.
-\label{HBphase}
-\end{equation}
-
-=> Direct resolution with Newton method !
-\ssp
-
-Remarks :
-
-- We need a good guess : use the WNL to produce it !
-
-- Computation can be optimized using preconditioning (Ask Olivier...)
-
-\end{frame}
-
-\subsection{Harmonic-balance approach}
-
-\begin{frame}{Harmonic-Balance}
-
-\small
-
-%The Navier-stokes equations can be posed as
-
-%\begin{eqnarray}
-%\partial_t {\bf u} = {\cal NS} ({\bf u},p)
-%\equiv - {\bf u} \cdot \nabla {\bf u} - \nabla p + \frac{2}{Re}  \nabla \cdot {\mathsf{D}}({\bf u}), \label{NSprimitive}  \\
-%\nabla \cdot {\bf u} = 0. \label{eq:DIV}
-%\end{eqnarray}
-
-We start with the following expansion:
-\begin{equation}
-{\bf u } = {\bf u }_m + {\bf u }_{1,c} \cos( \omega t ) +   {\bf u }_{1,s} \sin( \omega t ) +{\bf u }_{2,c} \cos(2 \omega t ) +   {\bf u }_{2,s} \sin(2 \omega t ),
-\end{equation}
-
-arriving to a system of equations:
-\begin{subequations}\label{eq_principal}
-\begin{eqnarray}
-{\cal NS}(  {\bf u }_m) = \frac{{\cal C}( {\bf u }_{1,c}, {\bf u }_{1,c}) +{\cal C}( {\bf u }_{1,s}, {\bf u }_{1,s})+{\cal C}( {\bf u }_{2,c}, {\bf u }_{2,c})+{\cal C}( {\bf u }_{2,s}, {\bf u }_{2,s})}{4},
-\label{HBEq0}
-\\
- \omega {\bf u }_{1,s} =  {\cal L}_{{\bf u }_m}(  {\bf u }_{1,c} )-\frac{1}{2}\Big(
- {\cal C}( {\bf u }_{1,c}, {\bf u }_{2,c})+{\cal C}( {\bf u }_{1,s}, {\bf u }_{2,s})
- \Big),
-\label{HBEq1}
-\\
- -\omega {\bf u }_{1,c} =  {\cal L}_{{\bf u }_m}(  {\bf u }_{1,s} )-\frac{1}{2}\Big(
- {\cal C}( {\bf u }_{1,c}, {\bf u }_{2,s})-{\cal C}( {\bf u }_{1,s}, {\bf u }_{2,c})
- \Big),
-\label{HBEq1b}
-\\
- 2 \omega {\bf u }_{2,s} =  {\cal L}_{{\bf u }_m}(  {\bf u }_{2,c} )-\frac{1}{4}\Big(
- {\cal C}( {\bf u }_{1,c}, {\bf u }_{1,c})-{\cal C}( {\bf u }_{1,s}, {\bf u }_{1,s})
- \Big),
-\label{HBEq2}
-\\
- -2\omega {\bf u }_{2,s} =  {\cal L}_{{\bf u }_m}(  {\bf u }_{2,s} )-\frac{1}{2}
- {\cal C}( {\bf u }_{1,s}, {\bf u }_{1,c}),
-\label{HBEq2b}
-\end{eqnarray}
-\end{subequations}
-%where ${\cal C}( {\bf U} , {\bf u}) = \left( {\bf U} \cdot \nabla \right) {\bf u} + \left( {\bf u} \cdot \nabla \right)  {\bf U}$.
-
-%To allow resolution we thus need an extra equation to fix this phase, e.g:
-\begin{equation}
-\Im \{F_y({\bf u}_1) \} =0.
-\label{HBphase}
-\end{equation}
-
-=> Direct Newton resolution again
-\end{frame}
-
-\begin{frame}{Harmonic-Balance : results for the cylinder ! }
-
-%\begin{figure}
-\begin{center}
-\includegraphics[width=.32 \linewidth]{../CYLINDER/FIGURES/Cylinder_Strouhal_Re_HB2.png}
-\includegraphics[width=.32 \linewidth]{../CYLINDER/FIGURES/Cylinder_Energy_Re_HB2.png}
-\includegraphics[width=.32 \linewidth]{../CYLINDER/FIGURES/Cylinder_Lx_Re_HB2.png}
-\end{center}
-\begin{center}
-\includegraphics[width=.32\linewidth]{../CYLINDER/FIGURES/Cylinder_Fx_Re_HB2.png}
-\includegraphics[width=.32 \linewidth]{../CYLINDER/FIGURES/Cylinder_Fy_Re_HB2.png}
-\end{center}
-%\caption{Comparison between the weakly nonlinear results (WNL) the harmonic balance data (HB), and baseflow/linear results : Strouhal number $(a)$, Mean drag $(b)$, amplitude of oscillating lift $(c)$, Energy-amplitude of the nonlinear perturbation $(d)$ and recirculation lenght of mean/base flows ($e)$.
-%c_x should be consistent with the drag definition given at beginning
-%}
-%\label{fig:HB_SC_DATA_COMP}
-%\end{figure}
-
-\end{frame}
-
-%
-%\subsection{Adjoint problem} 
-%
-%\begin{frame}{Adjoint problem}
-%
-%\small
-%
-%Define a scalar product :
-%$$
-%\left< \phi_1, \phi_2 \right> = \int_\Omega \overline{\phi_1} \cdot \phi_2   \mbox{ d} \Omega
-%$$
-%
-%
-%We can first define the {\em adjoint linearised Navier-Stokes operator} $NSL^\dag$ defined by the property:
-%\bes{NSLAdj}
-%\forall ( {\bf u}, p ; {\bf v}, q), & \left< NSL^\dag_{\bf U}( {\bf v},q) ,{\bf u}\right> + \left< \nabla \cdot {\bf v},p\right>  \\
-%=& \left< {\bf v}, NSL_{\bf U} ({\bf u},p)\right> + \left< q, \nabla \cdot {\bf u}\right>.
-%\ees
-%We can then define the adjoint eigenmodes as the solutions to the eigenvalue problem 
-%\be{EigenAdj} 
-%\forall ( {\bf u}, p), \quad  \lambda^\dag \left< \hat{\bf v}, {\bf u}\right> =
-% \left< NSL^\dag_{\bf U}( \hat{\bf v},\hat{q}) ,{\bf u}\right> + \left< \nabla \cdot \hat{\bf v},p\right>  
-%\ee
-%
-%Matricial form :
-%
-%\be{Eigen_Adj_matricial}
-%\overline{\lambda}^\dag B \hat{X}\dag = A^T \hat{X}\dag.
-%\ee
-%
-%
-%\end{frame}
-%
-%\begin{frame}{Adjoint mode and structural sensitivity}
-%
-%
-%Significance of the adjoint mode : 
-%
-%(optimal perturbation)
-%
-%
-%\end{frame}
-
-%\section{Nonlinear global approaches to hydrodynamic instabilities}
-%
-%\begin{frame}{Nonlinear global stability approaches : review}
-%
-%%The linear stability approach approach is the right tool to predict instability threshold ($Re_c$) and the %shedding frequency at threshold ($St_c = \omega_c/2\pi$).
-%
-%%\ssp
-%% But for $Re>Re_c$ it badly predicts the frequency of the limit cycle. 
-% 
-%%$$
-%%\includegraphics[width=8cm]{FIGURES/Barkley_figure.png}
-%%$$
-%
-% 
-% 
-%% \ssp It has been remarked that stability analysis of the {\em mean flow} obtained by time-averaging the limit cycle gives better predictions (Barkley, Leontini,...).
-%  
-%  
-%%\ssp 
-%  
-% % => Objective of nonlinear stability approaches : Give a rigourous ground to study the stability of mean flow.
-%  
-%  
-%
-%\end{frame}
-%
-%\begin{frame}{Weakly nonlinear approach {\small (Sipp \& Lebedev, 2007)}}
-%
-%Starting point : weakly non-linear expansion, with multiple scale method.
-%
-%$$
-%\epsilon : \frac{1}{Re_c} - \frac{1}{Re} ; \quad \tau = \epsilon^2 t
-%$$
-%
-%\begin{eqnarray}
-%{\bf u} &=& {\bf u}_{bc} + \epsilon \left[ A_{wnl} (\tau) \hat{\bf u} e^{i \omega_c t} + c.c. \right] \label{WNL1}\\
-%&+& \epsilon^2 \left[ {\bf u}_\epsilon + |A_{wnl}|^2  {\bf u}_{2,0} + \left(  A_{wnl}^2 {\bf u}_{2,2} e^{2 i \omega_c t} + c.c. \right) \right] + {\cal O}( \epsilon ^3)
-%\nonumber
-%\end{eqnarray}
-%
-%
-%\end{frame}
-%
-%
-%
-%\begin{frame}{Self-Consistent approach {\small (Mantic-Lugo, Arratia \& Gallaire, 2014)}}
-%
-%Starting point : Pseudo-eigenmode decomposition
-%
-%
-%
-%\end{frame}
-
-\begin{frame}{Conclusions}
-\end{frame}
-
-\appendix{The future of StabFem }
-
-\begin{frame}{Recent progress}
-
-\begin{itemize}
-
-\item Multi-platform objective : 
-MacOs OK ; Unix OK ; Windows 10 currently 50 \% compatible.
-
-{\small main issues with windows : cp = copy,...}%  \verb|\| instead of \verb|/|,...}
-
-\item Plotting options : recent intergration of "pdeplot2dff" from Markus "chloros" in place of pdeplot/pdetools .
-
-{\small other solutions for plotting : tecplot converter, vtk converter, ...}
-
-\item Compatibility with Octave : currently 50 \% compatible.
-
-{\small Main issues with octave : importdata, plotting (now solved), inputParser (now solved)}.
-
-\item Translation in Python  ??
-
-\end{itemize}
-
-\end{frame}
-
-%%%%%%%%%%%%
-\begin{frame}{Besoins}
-
-\begin{itemize}
-
-\item Maintaining a fully opensource  (Matlab-Octave or Python ?) and fully multiplatform version (windows).
-
-\item Managing a list of test cases (non-regression tests, etc...)
-
-\item Help simplifying/rationalizing the programation style.
-
-\item Gestion of errors / debugging / "verbosity" ...
-
-\item Upgrading to 3D / parallel computation ? (currently not priority)
-
-\item Support with github  (/ gitlab ?)
-
-\item Documentation
-
-Automatic generation from comments in programs ?  Doxygen ??
-
-\end{itemize}
-
-\end{frame}
-
-\end{document}

### 2018-07-17 99_Documentation/MANUAL/301_Mutual_Files_Matlab.tex
Reorganization of the arborescence (redone with « git mv » to keep tracking)

% !TEX root = main.tex
\chapter{Mutual Matlab Files}

In this section we give the documentation of the Matlab drivers of the project.

We have to find a way to generate automatically this documentation by extracting the documentation directly from the programs
(Doxygen ?)

\section{General drivers and FF/Matlab interface tools}

\subsection{\texttt{SF\_Mesh.m}}

\subsection{\texttt{SF\_Launch.m}}

\subsection{\texttt{importFFMesh.m}}

\subsection{\texttt{importFFData.m}}

\section{Stability-oriented drivers}

\subsection{\texttt{SF\_Init.m}}

\subsection{\texttt{SF\_BaseFlow.m}}

\subsection{\texttt{SF\_Stability.m}}

\subsection{\texttt{SF\_Adapt.m}}

\section{Plotting programs}

\section{Auxiliary programs}

\subsection{\texttt{mysystem.m}}

\subsection{\texttt{mycp.m}}

### 2018-07-17 99_Documentation/MANUAL/teste.tex
Reorganization of the arborescence (redone with « git mv » to keep tracking)

\documentclass[11pt,a4paper]{book}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{textcomp}
\usepackage{pslatex}
\usepackage{hyperref}

\input{../common/version.tex}
\input{../common/macros.tex}
\input{../common/title.tex}

%\makeindex

\begin{document}
\coverpage{A Tutorial}{Gérard Huet, Gilles Kahn and Christine Paulin-Mohring}{}

%\tableofcontents

\chapter*{Getting started}

\Coq{} is a Proof Assistant for a Logical Framework known as the Calculus
of Inductive Constructions. It allows the interactive construction of
formal proofs, and also the manipulation of functional programs 
consistently with their specifications. It runs as a computer program
on many architectures.

It is available with a variety of user interfaces. The present
document does not attempt to present a comprehensive view of all the
possibilities of \Coq, but rather to present in the most elementary
manner a tutorial on the basic specification language, called Gallina,
in which formal axiomatisations may be developed, and on the main
proof tools.  For more advanced information, the reader could refer to
the \Coq{} Reference Manual or the \textit{Coq'Art}, a book by Y.
Bertot and P. Castéran on practical uses of the \Coq{} system.

Instructions on installation procedures, as well as more comprehensive
documentation, may be found in the standard distribution of \Coq,
which may be obtained from \Coq{} web site
\url{https://coq.inria.fr/}\footnote{You can report any bug you find
while using \Coq{} at \url{https://coq.inria.fr/bugs}. Make sure to
always provide a way to reproduce it and to specify the exact version
you used. You can get this information by running \texttt{coqc -v}}.
\Coq{} is distributed together with a graphical user interface called
CoqIDE. Alternative interfaces exist such as
Proof General\footnote{See \url{https://proofgeneral.github.io/}.}.

In the following examples, lines preceded by the prompt \verb:Coq < :
represent user input, terminated by a period.
The following lines usually show \Coq's answer.
When used from a graphical user interface such as
CoqIDE, the prompt is not displayed: user input is given in one window
and \Coq's answers are displayed in a different window.

\chapter{Basic Predicate Calculus}

\section{An overview of the specification language Gallina}

A formal development in Gallina consists in a sequence of {\sl declarations}
and {\sl definitions}.

\subsection{Declarations}

A declaration associates a {\sl name} with a {\sl specification}.
A name corresponds roughly to an identifier in a programming
language, i.e. to a string of letters, digits, and a few ASCII symbols like
underscore (\verb"_") and prime (\verb"'"), starting with a letter. 
We use case distinction, so that the names \verb"A" and \verb"a" are distinct.
Certain strings are reserved as key-words of \Coq, and thus are forbidden 
as user identifiers.

A specification is a formal expression which classifies the notion which is
being declared. There are basically three kinds of specifications: 
{\sl logical propositions}, {\sl mathematical collections}, and
{\sl abstract types}. They are classified by the three basic sorts
of the system, called respectively \verb:Prop:, \verb:Set:, and
\verb:Type:, which are themselves atomic abstract types.

Every valid expression $e$ in Gallina is associated with a specification,
itself a valid expression, called its {\sl type} $\tau(E)$. We write
$e:\tau(E)$ for the judgment that $e$ is of type $E$. 
You may request \Coq{} to return to you the type of a valid expression by using
the command \verb:Check::

\begin{coq_eval}
Set Printing Width 60.
\end{coq_eval}

\begin{coq_example}
Check O.
\end{coq_example}

Thus we know that the identifier \verb:O: (the name `O', not to be
confused with the numeral `0' which is not a proper identifier!) is
known in the current context, and that its type is the specification 
\verb:nat:. This specification is itself classified as a mathematical
collection, as we may readily check:

\begin{coq_example}
Check nat.
\end{coq_example}

The specification \verb:Set: is an abstract type, one of the basic
sorts of the Gallina language, whereas the notions $nat$ and $O$ are
notions which are defined in the arithmetic prelude,
automatically loaded when running the \Coq{} system.

We start by introducing a so-called section name. The role of sections
is to structure the modelisation by limiting the scope of parameters,
hypotheses and definitions. It will also give a convenient way to
reset part of the development.

\begin{coq_example}
Section Declaration.
\end{coq_example}
With what we already know, we may now enter in the system a declaration,
corresponding to the informal mathematics {\sl let n be a natural
  number}.

\begin{coq_example}
Variable n : nat.
\end{coq_example}

If we want to translate a more precise statement, such as
{\sl let n be a positive natural number},
we have to add another declaration, which will declare explicitly the
hypothesis \verb:Pos_n:, with specification the proper logical
proposition:
\begin{coq_example}
Hypothesis Pos_n : (gt n 0).
\end{coq_example}

Indeed we may check that the relation \verb:gt: is known with the right type
in the current context:

\begin{coq_example}
Check gt.
\end{coq_example}

which tells us that \texttt{gt} is a function expecting two arguments of
type \texttt{nat} in order to build a logical proposition.
What happens here is similar to what we are used to in a functional
programming language: we may compose the (specification) type \texttt{nat}
with the (abstract) type \texttt{Prop} of logical propositions through the
arrow function constructor, in order to get a functional type
\texttt{nat -> Prop}:
\begin{coq_example}
Check (nat -> Prop).
\end{coq_example}
which may be composed once more with \verb:nat: in order to obtain the
type \texttt{nat -> nat -> Prop} of binary relations over natural numbers.
Actually the type \texttt{nat -> nat -> Prop} is an abbreviation for 
\texttt{nat -> (nat -> Prop)}.

Functional notions may be composed in the usual way. An expression $f$
of type $A\ra B$ may be applied to an expression $e$ of type $A$ in order
to form the expression $(f~e)$ of type $B$. Here we get that
the expression \verb:(gt n): is well-formed of type \texttt{nat -> Prop},
and thus that the expression \verb:(gt n O):, which abbreviates
\verb:((gt n) O):, is a well-formed proposition.
\begin{coq_example}
Check gt n O.
\end{coq_example}

\subsection{Definitions}

The initial prelude contains a few arithmetic definitions:
\texttt{nat} is defined as a mathematical collection (type \texttt{Set}),
constants \texttt{O}, \texttt{S}, \texttt{plus}, are defined as objects of
types respectively \texttt{nat}, \texttt{nat -> nat}, and \texttt{nat ->
nat -> nat}.
You may introduce new definitions, which link a name to a well-typed value.
For instance, we may introduce the constant \texttt{one} as being defined
to be equal to the successor of zero:
\begin{coq_example}
Definition one := (S O).
\end{coq_example}
We may optionally indicate the required type:
\begin{coq_example}
Definition two : nat := S one.
\end{coq_example}

Actually \Coq{} allows several possible syntaxes:
\begin{coq_example}
Definition three := S two : nat.
\end{coq_example}

Here is a way to define the doubling function, which expects an
argument \verb:m: of type \verb:nat: in order to build its result as
\verb:(plus m m)::

\begin{coq_example}
Definition double (m : nat) := plus m m.
\end{coq_example}
This introduces the constant \texttt{double} defined as the
expression \texttt{fun m : nat => plus m m}.
The abstraction introduced by \texttt{fun} is explained as follows.
The expression \texttt{fun x : A => e} is well formed of type
\texttt{A -> B} in a context whenever the expression \texttt{e} is
well-formed of type \texttt{B} in the given context to which we add the
declaration that \texttt{x} is of type \texttt{A}. Here \texttt{x} is a
bound, or dummy variable in the expression \texttt{fun x : A => e}.
For instance we could as well have defined \texttt{double} as
\texttt{fun n : nat => (plus n n)}.

Bound (local) variables and free (global) variables may be mixed.
For instance, we may define the function which adds the constant \verb:n:
to its argument as
\begin{coq_example}
Definition add_n (m:nat) := plus m n.
\end{coq_example}
However, note that here we may not rename the formal argument $m$ into $n$
without capturing the free occurrence of $n$, and thus changing the meaning
of the defined notion.

Binding operations are well known for instance in logic, where they
are called quantifiers.  Thus we may universally quantify a
proposition such as $m>0$ in order to get a universal proposition
$\forall m\cdot m>0$. Indeed this operator is available in \Coq, with
the following syntax: \texttt{forall m : nat, gt m O}. Similarly to the
case of the functional abstraction binding, we are obliged to declare
explicitly the type of the quantified variable. We check:
\begin{coq_example}
Check (forall m : nat, gt m 0).
\end{coq_example}

\begin{coq_eval}
Reset Initial.
Set Printing Width 60.
Set Printing Compact Contexts.
\end{coq_eval}

\section{Introduction to the proof engine: Minimal Logic}

In the following, we are going to consider various propositions, built
from atomic propositions $A, B, C$. This may be done easily, by
introducing these atoms as global variables declared of type \verb:Prop:.
It is easy to declare several names with the same specification:
\begin{coq_example}
Section Minimal_Logic.
Variables A B C : Prop.
\end{coq_example}

We shall consider simple implications, such as $A\ra B$, read as 
``$A$ implies $B$''. Note that we overload the arrow symbol, which
has been used above as the functionality type constructor, and which
may be used as well as propositional connective:
\begin{coq_example}
Check (A -> B).
\end{coq_example}

Let us now embark on a simple proof. We want to prove the easy tautology
$((A\ra (B\ra C))\ra (A\ra B)\ra (A\ra C)$. 
We enter the proof engine by the command
\verb:Goal:, followed by the conjecture we want to verify:
\begin{coq_example}
Goal (A -> B -> C) -> (A -> B) -> A -> C.
\end{coq_example}

The system displays the current goal below a double line, local hypotheses
(there are none initially) being displayed above the line. We call 
the combination of local hypotheses with a goal a {\sl judgment}.
We are now in an inner 
loop of the system, in proof mode. 
New commands are available in this
mode, such as {\sl tactics}, which are proof combining primitives.
A tactic operates on the current goal by attempting to construct a proof
of the corresponding judgment, possibly from proofs of some
hypothetical judgments, which are then added to the current
list of conjectured judgments.
For instance, the \verb:intro: tactic is applicable to any judgment
whose goal is an implication, by moving the proposition to the left
of the application to the list of local hypotheses:
\begin{coq_example}
intro H.
\end{coq_example}

Several introductions may be done in one step:
\begin{coq_example}
intros H' HA.
\end{coq_example}

We notice that $C$, the current goal, may be obtained from hypothesis
\verb:H:, provided the truth of $A$ and $B$ are established.
The tactic \verb:apply: implements this piece of reasoning:
\begin{coq_example}
apply H.
\end{coq_example}

We are now in the situation where we have two judgments as conjectures
that remain to be proved. Only the first is listed in full, for the
others the system displays only the corresponding subgoal, without its
local hypotheses list. Note that \verb:apply: has kept the local
hypotheses of its father judgment, which are still available for
the judgments it generated.

In order to solve the current goal, we just have to notice that it is
exactly available as hypothesis $HA$:
\begin{coq_example}
exact HA.
\end{coq_example}

Now $H'$ applies:
\begin{coq_example}
apply H'.
\end{coq_example}

And we may now conclude the proof as before, with \verb:exact HA.:
Actually, we may not bother with the name \verb:HA:, and just state that
the current goal is solvable from the current local assumptions:
\begin{coq_example}
assumption.
\end{coq_example}

The proof is now finished. We are now going to ask \Coq{}'s kernel
to check and save the proof.
\begin{coq_example}
Qed.
\end{coq_example}

Let us redo the same proof with a few variations. First of all we may name
the initial goal as a conjectured lemma:
\begin{coq_example}
Lemma distr_impl : (A -> B -> C) -> (A -> B) -> A -> C.
\end{coq_example}

Next, we may omit the names of local assumptions created by the introduction
tactics, they can be automatically created by the proof engine as new
non-clashing names.
\begin{coq_example}
intros.
\end{coq_example}

The \verb:intros: tactic, with no arguments, effects as many individual
applications of \verb:intro: as is legal.

Then, we may compose several tactics together in sequence, or in parallel,
through {\sl tacticals}, that is tactic combinators. The main constructions
are the following:
\begin{itemize}
\item $T_1 ; T_2$ (read $T_1$ then $T_2$) applies tactic $T_1$ to the current
goal, and then tactic $T_2$ to all the subgoals generated by $T_1$.
\item $T; [T_1 | T_2 | ... | T_n]$ applies tactic $T$ to the current
goal, and then tactic $T_1$ to the first newly generated subgoal, 
..., $T_n$ to the nth.
\end{itemize}

We may thus complete the proof of \verb:distr_impl: with one composite tactic:
\begin{coq_example}
apply H; [ assumption | apply H0; assumption ].
\end{coq_example}

You should be aware however that relying on automatically generated names is
not robust to slight updates to this proof script. Consequently, it is
discouraged in finished proof scripts. As for the composition of tactics with
\texttt{:} it may hinder the readability of the proof script and it is also
harder to see what's going on when replaying the proof because composed
tactics are evaluated in one go.

Actually, such an easy combination of tactics \verb:intro:, \verb:apply:
and \verb:assumption: may be found completely automatically by an automatic
tactic, called \verb:auto:, without user guidance:

\begin{coq_eval}
Abort.
\end{coq_eval}
\begin{coq_example}
Lemma distr_impl : (A -> B -> C) -> (A -> B) -> A -> C.
auto.
\end{coq_example}

Let us now save lemma \verb:distr_impl::
\begin{coq_example}
Qed.
\end{coq_example}

\section{Propositional Calculus}

\subsection{Conjunction}

We have seen how \verb:intro: and \verb:apply: tactics could be combined
in order to prove implicational statements. More generally, \Coq{} favors a style
of reasoning, called {\sl Natural Deduction}, which decomposes reasoning into 
so called {\sl introduction rules}, which tell how to prove a goal whose main 
operator is a given propositional connective, and {\sl elimination rules},
which tell how to use an hypothesis whose main operator is the propositional 
connective. Let us show how to use these ideas for the propositional connectives
\verb:/\: and \verb:\/:.

\begin{coq_example}
Lemma and_commutative : A /\ B -> B /\ A.
intro H.
\end{coq_example}

We make use of the conjunctive hypothesis \verb:H: with the \verb:elim: tactic,
which breaks it into its components:
\begin{coq_example}
elim H.
\end{coq_example}

We now use the conjunction introduction tactic \verb:split:, which splits the 
conjunctive goal into the two subgoals:
\begin{coq_example}
split.
\end{coq_example}
and the proof is now trivial. Indeed, the whole proof is obtainable as follows:
\begin{coq_eval}
Abort.
\end{coq_eval}
\begin{coq_example}
Lemma and_commutative : A /\ B -> B /\ A.
intro H; elim H; auto.
Qed.
\end{coq_example}

The tactic \verb:auto: succeeded here because it knows as a hint the 
conjunction introduction operator \verb+conj+
\begin{coq_example}
Check conj.
\end{coq_example}

Actually, the tactic \verb+split+ is just an abbreviation for \verb+apply conj.+

What we have just seen is that the \verb:auto: tactic is more powerful than
just a simple application of local hypotheses; it tries to apply as well 
lemmas which have been specified as hints. A 
\verb:Hint Resolve: command registers a
lemma as a hint to be used from now on by the \verb:auto: tactic, whose power 
may thus be incrementally augmented.

\subsection{Disjunction}

In a similar fashion, let us consider disjunction:

\begin{coq_example}
Lemma or_commutative : A \/ B -> B \/ A.
intro H; elim H.
\end{coq_example}

Let us prove the first subgoal in detail. We use \verb:intro: in order to
be left to prove \verb:B\/A: from \verb:A::

\begin{coq_example}
intro HA.
\end{coq_example}

Here the hypothesis \verb:H: is not needed anymore. We could choose to
actually erase it with the tactic \verb:clear:; in this simple proof it
does not really matter, but in bigger proof developments it is useful to
clear away unnecessary hypotheses which may clutter your screen.
\begin{coq_example}
clear H.
\end{coq_example}

The tactic \verb:destruct: combines the effects of \verb:elim:, \verb:intros:,
and \verb:clear::

\begin{coq_eval}
Abort.
\end{coq_eval}
\begin{coq_example}
Lemma or_commutative : A \/ B -> B \/ A.
intros H; destruct H.
\end{coq_example}

The disjunction connective has two introduction rules, since \verb:P\/Q:
may be obtained from \verb:P: or from \verb:Q:; the two corresponding
proof constructors are called respectively \verb:or_introl: and
\verb:or_intror:; they are applied to the current goal by tactics
\verb:left: and \verb:right: respectively. For instance:
\begin{coq_example}
right.
trivial.
\end{coq_example}
The tactic \verb:trivial: works like \verb:auto: with the hints
database, but it only tries those tactics that can solve the goal in one
step.

As before, all these tedious elementary steps may be performed automatically,
as shown for the second symmetric case:

\begin{coq_example}
auto.
\end{coq_example}

However, \verb:auto: alone does not succeed in proving the full lemma, because
it does not try any elimination step.
It is a bit disappointing that \verb:auto: is not able to prove automatically 
such a simple tautology. The reason is that we want to keep
\verb:auto: efficient, so that it is always effective to use.

\subsection{Tauto}

A complete tactic for propositional
tautologies is indeed available in \Coq{} as the \verb:tauto: tactic.
\begin{coq_eval}
Abort.
\end{coq_eval}
\begin{coq_example}
Lemma or_commutative : A \/ B -> B \/ A.
tauto.
Qed.
\end{coq_example}

It is possible to inspect the actual proof tree constructed by \verb:tauto:,
using a standard command of the system, which prints the value of any notion 
currently defined in the context:
\begin{coq_example}
Print or_commutative.
\end{coq_example}

It is not easy to understand the notation for proof terms without some
explanations. The \texttt{fun} prefix, such as \verb+fun H : A\/B =>+, 
corresponds
to \verb:intro H:, whereas a subterm such as 
\verb:(or_intror: \verb:B H0):
corresponds to the sequence of tactics \verb:apply or_intror; exact H0:. 
The generic combinator \verb:or_intror: needs to be instantiated by
the two properties \verb:B: and \verb:A:. Because \verb:A: can be
deduced from the type of \verb:H0:, only  \verb:B: is printed.
The two instantiations are effected automatically by the tactic
\verb:apply: when pattern-matching a goal. The specialist will of course
recognize our proof term as a $\lambda$-term, used as notation for the
natural deduction proof term through the Curry-Howard isomorphism. The
naive user of \Coq{} may safely ignore these formal details.

Let us exercise the \verb:tauto: tactic on a more complex example:
\begin{coq_example}
Lemma distr_and : A -> B /\ C -> (A -> B) /\ (A -> C).
tauto.
Qed.
\end{coq_example}

\subsection{Classical reasoning}

The tactic \verb:tauto: always comes back with an answer. Here is an example where it 
fails:
\begin{coq_example}
Lemma Peirce : ((A -> B) -> A) -> A.
try tauto.
\end{coq_example}

Note the use of the \verb:try: tactical, which does nothing if its tactic
argument fails.

This may come as a surprise to someone familiar with classical reasoning. 
Peirce's lemma is true in Boolean logic, i.e. it evaluates to \verb:true: for 
every truth-assignment to \verb:A: and \verb:B:. Indeed the double negation
of Peirce's law may be proved in \Coq{} using \verb:tauto::
\begin{coq_eval}
Abort.
\end{coq_eval}
\begin{coq_example}
Lemma NNPeirce : ~ ~ (((A -> B) -> A) -> A).
tauto.
Qed.
\end{coq_example}

In classical logic, the double negation of a proposition is equivalent to this 
proposition, but in the constructive logic of \Coq{} this is not so. If you
want to use classical logic in \Coq, you have to import explicitly the
\verb:Classical: module, which will declare the axiom \verb:classic:
of excluded middle, and classical tautologies such as de Morgan's laws.
The \verb:Require: command is used to import a module from \Coq's library:
\begin{coq_example}
Require Import Classical.
Check NNPP.
\end{coq_example}

and it is now easy (although admittedly not the most direct way) to prove
a classical law such as Peirce's:
\begin{coq_example}
Lemma Peirce : ((A -> B) -> A) -> A.
apply NNPP; tauto.
Qed.
\end{coq_example}

Here is one more example of propositional reasoning, in the shape of
a Scottish puzzle. A private club has the following rules:
\begin{enumerate}
\item Every non-scottish member wears red socks
\item Every member wears a kilt or doesn't wear red socks
\item The married members don't go out on Sunday
\item A member goes out on Sunday if and only if he is Scottish
\item Every member who wears a kilt is Scottish and married
\item Every scottish member wears a kilt
\end{enumerate}
Now, we show that these rules are so strict that no one can be accepted.
\begin{coq_example}
Section club.
Variables Scottish RedSocks WearKilt Married GoOutSunday : Prop.
Hypothesis rule1 : ~ Scottish -> RedSocks.
Hypothesis rule2 : WearKilt \/ ~ RedSocks.
Hypothesis rule3 : Married -> ~ GoOutSunday.
Hypothesis rule4 : GoOutSunday <-> Scottish.
Hypothesis rule5 : WearKilt -> Scottish /\ Married.
Hypothesis rule6 : Scottish -> WearKilt.
Lemma NoMember : False.
tauto.
Qed.
\end{coq_example}
At that point \verb:NoMember: is a proof of the absurdity depending on
hypotheses.
We may end the section, in that case, the variables and hypotheses
will be discharged, and the type of \verb:NoMember: will be
generalised.

\begin{coq_example}
End club.
Check NoMember.
\end{coq_example}

\section{Predicate Calculus}

Let us now move into predicate logic, and first of all into first-order
predicate calculus. The essence of predicate calculus is that to try to prove 
theorems in the most abstract possible way, without using the definitions of 
the mathematical notions, but by formal manipulations of uninterpreted 
function and predicate symbols.

\subsection{Sections and signatures}

Usually one works in some domain of discourse, over which range the individual 
variables and function symbols. In \Coq{}, we speak in a language with a rich
variety of types, so we may mix several domains of discourse, in our 
multi-sorted language. For the moment, we just do a few exercises, over a 
domain of discourse \verb:D: axiomatised as a \verb:Set:, and we consider two 
predicate symbols  \verb:P: and \verb:R: over \verb:D:, of arities 
1 and 2, respectively.

\begin{coq_eval}
Reset Initial.
Set Printing Width 60.
Set Printing Compact Contexts.
\end{coq_eval}

We start by assuming a domain of
discourse \verb:D:, and a binary relation \verb:R:  over \verb:D:: 
\begin{coq_example}
Section Predicate_calculus.
Variable D : Set.
Variable R : D -> D -> Prop.
\end{coq_example}

As a simple example of predicate calculus reasoning, let us assume
that relation \verb:R: is symmetric and transitive, and let us show that
\verb:R: is reflexive in any point \verb:x: which has an \verb:R: successor.
Since we do not want to make the assumptions about \verb:R: global axioms of 
a theory, but rather local hypotheses to a theorem, we open a specific
section to this effect.
\begin{coq_example}
Section R_sym_trans.
Hypothesis R_symmetric : forall x y : D, R x y -> R y x.
Hypothesis R_transitive :
    forall x y z : D, R x y -> R y z -> R x z.
\end{coq_example}

Note the syntax \verb+forall x : D,+ which stands for universal quantification
$\forall x : D$.

\subsection{Existential quantification}

We now state our lemma, and enter proof mode.
\begin{coq_example}
Lemma refl_if : forall x : D, (exists y, R x y) -> R x x.
\end{coq_example}

The hypotheses that are local to the currently opened sections
are listed as local hypotheses to the current goals.
That is because these hypotheses are going to be discharged, as
we shall see, when we shall close the corresponding sections.

Note the functional syntax for existential quantification. The existential
quantifier is built from the operator \verb:ex:, which expects a 
predicate as argument:
\begin{coq_example}
Check ex.
\end{coq_example}
and the notation \verb+(exists x : D, P x)+ is just concrete syntax for 
the expression \verb+(ex D (fun x : D => P x))+. 
Existential quantification is handled in \Coq{} in a similar
fashion to the connectives \verb:/\: and \verb:\/:: it is introduced by
the proof combinator \verb:ex_intro:, which is invoked by the specific 
tactic \verb:exists:, and its elimination provides a witness \verb+a : D+ to
\verb:P:, together with an assumption \verb+h : (P a)+ that indeed \verb+a+
verifies \verb:P:. Let us see how this works on this simple example.
\begin{coq_example}
intros x x_Rlinked.
\end{coq_example}

Note that \verb:intros: treats universal quantification in the same way
as the premises of implications. Renaming of bound variables occurs
when it is needed; for instance, had we started with \verb:intro y:,
we would have obtained the goal:
\begin{coq_eval}
Undo.
\end{coq_eval}
\begin{coq_example}
intro y.
\end{coq_example}
\begin{coq_eval}
Undo.
intros x x_Rlinked.
\end{coq_eval}

Let us now use the existential hypothesis \verb:x_Rlinked: to 
exhibit an R-successor y of x. This is done in two steps, first with
\verb:elim:, then with \verb:intros:

\begin{coq_example}
elim x_Rlinked.
intros y Rxy.
\end{coq_example}

Now we want to use \verb:R_transitive:. The \verb:apply: tactic will know
how to match \verb:x: with \verb:x:, and \verb:z: with \verb:x:, but needs
help on how to instantiate \verb:y:, which appear in the hypotheses of
\verb:R_transitive:, but not in its conclusion. We give the proper hint
to \verb:apply: in a \verb:with: clause, as follows:
\begin{coq_example}
apply R_transitive with y.
\end{coq_example}

The rest of the proof is routine:
\begin{coq_example}
assumption.
apply R_symmetric; assumption.
\end{coq_example}
\begin{coq_example*}
Qed.
\end{coq_example*}

Let us now close the current section.
\begin{coq_example}
End R_sym_trans.
\end{coq_example}

All the local hypotheses have been
discharged in the statement of \verb:refl_if:, which now becomes a general
theorem in the first-order language declared in section 
\verb:Predicate_calculus:. In this particular example, section
\verb:R_sym_trans: has not been really useful, since we could have
instead stated theorem \verb:refl_if: in its general form, and done 
basically the same proof, obtaining \verb:R_symmetric: and
\verb:R_transitive: as local hypotheses by initial \verb:intros: rather
than as global hypotheses in the context. But if we had pursued the
theory by proving more theorems about relation \verb:R:,
we would have obtained all general statements at the closing of the section,
with minimal dependencies on the hypotheses of symmetry and transitivity.

\subsection{Paradoxes of classical predicate calculus}

Let us illustrate this feature by pursuing our \verb:Predicate_calculus:
section with an enrichment of our language: we declare a unary predicate
\verb:P: and a constant \verb:d::
\begin{coq_example}
Variable P :  D -> Prop.
Variable d : D.
\end{coq_example}

We shall now prove a well-known fact from first-order logic: a universal 
predicate is non-empty, or in other terms existential quantification 
follows from universal quantification.
\begin{coq_example}
Lemma weird : (forall x:D, P x) ->  exists a, P a.
 intro UnivP.
\end{coq_example}

First of all, notice the pair of parentheses around
\verb+forall x : D, P x+ in
the statement of lemma \verb:weird:.
If we had omitted them, \Coq's parser would have interpreted the
statement as a truly trivial fact, since we would 
postulate an \verb:x: verifying \verb:(P x):. Here the situation is indeed
more problematic. If we have some element in \verb:Set: \verb:D:, we may
apply \verb:UnivP: to it and conclude, otherwise we are stuck. Indeed
such an element \verb:d: exists, but this is just by virtue of our
new signature. This points out a subtle difference between standard
predicate calculus and \Coq. In standard first-order logic,
the equivalent of lemma \verb:weird: always holds, 
because such a rule is wired in the inference rules for quantifiers, the
semantic justification being that the interpretation domain is assumed to
be non-empty. Whereas in \Coq, where types are not assumed to be 
systematically inhabited, lemma \verb:weird: only holds in signatures
which allow the explicit construction of an element in the domain of
the predicate.

Let us conclude the proof, in order to show the use of the \verb:exists:
tactic:
\begin{coq_example}
exists d; trivial.
Qed.
\end{coq_example}

Another fact which illustrates the sometimes disconcerting rules of
classical 
predicate calculus is Smullyan's drinkers' paradox: ``In any non-empty
bar, there is a person such that if she drinks, then everyone drinks''.
We modelize the bar by Set \verb:D:, drinking by predicate \verb:P:.
We shall need classical reasoning. Instead of loading the \verb:Classical:
module as we did above, we just state the law of excluded middle as a
local hypothesis schema at this point:
\begin{coq_example}
Hypothesis EM : forall A : Prop, A \/ ~ A.
Lemma drinker :  exists x : D, P x -> forall x : D, P x.
\end{coq_example}
The proof goes by cases on whether or not
there is someone who does not drink. Such reasoning by cases proceeds
by invoking the excluded middle principle, via \verb:elim: of the
proper instance of \verb:EM::
\begin{coq_example}
elim (EM (exists x, ~ P x)).
\end{coq_example}

We first look at the first case. Let Tom be the non-drinker.
The following combines at once the effect of \verb:intros: and
\verb:destruct::
\begin{coq_example}
intros (Tom, Tom_does_not_drink).
\end{coq_example}

We conclude in that case by considering Tom, since his drinking leads to
a contradiction:
\begin{coq_example}
exists Tom; intro Tom_drinks.
\end{coq_example}

There are several ways in which we may eliminate a contradictory case;
in this case, we use \verb:contradiction: to let \Coq{} find out the
two contradictory hypotheses:
\begin{coq_example}
contradiction.
\end{coq_example}

We now proceed with the second case, in which actually any person will do;
such a John Doe is given by the non-emptiness witness \verb:d::
\begin{coq_example}
intro No_nondrinker; exists d; intro d_drinks.
\end{coq_example}

Now we consider any Dick in the bar, and reason by cases according to its
drinking or not:
\begin{coq_example}
intro Dick; elim (EM (P Dick)); trivial.
\end{coq_example}

The only non-trivial case is again treated by contradiction:
\begin{coq_example}
intro Dick_does_not_drink; absurd (exists x, ~ P x); trivial.
exists Dick; trivial.
Qed.
\end{coq_example}

Now, let us close the main section and look at the complete statements
we proved:
\begin{coq_example}
End Predicate_calculus.
Check refl_if.
Check weird.
Check drinker.
\end{coq_example}

Note how the three theorems are completely generic in the most general 
fashion;
the domain \verb:D: is discharged in all of them, \verb:R: is discharged in
\verb:refl_if: only, \verb:P: is discharged only in \verb:weird: and
\verb:drinker:, along with the hypothesis that \verb:D: is inhabited. 
Finally, the excluded middle hypothesis is discharged only in 
\verb:drinker:.

Note, too, that the name \verb:d: has vanished from
the statements of \verb:weird: and \verb:drinker:, 
since \Coq's pretty-printer replaces
systematically a quantification such as \texttt{forall d : D, E},
where \texttt{d} does not occur in \texttt{E},
by the functional notation \texttt{D -> E}.
Similarly the name \texttt{EM} does not appear in \texttt{drinker}.

Actually, universal quantification, implication, 
as well as function formation, are
all special cases of one general construct of type theory called
{\sl dependent product}. This is the mathematical construction 
corresponding to an indexed family of functions. A function 
$f\in \Pi x:D\cdot Cx$ maps an element $x$ of its domain $D$ to its
(indexed) codomain $Cx$. Thus a proof of $\forall x:D\cdot Px$ is
a function mapping an element $x$ of $D$ to a proof of proposition $Px$.

\subsection{Flexible use of local assumptions}

Very often during the course of a proof we want to retrieve a local
assumption and reintroduce it explicitly in the goal, for instance
in order to get a more general induction hypothesis. The tactic
\verb:generalize: is what is needed here:

\begin{coq_example}
Section Predicate_Calculus.
Variables P Q : nat -> Prop.
Variable R :  nat -> nat -> Prop.
Lemma PQR :
 forall x y:nat, (R x x -> P x -> Q x) -> P x -> R x y -> Q x.
intros.
generalize H0.
\end{coq_example}

Sometimes it may be convenient to state an intermediate fact.
The tactic \verb:assert: does this and introduces a new subgoal
for this fact to be proved first. The tactic \verb:enough: does
the same while keeping this goal for later.
\begin{coq_example}
enough (R x x) by auto.
\end{coq_example}
We clean the goal by doing an \verb:Abort: command.
\begin{coq_example*}
Abort.
\end{coq_example*}

\subsection{Equality}

The basic equality provided in \Coq{} is Leibniz equality, noted infix like
\texttt{x = y}, when \texttt{x} and \texttt{y} are two expressions of
type the same Set. The replacement of \texttt{x} by \texttt{y} in any
term is effected by a variety of tactics, such as \texttt{rewrite}
and \texttt{replace}.

Let us give a few examples of equality replacement. Let us assume that
some arithmetic function \verb:f: is null in zero:
\begin{coq_example}
Variable f : nat -> nat.
Hypothesis foo : f 0 = 0.
\end{coq_example}

We want to prove the following conditional equality:
\begin{coq_example*}
Lemma L1 : forall k:nat, k = 0 -> f k = k.
\end{coq_example*}

As usual, we first get rid of local assumptions with \verb:intro::
\begin{coq_example}
intros k E.
\end{coq_example}

Let us now use equation \verb:E: as a left-to-right rewriting:
\begin{coq_example}
rewrite E.
\end{coq_example}
This replaced both occurrences of \verb:k: by \verb:O:.

Now \verb:apply foo: will finish the proof:

\begin{coq_example}
apply foo.
Qed.
\end{coq_example}

When one wants to rewrite an equality in a right to left fashion, we should
use \verb:rewrite <- E: rather than \verb:rewrite E: or the equivalent
\verb:rewrite -> E:. 
Let us now illustrate the tactic \verb:replace:.
\begin{coq_example}
Hypothesis f10 : f 1 = f 0.
Lemma L2 : f (f 1) = 0.
replace (f 1) with 0.
\end{coq_example}
What happened here is that the replacement left the first subgoal to be
proved, but another proof obligation was generated by the \verb:replace:
tactic, as the second subgoal. The first subgoal is solved immediately
by applying lemma \verb:foo:; the second one transitivity and then 
symmetry of equality, for instance with tactics \verb:transitivity: and 
\verb:symmetry::
\begin{coq_example}
apply foo.
transitivity (f 0); symmetry; trivial.
\end{coq_example}
In case the equality $t=u$ generated by \verb:replace: $u$ \verb:with:
$t$ is an assumption
(possibly modulo symmetry), it will be automatically proved and the
corresponding goal will not appear. For instance:

\begin{coq_eval}
Restart.
\end{coq_eval}
\begin{coq_example}
Lemma L2 : f (f 1) = 0.
replace (f 1) with (f 0).
replace (f 0) with 0; trivial.
Qed.
\end{coq_example}

\section{Using definitions}

The development of mathematics does not simply proceed by logical 
argumentation from first principles: definitions are used in an essential way.
A formal development proceeds by a dual process of abstraction, where one
proves abstract statements in predicate calculus, and use of definitions, 
which in the contrary one instantiates general statements with particular 
notions in order to use the structure of mathematical values for the proof of
more specialised properties.

\subsection{Unfolding definitions}

Assume that we want to develop the theory of sets represented as characteristic
predicates over some universe \verb:U:. For instance:
\begin{coq_example}
Variable U : Type.
Definition set := U -> Prop.
Definition element (x : U) (S : set) := S x.
Definition subset (A B : set) := 
  forall x : U, element x A -> element x B.
\end{coq_example}

Now, assume that we have loaded a module of general properties about
relations over some abstract type \verb:T:, such as transitivity:

\begin{coq_example}
Definition transitive (T : Type) (R : T -> T -> Prop) :=
  forall x y z : T, R x y -> R y z -> R x z.
\end{coq_example}

We want to prove that \verb:subset: is a \verb:transitive:
relation. 
\begin{coq_example}
Lemma subset_transitive : transitive set subset.
\end{coq_example}

In order to make any progress, one needs to use the definition of
\verb:transitive:. The \verb:unfold: tactic, which replaces all
occurrences of a defined notion by its definition in the current goal,
may be used here.
\begin{coq_example}
unfold transitive.
\end{coq_example}

Now, we must unfold \verb:subset::
\begin{coq_example}
unfold subset.
\end{coq_example}
Now, unfolding \verb:element: would be a mistake, because indeed a simple proof
can be found by \verb:auto:, keeping \verb:element: an abstract predicate:
\begin{coq_example}
auto.
\end{coq_example}

Many variations on \verb:unfold: are provided in \Coq. For instance,
instead of unfolding all occurrences of \verb:subset:, we may want to
unfold only one designated occurrence:
\begin{coq_eval}
Undo 2.
\end{coq_eval}
\begin{coq_example}
unfold subset at 2.
\end{coq_example}

One may also unfold a definition in a given local hypothesis, using the
\verb:in: notation:
\begin{coq_example}
intros.
unfold subset in H.
\end{coq_example}

Finally, the tactic \verb:red: does only unfolding of the head occurrence
of the current goal:
\begin{coq_example}
red.
auto.
Qed.
\end{coq_example}

\subsection{Principle of proof irrelevance}

Even though in principle the proof term associated with a verified lemma
corresponds to a defined value of the corresponding specification, such
definitions cannot be unfolded in \Coq: a lemma is considered an {\sl opaque}
definition. This conforms to the mathematical tradition of {\sl proof
irrelevance}: the proof of a logical proposition does not matter, and the
mathematical justification of a logical development relies only on
{\sl provability} of the lemmas used in the formal proof.

Conversely, ordinary mathematical definitions can be unfolded at will, they
are {\sl transparent}.

\chapter{Induction}

\begin{coq_eval}
Reset Initial.
Set Printing Width 60.
Set Printing Compact Contexts.
\end{coq_eval}

\section{Data Types as Inductively Defined Mathematical Collections}

All the notions which were studied until now pertain to traditional
mathematical logic. Specifications of objects were abstract properties
used in reasoning more or less constructively; we are now entering
the realm of inductive types, which specify the existence of concrete
mathematical constructions.

\subsection{Booleans}

Let us start with the collection of booleans, as they are specified
in the \Coq's \verb:Prelude: module: 
\begin{coq_example}
Inductive bool :  Set := true | false.
\end{coq_example}

Such a declaration defines several objects at once. First, a new
\verb:Set: is declared, with name \verb:bool:. Then the {\sl constructors}
of this \verb:Set: are declared, called \verb:true: and \verb:false:.
Those are analogous to introduction rules of the new Set \verb:bool:.
Finally, a specific elimination rule for \verb:bool: is now available, which
permits to reason by cases on \verb:bool: values. Three instances are
indeed defined as new combinators in the global context: \verb:bool_ind:,
a proof combinator corresponding to reasoning by cases,
\verb:bool_rec:, an if-then-else programming construct,
and \verb:bool_rect:, a similar combinator at the level of types.
Indeed:
\begin{coq_example}
Check bool_ind.
Check bool_rec.
Check bool_rect.
\end{coq_example}

Let us for instance prove that every Boolean is true or false.
\begin{coq_example}
Lemma duality : forall b:bool, b = true \/ b = false.
intro b.
\end{coq_example}

We use the knowledge that \verb:b: is a \verb:bool: by calling tactic
\verb:elim:, which is this case will appeal to combinator \verb:bool_ind:
in order to split the proof according to the two cases:
\begin{coq_example}
elim b.
\end{coq_example}

It is easy to conclude in each case:
\begin{coq_example}
left; trivial.
right; trivial.
\end{coq_example}

Indeed, the whole proof can be done with the combination of the
 \verb:destruct:, which combines \verb:intro: and \verb:elim:,
with good old \verb:auto::
\begin{coq_eval}
Abort.
\end{coq_eval}
\begin{coq_example}
Lemma duality : forall b:bool, b = true \/ b = false.
destruct b; auto.
Qed.
\end{coq_example}

\subsection{Natural numbers}

Similarly to Booleans, natural numbers are defined in the \verb:Prelude:
module with constructors \verb:S: and \verb:O::
\begin{coq_example}
Inductive nat : Set :=
  | O : nat
  | S : nat -> nat.
\end{coq_example}

The elimination principles which are automatically generated are Peano's
induction principle, and a recursion operator:
\begin{coq_example}
Check nat_ind.
Check nat_rec.
\end{coq_example}

Let us start by showing how to program the standard primitive recursion
operator \verb:prim_rec: from the more general \verb:nat_rec::
\begin{coq_example}
Definition prim_rec := nat_rec (fun i : nat => nat).
\end{coq_example}

That is, instead of computing for natural \verb:i: an element of the indexed
\verb:Set: \verb:(P i):, \verb:prim_rec: computes uniformly an element of 
\verb:nat:. Let us check the type of \verb:prim_rec::
\begin{coq_example}
About prim_rec.
\end{coq_example}

Oops! Instead of the expected type \verb+nat->(nat->nat->nat)->nat->nat+ we
get an apparently more complicated expression.
In fact, the two types are convertible and one way of having the proper
type would be to do some computation before actually defining \verb:prim_rec:
as such:

\begin{coq_eval}
Reset Initial.
Set Printing Width 60.
Set Printing Compact Contexts.
\end{coq_eval}

\begin{coq_example}
Definition prim_rec :=
    Eval compute in nat_rec (fun i : nat => nat).
About prim_rec.
\end{coq_example}

Let us now show how to program addition with primitive recursion:
\begin{coq_example}
Definition addition (n m:nat) :=
    prim_rec m (fun p rec : nat => S rec) n.
\end{coq_example}

That is, we specify that \verb+(addition n m)+ computes by cases on \verb:n:
according to its main constructor; when \verb:n = O:, we get \verb:m:;
 when \verb:n = S p:, we get \verb:(S rec):, where \verb:rec: is the result
of the recursive computation \verb+(addition p m)+. Let us verify it by
asking \Coq{} to compute for us say $2+3$:
\begin{coq_example}
Eval compute in (addition (S (S O)) (S (S (S O)))).
\end{coq_example}

Actually, we do not have to do all explicitly. {\Coq} provides a
special syntax {\tt Fixpoint/match} for generic primitive recursion,
and we could thus have defined directly addition as:

\begin{coq_example}
Fixpoint plus (n m:nat) {struct n} : nat :=
  match n with
  | O => m
  | S p => S (plus p m)
  end.
\end{coq_example}

\begin{coq_eval}
\begin{coq_example}
Reset Initial.
Set Printing Width 60.
Set Printing Compact Contexts.
\end{coq_eval}

\subsection{Simple proofs by induction}

Let us now show how to do proofs by structural induction. We start with easy
properties of the \verb:plus: function we just defined. Let us first
show that $n=n+0$.
\begin{coq_example}
Lemma plus_n_O : forall n : nat, n = n + 0.
intro n; elim n.
\end{coq_example}

What happened was that \texttt{elim n}, in order to construct a \texttt{Prop}
(the initial goal) from a \texttt{nat} (i.e. \texttt{n}), appealed to the
corresponding induction principle \texttt{nat\_ind} which we saw was indeed
exactly Peano's induction scheme. Pattern-matching instantiated the 
corresponding predicate \texttt{P} to \texttt{fun n : nat => n = n + 0},
and we get as subgoals the corresponding instantiations of the base case
\texttt{(P O)}, and of the inductive step
\texttt{forall y : nat, P y -> P (S y)}.
In each case we get an instance of function \texttt{plus} in which its second
argument starts with a constructor, and is thus amenable to simplification
by primitive recursion. The \Coq{} tactic \texttt{simpl} can be used for
this purpose:
\begin{coq_example}
simpl.
auto.
\end{coq_example}

We proceed in the same way for the base step:
\begin{coq_example}
simpl; auto.
Qed.
\end{coq_example}

Here \verb:auto: succeeded, because it used as a hint lemma \verb:eq_S:,
which say that successor preserves equality:
\begin{coq_example}
Check eq_S.
\end{coq_example}

Actually, let us see how to declare our lemma \verb:plus_n_O: as a hint
to be used by \verb:auto::
\begin{coq_example}
Hint Resolve plus_n_O .
\end{coq_example}

We now proceed to the similar property concerning the other constructor
\verb:S::
\begin{coq_example}
Lemma plus_n_S : forall n m:nat, S (n + m) = n + S m.
\end{coq_example}

We now go faster, using the tactic \verb:induction:, which does the
necessary \verb:intros: before applying \verb:elim:. Factoring simplification
and automation in both cases thanks to tactic composition, we prove this
lemma in one line:
\begin{coq_example}
induction n; simpl; auto.
Qed.
Hint Resolve plus_n_S .
\end{coq_example}

Let us end this exercise with the commutativity of \verb:plus::

\begin{coq_example}
Lemma plus_com : forall n m:nat, n + m = m + n.
\end{coq_example}

Here we have a choice on doing an induction on \verb:n: or on \verb:m:, the
situation being symmetric. For instance:
\begin{coq_example}
induction m as [ | m IHm ]; simpl; auto.
\end{coq_example}

Here \verb:auto: succeeded on the base case, thanks to our hint
\verb:plus_n_O:, but the induction step requires rewriting, which
\verb:auto: does not handle:

\begin{coq_example}
rewrite <- IHm; auto.
Qed.
\end{coq_example}

\subsection{Discriminate}

It is also possible to define new propositions by primitive recursion.
Let us for instance define the predicate which discriminates between
the constructors \verb:O: and \verb:S:: it computes to \verb:False: 
when its argument is \verb:O:, and to \verb:True: when its argument is 
of the form \verb:(S n)::
\begin{coq_example}
Definition Is_S (n : nat) := match n with
                             | O => False
                             | S p => True
                             end.
\end{coq_example}

Now we may use the computational power of \verb:Is_S: to prove
trivially that \verb:(Is_S (S n))::
\begin{coq_example}
Lemma S_Is_S : forall n:nat, Is_S (S n).
simpl; trivial.
Qed.
\end{coq_example}

But we may also use it to transform a \verb:False: goal into 
\verb:(Is_S O):. Let us show a particularly important use of this feature;
we want to prove that \verb:O: and \verb:S: construct different values, one
of Peano's axioms:
\begin{coq_example}
Lemma no_confusion : forall n:nat, 0 <> S n.
\end{coq_example}

First of all, we replace negation by its definition, by reducing the
goal with tactic \verb:red:; then we get contradiction by successive
\verb:intros::
\begin{coq_example}
red; intros n H.
\end{coq_example}

Now we use our trick:
\begin{coq_example}
change (Is_S 0).
\end{coq_example}

Now we use equality in order to get a subgoal which computes out to 
\verb:True:, which finishes the proof:
\begin{coq_example}
rewrite H; trivial.
simpl; trivial.
\end{coq_example}

Actually, a specific tactic \verb:discriminate: is provided
to produce mechanically such proofs, without the need for the user to define
explicitly the relevant discrimination predicates:

\begin{coq_eval}
Abort.
\end{coq_eval}
\begin{coq_example}
Lemma no_confusion : forall n:nat, 0 <> S n.
intro n; discriminate.
Qed.
\end{coq_example}

\section{Logic programming}

In the same way as we defined standard data-types above, we
may define inductive families, and for instance inductive predicates.
Here is the definition of predicate $\le$ over type \verb:nat:, as
given in \Coq's \verb:Prelude: module:
\begin{coq_example*}
Inductive le (n : nat) : nat -> Prop :=
  | le_n : le n n
  | le_S : forall m : nat, le n m -> le n (S m).
\end{coq_example*}

This definition introduces a new predicate
\verb+le : nat -> nat -> Prop+,
and the two constructors \verb:le_n: and \verb:le_S:, which are the
defining clauses of \verb:le:. That is, we get not only the ``axioms''
\verb:le_n: and \verb:le_S:, but also the converse property, that 
\verb:(le n m): if and only if this statement can be obtained as a
consequence of these defining clauses; that is, \verb:le: is the
minimal predicate verifying clauses \verb:le_n: and \verb:le_S:. This is
insured, as in the case of inductive data types, by an elimination principle,
which here amounts to an induction principle \verb:le_ind:, stating this 
minimality property:
\begin{coq_example}
Check le.
Check le_ind.
\end{coq_example}

Let us show how proofs may be conducted with this principle.
First we show that $n\le m \Rightarrow n+1\le m+1$:
\begin{coq_example}
Lemma le_n_S : forall n m : nat, le n m -> le (S n) (S m).
intros n m n_le_m.
elim n_le_m.
\end{coq_example}

What happens here is similar to the behaviour of \verb:elim: on natural
numbers: it appeals to the relevant induction principle, here \verb:le_ind:,
which generates the two subgoals, which may then be solved easily
with the help of the defining clauses of \verb:le:.
\begin{coq_example}
apply le_n; trivial.
intros; apply le_S; trivial.
\end{coq_example}

Now we know that it is a good idea to give the defining clauses as hints,
so that the proof may proceed with a simple combination of 
\verb:induction: and \verb:auto:. \verb:Hint Constructors le:
is just an abbreviation for \verb:Hint Resolve le_n le_S:.
\begin{coq_eval}
Abort.
\end{coq_eval}
\begin{coq_example}
Hint Constructors le.
Lemma le_n_S : forall n m : nat, le n m -> le (S n) (S m).
\end{coq_example}

We have a slight problem however. We want to say ``Do an induction on
hypothesis \verb:(le n m):'', but we have no explicit name for it. What we
do in this case is to say ``Do an induction on the first unnamed hypothesis'',
as follows.
\begin{coq_example}
induction 1; auto.
Qed.
\end{coq_example}

Here is a more tricky problem. Assume we want to show that
$n\le 0 \Rightarrow n=0$. This reasoning ought to follow simply from the
fact that only the first defining clause of \verb:le: applies.
\begin{coq_example} 
Lemma tricky : forall n:nat, le n 0 -> n = 0.
\end{coq_example}

However, here trying something like \verb:induction 1: would lead
nowhere (try it and see what happens). 
An induction on \verb:n: would not be convenient either.
What we must do here is analyse the definition of \verb"le" in order
to match hypothesis \verb:(le n O): with the defining clauses, to find
that only \verb:le_n: applies, whence the result. 
This analysis may be performed by the ``inversion'' tactic
\verb:inversion_clear: as follows:
\begin{coq_example} 
intros n H; inversion_clear H.
trivial.
Qed.
\end{coq_example}

\chapter{Modules}

\begin{coq_eval}
Reset Initial.
Set Printing Width 60.
Set Printing Compact Contexts.
\end{coq_eval}

\section{Opening library modules}

When you start \Coq{} without further requirements in the command line,
you get a bare system with few libraries loaded.  As we saw, a standard
prelude module provides the standard logic connectives, and a few
arithmetic notions. If you want to load and open other modules from
the library, you have to use the \verb"Require" command, as we saw for
classical logic above. For instance, if you want more arithmetic
constructions, you should request:
\begin{coq_example*}
Require Import Arith.
\end{coq_example*}

Such a command looks for a (compiled) module file \verb:Arith.vo: in
the libraries registered by \Coq. Libraries inherit the structure of
the file system of the operating system and are registered with the
command \verb:Add LoadPath:. Physical directories are mapped to
logical directories. Especially the standard library of \Coq{} is
pre-registered as a library of name \verb=Coq=.  Modules have absolute
unique names denoting their place in \Coq{} libraries.  An absolute
name is a sequence of single identifiers separated by dots.  E.g. the
module \verb=Arith= has full name \verb=Coq.Arith.Arith= and because
it resides in eponym subdirectory \verb=Arith= of the standard
library, it can be as well required by the command

\begin{coq_example*}
Require Import Coq.Arith.Arith.
\end{coq_example*}

This may be useful to avoid ambiguities if somewhere, in another branch
of the libraries known by Coq, another module is also called
\verb=Arith=. Notice that by default, when a library is registered,
all its contents, and all the contents of its subdirectories recursively are
visible and accessible by a short (relative) name as \verb=Arith=.
Notice also that modules or definitions not explicitly registered in
a library are put in a default library called \verb=Top=.

The loading of a compiled file is quick, because the corresponding
development is not type-checked again.

\section{Creating your own modules}

You may create your own module files, by writing {\Coq} commands in a file,
say \verb:my_module.v:. Such a module may be simply loaded in the current
context, with command \verb:Load my_module:. It may also be compiled,
in ``batch'' mode, using the UNIX command
\verb:coqc:. Compiling the module \verb:my_module.v: creates a 
file \verb:my_module.vo:{} that can be reloaded with command
\verb:Require: \verb:Import: \verb:my_module:.

If a required module depends on other modules then the latters are
automatically required beforehand. However their contents is not
automatically visible.  If you want a module \verb=M= required in a
module \verb=N= to be automatically visible when \verb=N= is required,
you should use \verb:Require Export M: in your module \verb:N:.

\section{Managing the context}

It is often difficult to remember the names of all lemmas and
definitions available in the current context, especially if large
libraries have been loaded. A convenient \verb:Search: command
is available to lookup all known facts 
concerning a given predicate. For instance, if you want to know all the
known lemmas about both the successor and the less or equal relation, just ask:
\begin{coq_eval}
Reset Initial.
Set Printing Width 60.
Set Printing Compact Contexts.
\end{coq_eval}
\begin{coq_example}
Search S le.
\end{coq_example}
Another command \verb:SearchHead: displays only lemmas where the searched
predicate appears at the head position in the conclusion.
\begin{coq_example}
SearchHead le.
\end{coq_example}

The \verb:Search: commands also allows finding the theorems
containing a given pattern, where \verb:_: can be used in
place of an arbitrary term. As shown in this example, \Coq{}
provides usual infix notations for arithmetic operators.

\begin{coq_example}
Search (_ + _ = _).
\end{coq_example}

\section{Now you are on your own}

This tutorial is necessarily incomplete. If you wish to pursue serious
proving in \Coq, you should now get your hands on \Coq's Reference Manual,
which contains a complete description of all the tactics we saw, 
plus many more.
You also should look in the library of developed theories which is distributed
with \Coq, in order to acquaint yourself with various proof techniques.

\end{document}

### 2018-07-17 CASES_DEVELOPMENT/POROUS_ROTATING_DISK/TEX/lojacono_fabre_prf.tex
Reorganization of the arborescence (redone with « git mv » to keep tracking)

%\documentclass[a4paper,12pt]{article}
\documentclass[showpacs,preprintnumbers,amsmath,amssymb,aps]{revtex4-1}
%\setlength{\textwidth}{17.2cm}
%\setlength{\textheight}{22.8cm}
%\setlength{\oddsidemargin}{-.3cm}
%\setlength{\evensidemargin}{-.3cm}
%\documentclass[10pt,twocolumn]{article}
%\documentclass[floatfix,twocolumn,aps,pra,superscriptaddress,showpacs]{revtex}
%\usepackage[utf8x]{inputenc}
\usepackage{caption}
%\usepackage[font=small,format=plain,labelfont=bf,up,textfont=normal,up,justification=justified,singlelinecheck=false]{caption}
\usepackage{default}
\usepackage{amssymb}
\usepackage{color}
\usepackage{amsmath}
%\usepackage[spanish]{babel}
\usepackage{mathrsfs}
\usepackage{graphicx}
\usepackage{subfig}
\usepackage{epsfig}
% Title Page

%\documentclass[aip,pof,amsmath,amssymb,preprint]{revtex4-1}

%\usepackage{graphicx}% Include figure files
%\usepackage{dcolumn}% Align table columns on decimal point
%\usepackage{bm}% bold math

%\usepackage{graphicx}
%\usepackage[T1]{fontenc}

\begin{document}

\title{{\bf Linear stability analysis of a disc: effect of porosity.}} 
\author{D. Lo Jacono}
\affiliation{
Institut de M\'ecanique des Fluides de Toulouse (IMFT), Universit\'e de Toulouse, CNRS, Toulouse, France} 
\author{D. Fabre}
\affiliation{
Institut de M\'ecanique des Fluides de Toulouse (IMFT), Universit\'e de Toulouse, CNRS, Toulouse, France} 
\date{\today}

% ----------------------------------------------------------------------------
\begin{abstract}
Axisymmetric wake of a disc placed normal to the incoming uniform flow. Focus from the trivial solution upto the onset of several unstable sutuations. Two main parameter is explored (Reynolds number, and porosity). Maybe we will explore some swirl. what about aspect-ratio. Understand basic mechanism of classical scenario with the effect of a porosiy. 
\end{abstract}   
% ---------------------------------------------------------------------------
\maketitle

\section{Introduction}

\section{Governing equations}\label{equations}
axisymmetric

\begin{figure}
\caption{Sketch of the geometry .\label{sketch}}
\end{figure}
Aspect-ratio of disc: 0.3 . thickness over diameter.

\section{Numerical method}
\label{numerics}
FreeFem+
here modelling of the porosity.
\cite{thompson:96}
\section{Results}
\label{results}
\subsection{The solid case: $\alpha=1$}

\subsection{The porous case: $\alpha<1$}

\subsection{Direct numerical simulations for $\alpha=1$}
some DNS simulations?

\section{Conclusions}\label{conclusions}

\bibliography{lit}

\end{document}

### 2018-07-17 99_Documentation/ARTICLE_STABFEM/ARTICLE_ASME_V3diogo.tex

--- 2018-05-24 ARTICLE_STABFEM/ARTICLE_ASME_V2.tex
@@
 %%% use twocolumn and 10pt options with the asme2ej format
+
 \documentclass[twocolumn,10pt]{asme2ej}
 
+\usepackage[none]{hyphenat}
 \usepackage{epsfig} %% for loading postscript figures
 \usepackage{amsmath}
+
+\usepackage{breqn}
 
@@
 \begin{eqnarray} \label{NSprimitive}
-\partial_t {\bf u} = {\cal NS} ({\bf u};p)
-\equiv - {\bf u} \cdot \nabla {\bf u} - \nabla p + \frac{2}{Re}  \nabla \cdot {\mathsf{D}}({\bf u})  \\
+\partial_t {\bf u} = {\color{red}{\cal NS} ({\bf u},p)}
+\equiv - {\bf u} \cdot \nabla {\bf u} - \nabla p + \frac{2}{Re}  \nabla \cdot {\mathsf{D}}({\bf u}),  \\
 \nabla \cdot {\bf u} = 0,
@@
  {\mathsf{D}}({\bf u}) = 1/2
-\left( \nabla {\bf u} +  \nabla^T  {\bf u}\right)
+\left( \nabla {\bf u} +  \nabla^T  {\bf u}\right),
 $$ 
@@
 $$
-\left< \phi_1, \phi_2 \right> = \int_\Omega \overline{\phi}_1 \cdot \phi_2   \mbox{ d} \Omega
+\left< \phi_1, \phi_2 \right> = \int_\Omega \overline{\phi}_1 \cdot \phi_2   \mbox{ d} \Omega,
 $$
@@
 \be{NSweak}
-\forall [{\bf v},q], \quad \partial_t \left< {\bf v}, {\bf u}\right> = \left< {\bf v} , {\cal NS} ({\bf u};p) \right> + \left< q, \nabla \cdot {\bf u}\right>.
+\forall [{\bf v},q], \quad \partial_t \left< {\bf v}, {\bf u}\right> = \left< {\bf v} , {\color{red}{\cal NS} ({\bf u},p)} \right> + \left< q, \nabla \cdot {\bf u}\right>.
 \ee
@@
 
-We look for a steady base-flow $({\bf u}_b;p_b)$ satisfying the steady Navier-Stokes equations, i.e. 
-${\cal NS} ({\bf u}_b,p_b) = 0$.
-Suppose that we have a 'guess' for the base flow $[{\bf u}_b^g,p_b^g]$  which almost satisfies the equations.  We look for a better approximation under the form
+We look for a steady base-flow {\color{red}$[{\bf u}_b,p_b]$} satisfying the steady Navier-Stokes equations, i.e. 
+%${\cal NS} ({\bf u}_b,p_b) = 0$.
+{\color{red}${\cal NS} ({\bf u}_b,p_b) = 0$.}
+Suppose that we have a {\color{red}``guess''}  for the base flow $[{\bf u}_b^g,p_b^g]$  which almost satisfies the equations.  We look for a better approximation under the form
 \be{Newton1}
@@
 Injecting (\ref{Newton1}) into the weak form (\ref{NSweak}) of the Navier-Stokes equations and developing up to linear terms in terms of the perturbation lead to  
-${\cal NS}  ({\bf u}_b^g,p_b^g) + {\cal L} _{{\bf u}_b^g}(\delta {\bf u}_b,\delta p_b;{\bf u}_b^g)$, which can also be written in weak form as :
+${\cal NS}  ({\bf u}_b^g,p_b^g) + {\color{red} {\cal L} _{{\bf u}_b^g}(\delta {\bf u}_b,\delta p_b)}$, which can also be written in weak form as :
 %\be
@@
 \bes{Newton2}
-&\left< {\bf v}, {\cal NS} ({\bf u}_b^g)\right> + \left<q, \nabla \cdot {\bf u}_b^g\right>  
-\\
-+ &\left< { \bf v}, {\cal L} _{{\bf u}_b^g}( \delta {\bf u}_b,\delta p_b; {\bf u}_b^g) \right> + \left<q, \nabla \cdot \delta{\bf u}_b\right> = 0,
+&\left< {\bf v}, {\color{red}{\cal NS} ({\bf u}_b^g,p_b^g)}\right> + \left<q, \nabla \cdot {\bf u}_b^g\right>  
+\\
++ &\left< { \bf v}, {\color{red}{\cal L} _{{\bf u}_b^g}( \delta {\bf u}_b,\delta p_b) }\right> + \left<q, \nabla \cdot \delta{\bf u}_b\right> = 0,
 \ees
-where ${\cal L}$ is the linearised Navier-Stokes operator, defined by its action on a flow field $({\bf u} ; p)$ as follows 
+where ${\cal L}$ is the linearised Navier-Stokes operator, defined by its action on a flow field {\color{red}$[{\bf u} , p]$} as follows 
 \be{defNSL}
- {\cal L}_{{\bf U}}( {\bf u}, p; {\bf U}) = - {\cal C}( {\bf U} , {\bf u}) -\nabla p
+{\color{red} {\cal L}_{{\bf U}}( {\bf u}, p)} = - {\cal C}( {\bf U} , {\bf u}) -\nabla p
 +\frac{2}{Re} \nabla  \cdot {\mathsf{D}}({\bf u}), %\quad ( \mbox{ with } \nabla \cdot {\bf u } = 0 \, ).
@@
 This problem can now be discretized by projecting upon a basis of Taylor-Hood $(u,v,p) \rightarrow (P2,P2,P1)$ finite elements.
-Noting $\delta X$ the discretization of ($\delta {\bf u}_b;\delta p_b$) this eventually leads to a matricial problem of the form $A \cdot \delta X = Y$.
+Noting $\delta X$ the discretization of {\color{red}$[\delta {\bf u}_b,\delta p_b]$} this eventually leads to a matricial problem of the form $A \cdot \delta X = Y$.
 The procedure of Newton iteration is to solve iteratively this set of equations up to convergence.
@@
 \be{startmodepropre}
-{\bf u} ({\bf{x}},t) = {\bf u}_b({\bf{x}}) + \epsilon \hat{\bf u}({\bf{x}}) e^{\lambda t}, \,\,\,\, {p}({\bf{x}},t) = {p}_b({\bf{x}}) + \epsilon \hat{p}({\bf{x}}) e^{\lambda t}
+{\bf u} ({\bf{x}},t) = {\bf u}_b({\bf{x}}) + \epsilon \hat{\bf u}({\bf{x}}) e^{\lambda t}, \,\,\,\, {p}({\bf{x}},t) = {p}_b({\bf{x}}) + \epsilon \hat{p}({\bf{x}}) e^{\lambda t},
 \ee
@@
 \be{Eigen_matricial}
-\lambda {\mathsf{B}} \hat{X} = {\mathsf{A}} \hat{X}
-\ee
-Where ${\mathsf{A}}$ is the matrix resulting from the discretization of ${\cal L}_{{\bf u}_b}$, i.e.
+\lambda {\mathsf{B}} \hat{X} = {\mathsf{A}} \hat{X},
+\ee
+{\color{red} where} ${\mathsf{A}}$ is the matrix resulting from the discretization of ${\cal L}_{{\bf u}_b}$, i.e.
 the same matrix  appearing in the Newton computation of the base flow, and  $B$ is a 'weight' matrix associated to the scalar product $\left<v,u\right> = \int \overline{\bf v} \cdot {\bf u} \mbox{ d} \Omega$.
@@
 D = F_x ({\bf u},p) = 
- \int_{\Gamma_{cil}} \left[-p {\bf n} + \frac{2}{Re} {\bf D}({\bf u}) \cdot {\bf n} \right]   \cdot {\bf e_x} d\ell
+ \int_{\Gamma_{cil}} \left[-p {\bf n} + \frac{2}{Re} {\bf D}({\bf u}) \cdot {\bf n} \right]   \cdot {\bf e_x} d\ell,
 \ee
@@
 In the past decade, efforts have been devoted to extend the range of validity of global approaches into the nonlinear regime for $Re>Re_c$, with the double objective to describe the properties of the limit cycle reached after saturation and to derive amplitude equations describing the transitent dynamics towards this cycle.
-The two main milestones in this direction is the {\em weakly nonlinear model}  (WNL) of Sipp \& Lebedev \cite{SippLebedev} and the {\em self-consistent model} (SC) of Manti\v{c}-Lugo et al \cite{MLugo2014}.
- {\color{blue} In this review, we will address only the first of the two questions, namely description of the saturated cycle, and leave aside the question of transient dynamics.
+The two main milestones in this direction {\color{red} are} the {\em weakly nonlinear model}  (WNL) of Sipp \& Lebedev \cite{SippLebedev} and the {\em self-consistent model} (SC) of Manti\v{c}-Lugo et al \cite{MLugo2014}.
+ {\color{blue} In this review, we will address only the first of the two questions, namely {\color{red} the} description of the saturated cycle, and leave aside the question of transient dynamics.
 We will successively review the two aforementioned models, in a simplified formulation devoted to describe only the saturated cycle.
@@
 
-\paragraph{General definitions in the nonlinear régime}
-
-In this part, to simplify the notations, we symbolically write the Navier-Stokes equations, as $\partial_t {\bf u} = {\cal 
-NS} ({\bf u};p)$, therefore dropping the systematic reference to the 
-incompressibility constraint and associated pressure field.
-
-In the nonlinear régime, the {\em base flow} introduced in the linear theory is not directly accessible and no longer relevant, especially when the oscillation amplitudes become large. 
-Instead, we will define a {\em mean flow}  as the time-average  of the flow :
+\paragraph{General definitions in the nonlinear r{\color{red}e}gime}
+
+In this part, to simplify the notations, we symbolically write the Navier-Stokes equations, as {\color{red}$\partial_t {\bf u} = {\cal NS} ({\bf u})$}, therefore dropping the systematic reference to the incompressibility constraint and associated pressure field.
+{\color{red} The same is done with the linearized operator ${\cal L}_{{\bf U}}( {\bf u})$.}
+
+In the nonlinear r{\color{red}e}gime, the {\em base flow} introduced in the linear theory is not directly accessible and no longer relevant, especially when the oscillation amplitudes become large. 
+Instead, {\color{red} we taken the Reynolds decomposition ${\bf u}={\bf u}_m({\bf x})+{\bf u}'({\bf x},t)$, with ${\bf u}'$ the nonlinear perturbation and ${\bf u}_m$ the {\em mean flow} defined as the time-average  of the flow:}
 \be{defumean}
-{\bf u}_m({\bf x})  = \frac{1}{T} \int_0^{T}  {\bf u}({\bf x},t)  dt
+{\bf u}_m({\bf x})  = \frac{1}{T} \int_0^{T}  {\bf u}({\bf x},t)  dt,
 \ee
@@
 
-A convenient measure of the unsteady part of the flow, which has been adopted in both the WNL and SC models, is the energy-amplitude, defined as the square-root of the total energy associated to the fluctuating part of the velocity field :
-
+A convenient measure of the unsteady part of the flow, which has been adopted in both the WNL and SC models, is the energy-amplitude, defined as the square-root of the total energy associated to the fluctuating part of the velocity field:
 \be{defAnergy}
-A_E = \sqrt{\frac{1}{T} \int_0^{T} \left( \int_\Omega | {\bf u} - {\bf u}_m |^2 \, dS \right) dt}
+A_E = \sqrt{\frac{1}{T} \int_0^{T} \left( \int_\Omega | {\bf u} - {\bf u}_m |^2 \, dS \right) dt}.
 \ee
@@
 Another quantity which has been particularly addressed in previous studies is the mean recirculation length $L_x$
-already discussed introduced and documented in figure ??.
-In the nonlinear regime, the recirculation bubble becomes unsteady so it is difficult to define properly an instantaneous recirculation length.
+already discussed{\color{red},} introduced and {\color{red}documented in figure \ref{fig:LxandDrag}}.
+{\color{red} However, in a} nonlinear regime, the recirculation bubble becomes unsteady, {\color{red} becoming} difficult to define properly an instantaneous recirculation length.
 It is still possible to define a mean recirculation length associated to the mean flow.
+%On va le faire ??
 
 In the next sections we will document the predictions of the WNL and SC models regarding the quantities $A_E$ and $L_x$ adopted in past studies.
-In addition, we will document two other quantities of practical interest : the drag and Lift forces $F_x$ and $F_y$ exerted on the cylinder.
-Both are periodic functions of time, and owing to symmetry consideration, the drag contains only even harmonics and the lift only odd harmonics :
-$$
-F_x  = F_{x,0}  + \Sigma \left(  F_{x,2n,c} \cos 2 n \omega t + F_{x,2n,s} \sin 2 n  \omega t \right)
-$$
-$$
-F_y  =  \Sigma \left(  F_{y,{2n+1},c} \cos (2n+1) \omega t + F_{y,(2n+1),s} \sin (2n+1) \omega t \right)
-$$
-
-In the sequel we will focus on the {\em mean drag}
- $F_{x,0}$ and the part of the fundamental frequency part of the lift  given by $F_{y,1,c}$ and $F_{y,1,s}$.
+In addition, we will document two other quantities of practical interest : the Drag and Lift forces $F_x$ and $F_y$ exerted on the cylinder.
+Both are periodic functions of time and{\color{red},} owing to symmetry consideration, the drag contains only even harmonics and the lift only odd harmonics:{\color{red}
+%\be{drag_lift_def}
+%\begin{cases}
+%F_x=F_{x,0} + \sum_{n=1}^\infty \big( F_{x,2n,c} \cos ( 2 n \omega t) + F_{x,2n,s} \sin( 2 n  \omega t ) \big) \\
+%\begin{split}
+%F_y  =  \sum_{n=1}^\infty \big(  F_{y,{2n-1},c} \cos ((2n-1) \omega t ) +\\
+% F_{y,(2n-1),s} \sin ((2n-1) \omega t) \big)
+%\end{split}
+%\end{cases}.
+%\ee
+\begin{align}
+F_x &=F_{x,0} + \sum_{n=1}^\infty \big( F_{x,2n,c} \cos ( 2 n \omega t) + F_{x,2n,s} \sin( 2 n  \omega t ) \big),
+\\
+\begin{split}
+F_y  & =\sum_{n=1}^\infty \big( F_{y,{2n-1},c} \cos ((2n-1) \omega t )\\
+             &\qquad + F_{y,(2n-1),s}  \sin ((2n-1) \omega t) \big).
+\end{split}
+\label{drag_lift_def}
+\end{align}
+
+In the sequel we will focus on the {\em mean drag}  $F_{x,0}$ and on the fundamental frequency part of the lift given by $F_{y,1,c}$ and $F_{y,1,s}$.
+ }
 
@@
 \paragraph{Weakly nonlinear model}
-
+%REFAIRE
+\iffalse
 \begin{figure*}
@@
 end
-
 \end{lstlisting}
@@
 \end{figure*}
+\fi
+\begin{figure*}
+\small
+\begin{lstlisting}
+[bf,em]=SF_FindThreshold(bf,em); Omegac=imag(em.lambda);
+[ev,em] = SF_Stability(bf,'shift',1i*Omegac,'nev',1,'type','S'); 
+[wnl,meanflow,mode] = SF_WNL(bf,em,'Retest',47.,'Normalization','L');
+
+Re_HB = [Rec 47.5 48 49 50 55 60 65 70 75 80 85 90 95 100];
+omega_HB = [Omegac]; Aenergy_HB = [0];
+
+bf=SF_BaseFlow(bf,47.5);
+[ev,em] = SF_Stability(bf,'shift',Omegac*i);
+Astart = sqrt(wnl.Lambda/(wnl.Nu0+wnl.Nu2)*(1/Rec-1/47.5));
+[meanflow,mode] = SF_HarmonicBalance(bf,em,'sigma',0.,'Re',47.5,'Aguess',Astart);
+
+for Re = Re_HB(2:end)
+    [meanflow,mode] = SF_HarmonicBalance(meanflow,mode,'Re',Re);
+    omega_HB = [omega_HB imag(mode.lambda)];
+    Aenergy_HB  = [Aenergy_HB mode.Energy];
+end
+\end{lstlisting}
+\normalsize
+\caption{Illustration of the procedure for nonlinear calculations using StabFem (from script {\color{red}{\em SCRIPT\_CYLINDER\_NONLINEAR.m})}. }
+\label{fig:listingNL}
+\end{figure*}
 
@@
 Lebedev\cite{SippLebedev}, also discussed by Gallaire et al. \cite{FDR2016}. 
-The derivation is based on a multiple scale  decomposition based on the parameter $\epsilon^2 = 1/Re - 1/Re_c$. 
-In the case where we are interested only in the desciption of the saturation cycle, the starting point can be taken as the following expansion of the state-vector ${\bf{q}}=({\bf{u}},p)$ defining the flow :
-
-\begin{eqnarray}
-{\bf q} &=& {\bf q}_{bc} + \epsilon \left[ A_{wnl}  \hat{\bf q} e^{i (\omega_c+\epsilon \omega_\epsilon)  t} + c.c. \right] \label{WNL1}\\
-&+& \epsilon^2 \left[ {\bf q}_\epsilon + |A_{wnl}|^2  {\bf q}_{2,0} + \left(  A_{wnl}^2 {\bf q}_{2,2} e^{2 i(\omega_c+\epsilon \omega_\epsilon)  t} + c.c. \right) \right] + {\cal O}( \epsilon ^3)
-\nonumber
-\label{eq:WNLdevelopment}
-\end{eqnarray}
-where ${\bf q}_{bc}$ is the base flow at the threshold $Re_c$, $\hat{\bf q}$ the neutral 
-eigenmode at $Re_c$, $A_{wnl}$, an amplitude, $\omega_c$ the frequency predicted by the linear approach at $Re=Re_c$ and $\omega_\epsilon$ a small deviation of the frequency.
-
-Note that this starting point is slightly different from the original approach of \cite{SippLebedev} who used a multiple scale method and assumed a dependence of the amplitude $A_{wnl}$ as function of a slow time-scale $\tau = \epsilon t$.
-This latter starting point is the righth way to parametrize the problem if one wants to obtain an amplitude equation, but as specified above our goal here is to provide a simpler formulation descibing only the saturated cycle.
-
-Details of the approach are given in the appendix. The outcome is a relationship with the form
-
+The derivation is based on a multiple scale  decomposition based on the parameter {\color{red}$\epsilon^2 = 1/Re_c - 1/Re$}. 
+In the case where we are interested only in the {\color{red}description} of the saturation cycle, the starting point can be taken as the following expansion of %the state-vector ${\bf{q}}=({\bf{u}},p)$ defining the flow:
+ {\color{red}the velocity flow field:} 
+ {\color{red}
+\be{WNL1}
+\begin{aligned}
+&{\bf u} = {}  {\bf u}_{bc} + \epsilon \left[ A_{wnl}  \hat{\bf u} e^{i (\omega_c+\epsilon^{\color{red}2} \omega_\epsilon)  t} + c.c. \right]\\
+&+ \epsilon^2 \left[ {\bf u}_\epsilon + |A_{wnl}|^2  {\bf u}_{2,0} + \left(  A_{wnl}^2 {\bf u}_{2,2} e^{2 i(\omega_c+\epsilon^{\color{red}2} \omega_\epsilon)  t} + c.c. \right) \right]\\
+& + {\cal O}( \epsilon ^3),
+\end{aligned}
+\ee
+}
+where {\color{red}${\bf u}_{bc}$} is the base flow at the threshold $Re_c$, {\color{red} $\hat{\bf u}$} the neutral 
+eigenmode at $Re_c$, {\color{red} $A_{wnl}$ an amplitude,} $\omega_c$ the frequency predicted by the linear approach at $Re=Re_c$ and $\omega_\epsilon$ a small deviation of the frequency, {\color{red} ${\bf u}_{\epsilon}$ the base flow modifications related to the increase of $\epsilon$, ${\bf u}_{2,0}$ the flow response to the steady nonlinear interactions of $\hat{\bf u}$ with its conjugate, ${\bf u}_{2,2}$ the flow response to the unsteady nonlinear interactions of $\hat{\bf u}$ with itself and  ${\cal O}( \epsilon ^3)$ the third order terms.
+}
+
+Note that this starting point is slightly different from the original approach of \cite{SippLebedev} who used a multiple scale method and assumed a dependence of the amplitude $A_{wnl}$ as function of a slow time-scale $\tau = {\color{red}\epsilon^2} t$.
+This latter starting point is the {\color{red}right} way to parametrize the problem if one wants to obtain an amplitude equation, but{\color{red},} as specified above{\color{red},} our goal here is to provide a simpler formulation {\color{red}describing} only the saturated cycle.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%DETAILS IN APPENDIX
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+{\color{red}
+The expansion \ref{WNL1} can be introduced into the Navier-Stokes equations \ref{NSprimitive}.
+Details at the different $\epsilon^i$ orders are given in the appendix}.
+The outcome is a relationship with the form
 \be{WNL3}
@@
 \ee
-
-Where coefficients $\Lambda$, $\nu_0$ and $\nu_2$ are given by eqs. (???)
-
-If one is interested in the amplitude of the limit cycle, we have 
-$|A_{wnl}| = \sqrt{\Lambda_r/(\nu_{0,r}+\nu_{2,r})}$.
-
-% and eventually, reintroducing the scaling :
-%\be{ANL} 
-%|A| =  \epsilon |A_{wnl}| = \frac{\Lambda_r}{\nu_{0,r}+\nu_{2,r} } \sqrt{\frac{1}{Re_c}-\frac{1}{Re}}.
-%\ee
-
-The frequency of the limit cycle is given by
+where the coefficients $\Lambda$, $\nu_0$ and $\nu_2$ are given by {\color{red}equations \ref{LAMBDA}, \ref{NU0} and \ref{NU2}, respectively.
+
+We note that $\Lambda$ does not depend on the normalization choice of the eigenmode, discussed later, while $\nu_0$ and $\nu_2$ depend.
+Hence, if one is interested in the amplitude of the limit cycle, the latter will depend on it and will be given by $|A_{wnl}| = \sqrt{\Lambda_r/(\nu_{0,r}+\nu_{2,r})}$.
+
+Reintroducing the scaling
+\be{ANL} 
+|A| =  \epsilon |A_{wnl}| =\sqrt{ \frac{\Lambda_r}{\nu_{0,r}+\nu_{2,r} }} \sqrt{\frac{1}{Re_c}-\frac{1}{Re}},
+\ee
+the frequency of the limit cycle is given by
 \be{omegaWNL} 
-\omega_\epsilon =  - \Lambda_i \frac{\nu_{0,i}+\nu_{2,i} }{\nu_{0,r}+\nu_{2,r} } 
-\ee
-
-THE MEAN FLOW IS GIVEN BY :
-
-AND THE ASSOCIATED DRAG FORCE IS GIVEN BY :
+\omega_{LC}=\omega_c+ \epsilon^2\Lambda_i- (\nu_{0,i}+\nu_{2,i})|A|^2,
+\ee
+
+where the subscripts $r$ and $i$ represent the real and imaginary parts.
+}
+{\color{red}
+Recasting equation \ref{WNL1} in the {\em mean flow} definition \ref{defumean}, we obtain
+\be{mean_flow_WNL}
+{\bf u}_m({\bf x })= {\bf u}_{bc}+\epsilon^2 {\bf u}_\epsilon + |A|^2{\bf u}_{2,0},
+\ee
+where the first two terms give the base flow approximation at the $Re$ prescribed by $\epsilon$. }
+
+{\color{red} Finally, the associated Drag and Lift are given respectively by:
+\be{drag_cos}
+\begin{aligned}
+F_{x,WNL} = F_{x}({\bf u}_{bc})&+\epsilon^2 \big( 
+F_{x}({\bf u}_{\epsilon})- 2\mathsf{D}({\bf u}_{bc}).{\bf n}_x \big)\\
+&+|A|^2 F_{x}({\bf u}_{2,0})\\
+&+2|A|^2\big(F_{x,r}({\bf u}_{2,2})\cos(2\omega t)
+-F_{x,i}({\bf u}_{2,2})\sin(2\omega t) \big),
+\end{aligned}
+\ee
+\be{lift_cos}
+\begin{aligned}
+F_{y,WNL} =2\big(|A|_r F_{x,r}({\bf \hat{u}})\cos(\omega t)-
+|A|_i F_{x,i}({\bf \hat{u}})\sin(\omega t) \big),\\
+\end{aligned}
+\ee
+where $F_{x}$ and $F_{y}$ are given by \ref{drag} and \ref{lift} (with the associated pressure field implicit), respectively .
+All terms in these equations can be matched with the interesting ones in \ref{drag_lift_def}: $F_{x,0}$ is the first 4 terms of \ref{drag_cos}; $F_{x,2,c}$, $F_{x,2,s}$ are the fifth and sixth terms of \ref{drag_cos}; $F_{y,1,c}$, $F_{y,1,s}$ are the first and second terms of \ref{lift_cos}.
+We note that the \textit{sin} term is associated to the phase of the forces in a physical way.
+}
+
+\iffalse
+\begin{eqnarray}
+\begin{aligned}
+F_{x,WNL} = F_{x}({\bf q}_{bc})&+\epsilon^2 \big( 
+F_{x}({\bf q}_{\epsilon})- 2\mathsf{D}({\bf u}_{bc}) \big)\\
+&+F_{x}({\bf q}_{2,0})|A|^2\\
+&+2F_{x,r}({\bf q}_{2,2}\cos(2\omega t)+
+2F_{x,i}({\bf q}_{2,2}\sin(2\omega t)
+),\\
+\end{aligned}\\
+F_{y,WNL} = |A|^2 \big[ F_{y}({\bf \hat{q}})e^{i\omega_{LC} t} +c.c. \big],
+\end{eqnarray}
+\fi
 
 {\color{blue}
-A key issue in the weakly nonlinear expansion is that the definition of the amplitude depends upon a normalization choice 
-of the eigenmodes. Several choices are possible. In the litterature three possibilities have been used :
+A key issue in the weakly nonlinear expansion is that the definition of the amplitude depends upon a normalization choice of the eigenmodes{\color{red}, as pointed before}.
+Several choices are possible.
+In the literature three possibilities have been used:
 \begin{itemize}
-\item First, \cite{SippLebedev} normalized the eigenmode by assuming a specified value to the $y$-component of the velocity at one point, namely :
+\item First, \cite{SippLebedev} normalized the eigenmode by assuming a specified value to the $y$-component of the velocity at one point, namely:
 \be{normsipp}
-\hat{u_y}(1,0) = 0.4612
-\ee
-The advantage of this choice is that the amplitude is then a measure of the energy of the perturbation: 
-$\epsilon A_{wnl} \approx A_E$.
-
-\item Secondly, \cite{FDR2016} proposed the following normalisation choice :
+{\color{red}\hat{u}}_y(1,0) = 0.4612.
+\ee
+The advantage of this choice is that the amplitude ${\color{red}|A|}$ is then a measure of the energy of the perturbation: 
+${\color{red}|A|} \approx A_E$. {\color{red}However the lift phase its not fixed.}
+
+\item Secondly, \cite{FDR2016} proposed the following {\color{red}normalization} choice:
 \be{normFDR}
-\int_\Omega |\hat{\bf u}|^2 d {\bf x}  = \frac{1}{2}
-\ee
-This directly leads to $\epsilon A_{wnl} = A_E$.
+\int_\Omega |\hat{\bf u}|^2 d {\bf x}  = \frac{1}{2}.
+\ee
+This directly leads to ${\color{red}|A|} = A_E$. {\color{red} The lift phase is not specified in \cite{FDR2016} and can be set to nil before the normalization.}
 
 \item Thirdly, following \cite{Fabre2012}, another convenient choice is to normalize the eigenmode with its lift 
-force : 
+force: 
 \be{normfabre}
-L(\hat{\bf u};\hat{p}) = 1/2
-\ee
-The advantage of this choice is that the amplitude $\epsilon A_{wnl}$ is directly related to the fundamental lift :
-$
+{\color{red}F_y(\hat{\bf u}) }={\color{red} \frac{1}{2}}.
+\ee
+The advantage of this choice is that the amplitude ${\color{red}|A|}$ is directly related to the fundamental lift:
+\be{lift_explanation}
 F_{y,1,c} 
-%= \epsilon A \left( 1/2 e^{i \omega t} + c.c. \right)
-=   \epsilon A \cos (\omega t) ; \quad F_{y,1,c} = 0. 
-$
+= {\color{red}|A|} \left( {\color{red}\frac{1}{2}} e^{i \omega t} + c.c. \right)
+=   {\color{red}|A|} \cos (\omega t) ; \quad F_{y,1,{\color{red}s}} = 0. 
+\ee
 
@@
 
-In our implementation of the WNL approach, we allowed to choose the normalization convention. 
-In table (??) we give the predictions of the WNL approach using the three normalization choices.
-We can note that the coefficients $\nu_0$ and $\nu_2$ strongly depend on the normalization choice.
-on the other hand, the frequency deviation as well as the drag and lift coefficients are independent of it.
-
-\begin{table}
-$$\begin{array}{cc}
-a&b
-\end{array}$$
-\caption{Coefficients of the weakly nonlinear coefficients : }
-\end{table}
-
-Figure \ref{fig:listingNL}, which is extracted from the script 
-\verb|SCRIPT_CYLINDER_DEMO.m|, illustrate the sequence of commands to 
+Figure \ref{fig:listingNL}, which is extracted from the script {\color{red}
+\verb|SCRIPT_CYLINDER_NONLINEAR.m|}, illustrate the sequence of commands to 
 perform the weakly nonlinear study for the cylinder wake.
-On line 1, we first determine the instability threshold, and the corresponding base flow 
-and eigenmode\footnote{This routine uses Newton iteration to directly compute the 
-base flow, the eigenmode, the frequency and the critical Reynolds. The algorithm is 
-very similar to the one presented for the HB, with an additional unknown (Re) and an 
-additional constraint (normalization of the mode). The interested reader should 
-reconstruct easily the whole procedure from the code provided.}.
-On line 2, we then compute all the terms and coefficients of the WNL model. 
+On line 1, we first determine the instability threshold, and the corresponding base flow and eigenmode
+\footnote{This routine uses Newton iteration to directly compute the base flow, the eigenmode, the frequency and the critical Reynolds.
+The algorithm is very similar to the one presented for the HB, with an additional unknown (Re) and an additional constraint (normalization of the mode).
+The interested reader should reconstruct easily the whole procedure from the code provided.}.
+{\color{red} On line 2 we solve the adjoint problem required for some terms in the WNL formulation.}
+On line 3, we then compute all the terms and coefficients of the WNL model.
+{\color{red}The other lines are explained latter.} 
 %After that, 
@@
 
-As can be seen on figure \ref{fig:Comp2},  the approach gives good prediction in the immediate vicinity of $Re_c$, but deviation appears very rapidly and disagreement is already large at $Re=48$ (although, as discussed by Gallaire et al.?
+{\color{red}
+In our implementation of the WNL approach, we allowed to choose the normalization convention, as seen in line 3 of figure \ref{fig:listingNL}.
+%%ATTENTION, si figure est actualisé, il faut actualiser la ligne
+In table \ref{tab:WNL_coefs} we give the predictions of the WNL approach using the three normalization choices.
+We can note that the coefficients $\nu_0$ and $\nu_2$ strongly depend on the normalization choice.
+On the other hand, the frequency deviation $\omega_\epsilon$ and the $\lambda$ coefficient, as well as the drag and lift coefficients are independent of it.
+%On the other hand, the frequency deviation as well as the drag and lift coefficients are independent of it.
+}
+\begin{table*}[!h]
+\centering
+$$
+\begin{array}{|c||c|c|c|c|c|c|c|}
+\hline
+\mbox{Norm.} & \lambda & \nu_{0} & \nu_{2} &\omega_{\epsilon}(rad/s)&F_{x,0}&|F_{x,2}|&|F_{y,1}|\\%& F_{y,1}
+\hline
+\mbox{\cite{SippLebedev}} & 9.10988 & 9.3996-32.0289i & -0.305116-0.866118i & 36.2307
+&0.709469&0.0324441\epsilon^2&0.537254\epsilon\\
+\mbox{\cite{FDR2016}} & +  & 4.88701\times 10^{-4}-1.66524\times 10^{-3}i & -1.58635\times 10^{-5}-4.50309\times 10^{-5}i &36.2307&
++&0.0324441\epsilon^2&0.537254\epsilon \\
+\mbox{\cite{Fabre2012}} & 3.28004i & 32.62-111.152i & -1.05886-3.00574i & 36.2307
+&5.2524\epsilon^2&0.0324441\epsilon^2&0.537254\epsilon\\
+\hline
+\end{array}
+$$
+\caption{Coefficients of the weakly nonlinear approach {\color{red} NB for D.Fabre: Columns 2 and 6 have the same value.}}
+\label{tab:WNL_coefs}
+\end{table*}
+
+{\color{red} 
+The forces coefficients given by $F_x({\bf u})$ and $F_y({\bf u})$ are then converted in a more traditional form, $C_x=2F_x({\bf u})$ and $C_y=2F_y({\bf u})$.
+}
+As can be seen on figure \ref{fig:HB_SC_DATA_COMP},  the approach gives good prediction in the immediate vicinity of $Re_c$, but deviation appears very rapidly and disagreement is already large at $Re=48$ (although, as discussed by Gallaire et al.?
 and also observed by Tchoufag et al.
 \cite{Tchoufag2015}, a convenient definition of the $\epsilon$ improves the results).
+{\color{red} These aspects are justified by the pertubative nature of the WNL approach.
+The description of the limit cycle can be extended to larger $Re$ with the approach presented next.
+}
 
@@
 \end{center}
-\caption{Comparison between the weakly nonlinear results (WNL) and the harmonic 
-balance data (HB). We report also the Strouhal number computed by using the 
-classical linear stability theory (Linear) and the base flow (BF) $C_x$.
+\caption{Comparison between the weakly nonlinear results (WNL) and the harmonic balance data (HB).
+We report also the Strouhal number computed by using the classical {\color{red} linear stability theory (Linear) (see figure \ref{fig:SigmaOmega})} and the base flow (BF) $C_x$.
 %c_x should be consistent with the drag definition given at beginning
 }
-\label{fig:Comp2}
+\label{fig:HB_SC_DATA_COMP}
 \end{figure}
 
-\paragraph{Self-Consistent approach}
-
-TO BE SHORTENED
+\paragraph{ {\color{red} Self-Consistent model}}
 
@@
 
-We now briefly review the self-consistent approach as introduced by Manti\v{c}-Lugo et 
+We now briefly review the self-consistent {\color{red} model} as introduced by Manti\v{c}-Lugo et 
 al \cite{MLugo2014}. The authors adopted a pseudo-eigenmode expansion of the flow 
@@
 \be{SC}
-{\bf u } = {\bf u }_m + A_{sc} \left[ \tilde{{\bf u }}_1 e^{\sigma_{sc} t + i \omega_{sc} t} +   \tilde{\bf u }_{-1} e^{\sigma_{sc} t  -i \omega_{sc} t} \right],
-\ee  
-where ${\bf u }_m$ is the {\em mean flow} defined by phase-averaging over the cycle, $\tilde{{\bf u }}_1$ is a pseudo-eigenvector which is normalized by the condition  $||\tilde{{\bf u }}_1|| = 1/\sqrt{2}$,
+{\bf u } = {\bf u }_m + A_{sc} \left[ \tilde{{\bf u }}_1 e^{\sigma_{sc} t + i \omega_{sc} t} +   {\color{red} \overline{\tilde{\bf u }_1}} e^{\sigma_{sc} t  -i \omega_{sc} t} \right],
+\ee  
+where ${\bf u }_m$ is the {\em mean flow} defined by phase-averaging over the cycle, $\tilde{{\bf u }}_1$ is a pseudo-eigenvector which is normalized by the condition  $||\tilde{{\bf u }}_1|| = 1/\sqrt{2}$, {\color{red}$\overline{\tilde{{\bf u }}_1}$ is its complex conjugate,}
 $A_{sc}$ is an amplitude parameter directly related to the energy of the oscillating flow, and $\lambda_{sc} = \sigma_{sc} + i \omega_{sc}$ is a pseudo-eigenvalue which depends upon the parameter $A_{sc}$.
@@
 \begin{eqnarray}
-{\cal NS}(  {\bf u }_m ) - A_{sc}^2 {\cal C}( \tilde{{\bf u }}, \overline{\tilde{\bf u }}) = 0, 
+{\cal NS}(  {\bf u }_m ) - A_{sc}^2 {\cal C}{\color{red}( \tilde{{\bf u }}_1, \overline{\tilde{\bf u }_1})} = 0, 
 \label{sis1}
 \\
-(\sigma_{sc} + i \omega_{sc}) \tilde{{\bf u }} =  {\cal L}_{{\bf u }_m}(  \tilde{{\bf u }} ).
+(\sigma_{sc} + i \omega_{sc}) {\color{red}\tilde{{\bf u }}_1} =  {\cal L}_{{\bf u }_m}( {\color{red} \tilde{{\bf u }}_1} ).
 \label{sis2}
@@
 Equation (\ref{sis1}) provides the mean flow field ${\bf u }_m$ while the 
-pseudo-eigenpairs $(\lambda_{sc}, \tilde{{\bf u }})$ can be computed by solving the eigenvalue problem (\ref{sis2}).
+pseudo-eigenpairs $(\lambda_{sc},{\color{red}  \tilde{{\bf u }}_1})$ can be computed by solving the eigenvalue problem (\ref{sis2}).
 %The computed mode is normalized as $ || \tilde{{\bf u }}|| = 1/{\sqrt{2}}$
@@
 
-The self-consistent model has the following properties :
+The self-consistent model has the following properties:
 \begin{itemize}
@@
 
-Figure \ref{fig:SC100} shows the results of the self-consistent model at Re=100.
-
-\paragraph{Harmonic balance : equations and procedure }
-
-TO BE SIMPLIFIED...
+%Figure \ref{fig:SC100} shows the results of the self-consistent model at Re=100.
+
+\paragraph{{\color{red}First Order Harmonic balance: equations and procedure} }
 
@@
 rear stagnation point) for different Reynolds number. Comparison between the base flow bubble and the mean flow bubble computed by using the harmonic balance.}
-\label{fig:Comp1}
+\label{fig:recirculation_lengh}
 \end{figure}
+
 As discussed above, the Self-Consistent model was initially presented by the authors as a rational way to explain the dynamics in terms of a stability analysis of the {\em mean flow}.
@@
 If one is only interested by the properties of the limit cycle and not the transient, the model is actually equivalent to a Fourier series, and amenable to a more direct resolution method. 
-We thus start with a Fourier decomposition of the limit cycle under the form :
+We thus start with a Fourier decomposition of the limit cycle under the form:
 \be{HB}
-{\bf u } = {\bf u }_m + {\bf u }_{1,c} \cos( \omega t ) +   {\bf u }_{1,s} \sin( \omega t )
-\ee
-
-The connection with the definition of Mantic-Lugo is as follows :
+{\bf u } = {\bf u }_m + {\bf u }_{1,c} \cos( \omega t ) +   {\bf u }_{1,s} \sin( \omega t ),
+\ee
+{\color{red} where ${\bf u }_1$ is the mode (Fourier component at the fundamental frequency) and $\omega$ is the (real) oscillation frequency of the limit cycle (which is not known a priori).}   
+The connection with the definition of {\color{red} Manti\v{c}-Lugo} is as follows :
 \be{HBtoSC}
-\left( {\bf u }_{1,c} - i {\bf u }_{1,s} \right) = 2 A_{sc} \tilde{{\bf u }}_1
-\ee
-
-Here ${\bf u }_0$ is the mean flow (averaged over time),  ${\bf u }_1$ is the mode
-(Fourier component at the fundamental frequency), ${\bf u }_{-1} = \overline{{\bf u }_1}$ is its complex conjugate, and $\omega$ is the (real) oscillation frequency of the limit cycle (which is not known a priori).
-Injecting this ansartz into the Navier-Stokes equations and taking the mean value and the first Fourier component leads to the following coupled equations :
-
-CHECK !!!
-
-\be{HBEq0}
-{\cal NS}(  {\bf u }_0 ) - \frac{{\cal C}( {\bf u }_{1,c}, {\bf u }_{1,c}) +{\cal C}( {\bf u }_{1,s}, {\bf u }_{1,s})}{2}  = 0,
-\ee
-\be{HBEq1}
- \omega {\bf u }_{1,s} =  {\cal L}_{{\bf u }_0}(  {\bf u }_{1,c} ).
-\ee
-
-\be{HBEq1b}
+\left( {\bf u }_{1,c} - i {\bf u }_{1,s} \right) = 2 A_{sc} \tilde{{\bf u }}_1.
+\ee  
+Injecting this ansartz into the Navier-Stokes equations and taking the mean value and the first Fourier component leads to the following coupled equations:
+\begin{subequations}\label{eq_principal}
+\begin{eqnarray}
+{\cal NS}(  {\color{red}{\bf u }_m }) = \frac{{\cal C}( {\bf u }_{1,c}, {\bf u }_{1,c}) +{\cal C}( {\bf u }_{1,s}, {\bf u }_{1,s})}{{\color{red}4}}, 
+\label{HBEq0}
+\\
+ \omega {\bf u }_{1,s} =  {\cal L}_{{\bf u }_0}(  {\bf u }_{1,c} ),
+\label{HBEq1}
+\\
  -\omega {\bf u }_{1,c} =  {\cal L}_{{\bf u }_0}(  {\bf u }_{1,s} ).
-\ee
-
-Note that contrary to the SC model, the ${\bf u }_1$ component is not normalized.
-The amplitude $A$ can easily be computed a posteriori as $A = \sqrt{2 ||{\bf u }_1||}$.
+\label{HBEq1b}
+\end{eqnarray}
+\end{subequations}
+
+Note {\color{red} that,} contrary to the SC model, the ${\bf u }_1$ component is not normalized.
+{\color{red}The amplitude $A_{HB}$ of the oscillation} can easily be computed a posteriori as ${\color{red}A_{HB}} = \sqrt{2 ||{\bf u }_1||}$.
 On the other hand, the Fourier description of the limit cycle is invariant with respect to the phase $\phi$ (i.e.
-the equations are unchanged when replacing $[ {\bf u }_1,  {\bf u }_{-1}] $ by  $[ {\bf u }_1 e^{i\varphi},  {\bf u }_{-1}  e^{-i\varphi}] $).
+the equations are unchanged when replacing ${\color{red} {\bf u }_1 }$ by  ${\color{red} {\bf u }_1 e^{i\phi}}$).
 To allow resolution we thus need an extra equation to fix this phase.
-Several choices are possible, but a convenient one is to set the lift associated with the imaginary part of ${\bf u }_1$ to lift.
+Several choices are possible, but a convenient one is to set the lift associated with the imaginary part of ${\bf u }_1$ to {\color{red}zero}.
 Physically, this means that the instant $t=0$ will correspond to a maximum of lift.
-This condition reads :
+This condition reads:
 \be{HBphase}
@@
 
-Mathematically, the system (\ref{HBEq0},\ref{HBEq1},\ref{HBphase}) for the unknown $[{\bf u }_0, {\bf u }_{1}, \omega]$ is well posed, and can be solved using a Newton iteration just as explained for the base flow in section 2.
-To allow resolution, we separate the mode into real and imaginary part, by writing ${\bf u }_1 = {\bf u }_{1,r} +  i {\bf u }_{1,i} $.
-We then assume that we know a 'guess' 
-$$
-[{\bf u }_0, {\bf u }_{1,r}, {\bf u }_{1,i}, \omega] = 
- [{\bf u }_0^g, {\bf u }_{1,r}^g, {\bf u }_{1,i}^g, \omega^g]
-+ [\delta {\bf u }_0, \delta {\bf u }_{1,r}, \delta {\bf u }_{1,i}, \delta \omega].
-$$
-
-Injecting and developing up to linear order leads to the following
-
-TO BE CORRECTED !
-
+Mathematically, the system (\ref{HBEq0},\ref{HBEq1},\ref{HBEq1b},\ref{HBphase}) for the unknown {\color{red}$[{\bf u }_m, {\bf u }_{1,c}, {\bf u }_{1,s}, \omega]$} is well posed, and can be solved using a Newton iteration just as explained for the base flow in section 2.
+%To allow resolution, we separate the mode into real and imaginary part, by writing ${\bf u }_1 = {\bf u }_{1,r} +  i {\bf u }_{1,i} $.
+We then assume that we know a {\color{red}``guess'':
+$$
+[{\bf u }_m, {\bf u }_{1,c}, {\bf u }_{1,s}, \omega] = 
+ [{\bf u }_m^g, {\bf u }_{1,c}^g, {\bf u }_{1,s}^g, \omega^g]
++ [\delta {\bf u }_m, \delta {\bf u }_{1,c}, \delta {\bf u }_{1,s}, \delta \omega].
+$$
+} Injecting and developing up to linear order leads to the following equations:{\color{red}
+\begin{subequations}\label{eq:harmonic_total}
+\begin{eqnarray}
+\begin{split}
+&{\cal NS}(  {\bf u }_m^g ) - \frac{1}{4} \big[ {\cal C}( {\bf u }_{1,c}^g,{\bf u }_{1,c}^g) +  {\cal C}( {\bf u }_{1,s}^g,{\bf u }_{1,s}^g) \big]+ {\cal L}_{{\bf u }_m^g}(\delta {\bf u }_m)
+\\
+&-\frac{1}{2} \big[ {\cal C}( {\bf u }_{1,c}^g,\delta {\bf u }_{1,c}) +  {\cal C}( {\bf u }_{1,s}^g,\delta {\bf u }_{1,s}) \big] = 0,
+\end{split}
+\label{HB_1}
+\\
+\begin{split}
+{\cal L}_{{\bf u }_m^g}( {\bf u }_{1,c}^g) - \omega^g {\bf u }_{1,s}^g& -  {\cal C}( \delta {\bf u }_{m}, {\bf u }_{1,c}^g)
+\\
+&+{\cal L}_{{\bf u }_m^g}( \delta {\bf u }_{1,c})  - \omega^g \delta {\bf u }_{1,s}  
+ - \delta \omega {\bf u }_{1,s}^g = 0 ,
+ \end{split}
+\label{HB_2}
+\\
+\begin{split}
+{\cal L}_{{\bf u }_m^g}({\bf u }_{1,s}^g) + \omega^g {\bf u }_{1,c}^g& -  {\cal C}( \delta {\bf u }_{m}, {\bf u }_{1,s}^g)
+\\
+&+{\cal L}_{{\bf u }_m^g}( \delta {\bf u }_{1,s}) + \omega^g \delta {\bf u }_{1,c} +  \delta \omega {\bf u }_{1,c}^g= 0 ,
+\end{split}
+\label{HB_3}
+\\
+\begin{split}
+ F_y({\bf u }_{1,s}^g) + F_y(\delta {\bf u }_{1,s}) = 0. \qquad \qquad \qquad \qquad \qquad \qquad \quad
+\end{split}
+\end{eqnarray}
+\end{subequations}
+}
+
+\iffalse
 \begin{equation}
@@
 \displaystyle
-& {\cal NS}(  {\bf u }_0^g ) - [ {\cal C}( {\bf u }_{1,r}^g,{\bf u }_{1,r}^g) +  {\cal C}( {\bf u }_{1,i}^g,{\bf u }_{1,i}^g) ]
+& {\cal NS}(  {\bf u }_m^g ) - [ {\cal C}( {\bf u }_{1,r}^g,{\bf u }_{1,r}^g) +  {\cal C}( {\bf u }_{1,i}^g,{\bf u }_{1,i}^g) ]
 \\
@@
 \end{equation}
-
-After discretization, this leads to a linear problem of the form $A X = Y$ where $X$ is the discretized version of the unknowns  $[\delta {\bf u }_0, \delta {\bf u }_{1,r}, \delta {\bf u }_{1,i}, \delta \omega]$, and $A$ is a matrix of dimension $3 N_{dof} +1$.
+\fi
+
+After discretization, this leads to a linear problem of the form $A X = Y$ where $X$ is the discretized version of the unknowns  $[\delta {\bf u }_m, \delta {\bf u }_{1,c}, \delta {\bf u }_{1,s}, \delta \omega]$, and $A$ is a matrix of dimension $3 N_{dof} +1${\color{red}, where $N_{dof}$ is the number of variables associated to ${\bf u}$ taken into account in \ref{HB}, i.e.
+3.}
 
@@
 
-As mentioned before, figure \ref{fig:Comp2} shows the comparison between the 
-weakly non linear approach and the harmonic balance data.  
-Figure \ref{fig:Comp1} compares the length of the cylinder bubble computed by using 
-the harmonic balance with the base flow length.
+As mentioned before, figure \ref{fig:HB_SC_DATA_COMP} shows the comparison between the weakly non linear approach and the harmonic balance data.  
+Figure \ref{fig:recirculation_lengh} compares the length of the cylinder bubble computed by using the harmonic balance with the base flow length.
 
@@
 
-\section*{Appendix A : details on mesh convergence}
+\section*{Appendix A: Details on mesh convergence}
 
@@
 \mathbf{M}_2 \mbox{(ref)} 	& 7974  	& 4.0772 & 0.64391 	& 0.04684. +  0.74511i 	& 2.6141  & 0.69338 	& 0.84383 & 0.12799 & 2.048   \\ 
-
 \mathbf{M}_5 [-20,40]x[0,20] 	& 7437	&  4.108 & 0.64987 	& 0.048368. +  0.74952i 	& 2  & 0.69957 	& 0.85015 & 0.13125 & 2.3638   \\ 
@@
 
-\section{detail of WNL approach}
-
-Substituting the above expansion (\ref{WNL1}) into the Navier-Stokes equations and grouping terms 
-multiplied by the same power of $\epsilon$, a hierarchy of equations is obtained.
-The order $\epsilon^2$ contains three terms respectively computed as the solutions of the following linear problems :
+\section*{{\color{red}Appendix B: }Details of the weakly nonlinear approach}
+
+Substituting the expansion \ref{WNL1} into the Navier-Stokes equations \ref{NSprimitive} and grouping terms multiplied by the same power of $\epsilon$, a hierarchy of equations is obtained.
+{\color{red} The order $\epsilon^0$ gives directly the base flow at $Re_c$.
+The order $\epsilon^1$ describes the linear perturbation behavior at a frequency $\omega_{WNL}=\omega_c+\epsilon\omega_\epsilon$ whose solution is computed as explained in the first part of this article.}
+The order $\epsilon^2$ contains three terms respectively computed as the solutions of the following linear problems:
 \begin{eqnarray}
-{\cal L}_{{\bf u}_{bc}} ({\bf u}_\epsilon) + 2 \nabla \cdot {\bf D}( \hat{\bf u}) &=&0,\\
+{\color{red} {\cal L}_{{\bf u}_{bc}} ({\bf u}_\epsilon) - 2 \nabla \cdot {\bf D}({\bf u}_{bc})} &=&0,\\
 {\cal L}_{{\bf u}_{bc}} ({\bf u}_{2,0}) &=& {\cal C}(\hat{\bf u},\overline{\hat{\bf u}}),\\
@@
 
-Finally, compatibility conditions are imposed at order $\epsilon^3$ lead to
-
-\be{WNL3}
-i \omega_\epsilon A_{wnl} = \Lambda A_{wnl} - (\nu_0+\nu_2)  |A_{wnl}|^2 A_{wnl},
-\ee
-
+Finally, compatibility conditions, {\color{red}given by the Fredholm's alternative, are imposed at order $\epsilon^3$ to remove the secular terms, leading to an amplitude equation, known as Stuart-Landau equation:
+\be{WNL3_2}
+\frac{\partial A_{wnl}}{\partial \tau} = \Lambda A_{wnl} - (\nu_0+\nu_2)  |A_{wnl}|^2 A_{wnl},
+\ee
+}
+where coefficients $\Lambda$, $\nu_0$ and $\nu_2$ are given by
+{\color{red}
 \begin{eqnarray}
-\Lambda &=& \frac{ \left< {\hat{\bf u}}^\dag, 
-\left( {\cal C}({\bf u}_\epsilon, \hat{\bf u}) - 2 \nabla \cdot  {\bf D}( \hat{\bf u}) \right) \right>}
-{  \left<  \hat{\bf u}^\dag,\hat{\bf u} \right> },\\
-\nu_0 &=& -\frac{ \left< {\hat{\bf u}}^\dag,  {\cal C}({\bf u}_{20}, \hat{\bf u} ) \right>}
-{  \left<  \hat{\bf u}^\dag,\hat{\bf u} \right> },\\
-\nu_2 &=& -\frac{ \left< {\hat{\bf u}}^\dag,  {\cal C}({\bf u}_{22}, \overline{\hat{\bf u}})  \right>}
-{  \left<  \hat{\bf u}^\dag,\hat{\bf u} \right> }.
+\Lambda &=& -\frac{ \left< {\hat{\bf u}}^\dag, 
+\left( {\cal C}({\bf u}_\epsilon, \hat{\bf u}) + 2 \nabla \cdot  {\bf D}( \hat{\bf u}) \right) \right>}
+{  \left<  \hat{\bf u}^\dag,\hat{\bf u} \right> },\label{LAMBDA}\\
+\nu_0 &=& \frac{ \left< {\hat{\bf u}}^\dag,  {\cal C}({\bf u}_{20}, \hat{\bf u} ) \right>}
+{  \left<  \hat{\bf u}^\dag,\hat{\bf u} \right> },\label{NU0}\\
+\nu_2 &=& \frac{ \left< {\hat{\bf u}}^\dag,  {\cal C}({\bf u}_{22}, \overline{\hat{\bf u}})  \right>}
+{  \left<  \hat{\bf u}^\dag,\hat{\bf u} \right> }.,\label{NU2}
  \end{eqnarray}
-
-\section{Detail of the weak formulation}
+}
+
+\section*{{\color{red}Appendix C: } Details of the weak formulation}
 %The problem can be set into weak form by multiplying by multiplying Eq.

### 2018-07-17 99_Documentation/MANUAL/04_General_view.tex

\chapter{General View of \ti{StabFem}}

\ti{StabFem} has a main directory where all the projects are located and where the mutual scripts are located too. The directory is composed by the following particular project directories:

\begin{enumerate}
\item ACOUSTICS\_PIPES;
\item CYLINDER;
\item CYLINDER\_VIV;
\item DISK\_IN\_PIPE.
\item etc...
\end{enumerate}
The mutual directories are the followings:

\begin{enumerate}
\item SOURCES\_FREEFEM;
\item SOURCES\_MATLAB;
\item Documentation.
\end{enumerate}

These directories are used by the several projects of \ti{StabFem}.

\medskip

\begin{leftbar}
Attention: When you do some change in the mutual directory files, we have to assure that it will work on all the projects.
\end{leftbar}
\section{General Features}

\begin{itemize}
\item With \ti{StabFem} we can solve forced problems, eigenvalue problems, etc...

\item  \ti{StabFem} allows us to save the scripts used to generate the different data and graphs, unabling to reproduce the same results (useful for repeat figures for articles, confirming results, etc...).
\end{itemize}

\section{What is attended from this manual document}
This document presents this first chapter describing what can be found in a  \ti{StabFem} project, a chapter describing the running logic of a \ti{StabFem} program and the main common files and a chapter for each project, describing succinctly their running features.

### 2018-07-17 99_Documentation/MANUAL/210_StabFem_LiquidBridges.tex

@@
 \begin{figure}
-\includegraphics[width=.8\linewidth]{../../CASES_STABLE/LiquidBridges/FIGURES/Bridges_NV_Eigenmodes_phi_cyl_L3_5.png}
+\includegraphics[width=.8\linewidth]{../LiquidBridges/FIGURES/Bridges_NV_Eigenmodes_phi_cyl_L3_5.png}
 \caption{Oscillation modes of a liquid bridge of aspect ratio $L/R=4$ and reduced volume $V^ =$...}
@@
 \begin{figure}
-\includegraphics[width=.45\linewidth]{../../CASES_STABLE/LiquidBridges/FIGURES/Bridges_NV_coal_omega.png}
-\includegraphics[width=.45\linewidth]{../../CASES_STABLE/LiquidBridges/FIGURES/Bridges_NV_coal_omega.png}
+\includegraphics[width=.45\linewidth]{../LiquidBridges/FIGURES/Bridges_NV_coal_omega.png}
+\includegraphics[width=.45\linewidth]{../LiquidBridges/FIGURES/Bridges_NV_coal_omega.png}
 \caption{Oscillation frequencies of a liquid bridge resulting from the coalescence of two spherical droplets

### 2018-07-18 99_Documentation/MANUAL/11_StabFem_BasicFunctionalities.tex

--- 2018-07-16 99_Documentation/11_StabFem_BasicFunctionalities.tex
@@
 \small
-\lstinputlisting{../EXAMPLE_Lshape/SCRIPT_Lshape.m}
+\lstinputlisting{../../CASES_STABLE/EXAMPLE_Lshape/SCRIPT_Lshape.m}
  \normalsize
@@
 \begin{figure*}[t]
-\includegraphics[width = .45 \linewidth]{../EXAMPLE_Lshape/FIGURES/Lshape_T0.png}
-\includegraphics[width = .45 \linewidth]{../EXAMPLE_Lshape/FIGURES/Lshape_T0_Cut.png}
+\includegraphics[width = .45 \linewidth]{../../CASES_STABLE/EXAMPLE_Lshape/FIGURES/Lshape_T0.png}
+\includegraphics[width = .45 \linewidth]{../../CASES_STABLE/EXAMPLE_Lshape/FIGURES/Lshape_T0_Cut.png}
 \caption{Solution for the steady hrat equation in a L-shape domain : $(a)$ Temperature field $T(x,y)$. 
@@
 \small
-\lstinputlisting{../EXAMPLE_Lshape/Lshape_Mesh.edp}
+\lstinputlisting{../../CASES_STABLE/EXAMPLE_Lshape/Lshape_Mesh.edp}
  \normalsize
@@
 \small
-\lstinputlisting{../EXAMPLE_Lshape/Lshape_Steady.edp}
+\lstinputlisting{../../CASES_STABLE/EXAMPLE_Lshape/Lshape_Steady.edp}
 \normalsize
@@
 Looking inside the file \keys{Data.ff2m}, the header (i.e.  first four lines) is as follows :
-\lstinputlisting[linerange={1-4}]{../EXAMPLE_Lshape/Data.ff2m}, 
+\lstinputlisting[linerange={1-4}]{../../CASES_STABLE/EXAMPLE_Lshape/Data.ff2m}, 
 meaning that this files contains a P1 mesh-organised field called 'T'.
@@
 The header of this file is as follows :
-\lstinputlisting[linerange={1-5}]{../EXAMPLE_Lshape/Heat_1Dcut.ff2m}, 
+\lstinputlisting[linerange={1-5}]{../../CASES_STABLE/EXAMPLE_Lshape/Heat_1Dcut.ff2m}, 
 meaning that this files contains two vectors of dimension 101 called X and T.
@@
 
-%\lstinputlisting[linerange={1-5}]{../EXAMPLE_Lshape/Heat_1Dcut.ff2m}
+%\lstinputlisting[linerange={1-5}]{../../CASES_STABLE/EXAMPLE_Lshape/Heat_1Dcut.ff2m}
 
-%\lstinputlisting{../EXAMPLE_Lshape/ExecutionExample}
+%\lstinputlisting{../../CASES_STABLE/EXAMPLE_Lshape/ExecutionExample}
 

### 2018-07-18 99_Documentation/MANUAL/211_StabFem_RotatingPolygons.tex

--- 2018-06-28 99_Documentation/211_StabFem_RotatingPolygons.tex
@@
 \begin{figure}
-\includegraphics[width=.8\linewidth]{../ROTATING_POLYGONS/FIGURES/POLYGONS_modes.png}
+\includegraphics[width=.8\linewidth]{../../CASES_STABLE/ROTATING_POLYGONS/FIGURES/POLYGONS_modes.png}
 \caption{Oscillation modes of a potential vortex for  $a=H/R=0.3$ and $m=3$ (figure 5, 6 of Mougel et al.).}
@@
 \begin{figure}
-\includegraphics[width=.45\linewidth]{../ROTATING_POLYGONS/FIGURES/POLYGONS_omega.png}
-\includegraphics[width=.45\linewidth]{../ROTATING_POLYGONS/FIGURES/POLYGONS_sigma.png}
+\includegraphics[width=.45\linewidth]{../../CASES_STABLE/ROTATING_POLYGONS/FIGURES/POLYGONS_omega.png}
+\includegraphics[width=.45\linewidth]{../../CASES_STABLE/ROTATING_POLYGONS/FIGURES/POLYGONS_sigma.png}
 \caption{Oscillation frequencies and amplification rates for f a potential vortex for $m=3$ (figure 4 of Mougel et al.).}

### 2018-07-19 CASES_DEVELOPMENT/BIRDCALL_Ercoftac/SCRIPT_BirdCall_WNL_Branch2.m
Redesign of Harmonic Balance : results are now stored in WORK/MEANFLOWS

@@ -1,14 +1,13 @@
 
+%% First we compute a piece of the linear branch
 
 guess2 = -0.0229848+5.39569i
-
-
-
-Re_Range = [400 408 409 410 420 430 440 450];
+Re_Range = [390 400 404 405 410 420 430 440 450];
   
  %if(exist('DP0_Branch')==0)% to save time if already computed
      DP0_Branch = [];
-     EVW = [];  
+     EVW = []; 
+     bf=SF_BaseFlow(bf,'Re',Re_Range(1));
     [ev,em] = SF_Stability(bf,'m',0,'shift',guess2,'nev',1);
     for Re = Re_Range
         bf=SF_BaseFlow(bf,'Re',Re);
@@ -19,39 +18,34 @@ Re_Range = [400 408 409 410 420 430 440 450];
     end
  %end
  
- figure(3);
+    figure(3);
     plot(Re_Range,DP0_Branch);
     title('Pressure drop across the whistle as function of Re');
-    
-
-%    if(exist('EV2')==0)
-%        EV2 = SF_Stability_LoopRe(bf,Re_Range,0,guess2,1,'Branch2.dat');
-%    end
-
-    
+     
     figure(4);
     subplot(2,1,1);
-    plot(Re_Range,real(EV2),'-*b');%,Re_Range,real(EV1),'-*g')
+    plot(Re_Range,real(EVW),'-*b');%,Re_Range,real(EV1),'-*g')
     title('growth rate Re(sigma) vs. Reynolds ; mode 1 (red) and mode 2 (blue)')
     subplot(2,1,2);
-    plot(Re_Range,imag(EV2)/(2*pi),'-*b');%,Re_Range,imag(EV3)/(2*pi),'-*g')%,Re_Range,imag(EVI),'-*r')
+    plot(Re_Range,imag(EVW)/(2*pi),'-*b');%,Re_Range,imag(EV3)/(2*pi),'-*g')%,Re_Range,imag(EVI),'-*r')
     title('Strouhal vs. Reynolds');
     
     
 
 pause(0.1);
 
-%%% WEAKLY NONLINEAR ANALYSIS AT THE THRESHOLD
+%% WEAKLY NONLINEAR ANALYSIS AT THE THRESHOLD
 
 
-Rec = 408.56;
+Rec = 404.26;
+omegac = 5.39;
 bf = SF_BaseFlow(bf,'Re',Rec)
 
[…]

### 2018-07-19 CASES_STABLE/CYLINDER/HB2_LoopRe.m

@@ -1,0 +1,30 @@
+
+function HB2res = HB2_LoopRe(bfT,emT,Re_TAB)
+
+Rec = bfT.Re;  Fxc = bfT.Fx; 
+Lxc=bfT.Lx;    Omegac=imag(emT.lambda);
+
+Res = Re_TAB(2);
+[wnl,meanflow,mode,mode2] = SF_WNL(bfT,emT,'Retest',Res); % Here to generate a starting point 
+
+HB2res.Re = Re_TAB;
+HB2res.Lx = [Lxc]; HB2res.Fx0 = [Fxc]; HB2res.omega = [Omegac]; HB2res.Aenergy  = [0]; HB2res.Fy = [0];HB2res.Fx2 = [0];
+
+for Re = HB2res.Re(2:end)
+    if(meanflow.iter>=0)
+        [meanflow,mode,mode2] = SF_HB2(meanflow,mode,mode2,'Re',Re);
+        HB2res.Lx = [HB2res.Lx meanflow.Lx];
+        HB2res.Fx0 = [HB2res.Fx0 meanflow.Fx];
+        HB2res.omega = [HB2res.omega imag(mode.lambda)];
+        HB2res.Aenergy  = [HB2res.Aenergy sqrt(mode.AEnergy^2+ mode2.AEnergy^2)];
+        HB2res.Fy = [HB2res.Fy mode.Fy];
+        HB2res.Fx2 = [HB2res.Fx2 mode2.Fx];
+    else
+        disp(['####### Loop HB2 : divergenge at Re = ',num2str(Re)]);
+        break;
+    end
+end
+
+HB2res.Re = HB2res.Re(1:length(HB2res.Lx)); % truncate if the computation has failed at some point
+
+end% Function HB2LoopRe

### 2018-07-19 CASES_STABLE/CYLINDER/SCRIPT_CYLINDER_HB.m

@@ -1,3 +1,4 @@
+
 %  Instability of the wake of a cylinder with STABFEM  
 %
 %  this script demonstrates the way to perform HARMONIC BALANCE
@@ -7,154 +8,127 @@
 %% ##### CHAPTER 1 : COMPUTING THE MESH WITH ADAPTMESH PROCEDURE
 run('../../SOURCES_MATLAB/SF_Start.m');verbosity=10;
 figureformat='png'; AspectRatio = 0.56; % for figures
+mkdir('RESULTS');
 
-type = 'D';
-bf = SmartMesh_Cylinder(type); 
+type = 'S';
+if(exist('WORK/mesh.msh')==1)
+    bf = SmartMesh_Cylinder(type); 
     % here use 'S' for mesh M2 (converged results for all quantities except for A_E , but much faster
     % or 'D' for mesh M4 (converged results for all quantities, but much
     % slower)
+else
+    ffmesh = importFFmesh('WORK/mesh.msh');
+    bf = importFFdata(ffmesh,'WORK/BaseFlow.ff2m');
+end
+
+
+%% chapter 2 : linear / BF results
+Re_TAB = [40 :10 : 200];
+
+if(exist('RESULTS/LINresS.mat')==0)
+    LINres = Linear_LoopRe(bf,0.75i-.1,Re_TAB);
+    save('RESULTS/LINresS.mat','LINres');
+else
+    load('RESULTS/LINresS.mat');
+end
 
 
 
-
-%%  CHAPTER 2 : determining instability threshold
-
+%%  CHAPTER 3 : determining instability threshold
 
 disp('COMPUTING INSTABILITY THRESHOLD');
 bf=SF_BaseFlow(bf,'Re',50);
 [ev,em] = SF_Stability(bf,'shift',+.75i,'nev',1,'type','S');
-[bf,em]=SF_FindThreshold(bf,em);
-Rec = bf.Re;  Fxc = bf.Fx; 
-Lxc=bf.Lx;    Omegac=imag(em.lambda);
+[bfT,emT]=SF_FindThreshold(bf,em);
+Rec = bfT.Re;
 
+%% CHAPTER 4 : HB1 Loop over Re
 
[…]

### 2018-07-19 CASES_STABLE/ROTATING_POLYGONS/autorun.m

@@ -42,28 +42,28 @@ n=1;
 plotFF(emm3(n),'phi.im','xlim',[0 1],'ylim',[0 .5]);hold on;
 hold on;E=0.05/max(abs(emm3(n).eta));
 plot(ffmesh.xsurf+E*emm3(n).eta.*ffmesh.N0r,ffmesh.ysurf+E*emm3(n).eta.*ffmesh.N0z,'r');
-title(['Mode C0 : omega = ',num2str(evm3(n))])
+title(['Mode G0 : omega = ',num2str(evm3(n))])
 hold off;
 subplot(2,2,2);
 n=3;
 plotFF(emm3(n),'phi.im','xlim',[0 1],'ylim',[0 .5]);hold on;
 hold on;E=0.05/max(abs(emm3(n).eta));
 plot(ffmesh.xsurf+E*emm3(n).eta.*ffmesh.N0r,ffmesh.ysurf+E*emm3(n).eta.*ffmesh.N0z,'r');
-title(['Mode C1 : omega = ',num2str(evm3(n))])
+title(['Mode G1 : omega = ',num2str(evm3(n))])
 hold off;
 subplot(2,2,3);
 n=2;
 plotFF(emm3(n),'phi.im','xlim',[0 1],'ylim',[0 .5]);hold on;
 hold on;E=0.05/max(abs(emm3(n).eta));
 plot(ffmesh.xsurf+E*emm3(n).eta.*ffmesh.N0r,ffmesh.ysurf+E*emm3(n).eta.*ffmesh.N0z,'r');
-title(['Mode G0 : omega = ',num2str(evm3(n))]);xlim([.2 1]);ylim([0 .5]);
+title(['Mode C0 : omega = ',num2str(evm3(n))]);xlim([.2 1]);ylim([0 .5]);
 hold off;
 subplot(2,2,4)
 n=4;
 plotFF(emm3(n),'phi.im','xlim',[0 1],'ylim',[0 .5]);hold on;
 hold on;E=0.05/max(abs(emm3(n).eta));
 plot(ffmesh.xsurf+E*emm3(n).eta.*ffmesh.N0r,ffmesh.ysurf+E*emm3(n).eta.*ffmesh.N0z,'r');
-title(['Mode G1 : omega = ',num2str(evm3(n))]);
+title(['Mode C1 : omega = ',num2str(evm3(n))]);
 hold off;
[…]

### 2018-07-19 SOURCES_MATLAB/SF_BaseFlow.m

@@ -78,7 +78,7 @@ else DarcyDefault = 0;
 end
 addParameter(p, 'Darcy', DarcyDefault, @isnumeric); % For porous body
 
-if (isfield(baseflow, 'Porosity')) PorosityDefault = baseflow.Porosity;
+if (isfield(baseflow, 'Porosity')) PorosityDefault = baseflow.PorosityDefault;
 else PorosityDefault = 0.95;
 end
 addParameter(p, 'Porosity', PorosityDefault, @isnumeric); % For porous body too
@@ -109,7 +109,7 @@ switch (baseflow.mesh.problemtype)
     case ('AxiXRPOROUS') % axisymmetric WITH SWIRL
         mydisp(1, '## Entering SF_BaseFlow (axisymmetric case WITH SWIRL)');
         solvercommand = ['echo ', num2str(Re), ' ', num2str(p.Results.Omegax), ' ', num2str(p.Results.Darcy), ' ', num2str(p.Results.Porosity), ' | ', ff, ' ', ffdir, 'Newton_AxiSWIRL.edp']
-        filename = [ffdatadir, 'BASEFLOWS/BaseFlow_Re', num2str(Re), '_Omega', num2str(p.Results.Omegax), '_Da', num2str(p.Results.Darcy), '_Por', num2str(p.Results.Porosity)]
+        filename = [ffdatadir, 'BASEFLOWS/BaseFlow_Re', num2str(Re), '_Omega', num2str(p.Results.Omegax), '_Da', num2str(p.Results.Darcy), '_Por', num2str(p.Results.Porosity)];
         
     case ('2D')
         mydisp(1, '## Entering SF_BaseFlow (2D INCOMPRESSIBLE)');

### 2018-07-19 SOURCES_MATLAB/SF_HB1.m

@@ -1,95 +1,116 @@
 
 function [meanflow, mode] = SF_HB1(meanflow, mode, varargin)
-% StabFem wrapper for Harmonic Balance order 1 (idem as Self-Consistent model of Mantic lugo et al.)
-%
-% usage : [meanflow,mode] = SF_HB1(meanflow,mode,[Param1, Value1,...])
-%
-% first argument is either a "baseflow" or 'meanflow"
-% second argument is either an "eigenmode" or a "selfconsistentmode".
-%
-% Parameters include :
-%
-%   Re :        Reynolds number (specify only if it differs from the one of base flow, which is not usual)
-%   Aguess :    Amplitude for renormalising the eigenmode/SCmode
-%   Fyguess :   Lift for renormalising the eigenmode/SCmode
-%   (if none of these is present then no renormalization is done)
-%   omegaguess : guess for frequency (if not provided we take the im. part of the eigenvalue of the mode)
-%   sigma  :    instantaneous growth rate (nonzero for SC model ; zero for HB model)
-%
-%  Copyright D. Fabre, 2018
+%> StabFem wrapper for Harmonic Balance order 1 (idem as Self-Consistent model of Mantic lugo et al.)
+%>
+%> usage : [meanflow,mode] = SF_HB1(meanflow,mode,[Param1, Value1,...])
+%>
+%> first argument is either a "baseflow" or 'meanflow"
+%> second argument is either an "eigenmode" or a "selfconsistentmode".
+%>
+%> Parameters include :
+%>
+%>   Re :        Reynolds number (specify only if it differs from the one of base flow, which is not usual)
+%>   Aguess :    Amplitude for renormalising the eigenmode/SCmode
+%>   Fyguess :   Lift for renormalising the eigenmode/SCmode
+%>   (if none of these is present then no renormalization is done)
+%>   omegaguess : guess for frequency (if not provided we take the im. part of the eigenvalue of the mode)
+%>   sigma  :    instantaneous growth rate (nonzero for SC model ; zero for HB model)
[…]

### 2018-07-19 SOURCES_MATLAB/SF_Mesh_Deform.m

@@ -30,11 +30,11 @@ switch (ffmesh.problemtype)
         
         if(p.Results.V~=-1)% V-controled mode
             mydisp(1,'## Deforming MESH For STATIC FREE SURFACE PROBLEM (V-controled)'); 
-            parameterstring = ['  V ',num2str(p.Results.V),' ',num2str(p.Results.gamma),' ',num2str(p.Results.rhog),' ',p.Results.typestart,' ',p.Results.typeend,'  '];
+            parameterstring = [' " V ',num2str(p.Results.V),' ',num2str(p.Results.gamma),' ',num2str(p.Results.rhog),' ',p.Results.typestart,' ',p.Results.typeend,' " '];
             solvercommand = ['echo ',parameterstring, ' | ',ff,' ',ffdir,'Newton_Axi_FreeSurface_Static.edp'];
         elseif(p.Results.P~=-1)% P-controled mode
             mydisp(1,'## Deforming MESH For STATIC FREE SURFACE PROBLEM (P-controled)'); 
-            parameterstring = ['  P ',num2str(p.Results.P),' ',num2str(p.Results.gamma),' ',num2str(p.Results.rhog),' ',p.Results.typestart,' ',p.Results.typeend,'  '];
+            parameterstring = [' " P ',num2str(p.Results.P),' ',num2str(p.Results.gamma),' ',num2str(p.Results.rhog),' ',p.Results.typestart,' ',p.Results.typeend,' " '];
             solvercommand = ['echo ',parameterstring, ' | ',ff,' ',ffdir,'Newton_Axi_FreeSurface_Static.edp'];
         end
 end
@@ -43,10 +43,10 @@ end
 error = 'ERROR : SF_BaseFlow_MoveMesh computation aborted';
 mysystem(solvercommand, error); %needed to generate .ff2m file
 
-if (exist([ffdatadir, 'BaseFlow.txt']) ~= 2)
-    error('ERROR in SF_BaseFlow_MoveMesh : Newton did not converge');
-end
-
+%if (exist([ffdatadir, 'BaseFlow.txt']) ~= 2)
+%    error('ERROR in SF_BaseFlow_MoveMesh : Newton did not converge');
+%end
+% Trouver autre chose pour critere de non convergence...
 
 ffmeshNew = importFFmesh('mesh.msh');
 

### 2018-07-20 99_Documentation/MANUAL/212_SessileDrops.tex
commit sur branche nabil

% !TEX root = main.tex

\chapter{Linear dynamics of sessile drops}

\begin{description}
\item{Directory in the StabFem project:}  \texttt{SessileDropsBostwickSteen}
\item{Main contributors:} Nabil ACHOUR \& David FABRE.
\item{Reference:} Linear and nonlinear oscillations of sessile drops and partially filled container, N. Achour.  
\end{description}

A sessile droplet partially wets a planar solid support. We study the linear stability of an inviscid sessile drops. In this test-case the three-phase contact line is pinned.

\section{Creation of initial mesh for Sessile drops}

\section{Eigenvalue computation for m=0 and m=1}

### 2018-07-20 CASES_DEVELOPMENT/SessileDropsBostwick_Steen/SCRIPT_SESSILEDROP.m

@@ -14,7 +14,10 @@ ffmesh = SF_Mesh('MeshInit_Drop.edp','Params',[R theta density]);
 %% CHAPTER 1 : Eigenvalue computation for m=0 and m=1 FOR A Sessile drop
 [evm0,emm0] =  SF_Stability(ffmesh,'nev',10,'m',0,'sort','SIA','typestart','pined','typeend','axis');
 [evm1,emm1] =  SF_Stability(ffmesh,'nev',10,'m',1,'sort','SIA','typestart','pined','typeend','axis');
-
+figure();
+plotFF(emm0(3),'mesh');
+hold on
+plot(ffmesh.xsurf,ffmesh.ysurf);hold on;quiver(ffmesh.xsurf,ffmesh.ysurf,ffmesh.N0r,ffmesh.N0z);
 
 %%% PLOT RESULTS
 figure(2);
@@ -121,3 +124,7 @@ area(-ffmesh.xsurf+E*real(emm1(3).eta).*ffmesh.N0r,ffmesh.ysurf-E*real(emm1(3).e
 plot([ffmesh.xsurf(end), -ffmesh.xsurf(end)],[ffmesh.ysurf(end), ffmesh.ysurf(end)],'k','LineWidth',3);
 title('Mode m=1,k=3')
 saveas(gcf,'FIGURES/SessileDrops_subplot_Eigenmodes_eta',figureformat);
+
+
+
+

### 2018-07-20 CASES_DEVELOPMENT/Vessel/SCRIPT_vessel.m

@@ -25,66 +25,76 @@ plot(ffmesh.xsurf,ffmesh.ysurf); hold
 [evm1,emm1] =  SF_Stability(ffmesh,'nev',10,'m',1,'sort','SIA','typestart','pined','typeend','axis');
 
 %%% PLOT RESULTS
+%%% PLOT RESULTS
 figure(2);
 plot(imag(evm0),real(evm0),'ro',imag(evm1),real(evm1),'bo');
-title('Cylindrical bridge, L= 4 : spectra for m=0 (red) and m=1 (blue)');
+title('Vessel, spectra for m=0 (red) and m=1 (blue)');
 xlabel('\omega_r');ylabel('\omega_i');
 
 figure(3); hold off;
-plot(ffmesh.S0,emm0(3).eta);hold on;
-plot(ffmesh.S0,emm0(5).eta);
+plot(ffmesh.S0,real(emm0(3).eta));hold on;
+plot(ffmesh.S0,real(emm0(5).eta));
 % note that for m=0 the two first modes are spurious, so we take modes 3 and 5
-plot(ffmesh.S0,emm1(1).eta);
-plot(ffmesh.S0,emm1(3).eta);
+plot(ffmesh.S0,real(emm1(1).eta));
+plot(ffmesh.S0,real(emm1(3).eta));
 % on the other hand for m=1 the first modes are regular
-title('Cylindrical bridge, L= 4 : structure of the four simplest modes eta(s) ');
+title('Vessel structure of the four simplest modes eta(s) ');
 legend('m=0,a','m=0,s','m=1,s','m=1,a');
 
 
 figure(4);
-subplot(1,4,1);plotFF(emm0(3),'phi.im','title','Mode m=0,a');
+subplot(1,4,1);plotFF(emm0(3),'phi.im','title','Mode m=0,k=2');
 hold on;E=0.15/max(abs(emm0(3).eta));
-plot(ffmesh.xsurf+E*emm0(3).eta.*ffmesh.N0r,ffmesh.ysurf+E*emm0(3).eta.*ffmesh.N0z,'r');hold off;
[…]

### 2018-10-02 DEVELOPMENT_CASES/WhistlingHole/JFM_PartII_Draft/jfm-instructions.tex
1/ redesigning free-surface cases (and upgrading case Vessel) ; 2/ change of arborescence, 3/ autorun

% This is file JFM2esam.tex
% first release v1.0, 20th October 1996
%       release v1.01, 29th October 1996
%       release v1.1, 25th June 1997
%       release v2.0, 27th July 2004
%       release v3.0, 16th July 2014
%   (based on JFMsampl.tex v1.3 for LaTeX2.09)
% Copyright (C) 1996, 1997, 2014 Cambridge University Press

\documentclass{jfm}
\usepackage{graphicx}
\usepackage{epstopdf, epsfig}

\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}

\shorttitle{Guidelines for authors}
\shortauthor{A. N. Other, H.-C. Smith and J. Q. Public}

\title{Guidelines for authors and submission template}

\author{David Fabre\aff{1}
  \corresp{\email{david.fabre@imft.fr}},
  Raffaele Longobardi\aff{1,2}
 \and Paolo Luchini\aff{2}}

\affiliation{\aff{1}Universit\'e de Toulouse; INPT, UPS; IMFT (Institut de M\'ecanique des Fluides de Toulouse); All\'ee Camille Soula, F-31400 Toulouse, France \\
\aff{2}DIIN, Universit\'a degli Studi di Salerno, Via Giovanni Paolo II, 84084 Fisciano (SA), Italy}

\begin{document}

\maketitle

\begin{abstract}
This file contains instructions for authors planning to submit a paper to the {\it Journal of Fluid Mechanics}. These instructions were generated in {\LaTeX} using the JFM style, so the {\LaTeX} source file can be used as a template for submissions. The present paragraph appears in the \verb}abstract} environment. All papers should feature a single-paragraph abstract of no more than 250 words, which provides a summary of the main aims and results. 
\end{abstract}

\begin{keywords}
Authors should not enter keywords on the manuscript, as these must be chosen by the author during the online submission process and will then be added during the typesetting process (see http://journals.cambridge.org/data/\linebreak[3]relatedlink/jfm-\linebreak[3]keywords.pdf for the full list)
\end{keywords}

\section{How to submit to the \textbf{\textit{Journal of Fluid Mechanics}}}
Authors must submit using the online submission and peer review system, Scholar One Manuscripts (formerly Manuscript Central) at http://mc.manuscriptcentral.com/jfm. If visiting the site for the first time, users must create a new account by clicking on `register here'. Once logged in, authors should click on the `Corresponding Author Centre', from which point a new manuscript can be submitted, with step-by-step instructions provided. Authors must at this stage specify whether the submission is a standard paper, or a {\it JFM Rapids} paper (see \S\ref{sec:filetypes} for more details). In addition, authors must specify an editor to whom the paper will be submitted from the drop-down list provided. Note that all editors exclusively deal with either standard papers or {\it JFM Rapids} (clearly indicated on the list), so please ensure that you choose an editor accordingly. Corresponding authors must provide a valid ORCID ID in order to submit a manuscript, either by linking an existing ORCID profile to your ScholarOne account or by creating a new ORCID profile. Once your submission is completed you will receive an email confirmation.  Book reviews should not be submitted via the online submission site and should instead be submitted by email to c.p.caulfield@damtp.cam.ac.uk.

\section{Rules of submission}\label{sec:rules_submission}
Submission of a paper implies a declaration by the author that the work has not previously been published, that it is not being considered for publication elsewhere and that it has not already been considered by a different editor of the Journal. Note that a report on a conference must be submitted within 3 months of the meeting.

\section{Types of paper}\label{sec:types_paper}
\subsection{Standard papers}
Regular submissions to JFM are termed `standard papers'. Note that such papers must contain original research, as review articles are not published in JFM. Papers should be written in a concise manner; though JFM has no page limit, each paper will be judged on its own merits, and those deemed excessive in length will be rejected or will require significant revision.  
\subsection{JFM Rapids}
{\it JFM Rapids} is devoted to the rapid publication of short, high-impact papers across the full range of fluid mechanics. Manuscripts submitted as {\it Rapids}  must be strictly 10 or fewer printed pages, and must be submitted in {\LaTeX} using the jfm.cls class file, so as to ensure that they meet the page limit and to expedite their production.  The principal and over-riding objective is to publish papers of the highest scientific quality.

Once a paper is submitted, referees are asked to provide reports with a short turnaround.  In order to be accepted for publication in {\it JFM Rapids}, such papers must require only minor revisions to improve clarity, usually without recourse to a second round of refereeing. In this case, and at the discretion of the editor, some additional pages may be allowed to address specific points raised by the referees, such as the addition of an extra figure or some explanatory text.

In cases where the editor, guided by the referees, judges that a paper has merit but requires substantial revision that will require significant refereeing, a decision of `revise and resubmit' will be given. On re-submission, such papers will be handled as standard JFM papers and if accepted will not subsequently appear as {\it JFM Rapids}.

{\it Rapids} will be published online within one month of final acceptance.  They will appear within a designated section on the Journal of Fluid Mechanics website.  Each {\it Rapid} will be cited and indexed as a JFM article but with a distinctive {\it Rapids} identifier, and will be assigned to a JFM volume. {\it Rapids} will not be included in the regular print versions of JFM, and accordingly they incur no colour figure charges.

\section{File types}\label{sec:filetypes}
Authors are strongly encouraged to compose their papers in {\LaTeX}, using the jfm.cls style file and supporting files provided at\\ http://journals.cambridge.org/action/displaySpecialPage?pageId=2860, with the jfm-instructions.tex file serving as a template (note that this is mandatory for {\it JFM Rapids}). A PDF of the {\LaTeX} file should then be generated and submitted via the submission site. Please note that PDFs larger than 10MB are not acceptable for review. There is no need to submit the {\LaTeX} source file alongside the PDF, but upon provisional acceptance of the paper, the {\LaTeX} source file, along with individual figure files and a PDF of the final version, will need to be submitted for typesetting purposes. 
Authors may also compose standard papers in Word, though this will lead to the paper spending a longer period in production. If using Word, please note that equations must NOT be converted to picture format and the file must be saved with the option `make equation editable'. 
\section{Preparing your manuscript}
Authors should write their papers clearly and concisely in English, adhering to JFM's established style for notation, as provided in \S\ref{notstyle}. We encourage the submission of online supplementary material alongside the manuscript where appropriate (see section \ref{online}). Metric units should be used throughout and all abbreviations must be defined at first use, even those deemed to be well known to the readership. British spelling must be used, and should follow the \textit{Shorter Oxford English Dictionary}.

\subsection{Figures}
Figures should be as small as possible while displaying clearly all the information required, and with all lettering readable. Every effort should be taken to avoid figures that run over more than one page. Figures submitted in colour will appear online in colour but, with the exception of {\it JFM Rapids}, all figures will be printed in black and white unless authors specify during submission that figures should be printed in colour, for which there is a charge of \pounds200 plus VAT per figure (i.e. \pounds240) with a cap of \pounds1000 plus VAT per article (i.e. \pounds1200) (colour is free for {\it JFM Rapids}).  Note that separate figures for online and print will {\bf not} be accepted and it is the author's responsibility to ensure that if a figure is to appear in colour online only, that same figure will still be meaningful when printed in black and white (for example, do not rely upon colours to distinguish lines if those colours will just appear as similar shades of grey when printed). If using colour, authors should also ensure that some consistency is applied within the manuscript. For review purposes figures should be embedded within the manuscript. Upon final acceptance, however, individual figure files will be required for production. These should be submitted in EPS or high-resolution TIFF format (1200 dpi for lines, 300 dpi for halftone and colour in CMYK format, and 600 dpi for a mixture of lines and halftone). The minimum acceptable width of any line is 0.5pt. Each figure should be accompanied by a single caption, to appear beneath, and must be cited in the text. Figures should appear in the order in which they are first mentioned in the text and figure files must be named accordingly (`Figure 1.eps', `Figure 2a.tiff', etc) to assist the production process (and numbering of figures should continue through any appendices). The word \textit {figure} is only capitalized at the start of a sentence. For example see figures \ref{fig:ka} and \ref{fig:kd}. Failure to follow figure guidelines may result in a request for resupply and a subsequent delay in the production process. Note that {\em all} figures are relabelled by the typesetter, so please ensure all figure labels are carefully checked against your originals when you receive your proofs.

\begin{figure}
  \centerline{\includegraphics{trapped}}% Images in 100% size
  \caption{Trapped-mode wavenumbers, $kd$, plotted against $a/d$ for
    three ellipses:\protect\\
    ---$\!$---,
    $b/a=1$; $\cdots$\,$\cdots$, $b/a=1.5$.}
\label{fig:ka}
\end{figure}

\begin{figure}
  \centerline{\includegraphics{modes}}
  \caption{The features of the four possible modes corresponding to
  (\textit{a}) periodic\protect\\ and (\textit{b}) half-periodic solutions.}
\label{fig:kd}
\end{figure}

\subsection{Tables}
Tables, however small, must be numbered sequentially in the order in which they are mentioned in the text. The word \textit {table} is only capitalized at the start of a sentence. See table \ref{tab:kd} for an example.

\begin{table}
  \begin{center}
\def~{\hphantom{0}}
  \begin{tabular}{lccc}
      $a/d$  & $M=4$   &   $M=8$ & Callan \etal \\[3pt]
       0.1   & 1.56905 & ~~1.56~ & 1.56904\\
       0.3   & 1.50484 & ~~1.504 & 1.50484\\
       0.55  & 1.39128 & ~~1.391 & 1.39131\\
       0.7   & 1.32281 & ~10.322 & 1.32288\\
       0.913 & 1.34479 & 100.351 & 1.35185\\
  \end{tabular}
  \caption{Values of $kd$ at which trapped modes occur when $\rho(\theta)=a$}
  \label{tab:kd}
  \end{center}
\end{table}

\subsection{Online supplementary material}\label{online}
Relevant material which is not suitable for print production, such as movies or numerical simulations/animations, can be uploaded as part of the initial submission. Movies should be designated as `Movie' and each individual file must be accompanied by a separate caption and a suitable title (eg Movie 1). Accepted formats are .mov, .mpg, .mp4, and .avi, though they should be archived as a .zip or .tar file before uploading. Each movie should be no more than 10MB. Upon publication these materials will then be hosted online alongside the final published article. Likewise, should there be detailed mathematical relations, tables or figures which are likely to be useful only to a few specialists or take up excessive space in the printed journal, these can also be published online as supplementary material [designated as `Other supplementary material']. Note that supplementary material is published `as is', with no further production performed.

\section{Editorial decisions}
\subsection{Revision}
If a revision is requested, you should upload revised files following the same procedure as for submitting a new paper. You begin by clicking on `Manuscripts with decision' in your Corresponding Author Center, and then on `Create a revision'. (Note that if you abandon the process before completing the submission, to continue the submission, you must click on `Revised manuscripts in draft'.) There is a new first page showing the decision letter and a space for your reply to the referee's/editor's comments. You also have the opportunity at this stage to upload your reply to the comments as a separate file. All the values filled in on original submission are displayed again. The ID number of the paper will be appended `.R1'. Also note that if a manuscript is submitted as a {\it JFM Rapid}, but requires substantial revision, it will be re-designated as a standard paper, and the ID and paper type will be amended to reflect this.

\subsection{Provisional acceptance}
If the paper is accepted as suitable for publication you will be sent a provisional acceptance decision. This enables you to upload the final files required for production:
(1) the final PDF or word version of the paper, designated as a `main document';
(2) any source files (see section \ref{sec:filetypes}) which must be designated as `production (not for review)' and uploaded as a single .zip or .tar file.

\subsection{Acceptance}
On receipt of the production files you will be sent an email indicating completion of the acceptance process.

\section{Publication process}
Once a paper has been accepted for publication and the source files have been uploaded, the manuscript will be sent to Cambridge University Press for copyediting and typesetting, and will be assigned a digital object identifier (doi). When the proof is ready, authors will receive an email alert containing a link to the PDF of the proof, and instructions for its correction and return. It is imperative that authors check their proofs closely, particularly the equations and figures, which should be checked against the accepted file, as the production schedule does not allow for corrections at a later stage. Once ready for printing, papers will be published online on Cambridge Journals Online in the current `open' volume. {\it JFM Rapids} will also be assigned to the current open volume, but will receive an article number in place of traditional pagination, as they will not appear in the print version of that volume. Each volume will be kept open for approximately two weeks, at which point it will be considered `closed', and then printed and distributed. The following volume will be immediately opened. Note that the PDF published online is the Version of Record, matching the print version, and no further alterations/corrections to this document will be allowed. The corresponding author is emailed a link to the published article when it is first published online.

\section{Corrigenda}
The Journal will publish corrigenda that alter significant conclusions made in a paper.  Such corrigenda should be submitted to an associate editor, who will consider the submission similarly to a new paper and may consult referees if appropriate.  When published, corrigenda are clearly linked with the original articles to which they refer, and the articles to them.

The Journal does not normally publish corrigenda to amend typographical errors, so it is extremely important that authors make very careful checks of their manuscript at every stage, including the reading of proofs, prior to publication.

\section{Obtaining help}
Technical support for the online submission system is available by clicking on the `Get Help Now' link at the top-right corner of each page of the submission site. Any other questions relating to the submission or publication process should be directed to the JFM Editorial Assistant, Mrs Amanda Johns, at ajohns@cambridge.org.

\section{Cambridge Language Editing Service} 
We suggest that authors whose first language is not English have their manuscripts checked by a native English speaker before submission. This is optional but will help to ensure that any submissions that reach peer review can be judged exclusively on academic merit. We offer a Cambridge service which you can find out more about at https://www.cambridge.org/core/services/authors/language-services, and suggest that authors make contact as appropriate. Please note that use of language editing services is voluntary and at the author’s own expense. Use of these services does not guarantee that the manuscript will be accepted for publication nor does it restrict the author to submitting to a Cambridge-published journal

\section{Notation and style}\label{notstyle}
Generally any queries concerning notation and journal style can be answered by viewing recent pages in the Journal. However, the following guide provides the key points to note. It is expected that Journal style will be followed, and authors should take care to define all variables or entities upon first use. Also note that footnotes are not normally accepted.

\subsection{Mathematical notation}
\subsubsection{Setting variables, functions, vectors, matrices etc}
{\bf Italic font} should be used for denoting variables, with multiple-letter symbols avoided except in the case of dimensionless numbers such as $\Rey$, $\Pran$ and $\Pen$ (Reynolds, Prandtl, and P\'eclet numbers respectively, which are defined as \verb}\Rey}, \verb}\Pran} and {\verb}\Pen} in the template).\\
{\bf Upright Roman font} (or upright Greek where appropriate) should be used for:\\
Operators: sin, log, d, $\Delta$, e etc.\\
Constants: i ($\sqrt{-1}$), $\upi$ (defined as \verb}\upi}), etc.\\
Functions: $\Ai$, $\Bi$ (Airy functions, defined as \verb}\Ai} and \verb}\Bi}), $\Real$ (real part, defined as \verb}\Real}), $\Imag$ (imaginary part, defined as \verb}\Imag}), etc.\\
Physical units: cm, s, etc\\
Abbreviations: c.c. (complex conjugate), h.o.t. (higher-order terms), DNS, etc.\\
{\bf Bold italic font} (or bold sloping Greek) should be used for:\\
Vectors (with the centred dot for a scalar product also in bold): $\boldsymbol{i \cdot j}$\\
{\bf Bold sloping sans serif font}, defined by the \verb}\mathsfbi} macro, should be used for:\\
Tensors and matrices: $\mathsfbi{D}$ \\
{\bf Script font} (for example $\mathcal{G}$, $\mathcal{R}$) can be used as an alternative to italic when the same letter denotes a different quantity (use \verb}\mathcal} in \LaTeX)\\
The product symbol ($\times$) should only be used to denote multiplication where an equation is broken over more than one line, to denote a cross product, or between numbers (the $\cdot$ symbol should not be used, except to denote a scalar product specifically).\\

\subsubsection{Other symbols}
A centred point should be used only for the scalar product of vectors.
Large numbers that are not scientific powers should not include commas, but have the
form 1600 or 16 000 or 160 000.
Use \textit{O} to denote `of the order of', not the \LaTeX\ $\mathcal{O}$.

\section{Citations and references}
All papers included in the References section must be cited in the article, and vice versa. Citations should be included as, for example ``It has been shown \citep{Rogallo81} that...'' (using the {\verb}\citep} command, part of the natbib package) ``recent work by \citet{Dennis85}...'' (using {\verb}\citet}).
The natbib package can be used to generate citation variations, as shown below.\\
\verb#\citet[pp. 2-4]{Hwang70}#:\\
\citet[pp. 2-4]{Hwang70} \\
\verb#\citep[p. 6]{Worster92}#:\\
\citep[p. 6]{Worster92}\\
\verb#\citep[see][]{Koch83, Lee71, Linton92}#:\\
\citep[see][]{Koch83, Lee71, Linton92}\\
\verb#\citep[see][p. 18]{Martin80}#:\\
\citep[see][p. 18]{Martin80}\\
\verb#\citep{Brownell04,Brownell07,Ursell50,Wijngaarden68,Miller91}#:\\
\citep{Brownell04,Brownell07,Ursell50,Wijngaarden68,Miller91}\\
The References section can either be built from individual \verb#\bibitem# commands, or can be built using BibTex. The BibTex files used to generate the references in this document can be found in the zip file at http://journals.cambridge.org/\linebreak[3]data/\linebreak[3]relatedlink/\linebreak[3]jfm-ifc.zip.\\
Where there are up to ten authors, all authors' names should be given in the reference list. Where there are more than ten authors, only the first name should appear, followed by et al.\\

Acknowledgements should be included at the end of the paper, before the References section or any appendicies, and should be a separate paragraph without a heading. Several anonymous individuals are thanked for contributions to these instructions.

\appendix
\section{}\label{appA}
This appendix contains sample equations in the JFM style. Please refer to the {\LaTeX} source file for examples of how to display such equations in your manuscript.

\begin{equation}
  (\nabla^2+k^2)G_s=(\nabla^2+k^2)G_a=0
  \label{Helm}
\end{equation}

\begin{equation}
  \bnabla\bcdot\boldsymbol{v} = 0,\quad \nabla^{2}P=
    \bnabla\bcdot(\boldsymbol{v}\times \boldsymbol{w}).
\end{equation}

\begin{equation}
  G_s,G_a\sim 1 / (2\upi)\ln r
  \quad \mbox{as\ }\quad r\equiv|P-Q|\rightarrow 0,
  \label{singular}
\end{equation}

\begin{equation}
\left. \begin{array}{ll}  
\displaystyle\frac{\p G_s}{\p y}=0
  \quad \mbox{on\ }\quad y=0,\\[8pt]
\displaystyle  G_a=0
  \quad \mbox{on\ }\quad y=0,
 \end{array}\right\}
  \label{symbc}
\end{equation}

\begin{equation}
  -\frac{1}{2\upi} \int_0^{\infty} \gamma^{-1}[\mathrm exp(-k\gamma|y-\eta|)
   + \mathrm exp(-k\gamma(2d-y-\eta))] \cos k(x-\xi)t\:\mathrm{d} t,
   \qquad 0<y,\quad \eta<d,
\end{equation}

\begin{equation}
  \gamma(t) = \left\{
    \begin{array}{ll}
      -\mathrm{i}(1-t^2)^{1/2}, & t\le 1 \\[2pt]
      (t^2-1)^{1/2},         & t>1.
    \end{array} \right.
\end{equation}

\[
  -\frac{1}{2\upi}
   \pvi B(t)\frac{\cosh k\gamma(d-y)}{\gamma\sinh k\gamma d}
   \cos k(x-\xi)t\:\mathrm{d} t
\]

\begin{equation}
  G = -\frac{1}{4}\mathrm{i} (H_0(kr)+H_0(kr_1))
    - \frac{1}{\upi} \pvi\frac{\mathrm{e}^{-\kgd}}%
    {\gamma\sinh\kgd} \cosh k\gamma(d-y) \cosh k\gamma(d-\eta)
\end{equation}

Note that when equations are included in definitions, it may be suitable to render them in line, rather than in the equation environment: $\boldsymbol{n}_q=(-y^{\prime}(\theta),
x^{\prime}(\theta))/w(\theta)$.
Now $G_a=\squart Y_0(kr)+\Gat$ where
$r=\{[x(\theta)-x(\psi)]^2 + [y(\theta)-y(\psi)]^2\}^{1/2}$ and $\Gat$ is
regular as $kr\ttz$. However, any fractions displayed like this, other than $\thalf$ or $\squart$, must be written on the line, and not stacked (ie 1/3).

\begin{eqnarray}
  \ndq\left(\frac{1}{4} Y_0(kr)\right) & \sim &
    \frac{1}{4\upi w^3(\theta)}
    [x^{\prime\prime}(\theta)y^{\prime}(\theta)-
    y^{\prime\prime}(\theta)x^{\prime}(\theta)] \nonumber\\
  & = & \frac{1}{4\upi w^3(\theta)}
    [\rho^{\prime}(\theta)\rho^{\prime\prime}(\theta)
    - \rho^2(\theta)-2\rho^{\prime 2}(\theta)]
    \quad \mbox{as\ }\quad kr\ttz . \label{inteqpt}
\end{eqnarray}

\begin{equation}
  \frac{1}{2}\phi_i = \frac{\upi}{M} \sumjm\phi_j K_{ij}^a w_j,
  \qquad i=1,\,\ldots,\,M,
\end{equation}
where
\begin{equation}
  K_{ij}^a = \left\{
    \begin{array}{ll}
      \p G_a(\theta_i,\theta_j)/\p n_q, & i\neq j \\[2pt]
      \p\Gat(\theta_i,\theta_i)/\p n_q
      + [\rho_i^{\prime}\rho_i^{\prime\prime}-\rho_i^2-2\rho_i^{\prime 2}]
      / 4\upi w_i^3, & i=j.
  \end{array} \right.
\end{equation}

\refstepcounter{equation}
$$
  \rho_l = \lim_{\zeta \rightarrow Z^-_l(x)} \rho(x,\zeta), \quad
  \rho_{u} = \lim_{\zeta \rightarrow Z^{+}_u(x)} \rho(x,\zeta)
  \eqno{(\theequation{\mathit{a},\mathit{b}})}\label{eq35}
$$

\begin{equation}
  (\rho(x,\zeta),\phi_{\zeta\zeta}(x,\zeta))=(\rho_0,N_0)
  \quad \mbox{for}\quad Z_l(x) < \zeta < Z_u(x).
\end{equation}

\begin{subeqnarray}
  \tau_{ij} & = &
    (\overline{\overline{u}_i \overline{u}_j}
    - \overline{u}_i\overline{u}_j)
    + (\overline{\overline{u}_iu^{SGS}_j
    + u^{SGS}_i\overline{u}_j})
    + \overline{u^{SGS}_iu^{SGS}_j},\\[3pt]
  \tau^\theta_j & = &
    (\overline{\overline{u}_j\overline{\theta}}
    - \overline{u}_j \overline{\theta})
    + (\overline{\overline{u}_j\theta^{SGS}
    + u^{SGS}_j \overline{\theta}})
    + \overline{u^{SGS}_j\theta^{SGS}}.
\end{subeqnarray}

\begin{equation}
\setlength{\arraycolsep}{0pt}
\renewcommand{\arraystretch}{1.3}
\slsQ_C = \left[
\begin{array}{ccccc}
  -\omega^{-2}V'_w  &  -(\alpha^t\omega)^{-1}  &  0  &  0  &  0  \\
  \displaystyle
  \frac{\beta}{\alpha\omega^2}V'_w  &  0  &  0  &  0  &  \mathrm{i}\omega^{-1} \\
  \mathrm{i}\omega^{-1}  &  0  &  0  &  0  &  0  \\
  \displaystyle
  \mathrm{i} R^{-1}_{\delta}(\alpha^t+\omega^{-1}V''_w)  &  0
    & -(\mathrm{i}\alpha^tR_\delta)^{-1}  &  0  &  0  \\
  \displaystyle
  \frac{\mathrm{i}\beta}{\alpha\omega}R^{-1}_\delta V''_w  &  0  &  0
    &  0  & 0 \\
  (\mathrm{i}\alpha^t)^{-1}V'_w  &  (3R^{-1}_{\delta}+c^t(\mathrm{i}\alpha^t)^{-1})
    &  0  &  -(\alpha^t)^{-2}R^{-1}_{\delta}  &  0  \\
\end{array}  \right] .
\label{defQc}
\end{equation}

\begin{equation}
\etb^t = \skew2\hat{\etb}^t \exp [\mathrm{i} (\alpha^tx^t_1-\omega t)],
\end{equation}
where $\skew2\hat{\etb}^t=\boldsymbol{b}\exp (\mathrm{i}\gamma x^t_3)$. 
\begin{equation}
\mbox{Det}[\rho\omega^2\delta_{ps}-C^t_{pqrs}k^t_qk^t_r]=0,
\end{equation}

\begin{equation}
 \langle k^t_1,k^t_2,k^t_3\rangle = \langle
\alpha^t,0,\gamma\rangle  
\end{equation}

\begin{equation}
\boldsymbol{f}(\theta,\psi) = (g(\psi)\cos \theta,g(\psi) \sin \theta,f(\psi)).
\label{eq41}
\end{equation}

\begin{eqnarray}
f(\psi_1) = \frac{3b}{\upi[2(a+b \cos \psi_1)]^{{3}/{2}}}
  \int^{2\upi}_0 \frac{(\sin \psi_1 - \sin \psi)(a+b \cos \psi)^{1/2}}%
  {[1 - \cos (\psi_1 - \psi)](2+\alpha)^{1/2}}\mathrm{d}x,
\label{eq42}
\end{eqnarray}
\begin{eqnarray}
g(\psi_1) & = & \frac{3}{\upi[2(a+b \cos \psi_1)]^{{3}/{2}}}
  \int^{2\upi}_0 \left(\frac{a+b \cos \psi}{2+\alpha}\right)^{1/2}
  \left\{ \astrut f(\psi)[(\cos \psi_1 - b \beta_1)S + \beta_1P]
  \right. \nonumber\\
&& \mbox{}\times \frac{\sin \psi_1 - \sin \psi}{1-\cos(\psi_1 - \psi)}
  + g(\psi) \left[\left(2+\alpha - \frac{(\sin \psi_1 - \sin \psi)^2}
  {1- \cos (\psi - \psi_1)} - b^2 \gamma \right) S \right.\nonumber\\
&& \left.\left.\mbox{} + \left( b^2 \cos \psi_1\gamma -
  \frac{a}{b}\alpha \right) F(\frac{1}{2}\upi, \delta) - (2+\alpha)
  \cos\psi_1 E(\frac{1}{2}\upi, \delta)\right] \astrut\right\} \mathrm{d} \psi,
\label{eq43}
\end{eqnarray}
\begin{equation}
\alpha = \alpha(\psi,\psi_1) = \frac{b^2[1-\cos(\psi-\psi_1)]}%
  {(a+b\cos\psi) (a+b\cos\psi_1)},
  \quad
  \beta - \beta(\psi,\psi_1) = \frac{1-\cos(\psi-\psi_1)}{a+b\cos\psi}.
\end{equation}

\begin{equation}
\left. \begin{array}{l}
\displaystyle
H(0) = \frac{\epsilon \overline{C}_v}{\tilde{v}^{{1}/{2}}_T
(1- \beta)},\quad H'(0) = -1+\epsilon^{{2}/{3}} \overline{C}_u
+ \epsilon \skew5\hat{C}_u'; \\[16pt]
\displaystyle
H''(0) = \frac{\epsilon u^2_{\ast}}{\tilde{v}^{{1}/{2}}
_T u^2_P},\quad H' (\infty) = 0.
\end{array} \right\}
\end{equation}

\begin{lemma}
Let $f(z)$ be a trial \citet[][pp.~231--232]{Batchelor59} function defined on $[0,1]$.  Let $\varLambda_1$ denote
the ground-state eigenvalue for $-\mathrm{d}^2g/\mathrm{d} z^2=\varLambda g$,
where $g$ must satisfy $\pm\mathrm{d} g/\mathrm{d} z+\alpha g=0$ at $z=0,1$
for some non-negative constant~$\alpha$.  Then for any $f$ that is not
identically zero we have
\begin{equation}
\frac{\displaystyle
  \alpha(f^2(0)+f^2(1)) + \int_0^1 \left(
  \frac{\mathrm{d} f}{\mathrm{d} z} \right)^2 \mathrm{d} z}%
  {\displaystyle \int_0^1 f^2\mathrm{d} z}
\ge \varLambda_1 \ge
\left( \frac{-\alpha+(\alpha^2+8\upi^2\alpha)^{1/2}}{4\upi} \right)^2.
\end{equation}
\end{lemma}

\begin{corollary}
Any non-zero trial function $f$ which satisfies the boundary condition
$f(0)=f(1)=0$ always satisfies
\begin{equation}
  \int_0^1 \left( \frac{\mathrm{d} f}{\mathrm{d} z} \right)^2 \mathrm{d} z.
\end{equation}
\end{corollary}

\bibliographystyle{jfm}
% Note the spaces between the initials
\bibliography{jfm-instructions}

\end{document}

### 2018-10-02 DEVELOPMENT_CASES/WhistlingHole/JFM_PartII_Draft/thick_hole.tex
1/ redesigning free-surface cases (and upgrading case Vessel) ; 2/ change of arborescence, 3/ autorun

% This is file JFM2esam.tex
% first release v1.0, 20th October 1996
%       release v1.01, 29th October 1996
%       release v1.1, 25th June 1997
%       release v2.0, 27th July 2004
%       release v3.0, 16th July 2014
%   (based on JFMsampl.tex v1.3 for LaTeX2.09)
% Copyright (C) 1996, 1997, 2014 Cambridge University Press

\NeedsTeXFormat{LaTeX2e}

\documentclass{jfm}
%\documentclass[referee]{jfm} %for double spaced output for submission

% See if the author has AMS Euler fonts installed: If they have, attempt
% to use the 'upmath' package to provide upright math.
\usepackage[english]{babel}
\usepackage{graphicx}
\usepackage{latexsym}
\usepackage{natbib}
\usepackage{rotate}
\usepackage{epstopdf}
\usepackage{pstricks}
\usepackage{amsmath}
\usepackage{url}
\newtheorem{lemma}{Lemma}
\usepackage{mathrsfs}  
\usepackage{latexsym}
\newtheorem{corollary}{Corollary}

\newcommand\be{\begin{equation}}
\newcommand\ee{\end{equation}}
\newcommand\bea{\begin{eqnarray}}
\newcommand\eea{\end{eqnarray}}
\newcommand\DP[2]{\frac{\p #1}{\p #2}}

%\pubyear{2012}
%\volume{}
%\pagerange{}
\date{\today}
%\setcounter{page}{1}

\shorttitle{Acoustic forcing of a laminar viscous jet through a thick circular aperture}
\shortauthor{D. Fabre, R. Longobardi, P. Bonnefis and P. Luchini}

\title{Acoustic forcing of a laminar viscous jet through a circular aperture in a thick plate : Impedance calculations and instability criteria}

\author{David Fabre\aff{1}
  \corresp{\email{david.fabre@imft.fr}},
  Raffaele Longobardi\aff{1,2},
  Paul Bonnefis\aff{1}
 \and Paolo Luchini\aff{2}}
\affiliation{\aff{1}Institut de M\'ecanique des Fluides de Toulouse, IMFT, Universit\'e de Toulouse, CNRS; All\'ee Camille Soula, 31400 Toulouse, France
\aff{2}DIIN (Dipartimento di Ingegneria Industriale); Universit\'a degli Studi di Salerno; Via Giovanni Paolo II, 84084 Fisciano (SA), Italy}

\begin{document}

\maketitle

\begin{abstract}
THIS IS THE ABSTRACT OF PART I !!!!!
The unsteady flow through a circular aperture in a thin plate subjected to harmonic forcing (for instance under the effect of an incident acoustic wave) is a classical problem first considered by Howe  ({\em Proc. R. Soc. London. A}, vol. 366, 1979, pp. $205-223$), using an inviscid model. The purpose of this work is to reconsider this problem through a  numerical resolution of the incompressible linearized Navier$-$Stokes equations (LNSE) in the range $Re = [100,3000]$. We first compute a steady base flow which allows us to describe the {\em vena contracta} phenomenon in accordance with experiments. We then solve a linear problem allowing to characterize both the spatial amplification of perturbations and the impedance (or equivalently the Rayleigh conductivity), which is a key quantity to investigate the response of the jet to acoustic forcing. Since the linear perturbation is characterized by a strong spatial amplification, the numerical resolution requires an original method based on the complex mapping of the axial coordinate in order to enlarge the range of Reynolds number investigated. 
The results show that the impedances computed with $Re\gtrsim 1500$ collapse onto a single curve, indicating that a large-Reynolds number asymptotic regime is effectively reached. However, expressing the results in terms of conductivity leads to substantial deviation with respect to the Howe model.
%The predictions for the Rayleigh conductivity are in good qualitative agreement with the model of Howe in the range of high Reynolds numbers. 
Finally, we investigate the case of finite amplitude perturbations through direct numerical simulations (DNS). We show that the impedance predicted by the linear approach remains 
valid for amplitudes up to order $\textit{O}(10^{-1})$, despite the fact that the spatial evolution of perturbations in the jet is strongly nonlinear.
\end{abstract}

\begin{keywords}

\end{keywords}

\section{Introduction}
%change the first sentence
The problem of the flow passing through a circular aperture in a plate is encountered in many practical applications, as for example fuel injectors, cooling system for gas turbines or wind instruments. 
When subjected to harmonic forcing, for instance under the effect of an incident acoustic wave, the vortex sheet formed at the rim of the aperture becomes periodically modulated and acts as a spatial amplifier of Kelvin-Helmholtz instability, reorganizing the jet into an array of vortex rings. This feature is an essential part of the sound production mechanism in situations where the jet subsequently passes through a second aperture, a configuration known as ``hole-tone'' and encountered for instance in tea kettles \citep{henrywood2013aeroacoustics} and birdcalls \citep{fabrea2014application}. The generation of vorticity is also an efficient mechanism to dissipate the acoustic energy. As a consequence, the use of multiply perforated plates traversed by a mean flow (or bias flow) is widely used as a sound attenuator device in many industrial applications, such as combustion systems.

The unsteady, periodic flow through a circular hole in a zero-thickness plate was initially solved by \citet{rayleigh1945theory} using inviscid, potential theory. The key result of his solution is the proportionality between the net pressure force felt from both sides of the hole and
the acceleration of the fluid, so that the whole situation can be modeled by assuming that there is a rigid plug of fluid, with area $A_h=\upi R_{h}^2$ and equivalent length $\ell_{eff}$, oscillating across the aperture, where $R_h$ is the radius of the hole.

The case where the flow has a mean component (or bias flow) in addition to the oscillating component was considered by \citet{howe1979theory}. He introduced a key quantity, the Rayleigh conductivity $K_R$, defined as the ratio of the acceleration of the fluid particules located within the aperture to the net force exerted on it. The real part of the conductivity generalizes the concept of equivalent length $\ell_{eff}$ previously introduced by Rayleigh, while its imaginary part is directly proportional to the flux of energy transferred from the imposed oscillatory flow to the jet. Under the hypothesis of high Reynolds number, low Mach number, and assuming that the oscillating flow is of small amplitude with respect to the mean flow, Howe derived an theoretical model describing the vorticity shed at the rim of the aperture and predicting the real and imaginary parts of the conductivity by analytical formulas. However, despite its mathematical rigour, the Howe's model starts from very simplified and limitating hypothesis regarding the shape and the location of the vortex sheet and its convective velocity. Recently, \citet{fabre2018} reviewed the Howe's problem using the Linearized Navier$-$Stokes equations in order to take into accout the effect of the viscosity and the exact shape of the vortex sheet. They show that for $Re \gtrsim 1500$, results are quite independent from the Reynolds number but they result to be quite different from the Howe's ones, above all for intermediate fequencies.

UNTIL HERE IS THE FIRST PART OF THE PART I INTRO: TO MODIFY.

A similar, but more realistic situation is the one in which the flow passes through a hole in a thick plate. Many analytical and semi$-$empirical models can be found in the dedicated literature in order to take into account the effect of the hole's length. 
\citet{bellucci2004use} found out a correction to Howe's model using a momentum balance for a one$-$dimensional flow crossing the hole. \citet{jing2000effect}, instead, improved Bellucci's model used boundary elements method and experimental data in order to interpolate the shape of the vortex sheet.
In order to improve the shape of the vortex sheet, recently \citet{yang2016semi} developed a semi$-$analytical model based on a free space Green formula, showing the inportance to capture the actual shape of the vortex noise. However, they considered the potential inviscid flow combined with a Kutta condition at the leading edge \citep{crighton1985kutta} in order to remove the singularity.
The literature cited until here does not consider the effect of the viscosity on such kind of flow configurations. \citet{eldredge2007numerical} performed incompressible Large Eddy Simulations (LES) to characterize the linear acoustic response of a turbulent flow tangential to both sides of a multi$-$perforated liner. They found a good agreement with the inviscid model by \citet{jing2000effect}, but only when \emph{ad$-$hoc} parameters of this model are selected in order to take into account the thickness of the hole, demonstrating that this model is not robust. \citet{su2015measurements} investigated the effect of linear acoustic oscillations of short and long holes. They used the Unsteady Navier$-$Stokes Equations (URANS) for a compressible low$-$Mach number flow and they found very good agreement with their own experiments but not with the inviscid model by \citet{jing2000effect}, in particular for very long holes respect to their diameters. If the viscosity is not considered, the acoustic boundary layer is not solved, leading to an excessive amount of vorticity and consequently to an overprediction of the whistling properties of the hole, as discussed by \citet{kierkegaard2012simulations}.
%%%%OBJECTIVES
Analyzing the current literature, it seems that the shape of the vortex sheet and the viscosity play a crucial role into the prediction of the acoustic properties of such kind of flow configurations. As far as the viscosity, however, the above cited authors calculated the impedance of circular holes in a turbulent regime (modelling the turbulence with LES or RANS techniques). Moreover, they didn't characterize the effect of the Reynolds number variation.
In this paper, we consider the oscillating ``laminar'' flow passing through a circular aperture in a thick plate, in order to take into accout the effect of both the hole length, the shape of the vortex sheet (with a precise description of the {\em vena contracta} phenomenon) and the variation of the Reynolds number (viscosity). In order to pursue this objectives, following the previous work by \citet{fabre2018} about the zero$-$thickness hole, we use the Linearized Navier$-$Stokes Equations (LNSE). Moreover, as demonstrated by the authors in this previous work, the computation of such kind of flow is notoriously difficult for two reasons. First, the base flow is characterized by a shear layer which remains very steep far away from the aperture, leading to the necessity of a very long computational domain in the axial direction. Secondly, the jet is strongly convectively unstable due to the Kelvin-Helmholtz instability, and it is difficult to design a method capturing both the coupling between the flow rate and the pressure jump, which is relevant to characterize the acoustic properties of the hole, and the spatial growth of perturbations in the axial direction, which can reach huge levels as far as the Reynolds number increases. Following the authors, we adopt the complex mapping of the axial coordinate $x$ in order to obtain suitable results up to $\Rey = 10^4$.\\

Finally, the main objectives of this paper can be summarized as follows.

\begin{itemize}
\item[(i)] First, we describe the base flow characteristics, focusing our attenction on the {\em vena contracta} phenomenon and the intensity of the recirculation bubble, varying the length of the hole.

 \item[(ii)]  Secondly, we investigate the linear response of the jet to harmonic forcing. We compute the impedance varying the length of the hole. We show that because of the thickness of the hole different mechanisms take place and the jet acts like a sound generator rather than a sound dampers. We show that the combined analysis of its real and imaginary parts gives important information about the stability of such kind of flow and the possibility of self$-$sustained oscillation processes \citep{howe1997influence}, which are responsable of the whistling emission.

\item [(iii)] Finally, We discuss the spatial structure of the forced problem.
\end{itemize}

 \section{Problem definition}
%The Howe's problem has been reviewed already in part I...we could talk about the end correction models.
\subsection{Problem definition}

\begin{figure}
$$
\includegraphics[width = .8 \linewidth]{FIGURES/SketchJetNV.pdf}
$$
\caption{Oscillating flow through a circular hole : inviscid modeling} 
\label{fig:Problem+Model}
\end{figure}

The situation considered here is the flow of an incompressible fluid of density $\rho$ and viscosity $\nu$ through a circular hole or radius $R_{hole}$ and area $S_{hole}= \pi R_{hole}^2$ inside a planar plate of thickness $H_{hole}$, connecting an inner domain and an outer domain. We note $Q$ the volumic flux through the hole, defined as follows :

$$
Q = \int_{\cal S} {\bf u}\cdot {\bf n} d S,
$$
where $\cal S$ is any surface traversed by the flow, and $\bf n$ the normal vector at this surface.

We also note $p_{in}$ and $p_{out}$ the pressure levels far away from the hole, in the upstream and downstream domain respectively.

\subsection{Steady flow}

Consider, first, the steady flow. We note $Q_0$, $P_{in}$ and $P_{out}$ the values of the volumic flux, upstream and downstream pressure.

In the inviscid case, a classical model was proposed by Levi-Civita and Prandtl. The model consists of a vortex sheet formed at the hole, surrounding the jet (see figure 1). After several diameters, the jet becomes parallel, but with a radius $R_J$ smaller than that of the hole. We classically call the ratio of surfaces $\alpha = (\pi R_J^2)/(\pi R_h)$ The {\em venna contracta} coefficient. This coefficient is classically associated to the pressure loss across the aperture. Assuming a constant velocity $U_J$ inside the jet, the conservation of flux through the hole leads to 
$Q = \pi R_J^2 U_J = \pi R_h^2 U_M^2$. Applying the Bernoulli theorem along streamlines passing through the hole thus leads to 
\be
[P_{in}-P_{out}] = \frac{\rho U_J^2}{2} = \frac{\alpha^2  \rho U_M^2}{2}
\label{eq:alpha}
\ee
%Therefore, the coefficient $\alpha$ is directly related to the pressure loss through the hole. 
Theoretical calculations by Prandtl and Levi Civita provide the value $\alpha = 0.5$ while experiments indicate typical values in the range $0.61< \alpha< 6.64$ for Large-Reynolds number flows. The global approach used in the sequel will allow to compute rigorously this parameter for arbitrary values of the Reynolds number, assuming laminar flow.

%From a practical point of view, the most important quantity associated to the base flow is the pressure drop $(P_in - P_out)$ and its relation with the volumic flux. This relationship is classically expressed through the so-called {\em venna contracta} coefficient $\alpha$.

%$Q = S_h U_M = S_J U_J$

%Where  $\alpha = S_J/S_h$ is the venna contracta coefficient.

\subsection{Unsteady flow}

We now reconsider the relationship between the pressure jump and the flow rate in the unsteady case, assuming a harmonic time dependance with frequency $\omega$. Hence, upstream and downstream pressure levels and the flow rate are

$$
p_{in} = P_{in} + p'_{in} e^{-i \omega t} ; \quad p_{out} = P_{out} + p'_{out} e^{-i \omega t} ; \quad Q = Q_0 + q' e^{-i \omega t}.
$$

It is convenient to introduce the Strouhal number $\Omega$

$$ 
\Omega = \frac{\omega R}{U_M}.
$$

We are still interested in the relationship between pressure jump and flow rate. This relationship can be characterized by the {\em impedance} of the apperture, defined as 
$$
Z_{app} = \frac{[p_{in}'-  p_{out}']}{q'}.
$$
An alternative definition was introduced by Rayleigh, who defined the {\em conductivity} $K$ of the aperture as follows :

$$
K = \frac{-i \omega \rho q'}{[p_{in}'-  p_{out}']} \equiv \frac{- i \omega \rho}{Z_{app}}  
$$

The advantage of this definition is that it has the physical dimension of a length, and a simple physical interpretation. Namely, one can recognize in this definition a proportionality between the acceleration of the fluid through the aperture and the net force exerted on it. Indeed, this proportionality can be recovered by assuming that the fluid in the vicinity of the hole behaves as a simple solid plug with mass $\rho \pi R_h^2 \ell_{eff}$ oscillating across the hole. Hence, when it is real, $K$ is directly related to the {\em equivalent lengh} of fluid
through $K = A/\ell_{eff}$ with $A = \pi R_h^2$ the area of the aperture. 
%a quantity which appears, for instance, in the classical modeling of the Helmholtz resonator. 
For a hole of zero thickness, Rayleigh gives the theoretical value $\ell_{eff} = 2 R/ \pi$, hence $K = 2R$
while for a very thick plate ($L_h\gg R_h$) one has $\ell_{eff} = L_h + 1.28 R_h$  (to be checked, and give references).

The problem of Rayleigh was reconsidered by Howe, in presence of a base flow, leading to a prediction for the conductivity as function of the Strouhal number. The derivation is extremely technical and not reproduced here. The final result amounts to :
$$
K = 2R ( \gamma - i \delta)
$$
with
\be
\gamma = \frac{
I_1(\Omega^*)^2[1+1/\Omega^*]+(4/\pi^2) e^{2\Omega^*}\cosh(\Omega^*) K_1(\Omega^*)^2[\cosh(\Omega^*)-\sinh(\Omega^*)/\Omega^*]
}
{
I_1(\Omega^*)^2+(4/\pi^2) e^{2\Omega^*}\cosh^2(\Omega^*) K_1(\Omega^*)^2
}
\label{eq:gammaHowe}
\ee

\be
\delta = 
\frac{
(2/\pi \Omega^*) I_1(\Omega^*) K_1(\Omega^*)e^{2\Omega^*}
}
{
I_1(\Omega^*)^2+(4/\pi^2) e^{2\Omega^*}\cosh^2(\Omega^*) K_1(\Omega^*)^2
}
\label{eq:deltaHowe}
\ee

Note that in the calculation of Howe, the Strouhal number is defined as $\Omega^* = \omega R/U$ where $U$ is the velocity of convection of the vorticity along the vortex sheet. Howe argues that $U= U_J/2$, in accordance with the classical modeling of the Kelvin-Helmholtz instability.
Hence the relationship with the Strouhal number used in the present paper is $\Omega^* = \Omega/(2 \alpha)$, and the two definitions are equivalent if $\alpha = 1/2$.

\subsection{Energy flux and instability criteria}

An important property of the Rayleigh conductivity is that it is directly related to the energy flux transmitted to the flow. This was demonstrated by Howe, leading to the following formula :

\be
\left< \Pi_{jet} \right>  = \frac{ |p'_{in}|^2 R \delta}{\rho_0 \omega} 
\quad 
\left( \, = \frac{\rho_0 \omega R \delta | q' |^2 }{|K^2|} \, \right) 
\label{eq:Pienergy}
\ee

\be
\left< \Pi_{jet} \right>  = \left< (p'_{in}-p'_{out}) q'  \right> 
\left( \, = \frac{Z_R | q' |^2 }{2} \, \right) 
\label{eq:Pienergy}
\ee

In the inviscid model of Howe, the term $\delta$ given by Eq. (\ref{eq:deltaHowe}) is always positive, meaning that 
exciting the jet at a given frequency necessitates the provision of energy by an outer system. 
Conversely, a negative $\delta$ means that oscillations of the jet can supply to an outer system, which can be for instance an acoustic resonator.

IMPORTANT: TALK ABOUT THE NYQUIST CRITERIA!!!!

\section{The viscous problem : analysis and numerical method}

\subsection{Parameters and general equations}

The dimensions of the inner and outer domains are assumed to be large compared to the dimensions of the hole, so the only physically meaningful parameter is the aspect ratio of the hole defined as follows :

$$
\beta = \frac{ L_{hole}}{2 R_{hole}}.
$$

Taking the diameter $2 R_{hole} $ as a length scale and the average velocity through the hole  $U_M/\pi R_{hole}^2$  as a velocity scale, we can define a Reynolds number and an aspect ratio :

$$ 
Re = \frac{ 2 R_{hole} U_M}{\nu} \equiv \frac{2 Q }{ \pi R_{hole} \nu} ; \quad
$$

The problem is governed by the Navier-Stokes equations which are written in the following form

\be
\DP{ }{t} \left[\begin{array}{c} {\bf u} \\ 0 \end{array} \right] = 
{\cal NS} \left[\begin{array}{c} {\bf u} \\ p \end{array} \right] =
 \left[\begin{array}{c}
- {\bf u} \cdot \nabla {\bf u} - \nabla p + \nu \Delta {\bf u} \\
 \nabla \cdot {\bf u} 
\end{array} \right] 
\label{eq:NS}
\ee

The flow is further decomposed into a base flow $[{\bf u_0};p_0]$ associated with the mean flux $Q_0$ and a small-amplitude perturbation  $[{\bf u}';p']e^{-i \omega t}$ associated with the oscillating flux $q' e^{-i \omega t}$.
The base flow obeys the steady Navier-Stokes equations ${\cal NS} [{\bf u_0};p_0] = 0$
and the perturbations obeys the linear equation $- i \omega [{\bf u}';0] = {\cal L}_0 [{\bf u}';p']$ where ${\cal L}_0$
is the linearized Navier-Stokes operator about the base flow, defined as follows: 
\be
{\cal L}_0 \left[\begin{array}{c} {\bf u}' \\ p' \end{array} \right] =
 \left[\begin{array}{c}
- \left( {\bf u}_0 \cdot \nabla {\bf u}' +{\bf u}' \cdot \nabla {\bf u}_0 \right) - \nabla p' + \nu \Delta {\bf u}' \\
 \nabla \cdot {\bf u}' 
\end{array} \right] 
\label{eq:NS}
\ee

 The detailed expression of these operators will be given below. The flow obviously verifies no-slip conditions ${\bf u} = {\bf 0}$ on the wall (noted $\Gamma_w$),  and symmetry conditions at the axis (noted $\Gamma_{ax}$). The treatment of the geometry and boundary conditions in the upstream and downstream domain require special attention and are detailed bellow.

\subsection{Upstream domain}

As sketched in figure 1, the upstream domain is expected to originate from an upstream container of large dimension, and sufficiently far away from the hole the flow is assumed to be radially convergent. However, in the numerical implementation, it is required to specify a given geometry for this upstream domain. Here, we have chosen to assume that the upstream region is a closed cavity of rectangular cross-section, with radius $R_{cav}$ and length $L_{cav}$. The volumic flux condition is imposed by assuming that both the base-flow and the perturbation velocities are constant along the bottom of the cavity, noted $\Gamma_{in}$

\be
 {\bf u}_0 = - Q_0/S_{cav} {\vec n} ; \quad {\bf u'} = - q'/S_{cav} {\vec n} \quad {\mbox at } \Gamma_{in}
\ee
where $S_{cav}= \pi R_{cav}^2$ is the area of the bottom wall and ${\bf n}$ is the outward normal vector.
The pressure levels $P_{in}$ and $p'_{in}$, which are required for the calculation of the mean pressure loss and the conductivity, are computed by averaging along the inlet boundary :
\be
 {P}_{in} = 1/S_{cav} \int_{\Gamma_{in}} P_0 2 \pi r dr ; \quad
  {p'}_{in} = 1/S_{cav} \int_{\Gamma_{in}} p' 2 \pi r dr.
\ee
It was verified that if the dimensions of the cavity are large enough, the pressure is effectively nearly constant along the inlet boundary $\Gamma_{in}$.

At the lateral wall of the cavity, noted $\Gamma_{lat}$, the physically relevant condition should be a no-slip condition. However, as the location of this wall is not really relevant, and in order to avoid the development of a boundary layer, 
we preferred to impose a stress-free condition, namely  
\be
 {\bf u} \cdot {\bf n} = 0 ; \quad \DP{({\bf u} \cdot {\bf x})}{r} = 0 \quad \mbox{  at  } \Gamma_{lat},
 \ee
which applies for both the base flow and the perturbation.

In the sequel we set the dimensions of the upstream cavity as $L_{cav} = R_{cav} = 10 R_{hole}$,
and verified that these values are large enough for the results to be insensible to these parameters.

\subsection{Downstream domain : boundary conditions and change of coordinates}

The treatment of the outlet conditions is a delicate point here, as the structure of both the base flow and the perturbation lead to some difficulties, especially when the Reynolds number becomes large. These difficulties led us to use an original method which consists of using a change of variables from a computational domain defined with $[X,R]$ coordinates to the physical domain with $[x,r]$ coordinates.

The first motivation for this method comes from the structure of the base flow. In effect, the laminar, steady solution 
 $[u_0,p_0]$ is characterized by a boundary layer which remains very sharp at large distances from the hole. More specifically, the boundary layer thickness $\delta$ scales as  $\delta(x) \approx \sqrt{\nu x/U_J}\approx Re^{-1/2} x^{1/2}$. Of course, in a real, High-Reynolds jet, the boundary layer thickness grows much faster because of turbulence. However, the global method used here requires computation of a laminar base flow  so we have to work around this issue. The solution is to use a change of coordinates $x = G_x(X)$ which stretches the outer domain from $X\in [0,X_{max}]$ to $[0,x_{max}]$, where the bound of the computational $X_{max}$ is relatively small, while the corresponding $x_{max} = x(X_{max})$ is several orders of magnitude larger.

The second issue is due to the structure of the perturbation. In effect, the jet is spatially unstable, and thus perturbations are convectively amplified in the downstream perturbation, and far away from the hole, they reach levels several orders of magnitude larger than the levels in the vicinity of the hole. As soon as the ratio between minimum and maximum levels of the perturbation becomes of the order of the numerical round-off error 
($10^{-15}$ using double-precision) this issue leads to the impossibility to compute accurately the structure of the perturbation in the vicinity of the whole, which is mostly relevant for the computation of the conductivity. In practice, when solving the problem in terms of the physical coordinates, this issue limits the validity of the results to $Re \leq 800$.

To detail the origin of the problem and introduce the idea used to overcome it, let us review the classical modeling of the Kelvin-Helmholtz instability for a planar shear layer of zero thickness in the inviscid case. The derivation can be found in any classical textbook on hydrodynamical stability (e.g. Shandrasekar, Drazin \& Reid, Charru, etc..). 
Consider as a base flow a shear layer separating two regions of constant axial velocity, namely $u= U$ for $y<0$ and $u=0$ for $y>0$. Now assume that the perturbation consists of a displacement of the shear layer with the form
\be 
y = \eta \approx e^{i k x - i\omega t} 
\label{eq:etaKH}
\ee
and assume a similar modal expansion for the velocity potential in the upper and lower region. Matching the two regions at the interface leads to the classical dispersion relation :
\be 
c \equiv \frac{\omega}{k} = \frac{1+i}{2} U
\label{eq:cKH}
\ee 
In a temporal stability framework, this means that a perturbation with real wavenumber $k$ will be convected
downstream with a phase velocity $U/2$ and temporally amplified with a growth rate $U k/2$. On the other hand, in a spatial stability framework ($\omega$ real, $k$ complex), which is more relevant here, this means that any perturbation will be spatially amplified downstream and will diverge at $x\rightarrow +\infty$. This divergence forbids a global resolution of the function $\eta(x,t)$ when the spatial variable $x$ is {\em real}. However, the problem disappears if we consider an analytical continuation of the function $\eta(x,t)$ with a {\em complex variable} $x$. More specifically, as $\arg(k) = -\pi/4$, the function $\eta(x,t)$ becomes convergent as soon as $|x| \rightarrow \infty$ in a direction of the complex plane verifying $\pi/4 < \arg(x) 5\pi/4$.

Thus, this study of the simple, inviscid, planar shear layer suggests a possible way to resolve the problem for the present case of a viscous, cylindrical shear layer : using a { \em  complex coordinate change} which maps the numerical $X \in [0;X_{max}]$ (with $X$ real) into a path for the physical $x$ coordinate which enters the complex plane and follows a direction where the perturbation is spatially damped.

Combining both ideas, namely stretching and complex deformation, we have used the following mapping function from numerical coordinate $X$ to physical coordinate $x$ :

\be
\begin{array}{rcll}
x = G_x(X) &=& \frac{X}{\left[1-X^2/L_s^2 \right]^2} \left[ 1 + i \gamma_c \tanh \left(\frac{X}{L_c}\right)^2  \right]  & \mbox{ for } X>0, \\
	& = & X & \mbox{ for } X<0.
\end{array}
\label{eq:mapX}
\ee
This choice has the following properties. First, it leaves the axial coordinate unchanged in the upstream domain and inside the hole $(x<0)$. Secondly, the numerical and spatial coordinates are also almost identical in the region where the jet emerges from the hole (namely  $x \leq L_c$ and $x \leq L_s$). Thirdly, as $X$ approaches the upper bound of the numerical domain $X_{max}$, and complex, the 
physical variable tends to $x_{max}= G_x(X_{max}$, which is very large as soon as $L_c$ is close to $X_{max}$
(with $L_s > X_{max}$), and complex, with argument $\tan^{-1} (\gamma_c)$, as soon as $\gamma_c \neq 0$.

Finally, although the issue is less crucial for the axial coordinate, we also used a change of coordinates $R(r)$ to stretch the radial coordinate from $R \in [0,R_{max}]$ to $r \in [0,r_{max}]$. Here there is no point in using a complex deformation, so we used the following mapping function :

\be
\begin{array}{rcll}
r= G_r(R) &=& 
R_{s1} + \displaystyle \frac{R-R_{s1}}{\left[1-(R-R_{s1})^2/(R_{s2}-R_{s1})^2 \right]^2}  & \mbox{ for } X>0 \mbox{ and } R>R_{s1}, \\
	& = & R & \mbox{  otherwise }
\end{array}
\label{eq:mapR}
\ee

This function leaves the radial coordinate unchanged in the upstream domain an in the region $r<R_{s1}$ where the jet develops, but it stretches the limit of the domain from $R_{max}$ to $r_{max} = G_r(R_{max})$ which is very
large as soon as $R_{s2}$ is close to $R_{max}$ (with $r_{s2} > R_{max}$).

Having explained this change of coordinates, it remains to specify the boundary conditions to be used at the outer limits of the computational domain. For the resolution of the Navier-Stokes equation in an open domain, the physically relevant boundary condition $[{\bf u}; p] \rightarrow [0; p_{out}]$ as $(x,r) \rightarrow \infty$   
are often replaced by setting the traction (or pseudo-stress) $-p {\bf n} + \nu \nabla {\bf u} \cdot {\bf n} $ to zero
at the outlet boundaries. An alternative choice is to nullify the stress $-p {\bf n} + \nu ( \nabla {\bf u} + \nabla {\bf u}^T) \cdot {\bf n} $. In the present case, we have chosen to impose a zero-traction condition at the boundaries $x_{max},r_{max}$, for both the base flow and the perturbation. A zero-stress condition was also tried, leading to similar results but convergence difficulties when computing the base flow. Note that the significance of

Note that the use of complex coordinate mapping for linear problems involving a single spatial coordinate is customary in stability studies, and mathematical theorems are available to justify how to chose the integration contour as function of the singularities of the problem (e.g. Bender \& Orzag). On the other hand, its use for a nonlinear problem (i.e. computation of the base flow) involving two spatial coordinates is totally new to our knowledge. The validity of the method is not justified by rigourous mathematical argument, but only by the fact that it effectively works and that the results are independent upon the parameters of the mapping. A few test showing that it is effectively the case, for both the base flow and the perturbation, are given in appendix A.

For most results presented in the present paper, the following choice of parameters was used:

$$
R_{cav}=L_{cav}=10 ; R_{max} = X_{max} = 15; X_s = 16 ; X_c = 2.5 ; \gamma_c = 0.3 ; R_{s1} = 5;
R_{s2} = 16.
$$

In terms of the physical coordinates, this means that the outer boundaries are located at
$x_{max} = 1022+306i ; r_{max} = 337$.

%This choice of functions $G_x, G_r$ they are continuous and continuously derivable across $X=0$ and $R=R_{m1}$, and that they map the infinite outer domain $[x,r]$ into a finite one $[X,R] \in [0,L_{m}] \times [0,R_{m2}]$. Note that the mapping is the identity function inside the cavity and the aperture ($X<0$), so that the dimensions $[L_{cav},R_{cav},L_{hole}]$ are the same in the physical and mapped coordinates. The mapping in the radial coordinate is also chosen so that the stretching only occurs for $R>R_{m1}$, which has obviously to be taken as $R_{m1}>R_{hole}$.

\subsection{Numerical implementation}

\begin{figure}
$$
\includegraphics[width = .8 \linewidth]{FIGURES/Mesh.eps}
$$
\caption{Example of computational mesh with dimensions in mapped coordinates and nomenclature of boundaries.} 
\label{fig:Mesh}
\end{figure}

The numerical resolution of the problem was performed with a finite element method,  using the FreeFem++ software. An example of computational mesh, in the $[X,R]$ coordinates, is shown in figure 2. Meshes were generated using Delaunay-Voronoi triangulation of the domain, and subsequently refined locally to fit the steep gradients of both the base flow and the perturbation using the adaptmesh command provided by the Freefem++ software.

For resolution, the Navier-Stokes equations have first to be expressed in terms of the mapped coordinates. For this purpose, the spatial derivatives have to be modified as follows :

\be
\DP{}{x} \equiv H_x \DP{}{X}  \quad \mbox{ with } H_x =   \frac{1}{G_x'};
\ee
\be
\DP{}{r} \equiv H_r \DP{}{R}  \quad \mbox{ with } H_r =   \frac{1}{G_r'}.
\ee

The incompressible Navier-Stokes operator thus have the following form :

\be
{\cal NS} \left[\begin{array}{c} u_x \\ u_r  \\ p \end{array} \right] =
 \left[\begin{array}{c}
- (u_x  H_x \partial_X u_x + u_r H_r \partial_R u_x) - H_x \partial_X p 
+ \nu \left[ H_x \partial_X ( H_x \partial_X u_x ) + H_r/r\partial_R ( r H_r \partial_r u_x ) \right]
\\
- (u_x  H_x \partial_X u_r + u_r H_r \partial_R u_r) - H_r \partial_R p 
+ \nu \left[ H_x \partial_X ( H_x \partial_X u_r ) - u_r/r^2 + H_r/r\partial_R ( r H_r \partial_r u_r ) \right]
\\
H_x \partial_X u_x + H_r/r \partial_R (r u_r) 
\end{array} \right] 
\label{eq:NS}
\ee

to solve these equations using finite element method, we classically multiply by test functions 
$[u_x^*, u_r^*,p^*]$ and integrate over the domain. Note that this integration has to be done over the physical domain, so in terms of the numerical variables the elementary volume of integration is $dV = r dr dx = (H_x H_r)^{-1} r dR dX$ .
After integration by parts of the pressure gradient and Laplacian terms, we are thus lead to the following weak formulation:

\be
\begin{array}{l}
\displaystyle
- \int \left[ 
u_x^* \left( u_x  H_x \partial_X u_x + u_r H_r \partial_R u_x \right) 
+ u_r^* \left( u_x  H_x \partial_X u_r + u_r H_r \partial_R u_r \right) 
\right] dV
\\
\displaystyle
+ \int \left[ 
p \left( H_x \partial_X u_x^* + H_r \partial_R u_r^* + u_r^*/r \right) 
-
p^* \left( H_x \partial_X u_x + H_r \partial_R u_r + u_r/r \right) 
\right] dV
\\
\displaystyle
- \int \left[ 
H_x^2 \partial_X u_x \partial_X u_x^* +H_r^2 \partial_R u_x \partial_R u_x^*
\right] dV
\\
\displaystyle
- \int \left[ 
H_x^2 \partial_X u_r \partial_X u_r^* +H_r^2 \partial_R u_r \partial_R u_r^*
+ u_r u_r^*/r^2
\right] dV
\\
= 0.
\end{array}
\ee

Note that with this formulation, the no-traction boundary conditions at the outlet boundary, as well as the symmetry condition at the axis and the zero tangential stress condition at the lateral wall of the cavity are automatically satisfied thanks to the integration by parts. The other boundary conditions are imposed by penalization.

Following a now customary approach, the computation of the base flow is done using a standart Newton method. The algorithm is as follows :
\begin{description}
\item[$(i)$] Start from a guess flow field $[{\bf u}^g;p^g]$.
\item[$(ii)$] Solve the linear system ${\cal NS}[{\bf u}^g,p^g] + {\cal L}_g [\delta {\bf u}, \delta p]$ where $ {\cal L}_g$ is the linearized Navier-Stokes operator around the guess field.
\item[$(iii)$] Obtain a better guess as $ [{\bf u},p] = [{\bf u}^g,p^g] +  [\delta {\bf u}, \delta p]$.
\item[$(iv)$] Repeat until convergence.
\end{description}
The inversion at step $(ii)$ is done with the UMFPACK64 library.

In practice, at point $(i)$ the guess field is generally taken as the base flow computed at a lower value of the Reynolds number. The whole algorithm is thus repeated for increasing values of the Reynolds number to generate a family of base flow. The mesh refinement is applied at each step, so that the refinement, and the number of points of the mesh, increases with the Reynolds number. Note that when using the complex mapping method described above, the radius of convergence of the Newton algorithm seems to be smaller than in the standard case.  This means that the Reynolds number has to be increased moderately between successive base flow computations.

The computation of the perturbations due to harmonic forcing $[u_x',u_r',p']$ is done using the same linear solver UMFPACK64. Note that the structure may involve steeper gradients compared to the base flow. To capture this, the problem is first solved on the refined mesh computed during the base flow computation. The mesh is subsequently refined a second time through the adaptmesh command, and the base flow and the perturbation are finally recomputed on this better mesh.

%\clearpage

\section{The nonzero thickness case}

We will now consider the case where the jet passes through a hole in a plate with finite thickness, characterized by an aspect ratio $\beta = L/D$. We particularly consider the cases $\beta= 0.3, 0.1 and 1$.

\subsection{Base flows : study of the recirculation region}

\begin{figure}
$$
\begin{array}{cc}
\includegraphics[width=.4\linewidth]{FIGURES/Recirculation_Ep03_Re500.eps} &
\includegraphics[width=.4\linewidth]{FIGURES/Recirculation_Ep03_Re600.eps} \\ 
Re = 500 &  Re = 600 \\
\includegraphics[width=.4\linewidth]{FIGURES/Recirculation_Ep03_Re800.eps} &
\includegraphics[width=.4\linewidth]{FIGURES/Recirculation_Ep03_Re1500.eps} \\
Re = 800 &  Re = 1500
\end{array}
$$
\caption{ Structure of the recirculation region. Colors levels : axial velocity. Black lines : streamfunction.}
\label{fig:Recirc}
\end{figure}

In the case of a hole with finite thickness, the general structure of the flow is similar to the case previously plotted in figure \ref{fig:chbase_C}, with an upstream radially converging flow turning into an almost parallel jet. However, an important feature is the occurence of a recirculation region within the thickness of the hole. This point is illustrated in figure \ref{fig:Recirc} which displays the structure of the flow in the close vicinity of the aperture, for $\beta = 0.3$. For $Re = 500$, the recirculation region takes the form of a narrow bubble trapped close to the upstream corner. As the Reynolds is increased, this bubble expands towards the downstream corner, until it opens up and involves an entraiment of the outer fluid which enters inside the thickness of the plate. Note that for $Re = 800$, the recirculation region still contains a bubble of closed streamlines, but detached from the wall. Further on, this bubble disappears and for $Re = 1500$ the recirculation region is fully open.

\begin{figure}
$$
\includegraphics[width=.7\linewidth]{FIGURES/Recirculation.eps}
$$
\caption{ Intensity of the recirculation flow inside the hole as function of $Re$, 
for $\beta = 0.1$ (dots),  $0.3$ (dashes),  and $1$ (long dashes). }
\label{fig:Umax}
\end{figure}

The intensity of the recirculation region can be characterized by the maximum level of negative velocity within the thickness of the hole, namely $U_{max} = max (-u_{x0})$. This quantity is plotted in figure \ref{fig:Umax} as function of the Reynolds number for $\beta = 0.1, 0.3$ and $1$. It is observed that in all cases, the recirculation region shows up for $Re \approx 400$. The intensity of the recirculation region first grows as the trapped bubble extends to reach the downstream corner, and then decreases as it turns into a fully open one. Not surprisingly, the intensity is larger in the case of a thicker hole, as the bubble is able to extend over a longer region.

\begin{figure}
$$
\includegraphics[width=.7\linewidth]{FIGURES/Alpha_VennaContracta.eps}
$$
\caption{ Vena contracta coefficient as function of $Re$, for $H_h/D_h = 0$ (full line), 
 $H_h/D_h = 0.1$ (dots),  $H_h/D_h = 0.3$ (dashes),  $H_h/D_h = 1$ (long dashes). }
\label{fig:alpha}
\end{figure}

To end up the description of the base flow, we document on figure \ref{fig:alpha} the venna contracta coefficient
deduced from the pressure drop computed from the base flows. It is found that for $Re \approx 10^4$ the venna contracta coefficient reaches a value close to 0.61 in all cases, again in accordance with known experimental results. Note that for the thicker case ($\beta=1$) $\alpha$ is lower than in the other cases for $Re \lesssim 100$, 
meaning that the pressure drop is weaker, but it is maximal for $Re \approx 2000$, a value corresponding approximately to the transition from a closed to an open recirculation region.

%\clearpage
\subsection{Unsteady flow}

\subsubsection{Case $\beta = 0.3$}

%\begin{figure}
%$$
%\includegraphics[width=.4\linewidth]{FIGURES/Cond_Ep03.eps}
%\includegraphics[width=.4\linewidth]{FIGURES/Cond_Ep03Z.eps}
%$$
%\caption{ Real part $\Gamma$ (thick) and Imaginary part $\Delta$ (thin) of the Rayleigh conductivity 
%for a hole of thickness $\beta = 0.3$, for $Re = 100$ ($\cdot \cdot \cdot$), $Re = 500$ (-- --),
%$Re = 800$ (-- $\cdot$ -- ),  $Re = 1500$ (---  ---),  and
%$Re = 3000$ (--- $\cdot$ ---). 
%Plot $(a)$ displays the range $\Omega = [0-5]$, and plot $(b)$ the range $\Omega = [5-15]$ with a different scale for $\gamma$ and $\delta$.}
%\label{fig:Cond03}
%\end{figure}

\begin{figure}
$$
\includegraphics[width=.8\linewidth]{FIGURES/Ep03_RL.eps}
$$
\caption{ Real part $R$ (thick) and Imaginary part $L$ (thin) of the impedance
for a hole of thickness $\beta = 0.3$, for %$Re = 100$ ($\cdot \cdot \cdot$), 
$Re = 500$ (-- --, black),
$Re = 800$ (-- $\cdot$ --, red ),  $Re = 1500$ (---  ---, green),  and
$Re = 3000$ (--- $\cdot$ ---, blue). 
%Plot $(a)$ displays the range $\Omega = [0-5]$, and plot $(b)$ the range $\Omega = [5-15]$ with a different scale for $\gamma$ and $\delta$.
}
\label{fig:Cond03}
\end{figure}

\begin{figure}
$$
\begin{array}{cc}
\includegraphics[width=.47\linewidth]{FIGURES/SR_03_1500_1_33.eps} &
\includegraphics[width=.47\linewidth]{FIGURES/SR_03_1500_2_24.eps} \\
(a) \quad \Omega = 1.33, \, \gamma = 0.799,\, \delta =0.924 & 
(b) \quad \Omega = 2.24,  \, \gamma = 0.904,\, \delta =-0.219 \\
\includegraphics[width=.47\linewidth]{FIGURES/SR_03_1500_5_41.eps} &
\includegraphics[width=.47\linewidth]{FIGURES/SR_03_1500_8_15.eps} \\
(c) \quad \Omega = 5.41,  \, \gamma = 0.689,\, \delta =0.122 & 
(d) \quad \Omega = 8.15,  \, \gamma = 0.715,\, \delta =-0.0069
\end{array}
$$
\caption{ Structure of the unsteady flow for $\beta = 0.3$ and $Re = 1500$, for different values of $\Omega$.
Real part of the pressure component (color levels) and pseudo-streamlines. 
}
\label{fig:Struct03}
\end{figure}

The most important quantity associated to the unsteady flow is the conductivity $K = 2R (\gamma-i \delta)$. This quantity is plotted as function of the frequency in figure \ref{fig:Cond03} for Reynolds ranging from 500 to 3000.
For $Re = 500$, $\gamma$ and $\delta$ are both positive and are close to the zero-thickness case plotted in figure \ref{fig:Cond0}. For $Re= 800$, one observes that the imaginary part $\delta$ becomes negative for 
$\Omega \approx 2.2$. As explained in section 2, this property is directly related to a possible instability. As the Reynolds number is increased further, one observes that the region of negative $\delta$ gets larger and reaches larger values. Note also that the negative, minimum value of $\delta$ is associated to a maximum of the real part $\gamma$. 
Figure \ref{fig:Cond03}$(b)$ magnifies the range $\Omega = [5-15]$ and shows that a second region of instability shows up for $Re \gtrsim 1500$, with higher frequencies in the range $\Omega \approx 9$. This is again associated with a maximum of the real part $\gamma$.

To explain these trends, and in particular the possibility for negative $\delta$, we detail the structure of the flow perturbation for four values the frequency, corresponding respectively to two positive maxima ($a$ and $c$)
 and two negative minima  ($b$ and $d$) of $\delta$. We recall that these structure are computed with the complex mapping method, so the details are not significant for $x \gtrsim 2$. However, several significant points can be noted. First, it is clear that in the unstable cases ($b$ and $d$) the pressure levels are negative in the upstream region, while they are positive in the stable cases ($a$ and $c$). Recalling that the pressure level far away in the downstream region is set to zero, this means that in the unstable cases the fluctuating flow goes against the pressure gradient. A second salient feature can be noted when looking at the streamlines in the vicinity
 of the lower corner. In the unstable cases ($b$ and $d$) the fluctuating flow emerging from the hole goes up along the outer wall, although in the stable cases stable cases ($a$ and $c$) the opposite happens, meaning that the fluid coming from along the wall is entrained within the jet.

\subsubsection{Case $\beta = 1$}

%\begin{figure}
%$$
%\begin{array}{cc}
%\includegraphics[width=.4\linewidth]{FIGURES/Cond_Ep1.eps}
%\includegraphics[width=.4\linewidth]{FIGURES/Z_Ep1.eps}
%\end{array}
%$$
%\caption{ Conductivity and impedance for a hole with thickness $\beta = 1$ :  
%$(a)$ Real part $\gamma$ (thick) and Imaginary part $\delta$ (thin) of the Rayleigh conductivity for 
%$Re = 500$ (-- --), $Re = 800$ (--$\cdot$--), $Re = 1200$ ( --$ \cdot \cdot$-- ).
%$(b)$ Real (thick) and Imaginary (thin)  parts  of the Impedance for $Re = 1500$ (---  ---)
%and  $Re = 3000$ (---$\cdot$---).
%}
%\label{fig:Cond1}
%\end{figure}

\begin{figure}
$$
\begin{array}{cc}
\includegraphics[width=.8\linewidth]{FIGURES/Ep1_RL.eps}
\end{array}
$$
\caption{ 
$(a)$ Real part $R$ (thick) and Imaginary part $L$ (thin) of the impedance for a hole of thickness
$\beta = 1$, for $Re = 800$ (--$\cdot$--, red), $Re = 1200$ ( --$ \cdot \cdot$--, magenta) and $Re = 1500$ (---  ---, green).
}
\label{fig:Cond1}
\end{figure}

We now consider the case of a thicker hole with aspect ratio $\beta = 1$. Figure \ref{fig:Cond1}$(a)$ plots the conductivity for $Re$ from 500 to 1200. As in the previous case, one can see the existence of several frequency intervals where the imaginary part $\delta$ becomes negative. For instance, for $Re = 800$ this occurs for $\Omega \approx 2.5$ while for $Re = 1200$ there are two intervals around 2.1 and 4.5. One can also notice that the real part $\gamma$ experiences much larger oscillations than in the previous case.

As the Reynolds number is increased, both real and imaginary parts of the conductivity reach very large value, so it becomes more appropriate to plot the impedance $Z_{app} = -i \omega/K$ instead of the conductivity. Figure \ref{fig:Cond1}$(b)$ plots this quantity as function of the frequency for $Re = 1500$ and $3000$.
Recall that the criterion $\delta<0$ leading to possible instability is equivalent to $Z_r<0$, which occurs in at least three intervals in the range of frequencies considered. Another important result which can be seen in this figure is the existence of true zeros of the impedance. This happens in particular for $Re = 1500$ at $\Omega \approx 2.07$. This property indicates the existence of a linear perturbation with nonzero flow rate but zero pressure jump across the aperture. So, the jet may be subject to self-sustained oscillation even in the absence of an acoustic resonator located upstream. This indicates the possibility of a purely hydrodynamical instability. This fact will be confirmed in section 6.

\begin{figure}
$$
\begin{array}{cc}
\includegraphics[width=.47\linewidth]{FIGURES/SR_1_1200_2_25.eps} &
\includegraphics[width=.47\linewidth]{FIGURES/SR_1_1200_4_55.eps} \\
(a) \quad Re = 1200, \, \Omega = 2.25, \, \gamma = 0.544,\, \delta =-0.161 & 
(b) \quad Re = 1200, \, \Omega = 4.45,  \, \gamma = 0.0.449,\, \delta =-0.038 \\
\includegraphics[width=.47\linewidth]{FIGURES/SR_1_1500_08.eps} &
\includegraphics[width=.47\linewidth]{FIGURES/SR_1_1500_2_07.eps} \\
(c) \quad Re = 1500, \, \Omega = 0.8,  \, \gamma = 0.380,\, \delta =-0.019 & 
(d) \quad Re = 1500, \, \Omega = 2.07,  \, \gamma = -15.637,\, \delta =-6.099
\end{array}
$$
\caption{ Structure of the unsteady flow for $\beta = 0.3$ and $Re = 1500$, for different values of $\Omega$.
The color levels indicate the real part of the radial velocity components, while the thin lines indicate the real part of the pressure component (dashed for negative levels). The thick dotted line indicate the recirculation region. 
Plot $(d)$ corresponds to the minimum impedance for $Re=1500$, namely $Z = -0.0224+0.0574i$.
}
\label{fig:Struct1}
\end{figure}

Finally, figure \ref{fig:Struct1} depicts the structure of the oscillating flow for the two first minima of $\delta$ for $Re = 1200$ (plots $a$ and $b$). One can observe that these perturbations display respectively 4 and 6 structures within the thickness of the hole. Note that a minimum of $\delta$ also exists for $Re =1200$ at $\Omega \approx 1$, but the value of $\delta$ remains positive. For $Re= 1500$, this first minimum becomes negative, and the
corresponding structure is plotted in figure \ref{fig:Struct1}$(c)$. As expected, it displays only two vortical structures within the thickness of the hole. Finally, figure \ref{fig:Struct1}$(d)$ displays the case corresponding to the minimum of $|Z_{app}|$ for $Re = 1500$. 
The structure is much similar to the case plotted in \ref{fig:Struct1}$(a)$, not surprisingly because the frequency is close.

\subsubsection{Case $\beta = 0.1$}

%\begin{figure}
%$$
%\includegraphics[width=.4\linewidth]{FIGURES/Cond_Ep01.eps}
%\includegraphics[width=.4\linewidth]{FIGURES/Cond_Ep01Z.eps}
%$$
%\caption{ Real part $\Gamma$ (thick) and Imaginary part $\Delta$ (thin) of the Rayleigh conductivity 
%for a hole of thickness $\beta = 0.1$, for $Re = 500$ (-- --),
%$Re = 800$ ($\cdot$ -- $\cdot$), $Re = 1500$ (---  ---), $Re = 3000$ (------).
%The right plot displays $\Delta$ in the range $5< \Omega < 15$, with a magnified scale allowing to show the region where it becomes negative.
%NB THE CASES WITH RE = 4500 ARE SPURIOUS.
%}
%\label{fig:Cond01}
%\end{figure}

\begin{figure}
$$
\includegraphics[width=.8\linewidth]{FIGURES/Ep01_RL.eps}
$$
\caption{ Real part $R$ (thick) and Imaginary part $L$ (thin) of the impedance
for a hole of thickness $\beta = 0.1$, for $Re = 800$ ($\cdot$ -- $\cdot$), 
$Re = 1500$ (---  ---), $Re = 3000$ (--- - ---).
}
\label{fig:Cond01}
\end{figure}

As a third case, we consider a thinner plate with $\beta = 0.1$. The conductivities are plotted in figure 
\ref{fig:Cond01}. We note that a negative minimum of $\delta$ is also observed but it only occurs for 
$Re \gtrsim 3000$ and at larger frequencies than in the previous cases, namely $\Omega = 8.2$.

Comparing the three previous cases, it is interesting to note that the minimum frequency where an negative $\delta$ can occur is inversely proportional to the thickness. Indeed, defining the Strouhal number based on the thickness
leads to $St = L \omega /U_M \approx 1 $  in the three cases. 
Note that the fact that the frequency of the whistling tone is inversely proportional to the thickness was already noted by Bouasse.

\subsubsection{Case of a rounded hole}

\begin{figure}
$$
\includegraphics[width=.7\linewidth]{FIGURES/CBRounded_3000_Complex.eps}
$$
\caption{Base flow for a rounded hole of thickness $\beta = 0.3$, with $Re = 3000$ 
(in numerical coordinates $(X,R)$, with complex mapping). 
}
\label{fig:chbase_C}
\end{figure}

The previous cases indicate that the source of instability is linked to the existence of a recirculation region, and this feature is particularly favored by the existence of sharp corners upstream and downstream of the hole. To support this statement, we investigated the case of a rounded hole. The aspect ratio is taken as $\beta=0.3$, but 
the shape of the hole is taken as a semicircle. Figure \ref{fig:chbase_C} displays the structure of the base flow in this case, with $Re = 3000$. It can be noted that the flow effectively detaches from the wall while passing through the hole leading to an open recirculation region. However, this recirculation region is much weaker than that observed in the case of a hole with sharp edge. Clearly, the absence of a sharp corner leads to a much smoother recirculation region, and therefore much less potential for instability.

\begin{figure}
$$
\includegraphics[width=.7\linewidth]{FIGURES/Rounded_RL.eps}
$$
\caption{ Real part $R$ (thick) and Imaginary part $L$ (thin) of the impedance 
for a rounded hole with thickness $\beta=0.3$, with
$Re = 500$ ($\cdot$ -- $\cdot$), $Re = 1500$ (---  ---), $Re = 3000$ (--- - ---).
Plot $(b)$ is a magnification of the range where $\delta$ becomes negative.
}
\label{fig:CondR}
\end{figure}

Figure \ref{fig:CondR} displays the conductivity for the case of a rounded hole, and suppports this conclusion. Indeed, a negative minimum of $\delta$ is effectively observed for $\Omega \approx 3$, which is about in the same range than for the sharp corner with the same aspect ratio, but this happens at much larger values of the Reynolds number, namely $Re = 3000$.

\section{Parametric study}

\begin{figure}
$$
\includegraphics[width=.7\linewidth]{FIGURES/Seuils_Re.eps}
$$
\caption{ Thresholds for the onset of acoustic instability (A1 to A4) and of hydrodynamical instability (I1 and I2).
}
\label{fig:ThresholdsRe}
\end{figure}

\begin{figure}
$$
\includegraphics[width=.7\linewidth]{FIGURES/Seuils_Om.eps}
$$
\caption{ Frequencies corresponding to acoustic instability (A1 to A4) and of hydrodynamical instability (I1 and I2).
}
\label{fig:ThresholdsRe}
\end{figure}

\section{Conclusions}

\appendix
\section{Numerical validations}
Only the mesh and mayle the parameter $L_M$

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\bibliographystyle{jfm}

\bibliography{OneHole_PartII_zerothickness}

\end{document}

### 2018-10-02 CASES_DEVELOPMENT/Vessel/SCRIPT_vessel.m

@@ -1,109 +1,0 @@
-close all;
-run('../../SOURCES_MATLAB/SF_Start.m');verbosity=10;
-system('mkdir FIGURES');
-figureformat = 'png';
-
-%% CHAPTER 1 : flat surface, free condition
-gamma=0.002;
-rhog=1;
-R = 1;
-L =2;
-
-
-density=100;
- %creation of an initial mesh 
- 
-ffmesh = SF_Mesh('MeshInit_Vessel.edp','Params',[L density]);
-ffmesh = SF_Mesh_Deform(ffmesh,'P',0,'gamma',gamma,'rhog',rhog,'typestart','pined','typeend','axis');
-%figure();plot(ffmesh.xsurf,ffmesh.ysurf);hold on;quiver(ffmesh.xsurf,ffmesh.ysurf,ffmesh.N0r,ffmesh.N0z); % to plot normal vectors
- 
-
-disp('###first test : flat surface, free condition')
-
-
-[evm1,emm1] =  SF_Stability(ffmesh,'nev',10,'m',1,'shift',2.1i,'typestart','angleV','typeend','axis');
-% NB with this value of the shift the modes number n=1,2,3 will be found with index (2,1,3)
-
-evTheory = [1.3606    2.3737    3.1274]; % see script Analytical solution
-error1 = abs(imag(evm1(2))/evTheory(1)-1)+abs(imag(evm1(1))/evTheory(2)-1)+abs(imag(evm1(3))/evTheory(3)-1)
-
-figure(1);
-plot(imag(evm1),0*real(evm1),'r+');hold on;
-legend('flat, free');
-
-figure(2);suptitle('m=1 sloshing modes : Horizontal surface, free condition');hold on;
-subplot(1,3,1);
-plotFF(emm1(2),'phi.im','title',{'Mode (m,n)= (1,1)',['freq = ',num2str(imag(evm1(2)))]},'symmetry','YA');hold on;plotFF_ETA(emm1(2),'symmetry','YA');
-subplot(1,3,2);
-plotFF(emm1(1),'phi.im','title',{'Mode (m,n)= (1,2)',['freq = ',num2str(imag(evm1(1)))]},'symmetry','YA');hold on;plotFF_ETA(emm1(1),'symmetry','YA');
-subplot(1,3,3);
[…]

### 2018-10-02 CASES_DEVELOPMENT/WhistlingHole/TESTS_Eigenvalues.m

@@ -1,53 +1,0 @@
-% This script computes eigenvalues for a whistling jet through a hole with beta = 1.
-
-% NOT WORKING YET, BUT THIS IS TO DEMONSTRATE HOW IT (doesn't) WORK...
-
-
-
-run('../../SOURCES_MATLAB/SF_Start.m');
-verbosity=10;
-
-
-%% chi = 1
-
-chi = 1;
-Re = 1500;
-if(exist('bf'))
-    bf = SF_BaseFlow(bf,'Re',Re);
-else
-    bf = SmartMesh_Hole(chi);
-end
-
-% FOR Re = 1500, according to impedance predictions, there should be a 
-% nearly-neutral eigenvalue close to omega = \pm 2.1i
-%
-% If i'm right the complex-mapping method should allow to calculate the
-% eigenvalue with negative imaginary part (lambda = sigma - i omega with omega >0) 
-
-% First test : USING general solver Stab_Axi_COMPLEX.edp (adapted from other sources of the StabFem project) 
-% nev = 20 => Slepc solver
-evG = SF_Stability(bf,'shift',-2.1i,'m',0,'nev',20)
-% nev = 1 => shift-invert solver
-evG1 = SF_Stability(bf,'shift',-2.1i,'m',0,'nev',20)
-
-% SECOND test : USING solver  Stab_Axi_COMPLEX_m0.edp adapted from Raffaele's sources
-% note that this solver is switched on by the "trick" m = 0+1i...
-% nev = 20 => Slepc solver
-ev = SF_Stability(bf,'shift',-2.1i,'m',0+1i,'nev',20)
-% nev = 1 => shift-invert solver
-ev1 = SF_Stability(bf,'shift',-2.1i,'m',0+1i,'nev',20)
-
-scatter(real(evG), imag(evG),'MarkerEdgeColor',[0 .5 .5],...
-              'MarkerFaceColor',[0 .7 .7],...
-              'LineWidth',1.5)
-hold on;
-scatter(real(evG1),imag(evG1),'s','red',...
-              'LineWidth',1.5)
-
-scatter(real(ev),imag(ev),'s','magenta',...
-              'LineWidth',1.5)
-hold on;
-scatter(real(ev1),imag(ev1),'s','black',...
-              'LineWidth',1.5)
-legend('Stab_Axi_Complex.edp, nev=20','Stab_Axi_Complex.edp, nev=1','Stab_Axi_Complex_m0.edp, nev=20','Stab_Axi_Complex_m0.edp, nev=1');
-

### 2018-10-02 CASES_STABLE/CYLINDER/Linear_LoopRe.m

@@ -1,15 +1,0 @@
-function LINres = Linear_LoopRe(bf,shiftinit,Re_LIN)
-
-bf=SF_BaseFlow(bf,'Re',Re_LIN(1));
-[ev,em] = SF_Stability(bf,'shift',shiftinit,'nev',1,'type','D');
-LINres.Re = Re_LIN;
-LINres.Fx = []; LINres.Lx = [];LINres.lambda=[];
-    for Re = LINres.Re
-        bf = SF_BaseFlow(bf,'Re',Re);
-        LINres.Fx= [LINres.Fx,bf.Fx];
-        LINres.Lx = [LINres.Lx,bf.Lx];
-        ev = SF_Stability(bf,'nev',1,'shift','cont','nev',1,'type','D');
-        LINres.lambda = [LINres.lambda ev];
-    end
-    
-end

### 2018-10-02 CASES_STABLE/CYLINDER/SCRIPT_CYLINDER_HB2_MeshIssues.m

@@ -1,135 +1,0 @@
-
-%  Instability of the wake of a cylinder with STABFEM
-%
-%  this script demonstrates the way to perform HARMONIC BALANCE
-%  for the wake of a cylinder in the range Re = [46.7 - 200].
- 
-clear all;
-run('../../SOURCES_MATLAB/SF_Start.m');verbosity=1;
-
-if(exist('RESULTS/HB2res_meshes.mat')==0)
-    
-   
-    figureformat='png'; AspectRatio = 0.56; % for figures
-    mkdir('RESULTS');
-    
-    Rec = 46.7;
-    Re_TAB = [Rec 47 47.5 48 49 50 52.5 55 60 65 70 75 80 85 90 95 100 110:10:200];
-    
-    %% ##### CHAPTER 1 : MESH 'S', 80, 'S'
-    
-    disp(' ');
-    disp(' #### MESH 1 #### ');
-    disp(' ');
-    
-    bf = SmartMesh_Cylinder('S',[-40 80 40]);
-    
-    disp('COMPUTING INSTABILITY THRESHOLD');
-    bf=SF_BaseFlow(bf,'Re',50);
-    [ev,em] = SF_Stability(bf,'shift',+.75i,'nev',1,'type','S');
-    [bfT,emT]=SF_FindThreshold(bf,em);
-    Rec = bfT.Re;
-    
-    HBres_mesh1 = HB2_LoopRe(bfT,emT,Re_TAB) ;    
-    
-    %% ##### CHAPTER 2 : MESH 'S', 120, 'S'
-    
-    disp(' ');
-    disp(' #### MESH 2 #### ');
-    disp(' ');
-    
-    bf = SmartMesh_Cylinder('S',[-40 120 40]);
-    
-    disp('COMPUTING INSTABILITY THRESHOLD');
-    bf=SF_BaseFlow(bf,'Re',50);
-    [ev,em] = SF_Stability(bf,'shift',+.75i,'nev',1,'type','S');
-    [bfT,emT]=SF_FindThreshold(bf,em);
-    Rec = bfT.Re;
-    
-    
-    HBres_mesh2 = HB2_LoopRe(bfT,emT,Re_TAB) ;
-    
-    
-    
-    
-    %% ##### CHAPTER 3 : MESH 'D', 80, 'S'
-    
-    disp(' ');
-    disp(' #### MESH 3 #### ');
-    disp(' ');
-    
[…]

### 2018-10-02 CASES_STABLE/CYLINDER/autorun.m

@@ -1,182 +1,0 @@
-function value = autorun(isfigures);
-% Autorun function for StabFem. 
-% This function will produce sample results for the wake of a cylinder with STABFEM  
-%  - Base flow computation
-%  - Linear stability
-%  - WNL
-%  - Harmonic Balance
-%
-% USAGE : 
-% autorun -> automatic check (non-regression test). 
-% Result "value" is the number of unsuccessful tests
-% autorun(1) -> produces the figures (in present case not yet any figures)
-
-if(nargin==0) 
-    isfigures=0; 
-end;
-format long;
-%% Chapter 0 : reference values for non-regression tests
-np_REF = 2193;
-Fx_REF =  0.6435;
-ev_REF =   0.0131 + 0.7377i;
-
-Rec_REF =   46.7785;
-Lxc_REF =    3.2027;
-Omegac_REF =    0.7333;
-
-Lambda_REF = 9.1331 + 3.3150i;
-nu0_REF = 3.2416e+01 - 1.0253e+02i;
-nu2_REF = -1.0405 - 3.0825i;
-              
-Lx_HB_REF =    3.18156;
-Fx_HB_REF =    0.709255;
-omega_HB_REF =    0.7371;
-Aenergy_HB_REF =    0.43559; % (???)
-Fy_HB_REF =   0.00612223 - 0.0000i;
-
-Lx_HB2_REF =   3.1804;
-Fx_HB2_REF =   0.709319;
-omega_HB2_REF =    0.737335;
-Aenergy_HB2_REF = 0.440344;
-Fy_HB2_REF =   0.0062163 + 0.0000i;
-Fx2_HB2_REF = 4.49226e-06 + 2.07459e-06i;
-
-% np_REF = 2241;
-% Fx_REF =  0.6435;
-% ev_REF =   0.0131 + 0.7377i;
-% Rec_REF =   46.7338;
-% Lxc_REF =    3.1999;
-% Omegac_REF =    0.7333;
-% 
-% Lambda_REF = 9.1737 + 3.2631i;
-% nu0_REF = 3.1349e+01 - 1.0253e+02i;
-% nu2_REF = -1.0238 - 3.0298i;
-%               
-% Lx_HB_REF =    3.1806;
-% Fx_HB_REF =    0.7089;
-% omega_HB_REF =    0.7373;
[…]

### 2018-10-02 CASES_STABLE/LiquidBridges/autorun.m

@@ -1,347 +1,0 @@
-function value = autorun(isfigures);
-% Autorun function for StabFem. 
-% This function will produce sample results for the case EXAMPLE_Lshape
-%
-% USAGE : 
-% autorun(0) -> automatic check
-% autorun(1) -> produces the figures used for the manual
-if(nargin==0) 
-    isfigures=0; 
-end;
-%%
-close all;
-run('../../SOURCES_MATLAB/SF_Start.m');
-system('mkdir FIGURES');
-figureformat = 'png';verbosity=0;
-value = 0;
-%% CHAPTER 0 : creation of initial mesh for cylindrical bridge, L=4
-
-L = 4;
-density=20;
- %creation of an initial mesh (with volume corresponding to coalescence of two spherical caps) 
-ffmesh = SF_Mesh('MeshInit_Bridge.edp','Params',[0 L density]);
-V = pi*L/2*(1+L^2/12);
-gamma = 1;
-rhog = 0;
-ffmesh = SF_Mesh_Deform(ffmesh,'V',V,'typestart','pined','typeend','pined','gamma',gamma,'rhog',rhog);
-
-
-disp('##### autorun test 1 :  deforming the mesh with prescrived volume')
-P0 = ffmesh.P0;
-P0_REF = 0.9699;
-error1 = abs(P0/P0_REF-1)
-if(error1>1e-3) 
-    value = value+1 
-end
-
-
-if(isfigures)
-figure(1);hold off;
-plot(ffmesh.xsurf,ffmesh.ysurf); hold on;
-end
-
-%% CHAPTER 1 : Eigenvalue computation for m=0 and m=1 FOR A CYLINDRICAL BRIDGE
-[evm0,emm0] =  SF_Stability(ffmesh,'nev',10,'m',0,'sort','SIA');
-[evm1,emm1] =  SF_Stability(ffmesh,'nev',10,'m',1,'sort','SIA');
-
-
-ev_m0a = evm0(4);
-ev_m0s = evm0(6);
-ev_m1s = evm1(2);
-ev_m1a = evm1(4);
-
-% previously computed reference values
-ev_m0a_REF =   0.0000 + 0.8158i;
-ev_m0s_REF =   0.0000 + 2.2418i;
[…]

### 2018-10-02 CASES_STABLE/ROTATING_POLYGONS/autorun.m

@@ -1,167 +1,0 @@
-function value = autorun(isfigures);
-% Autorun function for StabFem. 
-% This function will produce sample results for the case ROTATING_POLYGONS
-%
-% USAGE : 
-% autorun(0) -> automatic check
-% autorun(1) -> produces the figures used for the manual
-if(nargin==0) 
-    isfigures=0; 
-end;
-
-%%
-close all;
-run('../../SOURCES_MATLAB/SF_Start.m');
-system('mkdir FIGURES');
-figureformat = 'png';
-verbosity = 0;
-%% CHAPTER 0 : creation of initial mesh 
-a=.3;
-density=60;
-xi = .25;
-ffmesh = SF_Mesh('Mesh_PotentialVortex.edp','Params',[a xi density]);
-gamma = 0;
-
-% CHAPTER 1 : Eigenvalue computation for m=3
-[evm3,emm3] =  SF_Stability(ffmesh,'gamma',gamma,'nev',15,'m',3,'shift',3i,'typestart','angle','typeend','angle');
-evm3FIG = evm3(1:4).'
-
-evm3_REF =  [2.8333i, 3.7210i, 4.2695i, 1.3374i]
-
-disp('### autorun test 1 : check eigenvalues for a=0.3, xi = 0.25, m=3');
-error = sum(abs(evm3_REF-evm3FIG))
-
-value = (error>1e-3)
-
-if(isfigures)
-
-% 1b : plots
-figure(10);
-subplot(2,2,1);
-n=1;
-plotFF(emm3(n),'phi.im','xlim',[0 1],'ylim',[0 .5]);hold on;
-hold on;E=0.05/max(abs(emm3(n).eta));
-plot(ffmesh.xsurf+E*emm3(n).eta.*ffmesh.N0r,ffmesh.ysurf+E*emm3(n).eta.*ffmesh.N0z,'r');
-title(['Mode G0 : omega = ',num2str(evm3(n))])
-hold off;
-subplot(2,2,2);
-n=3;
-plotFF(emm3(n),'phi.im','xlim',[0 1],'ylim',[0 .5]);hold on;
-hold on;E=0.05/max(abs(emm3(n).eta));
-plot(ffmesh.xsurf+E*emm3(n).eta.*ffmesh.N0r,ffmesh.ysurf+E*emm3(n).eta.*ffmesh.N0z,'r');
-title(['Mode G1 : omega = ',num2str(evm3(n))])
[…]

### 2018-10-02 DEVELOPMENT_CASES/Vessel/SCRIPT_vessel.m

@@ -1,0 +1,110 @@
+
+close all;
+run('../../SOURCES_MATLAB/SF_Start.m');verbosity=100;
+system('mkdir FIGURES');
+figureformat = 'png';
+
+%% CHAPTER 1 : flat surface, free condition
+gamma=0.002;
+rhog=1;
+R = 1;
+L =2;
+
+
+density=100;
+ %creation of an initial mesh 
+ 
+ffmesh = SF_Mesh('MeshInit_Vessel.edp','Params',[L density]);
+ffmesh = SF_Mesh_Deform(ffmesh,'P',0,'gamma',gamma,'rhog',rhog,'typestart','pined','typeend','axis');
+%figure();plot(ffmesh.xsurf,ffmesh.ysurf);hold on;quiver(ffmesh.xsurf,ffmesh.ysurf,ffmesh.N0r,ffmesh.N0z); % to plot normal vectors
+ 
+
+disp('###first test : flat surface, free condition')
+
+
+[evm1,emm1] =  SF_Stability(ffmesh,'nev',10,'m',1,'shift',2.1i,'typestart','angleV','typeend','axis');
+% NB with this value of the shift the modes number n=1,2,3 will be found with index (2,1,3)
+
+evTheory = [1.3606    2.3737    3.1274]; % see script Analytical solution
+error1 = abs(imag(evm1(2))/evTheory(1)-1)+abs(imag(evm1(1))/evTheory(2)-1)+abs(imag(evm1(3))/evTheory(3)-1)
+
+figure(1);
+plot(imag(evm1),0*real(evm1),'r+');hold on;
+legend('flat, free');
+
+figure(2);suptitle('m=1 sloshing modes : Horizontal surface, free condition');hold on;
+subplot(1,3,1);
+plotFF(emm1(2),'phi.im','title',{'Mode (m,n)= (1,1)',['freq = ',num2str(imag(evm1(2)))]},'symmetry','YA');hold on;plotFF_ETA(emm1(2),'symmetry','YA');
+subplot(1,3,2);
+plotFF(emm1(1),'phi.im','title',{'Mode (m,n)= (1,2)',['freq = ',num2str(imag(evm1(1)))]},'symmetry','YA');hold on;plotFF_ETA(emm1(1),'symmetry','YA');
+subplot(1,3,3);
[…]

### 2018-10-02 DEVELOPMENT_CASES/Vessel/autorun.m

@@ -1,0 +1,149 @@
+function value = autorun(isfigures);
+% Autorun function for StabFem. 
+% This function will produce sample results for the case VESSEL (sloshing modes)
+%
+% USAGE : 
+% autorun(0) -> automatic check
+% autorun(1) -> produces the figures used for the manual
+
+%%
+close all;
+run('../../SOURCES_MATLAB/SF_Start.m');verbosity=10;
+system('mkdir FIGURES');
+figureformat = 'png';
+if(nargin==0) 
+    isfigures=0; verbosity=0;
+end;
+value =0;
+
+
+%% CHAPTER 1 : flat surface, free condition
+gamma=0.002;
+rhog=1;
+R = 1;
+L =2;
+
+
+density=100;
+ %creation of an initial mesh 
+ 
+ffmesh = SF_Mesh('MeshInit_Vessel.edp','Params',[L density]);
+ffmesh = SF_Mesh_Deform(ffmesh,'P',0,'gamma',gamma,'rhog',rhog,'typestart','pined','typeend','axis');
+%figure();plot(ffmesh.xsurf,ffmesh.ysurf);hold on;quiver(ffmesh.xsurf,ffmesh.ysurf,ffmesh.N0r,ffmesh.N0z); % to plot normal vectors
+ 
+
+disp('###first test : flat surface, free condition')
+
+
+[evm1,emm1] =  SF_Stability(ffmesh,'nev',10,'m',1,'shift',2.1i,'typestart','angleV','typeend','axis');
+% NB with this value of the shift the modes number n=1,2,3 will be found with index (2,1,3)
+
+evTheory = [1.3606    2.3737    3.1274]; % see script Analytical solution
+error1 = abs(imag(evm1(2))/evTheory(1)-1)+abs(imag(evm1(1))/evTheory(2)-1)+abs(imag(evm1(3))/evTheory(3)-1)
+
+if(error1>1e-2) 
+    value = value+1 
+end
+
+if(isfigures)
+figure(1);
+plot(imag(evm1),0*real(evm1),'r+');hold on;
+legend('flat, free');
+
+figure(2);suptitle('m=1 sloshing modes : Horizontal surface, free condition');hold on;
+subplot(1,3,1);
[…]

### 2018-10-02 SOURCES_MATLAB/SF_Adapt.m

@@ -103,12 +103,17 @@ optionstring = [' ', num2str(nfields), ' '];
 for i=1:nfields;
      mycp(flowforadapt(i).mesh.filename, [ffdatadir, 'mesh.msh']);
      mycp(flowforadapt(i).filename, [ffdatadir, 'FlowFieldToAdapt',num2str(i),'.txt']);
+%    if(isfield(flowforadapt(i),'datastoragemode')) 
     [dumb,storagemode,nscalars] = fileparts(flowforadapt(i).datastoragemode); % this is to extract two parts of datastoragemode, e.g. 
     if(strcmp(nscalars,''))
         nscalars = '0';
     else
         nscalars = nscalars(2:end); %to remove the dot
     end
+%    else 
+%        storagemode = 'ReP2P2P1';
+%        nscalars = 1;
+%    end
     optionstring = [optionstring, ' ', storagemode, ' ' , nscalars , ' '];
 end
 

### 2018-10-02 SOURCES_MATLAB/importFFmesh.m

@@ -8,7 +8,7 @@ global ff ffdir ffdatadir sfdir verbosity
 % 2/ mesh=importFFmesh(fileToRead1,'seg') -> imports information for points, triangles & SEGMENTS (VERY INEFFICIENT, SHOULD BE IMPROVED)
 %
 % FileToRead1 is typically of the form "mesh.msh".
-% The program will also need files "mesh.ff2m" and "SF_Init.ff2m"
+% The program will also need files "mesh.ff2m" a.nd "SF_Init.ff2m"
 %
 %  This program was originally adapted from FreeFem_to_matlab, copyright Julien Dambrine 2010 ;
 %  modified by D. Fabre (2017) ; and redesigned in 2018 with help of M. Chloros
@@ -53,6 +53,7 @@ if (verbosity > 2)
 end
 frewind(fid);
 if ~(dimension == 2)
+    dimension
     error('only supported dimension is 2');
 end
 %start over

### 2018-10-02 STABLE_CASES/CYLINDER/Linear_LoopRe.m

@@ -1,0 +1,19 @@
+function LINres = Linear_LoopRe(bf,shiftinit,Re_LIN)
+
+bf=SF_BaseFlow(bf,'Re',Re_LIN(1));
+[ev,em] = SF_Stability(bf,'shift',shiftinit,'nev',1,'type','D');
+LINres.Re = Re_LIN;
+LINres.Fx = []; LINres.Lx = [];LINres.lambda=[];
+    for Re = LINres.Re
+        bf = SF_BaseFlow(bf,'Re',Re);
+        [ev,em] = SF_Stability(bf,'nev',1,'shift','cont','nev',1,'type','D');
+        if(em.iter<0) 
+            disp(['warning : divergence in eigenvalue computation for Re = ',num2sdtr(Re)]);
+            break;
+        end
+        LINres.Fx= [LINres.Fx,bf.Fx];
+        LINres.Lx = [LINres.Lx,bf.Lx];
+        LINres.lambda = [LINres.lambda ev];
+    end
+    LINres.Re = LINres.Re(1:length(LINres.lambda)); % truncate if the computation has failed at some point
+end

### 2018-10-02 STABLE_CASES/CYLINDER/autorun.m

@@ -1,0 +1,184 @@
+function value = autorun(isfigures);
+% Autorun function for StabFem. 
+% This function will produce sample results for the wake of a cylinder with STABFEM  
+%  - Base flow computation
+%  - Linear stability
+%  - WNL
+%  - Harmonic Balance
+%
+% USAGE : 
+% autorun -> automatic check (non-regression test). 
+% Result "value" is the number of unsuccessful tests
+% autorun(1) -> produces the figures (in present case not yet any figures)
+
+run('../../SOURCES_MATLAB/SF_Start.m');verbosity=10;
+myrm('WORK/*')
+myrm('WORK/*/*')
+
+if(nargin==0) 
+    isfigures=0; verbosity=0;
+end;
+format long;
+%% Chapter 0 : reference values for non-regression tests
+np_REF = 2193;
+Fx_REF =  0.6435;
+ev_REF =   0.0131 + 0.7377i;
+
+Rec_REF =   46.7785;
+Lxc_REF =    3.2027;
+Omegac_REF =    0.7333;
+
+Lambda_REF = 9.1331 + 3.3150i;
+nu0_REF = 3.2416e+01 - 1.0253e+02i;
+nu2_REF = -1.0405 - 3.0825i;
+              
+Lx_HB_REF =    3.18156;
+Fx_HB_REF =    0.709255;
+omega_HB_REF =    0.7371;
+Aenergy_HB_REF =    0.43559; % (???)
+Fy_HB_REF =   0.00612223 - 0.0000i;
+
+Lx_HB2_REF =   3.1804;
+Fx_HB2_REF =   0.709319;
+omega_HB2_REF =    0.737335;
+Aenergy_HB2_REF = 0.440344;
+Fy_HB2_REF =   0.0062163 + 0.0000i;
+Fx2_HB2_REF = 4.49226e-06 + 2.07459e-06i;
+
+% np_REF = 2241;
+% Fx_REF =  0.6435;
+% ev_REF =   0.0131 + 0.7377i;
+% Rec_REF =   46.7338;
+% Lxc_REF =    3.1999;
+% Omegac_REF =    0.7333;
+% 
+% Lambda_REF = 9.1737 + 3.2631i;
+% nu0_REF = 3.1349e+01 - 1.0253e+02i;
+% nu2_REF = -1.0238 - 3.0298i;
[…]

### 2018-10-02 STABLE_CASES/ROTATING_POLYGONS/autorun.m

@@ -1,0 +1,189 @@
+function value = autorun(isfigures);
+% Autorun function for StabFem. 
+% This function will produce sample results for the case ROTATING_POLYGONS
+%
+% USAGE : 
+% autorun(0) -> automatic check
+% autorun(1) -> produces the figures used for the manual
+%%
+close all;
+run('../../SOURCES_MATLAB/SF_Start.m');
+system('mkdir FIGURES');
+figureformat = 'png';
+verbosity = 10;
+
+if(nargin==0)
+    isfigures=0; verbosity=0;
+end;
+
+
+%% CHAPTER 0 : creation of initial mesh 
+a=.3;
+xi = .25;
+rhog = 1;
+R = 1;
+gamma = 0;
+GammaBAR = xi*sqrt(2*rhog*a*R^2/(R^2-xi^2-2*xi^2*log(R/xi)));
+
+density=60;
+
+ffmesh = SF_Mesh('Mesh_PotentialVortex.edp','Params',[a xi density]);
+
+
+evm3_REF =  [2.8333, 3.7210, 4.2695 1.3374] % => Values from Mougel et al Paper 
+
+% CHAPTER 1 : Eigenvalue computation for m=3
+
+%%% warning : in Mougel we have modal dependance with the form exp( i (m theta - omega t) )
+%%% and omega is negative (real for pure waves).
+%%% here the form is exp ( lambda t + i m theta) . So omega corresponds to
+%%% minus the imaginary par of our omega. This is why the guess is -3i and
+%%% the eigenvalues are transposed for comparison.
+
+
+
+[evm3,emm3] =  SF_Stability(ffmesh,'gamma',gamma,'rhog',1,'GammaBAR',GammaBAR,'nev',15,'m',3,'shift',-3i);
+evm3FIG = 1i*evm3(1:4).' % transpose, not conjugate
+
+
+
+%evm3_REF =  [ 2.858705i 3.558175i  4.30018i  1.236246i] => wrong ref ?
+
+
+disp('### autorun test 1 : check eigenvalues for a=0.3, xi = 0.25, m=3');
+error = sum(abs(evm3_REF-evm3FIG))
+
+value = (error>1e-3)
+
[…]

### 2018-10-02 STABLE_CASES/Vessel/SCRIPT_vessel.m

@@ -1,0 +1,110 @@
+
+close all;
+run('../../SOURCES_MATLAB/SF_Start.m');verbosity=10;
+system('mkdir FIGURES');
+figureformat = 'png';
+
+%% CHAPTER 1 : flat surface, free condition
+gamma=0.002;
+rhog=1;
+R = 1;
+L =2;
+
+
+density=100;
+ %creation of an initial mesh 
+ 
+ffmesh = SF_Mesh('MeshInit_Vessel.edp','Params',[L density]);
+ffmesh = SF_Mesh_Deform(ffmesh,'P',0,'gamma',gamma,'rhog',rhog,'typestart','pined','typeend','axis');
+%figure();plot(ffmesh.xsurf,ffmesh.ysurf);hold on;quiver(ffmesh.xsurf,ffmesh.ysurf,ffmesh.N0r,ffmesh.N0z); % to plot normal vectors
+ 
+
+disp('###first test : flat surface, free condition')
+
+
+[evm1,emm1] =  SF_Stability(ffmesh,'nev',10,'m',1,'shift',2.1i,'typestart','angleV','typeend','axis');
+% NB with this value of the shift the modes number n=1,2,3 will be found with index (2,1,3)
+
+evTheory = [1.3606    2.3737    3.1274]; % see script Analytical solution
+error1 = abs(imag(evm1(2))/evTheory(1)-1)+abs(imag(evm1(1))/evTheory(2)-1)+abs(imag(evm1(3))/evTheory(3)-1)
+
+figure(1);
+plot(imag(evm1),0*real(evm1),'r+');hold on;
+legend('flat, free');
+
+figure(2);suptitle('m=1 sloshing modes : Horizontal surface, free condition');hold on;
+subplot(1,3,1);
+plotFF(emm1(2),'phi.im','title',{'Mode (m,n)= (1,1)',['freq = ',num2str(imag(evm1(2)))]},'symmetry','YA');hold on;plotFF_ETA(emm1(2),'symmetry','YA');
+subplot(1,3,2);
+plotFF(emm1(1),'phi.im','title',{'Mode (m,n)= (1,2)',['freq = ',num2str(imag(evm1(1)))]},'symmetry','YA');hold on;plotFF_ETA(emm1(1),'symmetry','YA');
+subplot(1,3,3);
[…]

### 2018-10-02 STABLE_CASES/Vessel/autorun.m

@@ -1,0 +1,148 @@
+function value = autorun(isfigures);
+% Autorun function for StabFem. 
+% This function will produce sample results for the case VESSEL (sloshing modes)
+%
+% USAGE : 
+% autorun(0) -> automatic check
+% autorun(1) -> produces the figures used for the manual
+
+%%
+close all;
+run('../../SOURCES_MATLAB/SF_Start.m');verbosity=10;
+system('mkdir FIGURES');
+figureformat = 'png';
+
+if(nargin==0) 
+    isfigures=0; verbosity=0;
+end;
+value =0;
+
+
+%% CHAPTER 1 : flat surface, free condition
+gamma=0.002;
+rhog=1;
+R = 1;
+L =2;
+
+
+density=100;
+ %creation of an initial mesh 
+ 
+ffmesh = SF_Mesh('MeshInit_Vessel.edp','Params',[L density]);
+ffmesh = SF_Mesh_Deform(ffmesh,'P',0,'gamma',gamma,'rhog',rhog,'typestart','pined','typeend','axis');
+%figure();plot(ffmesh.xsurf,ffmesh.ysurf);hold on;quiver(ffmesh.xsurf,ffmesh.ysurf,ffmesh.N0r,ffmesh.N0z); % to plot normal vectors
+ 
+
+disp('###first test : flat surface, free condition')
+
+
+[evm1,emm1] =  SF_Stability(ffmesh,'nev',10,'m',1,'shift',2.1i,'typestart','angleV','typeend','axis');
+% NB with this value of the shift the modes number n=1,2,3 will be found with index (2,1,3)
+
+evTheory = [1.3606    2.3737    3.1274]; % see script Analytical solution
+error1 = abs(imag(evm1(2))/evTheory(1)-1)+abs(imag(evm1(1))/evTheory(2)-1)+abs(imag(evm1(3))/evTheory(3)-1)
+
+if(error1>1e-2) 
+    value = value+1 
+end
+
+if(isfigures)
+figure(1);
+plot(imag(evm1),0*real(evm1),'r+');hold on;
+legend('flat, free');
+
+figure(2);suptitle('m=1 sloshing modes : Horizontal surface, free condition');hold on;
+subplot(1,3,1);
[…]

### 2018-10-09 DEVELOPMENT_CASES/WhistlingHole/JFM_PartII_Draft/thick_hole_2018.tex
New draft of part II on Whistling holes !!!

--- 2018-10-02 DEVELOPMENT_CASES/WhistlingHole/JFM_PartII_Draft/thick_hole.tex
@@
 
-The problem of Rayleigh was reconsidered by Howe, in presence of a base flow, leading to a prediction for the conductivity as function of the Strouhal number.
-The derivation is extremely technical and not reproduced here.
-The final result amounts to :
-$$
-K = 2R ( \gamma - i \delta)
-$$
-with
-\be
-\gamma = \frac{
-I_1(\Omega^*)^2[1+1/\Omega^*]+(4/\pi^2) e^{2\Omega^*}\cosh(\Omega^*) K_1(\Omega^*)^2[\cosh(\Omega^*)-\sinh(\Omega^*)/\Omega^*]
-}
-{
-I_1(\Omega^*)^2+(4/\pi^2) e^{2\Omega^*}\cosh^2(\Omega^*) K_1(\Omega^*)^2
-}
-\label{eq:gammaHowe}
-\ee
+\subsection{Energy flux and instability criteria}
 
-\be
-\delta = 
-\frac{
-(2/\pi \Omega^*) I_1(\Omega^*) K_1(\Omega^*)e^{2\Omega^*}
-}
-{
-I_1(\Omega^*)^2+(4/\pi^2) e^{2\Omega^*}\cosh^2(\Omega^*) K_1(\Omega^*)^2
-}
-\label{eq:deltaHowe}
-\ee
+WE HAVE TO EXPLAIN THE TWO CRITERIA
 
-Note that in the calculation of Howe, the Strouhal number is defined as $\Omega^* = \omega R/U$ where $U$ is the velocity of convection of the vorticity along the vortex sheet.
-Howe argues that $U= U_J/2$, in accordance with the classical modeling of the Kelvin-Helmholtz instability.
-Hence the relationship with the Strouhal number used in the present paper is $\Omega^* = \Omega/(2 \alpha)$, and the two definitions are equivalent if $\alpha = 1/2$.
+1/ Acoustic instability
 
-\subsection{Energy flux and instability criteria}
+$Z_r(\omega)$ < 0 for some real $\omega$
+
+Demonstrate that in this case, we have over reflexion.
+
+2/ Hydrodynamic instability.
+
+$Z_r>0$ and $Z_I>0$ for some real $\omega$
+
+FIGURE : sketch showing the NYQUIST diagrams.
+
+REWRITE IN TERMS OF IMPEDANCE
 
@@
 
-\section{The viscous problem : analysis and numerical method}
+\section{Numerical method}
+
+\includegraphics[width=.6\linewidth]{fig/mesh.eps}
 
@@
 
-\subsection{Upstream domain}
+THE REMAINDER IS THE SAME AS IN PART I.
 
-As sketched in figure 1, the upstream domain is expected to originate from an upstream container of large dimension, and sufficiently far away from the hole the flow is assumed to be radially convergent.
-However, in the numerical implementation, it is required to specify a given geometry for this upstream domain.
-Here, we have chosen to assume that the upstream region is a closed cavity of rectangular cross-section, with radius $R_{cav}$ and length $L_{cav}$.
-The volumic flux condition is imposed by assuming that both the base-flow and the perturbation velocities are constant along the bottom of the cavity, noted $\Gamma_{in}$
-
-\be
- {\bf u}_0 = - Q_0/S_{cav} {\vec n} ; \quad {\bf u'} = - q'/S_{cav} {\vec n} \quad {\mbox at } \Gamma_{in}
-\ee
-where $S_{cav}= \pi R_{cav}^2$ is the area of the bottom wall and ${\bf n}$ is the outward normal vector.
-The pressure levels $P_{in}$ and $p'_{in}$, which are required for the calculation of the mean pressure loss and the conductivity, are computed by averaging along the inlet boundary :
-\be
- {P}_{in} = 1/S_{cav} \int_{\Gamma_{in}} P_0 2 \pi r dr ; \quad
-  {p'}_{in} = 1/S_{cav} \int_{\Gamma_{in}} p' 2 \pi r dr.
-\ee
-It was verified that if the dimensions of the cavity are large enough, the pressure is effectively nearly constant along the inlet boundary $\Gamma_{in}$.
-
-At the lateral wall of the cavity, noted $\Gamma_{lat}$, the physically relevant condition should be a no-slip condition.
-However, as the location of this wall is not really relevant, and in order to avoid the development of a boundary layer,
-we preferred to impose a stress-free condition, namely  
-\be
- {\bf u} \cdot {\bf n} = 0 ; \quad \DP{({\bf u} \cdot {\bf x})}{r} = 0 \quad \mbox{  at  } \Gamma_{lat},
- \ee
-which applies for both the base flow and the perturbation.
-
-In the sequel we set the dimensions of the upstream cavity as $L_{cav} = R_{cav} = 10 R_{hole}$,
-and verified that these values are large enough for the results to be insensible to these parameters.
+SPECIFY THAT THE PROGRAM IS AVAILABLE ONLINE AS PART OF THE STABFEM PROJETCT.
 
@@
 
-The treatment of the outlet conditions is a delicate point here, as the structure of both the base flow and the perturbation lead to some difficulties, especially when the Reynolds number becomes large.
-These difficulties led us to use an original method which consists of using a change of variables from a computational domain defined with $[X,R]$ coordinates to the physical domain with $[x,r]$ coordinates.
-
-The first motivation for this method comes from the structure of the base flow. In effect, the laminar, steady solution 
- $[u_0,p_0]$ is characterized by a boundary layer which remains very sharp at large distances from the hole.
-More specifically, the boundary layer thickness $\delta$ scales as  $\delta(x) \approx \sqrt{\nu x/U_J}\approx Re^{-1/2} x^{1/2}$.
-Of course, in a real, High-Reynolds jet, the boundary layer thickness grows much faster because of turbulence.
-However, the global method used here requires computation of a laminar base flow  so we have to work around this issue.
-The solution is to use a change of coordinates $x = G_x(X)$ which stretches the outer domain from $X\in [0,X_{max}]$ to $[0,x_{max}]$, where the bound of the computational $X_{max}$ is relatively small, while the corresponding $x_{max} = x(X_{max})$ is several orders of magnitude larger.
-
-The second issue is due to the structure of the perturbation.
-In effect, the jet is spatially unstable, and thus perturbations are convectively amplified in the downstream perturbation, and far away from the hole, they reach levels several orders of magnitude larger than the levels in the vicinity of the hole.
-As soon as the ratio between minimum and maximum levels of the perturbation becomes of the order of the numerical round-off error
-($10^{-15}$ using double-precision) this issue leads to the impossibility to compute accurately the structure of the perturbation in the vicinity of the whole, which is mostly relevant for the computation of the conductivity.
-In practice, when solving the problem in terms of the physical coordinates, this issue limits the validity of the results to $Re \leq 800$.
-
-To detail the origin of the problem and introduce the idea used to overcome it, let us review the classical modeling of the Kelvin-Helmholtz instability for a planar shear layer of zero thickness in the inviscid case.
-The derivation can be found in any classical textbook on hydrodynamical stability (e.g.
-Shandrasekar, Drazin \& Reid, Charru, etc..).
-Consider as a base flow a shear layer separating two regions of constant axial velocity, namely $u= U$ for $y<0$ and $u=0$ for $y>0$.
-Now assume that the perturbation consists of a displacement of the shear layer with the form
-\be 
-y = \eta \approx e^{i k x - i\omega t} 
-\label{eq:etaKH}
-\ee
-and assume a similar modal expansion for the velocity potential in the upper and lower region. Matching the two regions at the interface leads to the classical dispersion relation :
-\be 
-c \equiv \frac{\omega}{k} = \frac{1+i}{2} U
-\label{eq:cKH}
-\ee 
-In a temporal stability framework, this means that a perturbation with real wavenumber $k$ will be convected
-downstream with a phase velocity $U/2$ and temporally amplified with a growth rate $U k/2$.
-On the other hand, in a spatial stability framework ($\omega$ real, $k$ complex), which is more relevant here, this means that any perturbation will be spatially amplified downstream and will diverge at $x\rightarrow +\infty$.
-This divergence forbids a global resolution of the function $\eta(x,t)$ when the spatial variable $x$ is {\em real}.
-However, the problem disappears if we consider an analytical continuation of the function $\eta(x,t)$ with a {\em complex variable} $x$.
-More specifically, as $\arg(k) = -\pi/4$, the function $\eta(x,t)$ becomes convergent as soon as $|x| \rightarrow \infty$ in a direction of the complex plane verifying $\pi/4 < \arg(x) 5\pi/4$.
-
-Thus, this study of the simple, inviscid, planar shear layer suggests a possible way to resolve the problem for the present case of a viscous, cylindrical shear layer : using a { \em  complex coordinate change} which maps the numerical $X \in [0;X_{max}]$ (with $X$ real) into a path for the physical $x$ coordinate which enters the complex plane and follows a direction where the perturbation is spatially damped.
+MAYBE EVERYTHING ABOUT COMPLEX MAPPING SHOULD BE POSTPONED IN APPENDIX ???
 
@@
 \begin{array}{rcll}
-x = G_x(X) &=& \frac{X}{\left[1-X^2/L_s^2 \right]^2} \left[ 1 + i \gamma_c \tanh \left(\frac{X}{L_c}\right)^2  \right]  & \mbox{ for } X>0, \\
+x = G_x(X) &=& \frac{X}{\left[1-(X-X_{s1}^2/(L_s-X_{s1})^2 \right]^2} \left[ 1 + i \gamma_c \tanh \left(\frac{X-X_{s1}}{L_c}\right)^2  \right]  & \mbox{ for } X>0, \\
 	& = & X & \mbox{ for } X<0.
@@
 \ee
-This choice has the following properties.
-First, it leaves the axial coordinate unchanged in the upstream domain and inside the hole $(x<0)$.
+
+This choice has the following properties. First, it leaves the axial coordinate unchanged in the upstream domain and inside the hole,
+AND IN THE DOWNSTREAM REGION UP TO $(x<X_{s1})$
+.
 Secondly, the numerical and spatial coordinates are also almost identical in the region where the jet emerges from the hole (namely  $x \leq L_c$ and $x \leq L_s$).
@@
 
-This function leaves the radial coordinate unchanged in the upstream domain an in the region $r<R_{s1}$ where the jet develops, but it stretches the limit of the domain from $R_{max}$ to $r_{max} = G_r(R_{max})$ which is very
-large as soon as $R_{s2}$ is close to $R_{max}$ (with $r_{s2} > R_{max}$).
-
-Having explained this change of coordinates, it remains to specify the boundary conditions to be used at the outer limits of the computational domain.
-For the resolution of the Navier-Stokes equation in an open domain, the physically relevant boundary condition $[{\bf u}; p] \rightarrow [0; p_{out}]$ as $(x,r) \rightarrow \infty$
-are often replaced by setting the traction (or pseudo-stress) $-p {\bf n} + \nu \nabla {\bf u} \cdot {\bf n} $ to zero
-at the outlet boundaries.
-An alternative choice is to nullify the stress $-p {\bf n} + \nu ( \nabla {\bf u} + \nabla {\bf u}^T) \cdot {\bf n} $.
-In the present case, we have chosen to impose a zero-traction condition at the boundaries $x_{max},r_{max}$, for both the base flow and the perturbation.
-A zero-stress condition was also tried, leading to similar results but convergence difficulties when computing the base flow.
-Note that the significance of
-
-Note that the use of complex coordinate mapping for linear problems involving a single spatial coordinate is customary in stability studies, and mathematical theorems are available to justify how to chose the integration contour as function of the singularities of the problem (e.g.
-Bender \& Orzag).
-On the other hand, its use for a nonlinear problem (i.e.
-computation of the base flow) involving two spatial coordinates is totally new to our knowledge.
-The validity of the method is not justified by rigourous mathematical argument, but only by the fact that it effectively works and that the results are independent upon the parameters of the mapping.
-A few test showing that it is effectively the case, for both the base flow and the perturbation, are given in appendix A.
-
 For most results presented in the present paper, the following choice of parameters was used:
@@
 
-\begin{figure}
-$$
-\includegraphics[width = .8 \linewidth]{FIGURES/Mesh.eps}
-$$
-\caption{Example of computational mesh with dimensions in mapped coordinates and nomenclature of boundaries.} 
-\label{fig:Mesh}
-\end{figure}
+SEE STABFEM AND PART I.
 
-The numerical resolution of the problem was performed with a finite element method,  using the FreeFem++ software.
-An example of computational mesh, in the $[X,R]$ coordinates, is shown in figure 2.
-Meshes were generated using Delaunay-Voronoi triangulation of the domain, and subsequently refined locally to fit the steep gradients of both the base flow and the perturbation using the adaptmesh command provided by the Freefem++ software.
+We should explain the two kibnds of problems:
 
-For resolution, the Navier-Stokes equations have first to be expressed in terms of the mapped coordinates. For this purpose, the spatial derivatives have to be modified as follows :
+1/ Forced harmonic problem => imepedance
 
-\be
-\DP{}{x} \equiv H_x \DP{}{X}  \quad \mbox{ with } H_x =   \frac{1}{G_x'};
-\ee
-\be
-\DP{}{r} \equiv H_r \DP{}{R}  \quad \mbox{ with } H_r =   \frac{1}{G_r'}.
-\ee
-
-The incompressible Navier-Stokes operator thus have the following form :
-
-\be
-{\cal NS} \left[\begin{array}{c} u_x \\ u_r  \\ p \end{array} \right] =
- \left[\begin{array}{c}
-- (u_x  H_x \partial_X u_x + u_r H_r \partial_R u_x) - H_x \partial_X p 
-+ \nu \left[ H_x \partial_X ( H_x \partial_X u_x ) + H_r/r\partial_R ( r H_r \partial_r u_x ) \right]
-\\
-- (u_x  H_x \partial_X u_r + u_r H_r \partial_R u_r) - H_r \partial_R p 
-+ \nu \left[ H_x \partial_X ( H_x \partial_X u_r ) - u_r/r^2 + H_r/r\partial_R ( r H_r \partial_r u_r ) \right]
-\\
-H_x \partial_X u_x + H_r/r \partial_R (r u_r) 
-\end{array} \right] 
-\label{eq:NS}
-\ee
-
-to solve these equations using finite element method, we classically multiply by test functions 
-$[u_x^*, u_r^*,p^*]$ and integrate over the domain.
-Note that this integration has to be done over the physical domain, so in terms of the numerical variables the elementary volume of integration is $dV = r dr dx = (H_x H_r)^{-1} r dR dX$ .
-After integration by parts of the pressure gradient and Laplacian terms, we are thus lead to the following weak formulation:
-
-\be
-\begin{array}{l}
-\displaystyle
-- \int \left[ 
-u_x^* \left( u_x  H_x \partial_X u_x + u_r H_r \partial_R u_x \right) 
-+ u_r^* \left( u_x  H_x \partial_X u_r + u_r H_r \partial_R u_r \right) 
-\right] dV
-\\
-\displaystyle
-+ \int \left[ 
-p \left( H_x \partial_X u_x^* + H_r \partial_R u_r^* + u_r^*/r \right) 
--
-p^* \left( H_x \partial_X u_x + H_r \partial_R u_r + u_r/r \right) 
-\right] dV
-\\
-\displaystyle
-- \int \left[ 
-H_x^2 \partial_X u_x \partial_X u_x^* +H_r^2 \partial_R u_x \partial_R u_x^*
-\right] dV
-\\
-\displaystyle
-- \int \left[ 
-H_x^2 \partial_X u_r \partial_X u_r^* +H_r^2 \partial_R u_r \partial_R u_r^*
-+ u_r u_r^*/r^2
-\right] dV
-\\
-= 0.
-\end{array}
-\ee
-
-Note that with this formulation, the no-traction boundary conditions at the outlet boundary, as well as the symmetry condition at the axis and the zero tangential stress condition at the lateral wall of the cavity are automatically satisfied thanks to the integration by parts.
-The other boundary conditions are imposed by penalization.
-
-Following a now customary approach, the computation of the base flow is done using a standart Newton method. The algorithm is as follows :
-\begin{description}
-\item[$(i)$] Start from a guess flow field $[{\bf u}^g;p^g]$.
-\item[$(ii)$] Solve the linear system ${\cal NS}[{\bf u}^g,p^g] + {\cal L}_g [\delta {\bf u}, \delta p]$ where $ {\cal L}_g$ is the linearized Navier-Stokes operator around the guess field.
-\item[$(iii)$] Obtain a better guess as $ [{\bf u},p] = [{\bf u}^g,p^g] +  [\delta {\bf u}, \delta p]$.
-\item[$(iv)$] Repeat until convergence.
-\end{description}
-The inversion at step $(ii)$ is done with the UMFPACK64 library.
-
-In practice, at point $(i)$ the guess field is generally taken as the base flow computed at a lower value of the Reynolds number.
-The whole algorithm is thus repeated for increasing values of the Reynolds number to generate a family of base flow.
-The mesh refinement is applied at each step, so that the refinement, and the number of points of the mesh, increases with the Reynolds number.
-Note that when using the complex mapping method described above, the radius of convergence of the Newton algorithm seems to be smaller than in the standard case.
-This means that the Reynolds number has to be increased moderately between successive base flow computations.
-
-The computation of the perturbations due to harmonic forcing $[u_x',u_r',p']$ is done using the same linear solver UMFPACK64.
-Note that the structure may involve steeper gradients compared to the base flow.
-To capture this, the problem is first solved on the refined mesh computed during the base flow computation.
-The mesh is subsequently refined a second time through the adaptmesh command, and the base flow and the perturbation are finally recomputed on this better mesh.
+2/ Eigenvalue problem
 
@@
 
-\section{The nonzero thickness case}
+%\section{The nonzero thickness case}
+
+\clearpage
+
+\section{Base flows : study of the recirculation region}
 
@@
 We particularly consider the cases $\beta= 0.3, 0.1 and 1$.
-
-\subsection{Base flows : study of the recirculation region}
 
@@
 $$
-\includegraphics[width=.7\linewidth]{FIGURES/Recirculation.eps}
+\includegraphics[width=.7\linewidth]{fig/Umin.eps}
 $$
@@
 $$
-\includegraphics[width=.7\linewidth]{FIGURES/Alpha_VennaContracta.eps}
+\includegraphics[width=.7\linewidth]{fig/Vena_contracta.eps}
 $$
@@
 
+SUGGESTION ABOUT USAGE OF COMPLEX MAPPING AND FIGURE MANAGEMENT.
+
+I SUGGEST TO USE A COMPLEX MAPPING WITH $X_s=3 (or 5)$
+
+IN THE WHOLE PAPER WE SHOULD ONLY PLOT THE STRUCTURES (and sensitivity) IN THE REGION NOT AFFECTED BY MAPPING.
+
+APPENDIX : STRUCTURE USING COMPLEX MAPPING.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %\clearpage
-\subsection{Unsteady flow}
+\section{Linear results for FORCED PROBLEM}
 
-\subsubsection{Case $\beta = 0.3$}
-
-%\begin{figure}
-%$$
-%\includegraphics[width=.4\linewidth]{FIGURES/Cond_Ep03.eps}
-%\includegraphics[width=.4\linewidth]{FIGURES/Cond_Ep03Z.eps}
-%$$
-%\caption{ Real part $\Gamma$ (thick) and Imaginary part $\Delta$ (thin) of the Rayleigh conductivity 
-%for a hole of thickness $\beta = 0.3$, for $Re = 100$ ($\cdot \cdot \cdot$), $Re = 500$ (-- --),
-%$Re = 800$ (-- $\cdot$ -- ),  $Re = 1500$ (---  ---),  and
-%$Re = 3000$ (--- $\cdot$ ---). 
-%Plot $(a)$ displays the range $\Omega = [0-5]$, and plot $(b)$ the range $\Omega = [5-15]$ with a different scale for $\gamma$ and $\delta$.}
-%\label{fig:Cond03}
-%\end{figure}
+\subsection{Case $\beta = 0.3$}
 
@@
 $$
-\includegraphics[width=.8\linewidth]{FIGURES/Ep03_RL.eps}
+\begin{array}{cc}
+\includegraphics[width=.45\linewidth]{fig/Z_Nyq_Re800_EP03.eps}
+&
+\includegraphics[width=.45\linewidth]{fig/Z_Nyq_Re1000_EP03.eps}
+\\
+\includegraphics[width=.45\linewidth]{fig/Z_Nyq_Re1200_EP03.eps}
+&
+\includegraphics[width=.45\linewidth]{fig/Z_Nyq_Re1600_EP03.eps}
+\\
+\includegraphics[width=.45\linewidth]{fig/Z_Nyq_Re2000_EP03.eps}&
+\end{array}
 $$
-\caption{ Real part $R$ (thick) and Imaginary part $L$ (thin) of the impedance
-for a hole of thickness $\beta = 0.3$, for %$Re = 100$ ($\cdot \cdot \cdot$), 
-$Re = 500$ (-- --, black),
-$Re = 800$ (-- $\cdot$ --, red ),  $Re = 1500$ (---  ---, green),  and
-$Re = 3000$ (--- $\cdot$ ---, blue). 
-%Plot $(a)$ displays the range $\Omega = [0-5]$, and plot $(b)$ the range $\Omega = [5-15]$ with a different scale for $\gamma$ and $\delta$.
-}
-\label{fig:Cond03}
+\caption{Nyquist diagrams for $\beta = 0.3$. CHECK THE FIGURES !!!!}
 \end{figure}
@@
 \end{figure}
+
+%\begin{figure}
+%$$
+%\includegraphics[width=.4\linewidth]{FIGURES/Cond_Ep03.eps}
+%\includegraphics[width=.4\linewidth]{FIGURES/Cond_Ep03Z.eps}
+%$$
+%\caption{ Real part $\Gamma$ (thick) and Imaginary part $\Delta$ (thin) of the Rayleigh conductivity 
+%for a hole of thickness $\beta = 0.3$, for $Re = 100$ ($\cdot \cdot \cdot$), $Re = 500$ (-- --),
+%$Re = 800$ (-- $\cdot$ -- ),  $Re = 1500$ (---  ---),  and
+%$Re = 3000$ (--- $\cdot$ ---). 
+%Plot $(a)$ displays the range $\Omega = [0-5]$, and plot $(b)$ the range $\Omega = [5-15]$ with a different scale for $\gamma$ and $\delta$.}
+%\label{fig:Cond03}
+%\end{figure}
+
+%ig/Vena_contracta.eps
+%\begin{figure}
+%$$
+%\includegraphics[width=.8\linewidth]{FIGURES/Ep03_RL.eps}
+%$$
+%\caption{ Real part $R$ (thick) and Imaginary part $L$ (thin) of the impedance
+%for a hole of thickness $\beta = 0.3$, for %$Re = 100$ ($\cdot \cdot \cdot$), 
+%$Re = 500$ (-- --, black),
+%$Re = 800$ (-- $\cdot$ --, red ),  $Re = 1500$ (---  ---, green),  and
+%$Re = 3000$ (--- $\cdot$ ---, blue). 
+%Plot $(a)$ displays the range $\Omega = [0-5]$, and plot $(b)$ the range $\Omega = [5-15]$ with a different scale for $\gamma$ and $\delta$.
+%}
+%\label{fig:Cond03}
+%\end{figure}
 
@@
 
-\subsubsection{Case $\beta = 1$}
+%\begin{figure}
+%\includegraphics[width=.47\linewidth]{FIGURES/SR_03_1500_1_33.eps}
+
+\subsection{Case $\beta = 1$}
 
@@
 
-\begin{figure}
-$$
-\begin{array}{cc}
-\includegraphics[width=.8\linewidth]{FIGURES/Ep1_RL.eps}
-\end{array}
-$$
-\caption{ 
-$(a)$ Real part $R$ (thick) and Imaginary part $L$ (thin) of the impedance for a hole of thickness
-$\beta = 1$, for $Re = 800$ (--$\cdot$--, red), $Re = 1200$ ( --$ \cdot \cdot$--, magenta) and $Re = 1500$ (---  ---, green).
-}
-\label{fig:Cond1}
-\end{figure}
+%\begin{figure}
+%$$
+%\begin{array}{cc}
+%\includegraphics[width=.8\linewidth]{FIGURES/Ep1_RL.eps}
+%\end{array}
+%$$
+%\caption{ 
+%$(a)$ Real part $R$ (thick) and Imaginary part $L$ (thin) of the impedance for a hole of thickness
+%$\beta = 1$, for $Re = 800$ (--$\cdot$--, red), $Re = 1200$ ( --$ \cdot \cdot$--, magenta) and $Re = 1500$ (---  ---, green).
+%}
+%\label{fig:Cond1}
+%\end{figure}
 
@@
 This fact will be confirmed in section 6.
+
+Finally, figure \ref{fig:Struct1} depicts the structure of the oscillating flow for the two first minima of $\delta$ for $Re = 1200$ (plots $a$ and $b$).
+One can observe that these perturbations display respectively 4 and 6 structures within the thickness of the hole.
+Note that a minimum of $\delta$ also exists for $Re =1200$ at $\Omega \approx 1$, but the value of $\delta$ remains positive.
+For $Re= 1500$, this first minimum becomes negative, and the
+corresponding structure is plotted in figure \ref{fig:Struct1}$(c)$.
+As expected, it displays only two vortical structures within the thickness of the hole.
+Finally, figure \ref{fig:Struct1}$(d)$ displays the case corresponding to the minimum of $|Z_{app}|$ for $Re = 1500$.
+The structure is much similar to the case plotted in \ref{fig:Struct1}$(a)$, not surprisingly because the frequency is close.
+
+\begin{figure}
+$$
+\begin{array}{cc}
+\includegraphics[width=.45\linewidth]{fig/Z_Nyq_Re800_EP1.eps}&
+\includegraphics[width=.45\linewidth]{fig/Z_Nyq_Re1200_EP1.eps}\\
+\includegraphics[width=.45\linewidth]{fig/Z_Nyq_Re1600_EP1.eps}&
+\includegraphics[width=.45\linewidth]{fig/Z_Nyq_Re2000_EP1.eps}
+\end{array}
+$$
+\caption{Nyquist diagrams for $\beta = 1$. CHECK THE FIGURES !}
+\end{figure}
 
@@
 
-Finally, figure \ref{fig:Struct1} depicts the structure of the oscillating flow for the two first minima of $\delta$ for $Re = 1200$ (plots $a$ and $b$).
-One can observe that these perturbations display respectively 4 and 6 structures within the thickness of the hole.
-Note that a minimum of $\delta$ also exists for $Re =1200$ at $\Omega \approx 1$, but the value of $\delta$ remains positive.
-For $Re= 1500$, this first minimum becomes negative, and the
-corresponding structure is plotted in figure \ref{fig:Struct1}$(c)$.
-As expected, it displays only two vortical structures within the thickness of the hole.
-Finally, figure \ref{fig:Struct1}$(d)$ displays the case corresponding to the minimum of $|Z_{app}|$ for $Re = 1500$.
-The structure is much similar to the case plotted in \ref{fig:Struct1}$(a)$, not surprisingly because the frequency is close.
+\subsection{Case $\beta = 0.1$}
 
-\subsubsection{Case $\beta = 0.1$}
+IS IT USEFUL TOI KEEP THIS ????
 
@@
 
-\subsubsection{Case of a rounded hole}
+\clearpage
+
+\subsection{Parametric study}
+
+\begin{figure}
+$$
+\includegraphics[width=.7\linewidth]{fig/Re_beta.eps}%%{FIGURES/Seuils_Re.eps}
+$$
+\caption{ Thresholds for the onset of acoustic instability (A1 to A4) and of hydrodynamical instability (I1 and I2).}
+\label{fig:ThresholdsRe}
+\end{figure}
+
+\begin{figure}
+$$
+\includegraphics[width=.7\linewidth]{fig/Omega_beta.eps}
+$$
+$$
+\includegraphics[width=.7\linewidth]{fig/OmegaL_beta.eps}
+$$
+\caption{ Frequencies corresponding to acoustic instability (A1 to A4) and of hydrodynamical instability (I1 and I2).
+}
+\label{fig:ThresholdsRe}
+\end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Linear stability results}
+
+RESULTS : growth rates, eigenmodes, sensitivity,  Comparison with impedance-based predictions. THIS WILL BE DONE FOR $\beta = 1$.
+
+Figure : growth rate / freq. as function of Re
+
+Figure : eigenmodes, adjoint,  sensitivity.
+
+\begin{figure}
+\includegraphics[width=\linewidth]{fig/dir_adj_sens.png}
+\caption{ Eigenmode, Adjoint and sensitivity}
+\end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\clearpage
+
+\section{Case of a rounded hole}
+
+TO KEEP OR NOT TO KEEP ???
 
@@
 
-\section{Parametric study}
-
-\begin{figure}
-$$
-\includegraphics[width=.7\linewidth]{FIGURES/Seuils_Re.eps}
-$$
-\caption{ Thresholds for the onset of acoustic instability (A1 to A4) and of hydrodynamical instability (I1 and I2).
-}
-\label{fig:ThresholdsRe}
-\end{figure}
-
-\begin{figure}
-$$
-\includegraphics[width=.7\linewidth]{FIGURES/Seuils_Om.eps}
-$$
-\caption{ Frequencies corresponding to acoustic instability (A1 to A4) and of hydrodynamical instability (I1 and I2).
-}
-\label{fig:ThresholdsRe}
-\end{figure}
-
 \section{Conclusions}
@@
 \appendix
+
+\section{Details on complex mapping}
+
+\section{Upstream domain : modelling of a reactive cavity}
+
+THIS IS TO BE KEPT FOR PART III : "augmented incompressible model" to be compared to fully compressible case.
+
+As sketched in figure 1, the upstream domain is expected to originate from an upstream container of large dimension, and sufficiently far away from the hole the flow is assumed to be radially convergent.
+However, in the numerical implementation, it is required to specify a given geometry for this upstream domain.
+Here, we have chosen to assume that the upstream region is a closed cavity of rectangular cross-section, with radius $R_{cav}$ and length $L_{cav}$.
+The volumic flux condition is imposed by assuming that both the base-flow and the perturbation velocities are constant along the bottom of the cavity, noted $\Gamma_{in}$
+
+\be
+ {\bf u}_0 = - Q_0/S_{cav} {\vec n} ; \quad {\bf u'} = - q'/S_{cav} {\vec n} \quad {\mbox at } \Gamma_{in}
+\ee
+where $S_{cav}= \pi R_{cav}^2$ is the area of the bottom wall and ${\bf n}$ is the outward normal vector.
+The pressure levels $P_{in}$ and $p'_{in}$, which are required for the calculation of the mean pressure loss and the conductivity, are computed by averaging along the inlet boundary :
+\be
+ {P}_{in} = 1/S_{cav} \int_{\Gamma_{in}} P_0 2 \pi r dr ; \quad
+  {p'}_{in} = 1/S_{cav} \int_{\Gamma_{in}} p' 2 \pi r dr.
+\ee
+It was verified that if the dimensions of the cavity are large enough, the pressure is effectively nearly constant along the inlet boundary $\Gamma_{in}$.
+
+At the lateral wall of the cavity, noted $\Gamma_{lat}$, the physically relevant condition should be a no-slip condition.
+However, as the location of this wall is not really relevant, and in order to avoid the development of a boundary layer,
+we preferred to impose a stress-free condition, namely  
+\be
+ {\bf u} \cdot {\bf n} = 0 ; \quad \DP{({\bf u} \cdot {\bf x})}{r} = 0 \quad \mbox{  at  } \Gamma_{lat},
+ \ee
+which applies for both the base flow and the perturbation.
+
+In the sequel we set the dimensions of the upstream cavity as $L_{cav} = R_{cav} = 10 R_{hole}$,
+and verified that these values are large enough for the results to be insensible to these parameters.
+
 \section{Numerical validations}

### 2018-10-09 DEVELOPMENT_CASES/BLUNTBODY_IN_PIPE/SCRIPT_BLUNTBODY_L2.m

@@ -18,24 +18,22 @@ pause(0.1);
 
 
 %% Spectrum explorator 
-[ev,eigenmode] = SF_Stability(bf,'m',1,'shift',1+0.2i,'nev',20,'type','D','plotspectrum','yes');   
-pause;
-
+[ev,em] = SF_Stability(bf,'m',1,'shift',.2+0.3i,'nev',20,'type','D','plotspectrum','yes');   
+pause(0.1);
+ bf.mesh.xlim = [-2 6];
+ bf.mesh.ylim = [-1 1];
  figure;
-    subplot(2,1,1);plotFF(em(2),'ux1');title('Blunt body : steady mode')
-    subplot(2,1,2);plotFF(em(1),'ux1');title('Blunt body : unsteady mode')
-    saveas(gcf,'FIGURES/BluntBody_L6_D2_Modes','png');
-    pos = get(gcf,'Position'); pos(4)=pos(3)*.5;set(gcf,'Position',pos); % resize aspect ratio
-box on; pos = get(gcf,'Position'); pos(4)=pos(3)*1;set(gcf,'Position',pos);
-
+    subplot(2,1,1);plotFF(em(1),'ux1','symmetry','XA','colormap','parula');hold on;title('Blunt body : steady mode')
+    subplot(2,1,2);plotFF(em(3),'ux1','symmetry','XA','colormap','parula');hold on;title('Blunt body : unsteady mode')
+box on; pos = get(gcf,'Position'); pos(4)=pos(3)*.75;set(gcf,'Position',pos);
+saveas(gcf,'FIGURES/BluntBody_L2_D2_Modes','png');
+pause(0.1);
  
 %% COMPUTING THE UNSTEADY BRANCH (going backwards)
 Re_RangeI = [500:-20:300];
 guessI =  0.1654 + 0.8358i;
 EVI = SF_Stability_Loop(bf,Re_RangeI,guessI);
        
-
-        
 %% COMPUTING THE STEADY BRANCH (going backwards)
 Re_RangeS = [500:-50:300 280 :-20:140];
 guessS = 0.3;
@@ -49,6 +47,12 @@ plot(Re_RangeS,real(EVS),'-b',Re_RangeI,real(EVI),'-r');hold on;
 plot(Re_RangeS,0*real(EVS),':k');%axis
 title('growth rate lambda_r vs. Reynolds ; unstready mode (red) and steady mode (blue)')
[…]

### 2018-11-28 99_Documentation/ARTICLE_STABFEM/ARTICLE_ASME_Revision.tex
Coming back to HB1 / HB2 (and few minor fixes)

--- 2018-06-25 ARTICLE_STABFEM/ARTICLE_ASME_Submitted.tex
@@
 
-% color code for matlab (thanks to SOUAD !)
+% color code for Octave/Matlab (thanks to SOUAD !)
 \usepackage{listings} 
-\lstset{language=Matlab}
 \usepackage{color} %red, green, blue, yellow, cyan, magenta, black, white
@@
    breaklines=true,%
-   morekeywords={matlab2tikz},
+   morekeywords={Matlab2tikz},
    keywordstyle=\color{blue},%
@@
 
-\graphicspath{{./}{../CYLINDER/FIGURES/}}
+\makeatletter
+\lst@CCPutMacro
+    \lst@ProcessOther {"2D}{\lst@ttfamily{-{}}{-}}
+    \@empty\z@\@empty
+\makeatother
+
+\graphicspath{{./}{../../STABLE_CASES/CYLINDER/FIGURES/}}
 
@@
 } 
-to perform such calculations. The software combines program written in both FreeFem++ and Matlab languages. 
+to perform such calculations. The software combines program written in both FreeFem++ and Octave/Matlab languages. 
 FreeFem++ is used to generate and adapt the meshes and to solve the various linear problems arising in the analysis.
-Matlab is used as a driver to monitor the computations, perform the required loops over parameters, and plot the results.
+Octave/Matlab is used as a driver to monitor the computations, perform the required loops over parameters, and plot the results.
 \end{itemize}
@@
 
-Although we don't claim to invent any radically new method, our exposition and implementation contains a number of originalities making the computation particularly efficient in terms of computational time and memory\footnote{All the figures contained in the present paper can be processed by launching a single Matlab script {\sf SCRIPT\_CYLINDER\_ALLFIGURES.m} .
+Although we don't claim to invent any radically new method, our exposition and implementation contains a number of originalities making the computation particularly efficient in terms of computational time and memory\footnote{All the figures contained in the present paper can be processed by launching a single Octave/Matlab script {\sf SCRIPT\_CYLINDER\_ALLFIGURES.m} .
 On a MacbookPro (2018,  2.5Ghz, 16Go Ram) in single-core sequential execution,  and using mesh ${\mathbf M}_2$ as described in appendix B, the execution time is 203 seconds for the linear analysis (section 3), and 413 seconds for the nonlinear analysis.}.
@@
 
-%which is based on both FreeFem++ and Matlab.
+%which is based on both FreeFem++ and Octave/Matlab.
 %The fundamental case of a cylinder is used as a guideline to present the method, but the 
@@
 In our implementation, the algorithm is written in the Freefem++ solver {\em Newton\_2D.edp} 
-which is wrapped by the Matlab driver {\sf SF\_BaseFlow.m}.
+which is wrapped by the Octave/Matlab driver {\sf SF\_BaseFlow.m}.
 
@@
 The adjoint eigenmode also allows us to introduce the so-called {\em structural sensitivity tensor } that is defined as 
-\be{Structursens} 
-{\bf{S}}({\bf{x}}) = \frac{|| \hat{\bf u}^\dag|| \,\, ||\hat{\bf u}|| }{{\left<\hat{\bf u}^\dag, \hat{\bf u}\right>}},
+\be{StructurrTens} 
+{\bf{S}}({\bf{x}}) = \frac{ \hat{\bf u}^\dag \otimes \hat{\bf u} }{{\left<\hat{\bf u}^\dag, \hat{\bf u}\right>}},
 \ee 
@@
 The region of the flow where ${\bf{S}}({\bf{x}})$ reaches its maximum values is, thus, the region where the instability mechanism originates, and is often referred to as the {\em wavemaker region}.
+
+\be{Structursens} 
+S_e({\bf x}) =  {||{\bf{S}}({\bf{x}})||}_\infty \equiv \frac{ ||\hat{\bf u}^\dag({\bf x})|| \,\, ||\hat{\bf u}({\bf x})|| }{{\left<\hat{\bf u}^\dag, \hat{\bf u}\right>}},
+\ee
+
+\be{Endo} 
+S_w({\bf x}) =  \frac{  \hat{\bf u}^\dag({\bf x}) \cdot  {\cal LNS}_{\bf U} \, \hat{\bf u}({\bf x})  }{{\left<\hat{\bf u}^\dag, \hat{\bf u}\right>}}  
+= \lambda \frac{ \hat{\bf u}^\dag({\bf x}) \cdot \hat{\bf u}({\bf x}) }{{\left<\hat{\bf u}^\dag, \hat{\bf u}\right>}},
+\ee
 
@@
 If we want to compute a larger number of eigenvalues, we can revert to a generalized version of iterative methods, called Arnoldi methods\cite{Arnoldi51}.
-The shift-invert version of the Arnoldi method is in fact the most commonly used method of the current time and is at the basis of both the popular matlab function {\tt{eigs}} and the eigenvalue solver of FreeFem (i.e.
+The shift-invert version of the Arnoldi method is in fact the most commonly used method of the current time and is at the basis of both the popular Octave/Matlab function {\tt{eigs}} and the eigenvalue solver of FreeFem (i.e.
 ARPACK++).
@@
 
-In our implementation, the whole process is performed using the Matlab driver {\em SF\_AdaptMesh.m} ; the kind of adaptation  (to base flow only, to eigenmode, or to sensitivity) is decided by the the nature of the eigenmode object transmitted to this function.
+In our implementation, the whole process is performed using the Octave/Matlab driver {\em SF\_AdaptMesh.m} ; the kind of adaptation  (to base flow only, to eigenmode, or to sensitivity) is decided by the the nature of the eigenmode object transmitted to this function.
 
@@
 
-Let us consider now the matlab code reported in figure \ref{Listing2}.
+Let us consider now the Octave/Matlab code reported in figure \ref{Listing2}.
 First we build an initial mesh (line 1), and compute base flow solutions for increasing values of the Reynolds number up to $Re = 60$ (lines 3-9).
@@
 %\vspace{-.5cm}
-\includegraphics[width=.9 \linewidth]{Cylinder_EigenModeRe60_AdaptD.png}
+\includegraphics[width=.9 \linewidth]{Cylinder_EigenModeRe60_AdaptS.png}%{Cylinder_EigenModeRe60_AdaptD.png}
 %\vspace{-.5cm}
 %\vspace{-.5cm}
+
 \includegraphics[width=.9 \linewidth]{Cylinder_EigenModeAdjRe60.png}
 %\vspace{-.5cm}\vspace{-.5cm}
+%\includegraphics[width=.9 \linewidth]{Cylinder_SensitivityRe60.png}
+%\vspace{-.5cm}
+\caption{Contour plot of the streamwise velocity component: $(a)$ (Direct) Eigenmode; $(b)$ Adjoint mode at $Re=Re_c = 46.7$.}
+\label{fig:Eigenmode}
+\end{figure}
+
+\begin{figure}
 \includegraphics[width=.9 \linewidth]{Cylinder_SensitivityRe60.png}
+\includegraphics[width=.9 \linewidth]{Cylinder_EndogeneityRe60.png}
 %\vspace{-.5cm}
-\caption{Contour plot of the streamwise velocity component: $(a)$ (Direct) Eigenmode; $(b)$ Adjoint mode and ($c$) Structural sensitivity field for the cylinder's wake at $Re=Re_c = 46.7$.}
+\caption{ ($a$) Structural sensitivity field $S_w$ and $(b)$ Endogeneiry field $S_e$ (color : real part ; levels: imaginary part) for the cylinder's wake at $Re=Re_c = 46.7$.}
 \label{fig:Eigenmode}
@@
 %from a {\tt practical} point of view. The reader can reproduce all the figures presented 
-%in this paper by just running the Matlab code available in the StabFem repository.
+%in this paper by just running the Octave/Matlab code available in the StabFem repository.
 
@@
 Secondly, we intended to provide an easy to use software performing all these computations from a single program.
-In accordance with this objective, all the figures presented in the paper can be produced by launching a single Matlab program available on the website of the project.
+In accordance with this objective, all the figures presented in the paper can be produced by launching a single Octave/Matlab program available on the website of the project.
 
@@
 \mathbf{M}_2 \mbox{(Adapt on sensitivity) } & 2038 & 17885	& 0.0155 & 14.17 		& 0.02826 & 0.2046 	& 0.3909 	& 1.2014 	\\
-\mathbf{M}_3 \mbox{(Adapt on sensitivity, split) } & 7974 & 70651	& 0.00786 & 7.131  		& 0.0104 	& 0.0744 	&   0.0975 & 0.614   \\
-\mathbf{M}_4 \mbox{(Adapt on mode) } 	& 12080  & 103564		&0.00825	& 124.61		& 0.0229	& 0.143	& 0.0993	& 0.0934 \\
-\mathbf{M}_5 \mbox{(Adapt on adjoint) } 	& 3813 	& 33715		& 0.0108	& 13.95		& 0.0176 	& 0.114	& 0.127	& 1.177  \\
+\mathbf{M}_2' \mbox{(Adapt on sensitivity, split) } & 7974 & 70651	& 0.00786 & 7.131  		& 0.0104 	& 0.0744 	&   0.0975 & 0.614   \\
+\mathbf{M}_3 \mbox{(Adapt on endogeneity) } & 3749 & 32655	& 0.01542 & 12.7109  		& 0.09689 	& 0.1236 	&   0.2004 & 0.65775   \\
+\mathbf{M}_4 \mbox{(Adapt on mode) } 	& 12080  & 103564		&0.00825	& 12.461		& 0.0229	& 0.143	& 0.0993	& 0.0934 \\
+\mathbf{M}_5 \mbox{(Adapt on adjoint) } 	& 3813 	& 330715		& 0.0108	& 13.95		& 0.0176 	& 0.114	& 0.127	& 1.177  \\
 \hline
@@
 \mathbf{M}_2 & 4.075 &.  0.64348  	& 0.046719 + 0.74489i 		& 2.6153  & 0.69246 	& 0.84351 & 0.12789 & 1.7134 \\ 
-\mathbf{M}_3 & 4.0772 & 0.64391 	& 0.04684. +  0.74511i 		& 2.6141  & 0.69338 	& 0.84383 & 0.12799 & 2.048   \\ 
+\mathbf{M}_2' & 4.0772 & 0.64391 	& 0.04684 +  0.74511i 		& 2.6141  & 0.69338 	& 0.84383 & 0.12799 & 2.048   \\  
+\mathbf{M}_3 & 4.0749 & 0.64370 	& 0.04673 + 0.74538i		& 2.6140     & 0.69317	& 0.84408 & 0.12808 & 2.064   \\ 
 \mathbf{M}_4 & 4.0748 & 0.64402 	& 0.04676  + 0.74502i 		& 2.6130 	& 0.69034 	& 0.84371 & 0.12809 & 2.5905 \\
@@
 \caption{Results for mesh adaptation strategy ($Re = 60$) : Base-flow characteristics $L_x$ and $F_x$, linear eigenvalue $\lambda$, 
-Nonlinear self-consistent model characteristics  $\omega_{SC}$, $F_{y,1,c}$ and $A_E$. All the results can be optained using the matlab program
+Nonlinear self-consistent model characteristics  $\omega_{SC}$, $F_{y,1,c}$ and $A_E$. All the results can be optained using the Octave/Matlab script
 {\sf SCRIPT\_CYLINDER\_MESHCONVERGENCE.m}. }
@@
 Note that in our numerical implementation, the programs can actually be used to solve the SC model in the general case (with $\sigma\ne0$). 
-This can be controlled by assigning a nonzero value to the optional parameter \verb|sigma| of the  {\sf SF\_SelfConsistent.m} Matlab function.
+This can be controlled by assigning a nonzero value to the optional parameter \verb|sigma| of the  {\sf SF\_SelfConsistent.m} Octave/Matlab function.
 The interested reader will find on the website of the {\em StabFem} project a program {\sf SCRIPT\_CYLINDER\_NONLINEAR.m} which computes $A$ as function of $\sigma$ for $Re=100$, yielding identical results as displayed in figure 3 of \cite{MLugo2014}.
@@
 
+\section{Numerical implementation in FreeFem++}
+
+\lstset{language=c++,%
+   %basicstyle=\color{red},
+   breaklines=true,%
+   morekeywords={c++},
+   keywordstyle=\color{blue},%
+   morekeywords=[2]{1}, keywordstyle=[2]{\color{black}},
+   identifierstyle=\color{black},%
+   stringstyle=\color{mylilas},
+   commentstyle=\color{mygreen},%
+   showstringspaces=false,%without this there will be a symbol in the places where there is a space
+   numbers=left,%
+   frame=trBL,
+   numberstyle={\tiny \color{black}},% size of the numbers
+   numbersep=9pt, % this defines how far the numbers are from the text
+   emph=[1]{for,end,break},emphstyle=[1]\color{red}, %some words to emphasise
+   %emph=[2]{word1,word2}, emphstyle=[2]{style},   
+   }
+
+\begin{figure*}[t]
+\small
+\lstinputlisting[firstline=2, lastline=19]{Extract_From_Stab2D.edp}
+ \normalsize
+\caption{Illustration of the implementation of the Newton algorithm for base-flow computation (extract from FreeFem++ program {\em Newton2D.edp}).}
+\label{Listing2}
+\end{figure*}
+
+\begin{figure*}[t]
+\small
+\lstinputlisting[firstline = 24]{Extract_From_Stab2D.edp}
+ \normalsize
+\caption{Illustration of the implementation of the Newton algorithm for base-flow computation (extract from FreeFem++ program {\em Newton2D.edp}).}
+\label{Listing2}
+\end{figure*}
+
 %In this appendix we compare the results obtained with 8 different meshes, to demonstrate the efficency of the mesh adaptation process.
@@
 Figure \ref{ill_bsflow} illustrate the procedure adopted to compute the
-%base flow and the adapted mesh. Figure \ref{stabmesh} reports the Matlab code 
+%base flow and the adapted mesh. Figure \ref{stabmesh} reports the Octave/Matlab code 
 %adopted to adapt the mesh by using the information provided by both the base flow and the sensitivity field.

### 2018-11-28 99_Documentation/ARTICLE_STABFEM/SCRIPT_CYLINDER_Part1.m

@@ -5,8 +5,9 @@ bf = SF_BaseFlow(bf,'Re',60);
 bf = SF_Adapt(bf,'Hmax',10,'InterpError',0.01);
 [ev,em] = SF_Stability(bf,'shift',0.04+0.74i,'type','S')
 bf = SF_Adapt(bf,em,'Hmax',10,'InterpError',0.01);
-plotFF(bf,'mesh');  % Figure 2a
-plotFF(bf,'ux','Contour','on','Levels', [0,0] ); % Figure 2b
+SF_Plot(bf,'p','contour','psi','clevels',[-.02 0 .2 1 2 5],'cstyle','patchdashedneg',...
+      'xlim',[-1.5 4.5],'ylim',[0 3],'cbtitle','p','colormap','redblue','colorrange','centered',...
+      'boundary','on','bdlabels',2,'bdcolors','k'); % figure 2
 
 Re_Range = [2 : 2: 50]; Drag_tab = []; Lx_tab = [];
     for Re = Re_Range

### 2018-11-28 SOURCES_MATLAB/SF_HB1.m

@@ -4,8 +4,8 @@ function [meanflow, mode] = SF_HB1(meanflow, mode, varargin)
 %>
 %> usage : [meanflow,mode] = SF_HB1(meanflow,mode,[Param1, Value1,...])
 %>
-%> first argument is either a "baseflow" or 'meanflow"
-%> second argument is either an "eigenmode" or a "selfconsistentmode".
+%> first argument is either a "baseflow" or a "meanflow"
+%> second argument is either an "eigenmode" or a "harmonicmode".
 %>
 %> Parameters include :
 %>
@@ -66,7 +66,8 @@ switch (meanflow.mesh.problemtype)
         
 end
 
-if(exist([filenameBase '.txt'])==2)&&(exist([filenameHB1 '.txt'])==2)&&(exist([filenameHB2 '.txt'])==0)&&(strcmp(p.Results.specialmode,'NEW')==0)
+if(exist([filenameBase '.txt'])==2)&&(exist([filenameHB1 '.txt'])==2)...
+    &&(exist([filenameHB2 '.txt'])==0)&&(strcmpi(p.Results.specialmode,'NEW')==0)&&(p.Results.sigma==0)
     
     %%% Recover results from a previous calculation
     mydisp(1,['#### Self-Consistent (HB1) CALCULATION seems to be previously done... recover files ...' ]);
@@ -109,6 +110,8 @@ else
         mycp([ffdatadir, 'HBMode1.txt'],[filenameHB1 '.txt']);
         mycp([ffdatadir, 'HBMode1.ff2m'],[filenameHB1 '.ff2m']);
         mode = importFFdata(meanflow.mesh,[filenameHB1 '.ff2m']);
+        
+        myrm(filenameHB2); % to avoid possible bad interaction with HB2 
         
     else
         error(['ERROR in SF_HB1 : return code of the FF solver is ',value]);

### 2018-11-28 STABLE_CASES/CYLINDER/SCRIPT_CYLINDER_ALLFIGURES.m

@@ -83,8 +83,8 @@ figure();
 %    'contour','psi','clevels',[-.02 0 .2 1 2 5],'symmetry','XM');
 %SF_Plot(bf,'psi','xlim',[-1.5 4.5],'ylim',[-3 3],'contours','on','xystyle','off','symmetry','XA');
 
-SF_Plot(bf,'p','contour','psi','clevels',[-.02 0 .2 1 2 5],'xlim',[-1.5 4.5],'ylim',[0 3],...
-        'cbtitle','p','colormap','redblue','colorrange','centered','boundary','on','bdlabels',2,'bdcolors','k','cstyle','patchdashedneg');
+SF_Plot(bf,'p','contour','psi','clevels',[-.02 0 .2 1 2 5],'cstyle','patchdashedneg','xlim',[-1.5 4.5],'ylim',[0 3],...
+        'cbtitle','p','colormap','redblue','colorrange','centered','boundary','on','bdlabels',2,'bdcolors','k');
 box on; pos = get(gcf,'Position'); pos(4)=pos(3)*AspectRatio;set(gcf,'Position',pos); % resize aspect ratio
 set(gca,'FontSize', 18);
 saveas(gca,'FIGURES/Cylinder_BaseFlowRe60',figureformat);

### 2018-11-28 STABLE_CASES/CYLINDER/SCRIPT_CYLINDER_MESHTESTS.m

@@ -37,15 +37,15 @@ disp(['max : ' num2str(bf.mesh.deltamax)]);
 disp(' ' );
 
 bf=SF_BaseFlow(bf,'Re',60);
-[ev,em] = SF_Stability(bf,'shift',0.47+.74i,'type','S');
+[ev,em] = SF_Stability(bf,'shift',0.04+.74i,'type','D');
 disp('##### EIGENVALUE COMPUTATION');
 
 disp([' Eigenvalue : ' , num2str(ev)]);
 
-[meanflow,mode] = SF_SelfConsistentDirect(bf,em,'Re',60,'sigma',0.04,'Fyguess',0.015);
-[meanflow,mode] = SF_SelfConsistentDirect(meanflow,mode,'Re',60,'sigma',0.03);
-[meanflow,mode] = SF_SelfConsistentDirect(meanflow,mode,'Re',60,'sigma',0.02);
-[meanflow,mode] = SF_SelfConsistentDirect(meanflow,mode,'Re',60,'sigma',0.0);
+[meanflow,mode] = SF_HB1(bf,em,'Re',60,'sigma',0.04,'Fyguess',0.015);
+[meanflow,mode] = SF_HB1(meanflow,mode,'Re',60,'sigma',0.03);
+[meanflow,mode] = SF_HB1(meanflow,mode,'Re',60,'sigma',0.02);
+[meanflow,mode] = SF_HB1(meanflow,mode,'Re',60,'sigma',0.0,'specialmode','NEW');
 
 disp('##### NONLINEAR SELFCONSISTENT COMPUTATION');
 disp(['mean Fx : ' num2str(meanflow.Fx)]);
@@ -71,7 +71,7 @@ bf=SF_Adapt(bf,em,'Hmax',10);
 
 % plot the mesh (full size)
 bf.xlim = [-40 80]; bf.ylim=[0,40];
-plotFF(bf,'mesh');
+SF_Plot(bf,'mesh');
 %title('Mesh M2 (full size)');
 box on; pos = get(gcf,'Position'); pos(4)=pos(3)*.4;set(gcf,'Position',pos); % resize aspect ratio
 set(gca,'FontSize', 18);
@@ -79,7 +79,7 @@ saveas(gca,'FIGURES/Cylinder_Mesh2_Full',figureformat);
 
 % plot the mesh (zoom)
 bf.xlim = [-1.5 4.5]; bf.ylim=[0,3];
[…]

### 2018-11-29 99_Documentation/ARTICLE_STABFEM/ARTICLE_ASME_Revision.tex
Revision of the StabFem paper

@@
 %%% first author
-\author{D. Fabre$^{(a)}$,  V. Citro$^{(b)}$,  D. Ferreira Sabino$^{(a)}$, P. Bonnefis$^{(a)}$,  \& F. Giannetti$^{(b)}$
+\author{D. Fabre$^{(a)}$,  V. Citro$^{(b,a)}$,  D. Ferreira Sabino$^{(a)}$, P. Bonnefis$^{(a)}$,  F. Giannetti$^{(b)}$ \& M. Pigou$^(a)$ 
     \affiliation{
@@
 plane Poiseuille flow \cite{Dreid2004}.
-This implies that the streamwise and the spanwise base-flow gradients vanish and, as a consequence, it is possible to consider only one (streamwise) velocity component.
-Thus, the stability problem requires a \textit{local} numerical resolution, i.e.
-a one-dimensional problem.
+In this case, thanks to a Fourier decomposition in the two homogeneous directions, it is possible to reduce the stability problem to  a one-dimensional problem, an approach usually referred to as \textit{local stability approach}.
 On the other hand,  when there are at least two spatial variables, the class of methods suited to solve such problems are generally called {\em global stability approaches}.
@@
 {\em Adjoint methods} are an important extension \cite{GiannettiLuchini},\cite{Marquet}; they can give insight into the sensitivity of the flow to intrinsic or extrinsic contributions.
-{\em Nonlinear stability approaches} \cite{MLugo2014}, \cite{SippLebedev} have also been developed in order to extend the range of applicability of the approach towards large amplitude perturbations.
+{\em Nonlinear stability approaches} \cite{SippLebedev} \cite{MLugo2014} have also been developed in order to extend the range of applicability of the numerical methods towards large amplitude perturbations.
 
@@
 \begin{itemize}
-\item
+\item[-]
 First, we give a concise but self-contained exposition of the main concepts and 
 specific numerical methods pertaining to global stability, including basic linear stability, adjoint-based sensitivity, as well as the most recent nonlinear developments.
-\item
+\item[-]
 Secondly we offer an open-source and user-friendly software called  {\em StabFem} %\cprotect 
 \footnote{The StabFem software may be obtained at the following url : \\
-\url{https://github.com/erbafdavid/StabFem}
-%{\sf \color{blue} https://github.com/erbafdavid/StabFem}
+\url{https://www.gitlab.com/stabfem/StabFem}. 
 } 
-to perform such calculations. The software combines program written in both FreeFem++ and Octave/Matlab languages. 
+to perform such calculations. The software combines programs written in both FreeFem++ \cite{MR3043640} and Octave/Matlab languages. 
 FreeFem++ is used to generate and adapt the meshes and to solve the various linear problems arising in the analysis.
 Octave/Matlab is used as a driver to monitor the computations, perform the required loops over parameters, and plot the results.
+The software is developed as a collaborative project and intended as multiplatform and easily customizable to a variety of cases.
 \end{itemize}
@@
 % 1868 seconds using mesh M4
-The most notable originalities are the systematic use of mesh adaptation (\S 2 and 3), the use of simple shift-invert instead of Arnoldi (\S 3), and a reformulation and simplification of the nonlinear self-consistent approach of Mantic-Lugo et al  (\S 4).
+The most notable originalities are the systematic use of mesh adaptation (\S 2 and 3), the use of simple shift-invert instead of Arnoldi (\S 3), and a reformulation and simplification of the self-consistent approach of Mantic-Lugo in the framework of the Harmonic Balance formalism   (\S 4).
 
@@
 The procedure of Newton iteration is to solve iteratively this set of equations up to convergence.
-In our implementation, the algorithm is written in the Freefem++ solver {\em Newton\_2D.edp} 
-which is wrapped by the Octave/Matlab driver {\sf SF\_BaseFlow.m}.
+In our implementation, the algorithm for a 2D incompressible flow is written in the Freefem++ solver {\em Newton\_2D.edp} (an extract of this code featuring the implementation of the Newton loop is given in appendix E).
+This FreeFem++ solver is wrapped by the Octave/Matlab driver {\sf SF\_BaseFlow.m}.
 
@@
 \paragraph{Direct eigenvalue problem}
-We study the onset of the instability within the linear theory by using a normal-mode analysis:
+We study the onset of the instability within the linear theory considering perturbations with eigenmode form:
 \be{startmodepropre}
@@
 where $\lambda = \sigma + i \omega$ is the eigenvalue, $\sigma$ the amplification rate,
-$\omega$ the oscillation rate, $\hat{{\bf u}},\hat{p}$ the eigenmodes, and $\epsilon$ a small parameter.
-The eigenmodes and the eigenvalues are the solution of the following eigenproblem:
+$\omega$ the oscillation rate, $\hat{{\bf u}},\hat{p}$ the eigenmode (also called direct eigenmode, to distinguish with the adjoint eigenmode introduced below), 
+and $\epsilon$ a small parameter. The eigenmodes and eigenvalues are the solution of the following eigenproblem:
  \be{LEP}
@@
 
-\paragraph{Adjoint eigenvalue problem and structural sensitivity}
-Developed in the two past decades, the concept adjoint modes has now become an unavoidable complement to the linear global stability approach.
-We here give a short summary of the definition and usefulness of this concept,
-we refer to Luchini \& Bottaro\cite{LucBott2014} for further details.
+\paragraph{Adjoint eigenvalue problem, structural sensitivity, and wavemaker characterization}
+Developed in the two past decades, the concept adjoint eigenmodes has now become an unavoidable complement to the linear global stability approach.
+We here give a short summary of the definition and usefulness of this concept and refer the reader to Luchini \& Bottaro\cite{LucBott2014} for further details.
 First of all, the {\em adjoint linearised Navier-Stokes operator} ${\cal LNS}^\dag$ is defined thanks to the following 
@@
 
-The adjoint eigenmode also allows us to introduce the so-called {\em structural sensitivity tensor } that is defined as 
+Examination of the structure of the adjoint eigenmodes gives access to a number of informations about the instability mechanism which are not visible when examining only the direct eigenmodes.
+First, a simple examination the dissimilarity between direct and adjoint eigenmodes is an indication of the nonnormality of the linear operator, mostly associated to the convection term in open flows \cite{Jmc2005}.
+Secondly, in a more elaborated way, the product of both fields allows to define the the so-called {\em structural sensitivity tensor } defined as
 \be{StructurrTens} 
-{\bf{S}}({\bf{x}}) = \frac{ \hat{\bf u}^\dag \otimes \hat{\bf u} }{{\left<\hat{\bf u}^\dag, \hat{\bf u}\right>}},
-\ee 
-which has became popular in the recent years.
-%is called the structural sensitivity of the eigenmode. 
-This quantity is a direct and practical measure of the effect of perturbations of the linear operator on the eigenvalue.
-The region of the flow where ${\bf{S}}({\bf{x}})$ reaches its maximum values is, thus, the region where the instability mechanism originates, and is often referred to as the {\em wavemaker region}.
-
+{\bf{S}}({\bf{x}}) = \frac{ \hat{\bf u}^\dag \otimes \hat{\bf u} }{{\left<\hat{\bf u}^\dag, \hat{\bf u}\right>}}.
+\ee 
+As formalized by \cite{GiannettiLuchini} (following ideas previously proposed by \cite{hill1992theoretical}), this quantity quantifies how an eigenvalue is 
+affected by the introduction of localized feedback of the flow perturbation on itself.
+It thereby indicates the spatial regions where closed-loop control using a localized activator will be most efficient.
+Giannetti \& Luchini (2007) conjectured that those regions where such an extrinsic feedback induce the strongest change of the eigenvalue are also the most significant regions considering the intrinsic feedback mechanisms that underpin the genuine eigenmode dynamics.
+Following this idea, structural sensitivity has thus become a popular way to characherize the  {\em wavemaker region} where the instability mechanism originates.
+The structural sensitivity being a tensor, is is convenient to simply represent its norm $S_w$, often simply called 'the wavemaker':
 \be{Structursens} 
-S_e({\bf x}) =  {||{\bf{S}}({\bf{x}})||}_\infty \equiv \frac{ ||\hat{\bf u}^\dag({\bf x})|| \,\, ||\hat{\bf u}({\bf x})|| }{{\left<\hat{\bf u}^\dag, \hat{\bf u}\right>}},
-\ee
-
+S_w({\bf x}) =  {||{\bf{S}}({\bf{x}})||}_\infty \equiv \frac{ ||\hat{\bf u}^\dag({\bf x})|| \,\, ||\hat{\bf u}({\bf x})|| }{{\left<\hat{\bf u}^\dag, \hat{\bf u}\right>}},
+\ee 
+More recently, \cite{marquet2015endogeneity} reconsidered the question of identification of the active flow regions that drive the instabilities.
+They argued that such regions might be better identified by a quantity called the {\em endogeneity} and defined as
 \be{Endo} 
-S_w({\bf x}) =  \frac{  \hat{\bf u}^\dag({\bf x}) \cdot  {\cal LNS}_{\bf U} \, \hat{\bf u}({\bf x})  }{{\left<\hat{\bf u}^\dag, \hat{\bf u}\right>}}  
+S_e({\bf x}) =  \frac{  \hat{\bf u}^\dag({\bf x}) \cdot  {\cal LNS}_{\bf U} \, \hat{\bf u}({\bf x})  }{{\left<\hat{\bf u}^\dag, \hat{\bf u}\right>}}  
 = \lambda \frac{ \hat{\bf u}^\dag({\bf x}) \cdot \hat{\bf u}({\bf x}) }{{\left<\hat{\bf u}^\dag, \hat{\bf u}\right>}},
 \ee 
+This definition has several advantages.
+In particular, being a complex quantity, it allows to distinguish the flow regions which contribute respectively to the oscillation frequency and the growth rate, hence giving more insight into the intrinsic flow dynamics.
+This quantity is also potentially useful for mesh design, as will be discussed in section 2.3.
 
@@
 
-When a good estimation of the eigenvalue is available, this method converges very rapidly and is very efficient, but it can only provide a single eigenvalue.
+When a good estimation of the eigenvalue is available, this method is very efficient and converges very rapidly.
+On the other hand, it can only provide a single eigenvalue.
 If we want to compute a larger number of eigenvalues, we can revert to a generalized version of iterative methods, called Arnoldi methods\cite{Arnoldi51}.
-The shift-invert version of the Arnoldi method is in fact the most commonly used method of the current time and is at the basis of both the popular Octave/Matlab function {\tt{eigs}} and the eigenvalue solver of FreeFem (i.e.
+The shift-invert version of the Arnoldi method is in fact the most commonly used method of the current time and is at the basis of both the popular Octave/Matlab function {\tt{eigs}} and the standard eigenvalue solver of FreeFem (i.e.
 ARPACK++).
-Our implementation in StabFem allows to chose between single eigenvalue computation (power method) and multiple eigenvalue computation (Arnoldi).
-The selection is made according to the parameter \verb|nev|  (i.e.
+%Our implementation in StabFem allows to chose between single eigenvalue computation (power method) and multiple eigenvalue computation (Arnoldi). 
+For the case of the 2D incompressible flow, resolution of the eigenvalue problem (including adjoint, sensitivity and endogeneity) is done by the FreeFem++ solver {\em Stab2D.edp}; an extract of this solver featuring the implementation of the shift-invert algorithm is displayed in appendix E.
+The latter is wrapped by the Octave/Matlab driver {\em SF\_Stability.m} which accepts a number of optional parameters.
+For instance, the selection between shfift-invert and Arnoldi is made according to the parameter \verb|nev|  (i.e.
 number of requested eigenvalues) transmitted to the driver.
+(an extract of this code featuring the implementation of the Newton loop is given in appendix E).
 
@@
 \begin{figure}
-%\vspace{-.5cm}
-%\includegraphics[width=.9 \linewidth]{Cylinder_Mesh.png}
-%\vspace{-.5cm}
-%\vspace{-.5cm}
-\includegraphics[width=.9 \linewidth]{Cylinder_BaseFlowRe60.png}
-%\vspace{-1.cm}
-\caption{Base flow (streamwise velocity component) for the flow over a cylinder at $Re=60$.}
+\includegraphics[width= \linewidth]{Cylinder_BaseFlowRe60.png}
+\caption{Base flow for the flow over a cylinder at $Re=60$. Pressure field (color levels) and streamlines (iso-levels of the streamfunction $\psi$). }
 \label{fig:Baseflow}
@@
 This is easily done with FreeFem, as the  AdaptMesh procedure can be used with several objective functions.
-We have experimented three different ideas.
-The first is to adapt the mesh to the base flow and the structure of the leading eigenmode.
-The second idea is to use the adjoint mode instead of the direct mode for mesh adaptation.
-The third idea is to adapt the mesh to the base flow and the structural sensitivity.
-This idea is supported by Giannetti \& Luchini\cite{GiannettiLuchini} who showed that the accuracy of the stability results for the flow past a circular cylinder is strictly related to the mesh characteristics in the wavemaker region, i.e.
-the region where the structural sensitivity reaches its maximum values.
-Results show that the three procedures yield the same values for base flow characteristics and eigenvalues with less than $0,3\%$ deviation, but that compared to the two previous ideas mesh adaptation to structural sensitivity result in a mesh with much less grid vertices, leading to much faster computations (see appendix A).
-So, if one is interested only in the eigenvalues, for instance to plot growth rates as function of Reynolds or to identify the critical Reynolds number, mesh adaptation to the sensitivity gives the best option.
-On the other hand, if one is interested in the detailed structure of the eigenmode, which may extend far away from the wavemaker region, it is advised to use mesh adaptation on the eigenmode.
-
-In our implementation, the whole process is performed using the Octave/Matlab driver {\em SF\_AdaptMesh.m} ; the kind of adaptation  (to base flow only, to eigenmode, or to sensitivity) is decided by the the nature of the eigenmode object transmitted to this function.
+We have experimented four different strategies.
+The first (D strategy) is to adapt the mesh to the base flow and the structure of the leading direct eigenmode.
+A second strategy (A) is to use the adjoint mode instead of the direct mode for mesh adaptation.
+However, as the sensitivity of the eigenvalue to perturbations of the operator (including discretization errors) is more closely linked to structural sensitivity concepts, it sounds a better idea to use either the 'wavemaker' $S_w$ or the endogeneity $S_e$ to adapt the mesh, leading to the two last experimented strategies, called S and E.
+Note that using the S strategy was already experimented in {\em \cite{GiannettiLuchini} for the wake of a cylinder (IS THAT THE RIGHT REFERENCE ??}).
+Mesh adaptation using the scalar product of the direct and adjoint eigenmodes (which turns out to be equivalent to the E strategy introduced here considering the definition of the endogeneity) was also proposed in {(\em DIOGO PLEASE PUT THE REF OF THE PAPER OLIVIER SHOWED US, AND COMPLETE THE SENTENCE}.
+A detailed comparison of the four strategies is reported in appendix A.
+It is shown that for the case of a cylinder, all strategies give the same values for base-flow drag, eigenvalues and several properties of the nonlinear limit cycle (see sec.
+4) with less than $0,3\%$ deviation, but that the A, E and especially the S strategy lead to significantly lower number of grid points compared to the D strategy.
+The practical conclusions of this study are the following recommendations :
+
+\begin{itemize}
+\item[-] 
+First, if one is interested only in the eigenvalues, for instance to plot growth rates as function of Reynolds or to identify the critical Reynolds number, The A, E or S strategies are the best options.
+In the case of the cylinder, the S strategy leads to the lightest mesh.
+The E strategy results in a more refined mesh because the function $S_e$ is complex and displays more gradients than the real-valued function $S_w$ (as will be illustrated in figure 6) ; hence the sensitivity revealed by the phase of $S_e$, which may be significant, is not capture by using the simpler function $S_w$.
+In the case of the flow around a cylinder,  this loss of information has no practical effect on the results, but for usage with more complex flows, or recommendation for future studies will be to privilege the E strategy.
+\item[-] 
+The situation is different if one wants to design a mesh allowing to study the structure of the flow in the whole domain (for instance for plotting its structure).
+In that case, using A,E or S strategy will allow to accurately compute the eigenvalue and the structure of the mode in the wavemaker region, but will not allow a proper resolution in the regions located far away where the direct mode may reach large amplitude.
+This is particularly the case for open flows characterized by large spatial convective amplifications.
+In such cases the D strategy is the only way to get a proper description of the eigenmode in the whole domain.
+\end{itemize}
+
+In our implementation, the whole process of mesh adaptation (including projection and recomputation of the base flow on the new mesh) is monitored using the Octave/Matlab driver {\em SF\_AdaptMesh.m} ; the kind of adaptation  (to base flow only (BF), or D, A, S , E strategies) is decided by the the nature of the objects transmitted to this function.
+In the current implementation it is possible to adapt the mesh to as much as 8 fields of diverse nature (for instance, multiple eigenmodes along with their adjoint fields, harmonic-balance fourirer components, etc...)
 
@@
 Note that we take advantage of the symmetry properties of the problem to use a half-domain for resolution.
-%We impose a no-slip condition $(u=0,v=0)$ on the cylinder surface (${\Gamma_{cil}}$), a uniform velocity $(u=1,v=0)$ at the inflow 
-%$x/D=-40$ and a no-stress condition at the outlet $x/D=80$ and on the lateral boundaries of the computational domain $y/D=\pm 40$.
-
-%Domain dimension $[-40,80]x[0,40]$. No-stress conditions at outlet AND LATERAL BOUNDARY.
+
 The hydrodynamic loads can be obtained by integrating the stress tensor over the cylinder surface.
@@
 First we build an initial mesh (line 1), and compute base flow solutions for increasing values of the Reynolds number up to $Re = 60$ (lines 3-9).
-Then we perform the mesh adaptation with the structural sensitivity, as explained previously (line 13). 
-The resulting mesh, depicted in figure \ref{fig:mesh2}, is used for the rest of the computations presented in this paper (except for computing
-the energy of the nonlinear perturbation displayed in figure \ref{fig:HB_SC_DATA_COMP}$(d)$ which requires a heavier mesh). 
+Then we perform the mesh adaptation with S strategy, as explained previously (line 13). 
+The resulting mesh, depicted in figure \ref{fig:mesh2}, is used for the rest of the computations presented in this paper (except for plotting the structure of the direct eigenmode in figure 5$a$ and computing the energy of the nonlinear perturbation displayed in figure \ref{fig:HB_SC_DATA_COMP}$(d)$ which a heavier mesh obtained with adaptation strategy D).
 Appendix A presents additional test regarding mesh convergence, and demonstrate that results obtained with the resulting mesh are trustable within $0.3\%$ accuracy for the eigenvalue.
@@
 An illustration of the structure of the base flow is given in figure \ref{fig:Baseflow},  for the case $Re = 60$.
-The contour line on this plot corresponds to the iso-level $u_x = 0$, and allows to visualize the recirculation region associated to this base flow.
+This figure is obtained using the Matlab/Octave function {\em SF\_Plot.m}, which is built over the function {\em ffpdeplot.m} developed by M.
+Meister and also distributed on an open-source basis
+\footnote{\url{https://github.com/samplemaker/freefem\_matlab\_octave\_plot}}.  
+This function allows a number of possibilities for plotting data on unstructured meshes, including color plots, isolevels, streamlines, quiver plots, etc..
+The choice of parameters used here (lines 8-10 of the script in figure \ref{Listing2})  allows to plot both the pressure field and selection of streamlines (through isocontours of the streamfunction $\psi$).
+This representation allows to easily visualize the extension of the recirculation region.
 In accordance with figure \ref{fig:LxandDrag}$(b)$, for $Re = 60$ the recirculation length is $L_x = \approx 4.07$.
-
-%\subsection{Implementation}
-
-%\subsection{Application to the cylinder}
-
-%\clearpage
-
-%We now review the main concepts of linear stability approach and explain how such calculations are implemented in our software.
 
@@
 %\vspace{-.5cm}
-\caption{ ($a$) Structural sensitivity field $S_w$ and $(b)$ Endogeneiry field $S_e$ (color : real part ; levels: imaginary part) for the cylinder's wake at $Re=Re_c = 46.7$.}
-\label{fig:Eigenmode}
+\caption{ ($a$) {\em Wavemaker}  field $S_w$ and $(b)$ {\em Endogeneity} field $S_e$ (color : real part ; levels: imaginary part) for the cylinder's wake at $Re=Re_c = 46.7$.
+The red line represents the streamline bounding the recirculation region.}
+\label{fig:StructEndo}
 \end{figure}
@@
 
-We investigate the stability of the base flow fields by performing a parametric study of the eigenproblem 
-(\ref{Eigen_matricial}). In this way, we determine the critical Reynolds number $Re_c$ at with the steady base flow
-first becomes unstable: to this end it is useful to remember that a flow state is 
-linearly unstable when the real part of 
-the leading eigenvalue, i.e. the growth rate, is positive. 
-Figure \ref{fig:SigmaOmega} shows growth rate and the Strouhal number 
-$St=a\omega/2 \pi U_{\infty}$ as a function of the 
-Reynolds number. It is easy to check that the critical Reynolds number is about 47 
-for the first mode. 
-The associated direct eigenmode is depicted in figure \ref{fig:Eigenmode}. The 
-spatial structure of this mode 
-extends downstream of the bluff body and is characterized by streamwise 
-extended spatial disturbances. 
-On the other hand, the adjoint mode is highly localized near the cylinder 
-on the upper (and lower) side of the body surface. 
-We recall that the adjoint field provides useful information about the mechanism to
-flow receptivity to momentum forcing and mass injection.
-We note also that this receptivity decays rapidly both upstream and downstream 
-of the bluff body.
-
-The structural sensitivity field displayed in figure \ref{fig:Eigenmode}c)
-is obtained by evaluating eq. \ref{Structursens}.
-In particular, we plot the spectral norm of the sensitivity tensor, it 
-gives the maximum possible coupling among the velocity components. 
-This spatial map can be used to identify the flow region where the 
-instability mechanism acts.
+We investigate the stability of the base flow field by performing a parametric study of the eigenproblem (\ref{LEP}).
+In this way, we determine the critical Reynolds number $Re_c$ at with the steady base flow first becomes unstable: to this end it is useful to remember that a flow state is linearly unstable when the real part of  the leading eigenvalue, i.e.
+the growth rate, is positive.
+In our implementation, parametric study is done by the loop over Reynolds corresponding to lines 21-30 of the script in figure \ref{Listing2}.
+Note that at line 26 the options {\em 'shift, 'cont' ,'guess', em} transmitted to the driver {\em SF\_Stability} allow to use an optimum value for the shift interpolated using the previous computations, and a guess value to initialize the shift-invert procedure corresponding to the previously computed eigenmode.
+Both these ideas very efficiently accelerate the calculations (the shift-invert procedure typically converges after only 2-3 iterations).
+
+ Figure \ref{fig:SigmaOmega} shows growth rate and the Strouhal number $St=a\omega/2 \pi U_{\infty}$ as a function of the Reynolds number.
+It is easy to check that the critical Reynolds number is about 47 for the first mode.
+The associated direct eigenmode is depicted in figure \ref{fig:Eigenmode}.
+The spatial structure of this mode extends downstream of the bluff body and is characterized by streamwise extended spatial disturbances.
+On the other hand, the adjoint mode is highly localized near the cylinder  on the upper (and lower) side of the body surface.
+We recall that the adjoint field provides useful information about the mechanism to flow receptivity to momentum forcing and mass injection.
+We note also that this receptivity decays rapidly both upstream and downstream of the bluff body.
+
+The wavemaker $S_w$ and endogeneity $S_e$ fields, introduced in section 2.2, are displayed in figure \ref{fig:StructEndo}.
+As discussed in section 2.2, both these quantities allow to identify the 'active' flow regions responsible for the instability mechanism.
+The real quantity $S_w$ indicates that the most active region  roughly coincides with the recirculation bubble.
+The endogeneity $S_e$ give more information.
+The sign of the real part (color levels)  indicate that the two most destabilizing regions are the boundary layer at the top of the cylinder and the shear layer bonding the recirculation region, and that the region of the stagnation point and the exterior of the recirculation region are destabilizing.
+The imaginary part (isolevels) indicate that the frequency selection occurs in the shear layer region.
 
@@
 \end{center}
-\caption{Comparison between the weakly nonlinear results (WNL) the harmonic balance data (HB), and baseflow/linear results : Strouhal number $(a)$, Mean drag $(b)$, amplitude of oscillating lift $(c)$, Energy-amplitude of the nonlinear perturbation $(d)$ and recirculation lenght of mean/base flows ($e)$.
+\caption{Comparison between the weakly nonlinear results (WNL), the harmonic balance data (HB1), and baseflow/linear results : Strouhal number $(a)$, Mean drag $(b)$, amplitude of oscillating lift $(c)$, Energy-amplitude of the nonlinear perturbation $(d)$ and recirculation lenght of mean/base flows ($e)$.
 %c_x should be consistent with the drag definition given at beginning
@@
 
-\subsection{The Self-Consistent model  }
-\paragraph{SC model : analysis }
+\subsection{The Self-Consistent model reformulated in the Harmonic-Balance formalism }
+\paragraph{Analysis}
 
@@
 
-%Figure \ref{fig:SC100} shows the results of the self-consistent model at Re=100.
-
-%\paragraph{{\color{red}First Order Harmonic balance: equations and procedure} }
-
-%\begin{figure}
-%\begin{center}
-%\includegraphics[width=.9 \linewidth]{Cylinder_Lx_Re_HB.png}
-%\end{center}
-%\caption{Flow past a circular cylinder: length of the wake bubble (measured from the 
-%rear stagnation point) for different Reynolds number. Comparison between the base flow bubble and the mean flow bubble computed by using the harmonic balance.}
-%\label{fig:recirculation_lengh}
-%\end{figure}
-
-%As discussed above, the Self-Consistent model was initially presented by the authors as a rational way to explain the dynamics in terms of a stability analysis of the {\em mean flow}.
-Furthermore, the resolution method presented by the authors, which involves a double iteration loop, is not easy to implement and not particularly efficient.
-
-%If one is only interested by the properties of the limit cycle and not the transient, the model is actually equivalent to a Fourier series, and amenable to a more direct resolution method. 
 We thus start with a truncated Fourier decomposition of the limit cycle under the form:
@@
 where ${\bf u }_{1,c}$ and ${\bf u }_{1,s}$ are two {\em real} fields describing the nonlinear perturbation at two instants separated by a quarter-period of oscillation, and $\omega$ is the (real) oscillation frequency of the limit cycle (which is not known a priori).
-The connection with the definition of Manti\v{c}-Lugo is as follows :
-\be{HBtoSC}
-\left( {\bf u }_{1,c} - i {\bf u }_{1,s} \right) = 2 A_{sc} \tilde{{\bf u }}_1.
-\ee
-
-Injecting this ansartz into the Navier-Stokes equations and taking the mean value and the first Fourier component leads to the following coupled equations:
+
+Injecting this ansatz into the Navier-Stokes equations and taking the mean value and the first Fourier component leads to the following coupled equations:
 \begin{subequations}\label{eq_principal}
@@
 Note that the amplitude $A_{sc}$, which was considered as a key parameter in the original model of \cite{MLugo2014}, 
-does not appear in the simplified version discussed here. This parameter can easily be computed a posteriori as 
+does not appear in the simplified version discussed here. The connection between our parametrization and that of Manti\v{c}-Lugo is as follows :
+\be{HBtoSC}
+\left( {\bf u }_{1,c} - i {\bf u }_{1,s} \right) = 2 A_{sc} \tilde{{\bf u }}_1.
+\ee 
+Considering their normalization choice, the parameter $A_{sc}$ of \cite{MLugo2014},  can be easily deduced from our results as follows :
 $A_{sc} = \sqrt{2 \int_\Omega ( |{\bf u }_{1,c}|^2+ |{\bf u }_{1,s}|^2) d S} $.
 
-\paragraph{SC model: implementation and results for a cylinder}
-
-Mathematically, the system (\ref{HBEq0}, \ref{HBEq1}, \ref{HBEq1b}, \ref{HBphase}) for the unknown $[{\bf u }_m, {\bf u }_{1,c}, {\bf u }_{1,s}, \omega]$ is well posed.
-Instead of the double-loop resolution procedure of \cite{MLugo2014}, we propose a direct resolution using a Newton iteration just as explained for the base flow in section 2.
-%To allow resolution, we separate the mode into real and imaginary part, by writing ${\bf u }_1 = {\bf u }_{1,r} +  i {\bf u }_{1,i} $.
-We then assume that we know a {\em guess}:
+\paragraph{SC/HB1 model: a direct algorithm }
+
+When reformulated in this way, the nonlinear problem addressed by the self-consistent model actually reduces to the restriction to order one of a more general class of methods called  harmonic balance methods (HB) (DIOGO PUT A FEW REFERENCES HERE \cite{}).
+The development of such methods, or related ones such the time-spectral method (REFS ?)  and the search for efficient numerical implementation to solve such problems is currently an active field of development in the fluid dynamics community.
+When considering HB development with a large order of terms, direct resolution by inversion of the full matrix is not achievable.
+Methods including iterative solvers and efficient preconditioning are currently under development (O.
+Marquet, personal communication).
+
+On the other hand, when restricting as here to a truncation to order one (HB1 method), the use of adapted meshes makes the building and inversion of the matrix accessible on standard computers.
+We thus propose here a simple algorithm based on a direct resolution using a Newton iteration, just as explained for the base flow in section 2.
+This method is proposed as an efficient alternative compared to the double-loop resolution procedure of \cite{MLugo2014}.
+
+The algorithm assumes that we know a {\em guess} for the full state-vector defined as follows:
 $$
@@
 Mesh convergence issues for the nonlinear calculations are discussed in appendix A.
-It is shown that the mesh $\mathbf{M}_2$ adapted to {\em structural sensitivity} is sufficient to yield converged results within $0.3\%$ accuracy for all quantities considered here, with the exception of the energy-amplitude $A_E$ which requires the more refined mesh $\mathbf{M}_4$ obtained by adaptation to the structure of direct eigenmode.\footnote{In terms of computational cost, on a standard laptop the program  \ref{fig:listingNL} requires approximatively 413 seconds using  mesh $\mathbf{M}_2$ and 31 minutes using mesh $\mathbf{M}_4$.}
-
-Lines 10-17 of the script shown in figure \ref{fig:listingNL}  explain how to solve SC model using the StabFem software, 
-for the wake of a cylinder in the range $Re \in [47-100] $.
+It is shown that the mesh $\mathbf{M}_2$ designed using 'S' strategy is sufficient to yield converged results within $0.3\%$ accuracy for all quantities considered here, with the exception of the energy-amplitude $A_E$ which requires the more refined mesh $\mathbf{M}_4$ obtained using 'D' strategy.\footnote{In terms of computational cost, on a standard laptop the program  \ref{fig:listingNL} requires approximatively 413 seconds using  mesh $\mathbf{M}_2$ and 31 minutes using mesh $\mathbf{M}_4$.}
+
+I n the proposed implementation, resolution of the problem is done by the FreeFem++ program {\em HB1\_2D.edp} which is wrapped by the Octave/Matlab function {\em SF\_HB1.m}.
+Note that the interested reader will also find within the sources of StabFem project a driver {\em SF\_HB2.m} implementing the same direct resolution method for the order-2 truncated harmonic balance.
+Generalization to higher orders is planned for future developments of the project.
+
+ \paragraph{Results for a cylinder}
+
+Lines 10-17 of the script shown in figure \ref{fig:listingNL}  explain how to to use these programs to the SC/HB1 model for the wake of a cylinder in the range $Re \in [47-100] $.
 Note that a {\em guess} for the mean flow and the self-consistent mode for $Re = 47$, i.e.
@@
 \end{center}
-\caption{Structure of the {\em mean flow} over a cylinder for $Re = 
-60$, as computed by the Self-Consistent model (streamwise velocity component).}
+\caption{Structure of the {\em mean flow} over a cylinder for $Re = 60$, as computed by the HB1 model. color levels : pressure ; streamlines.}
 \label{fig:MF60}
@@
 
-Figure \ref{fig:HB_SC_DATA_COMP} shows the comparison between the WNL (green) and SC (red) models for the quantities of interest identified in this paper, namely the Strouhal number, the mean drag, the maximum lift, the energy-ampligude, and the recirculation length associated to the mean flow.
+Figure \ref{fig:HB_SC_DATA_COMP} shows the comparison between the WNL (green) and HB1/SC (red) models for the quantities of interest identified in this paper, namely the Strouhal number, the mean drag, the maximum lift, the energy-amplitude, and the recirculation length associated to the mean flow.
 When relevant, results concerning the base flow and the linear approach are also displayed (blue)
@@
 The entire set of commands to obtain all figures is provided in the script {\sf SCRIPT\_CYLINDER\_ALLFIGURES.m} .}.
-Concerning the quantities $St$, $A_E$ and $L_x$, differences between SC, WNL models have already been commented in  \cite{MLugo2014} and \cite{FDR2016}.
+Concerning the quantities $St$, $A_E$ and $L_x$, differences between HB1/SC, WNL models have already been commented in  \cite{MLugo2014} and \cite{FDR2016}.
+
+{\em DIOGO : replace this paragraph by a description of figures displaying the comparison.
 The predictions of the SC models were also compared to numerical simulations results showing excellent agreement in the range $Re \in [Re_c,100]$.
-Regarding the forces exerted on the body, we can remark that the predictions of the WNL and SC models rapidly depart from each other as soon as $Re-Re_c \gtrsim 1$.
+Regarding the forces exerted on the body, we can remark that the predictions of the WNL and HB1/SC models rapidly depart from each other as soon as $Re-Re_c \gtrsim 1$.
 Comparison of these results with DNS simulations is not provided here (consistently with the objectives of the present paper) but the reader may verify that the SC model correctly predicts these quantities in the range of Reynolds number considered here.
+}
 
@@
 \begin{itemize}
-\item Incompressible flows around 2D objects, either fixed or in movement such as the case of a spring-mounted cylinder \cite{Navrose},
-\item Incompressible flows in axisymmetric geometries such as the wake of spheres and disks \cite{Tchoufag2015} and the flow through apertures \cite{FabreISMA}, 
-\item Compressible flow around 2D objects  \cite{Fani2018}, 
-\item Oscillations of hanging drops and liquid bridges \cite{Chireux2015}
+\item[-] Incompressible flows around 2D objects, either fixed or in movement such as the case of a spring-mounted cylinder \cite{Navrose},
+\item[-] Incompressible flows in axisymmetric geometries such as the wake of spheres and disks \cite{Tchoufag2015} and the flow through apertures \cite{FabreISMA}, 
+\item[-] Compressible flow around 2D objects  \cite{Fani2018}, 
+\item[-] Oscillations of hanging drops and liquid bridges \cite{Chireux2015}
 \end{itemize}
@@
 \hline
-\mbox{Mesh} & L_x & F_x & \lambda & L_{x,SC} & F_{x,SC} & \omega_{SC}  & F_{y,1,c} & A_{E} \\
+\mbox{Mesh} & L_x & F_x & \lambda & L_{x,HB1} & F_{x,HB1} & \omega_{HB1}  & F_{y,1,c} & A_{E} \\
 \hline
@@
 \caption{Results for mesh adaptation strategy ($Re = 60$) : Base-flow characteristics $L_x$ and $F_x$, linear eigenvalue $\lambda$, 
-Nonlinear self-consistent model characteristics  $\omega_{SC}$, $F_{y,1,c}$ and $A_E$. All the results can be optained using the Octave/Matlab script
+Nonlinear self-consistent model characteristics  $\omega_{HB1}$, $F_{y,1,c}$ and $A_E$. All the results can be optained using the Octave/Matlab script
 {\sf SCRIPT\_CYLINDER\_MESHCONVERGENCE.m}. }
@@
 
-For this purpose, 5 meshes were generated. 
+For this purpose, 6 meshes were generated. 
 Mesh $\mathbf{M}_1$ was adapted on the {\em base flow} obtained for $Re=60$.
-Mesh $\mathbf{M}_2$ was adapted to both the base flow and structural sensitivity.
-Mesh $\mathbf{M}_3$ was obtained by a subsequent refinement of mesh $\mathbf{M}_2$, splitting all triangles in four subtriangles, therefore doubling the effective density of the mesh.
-Meshes $\mathbf{M}_4$ and $\mathbf{M}_5$ were obtained by adapting to the structure of the direct eigenmode and of the adjoint eigenmode.
+Mesh $\mathbf{M}_2$ was adapted to both the base flow and structural sensitivity (strategy S).
+Mesh $\mathbf{M}_2'$ was obtained by a subsequent refinement of mesh $\mathbf{M}_2$, splitting all triangles in four subtriangles, therefore doubling the effective density of the mesh.
+Mesh $\mathbf{M}_3$ was adapted to both the base flow and endogeneity (strategy E).
+Meshes $\mathbf{M}_4$ and $\mathbf{M}_5$ were obtained by adapting to the structure of the direct eigenmode (strategy D) and of the adjoint eigenmode (strategy A).
 In each case, the adaptmesh process was repeated twice in order to ensure a correct convergence.
@@
 
-Table  \ref{tab:conv2} compares the results obtained with the five meshes.
+Table  \ref{tab:conv2} compares the results obtained with the six meshes.
 For base-flow characteristics $L_x$ and $F_x$, all values agree with a relative dispersion of less than $0.15\%$, confiming that all adaptation stategies are successful to correctly compute the base flow.
@@
 
-From this study we can conclude that if we are only interested in predicting the frequency of the mode and the forces exerted on the cylinder (in both linear and nonlinear regimes), the strategy of mesh adaptation to both base flow and structural sensitivity (mesh $\mathbf{M}_2$) is the most efficient and leads to a very light mesh (here only 2048 vertices).
+From this study we can conclude that if we are only interested in predicting the frequency of the mode and the forces exerted on the cylinder (in both linear and nonlinear regimes), the strategies S (mesh $\mathbf{M}_2$) and E (mesh $\mathbf{M}_3$) are the most efficient and lead to a very light mesh (here only 2048 vertices for mesh $\mathbf{M}_2$).
 On the other hand, if we are interested in describing the structure of the perturbation in the whole domain (and being able to correctly evaluate its energy), mesh adaptation to the eigenmode structure is preferable.
@@
 \end{itemize}
+
+\lstset{language=c++,%
+   %basicstyle=\color{red},
+   breaklines=true,%
+   morekeywords={c++},
+   keywordstyle=\color{blue},%
+   morekeywords=[2]{1}, keywordstyle=[2]{\color{black}},
+   identifierstyle=\color{black},%
+   stringstyle=\color{mylilas},
+   commentstyle=\color{mygreen},%
+   showstringspaces=false,%without this there will be a symbol in the places where there is a space
+   numbers=left,%
+   frame=trBL,
+   numberstyle={\tiny \color{black}},% size of the numbers
+   numbersep=9pt, % this defines how far the numbers are from the text
+   emph=[1]{for,end,break},emphstyle=[1]\color{red}, %some words to emphasise
+   %emph=[2]{word1,word2}, emphstyle=[2]{style},   
+   }
+
+\begin{figure*}[t]
+\small
+\lstinputlisting[firstline=2, lastline=19]{Extract_From_Stab2D.edp}
+ \normalsize
+\caption{Illustration of the implementation of the Newton algorithm for base-flow computation (extract from FreeFem++ program {\em Newton2D.edp}).}
+\label{Listing3}
+\end{figure*}
 
@@
 
-\section{Numerical implementation in FreeFem++}
-
-\lstset{language=c++,%
-   %basicstyle=\color{red},
-   breaklines=true,%
-   morekeywords={c++},
-   keywordstyle=\color{blue},%
-   morekeywords=[2]{1}, keywordstyle=[2]{\color{black}},
-   identifierstyle=\color{black},%
-   stringstyle=\color{mylilas},
-   commentstyle=\color{mygreen},%
-   showstringspaces=false,%without this there will be a symbol in the places where there is a space
-   numbers=left,%
-   frame=trBL,
-   numberstyle={\tiny \color{black}},% size of the numbers
-   numbersep=9pt, % this defines how far the numbers are from the text
-   emph=[1]{for,end,break},emphstyle=[1]\color{red}, %some words to emphasise
-   %emph=[2]{word1,word2}, emphstyle=[2]{style},   
-   }
-
-\begin{figure*}[t]
-\small
-\lstinputlisting[firstline=2, lastline=19]{Extract_From_Stab2D.edp}
- \normalsize
-\caption{Illustration of the implementation of the Newton algorithm for base-flow computation (extract from FreeFem++ program {\em Newton2D.edp}).}
-\label{Listing2}
-\end{figure*}
-
 \begin{figure*}[t]
@@
  \normalsize
-\caption{Illustration of the implementation of the Newton algorithm for base-flow computation (extract from FreeFem++ program {\em Newton2D.edp}).}
-\label{Listing2}
+\caption{Illustration of the implementation of the shift-invert algorithm for single eigenmode computation (extract from FreeFem++ program {\em Stab2D.edp}).}
+\label{Listing4}
 \end{figure*}
+
+\section{Numerical implementation in FreeFem++}
+
+In this appendix, we provide pieces of codes illustrating how the basic algorithms are implemented in the FreeFem++ solvers.
+These expanations will be useful for both people codes who whish to use directly FreeFem++ solvers without using the overlayer of Octave/Matlab drivers provided by the StabFem software, and also for persons who want to understand the logics of the implementation and customize the software to implement their own cases.
+The full version of the codes is available in the web repository of the StabFem project.
+A full documentation of the software is also in progress \footnote{\url{https://gitlab.com/stabfem/StabFem/blob/master/99_Documentation/MANUAL/main.pdf}}.
+
+Figure \ref{Listing3} details the implementation of the Newton algorithm for base-flow computation, as implemented in the FreeFem++ solver {\em Newton2D.edp} which is a generic solver usable for the whole class of 2D incompressible problems.
+Note that the syntax makes use of macros {\em D, div, Conv}, resulting in a very similar to the weak formulation written in the previous appendix.
+The boundary conditions are also coded using a macro {\em BoundaryconditionsBaseFlow}.
+To allow an easy customization, this macro is not defined in the generic solver {\em Newton2D.edp} but is reported in a file {\em Macros\_StabFem.idp} regrouping case-dependant macros (essentially boundary conditions and postprocessing options).
+
+Figure \ref{Listing4} details the implementation of the shift-invert algorithm for eigenvalue computation, as implemented in the generic solver {\em Stab2D.edp} for 2D incompressible flows.
+Here again, the boundary conditions (which may differ from a case to an other within the generic class of 2D incompressible flows) is given by a macro {\em BoundaryconditionsBaseFlow} which has to be defined in the  {\em Macros\_StabFem.idp} file.
+
+We do not provide here the listing for the Newton resolution of the HB1 model, but the interested reader is encouraged to look at the program {\em HB1\_2D.edp} on the project's site.
 

### 2018-11-29 99_Documentation/ARTICLE_STABFEM/SCRIPT_CYLINDER_Part1.m

@@ -6,8 +6,8 @@ bf = SF_Adapt(bf,'Hmax',10,'InterpError',0.01);
 [ev,em] = SF_Stability(bf,'shift',0.04+0.74i,'type','S')
 bf = SF_Adapt(bf,em,'Hmax',10,'InterpError',0.01);
 SF_Plot(bf,'p','contour','psi','clevels',[-.02 0 .2 1 2 5],'cstyle','patchdashedneg',...
-      'xlim',[-1.5 4.5],'ylim',[0 3],'cbtitle','p','colormap','redblue','colorrange','centered',...
-      'boundary','on','bdlabels',2,'bdcolors','k'); % figure 2
+      'xlim',[-1.5 4.5],'ylim',[0 3],'cbtitle','p','colormap','redblue','colorrange',...
+      'centered','boundary','on','bdlabels',2,'bdcolors','k'); % figure 2
 
 Re_Range = [2 : 2: 50]; Drag_tab = []; Lx_tab = [];
     for Re = Re_Range
@@ -23,7 +23,7 @@ bf=SF_BaseFlow(bf,'Re',40);
 [ev,em] = SF_Stability(bf,'shift',-.03+.72i,'nev',1,'type','D');
     for Re = Re_Range
         bf = SF_BaseFlow(bf,'Re',Re);
-        [ev,em] = SF_Stability(bf,'nev',1,'shift','cont');
+        [ev,em] = SF_Stability(bf,'nev',1,'shift','cont','guess',em);
         lambda_branch = [lambda_branch ev];
     end
 plot(Re_Range,real(lambda_branch),'b+-'); %Figure 4a

### 2018-11-29 99_Documentation/ARTICLE_STABFEM/SCRIPT_CYLINDER_Part2.m

@@ -7,12 +7,12 @@ epsilon2_WNL = -0.003:.0001:.005;
 Re_WNL = 1./(1/Rec-epsilon2_WNL);
 A_WNL = wnl.Aeps*real(sqrt(epsilon2_WNL));
 
-% SC model
+% HB model
 Re_SC = [Rec 47 47.5 48 49 50 55 60 65 70 75 80 85 90 95 100];
 Aenergy_SC  = [0]; 
 
 for Re = Re_SC(2:end)
-    [meanflow,mode] = SF_SelfConsistentDirect(meanflow,mode,'Re',Re);
+    [meanflow,mode] = SF_HB1(meanflow,mode,'Re',Re);
     Aenergy_SC  = [Aenergy_SC mode.AEnergy];
 end
 

### 2018-11-30 99_Documentation/ARTICLE_STABFEM/ARTICLE_ASME_Revision.tex
paper

@@
 \item[-]
-Secondly we offer an open-source and user-friendly software called  {\em StabFem} %\cprotect 
+Secondly we offer an open-source and user-friendly software called  {\sf StabFem} %\cprotect 
 \footnote{The StabFem software may be obtained at the following url : \\
@@
 The procedure of Newton iteration is to solve iteratively this set of equations up to convergence.
-In our implementation, the algorithm for a 2D incompressible flow is written in the Freefem++ solver {\em Newton\_2D.edp} (an extract of this code featuring the implementation of the Newton loop is given in appendix E).
+In our implementation, the algorithm for a 2D incompressible flow is written in the Freefem++ solver {\sf Newton\_2D.edp} (an extract of this code featuring the implementation of the Newton loop is given in appendix E).
 This FreeFem++ solver is wrapped by the Octave/Matlab driver {\sf SF\_BaseFlow.m}.
@@
 %Our implementation in StabFem allows to chose between single eigenvalue computation (power method) and multiple eigenvalue computation (Arnoldi). 
-For the case of the 2D incompressible flow, resolution of the eigenvalue problem (including adjoint, sensitivity and endogeneity) is done by the FreeFem++ solver {\em Stab2D.edp}; an extract of this solver featuring the implementation of the shift-invert algorithm is displayed in appendix E.
-The latter is wrapped by the Octave/Matlab driver {\em SF\_Stability.m} which accepts a number of optional parameters.
+For the case of the 2D incompressible flow, resolution of the eigenvalue problem (including adjoint, sensitivity and endogeneity) is done by the FreeFem++ solver {\sf  Stab2D.edp}; an extract of this solver featuring the implementation of the shift-invert algorithm is displayed in appendix E.
+The latter is wrapped by the Octave/Matlab driver {\sf  SF\_Stability.m} which accepts a number of optional parameters.
 For instance, the selection between shfift-invert and Arnoldi is made according to the parameter \verb|nev|  (i.e.
@@
 \caption{Illustration of the usage of the StabFem software to produce an adapted mesh and study the base flow and the linear stability properties of the wake flow around a cylinder 
-(extract from script {\em SCRIPT\_CYLINDER\_ALLFIGURES.m})}
+(extract from script {\sf  SCRIPT\_CYLINDER\_ALLFIGURES.m})}
 \label{Listing2}
@@
 Note that using the S strategy was already experimented in {\em \cite{GiannettiLuchini} for the wake of a cylinder (IS THAT THE RIGHT REFERENCE ??}).
-Mesh adaptation using the scalar product of the direct and adjoint eigenmodes (which turns out to be equivalent to the E strategy introduced here considering the definition of the endogeneity) was also proposed in {(\em DIOGO PLEASE PUT THE REF OF THE PAPER OLIVIER SHOWED US, AND COMPLETE THE SENTENCE}.
+Mesh adaptation using the scalar product of the direct and adjoint eigenmodes (which turns out to be equivalent to the E strategy introduced here considering the definition of the endogeneity) was also proposed in \cite{mavripilis2015adjoint}.
 A detailed comparison of the four strategies is reported in appendix A.
@@
 
-In our implementation, the whole process of mesh adaptation (including projection and recomputation of the base flow on the new mesh) is monitored using the Octave/Matlab driver {\em SF\_AdaptMesh.m} ; the kind of adaptation  (to base flow only (BF), or D, A, S , E strategies) is decided by the the nature of the objects transmitted to this function.
+In our implementation, the whole process of mesh adaptation (including projection and recomputation of the base flow on the new mesh) is monitored using the Octave/Matlab driver {\sf  SF\_AdaptMesh.m} ; the kind of adaptation  (to base flow only (BF), or D, A, S , E strategies) is decided by the the nature of the objects transmitted to this function.
 In the current implementation it is possible to adapt the mesh to as much as 8 fields of diverse nature (for instance, multiple eigenmodes along with their adjoint fields, harmonic-balance fourirer components, etc...)
@@
 An illustration of the structure of the base flow is given in figure \ref{fig:Baseflow},  for the case $Re = 60$.
-This figure is obtained using the Matlab/Octave function {\em SF\_Plot.m}, which is built over the function {\em ffpdeplot.m} developed by M.
+This figure is obtained using the Matlab/Octave function {\sf  SF\_Plot.m}, which is built over the function {\sf  ffpdeplot.m} developed by M.
 Meister and also distributed on an open-source basis
@@
 %\vspace{-.5cm}
-\caption{Contour plot of the streamwise velocity component: $(a)$ (Direct) Eigenmode; $(b)$ Adjoint mode at $Re=Re_c = 46.7$.}
+\caption{Contour plot of the streamwise velocity component: $(a)$ (Direct) Eigenmode; $(b)$ Adjoint mode at $Re=Re_c = 60$.}
 \label{fig:Eigenmode}
@@
 %\vspace{-.5cm}
-\caption{ ($a$) {\em Wavemaker}  field $S_w$ and $(b)$ {\em Endogeneity} field $S_e$ (color : real part ; levels: imaginary part) for the cylinder's wake at $Re=Re_c = 46.7$.
+\caption{ ($a$) {\em Wavemaker}  field $S_w$ and $(b)$ {\em Endogeneity} field $S_e$ fields for the cylinder's wake at $Re=Re_c = 60$.
+In plot $(b)$ the color scale indicates real part and levels indicate imaginary part (10 equidistant levels, the maximum value being +0.240).
 The red line represents the streamline bounding the recirculation region.}
@@
 In our implementation, parametric study is done by the loop over Reynolds corresponding to lines 21-30 of the script in figure \ref{Listing2}.
-Note that at line 26 the options {\em 'shift, 'cont' ,'guess', em} transmitted to the driver {\em SF\_Stability} allow to use an optimum value for the shift interpolated using the previous computations, and a guess value to initialize the shift-invert procedure corresponding to the previously computed eigenmode.
+Note that at line 26 the options {\sf  'shift, 'cont' ,'guess', em} transmitted to the driver {\sf  SF\_Stability} allow to use an optimum value for the shift interpolated using the previous computations, and a guess value to initialize the shift-invert procedure corresponding to the previously computed eigenmode.
 Both these ideas very efficiently accelerate the calculations (the shift-invert procedure typically converges after only 2-3 iterations).
@@
 
-I n the proposed implementation, resolution of the problem is done by the FreeFem++ program {\em HB1\_2D.edp} which is wrapped by the Octave/Matlab function {\em SF\_HB1.m}.
-Note that the interested reader will also find within the sources of StabFem project a driver {\em SF\_HB2.m} implementing the same direct resolution method for the order-2 truncated harmonic balance.
+In the proposed implementation, resolution of the problem is done by the FreeFem++ program {\sf  HB1\_2D.edp} which is wrapped by the Octave/Matlab function {\sf  SF\_HB1.m}.
+Note that the interested reader will also find within the sources of StabFem project a driver {\sf  SF\_HB2.m} implementing the same direct resolution method for the order-2 truncated harmonic balance.
 Generalization to higher orders is planned for future developments of the project.
@@
 
-{\em DIOGO : replace this paragraph by a description of figures displaying the comparison.
+{\em DIOGO : replace this paragraph by a description of figures displaying the comparison
 The predictions of the SC models were also compared to numerical simulations results showing excellent agreement in the range $Re \in [Re_c,100]$.
@@
 }
+
+\cite{williamson1988defining}
 
@@
  \normalsize
-\caption{Illustration of the implementation of the Newton algorithm for base-flow computation (extract from FreeFem++ program {\em Newton2D.edp}).}
+\caption{Illustration of the implementation of the Newton algorithm for base-flow computation (extract from FreeFem++ program {\sf  Newton2D.edp}).}
 \label{Listing3}
@@
 This can be controlled by assigning a nonzero value to the optional parameter \verb|sigma| of the  {\sf SF\_SelfConsistent.m} Octave/Matlab function.
-The interested reader will find on the website of the {\em StabFem} project a program {\sf SCRIPT\_CYLINDER\_NONLINEAR.m} which computes $A$ as function of $\sigma$ for $Re=100$, yielding identical results as displayed in figure 3 of \cite{MLugo2014}.
+The interested reader will find on the website of the {\sf  StabFem} project a program {\sf SCRIPT\_CYLINDER\_NONLINEAR.m} which computes $A$ as function of $\sigma$ for $Re=100$, yielding identical results as displayed in figure 3 of \cite{MLugo2014}.
 
@@
  \normalsize
-\caption{Illustration of the implementation of the shift-invert algorithm for single eigenmode computation (extract from FreeFem++ program {\em Stab2D.edp}).}
+\caption{Illustration of the implementation of the shift-invert algorithm for single eigenmode computation (extract from FreeFem++ program {\sf  Stab2D.edp}).}
 \label{Listing4}
@@
 
-Figure \ref{Listing3} details the implementation of the Newton algorithm for base-flow computation, as implemented in the FreeFem++ solver {\em Newton2D.edp} which is a generic solver usable for the whole class of 2D incompressible problems.
-Note that the syntax makes use of macros {\em D, div, Conv}, resulting in a very similar to the weak formulation written in the previous appendix.
-The boundary conditions are also coded using a macro {\em BoundaryconditionsBaseFlow}.
-To allow an easy customization, this macro is not defined in the generic solver {\em Newton2D.edp} but is reported in a file {\em Macros\_StabFem.idp} regrouping case-dependant macros (essentially boundary conditions and postprocessing options).
-
-Figure \ref{Listing4} details the implementation of the shift-invert algorithm for eigenvalue computation, as implemented in the generic solver {\em Stab2D.edp} for 2D incompressible flows.
-Here again, the boundary conditions (which may differ from a case to an other within the generic class of 2D incompressible flows) is given by a macro {\em BoundaryconditionsBaseFlow} which has to be defined in the  {\em Macros\_StabFem.idp} file.
-
-We do not provide here the listing for the Newton resolution of the HB1 model, but the interested reader is encouraged to look at the program {\em HB1\_2D.edp} on the project's site.
+Figure \ref{Listing3} details the implementation of the Newton algorithm for base-flow computation, as implemented in the FreeFem++ solver {\sf  Newton2D.edp} which is a generic solver usable for the whole class of 2D incompressible problems.
+Note that the syntax makes use of macros {\sf  D, div, Conv}, resulting in a very similar to the weak formulation written in the previous appendix.
+The boundary conditions are also coded using a macro {\sf  BoundaryconditionsBaseFlow}.
+To allow an easy customization, this macro is not defined in the generic solver {\sf  Newton2D.edp} but is reported in a file {\sf  Macros\_StabFem.idp} regrouping case-dependant macros (essentially boundary conditions and postprocessing options).
+
+Figure \ref{Listing4} details the implementation of the shift-invert algorithm for eigenvalue computation, as implemented in the generic solver {\sf  Stab2D.edp} for 2D incompressible flows.
+Here again, the boundary conditions (which may differ from a case to an other within the generic class of 2D incompressible flows) is given by a macro {\sf  BoundaryconditionsStability} which has to be defined in the  {\sf  Macros\_StabFem.idp} file.
+
+We do not provide here the listing for the Newton resolution of the HB1 model, but the interested reader is encouraged to look at the program {\sf  HB1\_2D.edp} on the project site.
 

### 2018-11-30 SOURCES_MATLAB/SF_BaseFlow.m

@@ -5,24 +5,32 @@
 %> @param[in] varargin: list of parameters and associated values
 %> @param[out] baseflow: baseflow solved by Newton iterations
 %>
-%> usage: <code>baseflow = SF_BaseFlow(baseflow1,['Param1',Value1,...])</code>
+%> usage: 
+%> 1/ baseflow = SF_BaseFlow(baseflow,['Param1',Value1,...])
+%> 2/ baseflow = SF_BaseFlow(ffmesh,['Param1',Value1,...])
+%>
+%> in mode 1 (first argument is a previously computed baseflow) 
+%             this previous baseflow will be used to initialmize the Newton iter.  
+%> in mode 2 (first argument is a mesh) 
+%>              No initial condition is prescribed. The solver will use a default one 
+%>             unless a macro "DefaultGuessForNewton" is defined in your Macro_StabFem.idp  
 %>
 %> This wrapper will launch the Newton FreeFem++ program of the corresponding
 %>  case. Nota Bene: if baseflow was already created, it is simply copied from
 %>  the "BASEFLOW" directory (unless specified otherwise by parameter 'Type').
 %>
 %> List of valid parameters:
-%>   - <code>Re</code>          Reynolds number
-%>   - <code>Ma</code>          Mach number (for compressible cases)
-%>   - <code>Omegax</code>      Rotation rate (for swirling axisymetric or 2D body)
-%>   - <code>Darcy</code>       Darcy number (for cases with porous body)
-%>   - <code>Porosity</code> \t\t    Porosity (for cases with porous body)
-%>   - <code>Type</code>
-%>      - <code>'Normal'</code> (default) ;
-%>      - <code>'NEW'</code> to force new computation ;
-%>      - <code>'POSTADAPT'</code> for recomputing baseflow after mesh adaptation ;
-%>      - <code>'PREV'</code> if connection was lost (obsolete ?)
-%>   - <code>ncores</code>      Number of cores (for parallel computations)
+%>   - Re          Reynolds number
+%>   - Ma          Mach number (for compressible cases)
+%>   - Omegax      Rotation rate (for swirling axisymetric or 2D body)
[…]

### 2018-11-30 SOURCES_MATLAB/SF_Stability.m

@@ -5,8 +5,9 @@ function varargout = SF_Stability(baseflow,varargin)
 %>
 %> usage : 
 %> 1/  [eigenvalues,eigenvectors] = SF_Stability(field, [,param1,value1] [,param2,value2] [...])
-%> 2/  [eigenvalues,sensitivity,evD,evA,Endo] = SF_Stability(field,'type','S','nev',1, [...])
+%> 2/  [eigenvalues,sensitivity,evD,evA] = SF_Stability(field,'type','S','nev',1, [...])
 %> 3/  [eigenvalues,Endogeneity,evD,evA] = SF_Stability(field,'type','E','nev',1, [...])
+%> 4/  [eigenvalues,sensitivity,evD,evA,Endo] = SF_Stability(field,'type','S','nev',1, [...]) (not recommended)
 %>
 %> field is either a "baseflow" structure (with "mesh" structure as a subfield) 
 %> or directly a "mesh" structure (for instance in problems such as sloshing where baseflow is not relevant).
@@ -39,6 +40,10 @@ function varargout = SF_Stability(baseflow,varargin)
 %>               (e.g. myStab2D.edp instead of Stab2D.edp)
 %>               Useful in developpment/debugging mode ; the alternative
 %>               solver has to use the same input parameters is the standard.
+%>  guess :      eigenmode object used as initial condition for shift-invert (if nev=1)
+%>  guessAdj :   same for the adjoint problem (if nev=1 and type = A,S or E)
+%
+%
 %>
 %>  3/ Physical parameters
 %>
@@ -82,21 +87,6 @@ global ff ffMPI ffdir ffdatadir sfdir verbosity
 
 persistent sigmaPrev sigmaPrevPrev % for continuation on one branch
 persistent eigenvaluesPrev % for sort of type 'cont'
-
-myrm([ffdatadir 'Eigenmode_guess.txt']) % TODO : add parameter to put a guess file only when required
-
-
-
-   if(strcmpi(baseflow.datatype,'Mesh')==1)
-       % first argument is a simple mesh
-       ffmesh = baseflow; 
-       mycp(ffmesh.filename,[ffdatadir 'mesh.msh']); % this should be done in this way in the future
-   else
-       % first argument is a base flow
-       ffmesh = baseflow.mesh;
-       mycp(baseflow.filename,[ffdatadir 'BaseFlow.txt']);
[…]

### 2018-11-30 99_Documentation/ARTICLE_STABFEM/ARTICLE_ASME_Revision.tex
Changes of Diogo in the references and small errors in the text in general.

@@
 %%% first author
-\author{D. Fabre$^{(a)}$,  V. Citro$^{(b,a)}$,  D. Ferreira Sabino$^{(a)}$, P. Bonnefis$^{(a)}$,  F. Giannetti$^{(b)}$ \& M. Pigou$^(a)$ 
+\author{D. Fabre$^{(a)}$,  V. Citro$^{(b,a)}$,  D. Ferreira Sabino$^{(a)}$, P. Bonnefis$^{(a)}$,  F. Giannetti$^{(b)}$ \& M. Pigou$^{(a)}$ 
     \affiliation{
-	$^{(a)}$ Institut de Mécanique des fluides de Toulouse (IMFT), University of Toulouse \\
+	$^{(a)}$ Institut de M\'ecanique des fluides de Toulouse (IMFT), University of Toulouse \\
 	$^{(b)}$ Dipartimento do Ingegneria (DIIN), Universit\`a} di Salerno. 
@@
 
-\paragraph{Navier-Stokes equations and weak form}
-
-We start from the general problem of a flow field $[{\bf u},p]$ satisfying the incompressible Navier-Stokes equations on a domain $\Omega$,
+\paragraph{Navier--Stokes equations and weak form}
+
+We start from the general problem of a flow field $[{\bf u},p]$ satisfying the incompressible Navier--Stokes equations on a domain $\Omega$,
 \begin{eqnarray} \label{NSprimitive}
@@
 $$
-The weak form of the Navier-Stokes equations is readily defined by introducing test functions 
+The weak form of the Navier--Stokes equations is readily defined by introducing test functions 
 $[{\bf v},q]$ associated with the momentum and continuity equations, and integrating over the domain\footnote{In the simple presentation given here we have omitted the issue of boundary conditions.
@@
 
-We look for a steady base-flow $[{\bf u}_b,p_b]$ satisfying the steady Navier-Stokes equations, i.e. 
+We look for a steady base-flow $[{\bf u}_b,p_b]$ satisfying the steady Navier--Stokes equations, i.e. 
 %${\cal NS} ({\bf u}_b,p_b) = 0$.
@@
 \ee
-Injecting (\ref{Newton1}) into the weak form (\ref{NSweak}) of the Navier-Stokes equations and linearizing leads to  
+Injecting (\ref{Newton1}) into the weak form (\ref{NSweak}) of the Navier--Stokes equations and linearizing leads to  
 ${\cal NS}  ({\bf u}_b^g,p_b^g) +  {\cal LNS} _{{\bf u}_b^g}(\delta {\bf u}_b,\delta p_b)$, which can also be written in weak form as :
@@
 \ees
-where ${\cal LNS}$ is the linearised Navier-Stokes operator, defined by its action on a flow field $[{\bf u} , p]$ as follows 
+where ${\cal LNS}$ is the linearised Navier--Stokes operator, defined by its action on a flow field $[{\bf u} , p]$ as follows 
 \be{defNSL}
@@
 \ee
-This problem can now be discretized by projecting upon a basis of Taylor-Hood $(u,v,p) \rightarrow (P2,P2,P1)$ finite elements.
+This problem can now be discretized by projecting upon a basis of Taylor--Hood $(u,v,p) \rightarrow (P2,P2,P1)$ finite elements.
 Noting $\delta X$ the discretization of $[\delta {\bf u}_b,\delta p_b]$ this eventually leads to a matricial problem of the form $A \cdot \delta X = Y$.
@@
 We here give a short summary of the definition and usefulness of this concept and refer the reader to Luchini \& Bottaro\cite{LucBott2014} for further details.
-First of all, the {\em adjoint linearised Navier-Stokes operator} ${\cal LNS}^\dag$ is defined thanks to the following 
+First of all, the {\em adjoint linearised Navier--Stokes operator} ${\cal LNS}^\dag$ is defined thanks to the following 
 property:
@@
 
-To build an optimal mesh for the base-flow calculation, the idea is to use as the objective function $u_h$ the solution ${\bf u}_b$ itself, as computed on a previous mesh.%The procedure thus ensures that the mesh will be locally adapted to the gradients of the base flow.
+To build an optimal mesh for the base-flow calculation, the idea is to use as the objective function $u_h$ the solution ${\bf u}_b$ itself, as computed on a previous mesh.
+%The procedure thus ensures that the mesh will be locally adapted to the gradients of the base flow.
 The base flow is then recomputed on the adapted mesh, providing a better approximation of the solution. The procedure can be repeated a few steps to ensure a right convergence.
@@
 
-In the past decade, efforts have been devoted to extend the range of validity of global approaches into the nonlinear regime for $Re>Re_c$, with the double objective to describe the properties of the limit cycle reached after saturation and to derive amplitude equations describing the transitent dynamics towards this cycle.
+In the past decade, efforts have been devoted to extend the range of validity of global approaches into the nonlinear regime for $Re>Re_c$, with the double objective to describe the properties of the limit cycle reached after saturation and to derive amplitude equations describing the transient dynamics towards this cycle.
 The two main milestones in this direction  are the {\em weakly nonlinear model}  (WNL) of Sipp \& Lebedev \cite{SippLebedev} and the {\em self-consistent model} (SC) of Manti\v{c}-Lugo et al \cite{MLugo2014}.
@@
 
- In this part, to simplify the notations, we symbolically write the Navier-Stokes equations as $\partial_t {\bf u} = {\cal NS} ({\bf u})$, therefore dropping the systematic reference to the incompressibility constraint and associated pressure field.
+ In this part, to simplify the notations, we symbolically write the Navier--Stokes equations as $\partial_t {\bf u} = {\cal NS} ({\bf u})$, therefore dropping the systematic reference to the incompressibility constraint and associated pressure field.
 The same is done with the linearized operator ${\cal LNS}_{{\bf U}}( {\bf u})$.
@@
 In addition, we will document two other quantities of practical interest : the Drag and Lift forces $F_x$ and $F_y$ exerted on the cylinder.
-Both are periodic functions of time and; owing to symmetry consideration, the drag contains only even harmonics and the lift only odd harmonics:
+Both are periodic functions of time and, owing to symmetry consideration, the drag contains only even harmonics and the lift only odd harmonics:
 
@@
 Lebedev\cite{SippLebedev}, also discussed by Gallaire et al. \cite{FDR2016}.  
-The initial derivation of \cite{SippLebedev} makes use of a multiple scale method in order to obtained an amplitude equation.
+The initial derivation of \cite{SippLebedev} makes use of a multiple scale method in order to obtain an amplitude equation.
 This complete analysis is reproduced in appendix B. In the present paragraph, we give a simplified derivation of this model restricted to the description of the periodic saturated cycle.
@@
 
-Injecting this ansatz into the Navier-Stokes equations and taking the mean value and the first Fourier component leads to the following coupled equations:
+Injecting this ansatz into the Navier--Stokes equations and taking the mean value and the first Fourier component leads to the following coupled equations:
 \begin{subequations}\label{eq_principal}
@@
 
-Note that this system of equations contains three unknown fields (discretized on the Taylor-Hood basis) plus an extra scalar unknown, 
+Note that this system of equations contains three unknown fields (discretized on the Taylor--Hood basis) plus an extra scalar unknown, 
 namely the frequency $\omega$. 
@@
 
-When reformulated in this way, the nonlinear problem addressed by the self-consistent model actually reduces to the restriction to order one of a more general class of methods called  harmonic balance methods (HB) (DIOGO PUT A FEW REFERENCES HERE \cite{}).
-The development of such methods, or related ones such the time-spectral method (REFS ?)  and the search for efficient numerical implementation to solve such problems is currently an active field of development in the fluid dynamics community.
+When reformulated in this way, the nonlinear problem addressed by the self-consistent model actually reduces to the restriction to order one of a more general class of methods called harmonic balance methods (HB).
+One of the first aplications of these methods in the domain of fluid mechanics has done by Carte and Du\v{s}ek (\cite{CarteDusek1995},\cite{CarteDusekfraunie1996}).
+The development of such methods, or related ones such the time-spectral method (\cite{HallThomasClark2002}) and the search for efficient numerical implementation to solve such problems is currently an active field of development in the fluid dynamics community.
 When considering HB development with a large order of terms, direct resolution by inversion of the full matrix is not achievable.
@@
 
-After discretization, this leads to a linear problem of the form $A X = Y$ where $X$ is the discretized version of the unknowns  $[\delta {\bf u }_m, \delta {\bf u }_{1,c}, \delta {\bf u }_{1,s}, \delta \omega]$, and $A$ is a matrix of dimension $3 N_{dof} +1$, where $N_{dof}$ is the dimension of the Taylor-Hood basis of finite elements describing each of the three $[{\bf u},p]$ fields.
+After discretization, this leads to a linear problem of the form $A X = Y$ where $X$ is the discretized version of the unknowns  $[\delta {\bf u }_m, \delta {\bf u }_{1,c}, \delta {\bf u }_{1,s}, \delta \omega]$, and $A$ is a matrix of dimension $3 N_{dof} +1$, where $N_{dof}$ is the dimension of the Taylor--Hood basis of finite elements describing each of the three $[{\bf u},p]$ fields.
 This system is solved iteratively in the same way as explained in section 2.1 for determination of the base flow.
@@
 Figure \ref{fig:MF60} illustrates the structure of the mean flow for $Re=60$.
-As already identified by  \cite{MLugo2014}, the recirculation region associated with this mean flow is notably shorter than the one associated with the base flow (figure 2).
+As already identified by  \cite{MLugo2014}, the recirculation region associated with this mean flow is notably shorter than the one associated with the base flow (figure \ref{fig:Baseflow}).
 
 %Line 19 shows how to plot the results along with the 
-
 %\ref{HBEq0,HBEq1,HBphase}
@@
 
-{\em DIOGO : replace this paragraph by a description of figures displaying the comparison
-The predictions of the SC models were also compared to numerical simulations results showing excellent agreement in the range $Re \in [Re_c,100]$.
-Regarding the forces exerted on the body, we can remark that the predictions of the WNL and HB1/SC models rapidly depart from each other as soon as $Re-Re_c \gtrsim 1$.
-Comparison of these results with DNS simulations is not provided here (consistently with the objectives of the present paper) but the reader may verify that the SC model correctly predicts these quantities in the range of Reynolds number considered here.
-}
-
-\cite{williamson1988defining}
+%replace this paragraph by a description of figures displaying the comparison
+
+The present results are also compared with the available literature, namely with the experiments of \cite{williamson1988defining} for the $St$ number and  with the DNS results of \cite{MLugo2014} for $A_E$ and $L_x$.
+The predictions of the SC/HB1 model show an excellent agreement in the range $Re \in [Re_c,100]$ with the rReferences. %Regarding the forces exerted on the body, 
+However, we can remark that the predictions of the WNL model rapidly depart from the previous ones as soon as $Re-Re_c \gtrsim 1$.
+
+%Comparison of these results with DNS simulations is not provided here (consistently with the objectives of the present paper) but the reader may verify that the SC model correctly predicts these quantities in the range of Reynolds number considered here.
 
@@
 $$
-\caption{Description of meshes used for validation of mesh adaptation strategy : number of vertices $N_p$ ; number of degrees of freedom of the P2-P2-P1 Taylor-hood basis $N_{dof}$ ; cell size (minimum and maximum value, and value at four characteristic point A,B,C,D as defined in the text).
+\caption{Description of meshes used for validation of mesh adaptation strategy : number of vertices $N_p$ ; number of degrees of freedom of the P2-P2-P1 Taylor--Hood basis $N_{dof}$ ; cell size (minimum and maximum value, and value at four characteristic point A,B,C,D as defined in the text).
  }
@@
 
-Fx = 0.6447; Lx = 4.0736
+%Fx = 0.6447; Lx = 4.0736
 \begin{table*}
@@
 As can be observed, these two mesh adaptation strategies lead to meshes with comparable densities in the region close to the cylinder.
-On the other hand, when moving downwards in the wake, mesh $\mathbf{M}_2$ quickly gets rather coarse, while mesh $\mathbf{M}_4$ maintains a significant density
+On the other hand, when moving downwards in the wake, mesh $\mathbf{M}_2$ quickly gets rather coarse, while mesh $\mathbf{M}_4$ maintains a significant density.
 
@@
 
-From this study we can conclude that if we are only interested in predicting the frequency of the mode and the forces exerted on the cylinder (in both linear and nonlinear regimes), the strategies S (mesh $\mathbf{M}_2$) and E (mesh $\mathbf{M}_3$) are the most efficient and lead to a very light mesh (here only 2048 vertices for mesh $\mathbf{M}_2$).
+From this study we can conclude that if we are only interested in predicting the frequency of the mode and the forces exerted on the cylinder (in both linear and nonlinear regimes), the strategies S (mesh $\mathbf{M}_2$) and E (mesh $\mathbf{M}_3$) are the most efficient and lead to a very light mesh (here only 2038 vertices for mesh $\mathbf{M}_2$).
 On the other hand, if we are interested in describing the structure of the perturbation in the whole domain (and being able to correctly evaluate its energy), mesh adaptation to the eigenmode structure is preferable.
@@
 
-Substituting the expansion \ref{WNL2} into the Navier-Stokes equations \ref{NSprimitive} and grouping terms multiplied by the same power of $\epsilon$, a hierarchy of equations is obtained.
+Substituting the expansion \ref{WNL2} into the Navier--Stokes equations \ref{NSprimitive} and grouping terms multiplied by the same power of $\epsilon$, a hierarchy of equations is obtained.
 The order $\epsilon^0$ gives directly the base flow at $Re_c$.
@@
 The objective of this appendix is to provide additional details about the  SC model in its original form as given by \cite{MLugo2014}, and to explain the connection with the simpler version discussed in section 4.2.
-The full model is obtained by introducing the decomposition (\ref{SC}) into the Navier-Stokes equations, leading to :
+The full model is obtained by introducing the decomposition (\ref{SC}) into the Navier--Stokes equations, leading to :
 \begin{subequations}\label{sc12}
@@
 In this appendix we explain more rigorously how the weak formulation is obtained.
-We consider here the full time-dependent nonlinear Navier-Stokes equations, but the treatment of the base-flow equations and the linearised equations is essentially the same.
+We consider here the full time-dependent nonlinear Navier--Stokes equations, but the treatment of the base-flow equations and the linearised equations is essentially the same.
 
@@
 where $\epsilon=10^{-30}$ is a small parameter used to impose the Dirichlet boundary conditions by penalization.
-An integration by parts of the pressure gradient and viscous stress terms of the Navier-Stokes equation eventually 
+An integration by parts of the pressure gradient and viscous stress terms of the Navier--Stokes equation eventually 
 leads to the weak form effectively used in the programs {\sf Newton2D.edp} and {\sf Stab2D.edp}:

### 2018-12-06 99_Documentation/ARTICLE_STABFEM/ARTICLE_ASME_Revision.tex
Corrections of article up to end of Section 2.

@@
 {\it 
-This paper aims at reviewing the linear and nonlinear approaches to study the stability of fluid flows. 
+This paper aims at reviewing linear and nonlinear approaches to study the stability of fluid flows. 
 We provide a concise but self-contained exposition of the main concepts and specific numerical methods 
@@
 including mesh adaptation, simple shift-invert strategy instead of the classical Arnoldi algorithm, 
-and a simplification of the recent nonlinear self-consistent approach proposed by Manti\v{c}-Lugo et al (2014). 
+and a simplification of the recent nonlinear self-consistent approach proposed by Manti\v{c}-Lugo et al. (2014). 
 An open-source software implementing all the concepts discussed in the present paper is provided. 
@@
 
-The concept of stability bears on the reaction of a system to a small perturbation of its state.
+The concept of stability bears on the response of a system to small perturbations of its state.
 If the generic disturbance grows in time, the system is unstable.
@@
 The stability of fluid flows usually depends on the value of a given parameter.
-A bifurcation occurs when a critical value is reached and the original solution becomes linearly unstable, with the system tending towards a new steady or unsteady state.
-In the second part of the 19th century, specific analytical and numerical methods able to study these bifurcations have emerged and are continuously evolving up to the present days. 
-A crucial point, that drove the development in this field, is the availability of larger and larger computing resources. 
-Initially, the linear stability theory focused on fluid flows that are homogeneous in two spatial directions, e.g.
-plane Poiseuille flow \cite{Dreid2004}.
-In this case, thanks to a Fourier decomposition in the two homogeneous directions, it is possible to reduce the stability problem to  a one-dimensional problem, an approach usually referred to as \textit{local stability approach}.
+A bifurcation occurs when a critical value is reached and the original solution becomes linearly unstable, the system then starts evolving towards a new state, either steady or unsteady. 
+In the second part of the 19th century, specific analytical and numerical methods have emerged to study these bifurcations and have continuously evolved up to the present days. 
+A crucial point, that drove the development in this field, is the availability of significantly increasing and improving computing resources. 
+Initially, the linear stability theory focused on fluid flows that are homogeneous in two spatial directions, \textit{e.g.} plane Poiseuille flow \cite{Dreid2004}.
+In this case, thanks to a Fourier decomposition in the two homogeneous directions, it is possible to reduce the stability problem to a one-dimensional problem, an approach usually referred to as {\em local stability approach}.
 On the other hand,  when there are at least two spatial variables, the class of methods suited to solve such problems are generally called {\em global stability approaches}.
@@
 This flow configuration has served as a benchmark in the development of this class of methods.  
-If one is only interested in predicting the stability or instability of a flow, it is enough to conduct a {\em linear stability analysis} which is the fundamental brick of global stability approaches.
+If one is only interested in predicting whether a flow is stable, it is sufficient to conduct a {\em linear stability analysis} which is the fundamental brick of global stability approaches. 
 Beyond this simple question, in the past two decades, a number of extensions have been developed and popularized.
@@
 to perform such calculations. The software combines programs written in both FreeFem++ \cite{MR3043640} and Octave/Matlab languages. 
-FreeFem++ is used to generate and adapt the meshes and to solve the various linear problems arising in the analysis.
-Octave/Matlab is used as a driver to monitor the computations, perform the required loops over parameters, and plot the results.
-The software is developed as a collaborative project and intended as multiplatform and easily customizable to a variety of cases.
+FreeFem++ is used to generate and adapt meshes and to solve the various linear problems arising in the analysis.
+Octave/Matlab is used as a driver/wrapper to monitor the computations, perform the required loops over parameters, and post-process the results.
+The software is developed as a collaborative project, it aims a multi-platform support and is easily customizable to a variety of cases.
 \end{itemize}
@@
 
-Although we don't claim to invent any radically new method, our exposition and implementation contains a number of originalities making the computation particularly efficient in terms of computational time and memory\footnote{All the figures contained in the present paper can be processed by launching a single Octave/Matlab script {\sf SCRIPT\_CYLINDER\_ALLFIGURES.m} .
+Although we do not claim inventing any radically new method, our exposition and implementation contains a number of novelties making the computation particularly efficient in terms of computational time and memory\footnote{All the figures contained in the present paper can be processed by launching a single Octave/Matlab script {\sf SCRIPT\_CYLINDER\_ALLFIGURES.m} .
 On a MacbookPro (2018,  2.5Ghz, 16Go Ram) in single-core sequential execution,  and using mesh ${\mathbf M}_2$ as described in appendix B, the execution time is 203 seconds for the linear analysis (section 3), and 413 seconds for the nonlinear analysis.}.
 % 1868 seconds using mesh M4
-The most notable originalities are the systematic use of mesh adaptation (\S 2 and 3), the use of simple shift-invert instead of Arnoldi (\S 3), and a reformulation and simplification of the self-consistent approach of Mantic-Lugo in the framework of the Harmonic Balance formalism   (\S 4).
+The most notable originalities are the systematic use of mesh adaptation (\S 2 and 3), the use of simple shift-invert instead of Arnoldi (\S 3), and a reformulation and simplification of the self-consistent approach of Manti\v{c}-Lugo in the framework of the Harmonic Balance formalism   (\S 4).
 
@@
  {\mathsf{D}}({\bf u}) = 1/2
-\left( \nabla {\bf u} +  \nabla^T  {\bf u}\right),
-$$ 
-In the framework of finite element methods, we need to write the equation in weak form.
-Prior to this we define a scalar product as follows, for either scalar or vectorial quantities 
+\left( \nabla {\bf u} +  \nabla^T  {\bf u}\right).
+$$ 
+In the framework of finite element methods, we need to write the equations in weak form.
+Prior to this we define a scalar product as follows, for both scalar or vectorial quantities 
 $\left< \phi_1, \phi_2 \right> $:
 $$
-\left< \phi_1, \phi_2 \right> = \int_\Omega \overline{\phi}_1 \cdot \phi_2   \mbox{ d} \Omega,
+\left< \phi_1, \phi_2 \right> = \int_\Omega \overline{\phi}_1 \cdot \phi_2   \mbox{ d} \Omega.
 $$
 The weak form of the Navier--Stokes equations is readily defined by introducing test functions 
-$[{\bf v},q]$ associated with the momentum and continuity equations, and integrating over the domain\footnote{In the simple presentation given here we have omitted the issue of boundary conditions.
-Details on way boundary conditions can be incorporated in the weak formulation through integration by parts can be found in appendix D.}
+$[{\bf v},q]$ associated with momentum and continuity equations, and by integrating over the domain\footnote{In the simple presentation given here we have omitted the issue of boundary conditions.
+Details on how to incorporate boundary conditions in the weak formulation through integration by parts can be found in appendix D.}
 \be{NSweak}
@@
 ${\cal NS} ({\bf u}_b,p_b) = 0$.
-Suppose that we have a {\em guess}  for the base flow $[{\bf u}_b^g,p_b^g]$  which almost satisfies the equations.  We look for a better approximation under the form
+Suppose that we have a {\em guess}  for the base flow $[{\bf u}_b^g,p_b^g]$  which almost satisfies the equations. 
+We look for a better approximation under the form
 \be{Newton1}
@@
 \ee
-Injecting (\ref{Newton1}) into the weak form (\ref{NSweak}) of the Navier--Stokes equations and linearizing leads to  
+Injecting \eqref{Newton1} into the weak form \eqref{NSweak} of the Navier--Stokes equations and linearizing leads to  
 ${\cal NS}  ({\bf u}_b^g,p_b^g) +  {\cal LNS} _{{\bf u}_b^g}(\delta {\bf u}_b,\delta p_b)$, which can also be written in weak form as :
@@
 Noting $\delta X$ the discretization of $[\delta {\bf u}_b,\delta p_b]$ this eventually leads to a matricial problem of the form $A \cdot \delta X = Y$.
-The procedure of Newton iteration is to solve iteratively this set of equations up to convergence.
+The Newton iteration procedure aims at iteratively solving this set of equations up to a defined convergence criterion.
 In our implementation, the algorithm for a 2D incompressible flow is written in the Freefem++ solver {\sf Newton\_2D.edp} (an extract of this code featuring the implementation of the Newton loop is given in appendix E).
@@
 where $\lambda = \sigma + i \omega$ is the eigenvalue, $\sigma$ the amplification rate,
-$\omega$ the oscillation rate, $\hat{{\bf u}},\hat{p}$ the eigenmode (also called direct eigenmode, to distinguish with the adjoint eigenmode introduced below), 
+$\omega$ the oscillation rate, $\hat{{\bf u}},\hat{p}$ the eigenmode (also called direct eigenmode, as opposed to the adjoint eigenmode introduced below), 
 and $\epsilon$ a small parameter. The eigenmodes and eigenvalues are the solution of the following eigenproblem:
@@
 \paragraph{Adjoint eigenvalue problem, structural sensitivity, and wavemaker characterization}
-Developed in the two past decades, the concept adjoint eigenmodes has now become an unavoidable complement to the linear global stability approach.
+Developed in the two past decades, the concept of adjoint eigenmodes has now become an unavoidable complement to the linear global stability approach.
 We here give a short summary of the definition and usefulness of this concept and refer the reader to Luchini \& Bottaro\cite{LucBott2014} for further details.
@@
 
-Although the concept of adjoint operator may sound complicate, the resolution of the adjoint problem using finite elements methods is actually extremely easy.
-In effect, the scalar product used in the definition of the weak formulation and that appearing in the definition of adjoint being the same, the weak formulations of both problems are thus identical when exchanging the test functions and the unknown functions.
-Thus the matricial form of the discretized version of (\ref{EigenAdj}) is deduced from the one of the direct problem by a simple (Hermitian) transpose of the matrix :
+Although the concept of adjoint operator may sound complicated, the resolution of the adjoint problem using finite elements methods is actually extremely easy.
+Indeed, as the scalar product used in the definition of the weak formulation \eqref{NSweak} and of the adjoint \eqref{EigenAdj} is the same, the weak formulations of both problems happen to be identical when swapping the test and the unknown functions .
+Therefore, the matricial form of the discretized version of \eqref{EigenAdj} is deduced from the one of the direct problem by a simple (Hermitian) transpose of the matrix :
 \be{Eigen_Adj_matricial}
@@
 \ee
-Adjoint eigenmodes are a powerful tool for investigating problems such as receptivity, transient growth, control and sensitivity (see the reviews of \cite{Jmc2005}, \cite{Ps2007}, \cite{LucBott2014}).
-The simplest physical interpretation of an adjoint eigenmode is as follows : it corresponds to the initial condition which has maximum projection along the direction of the corresponding eigenmode.
+Adjoint eigenmodes are a powerful tool for investigating problems such as receptivity, transient growth, control and sensitivity (see the reviews of \cite{Jmc2005}, \cite{Ps2007} and \cite{LucBott2014}).
+The simplest physical interpretation of an adjoint eigenmode is as follows: it corresponds to the initial condition which has maximum projection along the direction of the corresponding eigenmode.
 Thus, the adjoint of the most amplified mode corresponds to the optimal perturbation which will maximize the growth of energy in the limit of large time.
@@
 
-Examination of the structure of the adjoint eigenmodes gives access to a number of informations about the instability mechanism which are not visible when examining only the direct eigenmodes.
-First, a simple examination the dissimilarity between direct and adjoint eigenmodes is an indication of the nonnormality of the linear operator, mostly associated to the convection term in open flows \cite{Jmc2005}.
-Secondly, in a more elaborated way, the product of both fields allows to define the the so-called {\em structural sensitivity tensor } defined as
+Investigating the structure of the adjoint eigenmodes gives access to a number of informations about the instability mechanism which are not visible when examining only the direct eigenmodes.
+First, a simple examination of the dissimilarity between direct and adjoint eigenmodes is an indication of the non-normality of the linear operator, mostly associated to the convection term in open flows \cite{Jmc2005}.
+Secondly, in a more elaborated way, the product of both fields allows defining the so-called {\em structural sensitivity tensor } defined as
 \be{StructurrTens} 
@@
 \ee
-As formalized by \cite{GiannettiLuchini} (following ideas previously proposed by \cite{hill1992theoretical}), this quantity quantifies how an eigenvalue is 
-affected by the introduction of localized feedback of the flow perturbation on itself.
+
+As formalized by \cite{GiannettiLuchini} (following ideas previously proposed by \cite{hill1992theoretical}), this metrics quantifies how an eigenvalue is affected by the introduction of localized feedback of a flow perturbation onto itself.
 It thereby indicates the spatial regions where closed-loop control using a localized activator will be most efficient.
-Giannetti \& Luchini (2007) conjectured that those regions where such an extrinsic feedback induce the strongest change of the eigenvalue are also the most significant regions considering the intrinsic feedback mechanisms that underpin the genuine eigenmode dynamics.
-Following this idea, structural sensitivity has thus become a popular way to characherize the  {\em wavemaker region} where the instability mechanism originates.
+Giannetti \& Luchini (2007) conjectured that regions where such an extrinsic feedback induces the strongest change of the eigenvalue are also the most significant regions considering the intrinsic feedback mechanisms that underpins the genuine eigenmode dynamics.
+Following this idea, structural sensitivity has thus become a popular way to characherize the  {\em wavemaker region} from where the instability mechanism originates.
 The structural sensitivity being a tensor, is is convenient to simply represent its norm $S_w$, often simply called 'the wavemaker':
@@
 \ee 
-More recently, \cite{marquet2015endogeneity} reconsidered the question of identification of the active flow regions that drive the instabilities.
+More recently, \cite{marquet2015endogeneity} reconsidered the question of identifying the active flow regions that drive the instabilities.
 They argued that such regions might be better identified by a quantity called the {\em endogeneity} and defined as
@@
 This definition has several advantages.
-In particular, being a complex quantity, it allows to distinguish the flow regions which contribute respectively to the oscillation frequency and the growth rate, hence giving more insight into the intrinsic flow dynamics.
-This quantity is also potentially useful for mesh design, as will be discussed in section 2.3.
+In particular, being a complex quantity, it allows distinguishing the flow regions which contribute respectively to the oscillation frequency and the growth rate, hence giving more insight into the intrinsic flow dynamics.
+This quantity is also potentially useful for mesh design, as discussed in section 2.3.
 
@@
 can be performed using several methods.
-Direct methods to compute the whole spectrum are both costly prohibitive and useless.
+Direct methods to compute the whole spectrum are both costly prohibitive and their usefulness is disputable.
 A popular alternative is the use of iterative methods to compute a limited set of eigenvalues located in the vicinity of a
-{\em shift} value $\lambda_{shift}$. The simplest version of this method is the simple shift-invert iteration, which consists of solving iteratively the system
+{\em shift} value $\lambda_{shift}$. The simplest version of this method is the simple shift-invert iteration which consists in solving iteratively the system
 $$
@@
 %Our implementation in StabFem allows to chose between single eigenvalue computation (power method) and multiple eigenvalue computation (Arnoldi). 
-For the case of the 2D incompressible flow, resolution of the eigenvalue problem (including adjoint, sensitivity and endogeneity) is done by the FreeFem++ solver {\sf  Stab2D.edp}; an extract of this solver featuring the implementation of the shift-invert algorithm is displayed in appendix E.
+For the case of the 2D incompressible flow, resolution of the eigenvalue problem (including adjoint, sensitivity and endogeneity) is done by the FreeFem++ solver {\sf  Stab2D.edp}; an excerpt of this solver featuring the implementation of the shift-invert algorithm is displayed in appendix E.
 The latter is wrapped by the Octave/Matlab driver {\sf  SF\_Stability.m} which accepts a number of optional parameters.
-For instance, the selection between shfift-invert and Arnoldi is made according to the parameter \verb|nev|  (i.e.
+For instance, the selection between shift-invert and Arnoldi is made according to the parameter \verb|nev|  (i.e.
 number of requested eigenvalues) transmitted to the driver.
-(an extract of this code featuring the implementation of the Newton loop is given in appendix E).
+(an excerpt of this code featuring the implementation of the Newton loop is given in appendix E).
 
@@
 \small
-\lstinputlisting{Script_Cylinder_Part1.m}
+\lstinputlisting{SCRIPT_CYLINDER_Part1.m}
  \normalsize
 \caption{Illustration of the usage of the StabFem software to produce an adapted mesh and study the base flow and the linear stability properties of the wake flow around a cylinder 
-(extract from script {\sf  SCRIPT\_CYLINDER\_ALLFIGURES.m})}
+(extracted from script {\sf  SCRIPT\_CYLINDER\_ALLFIGURES.m})}
 \label{Listing2}
@@
 
-As for any numerical method, a crucial point in the numerical efficiency is the design of the mesh.
-The finite element method allows to use unstructured mesh and hence to locally adapt the refinement.
+As for any numerical method, a crucial aspect for numerical efficiency is the design of the mesh.
+The finite element method allows using unstructured mesh and hence to locally adapt the refinement.
 %Following Sipp \& Lebedev,
 The most common procedure is to decompose the domain into several parts with different grid densities; for instance for the wake of a cylinder, we will design a near-wall region with very small  size, a wake region with intermediate mesh size, and an outer region with large mesh size.
-The inconvenient is that the design relies on an a priori expectation of the regions where gradients will be large.
-
-In our implementation, we used an automatic mesh adaptation method. %which provides an optimal mesh adapted to the structure of the flow. 
-The implementation relies on the AdaptMesh procedure of the FreeFem++ software. This procedure is detailed in detail in ref. \cite{adapt}. 
+The drawback of such mesh generation guidelines is that the design relies on an a priori expectation of the regions where gradients will be large.
+
+In our implementation, we use an automated mesh adaptation method. %which provides an optimal mesh adapted to the structure of the flow. 
+The implementation relies on the AdaptMesh procedure of the FreeFem++ software. This procedure is detailed in ref. \cite{adapt}. 
 In short, the classical Delaunay-Voronoi algorithm produces a mesh with gridpoint distribution specified by a {\em Metric } matrix $\cal M$.
-The AdaptMesh algorithm consists of using as a metric the {\em Hessian} (second-order spatial derivatives) of an objective function $u_h$ defined over the domain, i.e.
+The AdaptMesh algorithm consists in using as a metric the {\em Hessian} (second-order spatial derivatives) of an objective function $u_h$ defined over the domain, i.e.
 ${\cal M} = \nabla \nabla u_h$.
@@
 %The procedure thus ensures that the mesh will be locally adapted to the gradients of the base flow.
-The base flow is then recomputed on the adapted mesh, providing a better approximation of the solution. The procedure can be repeated a few steps to ensure a right convergence.
-
-The mesh generated in the previous way may not be optimal for the stability calculations as the structure of the eigenmode may be more complex than that of the base flow.
-To remedy with this, the idea is to subsequently adapt the mesh to both the mesh flow and the results of the stability calculation.
+The base flow is then recomputed on the adapted mesh, providing a better approximation of the solution. The procedure can be repeated over a few steps to ensure a right convergence.
+
+The mesh generated by the previous way may not be optimal for the stability calculations as the structure of the eigenmode may be more complex than that of the base flow. 
+To tackle this aspect, the idea is to subsequently adapt the mesh to both the mesh flow and the results of the stability calculation.
 This is easily done with FreeFem, as the  AdaptMesh procedure can be used with several objective functions.
@@
 It is shown that for the case of a cylinder, all strategies give the same values for base-flow drag, eigenvalues and several properties of the nonlinear limit cycle (see sec.
-4) with less than $0,3\%$ deviation, but that the A, E and especially the S strategy lead to significantly lower number of grid points compared to the D strategy.
+4) with less than $0.3\%$ deviation, but that the A, E and especially the S strategy lead to significantly lower number of grid points compared to the D strategy.
 The practical conclusions of this study are the following recommendations :
@@
 \item[-] 
-First, if one is interested only in the eigenvalues, for instance to plot growth rates as function of Reynolds or to identify the critical Reynolds number, The A, E or S strategies are the best options.
+First, if one is only interested in the eigenvalues --for instance to plot growth rates as function of Reynolds or to identify the critical Reynolds number,-- the A, E or S strategies are the best options.
 In the case of the cylinder, the S strategy leads to the lightest mesh.
-The E strategy results in a more refined mesh because the function $S_e$ is complex and displays more gradients than the real-valued function $S_w$ (as will be illustrated in figure 6) ; hence the sensitivity revealed by the phase of $S_e$, which may be significant, is not capture by using the simpler function $S_w$.
-In the case of the flow around a cylinder,  this loss of information has no practical effect on the results, but for usage with more complex flows, or recommendation for future studies will be to privilege the E strategy.
+The E strategy results in a more refined mesh as the function $S_e$ is complex and displays more gradients than the real-valued function $S_w$ (as illustrated in Fig.
+\ref{fig:StructEndo}); hence the sensitivity revealed by the phase of $S_e$, which may be significant, is not captured by using the simpler function $S_w$.
+In the case of the flow around a cylinder,  this loss of information has no practical effect on the results, but for usage with more complex flows, our recommendation for future studies will be to favour the E strategy.
 \item[-] 
-The situation is different if one wants to design a mesh allowing to study the structure of the flow in the whole domain (for instance for plotting its structure).
-In that case, using A,E or S strategy will allow to accurately compute the eigenvalue and the structure of the mode in the wavemaker region, but will not allow a proper resolution in the regions located far away where the direct mode may reach large amplitude.
+The situation is different if one wants to design a mesh allowing to study the flow structure in the whole domain (for instance for plotting its structure).
+In that case, using A,E or S strategy will allow to accurately compute the eigenvalue and the structure of the mode in the wavemaker region, but will not allow for a proper resolution in the regions located far away where the direct mode may reach large amplitude.
 This is particularly the case for open flows characterized by large spatial convective amplifications.
@@
 
-In our implementation, the whole process of mesh adaptation (including projection and recomputation of the base flow on the new mesh) is monitored using the Octave/Matlab driver {\sf  SF\_AdaptMesh.m} ; the kind of adaptation  (to base flow only (BF), or D, A, S , E strategies) is decided by the the nature of the objects transmitted to this function.
-In the current implementation it is possible to adapt the mesh to as much as 8 fields of diverse nature (for instance, multiple eigenmodes along with their adjoint fields, harmonic-balance fourirer components, etc...)
+In our implementation, the whole process of mesh adaptation (including projection and recomputation of the base flow on the new mesh) is monitored using the Octave/Matlab driver {\sf  SF\_AdaptMesh.m} ; the kind of adaptation  (to base flow only (BF), or D, A, S , E strategies) is decided by the the nature of the objects given as input to this function.
+In the current implementation it is possible to adapt the mesh to as much as 8 fields of diverse nature (for instance, multiple eigenmodes along with their adjoint fields, harmonic-balance Fourier components, etc...)
 
@@
 \small
-\lstinputlisting{Script_Cylinder_Part2.m}
+\lstinputlisting{SCRIPT_CYLINDER_Part2.m}
  \normalsize

### 2018-12-06 99_Documentation/ARTICLE_STABFEM/ARTICLE_ASME_Revision.tex
Supplementary corrections of article up to end of Conclusion.

@@
 
-%\title{Popularizing linear and nonlinear global approaches to hydrodynamic instabilities : 
+%\title{Popularizing linear and nonlinear global approaches to hydrodynamic instabilities: 
 %A review and a simple implementation for the wake of a cylinder}
@@
 Secondly we offer an open-source and user-friendly software called  {\sf StabFem} %\cprotect 
-\footnote{The StabFem software may be obtained at the following url : \\
+\footnote{The StabFem software may be obtained at the following url: \\
 \url{https://www.gitlab.com/stabfem/StabFem}. 
@@
 
-\section{Linear stability analysis : equations and methods}
+\section{Linear stability analysis: equations and methods}
 \vspace{.2cm}
@@
 
-We look for a steady base-flow $[{\bf u}_b,p_b]$ satisfying the steady Navier--Stokes equations, i.e. 
+We look for a steady base-flow $[{\bf u}_b,p_b]$ satisfying the steady Navier--Stokes equations, \textit{i.e.} 
 %${\cal NS} ({\bf u}_b,p_b) = 0$.
@@
 Injecting \eqref{Newton1} into the weak form \eqref{NSweak} of the Navier--Stokes equations and linearizing leads to  
-${\cal NS}  ({\bf u}_b^g,p_b^g) +  {\cal LNS} _{{\bf u}_b^g}(\delta {\bf u}_b,\delta p_b)$, which can also be written in weak form as :
+${\cal NS}  ({\bf u}_b^g,p_b^g) +  {\cal LNS} _{{\bf u}_b^g}(\delta {\bf u}_b,\delta p_b)$, which can also be written in weak form as:
 \bes{Newton2}
@@
 \ee
-or, in weak form : 
+or, in weak form: 
 \be{eigenvalueproblem}
@@
 \ee
-where ${\mathsf{A}}$ is the matrix resulting from the discretization of ${\cal LNS}_{{\bf u}_b}$, i.e.
-the same matrix  appearing in the Newton computation of the base flow, and  $B$ is a weight matrix associated to the scalar product $\left<v,u\right> = \int \overline{\bf v} \cdot {\bf u} \mbox{ d} \Omega$.
+where ${\mathsf{A}}$ is the matrix resulting from the discretization of ${\cal LNS}_{{\bf u}_b}$, \textit{i.e.} the same matrix  appearing in the Newton computation of the base flow, and  $B$ is a weight matrix associated to the scalar product $\left<v,u\right> = \int \overline{\bf v} \cdot {\bf u} \mbox{ d} \Omega$.
 
@@
 Indeed, as the scalar product used in the definition of the weak formulation \eqref{NSweak} and of the adjoint \eqref{EigenAdj} is the same, the weak formulations of both problems happen to be identical when swapping the test and the unknown functions .
-Therefore, the matricial form of the discretized version of \eqref{EigenAdj} is deduced from the one of the direct problem by a simple (Hermitian) transpose of the matrix :
+Therefore, the matricial form of the discretized version of \eqref{EigenAdj} is deduced from the one of the direct problem by a simple (Hermitian) transpose of the matrix:
 \be{Eigen_Adj_matricial}
@@
 Thus, the adjoint of the most amplified mode corresponds to the optimal perturbation which will maximize the growth of energy in the limit of large time.
-In effect, one can prove that for $t \rightarrow \infty$  the asymptotic behaviour of a solution with initial condition ${\bf u}_i$  is given as :
+In effect, one can prove that for $t \rightarrow \infty$  the asymptotic behaviour of a solution with initial condition ${\bf u}_i$  is given as:
 $$
@@
 It is easy to show that this iterative procedure quickly asymptotes to $X^{n+1} \approx ({\lambda^*}^{-1})^n \hat{X}$
-where $\hat{X}$ is the eigenmode with largest ${\lambda^*}^{-1}$ (i.e. the one with eigenvalue $\lambda$ closest to the shift).
+where $\hat{X}$ is the eigenmode with largest ${\lambda^*}^{-1}$ (\textit{i.e.} the one with eigenvalue $\lambda$ closest to the shift).
 
@@
 If we want to compute a larger number of eigenvalues, we can revert to a generalized version of iterative methods, called Arnoldi methods\cite{Arnoldi51}.
-The shift-invert version of the Arnoldi method is in fact the most commonly used method of the current time and is at the basis of both the popular Octave/Matlab function {\tt{eigs}} and the standard eigenvalue solver of FreeFem (i.e.
-ARPACK++).
+The shift-invert version of the Arnoldi method is in fact the most commonly used method of the current time and is at the basis of both the popular Octave/Matlab function {\tt{eigs}} and the standard eigenvalue solver of FreeFem (\textit{i.e.} ARPACK++).
 %Our implementation in StabFem allows to chose between single eigenvalue computation (power method) and multiple eigenvalue computation (Arnoldi). 
@@
 The latter is wrapped by the Octave/Matlab driver {\sf  SF\_Stability.m} which accepts a number of optional parameters.
-For instance, the selection between shift-invert and Arnoldi is made according to the parameter \verb|nev|  (i.e.
-number of requested eigenvalues) transmitted to the driver.
+For instance, the selection between shift-invert and Arnoldi is made according to the parameter \verb|nev|  (\textit{i.e.} number of requested eigenvalues) transmitted to the driver.
 (an excerpt of this code featuring the implementation of the Newton loop is given in appendix E).
@@
 In short, the classical Delaunay-Voronoi algorithm produces a mesh with gridpoint distribution specified by a {\em Metric } matrix $\cal M$.
-The AdaptMesh algorithm consists in using as a metric the {\em Hessian} (second-order spatial derivatives) of an objective function $u_h$ defined over the domain, i.e.
-${\cal M} = \nabla \nabla u_h$.
+The AdaptMesh algorithm consists in using as a metric the {\em Hessian} (second-order spatial derivatives) of an objective function $u_h$ defined over the domain, \textit{i.e.} ${\cal M} = \nabla \nabla u_h$.
 The precision can be controlled by specifying an objective value for the interpolation error of the function on the new mesh.
@@
 4) with less than $0.3\%$ deviation, but that the A, E and especially the S strategy lead to significantly lower number of grid points compared to the D strategy.
-The practical conclusions of this study are the following recommendations :
+The practical conclusions of this study are the following recommendations:
 
@@
 In the case of the cylinder, the S strategy leads to the lightest mesh.
-The E strategy results in a more refined mesh as the function $S_e$ is complex and displays more gradients than the real-valued function $S_w$ (as illustrated in Fig.
-\ref{fig:StructEndo}); hence the sensitivity revealed by the phase of $S_e$, which may be significant, is not captured by using the simpler function $S_w$.
+The E strategy results in a more refined mesh as the function $S_e$ is complex and displays more gradients than the real-valued function $S_w$ (as illustrated in figure \ref{fig:StructEndo}); hence the sensitivity revealed by the phase of $S_e$, which may be significant, is not captured by using the simpler function $S_w$.
 In the case of the flow around a cylinder,  this loss of information has no practical effect on the results, but for usage with more complex flows, our recommendation for future studies will be to favour the E strategy.
@@
 Here, we consider the two-dimensional flow of an incompressible fluid of density $\rho$ past a circular cylinder. 
-All flow quantities are normalized using the uniform incoming velocity $U_{\infty}$ and the cylinder diameter $D$, 
-which are the characteristic velocity and length scales used for the definition of Reynolds number $Re= U_{\infty} D / \nu$.
-The origin of the cartesian frame of reference is considered located on the cylinder axis, the x-axis is chosen to be parallel to 
+All flow quantities are normalized using the uniform incoming velocity $U_{\infty}$ and the cylinder diameter $D$,  which are the characteristic velocity and length scales used for the definition of Reynolds number $Re= U_{\infty} D / \nu$.
+The origin of the Cartesian frame of reference is considered located on the cylinder axis, the x-axis is chosen to be parallel to 
 the incoming free-stream velocity while the y-axis with the cross-stream velocity.
 The dimensions of the computational domain are the following: $-40 \le x/D \le 80$ and $0 \le y/D \le 40$ (boundary conditions and their implementation are detailed in appendix D).
-Note that we take advantage of the symmetry properties of the problem to use a half-domain for resolution.
+Note that we take advantage of the symmetry properties of the problem to only solve it on the positive $y$ half-domain.
 
@@
 In particular, the hydrodynamic lift and drag forces read
-\footnote{ Remark that $F_x$ and $F_y$ are actually nondimensional forces per unit length. 
+\footnote{ Note that $F_x$ and $F_y$ are actually nondimensional forces per unit length. 
 For a cylinder of diameter $D$ and length $L$ (assuming $L\gg D$ so that the assumption of 2D flow makes sense), 
@@
 
-Let us consider now the Octave/Matlab code reported in figure \ref{Listing2}.
+Let us now consider the Octave/Matlab code reported in figure \ref{Listing2}.
 First we build an initial mesh (line 1), and compute base flow solutions for increasing values of the Reynolds number up to $Re = 60$ (lines 3-9).
 Then we perform the mesh adaptation with S strategy, as explained previously (line 13). 
-The resulting mesh, depicted in figure \ref{fig:mesh2}, is used for the rest of the computations presented in this paper (except for plotting the structure of the direct eigenmode in figure 5$a$ and computing the energy of the nonlinear perturbation displayed in figure \ref{fig:HB_SC_DATA_COMP}$(d)$ which a heavier mesh obtained with adaptation strategy D).
-Appendix A presents additional test regarding mesh convergence, and demonstrate that results obtained with the resulting mesh are trustable within $0.3\%$ accuracy for the eigenvalue.
+The resulting mesh, depicted in figure \ref{fig:mesh2}, is used for the rest of the computations presented in this paper (except for plotting the structure of the direct eigenmode in figure \ref{fig:Eigenmode}$(a)$ and computing the energy of the nonlinear perturbation displayed in figure \ref{fig:HB_SC_DATA_COMP}$(d)$ which a heavier mesh obtained with adaptation strategy D).
+Appendix A presents additional tests regarding mesh convergence, and demonstrates that results obtained with the resulting mesh are reliable within $0.3\%$ accuracy tolerance for the eigenvalue.
 It must be emphasized  that the mesh generated through this adaptation process is very light, with only 2048 vertices, which is significantly less than reported in previous work (for instance, in their mesh convergence studies, \cite{SippLebedev} and \cite{MLugo2014} used respectively 190868  and 6731 vertices).
@@
 
-Having thus produced a convenient mesh, we can now illustrate the properties of the base flow as function of Reynolds number.
-Figure \ref{Listing2} shows how to compute and plot with StabFem the two most commonly studied quantities, namely the recirculation length $Lx(Re)$, i.e.
-the location of the stagnation point at the rear of the recirculation region, and the drag force $F_x(Re)$.
+Having thus produced a convenient mesh, we can now illustrate the properties of the base flow as a function of Reynolds number.
+Figure \ref{Listing2} shows how to compute and plot with StabFem the two most commonly studied quantities, namely the recirculation length $Lx(Re)$, \textit{i.e.} the location of the stagnation point at the rear of the recirculation region, and the drag force $F_x(Re)$.
 Note that the object \verb|bf| is defined as a structure with fields \verb|Fx| and \verb|Lx|. 
@@
 \footnote{\url{https://github.com/samplemaker/freefem\_matlab\_octave\_plot}}.  
-This function allows a number of possibilities for plotting data on unstructured meshes, including color plots, isolevels, streamlines, quiver plots, etc..
-The choice of parameters used here (lines 8-10 of the script in figure \ref{Listing2})  allows to plot both the pressure field and selection of streamlines (through isocontours of the streamfunction $\psi$).
+This function provides a number of possibilities for plotting data on unstructured meshes, including color plots, isolevels, streamlines, quiver plots, etc\ldots
+The choice of parameters used here (lines 8-10 of the script in figure \ref{Listing2})  allows plotting both the pressure field and selection of streamlines (through isocontours of the streamfunction $\psi$).
 This representation allows to easily visualize the extension of the recirculation region.
-In accordance with figure \ref{fig:LxandDrag}$(b)$, for $Re = 60$ the recirculation length is $L_x = \approx 4.07$.
+In accordance with figure \ref{fig:LxandDrag}$(b)$, for $Re = 60$ the recirculation length is $L_x \approx 4.07$.
 
@@
 
-We investigate the stability of the base flow field by performing a parametric study of the eigenproblem (\ref{LEP}).
-In this way, we determine the critical Reynolds number $Re_c$ at with the steady base flow first becomes unstable: to this end it is useful to remember that a flow state is linearly unstable when the real part of  the leading eigenvalue, i.e.
-the growth rate, is positive.
-In our implementation, parametric study is done by the loop over Reynolds corresponding to lines 21-30 of the script in figure \ref{Listing2}.
+We investigate the stability of the base flow field by performing a parametric study of the eigenproblem \eqref{LEP}. 
+In this way, we determine the critical Reynolds number $Re_c$ from which the steady base flow first becomes unstable: to this end it is useful to remember that a flow state is linearly unstable when the real part of  the leading eigenvalue, \textit{i.e.} the growth rate, is positive.
+In our implementation, a parametric study is performed by looping over increasing Reynolds, corresponding to lines 21-30 of the script in figure \ref{Listing2}.
 Note that at line 26 the options {\sf  'shift, 'cont' ,'guess', em} transmitted to the driver {\sf  SF\_Stability} allow to use an optimum value for the shift interpolated using the previous computations, and a guess value to initialize the shift-invert procedure corresponding to the previously computed eigenmode.
@@
 The wavemaker $S_w$ and endogeneity $S_e$ fields, introduced in section 2.2, are displayed in figure \ref{fig:StructEndo}.
-As discussed in section 2.2, both these quantities allow to identify the 'active' flow regions responsible for the instability mechanism.
+As discussed in section 2.2, both these quantities allow identifying the 'active' flow regions responsible for the instability mechanism.
 The real quantity $S_w$ indicates that the most active region roughly coincides with the recirculation bubble.
-The endogeneity $S_e$ give more information.
-The sign of the real part (color levels)  indicate that the two most destabilizing regions are the boundary layer at the top of the cylinder and the shear layer bonding the recirculation region, and that the region of the stagnation point and the exterior of the recirculation region are destabilizing.
-The imaginary part (isolevels) indicate that the frequency selection occurs in the shear layer region.
+The endogeneity $S_e$ yields more information of interest.
+The sign of the real part (color levels) indicates that the two most destabilizing regions are the boundary layer at the top of the cylinder and the shear layer bonding the recirculation region, and that the region of the stagnation point and the exterior of the recirculation region are destabilizing.
+The imaginary part (isolevels) indicates that the frequency selection occurs in the shear layer region.
 
@@
 
-In the past decade, efforts have been devoted to extend the range of validity of global approaches into the nonlinear regime for $Re>Re_c$, with the double objective to describe the properties of the limit cycle reached after saturation and to derive amplitude equations describing the transient dynamics towards this cycle.
-The two main milestones in this direction  are the {\em weakly nonlinear model}  (WNL) of Sipp \& Lebedev \cite{SippLebedev} and the {\em self-consistent model} (SC) of Manti\v{c}-Lugo et al \cite{MLugo2014}.
- In this review, we will address only the first of the two questions, namely  the description of the saturated cycle, and leave aside the question of transient dynamics.
+In the past decade, efforts have been devoted to extend the range of validity of global approaches into the nonlinear regime for $Re>Re_c$, with the double objective of (i) describing the properties of the limit cycle reached after saturation and (ii) deriving amplitude equations describing the transient dynamics towards this cycle.
+The two main milestones in this direction are the {\em weakly nonlinear model} (WNL) of Sipp \& Lebedev \cite{SippLebedev} and the {\em self-consistent model} (SC) of Manti\v{c}-Lugo et al.
+\cite{MLugo2014}.
+In this review, we will only address the first of the two questions, namely  the description of the saturated cycle, and leave aside the question of transient dynamics.
 We will successively review the two aforementioned models, in a simplified formulation devoted to describe only the saturated cycle.
 We also provide a simple implementation of these two models.
-Finally, in line with the previous section, we will again illustrate with results obtained for the wake of a cylinder.
+Finally, in line with the previous sections, this analysis is illustrated with results obtained for the wake of a cylinder.
 
@@
 In the nonlinear regime, the {\em base flow} introduced in the linear theory is no longer relevant, especially when the oscillation amplitudes become large. 
-Instead, one may define a {\em mean flow} by time-averaging : 
+Instead, one may define a {\em mean flow} by time-averaging: 
 %{\color{red} we taken the Reynolds decomposition ${\bf u}={\bf u}_m({\bf x})+{\bf u}'({\bf x},t)$, with ${\bf u}'$ the nonlinear perturbation and ${\bf u}_m$ the {\em mean flow} defined as the time-average  of the flow:}
@@
 In the next sections we will document the predictions of the WNL and SC models regarding the quantities $A_E$ and $L_x$ adopted in past studies.
-In addition, we will document two other quantities of practical interest : the Drag and Lift forces $F_x$ and $F_y$ exerted on the cylinder.
+In addition, we will document two other quantities of practical interest: the Drag and Lift forces $F_x$ and $F_y$ exerted on the cylinder. 
 Both are periodic functions of time and, owing to symmetry consideration, the drag contains only even harmonics and the lift only odd harmonics:
@@
 In the sequel we will focus on the {\em mean drag}  $F_{x,0}$ and on the fundamental components of the lift  
-$F_{y,1,c}$ and $F_{y,1,s}$. These quantities are easily extractible from a numerical simulation or an experiment, and we will
-show how they can be predicted from the nonlinear global approaches.
+$F_{y,1,c}$ and $F_{y,1,s}$. These quantities are easily retrievable from a numerical simulation or an experiment, and we will show how they can be predicted from the nonlinear global approaches.
 
@@
 Lebedev\cite{SippLebedev}, also discussed by Gallaire et al. \cite{FDR2016}.  
-The initial derivation of \cite{SippLebedev} makes use of a multiple scale method in order to obtain an amplitude equation.
+The initial derivation of \cite{SippLebedev} makes use of a multiple scales method in order to obtain an amplitude equation.
 This complete analysis is reproduced in appendix B. In the present paragraph, we give a simplified derivation of this model restricted to the description of the periodic saturated cycle.
@@
 
-The second-order term contains three contributions: ${\bf u}_{\epsilon}$ is the modification to the base flow related to the 
-increase of $Re$, ${\bf u}_{2,0}$  represents the nonlinear interaction of $\hat{\bf u}$ with its conjugate, ${\bf u}_{2,2}$ the nonlinear 
-interaction of $\hat{\bf u}$ with itself. These three terms are computed as solutions of nonsingular linear systems 
-(see eqs. \ref{eq:LL1}, \ref{eq:LL2}, \ref{eq:LL3} in appendix B).
-
-At ${\cal O}( \epsilon ^3)$, compatibility conditions have to be imposed to ensure that the problem is correctly posed.
+The second-order term contains three contributions: ${\bf u}_{\epsilon}$ is the modification to the base flow related to the increase of $Re$, ${\bf u}_{2,0}$ represents the nonlinear interaction of $\hat{\bf u}$ with its conjugate, ${\bf u}_{2,2}$ the nonlinear interaction of $\hat{\bf u}$ with itself.
+These three terms are computed as solutions of nonsingular linear systems (see eqs. \eqref{eq:LL1}, \eqref{eq:LL2} and \eqref{eq:LL3} in appendix B).
+
+At ${\cal O}( \epsilon ^3)$, compatibility conditions need to be enforced to ensure that the problem is correctly posed.
 These conditions lead to an {\em amplitude equation} which relates the amplitude $ A_{wnl}$ to three parameters $\Lambda, \nu_{0}$ and $\nu_{2}$ which depend
-uniquely on ${\bf u}_\epsilon$, ${\bf u}_{2,0}$ and ${\bf u}_{2,2}$, respectively (see equations \ref{LAMBDA}, \ref{NU0} and \ref{NU2} in appendix B).
-Restricting to the description of the limit cycle, the {\em amplitude equation} takes the form :
+uniquely on ${\bf u}_\epsilon$, ${\bf u}_{2,0}$ and ${\bf u}_{2,2}$, respectively (see equations \eqref{LAMBDA}, \eqref{NU0} and \eqref{NU2} in appendix B).
+Restricting to the description of the limit cycle, the {\em amplitude equation} takes the form:
 
@@
 Finally, as specified above, we explain how the mean drag $F_{x,0}$ and fundamental components $(F_{y,1,c},F_{y,1,s})$ of the oscillating lift can be predicted from the WNL approach.
-The mean drag  can be obtained by $F_{x,0} = {\cal D}_{Re}({\bf u}_m,p_m)$, where ${\cal D}$ is the drag operator defined in \ref{drag} and 
+The mean drag  can be obtained by $F_{x,0} = {\cal D}_{Re}({\bf u}_m,p_m)$, where ${\cal D}$ is the drag operator defined in \eqref{drag} and 
 $[{\bf u}_m,p_m]$ is the {\em mean flow}  
-which corresponds to the time-average of expansion  \ref{WNL1}, namely :
+which corresponds to the time-average of expansion  \eqref{WNL1}, namely:
 $
@@
 $
-Developing the terms as an asymptotic expansion leads to :
+Developing the terms as an asymptotic expansion leads to:
 \be{drag_cos}
@@
 
-Similarly the required components of the lift force are obtained by applying the lift operator ${\cal L}$ defined in \ref{lift} 
-to the order-one component of the expansion, leading to :
+Similarly the required components of the lift force are obtained by applying the lift operator ${\cal L}$ defined in \eqref{lift} 
+to the order-one component of the expansion, leading to:
 \be{lift_cos}
@@
 On line 4, we then compute all the terms and coefficients of the WNL model.
-Lines 6-8 then processes the results in a way they can be plotted.
+Lines 6-8 then process the results so that they can be plotted.
 %{\color{red}The other lines are explained latter.}
@@
 
-Figure \ref{fig:HB_SC_DATA_COMP} represent the predictions of the WNL approach regarding the frequency (expressed as a Strouhal number through $St = \omega/2\pi$), mean drag, amplitude of the oscillating lift, and energy-amplitude.
-As discussed in \cite{SippLebedev} and \cite{FDR2016},  when compared to DNS results the approach gives good prediction in the immediate vicinity of $Re_c$, but deviation appears very rapidly and disagreement is already large at $Re=48$ (although, as discussed by \cite{FDR2016} and also observed  \cite{Tchoufag2015}, a convenient definition of the $\epsilon$ improves the results).
+Figure \ref{fig:HB_SC_DATA_COMP} represents the predictions of the WNL approach regarding the frequency (expressed as a Strouhal number through $St = \omega/2\pi$), mean drag, amplitude of the oscillating lift, and energy-amplitude.
+As discussed in \cite{SippLebedev} and \cite{FDR2016},  when compared to DNS results, this approach gives good prediction in the immediate vicinity of $Re_c$, but deviation appears very rapidly and disagreement is already large at $Re=48$ (although, as discussed by \cite{FDR2016} and also observed by \cite{Tchoufag2015}, a convenient definition of $\epsilon$ improves the prediction).
  These aspects are justified by the perturbative nature of the WNL approach. The description of the limit cycle can be extended to larger $Re$ with the approach presented next.
@@
 \end{center}
-\caption{Comparison between the weakly nonlinear results (WNL), the harmonic balance data (HB1), and baseflow/linear results : Strouhal number $(a)$, Mean drag $(b)$, amplitude of oscillating lift $(c)$, Energy-amplitude of the nonlinear perturbation $(d)$ and recirculation lenght of mean/base flows ($e)$.
+\caption{Comparison between the weakly nonlinear results (WNL), the harmonic balance data (HB1), and baseflow/linear results: Strouhal number $(a)$, Mean drag $(b)$, amplitude of oscillating lift $(c)$, Energy-amplitude of the nonlinear perturbation $(d)$ and recirculation length of mean/base flows $(e)$.
 %c_x should be consistent with the drag definition given at beginning
@@
 We now briefly review the self-consistent model as introduced by Manti\v{c}-Lugo et 
-al \cite{MLugo2014}. In its original exposition, the authors adopted a pseudo-eigenmode expansion of the flow 
+al. \cite{MLugo2014}.
+In their original exposition, the authors adopted a pseudo-eigenmode expansion of the flow 
 as follows: 
@@
 
-The original version of the model (discussed with some more details in appendix C) allowed to obtain an amplitude equation predicting the instantaneous growth rate $\sigma$ as function of the amplitude $A_{sc}$.
+The original version of the model (discussed with some supplementary details in appendix C) allowed obtaining an amplitude equation predicting the instantaneous growth rate $\sigma$ as function of the amplitude $A_{sc}$.
 However, if we are simply interested in the properties of the limit cycle, not the transient, we may recast the self-consistent model in a simpler way.
@@
 %Note {\color{red} that,} contrary to the SC model, the amplitude $A_{HB}$ of the oscillation} can easily be computed a posteriori as ${\color{red}A_{HB}} = \sqrt{2 ||{\bf u }_1||}$. 
-%On the other hand, the Fourier description of the limit cycle is invariant with respect to the phase $\phi$ (i.e.
-the equations are unchanged when replacing ${\color{red} {\bf u }_1 }$ by  ${\color{red} {\bf u }_1 e^{i\phi}}$).
+%On the other hand, the Fourier description of the limit cycle is invariant with respect to the phase $\phi$ (\textit{i.e.} the equations are unchanged when replacing ${\color{red} {\bf u }_1 }$ by  ${\color{red} {\bf u }_1 e^{i\phi}}$).
 
@@
 Note that the amplitude $A_{sc}$, which was considered as a key parameter in the original model of \cite{MLugo2014}, 
-does not appear in the simplified version discussed here. The connection between our parametrization and that of Manti\v{c}-Lugo is as follows :
+does not appear in the simplified version discussed here. The connection between our parametrization and that of Manti\v{c}-Lugo et al. is as follows:
 \be{HBtoSC}
@@
 \ee 
-Considering their normalization choice, the parameter $A_{sc}$ of \cite{MLugo2014},  can be easily deduced from our results as follows :
+Considering their normalization choice, the parameter $A_{sc}$ of \cite{MLugo2014} can be easily deduced from our results as follows:
 $A_{sc} = \sqrt{2 \int_\Omega ( |{\bf u }_{1,c}|^2+ |{\bf u }_{1,s}|^2) d S} $.
@@
 When reformulated in this way, the nonlinear problem addressed by the self-consistent model actually reduces to the restriction to order one of a more general class of methods called harmonic balance methods (HB).
-One of the first aplications of these methods in the domain of fluid mechanics has done by Carte and Du\v{s}ek (\cite{CarteDusek1995},\cite{CarteDusekfraunie1996}).
-The development of such methods, or related ones such the time-spectral method (\cite{HallThomasClark2002}) and the search for efficient numerical implementation to solve such problems is currently an active field of development in the fluid dynamics community.
+One of the first applications of these methods in the domain of fluid mechanics has been done by Carte and Du\v{s}ek \cite{CarteDusek1995,CarteDusekfraunie1996}.
+The development of such methods, or related ones such as the time-spectral method (\cite{HallThomasClark2002}) and the search for efficient numerical implementation to solve such problems is currently an active field of development in the fluid dynamics community.
 When considering HB development with a large order of terms, direct resolution by inversion of the full matrix is not achievable.
@@
 After discretization, this leads to a linear problem of the form $A X = Y$ where $X$ is the discretized version of the unknowns  $[\delta {\bf u }_m, \delta {\bf u }_{1,c}, \delta {\bf u }_{1,s}, \delta \omega]$, and $A$ is a matrix of dimension $3 N_{dof} +1$, where $N_{dof}$ is the dimension of the Taylor--Hood basis of finite elements describing each of the three $[{\bf u},p]$ fields.
-This system is solved iteratively in the same way as explained in section 2.1 for determination of the base flow.
+This system is solved iteratively as explained in section 2.1 for determination of the base flow.
 %Using the adapted mesh described in figure 2, the dimension of the system is $3 N_{dof} +1 \approx 58 000$ and the resolution remains possible at very reasonable computational costs.
 Mesh convergence issues for the nonlinear calculations are discussed in appendix A.
-It is shown that the mesh $\mathbf{M}_2$ designed using 'S' strategy is sufficient to yield converged results within $0.3\%$ accuracy for all quantities considered here, with the exception of the energy-amplitude $A_E$ which requires the more refined mesh $\mathbf{M}_4$ obtained using 'D' strategy.\footnote{In terms of computational cost, on a standard laptop the program  \ref{fig:listingNL} requires approximatively 413 seconds using  mesh $\mathbf{M}_2$ and 31 minutes using mesh $\mathbf{M}_4$.}
+It is shown that the mesh $\mathbf{M}_2$ designed using 'S' strategy is sufficient to yield converged results within $0.3\%$ accuracy for all quantities considered here, with the exception of the energy-amplitude $A_E$ which requires the more refined mesh $\mathbf{M}_4$ obtained using 'D' strategy.\footnote{In terms of computational cost, on a standard laptop the program  \ref{fig:listingNL} requires approximatively 7 minutes using  mesh $\mathbf{M}_2$ and 31 minutes using mesh $\mathbf{M}_4$.}
 
@@
 Lines 10-17 of the script shown in figure \ref{fig:listingNL} explain how to to use these programs to the SC/HB1 model for the wake of a cylinder in the range $Re \in [47-100] $.
-Note that a {\em guess} for the mean flow and the self-consistent mode for $Re = 47$, i.e.
-just above the threshold, has already been generated from the weakly nonlinear model at line 4 of the same script.
+Note that a {\em guess} for the mean flow and the self-consistent mode for $Re = 47$, \textit{i.e.} just above the threshold, has already been generated from the weakly nonlinear model at line 4 of the same script.
 This guess is used for the first step of the loop over Reynolds in lines 14-17.
-For next steps of the loop, continuation is done using the previous calculation as a guess.
+For next steps of the loop, continuation is done using the previous calculation results as guess.
 
@@
 \end{center}
-\caption{Structure of the {\em mean flow} over a cylinder for $Re = 60$, as computed by the HB1 model. color levels : pressure ; streamlines.}
+\caption{Structure of the {\em mean flow} over a cylinder for $Re = 60$, as computed by the HB1 model. color levels: pressure ; streamlines.}
 \label{fig:MF60}
@@
 Figure \ref{fig:HB_SC_DATA_COMP} shows the comparison between the WNL (green) and HB1/SC (red) models for the quantities of interest identified in this paper, namely the Strouhal number, the mean drag, the maximum lift, the energy-amplitude, and the recirculation length associated to the mean flow.
-When relevant, results concerning the base flow and the linear approach are also displayed (blue)
+When relevant, results regarding the base flow and the linear approach are also displayed (blue)
 \footnote{Figure   \ref{fig:HB_SC_DATA_COMP} is obtained by line 19 of the script displayed in figure \ref{fig:listingNL}.
 The other figures are processed in a similar way.
-The entire set of commands to obtain all figures is provided in the script {\sf SCRIPT\_CYLINDER\_ALLFIGURES.m} .}.
+The entire set of commands to obtain all figures is provided in the script {\sf SCRIPT\_CYLINDER\_ALLFIGURES.m}.}.
 Concerning the quantities $St$, $A_E$ and $L_x$, differences between HB1/SC, WNL models have already been commented in \cite{MLugo2014} and \cite{FDR2016}.
@@
 The present results are also compared with the available literature, namely with the experiments of \cite{williamson1988defining} for the $St$ number and with the DNS results of \cite{MLugo2014} for $A_E$ and $L_x$.
-The predictions of the SC/HB1 model show an excellent agreement in the range $Re \in [Re_c,100]$ with the rReferences. %Regarding the forces exerted on the body, 
+The predictions of the SC/HB1 model show an excellent agreement in the range $Re \in [Re_c,100]$ with the references. %Regarding the forces exerted on the body, 
 However, we can remark that the predictions of the WNL model rapidly depart from the previous ones as soon as $Re-Re_c \gtrsim 1$.
@@
 In accordance with this objective, all the figures presented in the paper can be produced by launching a single Octave/Matlab program available on the website of the project.
-
-Although the focus here was on the reference case of 2D, incompressible flow around a cylinder, the  {\em StabFem } software is designed to be easily customisable to a variety of other situations.
+This program handles all computation steps, from calls to FreeFem++ to figure generation.
+
+Although the focus here was on the reference case of 2D incompressible flow around a cylinder, the {\em StabFem } software is designed to be easily customisable to a variety of other situations.
 The project is currently in constant development, and incorporates a growing number of other configurations.
-In the present status, the project incorporates test-cases for the following classes of problems:
+Under its present status, the project incorporates test-cases for the following classes of problems:
 \begin{itemize}
@@
 \ref{Newton2} by a test function ${\bf v}$ and the associated divergence constraint by a test function $q$.
-After a few integration by parts we are led to :
+After a few integration by parts we are led to:
 
@@
 %\displaystyle &\int \left[ {\bf v} \cdot {\cal C}( {\bf u}_b^g , \delta {\bf u}_b) +  \nabla  \cdot \delta {\bf u}_b q -\nabla  \cdot {\bf v} \delta p_b
-%+ \frac{2}{Re} {\bf D}(\delta {\bf u}_b) : {\bf D}({\bf v}) \right]
+%+ \frac{2}{Re} {\bf D}(\delta {\bf u}_b): {\bf D}({\bf v}) \right]
 %\nonumber
@@
 %- \nabla \cdot {\bf v} p_b^g
-%+ \frac{2}{Re} {\bf D}({\bf u}_b^g) : {\bf D}({\bf v}) \right] = 0 
+%+ \frac{2}{Re} {\bf D}({\bf u}_b^g): {\bf D}({\bf v}) \right] = 0 
 %\end{eqnarray}
 
-\section{Mesh convergence : efficiency of mesh adaptation and effect of domain size}
+\section{Mesh convergence: efficiency of mesh adaptation and effect of domain size}
 \begin{figure}
@@
 $$
-\caption{Description of meshes used for validation of mesh adaptation strategy : number of vertices $N_p$ ; number of degrees of freedom of the P2-P2-P1 Taylor--Hood basis $N_{dof}$ ; cell size (minimum and maximum value, and value at four characteristic point A,B,C,D as defined in the text).
+\caption{Description of meshes used for validation of mesh adaptation strategy: number of vertices $N_p$ ; number of degrees of freedom of the P2-P2-P1 Taylor--Hood basis $N_{dof}$ ; cell size (minimum and maximum value, and value at four characteristic point A,B,C,D as defined in the text).
  }
@@
 $$
-\caption{Results for mesh adaptation strategy ($Re = 60$) : Base-flow characteristics $L_x$ and $F_x$, linear eigenvalue $\lambda$, 
+\caption{Results for mesh adaptation strategy ($Re = 60$): Base-flow characteristics $L_x$ and $F_x$, linear eigenvalue $\lambda$, 
 Nonlinear self-consistent model characteristics  $\omega_{HB1}$, $F_{y,1,c}$ and $A_E$. All the results can be optained using the Octave/Matlab script
@@
 This appendix presents complementary results obtained using various mesh designs. 
-All the results can be obtained using the following program available on the StabFem website : 
+All the results can be obtained using the following program available on the StabFem website: 
 {\sf SCRIPT\_CYLINDER\_MESHCONVERGENCE.m}.
@@
 Table \ref{tab:conv1} gives numerical informations about the geometry of these meshes.
-In particular, we document the minimum and maximum cell size, as well as the cell size at four point A,B,C,D defined with by their coordinates as follows : $(x_A,y_A) = (0,0.5)$ (within the boundary layer at the cylinder wall); $(x_B,y_B) = (2.5,0.5)$ (in the region of maximum structural sensitivity); $(x_C,y_C) = (4,0)$ (in the near wake); $(x_D,y_D) = (10,0)$ (in the far wake).
+In particular, we document the minimum and maximum cell size, as well as the cell size at four point A,B,C,D defined with by their coordinates as follows: $(x_A,y_A) = (0,0.5)$ (within the boundary layer at the cylinder wall); $(x_B,y_B) = (2.5,0.5)$ (in the region of maximum structural sensitivity); $(x_C,y_C) = (4,0)$ (in the near wake); $(x_D,y_D) = (10,0)$ (in the far wake).
 Results confirm that mesh all meshes have similar densities in the near wake (cell size at points A,B,C are comparable)
@@
 The objective of this appendix is to provide additional details about the  SC model in its original form as given by \cite{MLugo2014}, and to explain the connection with the simpler version discussed in section 4.2.
-The full model is obtained by introducing the decomposition (\ref{SC}) into the Navier--Stokes equations, leading to :
+The full model is obtained by introducing the decomposition (\ref{SC}) into the Navier--Stokes equations, leading to:
 \begin{subequations}\label{sc12}
@@
 \begin{itemize}
-\item[-] For $ A \ll 1$ it is equivalent to the linear eigenvalue problem (\ref{LEP}), and the generalized eigenvalue coincides with the one predicted by linear stability : $\sigma_{SC} + i \omega_{SC} = \sigma_{lin} + i \omega_{lin}$.
+\item[-] For $ A \ll 1$ it is equivalent to the linear eigenvalue problem (\ref{LEP}), and the generalized eigenvalue coincides with the one predicted by linear stability: $\sigma_{SC} + i \omega_{SC} = \sigma_{lin} + i \omega_{lin}$.
 \item[-] For $\sigma_{SC}=0$ (corresponding to a specific choice of the amplitude $A=A_{sc}$),  the expansion (\ref{SC}) is equivalent to 
@@
 
-Noting $\Gamma$ the boundary of the numerical domain, the latter can be decomposed in five parts : 
+Noting $\Gamma$ the boundary of the numerical domain, the latter can be decomposed in five parts: 
 $\Gamma = \Gamma_{in} \cup \Gamma_{cyl} \cup \Gamma_{axis} \cup \Gamma_{out} \cup \Gamma_{lat}$. 
@@
 \end{itemize}
-We will introduce the following notation for integrals along any portion of the boundary $\Gamma_i$ of the product of two quantities $\phi_1, \phi_2$ (either scalar or vectorial) :
+We will introduce the following notation for integrals along any portion of the boundary $\Gamma_i$ of the product of two quantities $\phi_1, \phi_2$ (either scalar or vectorial):
 %$\left< \phi_1, \phi_2 \right>_{\Gamma_i} $:
@@
 \forall [{\bf v},q], &&\, \partial_t \left< {\bf v}, {\bf u}\right> = - \left< {\bf v} , {\cal C}({\bf u},{\bf u})/2 \right>
-- 2 Re^{-1} \left< {\mathsf D}({\bf v}) : {\mathsf D}({\bf u})  \right>  \nonumber \\
+- 2 Re^{-1} \left< {\mathsf D}({\bf v}): {\mathsf D}({\bf u})  \right>  \nonumber \\
 + &&\left< \nabla \cdot {\bf v}, p \right> + \left< q, \nabla \cdot {\bf u} \right> \label{NSweakFullN} \\
@@
 
-%Giannetti \& Luchini\cite{GiannettiLuchini} showed that the accuracy of the stability results for the flow past a circular cylinder is strictly related to the mesh characteristics  in the wavemaker region, i.e.
-the region where the structural sensitivity reaches its maximum values.
+%Giannetti \& Luchini\cite{GiannettiLuchini} showed that the accuracy of the stability results for the flow past a circular cylinder is strictly related to the mesh characteristics  in the wavemaker region, \textit{i.e.} the region where the structural sensitivity reaches its maximum values.
 Following this idea, we chose as reference solution the field, computed on an adapted mesh obtained by using the structural sensitivity field.We set the interpolation  error equal to 0.01 and the size of the computational domain is $[-40,120]\times[0,40]$.

### 2018-12-07 99_Documentation/ARTICLE_STABFEM/ARTICLE_ASME_Revision.tex
Appendices corrections.

@@
 
-The numerical resolution of generalized eigenvalue problems such as $A X = \lambda B X$ (or its adjoint version (\ref{Eigen_Adj_matricial}) ), 
+The numerical resolution of generalized eigenvalue problems such as $A X = \lambda B X$ (or its adjoint version \eqref{Eigen_Adj_matricial}), 
 can be performed using several methods.
@@
 \ee
-so that the Fourier decomposition of the lift force \ref{drag_lift_def} will contain only a cosine term, namely 
+so that the Fourier decomposition of the lift force \eqref{drag_lift_def} will contain only a cosine term, namely 
 \be{FySC}
@@
 This appendix presents complementary results obtained using various mesh designs. 
-All the results can be obtained using the following program available on the StabFem website: 
+All results can be obtained using the following program available on the StabFem website: 
 {\sf SCRIPT\_CYLINDER\_MESHCONVERGENCE.m}.
@@
 
-As discussed in section 3, the mesh adaptation proves to be an extremely efficient way to obtain significant results 
-with very reasonable meshes. The objective of this paragraph is to demonstrate this point by comparing the efficiency of several ways to perform mesh adaptation.
+As discussed in section 3, the mesh adaptation proves to be an extremely efficient way to obtain significant and reliable results 
+with very reasonable meshes.
+The objective of this paragraph is to demonstrate this point by comparing the efficiency of several mesh adaptation ways.
 
@@
 Meshes $\mathbf{M}_4$ and $\mathbf{M}_5$ were obtained by adapting to the structure of the direct eigenmode (strategy D) and of the adjoint eigenmode (strategy A).
-In each case, the adaptmesh process was repeated twice in order to ensure a correct convergence.
+In each case, the adapt-mesh process was repeated twice to ensure a correct convergence.
 
 Figures \ref{fig:mesh2} and \ref{fig:mesh4} illustrate the structure of meshes $\mathbf{M}_2$ and $\mathbf{M}_4$.
-As can be observed, these two mesh adaptation strategies lead to meshes with comparable densities in the region close to the cylinder.
-On the other hand, when moving downwards in the wake, mesh $\mathbf{M}_2$ quickly gets rather coarse, while mesh $\mathbf{M}_4$ maintains a significant density.
+It can be observed that these two mesh adaptation strategies lead to meshes with comparable densities in the region close to the cylinder.
+On the other hand, when moving downwards in the wake, mesh $\mathbf{M}_2$ quickly gets rather coarse while mesh $\mathbf{M}_4$ maintains a significant density.
 
@@
 In particular, we document the minimum and maximum cell size, as well as the cell size at four point A,B,C,D defined with by their coordinates as follows: $(x_A,y_A) = (0,0.5)$ (within the boundary layer at the cylinder wall); $(x_B,y_B) = (2.5,0.5)$ (in the region of maximum structural sensitivity); $(x_C,y_C) = (4,0)$ (in the near wake); $(x_D,y_D) = (10,0)$ (in the far wake).
-Results confirm that mesh all meshes have similar densities in the near wake (cell size at points A,B,C are comparable)
-while $\mathbf{M}_4$ has maximum resolution in the far wake (in the vicinity of point D).
+Results confirm that all meshes have similar densities in the near wake (cell size at points A,B,C are comparable) while $\mathbf{M}_4$ has maximum resolution in the far wake (in the vicinity of point D).
 
 Table \ref{tab:conv2} compares the results obtained with the six meshes.
-For base-flow characteristics $L_x$ and $F_x$, all values agree with a relative dispersion of less than $0.15\%$, confiming that all adaptation stategies are successful to correctly compute the base flow.
+For base-flow characteristics $L_x$ and $F_x$, all values agree with a relative dispersion of less than $0.15\%$.
+This underlines that all adaptation strategies are successful to correctly compute the base flow. 
 The performances of meshes for linear stability calculations can then be evaluated by comparing the eigenvalues.
@@
 As for the frequency and the maximum lift, meshes $\mathbf{M}_2$ to $\mathbf{M}_5$ again give almost identical values within less than $0.1\%$ dispersion.
-The dispersion is much larger concerning the energy-amplitude of the perturbation $A_E$ displayed in the last column.
-Only the mesh $\mathbf{M}_4$ is able to correctly compute this quantities, while all other meshes significantly underestimate it.
-This is not surprising since this quantity is an integral one which depends upon the structure of the nonlinear perturbation in the whole wake, not only the near-wake region.
+The dispersion concerning the energy-amplitude of the perturbation $A_E$ displayed in the last column is however much larger.
+Only the mesh $\mathbf{M}_4$ is able to correctly compute this quantity, while all other meshes significantly underestimate it.
+ This is not surprising since this quantity is an integral property which depends upon the structure of the nonlinear perturbation over the whole wake, not only the near-wake region.
 
@@
 
-As already identified in several previous studies, the size of the domain and the type of boundary conditions applied at the boundaries have a notable impact on the results.
+As already identified in several previous studies, the size of the domain and the type of boundary conditions applied at the boundaries have a notable impact on results.
 To illustrate this, we designed four additional meshes.
@@
 Meshes $\mathbf{M}_6$ and $\mathbf{M}_7$ are respectively twice smaller and twice larger than the reference one. 
-Meshes $\mathbf{M}_8$ and $\mathbf{M}_9$ have the same dimension but the boundary condition at the lateral boundary
- $\Gamma_{lat}$ differs.
+Meshes $\mathbf{M}_8$ and $\mathbf{M}_9$ have the same dimension but the boundary condition at the lateral boundary $\Gamma_{lat}$ differs. 
 Unlike the reference case $\mathbf{M}_2$ which uses a no-stress boundary condition (identical to that applied at the outlet), mesh $\mathbf{M}_8$ uses a "slip" condition $u_y = 0 ; \partial u_x/\partial y = 0$ while mesh $\mathbf{M}_9$ uses an even more restrictive constant-flow condition (the condition at the lateral boundary is $u_x = 1, u_y = 0$, just as for the inlet).
@@
 Even though the domain size of the reference case (namely $[-40,80]\times[0,40]$) may appear large, the table shows that confinement effects are still present.
-The quantity which appears the most sensible to domain size and/or boundary conditions is the imaginary part of the linear eigenvalue.
+The quantity which appears to be the the most sensitive to domain size and/or boundary conditions is the imaginary part of the linear eigenvalue.
 Interestingly, the nonlinear SC results appears to be more robust with respect to confinement effects than linear ones. 
@@
 
-The initial derivation of \cite{SippLebedev} makes use of a multiple scale method in order to obtained an amplitude equation.
+The initial derivation of \cite{SippLebedev} makes use of a multiple scale method in order to obtain an amplitude equation.
 The starting point can be taken as the following expansion of the velocity flow field:
@@
 \ee
-Note that compared to the simplified version given in the main text by eq. \ref{WNL1}, the amplitude $A_{wnl}$ depends upon a slow time scale 
+Note that compared to the simplified version given in the main text by eq. \eqref{WNL1}, the amplitude $A_{wnl}$ depends upon a slow time scale 
 $\tau = \epsilon^2 t$.
 
-Substituting the expansion \ref{WNL2} into the Navier--Stokes equations \ref{NSprimitive} and grouping terms multiplied by the same power of $\epsilon$, a hierarchy of equations is obtained.
+Substituting the expansion \eqref{WNL2} into the Navier--Stokes equations \eqref{NSprimitive} and grouping terms multiplied by the same power of $\epsilon$, a hierarchy of equations is obtained.
 The order $\epsilon^0$ gives directly the base flow at $Re_c$.
@@
 
-A key issue in the weakly nonlinear expansion is that the definition of the amplitude depends upon a normalization choice of the eigenmodes.
-Several choices are possible.
+A key issue in the weakly nonlinear expansion is that the definition of the amplitude depends upon a normalization choice of the eigenmodes. Several choices are possible.
 In the literature three possibilities have been used:
@@
 \ee
-The advantage of this choice is that the amplitude $|A|$ is then an direct measure of the fundamental lift.
-In effect, eq. \ref{lift_cos} directlty leads to $F_{y,1,c} = |A|$, $F_{y,1,s} = 0$.
-
-In our implementation of the WNL approach, we allowed to choose the normalization convention, as seen in line 3 of figure \ref{fig:listingNL}.
+The advantage of this choice is that the amplitude $|A|$ is then a direct measure of the fundamental lift.
+In effect, eq. \eqref{lift_cos} directlty leads to $F_{y,1,c} = |A|$, $F_{y,1,s} = 0$.
+
+In our implementation of the WNL approach, we allowed choosing the normalization convention, as seen in line 4 of figure \ref{fig:listingNL}.
 %%ATTENTION, si figure est actualisé, il faut actualiser la ligne
@@
 We can note that the coefficients $\nu_0$ and $\nu_2$ strongly depend on the normalization choice.
-On the other hand, the frequency deviation $\omega_\epsilon$ and the $\lambda$ coefficient, and the term $F_{x,0,\epsilon}$ related to the dependency of mean drag with deviation from the threshold are independent upon the normalization.
+On the other hand, the frequency deviation $\omega_\epsilon$, the $\lambda$ coefficient, and the term $F_{x,0,\epsilon}$ related to the dependency of mean drag with deviation from the threshold are independent upon the normalization.
 
@@
 The objective of this appendix is to provide additional details about the SC model in its original form as given by \cite{MLugo2014}, and to explain the connection with the simpler version discussed in section 4.2.
-The full model is obtained by introducing the decomposition (\ref{SC}) into the Navier--Stokes equations, leading to:
+The full model is obtained by introducing the decomposition \eqref{SC} into the Navier--Stokes equations, leading to:
 \begin{subequations}\label{sc12}
@@
 
-Equation (\ref{sis1}) provides the mean flow field ${\bf u }_m$ while the 
-pseudo-eigenpairs $(\lambda_{sc},  \tilde{{\bf u }}_1)$ can be computed by solving the eigenvalue problem (\ref{sis2}).
-\cite{MLugo2014} Initially proposed a resolution method involving two imbricated loops, which is advantageaously replaced by
+Equation \eqref{sis1} provides the mean flow field ${\bf u }_m$ while the 
+pseudo-eigenpairs $(\lambda_{sc},  \tilde{{\bf u }}_1)$ can be computed by solving the eigenvalue problem \eqref{sis2}.
+\cite{MLugo2014} initially proposed a resolution method involving two nested loops, which is advantageously replaced by
 the direct Newton resolution of section 4.3.
@@
 \begin{itemize}
-\item[-] For $ A \ll 1$ it is equivalent to the linear eigenvalue problem (\ref{LEP}), and the generalized eigenvalue coincides with the one predicted by linear stability: $\sigma_{SC} + i \omega_{SC} = \sigma_{lin} + i \omega_{lin}$.
-\item[-] For $\sigma_{SC}=0$ (corresponding to a specific choice of the amplitude $A=A_{sc}$),  the expansion (\ref{SC}) is equivalent to 
-the Fourier expansion \ref{eq:sc1} taken as the starting point in the present paper. 
+\item[-] For $ A \ll 1$, it is equivalent to the linear eigenvalue problem \eqref{LEP}, and the generalized eigenvalue coincides with the one predicted by linear stability: $\sigma_{SC} + i \omega_{SC} = \sigma_{lin} + i \omega_{lin}$.
+\item[-] For $\sigma_{SC}=0$ (corresponding to a specific choice of the amplitude $A=A_{sc}$), the expansion \eqref{SC} is equivalent to 
+the Fourier expansion \eqref{eq:sc1} taken as the starting point in the present paper. 
 \item[-] For $0<A<A_{sc}$, the resolution leads to a relation $\sigma_{SC}(A) ; \omega_{SC}(A)$
@@
 $$
-Instead of the simplified version \ref{NSweak}, the more precise form of the weak formulation can be first written as follows:
+Instead of the simplified version \eqref{NSweak}, the more precise form of the weak formulation can be first written as follows:
 \begin{eqnarray}
@@
 \end{eqnarray}
-Note that the Neumann boundary conditions do not appear any more thanks to the integration by parts.
+Note that the Neumann boundary conditions do not appear anymore thanks to the integration by parts.
 
@@
 In this appendix, we provide pieces of codes illustrating how the basic algorithms are implemented in the FreeFem++ solvers.
-These expanations will be useful for both people codes who whish to use directly FreeFem++ solvers without using the overlayer of Octave/Matlab drivers provided by the StabFem software, and also for persons who want to understand the logics of the implementation and customize the software to implement their own cases.
+These explanations will be useful both for readers who wish to use directly FreeFem++ solvers without using the overlayer of Octave/Matlab drivers provided by the StabFem software, and also for those who want to understand the logics of the implementation and customize the software to implement their own cases.
 The full version of the codes is available in the web repository of the StabFem project.
@@
 Note that the syntax makes use of macros {\sf  D, div, Conv}, resulting in a very similar to the weak formulation written in the previous appendix.
-The boundary conditions are also coded using a macro {\sf  BoundaryconditionsBaseFlow}.
-To allow an easy customization, this macro is not defined in the generic solver {\sf  Newton2D.edp} but is reported in a file {\sf  Macros\_StabFem.idp} regrouping case-dependant macros (essentially boundary conditions and postprocessing options).
+The boundary conditions are also implemented using a macro {\sf  BoundaryconditionsBaseFlow}.
+To allow an easy customization, this macro is not defined in the generic solver {\sf  Newton2D.edp} but is reported in a file {\sf  Macros\_StabFem.idp} regrouping case-dependant macros (essentially boundary conditions and post-processing options).
 
 Figure \ref{Listing4} details the implementation of the shift-invert algorithm for eigenvalue computation, as implemented in the generic solver {\sf  Stab2D.edp} for 2D incompressible flows.
-Here again, the boundary conditions (which may differ from a case to an other within the generic class of 2D incompressible flows) is given by a macro {\sf  BoundaryconditionsStability} which has to be defined in the  {\sf  Macros\_StabFem.idp} file.
+Here again, boundary conditions (which may differ from a case to an other within the generic class of 2D incompressible flows) are defined by a macro {\sf  BoundaryconditionsStability} which has to be defined in the  {\sf  Macros\_StabFem.idp} file.
 

### 2018-12-07 99_Documentation/ARTICLE_STABFEM/ARTICLE_ASME_Revision.tex
Incorporate corrections sent by David.

@@
 
-\graphicspath{{./}{../../STABLE_CASES/CYLINDER/FIGURES/}}
+\graphicspath{{./}{../../STABLE_CASES/CYLINDER/FIGURES/}{../../DEVELOPMENT_CASES/CompressibleCylinder/Sponge/FIGURES/}}
 
@@
 	$^{(a)}$ Institut de M\'ecanique des fluides de Toulouse (IMFT), University of Toulouse \\
-	$^{(b)}$ Dipartimento do Ingegneria (DIIN), Universit\`a} di Salerno. 
+	$^{(b)}$ Dipartimento di Ingegneria (DIIN), Universit\'a} di Salerno. 
 }
@@
 On the other hand,  when there are at least two spatial variables, the class of methods suited to solve such problems are generally called {\em global stability approaches}.
-A classical example of such behavior in fluid dynamics is the instability occurring in the wake of a circular cylinder.
+A classical example of such behaviour in fluid dynamics is the instability occurring in the wake of a circular cylinder.
 At low Reynolds number (precisely for $Re < 46.7$) the flow is steady and symmetric, but for larger values of Re a global instability arises in the flow field leading to the well-known von K\'arm\'an vortex alley.
@@
 
-In the present paper the concepts are introduced and the software is demonstrated for the reference case of the incompressible, two-dimensional flow around a cylinder, but the software is easily customizable to a variety of other situations (compressible, three-dimensional, etc..).
+In the present paper the concepts are introduced and the software is demonstrated for the reference case of the incompressible, two-dimensional flow around a cylinder, but the software is easily customizable to a variety of other situations (free-surface, three-dimensional, etc..).
+We show also the application to compressible flows for the same geometrical configuration.
 
@@
 
+In this part, we expose the main concepts and methods of linear stability analysis for the case of a incompressible flow.
+The extension to compressible flow will be considered in section \ref{sec:compressible}.
+
 \paragraph{Navier--Stokes equations and weak form}
@@
 \begin{eqnarray} \label{NSprimitive}
-\partial_t {\bf u} = {\cal NS} ({\bf u},p)
+\partial_t  [{\bf u},p] = {\cal NS} ( [{\bf u},p] )
 \equiv - {\bf u} \cdot \nabla {\bf u} - \nabla p + \frac{2}{Re}  \nabla \cdot {\mathsf{D}}({\bf u}),  \\
@@
 $$
+
 In the framework of finite element methods, we need to write the equations in weak form.
 Prior to this we define a scalar product as follows, for both scalar or vectorial quantities
+
 $\left< \phi_1, \phi_2 \right> $:
@@
 \ee
+
 Injecting \eqref{Newton1} into the weak form \eqref{NSweak} of the Navier--Stokes equations and linearizing leads to  
-${\cal NS}  ({\bf u}_b^g,p_b^g) +  {\cal LNS} _{{\bf u}_b^g}(\delta {\bf u}_b,\delta p_b)$, which can also be written in weak form as:
+${\cal NS}  ({\bf u}_b^g,p_b^g) +  {\cal LNS} _{{\bf u}_b^g}(\delta {\bf u}_b,\delta p_b) = 0$, which can also be written in weak form as:
+
 \bes{Newton2}
@@
 \ee
-This problem can now be discretized by projecting upon a basis of Taylor--Hood $(u,v,p) \rightarrow (P2,P2,P1)$ finite elements.
+
+In the framework of finite elements, this problem can now be discretized by projecting upon a basis of Taylor--Hood $(u,v,p) \rightarrow (P2,P2,P1)$ elements.
 Noting $\delta X$ the discretization of $[\delta {\bf u}_b,\delta p_b]$ this eventually leads to a matricial problem of the form $A \cdot \delta X = Y$.
-The Newton iteration procedure aims at iteratively solving this set of equations up to a defined convergence criterion.
+The procedure of Newton iteration is to solve iteratively this set of equations up to convergence.
 In our implementation, the algorithm for a 2D incompressible flow is written in the Freefem++ solver {\sf Newton\_2D.edp} (an extract of this code featuring the implementation of the Newton loop is given in appendix E).
@@
 
-\paragraph{Adjoint eigenvalue problem, structural sensitivity, and wavemaker characterization}
+\paragraph{Adjoint eigenvalue problem, structural sensitivity and wavemaker characterization}
 Developed in the two past decades, the concept of adjoint eigenmodes has now become an unavoidable complement to the linear global stability approach.
 We here give a short summary of the definition and usefulness of this concept and refer the reader to Luchini \& Bottaro\cite{LucBott2014} for further details.
+
 First of all, the {\em adjoint linearised Navier--Stokes operator} ${\cal LNS}^\dag$ is defined thanks to the following 
@@
 \ees
-We can then define the adjoint eigenvalues and eigenmodes as the solutions of the eigenvalue problem 
+We can then define the adjoint eigenvalues and eigenmodes as the solution of the eigenvalue problem 
 \be{EigenAdj} 
@@
 \ee
-Adjoint eigenmodes are a powerful tool for investigating problems such as receptivity, transient growth, control and sensitivity (see the reviews of \cite{Jmc2005}, \cite{Ps2007} and \cite{LucBott2014}).
+The adjoint field is a powerful tool for investigating problems such as receptivity, transient growth, control and sensitivity (see the reviews of \cite{Jmc2005}, \cite{Ps2007} and \cite{LucBott2014}).
 The simplest physical interpretation of an adjoint eigenmode is as follows: it corresponds to the initial condition which has maximum projection along the direction of the corresponding eigenmode.
@@
 
-Investigating the structure of the adjoint eigenmodes gives access to a number of informations about the instability mechanism which are not visible when examining only the direct eigenmodes.
+Investigating the structure of the adjoint eigenmodes gives access to a number of information about the instability mechanism which are not visible when examining only the direct eigenmodes.
 First, a simple examination of the dissimilarity between direct and adjoint eigenmodes is an indication of the non-normality of the linear operator, mostly associated to the convection term in open flows \cite{Jmc2005}.
@@
 \ee 
-More recently, \cite{marquet2015endogeneity} reconsidered the question of identifying the active flow regions that drive the instabilities.
+%More recently, \cite{marquet2015endogeneity} reconsidered the question of identifying the active flow regions that drive the instabilities.
 They argued that such regions might be better identified by a quantity called the {\em endogeneity} and defined as
-\be{Endo} 
-S_e({\bf x}) =  \frac{  \hat{\bf u}^\dag({\bf x}) \cdot  {\cal LNS}_{\bf U} \, \hat{\bf u}({\bf x})  }{{\left<\hat{\bf u}^\dag, \hat{\bf u}\right>}}  
-= \lambda \frac{ \hat{\bf u}^\dag({\bf x}) \cdot \hat{\bf u}({\bf x}) }{{\left<\hat{\bf u}^\dag, \hat{\bf u}\right>}},
-\ee 
-This definition has several advantages.
+%\be{Endo} 
+%S_e({\bf x}) =  \frac{  \hat{\bf u}^\dag({\bf x}) \cdot  {\cal LNS}_{\bf U} \, \hat{\bf u}({\bf x})  }{{\left<\hat{\bf u}^\dag, \hat{\bf u}\right>}}  
+%= \lambda \frac{ \hat{\bf u}^\dag({\bf x}) \cdot \hat{\bf u}({\bf x}) }{{\left<\hat{\bf u}^\dag, \hat{\bf u}\right>}},
+%\ee 
+%This definition has several advantages.
 In particular, being a complex quantity, it allows distinguishing the flow regions which contribute respectively to the oscillation frequency and the growth rate, hence giving more insight into the intrinsic flow dynamics.
@@
 %Our implementation in StabFem allows to chose between single eigenvalue computation (power method) and multiple eigenvalue computation (Arnoldi).
-For the case of the 2D incompressible flow, resolution of the eigenvalue problem (including adjoint, sensitivity and endogeneity) is done by the FreeFem++ solver {\sf  Stab2D.edp}; an excerpt of this solver featuring the implementation of the shift-invert algorithm is displayed in appendix E.
+For the case of the 2D incompressible flow, resolution of the eigenvalue problem is done by the FreeFem++ solver {\sf  Stab2D.edp}; an excerpt of this solver featuring the implementation of the shift-invert algorithm is displayed in appendix E.
 The latter is wrapped by the Octave/Matlab driver {\sf  SF\_Stability.m} which accepts a number of optional parameters.
@@
 \begin{figure}
-\includegraphics[width=.9 \linewidth]{Cylinder_Lx_baseflow.png}
-\includegraphics[width=.9 \linewidth]{Cylinder_Fx_baseflow}
+\includegraphics[width=\linewidth]{Cylinder_Lx_baseflow.png}
+\includegraphics[width=\linewidth]{Cylinder_Fx_baseflow}
 \caption{Recirculation length $L_x$ $(a)$  and nondimensional drag $F_x$ ($b$) of the base flow over a cylinder as function of $Re$.}
@@
 As for any numerical method, a crucial aspect for numerical efficiency is the design of the mesh.
-The finite element method allows using unstructured mesh and hence to locally adapt the refinement.
+The finite element method allows using unstructured mesh and hence to have a local adaptation.
 %Following Sipp \& Lebedev,
@@
 
-\section{Illustration for the wake of a cylinder} 
+\section{Illustration for the wake of a cylinder (incompressible case)}  
 \vspace{.2cm}
@@
 Here, we consider the two-dimensional flow of an incompressible fluid of density $\rho$ past a circular cylinder. 
-All flow quantities are normalized using the uniform incoming velocity $U_{\infty}$ and the cylinder diameter $D$,  which are the characteristic velocity and length scales used for the definition of Reynolds number $Re= U_{\infty} D / \nu$.
-The origin of the Cartesian frame of reference is considered located on the cylinder axis, the x-axis is chosen to be parallel to 
-the incoming free-stream velocity while the y-axis with the cross-stream velocity.
+All flow quantities are normalized using the uniform incoming velocity $U_{\infty}$ and the cylinder diameter $D$, which are the characteristic velocity and length scales used for the definition of the Reynolds number $Re= U_{\infty} D / \nu$.
+The origin of the Cartesian frame of reference is considered located on the cylinder axis, the x-axis is chosen to be parallel to the incoming free-stream velocity while the y-axis with the cross-stream velocity.
 The dimensions of the computational domain are the following: $-40 \le x/D \le 80$ and $0 \le y/D \le 40$ (boundary conditions and their implementation are detailed in appendix D).
@@
 Then we perform the mesh adaptation with S strategy, as explained previously (line 13).
-The resulting mesh, depicted in figure \ref{fig:mesh2}, is used for the rest of the computations presented in this paper (except for plotting the structure of the direct eigenmode in figure \ref{fig:Eigenmode}$(a)$ and computing the energy of the nonlinear perturbation displayed in figure \ref{fig:HB_SC_DATA_COMP}$(d)$ which a heavier mesh obtained with adaptation strategy D).
+The resulting mesh, depicted in figure \ref{fig:mesh2}, is used for the rest of the computations presented in this paper (except for plotting the structure of the direct eigenmode in figure \ref{fig:Eigenmode}$(a)$ and computing the energy of the nonlinear perturbation displayed in figure \ref{fig:HB_SC_DATA_COMP}$(d)$ which adopted a finer mesh obtained with the strategy D).
 Appendix A presents additional tests regarding mesh convergence, and demonstrates that results obtained with the resulting mesh are reliable within $0.3\%$ accuracy tolerance for the eigenvalue.
@@
 \begin{figure}
-\includegraphics[width=.9 \linewidth]{Cylinder_Sigma_Re.png}
-\includegraphics[width=.9 \linewidth]{Cylinder_Strouhal_Re.png}
-\caption{Growth rate $\sigma$ $(a)$  and Strouhal number $St = \omega/2\pi$ ($b$) as function of Reynolds number}
+\includegraphics[width=\linewidth]{Cylinder_Sigma_Re.png}
+\includegraphics[width=\linewidth]{Cylinder_Strouhal_Re.png}
+\caption{Growth rate $\sigma$ $(a)$  and Strouhal number $St = \omega/2\pi$ ($b$) as function of the Reynolds number.}
 \label{fig:SigmaOmega}
@@
 %\vspace{-.5cm}
-\includegraphics[width=.9 \linewidth]{Cylinder_EigenModeRe60_AdaptS.png}%{Cylinder_EigenModeRe60_AdaptD.png}
+\includegraphics[width=\linewidth]{Cylinder_EigenModeRe60_AdaptS.png}%{Cylinder_EigenModeRe60_AdaptD.png}
 %\vspace{-.5cm}
@@
 
-\includegraphics[width=.9 \linewidth]{Cylinder_EigenModeAdjRe60.png}
+\includegraphics[width=\linewidth]{Cylinder_EigenModeAdjRe60.png}
 %\vspace{-.5cm}\vspace{-.5cm}
-%\includegraphics[width=.9 \linewidth]{Cylinder_SensitivityRe60.png}
+%\includegraphics[width=\linewidth]{Cylinder_SensitivityRe60.png}
 %\vspace{-.5cm}
-\caption{Contour plot of the streamwise velocity component: $(a)$ (Direct) Eigenmode; $(b)$ Adjoint mode at $Re=Re_c = 60$.}
+\caption{Contour plot of the streamwise velocity component: $(a)$ (Direct) Eigenmode; $(b)$ Adjoint mode at $Re= 60$.}
 \label{fig:Eigenmode}
@@
 \begin{figure}
-\includegraphics[width=.9 \linewidth]{Cylinder_SensitivityRe60.png}
-\includegraphics[width=.9 \linewidth]{Cylinder_EndogeneityRe60.png}
+\includegraphics[width=\linewidth]{Cylinder_SensitivityRe60.png}
 %\vspace{-.5cm}
-\caption{ ($a$) {\em Wavemaker}  field $S_w$ and $(b)$ {\em Endogeneity} field $S_e$ fields for the cylinder's wake at $Re=Re_c = 60$.
-In plot $(b)$ the color scale indicates real part and levels indicate imaginary part (10 equidistant levels, the maximum value being +0.240).
-The red line represents the streamline bounding the recirculation region.}
+\caption{ Structural sensitivity $S_w$ for the cylinder's wake at $Re= 60$. The red line represents the streamline bounding the recirculation region.}
 \label{fig:StructEndo}
@@
 
-The wavemaker $S_w$ and endogeneity $S_e$ fields, introduced in section 2.2, are displayed in figure \ref{fig:StructEndo}.
+The structural sensitivity $S_w$ introduced in section 2.2 is displayed in figure \ref{fig:StructEndo}.
 As discussed in section 2.2, both these quantities allow identifying the 'active' flow regions responsible for the instability mechanism.
 The real quantity $S_w$ indicates that the most active region roughly coincides with the recirculation bubble.
-The endogeneity $S_e$ yields more information of interest.
-The sign of the real part (color levels) indicates that the two most destabilizing regions are the boundary layer at the top of the cylinder and the shear layer bonding the recirculation region, and that the region of the stagnation point and the exterior of the recirculation region are destabilizing.
-The imaginary part (isolevels) indicates that the frequency selection occurs in the shear layer region.
+%The endogeneity $S_e$ yields more information.
+The sign of the real part (color levels)  indicate that the two most destabilizing regions are the boundary layer at the top of the cylinder and the shear layer bonding the recirculation region, and that the region of the stagnation point and the exterior of the recirculation region are destabilizing.
+The imaginary part (isolevels) indicate that the frequency selection occurs in the shear layer region.
+
+\section{Extension : compressible flows}
+
+The main concepts of global linear stability analysis, exposed in section 2 for the simplest case of incompressible flows, are directly generalizable to more complex situations involving compressibility, fluid-structure interactions, deformable free surfaces, etc...
+Such more complex situations can also be studied using the same class of numerical methods and the same methodology.
+One of the ambitions of the StabFem software if to provide a unified procedure to perform such stability studies, so that despite the fact that the underlying equations may be different, the corresponding Octave/Matlab scripts will be almost the same in all cases.
+In this section, we will illustrate this point for the case of a compressible flow, keeping the geometry as a 2D cylinder, and will reproduce the results of the recent study of \cite{Fani2018}.
+
+\subsection{Analysis and implementation}
+
+In the compressible case, the Navier-Stokes equations have to be formulated in terms of a state-vector $[{\bf u},p,\rho,T]$ with larger dimension. 
+The equations involve a larger number of terms but can be written in a compact way as follows :
+
+\begin{eqnarray} \label{NSprimitive}
+\partial_t {\cal B} [{\bf u},p,\rho,T] = {\cal NS}  [{\bf u},p,\rho,T] 
+\end{eqnarray}
+
+Here $\cal B$ is a "weight" operator specifying the coefficients in front of the time-derivatives of $[{\bf u},p,\rho,T]$ , and the operator $ {\cal NS}  [{\bf u},p,\rho,T] $ specifies the time-evolution of  $[{\bf u},\rho,T]$ coming from the momentum, energy and mass balances as well as the state equation linking $[p,T,\rho]$.
+The detailed form of these equation is given in \cite{Fani2018}.
+
+Starting with this form, the two main steps of the analysis, namely computation of a base-flow and eigenvalue computation, can be done in the same way as explained in sec. 2. Namely :
+\begin{itemize}
+\item[-] The base-flow $[{\bf u}_b,p_b,\rho_b,T_b]$ is the solution of ${\cal NS}  [{\bf u}_b,p_b,\rho_b,T_b]=0$ (eqs.
+4$(a-d)$ of  \cite{Fani2018}) which can readily be computed using Newton iteration.
+\item[-] Eigenvalues $\lambda$ and Eigenvalues $[\hat{{\bf u}},\hat{p},\hat{\rho},\hat{T}]$ are solutions of the eigenvalue problem $\lambda {\cal B}  [\hat{{\bf u}},\hat{p},\hat{\rho},\hat{T}]^T = {\cal LNS} [\hat{{\bf u}},\hat{p},\hat{\rho},\hat{T}]^T $ (eqs.
+5$(a-d)$ of  \cite{Fani2018}) which can be solved using either single-mode shift-invert iteration or multiple-mode Arnoldi iteration.
+\end{itemize}
+
+In our implementation, these calculations are done by the FreeFem++ solvers {\sf  Newton2DComp.edp} and {\sf  Stab2DComp.edp}, which are quite different from their incompressible counterparts, but these solvers are wrapped by the same generic drivers {\sf  SF_BaseFlow.m}  and {\sf  SF_Stability.m}.
+The selection of which solver to use is made according to the parameters transmitted to them.
+
+\subsection{Example : 2D compressible flow around a cylinder}
+
+ \begin{figure}
+\includegraphics[width=\linewidth]{Cylinder_EigenmodeRe60Ma02_vort.png}
+\caption{Structure of the unstable eigenmode (streamwise velocity component) for the compressible flow around a cylinder  $(Re= 150,M=0.2)$.}
+\label{fig:Eigenmode}
+\end{figure}
+
+As an illustration, we consider the compressible flow around a 2D cylinder (same geometry as in previous section).
+The reader may find on the website of the project a script \footnote{ \url{https://gitlab.com/stabfem/StabFem/blob/master/STABLE_CASES/compCYLINDER/SRIPT_Fani.m}} reproducing the main results of the study of \cite{Fani2018}.
+We restrict here to the illustration of the structure of the unstable eigenmode for $Re = 150; M = 0.2$.
+Figure \ref{fig:compcyl_ux} shows the axial velocity associated to the eigenmode in a domain centered on the body.
+Figure \ref{fig:compcyl_p} displays the stucture of the pressure field on a much larger domain, allowing to detail the structure of the radiated acoustic field.
+The structure is in perfect agreement with the results of \cite{Fani2018} (see 5$(a)$ and $8$ of this paper).
+The value of the corresponding eigenvalue is also perfectly reproduced, namely $\lambda = 0.446+0.697i$.
+
+ \begin{figure}
+\includegraphics[width=\linewidth]{Cylinder_EigenmodeRe60Ma02_p.png}
+\caption{Structure of the unstable eigenmode (pressure component) for the compressible flow around a cylinder  $(Re= 150,M=0.2)$.}
+\label{fig:Eigenmode}
+\end{figure}
 
@@
 In the nonlinear regime, the {\em base flow} introduced in the linear theory is no longer relevant, especially when the oscillation amplitudes become large.
-Instead, one may define a {\em mean flow} by time-averaging: 
+Instead, one may define a {\em mean flow} by using a time-average: 
 %{\color{red} we taken the Reynolds decomposition ${\bf u}={\bf u}_m({\bf x})+{\bf u}'({\bf x},t)$, with ${\bf u}'$ the nonlinear perturbation and ${\bf u}_m$ the {\em mean flow} defined as the time-average  of the flow:}
@@
 
-This expansion is built as an asymptotic expansion in terms of the small parameter $\epsilon = \sqrt{1/Re_c - 1/Re}$ corresponding to the distance to the critical Reynolds. 
+This expansion is built as an asymptotic expansion in terms of the small parameter $\epsilon = \sqrt{1/Re_c - 1/Re}$ corresponding to the distance to the critical Reynolds number. 
 The zero-order term ${\bf u}_{bc}$ is the base flow at the threshold $Re_c$.
@@
 In the first-order term, $\hat{\bf u}$ is the neutral eigenmode at $Re_c$ conveniently normalized (see discussion in appendix B), 
-$A_{wnl}$ an amplitude which can be assumed as real, $\omega_c$ the frequency predicted by the linear approach at $Re=Re_c$ and $\omega_\epsilon$ a small deviation of the frequency.
+$A_{wnl}$ an amplitude which can be assumed as real, $\omega_c$ the frequency predicted by the linear approach at $Re=Re_c$ and $\omega_\epsilon$ a small deviation on the frequency.
 
@@
 
-Finally, as specified above, we explain how the mean drag $F_{x,0}$ and fundamental components $(F_{y,1,c},F_{y,1,s})$ of the oscillating lift can be predicted from the WNL approach.
+Finally, as specified above, we explain how the mean drag $F_{x,0}$ and fundamental components $(F_{y,1,c},F_{y,1,s})$ of the oscillating lift can be predicted by the WNL approach.
 The mean drag  can be obtained by $F_{x,0} = {\cal D}_{Re}({\bf u}_m,p_m)$, where ${\cal D}$ is the drag operator defined in \eqref{drag} and 
@@
 
-Lines 1-8 of the script shown in figure \ref{fig:listingNL}, which is extracted from the script 
-{\sf SCRIPT\_CYLINDER\_ALLFIGURES.m}, illustrate the sequence of commands to 
+Lines 1-8 of the script shown in figure \ref{fig:listingNL} (extracted from the script 
+{\sf SCRIPT\_CYLINDER\_ALLFIGURES.m}) illustrate the sequence of commands to 
 perform the weakly nonlinear study for the cylinder wake.
@@
 On line 4, we then compute all the terms and coefficients of the WNL model.
-Lines 6-8 then process the results so that they can be plotted.
+Lines 6-8 then process the results in a way they can be plotted.
 %{\color{red}The other lines are explained latter.}
@@
 
-Figure \ref{fig:HB_SC_DATA_COMP} represents the predictions of the WNL approach regarding the frequency (expressed as a Strouhal number through $St = \omega/2\pi$), mean drag, amplitude of the oscillating lift, and energy-amplitude.
+Figure \ref{fig:HB_SC_DATA_COMP} shows the predictions of the WNL approach regarding the frequency (expressed as a Strouhal number through $St = \omega/2\pi$), mean drag, amplitude of the oscillating lift, and energy-amplitude.
 As discussed in \cite{SippLebedev} and \cite{FDR2016}, when compared to DNS results, this approach gives good prediction in the immediate vicinity of $Re_c$, but deviation appears very rapidly and disagreement is already large at $Re=48$ (although, as discussed by \cite{FDR2016} and also observed by \cite{Tchoufag2015}, a convenient definition of $\epsilon$ improves the prediction).
@@
 \begin{center}
-\includegraphics[width=.9 \linewidth]{Cylinder_Strouhal_Re_HB.png}
-\includegraphics[width=.9 \linewidth]{Cylinder_Cx_Re_HB.png}
-\includegraphics[width=.9 \linewidth]{Cylinder_Cy_Re_SC.png}
-\includegraphics[width=.9 \linewidth]{Cylinder_Energy_Re_SC_AdaptD.png}
-\includegraphics[width=.9 \linewidth]{Cylinder_Lx_Re_HB.png}
+\includegraphics[width=\linewidth]{Cylinder_Strouhal_Re_HB.png}
+\includegraphics[width=\linewidth]{Cylinder_Cx_Re_HB.png}
+\includegraphics[width=\linewidth]{Cylinder_Cy_Re_SC.png}
+\includegraphics[width=\linewidth]{Cylinder_Energy_Re_SC_AdaptD.png}
+\includegraphics[width=\linewidth]{Cylinder_Lx_Re_HB.png}
 \end{center}
@@
 %\begin{center}
-%\includegraphics[width=.9 \linewidth]{Cylinder_SC100_EnergySigma.png}
-%\includegraphics[width=.9 \linewidth]{Cylinder_SC100_CySigma.png}
+%\includegraphics[width=\linewidth]{Cylinder_SC100_EnergySigma.png}
+%\includegraphics[width=\linewidth]{Cylinder_SC100_CySigma.png}
 %\end{center}
@@
 
-The original version of the model (discussed with some supplementary details in appendix C) allowed obtaining an amplitude equation predicting the instantaneous growth rate $\sigma$ as function of the amplitude $A_{sc}$.
+The original version of the model (discussed in detail in appendix C) allowed to obtain an amplitude equation predicting the instantaneous growth rate $\sigma$ as function of the amplitude $A_{sc}$.
 However, if we are simply interested in the properties of the limit cycle, not the transient, we may recast the self-consistent model in a simpler way.
@@
 In order to solve this coupled problem, we thus need an extra scalar equation.
-The latter is provided by fixing {\em phase} of the cycle.
+The latter is provided by fixing the {\em phase} of the cycle.
 Several choices are possible, but a convenient one is to decide that the instant $t=0$ corresponds to a maximum of the lift force.
@@
 After discretization, this leads to a linear problem of the form $A X = Y$ where $X$ is the discretized version of the unknowns  $[\delta {\bf u }_m, \delta {\bf u }_{1,c}, \delta {\bf u }_{1,s}, \delta \omega]$, and $A$ is a matrix of dimension $3 N_{dof} +1$, where $N_{dof}$ is the dimension of the Taylor--Hood basis of finite elements describing each of the three $[{\bf u},p]$ fields.
-This system is solved iteratively as explained in section 2.1 for determination of the base flow.
+This system is solved iteratively as explained in section 2.1 for the determination of the base flow.
 %Using the adapted mesh described in figure 2, the dimension of the system is $3 N_{dof} +1 \approx 58 000$ and the resolution remains possible at very reasonable computational costs.
@@
 
- \paragraph{Results for a cylinder}
-
-Lines 10-17 of the script shown in figure \ref{fig:listingNL} explain how to to use these programs to the SC/HB1 model for the wake of a cylinder in the range $Re \in [47-100] $.
+ \paragraph{Results for the cylinder's wake}
+
+Lines 10-17 of the script shown in figure \ref{fig:listingNL} explain how to use these programs to the SC/HB1 model for the wake of a cylinder in the range $Re \in [47-100] $.
 Note that a {\em guess} for the mean flow and the self-consistent mode for $Re = 47$, \textit{i.e.} just above the threshold, has already been generated from the weakly nonlinear model at line 4 of the same script.
@@
 \begin{center}
-\includegraphics[width=.9 \linewidth]{Cylinder_MeanFlowRe60.png}
+\includegraphics[width=\linewidth]{Cylinder_MeanFlowRe60.png}
 \end{center}
@@
 
-The objective of this paper was twofold.
+The objective of this paper is twofold.
 First, we aimed at giving an up-to-date and comprehensive review on global stability approaches, both linear and nonlinear, including the most recent developments of the field.
@@
 \mathbf{M}_2' \mbox{(Adapt on sensitivity, split) } & 7974 & 70651	& 0.00786 & 7.131  		& 0.0104 	& 0.0744 	&   0.0975 & 0.614   \\
-\mathbf{M}_3 \mbox{(Adapt on endogeneity) } & 3749 & 32655	& 0.01542 & 12.7109  		& 0.09689 	& 0.1236 	&   0.2004 & 0.65775   \\
+\mathbf{M}_3 \mbox{(Adapt following \cite{mavripilis2015adjoint}) } & 3749 & 32655	& 0.01542 & 12.7109  		& 0.09689 	& 0.1236 	&   0.2004 & 0.65775   \\
 \mathbf{M}_4 \mbox{(Adapt on mode) } 	& 12080  & 103564		&0.00825	& 12.461		& 0.0229	& 0.143	& 0.0993	& 0.0934 \\
@@
 Mesh $\mathbf{M}_2'$ was obtained by a subsequent refinement of mesh $\mathbf{M}_2$, splitting all triangles in four subtriangles, therefore doubling the effective density of the mesh.
-Mesh $\mathbf{M}_3$ was adapted to both the base flow and endogeneity (strategy E).
+Mesh $\mathbf{M}_3$ was adapted to both the base flow and following \cite{mavripilis2015adjoint} (strategy E).
 Meshes $\mathbf{M}_4$ and $\mathbf{M}_5$ were obtained by adapting to the structure of the direct eigenmode (strategy D) and of the adjoint eigenmode (strategy A).
@@
 Figures \ref{fig:mesh2} and \ref{fig:mesh4} illustrate the structure of meshes $\mathbf{M}_2$ and $\mathbf{M}_4$.
-It can be observed that these two mesh adaptation strategies lead to meshes with comparable densities in the region close to the cylinder.
+It can be observed that these two mesh-adaptation strategies lead to meshes with comparable densities in the region close to the cylinder.
 On the other hand, when moving downwards in the wake, mesh $\mathbf{M}_2$ quickly gets rather coarse while mesh $\mathbf{M}_4$ maintains a significant density.
@@
 Table \ref{tab:conv1} gives numerical informations about the geometry of these meshes.
-In particular, we document the minimum and maximum cell size, as well as the cell size at four point A,B,C,D defined with by their coordinates as follows: $(x_A,y_A) = (0,0.5)$ (within the boundary layer at the cylinder wall); $(x_B,y_B) = (2.5,0.5)$ (in the region of maximum structural sensitivity); $(x_C,y_C) = (4,0)$ (in the near wake); $(x_D,y_D) = (10,0)$ (in the far wake).
+In particular, we document the minimum and maximum cell size, as well as the cell size at four points A,B,C,D defined with by their coordinates as follows: $(x_A,y_A) = (0,0.5)$ (within the boundary layer at the cylinder wall); $(x_B,y_B) = (2.5,0.5)$ (in the region of maximum structural sensitivity); $(x_C,y_C) = (4,0)$ (in the near wake); $(x_D,y_D) = (10,0)$ (in the far wake).
 Results confirm that all meshes have similar densities in the near wake (cell size at points A,B,C are comparable) while $\mathbf{M}_4$ has maximum resolution in the far wake (in the vicinity of point D).
@@
 On the other hand, if we are interested in describing the structure of the perturbation in the whole domain (and being able to correctly evaluate its energy), mesh adaptation to the eigenmode structure is preferable.
-However this second strategy produces a much heavier mesh (here 12080 point).
+However this second strategy produces a much finer mesh (here 12080 point).
 
@@
 In this appendix, we provide pieces of codes illustrating how the basic algorithms are implemented in the FreeFem++ solvers.
-These explanations will be useful both for readers who wish to use directly FreeFem++ solvers without using the overlayer of Octave/Matlab drivers provided by the StabFem software, and also for those who want to understand the logics of the implementation and customize the software to implement their own cases.
+These explanations will be useful both for readers who wish to use directly FreeFem++ solvers without using the overlayer of Octave/Matlab drivers provided by the StabFem software, and also for the reader who wants to understand the logics of the implementation and to customize the software to implement their own cases.
 The full version of the codes is available in the web repository of the StabFem project.

### 2018-12-09 99_Documentation/ARTICLE_STABFEM/ARTICLE_ASME_Revision.tex
final (?) version of the paper

@@
 %%% first author
-\author{D. Fabre$^{(a)}$,  V. Citro$^{(b,a)}$,  D. Ferreira Sabino$^{(a)}$, P. Bonnefis$^{(a)}$,  F. Giannetti$^{(b)}$ \& M. Pigou$^{(a)}$ 
+\author{D. Fabre$^{(a)}$,  V. Citro$^{(b,a)}$,  D. Ferreira Sabino$^{(a)}$, P. Bonnefis$^{(a)}$,  J. Sierra $^{(a)}$, F. Giannetti$^{(b)}$ \& M. Pigou$^{(a)}$ 
     \affiliation{
@@
 An open-source software implementing all the concepts discussed in the present paper is provided. 
-The software is demonstrated for the reference case of the incompressible, two-dimensional flow around a circular cylinder, but is easily customisable to a variety of other flow configurations or flow equations.
+The software is demonstrated for the reference case of the two-dimensional flow around a circular cylinder, in both incompressible and compressible cases, but is easily customisable to a variety of other flow configurations or flow equations.
 %An abstract for an ASME paper should be less than 150 words and is normally in italics.
@@
 
-The mesh generated by the previous way may not be optimal for the stability calculations as the structure of the eigenmode may be more complex than that of the base flow. 
-To tackle this aspect, the idea is to subsequently adapt the mesh to both the mesh flow and the results of the stability calculation.
+%The mesh generated by the previous way may not be optimal for the stability calculations as the structure of the eigenmode may be more complex than that of the base flow.
+To tackle this aspect, the idea is to subsequently adapt the mesh to both the mesh flow and the results of the stability calculation.This is easily done with FreeFem, as the  AdaptMesh procedure can be used with several objective functions.We have experimented four different strategies.The first (D strategy) is to adapt the mesh to the base flow and the structure of the leading direct eigenmode.
+A second strategy (A) is to use the adjoint mode instead of the direct mode for mesh adaptation.
+However, as the sensitivity of the eigenvalue to perturbations of the operator (including discretization errors) is more closely linked to structural sensitivity concepts, it sounds a better idea to use either the 'wavemaker' $S_w$ or the endogeneity $S_e$ to adapt the mesh, leading to the two last experimented strategies, called S and E.Note that using the S strategy was already experimented in {\em \cite{GiannettiLuchini} for the wake of a cylinder (IS THAT THE RIGHT REFERENCE ??}).Mesh adaptation using the scalar product of the direct and adjoint eigenmodes (which turns out to be equivalent to the E strategy introduced here considering the definition of the endogeneity) was also proposed in \cite{mavripilis2015adjoint}.A detailed comparison of the four strategies is reported in appendix A.It is shown that for the case of a cylinder, all strategies give the same values for base-flow drag, eigenvalues and several properties of the nonlinear limit cycle (see sec.
+4) with less than $0.3\%$ deviation, but that the A, E and especially the S strategy lead to significantly lower number of grid points compared to the D strategy.
+%The practical conclusions of this study are the following recommendations:
+
+%\begin{itemize}
+%\item[-] 
+%First, if one is only interested in the eigenvalues --for instance to plot growth rates as function of Reynolds or to identify the critical Reynolds number,-- the A, E or S strategies are the best options.
+In the case of the cylinder, the S strategy leads to the lightest mesh.
+The E strategy results in a more refined mesh as the function $S_e$ is complex and displays more gradients than the real-valued function $S_w$ (as illustrated in figure \ref{fig:StructEndo}); hence the sensitivity revealed by the phase of $S_e$, which may be significant, is not captured by using the simpler function $S_w$.
+In the case of the flow around a cylinder,  this loss of information has no practical effect on the results, but for usage with more complex flows, our recommendation for future studies will be to favour the E strategy.
+%\item[-] 
+%The situation is different if one wants to design a mesh allowing to study the flow structure in the whole domain (for instance for plotting its structure).
+In that case, using A,E or S strategy will allow to accurately compute the eigenvalue and the structure of the mode in the wavemaker region, but will not allow for a proper resolution in the regions located far away where the direct mode may reach large amplitude.
+This is particularly the case for open flows characterized by large spatial convective amplifications.
+In such cases the D strategy is the only way to get a proper description of the eigenmode in the whole domain.
+%\end{itemize}
+
+The mesh generated in the previous way may not be optimal for the stability calculations as the structure of the eigenmode may be more complex than that of the base flow.
+To remedy with this, the idea is to subsequently adapt the mesh to both the mesh flow and the results of the stability calculation.
 This is easily done with FreeFem, as the  AdaptMesh procedure can be used with several objective functions.
@@
 A second strategy (A) is to use the adjoint mode instead of the direct mode for mesh adaptation.
-However, as the sensitivity of the eigenvalue to perturbations of the operator (including discretization errors) is more closely linked to structural sensitivity concepts, it sounds a better idea to use either the 'wavemaker' $S_w$ or the endogeneity $S_e$ to adapt the mesh, leading to the two last experimented strategies, called S and E.
-Note that using the S strategy was already experimented in {\em \cite{GiannettiLuchini} for the wake of a cylinder (IS THAT THE RIGHT REFERENCE ??}).
-Mesh adaptation using the scalar product of the direct and adjoint eigenmodes (which turns out to be equivalent to the E strategy introduced here considering the definition of the endogeneity) was also proposed in \cite{mavripilis2015adjoint}.
+However, as the sensitivity of the eigenvalue to perturbations of the operator (including discretization errors) is more closely linked to structural sensitivity concepts, it sounds a better idea to use the 'wavemaker' $S_w$ to adapt the mesh, leading to the last experimented strategy, called S.
+Mesh adaptation using the scalar product of the direct and adjoint eigenmodes  (called E-strategy) was also proposed in \cite{mavripilis2015adjoint} (this quantity has also beed discussed by \cite{marquet2015endogeneity}).
 A detailed comparison of the four strategies is reported in appendix A.
 It is shown that for the case of a cylinder, all strategies give the same values for base-flow drag, eigenvalues and several properties of the nonlinear limit cycle (see sec.
-4) with less than $0.3\%$ deviation, but that the A, E and especially the S strategy lead to significantly lower number of grid points compared to the D strategy.
-The practical conclusions of this study are the following recommendations:
-
-\begin{itemize}
-\item[-] 
-First, if one is only interested in the eigenvalues --for instance to plot growth rates as function of Reynolds or to identify the critical Reynolds number,-- the A, E or S strategies are the best options.
-In the case of the cylinder, the S strategy leads to the lightest mesh.
-The E strategy results in a more refined mesh as the function $S_e$ is complex and displays more gradients than the real-valued function $S_w$ (as illustrated in figure \ref{fig:StructEndo}); hence the sensitivity revealed by the phase of $S_e$, which may be significant, is not captured by using the simpler function $S_w$.
-In the case of the flow around a cylinder,  this loss of information has no practical effect on the results, but for usage with more complex flows, our recommendation for future studies will be to favour the E strategy.
-\item[-] 
-The situation is different if one wants to design a mesh allowing to study the flow structure in the whole domain (for instance for plotting its structure).
-In that case, using A,E or S strategy will allow to accurately compute the eigenvalue and the structure of the mode in the wavemaker region, but will not allow for a proper resolution in the regions located far away where the direct mode may reach large amplitude.
-This is particularly the case for open flows characterized by large spatial convective amplifications.
-In such cases the D strategy is the only way to get a proper description of the eigenmode in the whole domain.
-\end{itemize}
+4) with less than $0,3\%$ deviation, but that the A, E and especially the S strategy lead to significantly lower number of grid points compared to the D strategy.
+Note that a valid alternative (not yet available in the StabFem  project) is offered by the Error Sensitivity to Refinement recently proposed by \cite{Luchini2017}.
 
@@
 The main concepts of global linear stability analysis, exposed in section 2 for the simplest case of incompressible flows, are directly generalizable to more complex situations involving compressibility, fluid-structure interactions, deformable free surfaces, etc...
-Such more complex situations can also be studied using the same class of numerical methods and the same methodology.
+Such more complex situations can be studied using the same class of numerical methods and the same methodology.
 One of the ambitions of the StabFem software if to provide a unified procedure to perform such stability studies, so that despite the fact that the underlying equations may be different, the corresponding Octave/Matlab scripts will be almost the same in all cases.
@@
 
-In our implementation, these calculations are done by the FreeFem++ solvers {\sf  Newton2DComp.edp} and {\sf  Stab2DComp.edp}, which are quite different from their incompressible counterparts, but these solvers are wrapped by the same generic drivers {\sf  SF_BaseFlow.m}  and {\sf  SF_Stability.m}.
+In our implementation, these calculations are done by the FreeFem++ solvers {\sf  Newton2DComp.edp} and {\sf  Stab2DComp.edp}, which are quite different from their incompressible counterparts.
+However these solvers are wrapped by the same generic drivers {\sf  SF\_BaseFlow.m}  and {\sf  SF\_Stability.m}.
 The selection of which solver to use is made according to the parameters transmitted to them.
@@
 \caption{Structure of the unstable eigenmode (streamwise velocity component) for the compressible flow around a cylinder  $(Re= 150,M=0.2)$.}
-\label{fig:Eigenmode}
+\label{fig:compcyl_ux} 
 \end{figure}
@@
 The structure is in perfect agreement with the results of \cite{Fani2018} (see 5$(a)$ and $8$ of this paper).
-The value of the corresponding eigenvalue is also perfectly reproduced, namely $\lambda = 0.446+0.697i$.
+The value of the corresponding eigenvalue is also perfectly reproduced, namely $\lambda = 0.15273+0.64482i$.
 
@@
 \includegraphics[width=\linewidth]{Cylinder_EigenmodeRe60Ma02_p.png}
-\caption{Structure of the unstable eigenmode (pressure component) for the compressible flow around a cylinder  $(Re= 150,M=0.2)$.}
-\label{fig:Eigenmode}
+\caption{Structure of the unstable eigenmode (pressure component) for the compressible flow around a cylinder  $(Re= 150,M=0.2)$. Upper half : real part ; lower half : imaginary part. }
+\label{fig:compcyl_p}
 \end{figure}
@@
 \begin{center}
-\includegraphics[width=\linewidth]{Cylinder_Strouhal_Re_HB.png}
-\includegraphics[width=\linewidth]{Cylinder_Cx_Re_HB.png}
-\includegraphics[width=\linewidth]{Cylinder_Cy_Re_SC.png}
-\includegraphics[width=\linewidth]{Cylinder_Energy_Re_SC_AdaptD.png}
-\includegraphics[width=\linewidth]{Cylinder_Lx_Re_HB.png}
+\includegraphics[width=0.9\linewidth]{Cylinder_Strouhal_Re_HB.png}
+\includegraphics[width=0.9\linewidth]{Cylinder_Cx_Re_HB.png}
+\includegraphics[width=0.9\linewidth]{Cylinder_Cy_Re_SC.png}
+\includegraphics[width=0.9\linewidth]{Cylinder_Energy_Re_SC_AdaptD.png}
+\includegraphics[width=0.9\linewidth]{Cylinder_Lx_Re_HB.png}
 \end{center}
@@
 Secondly, we intended to provide an easy to use software performing all these computations from a single program.
-In accordance with this objective, all the figures presented in the paper can be produced by launching a single Octave/Matlab program available on the website of the project.
+In accordance with this objective, all the figures presented in the paper can be produced by launching a single Octave/Matlab program available on the website of th project.
 This program handles all computation steps, from calls to FreeFem++ to figure generation.
 
-Although the focus here was on the reference case of 2D incompressible flow around a cylinder, the {\em StabFem } software is designed to be easily customisable to a variety of other situations.
+Although the focus here was on the reference case of 2D incompressible and compressible flow around a cylinder, the {\em StabFem } software is designed to be easily customisable to a variety of other situations.
 The project is currently in constant development, and incorporates a growing number of other configurations.
@@
 \begin{itemize}
-\item[-] Incompressible flows around 2D objects, either fixed or in movement such as the case of a spring-mounted cylinder \cite{Navrose},
-\item[-] Incompressible flows in axisymmetric geometries such as the wake of spheres and disks \cite{Tchoufag2015} and the flow through apertures \cite{FabreISMA}, 
-\item[-] Compressible flow around 2D objects  \cite{Fani2018}, 
-\item[-] Oscillations of hanging drops and liquid bridges \cite{Chireux2015}
+\item[-] Incompressible flows around 2D and axisymmetric blunt bodies of various geometries, including spheres and disks \cite{Tchoufag2015}. 
+\item[-] Incompressible flows around 2D and 3D objects in free movement, including for instance the spring-mounted cylinder \cite{Navrose}, and freely falling disks and spheres \cite{tchoufag2014global}.
+\item[-] Incompressible and compressible flow flow through apertures \cite{FabreISMA,longobardi2018IUTAM}, 
+\item[-] Compressible flow around 3D objects  \cite{meliga2010effect},
+\item[-] Oscillations of hanging drops, sessile drops and liquid bridges \cite{Chireux2015},
+\item[-] Rotating free surface flows \cite{mougel2017instabilities}.
 \end{itemize}
-The project is intended as collaborative, so anyone who wants to contribute is welcome !
+Our ambition is to use the website of the project as a support to publish scripts allowing anyone to reproduce the main results of our past and future publications
+on such topics.
+Such scripts are already available concerning Refs.
+\cite{Tchoufag2015,longobardi2018IUTAM,Chireux2015,mougel2017instabilities} and the list of available case will be growing in the coming months.The project is intended as collaborative, so anyone who wants to contribute is welcome !
 

### 2018-12-11 99_Documentation/ARTICLE_STABFEM/ARTICLE_ASME_Revision.tex
Submitted version of the paper

@@
 
-In this part, we expose the main concepts and methods of linear stability analysis for the case of a incompressible flow.
+In this part, we expose the main concepts and methods of linear stability analysis for the case of an incompressible flow.
 The extension to compressible flow will be considered in section \ref{sec:compressible}.
@@
  {\mathsf{D}}({\bf u}) = 1/2
-\left( \nabla {\bf u} +  \nabla^T  {\bf u}\right).
+\left( \nabla {\bf u} +  \nabla {\bf u}^T  \right).
 $$
@@
 \ees
-where ${\cal LNS}$ is the linearised Navier--Stokes operator, defined by its action on a flow field $[{\bf u} , p]$ as follows 
+where ${\cal LNS}$ is the linearised Navier--Stokes operator, defined by its action on the field $[{\bf u} , p]$ as follows 
 \be{defNSL}
@@
 As formalized by \cite{GiannettiLuchini} (following ideas previously proposed by \cite{hill1992theoretical}), this metrics quantifies how an eigenvalue is affected by the introduction of localized feedback of a flow perturbation onto itself.
-It thereby indicates the spatial regions where closed-loop control using a localized activator will be most efficient.
+It thereby indicates the spatial regions where closed-loop control using a localized feedback will be most efficient.
 Giannetti \& Luchini (2007) conjectured that regions where such an extrinsic feedback induces the strongest change of the eigenvalue are also the most significant regions considering the intrinsic feedback mechanisms that underpins the genuine eigenmode dynamics.
 Following this idea, structural sensitivity has thus become a popular way to characherize the  {\em wavemaker region} from where the instability mechanism originates.
-The structural sensitivity being a tensor, is is convenient to simply represent its norm $S_w$, often simply called 'the wavemaker':
+The structural sensitivity being a tensor, it is convenient to simply represent its norm $S_w$, often called the "wavemaker'"
 \be{Structursens} 
@@
 A second strategy (A) is to use the adjoint mode instead of the direct mode for mesh adaptation.
-However, as the sensitivity of the eigenvalue to perturbations of the operator (including discretization errors) is more closely linked to structural sensitivity concepts, it sounds a better idea to use the 'wavemaker' $S_w$ to adapt the mesh, leading to the last experimented strategy, called S.
+However, as the sensitivity of the eigenvalue to perturbations of the operator (including discretization errors) is more closely linked to structural sensitivity concepts, it sounds a better idea to use the "wavemaker" $S_w$ to adapt the mesh, leading to the last experimented strategy, called S.
 Mesh adaptation using the scalar product of the direct and adjoint eigenmodes  (called E-strategy) was also proposed in \cite{mavripilis2015adjoint} (this quantity has also beed discussed by \cite{marquet2015endogeneity}).
@@
 Appendix A presents additional tests regarding mesh convergence, and demonstrates that results obtained with the resulting mesh are reliable within $0.3\%$ accuracy tolerance for the eigenvalue.
-It must be emphasized  that the mesh generated through this adaptation process is very light, with only 2048 vertices, which is significantly less than reported in previous work (for instance, in their mesh convergence studies, \cite{SippLebedev} and \cite{MLugo2014} used respectively 190868  and 6731 vertices).
+It must be emphasized  that the mesh generated through this adaptation process is very light, with only 2048 vertices, which is significantly less than reported in previous works (for instance, in their mesh convergence studies, \cite{SippLebedev} and \cite{MLugo2014} used respectively 190868  and 6731 vertices).
 
@@
 The structural sensitivity $S_w$ introduced in section 2.2 is displayed in figure \ref{fig:StructEndo}.
-As discussed in section 2.2, both these quantities allow identifying the 'active' flow regions responsible for the instability mechanism.
+As discussed in section 2.2, both these quantities allow identifying the "active" flow regions responsible for the instability mechanism.
 The real quantity $S_w$ indicates that the most active region roughly coincides with the recirculation bubble.
@@
 \section{Extension : compressible flows}  
-
-The main concepts of global linear stability analysis, exposed in section 2 for the simplest case of incompressible flows, are directly generalizable to more complex situations involving compressibility, fluid-structure interactions, deformable free surfaces, etc...
+\label{sec:compressible}.
+
+The main concepts of global linear stability analysis, exposed in section 2 for the case of incompressible flows, are directly generalizable to more complex situations involving compressibility, fluid-structure interactions, deformable free surfaces, etc...
 Such more complex situations can be studied using the same class of numerical methods and the same methodology.
@@
  \begin{figure}
-\includegraphics[width=\linewidth]{Cylinder_EigenmodeRe60Ma02_vort.png}
+\includegraphics[width=\linewidth]{Cylinder_EigenmodeRe150Ma02_ux.png}
 \caption{Structure of the unstable eigenmode (streamwise velocity component) for the compressible flow around a cylinder  $(Re= 150,M=0.2)$.}
@@
  \begin{figure}
-\includegraphics[width=\linewidth]{Cylinder_EigenmodeRe60Ma02_p.png}
+\includegraphics[width=\linewidth]{Cylinder_EigenmodeRe150Ma02_p.png}
 \caption{Structure of the unstable eigenmode (pressure component) for the compressible flow around a cylinder  $(Re= 150,M=0.2)$. Upper half : real part ; lower half : imaginary part. }
@@
 Mesh convergence issues for the nonlinear calculations are discussed in appendix A.
-It is shown that the mesh $\mathbf{M}_2$ designed using 'S' strategy is sufficient to yield converged results within $0.3\%$ accuracy for all quantities considered here, with the exception of the energy-amplitude $A_E$ which requires the more refined mesh $\mathbf{M}_4$ obtained using 'D' strategy.\footnote{In terms of computational cost, on a standard laptop the program  \ref{fig:listingNL} requires approximatively 7 minutes using  mesh $\mathbf{M}_2$ and 31 minutes using mesh $\mathbf{M}_4$.}
+It is shown that the mesh $\mathbf{M}_2$ designed using "S" strategy is sufficient to yield converged results within $0.3\%$ accuracy for all quantities considered here, with the exception of the energy-amplitude $A_E$ which requires the more refined mesh $\mathbf{M}_4$ obtained using "D" strategy.\footnote{In terms of computational cost, on a standard laptop the program  \ref{fig:listingNL} requires approximatively 7 minutes using  mesh $\mathbf{M}_2$ and 31 minutes using mesh $\mathbf{M}_4$.}
 
@@
 \item[-] For $\sigma_{SC}=0$ (corresponding to a specific choice of the amplitude $A=A_{sc}$), the expansion \eqref{SC} is equivalent to 
-the Fourier expansion \eqref{eq:sc1} taken as the starting point in the present paper. 
+the Fourier expansion \eqref{HB} taken as the starting point in the present paper. 
 \item[-] For $0<A<A_{sc}$, the resolution leads to a relation $\sigma_{SC}(A) ; \omega_{SC}(A)$
